### 2021-06-29 Documents/Report-Project/Attachment_Analysis_Report.Rmd
init repo

---
title: 'Attachment Analysis: Report Project'
author: 'CZC, TM & GA'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2: 
    toc: true
    toc_depth: 3
    toc_float: true
    collapsed: false
    css: ["css/custom.css"]
linestretch: 1.5
number_sections: true
bibliography: "../Biblio-attachment.bib"
csl: apa.csl
link-citations: true 
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, collapse = TRUE)

library(tidyverse)
library(kableExtra)
library(mclust)

devtools::load_all("../../")

path_drake <- "../../.drake"

#----    load drake    ----

# Data
drake::loadd(data_munged)

# Cluster
drake::loadd(cluster_mother_tat)
drake::loadd(cluster_father_tat)
drake::loadd(data_cluster_tat)
drake::loadd(mclust_mother)
drake::loadd(mclust_father)

# brms models
drake::loadd(fit_int)
```

# Descriptive Statistics

## Dependent Variable

### Externalizing
```{r}
ggplot(data_munged) +
  geom_bar(aes(x = externalizing_sum, fill = genere), alpha = 0.7) +
  facet_grid(genere ~ .)
```

### Internalizing
```{r}
ggplot(data_munged) +
  geom_bar(aes(x = internalizing_sum, fill = genere), alpha = 0.7) +
  facet_grid(genere ~ .)
```

# Cluster Analysis

## Mother

```{r}
plot(cluster_mother_tat, main = "Dendrogramma")
rect.hclust(cluster_mother_tat, k=4, border="red")
```

Frequencies

```{r, echo = TRUE}
table(data_cluster_tat$cluster_mother_tat)

prop.table(table(data_cluster_tat$cluster_mother_tat))

prop.table(table(data_cluster_tat$cluster_mother_tat,
                 data_cluster_tat$genere),2)

summary(table(data_cluster_tat$cluster_mother_tat,
              data_cluster_tat$genere))
```

Plot Scores

```{r}
plot_scores_mother(data = data_cluster_tat)
```

#### Mclust check

```{r}
plot(mclust_mother)
summary(mclust_mother)
```

## Father

```{r}
plot(cluster_father_tat, main = "Dendrogramma")
rect.hclust(cluster_father_tat, k=4, border="red")
```

Frequencies

```{r, echo = TRUE}
table(data_cluster_tat$cluster_father_tat)

prop.table(table(data_cluster_tat$cluster_father_tat))

prop.table(table(data_cluster_tat$cluster_father_tat,
                 data_cluster_tat$genere),2)

summary(table(data_cluster_tat$cluster_father_tat,
              data_cluster_tat$genere))
```

Plot Scores

```{r}
plot_scores_father(data = data_cluster_tat)
```

#### Mclust check

```{r}
plot(mclust_father)
summary(mclust_father)
```

# Statistical Approach

In this section we describe the statistical approach. First we define the statistical model used to describe the data generative process. Subsequently, the approach for testing hypotheses with inequality and equality constraints is discussed. Finally, the Gibbs sampler to estimate the model with inequality constraints is presented.

## Model Definition

### Psychologial Background

In this analysis, we want to evaluate children psychological problems according to children gender and  children-mother and children-father attachment relationship. Note that attachment relationship is considered as a categorical variable.

### Zero Inflated Poisson (ZIP) {#model}

The dependent variable is a positive discrete variable. Considering Figure \@ref(fig:plot-int), it is possible to observe the the distribution of the dependent variable is characterized by a zero inflation.

```{r plot-int, fig.cap = "Dependent variable distribution"}
ggplot(data_munged) +
  geom_bar(aes(x = internalizing_sum, fill = 1), alpha = 0.7) +
  labs(x = "Internalizing Problems") +
  theme_bw() + 
  theme(legend.position = "none")
```

Thus, we decided to model the data considering a Zero Inflated Poisson (ZIP):

$$
y_i \sim ZIPoisson(p_i, \lambda_i)
$$

Where, $1 - p_i$ indicates the probability of given observation $y_i$ being generated from a Poisson distribution with mean $\lambda_i$. In particular,

$$
p_i = \text{logit}^{-1}(X_i^T\beta_{p}),\\
\lambda_i = \text{exp}(X_i^T\beta_{\lambda}).
$$

That is, we want to model both $p_i$ and $\lambda_i$ according to the variables previously defined estimating respectively parameters vector $\beta_p$ and $\beta_{\lambda}$. Note that these are the only parameters in the model.

This model can be easily estimate using `brms`. However, currently it is not possible to include inequality and equality constraints in the parameters prior definition.

Note that, the actual distribution of the dependent variable is truncated (limit given by the maximum questionnaire score). However, we do not consider this aspect to avoid a further level of complexity in the model.

## Test of Hypotheses with Inequality and Equality Constraints

**Bayes Factor** to evaluate different hypotheses with inequality and equality constraints can be obtained following the **Encompassing Prior Approach**. That is, an unconstrained model is considered as reference with encompassing priors that are uninformative with respect to the parameters. All other models are nested in this model and the priors ore obtained by restricting the parameter space in accordance with the constraints imposed by each model.

### Inequality Constraints: A First Approach

@katoBayesianApproachInequality2006 presented an approach to evaluate **inequality constraints** based on the principle of encompassing priors. Given an unconstrained model $M_u$ and a nested model $M_i$,  the prior and posterior densities of $M_i$ can be rewritten in terms of the prior and posterior densities of $M_u$:

$$
\pi(\theta|M_i) = B_i \times \pi(\theta|M_u),\\
Pr(\theta|D,\ M_i) = A_i \times Pr(\theta|D,\ M_u).
$$

Where, $1/B_i$ indicates the proportion of the prior distribution of $M_u$ in agreement with $M_i$ and $1/A_i$ is the proportion of the posterior distribution of $M_u$ in agreement with $M_i$.

Assuming equal prior probability of the two models ($\pi(M_u) = \pi(M_i)$), the Bayes Factor is obtained as follow:

\begin{aligned}
BF_{iu} =& \frac{Pr(D|M_i)}{Pr(D|M_u)} =\\ \\
&\frac{L(D|\theta)\pi(\theta|M_i)/Pr(\theta|D,\ M_i)}{L(D|\theta)\pi(\theta|M_u)/Pr(\theta|D,\ M_u)} = \\ \\
&\frac{\pi(\theta|M_i)Pr(\theta|D,\ M_u)}{\pi(\theta|M_u)Pr(\theta|D,\ M_i)} = \\ \\
&\frac{[B_i \times \pi(\theta|M_u)] Pr(\theta|D,\ M_u)}{\pi(\theta|M_u)[A_i \times Pr(\theta|D,\ M_u)]} = \frac{B_i}{A_i}
\end{aligned}

That is, the Bayes Factor is the ratio between $1/A_i$ (i.e. the proportion of the posterior distribution of $M_u$ in agreement with $M_i$ that provides information about the *fit* of $M_i$ relative to $M_u$), and $1/B_i$ (i.e., the proportion of the prior distribution of $M_u$ in agreement with $M_i$ that provides information about the *complexity* of $M_i$ relative to $M_u$).

Note that Bayes Factor is obtained without computing the marginal likelihoods of the two models, but only considering the proportions of the prior and the posterior in agreement with constraints of each of the models.

#### Pro {-}

- Given the prior and posterior samples of the model, it is straightforward to compute $1/A_i$ and $1/B_i$. The analytical distributions are not required.
- If Prior distributions of $\beta_p$ and $\beta_{\lambda}$ are vague enough and sample is large, influence of the choice of the encompassing prior on the posterior distributions is negligible, and subsequently also its influence on $1/A_i$ is negligible.
- For constraints of the form $\beta_i > \beta_j > \beta_k$ with $\beta_{i,j,k} \stackrel{i.i.d.}{\sim} \pi(\beta)$, the prior probability of the constraints is independent of the actual choice of the encompassing prior, and subsequently also $1/B_i$ is not influenced.

#### Cons {-}

- It is not possible to evaluate **equality constraints**. In the case of $H_i:\ \beta_i = \beta_j$,  $1/A_i$ and $1/B_i$ are equal to zero.
- Equality constraints can be expressed as $$|\beta_i - \beta_j|\leq \xi$$ for small value of $\xi$. In this case, however, for vague encompassing prior $1/A_i$ is still virtually independent but $1/B_i$ is not. The more diffuse the encompassing prior is the smaller the Bayes factor in favor of the unconstrained model (similar to *Lindley’s paradox* where results are influenced by the vagueness of the prior distribution of the parameters involved). Sensitivity analysis is required considering both the choice of prior distributions and the value of $\xi$.

#### Consideration {-}

This is a possible approach. However, in our hypotheses there are several equality constraints. Thus, it would be important to properly evaluate them.

### Inequality and Equality Constraints: A Second Approach {#in-eq-const}

@guApproximatedAdjustedFractional2018 and @mulderBayesFactorTesting2019 presented an approach to evaluate **inequality and equality constraints** still based on the principle of encompassing priors.

Informative hypotheses using equality and/or inequality constraints can be expressed as

$$
H_i:\ R_E\theta = r_E,\  R_I\theta > r_I
$$
where $R_E$ and $R_I$ are the restriction matrices for equality and inequality constraints, respectively, and $r_E$ and $r_I$ contain constants.

Following encompassing prior approach, given an unconstrained model $M_u$ and a nested model $M_i$, the Bayes Factor is computed as

\begin{aligned}
BF_{iu} = \frac{Pr(\text{Inequality Const} | \text{Equality Const}, \text{Data})}{\pi_u(\text{Inequality Const} | \text{Equality Const})} &\frac{Pr(\text{Equality Const}| \text{Data})}{\pi_u( \text{Equality Const})} = \\ \\  \frac{Pr(R_I\theta > r_I | R_E\theta = r_E, Y)}{\pi_u(R_I\theta > r_I | R_E\theta = r_E)} &\frac{Pr(R_E\theta = r_E| Y)}{\pi_u( R_E\theta = r_E)}.
\end{aligned}

Where, the first part is a ratio between conditional posterior and conditional prior **probabilities** that the inequality constraints hold under $M_u$. The second part is a ratio between  marginal posterior and marginal prior **densities** of the equality constraints under $M_u$, the well-known *Savage–Dickey density ratio*.

Note that the numerators provide information about the *fit* of $M_i$ relative to $M_u$ and the denominators provide information about the *complexity* of $M_i$ relative to $M_u$.

#### Pro {-}

- It allows to evaluate inequality and equality constraints.

#### Cons {-}

- The encompassing prior and posterior distributions are required in analytic form to compute conditional probabilities and marginal densities.

#### Consideration {-}

Obtaining the analytic posterior distribution is often difficult. To overcome this issue, @guApproximatedAdjustedFractional2018 and @mulderBayesFactorTesting2019 proposed two different solutions both based on **Normal approximations**. Let's consider the two approaches separately.

#### @mulderBayesFactorTesting2019 {#mulder}

Authors used to different solutions for computing the posterior and the prior:

- **Computing Posterior** - a Metropolis-Hastings algorithm is used to obtain draws from the posterior of the unconstrained model. Subsequently the posterior was assumed to be approximately normally distributed
$$
Pr(\theta|Y) \sim \mathcal{N}(\mu_\theta, \Sigma_\theta)
$$
where $\mu_\theta$ and $\Sigma_\theta$ are the posterior mean and covariance matrix estimated from the posterior draws. Thus, conditional posterior probability and marginal posterior density are computed based on the normal approximation.

- **Computing Prior** - in their case priors are not normally distributed. To estimate the marginal prior density they considered the fact that for a sufficiently small $\delta$,
$$
Pr(|\theta_{E_1} - r_{E_1}| < \frac{\delta}{2}, \ldots, |\theta_{E_i} - r_{E_i}| < \frac{\delta}{2}|M_u) \approx \delta^i \times \pi_u(\theta_E = r_E)
$$
Thus, the probability can be estimated considering the proportion of draws satisfying the constraints. To compute conditional prior probability, they used a normal approximation because this probability is not sensitive to the exact distributional form as long as they are symmetrical distributed around the value of the constraints, usually zero. The mean and covariance matrix were estimated based on the prior draws that satisfied the equality constraints. To do that they used the same approximation as before (i.e., $|\theta_{E_i} - r_{E_i}| < \frac{\delta}{2}$).

<!-- Note that their procedure implied a linear transformation of the parameters  to express constraints in a simpler form. -->

#### @guApproximatedAdjustedFractional2018

In this paper, the Approximated Adjusted Fractional Bayes Factors (AAFBF) method is presented. To avoid ad hoc or subjective specification of the unconstrained prior, the fractional Bayes factor approach is used. That is, proper default prior were defined updating non informative priors according to a a fraction *b* of the data
$$
\text{Proper Prior: }\pi_u(\theta|Y_b) \approx Pr(Y_b|\theta) \times \pi_u(\theta).
$$
The choice of the fraction $b$ also plays a crucial in the AAFBF and is extensively discussed in the article.

Prior and posterior distributions are assumed to be approximately normally distributed due to the large-sample theory:
\begin{aligned}
\text{Prior: }& \pi_u(\theta|Y_b) \sim \mathcal{N}(\hat{\theta}, \hat{\Sigma}_\theta/b),\\ \\
\text{Posterior: }& \pi_u(\theta|Y) \sim \mathcal{N}(\hat{\theta}, \hat{\Sigma}_\theta).
\end{aligned}
Where $\hat{\theta}$ and $\hat{\Sigma}_\theta$ denote the maximum likelihood estimate and covariance matrix of $\theta$, respectively.

Moreover, authors proposed an adjustment of the prior mean for centering the prior distribution of $\theta$ on the boundary of the constrained space. This ensure that $Pr(\theta>0)$ and $Pr(\theta<0)$ are equal for symmetric distributions and follow common assumption that small effects are more likely a prior than large effects. To facilitate the computation of the adjusted prior mean, the parameters are transformed,
$$
\beta = \left[\begin{array}{cc}\beta_E\\ \beta_I\end{array}\right] = \left[\begin{array}{cc}R_E \theta - r_E\\ R_I \theta - r_I\end{array}\right].
$$
In this way, informative hypothesis becomes $H_i:\ \beta_E=0, \beta_I>0$ and the prior mean vector is simply zero for the new parameter vector $\beta$. This parameter transformation from $\theta$ to $\beta$ simplifies the computation of the AAFBF.

Note authors did not adjusted posterior mean since, according to large-sample theory, the prior has a negligible effect on the posterior for large samples. Thus, resulting prior and posterior distributions are:
\begin{aligned}
\text{Adjusted Prior: }& \pi_u^*(\beta|Y_b) \sim \mathcal{N}(0, \hat{\Sigma}_\beta/b),\\ \\
\text{Posterior: }& \pi_u(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_\beta).
\end{aligned}
Where $\hat{\beta} = R\hat{\theta}-r$ and $\hat{\Sigma}_\beta = R\hat{\Sigma}_\theta R^T$.

### Present Study

In our case, the unconstrained model is a Zero Inflated Poisson model with parameter vectors $\beta_p$ and $\beta_{\lambda}$ (see Section \@ref(model)):

\begin{aligned}
y_i \sim& ZIPoisson(p_i, \lambda_i),\\ \\
p_i =& \text{logit}^{-1}(X_i^T\beta_{p}),\\ \\
\lambda_i =& \text{exp}(X_i^T\beta_{\lambda}).
\end{aligned}

We can assume independent priors for each parameter $\beta_i \sim \mathcal{N}(0, \sigma)$, with $\sigma$ a large enough so the priors are vague.

To evaluate informative hypothesis with equality and inequality constraints, we can follow the approach presented in Section \@ref(in-eq-const) considering the method proposed by @mulderBayesFactorTesting2019, see Section \@ref(mulder).

In our case, both the prior and the posterior distributions are normally distributed (TODO: is it true?):
\begin{aligned}
\text{Prior: }& \Pr(\beta) \sim \mathcal{N}(0, \Sigma_{\sigma}),\\ \\
\text{Posterior: }& \Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}).
\end{aligned}
Where $\Sigma_{\sigma}$ is a diagonal matrix with all the diagonal elements equal to $\sigma$. Whereas, $\mu_\theta$ and $\Sigma_\theta$ are the posterior mean and covariance matrix estimated from the posterior draws. Posterior sample can be easily obtained in STAN.

### Issues

1. Ha senso questo approccio?
1. Come posso marginalizzare i valori delle densità? Vedi le loro formule (p.27 in basso).
1. Come ottenere le distribuzioni condizionate? Vedi le loro formule negli articoli (p.28).
1. Dovrei preferire invece  l'Approximated Adjusted Fractional Bayes Factors method?
1. Nel modello ci saranno anche interazioni tra fattori, tutti i possibili gruppi. Devo pensare bene su come parametrizzare i contrasti.
1. Non sappiamo ancora quali saranno tutti i constraints e confronti ma sono tutti confronti tra gruppi. Devo essere sicuro che vengano rispettate le assunzioni delle ipotesi se uso l'Approximated Adjusted Fractional Bayes Factors method. Vedi "comparable hypotheses" formula 24 in @guApproximatedAdjustedFractional2018.
1. Potrei fare dell'hard coding codificando ogni gruppo con dummy variables. Non avrei "effetti principali" ma mi permette di evitare casini nel definire i confronti. (Nella codifica tradizionale i valori medi dei gruppi sarebbero dati da somme di più parametri, gli stessi parametri sarebbero usati per più gruppi e questo potrebbee compicare la definizione dei constraints sui parametri).
1. Devo stare attento che le prior non favoriscano alcun constraints e questo è problematico con gli equality constraints. (Al massimo faccio un po' di sensitivity sulle prior)

## Estimating the Constrained Model

Hypothesis testing will idicate us the most likely model according to the data. To evaluate the model parameters, howevere, we need to estimate the parameter posteriors.

Parameter posteriors of the unconstrained model can be simply obtained using MCMC sampling implemented in STAN. However, obtaining parameter posteriors of models including inequality constraints is not straightforward. Here we describe two possible direction: the first one based on STAN and the second one based Gibbs sampling.

### STAN Approach

Considering the thread in the STAN forum *"How to give prior to ordered parameters, and also to simplex?"* ([link](https://discourse.mc-stan.org/t/how-to-give-prior-to-ordered-parameters-and-also-to-simplex/12041)), there is one answer ([link](https://discourse.mc-stan.org/t/how-to-give-prior-to-ordered-parameters-and-also-to-simplex/12041/7?u=claudio.zandonella)) suggesting a possible solution based on uniform priors.

Given the restriction $a<\theta_1<\theta_2<\theta_3<b$, is it possible to redefine parameters as follow
$$
d\theta_2:= \theta_2 - \theta_1,\\
d\theta_3:= \theta_3 - \theta_2.
$$
Subsequentely, priors can be defined as
$$
\theta_1\sim \text{Unif}(a, b),\\
d\theta_2\sim \text{Unif}(0, b-\theta_1),\\
d\theta_3\sim \text{Unif}(0, b-\theta_2).
$$
Using Uniform prior is plausible as, selecting a range large enough, they can be considered uninformative and similar to a Normal distribution with very large $\sigma$. Note that in the present study, the sample size is large ($n\approx$900) so the posterior is not affected by the choice of vague priors.

#### Issues

Questa soluzione l'ho trovata all'ultimo, devo ancora fare delle prove per capire quanto possa essere realmente valida. Ma comunque la segnalo perchè mi sembra interessante.

Precedentemente cercavo se fosse possibile specificare prior normali con troncature. Il problema era che la troncatura dipenderebbe dagli altri parametri e quindi la stima diventerebba altamente instabile e le catene non convergono.

In effetti ridefinire i parametri e utilizzare delle uniformi sembra una buona soluzione. Solo non riesco a capire se ci saranno comunque problemi di convergenza delle catene e soprattutto la finale intertpretazione dei parametri.

### Gibbs Sampler Approach

@rodriguez-yamEfficientGibbsSampling implemented a Gibbs sampler for a ZIP model, whereas @ katoBayesianApproachInequality2006 presented a Gibbs sampler to estimate a model with inequality constraints using truncated normal distributions. We would like to put together the two methods in order to estimate a ZIP model with inequality constraints on the parameters.

We first consider the Gibbs sampler without constraints. Subsequently we discuss how to introduce the inequality constraints.

#### Conditional Posterior Distributions

In order to define the Gibbs sampler we need the joint posterior distribution from which to obtain the conditional distribution of each parameter. Let's define the elements of the posterior distribution.

#### Likelihood {-}

The likelihood of the ZIP model is

$$l(p,\lambda| \beta_p, \beta_{\lambda}, Y) = \prod_{y_i=0}\left[p_i + (1-p_i)e^{-\lambda_i}\right] \prod_{y_i\neq0}\left[ (1-p_i)\frac{\lambda_i^{y_i}e^{-\lambda_i}}{y_i!}\right]$$
where $p_i$ and $\lambda_i$ are defined according to parameters vector $\beta_p$ and $\beta_{\lambda}$, respectively. In particular,
$$
p_i = \text{logit}^{-1}(X_i^T\beta_{p}),\\
\lambda_i = \text{exp}(X_i^T\beta_{\lambda}).
$$

#### Prior{-}

We can assume the same independent prior distribution for all parameters of $\beta_p$ and $\beta_{\lambda}$.

$$\pi(\beta_p, \beta_{\lambda}) = \pi(\beta_p) \times \pi(\beta_{\lambda})$$
For example we can assume
$$
\pi(\beta) \sim \mathcal{N}(0, \Sigma).
$$

#### Posterior{-}

$$Pr(\beta_p, \beta_\lambda| Y) \propto l(p,\lambda| \beta_p, \beta_{\lambda}, Y) \times \pi(\beta_p, \beta_{\lambda_i})$$

#### Conditional Posteriors

Ok onde evitare di scrivere cavolate non mi metto a ottenere le distribuzioni condizionate. Ho trovato varie cose in internet, sembra abbastanza diretto ma sinceramente andrei alla cieca perchè gli esempi riguardano casi in cui non si fa la regressione di $\lambda_i$ e $p_i$. Quindi dato che si parla di conjugate priors e tante altre cose di cui sono assai ignorante, non riesco a capire se quelle soluzioni sono utilizzabili anche nel nostro caso direttamente.

Nel lavoro di @rodriguez-yamEfficientGibbsSampling, inoltre, fanno una cosa strana nel senso che definiscono $\lambda = X\beta+\epsilon$ e oltre a mettere le prior sui parametri $\beta$ la mettono anche su $\lambda$. Non capisco:

- perchè ci mettono il termine di errore $\epsilon$?
- il fatto di mettere la prior anche su $\lambda$ è un loro modo strano per mettere la prior sul termine $\epsilon$? Dato che la distibuzione di $\lambda$ dovrebbe essere data dai $\beta$ e $\epsilon$.

**Insomma la domanda è come ottengo le Conditional Posteriors Distributions da utilizzare nel Gibbs sampler?**

#### Including Inequality Constraints

To include inequality constraints in the model, @katoBayesianApproachInequality2006 sampled each $\beta_j$ from a truncated normal distribution with some lower bound $b$
and upper bound $c$, set equal to the other parameters according to the constrains. In particular, they sampled first a value $i$ from a uniform distribution on the interval (0,1) and then taking $\beta_j = \Phi_{\beta_j}^{-1}[\Phi_{\beta_j}(b) + i(\Phi_{\beta_j}(c)- \Phi_{\beta_j}(b))]$, where $\Phi_{\beta_j}$ denotes the standard normal cumulative probability function of $\beta_j$ evaluated at the argument.

Ook che so geroglifici? Immagino sia l'inversa di una distribuzione troncata... Comunque mi sembra una soluzione plausibile. Poi guardando le formule del loro gibbs sampling è tutto un casino. Ma sembra fattibile no?

### Issue

Vorrei poter stimare effettivamente i parametri del modello con i constraints per valutare quali sono gli effetti e non fermarmi al hypothesis testing con il BF. Penso che la soluzione del Gibbs sampling sia quella "più giusta" (o meno sbagliata ;) ) perchè quella con STAN non capisco bene se è realmente fattibile o meno.

Il problema resta che comunque non saprei come ricavarmi le distribuzioni condizionate delle posteriro da usare per il Gibbs Sampling.

Vorrei capire se

1. Ha senso questo approccio?
2. Come poter procedere per creare il Gibbs sampling con inequlaity constraints

## brms

```{r}
summary(fit_int)
```

```{r}
brms::conditional_effects(fit_int, ask= FALSE)
```

### Prior

```{r, echo = TRUE}
brms::get_prior(brms::bf(
      internalizing_sum ~ genere + cluster_mother_tat + cluster_father_tat,
      zi ~ genere + cluster_mother_tat + cluster_father_tat),
      data = data_cluster_tat,
      family = brms::zero_inflated_poisson())
```

# References {-}

### 2021-06-29 Documents/Report-Project/Report-analysis.Rmd
init repo

--- 2021-06-29 Documents/Report-Project/Attachment_Analysis_Report.Rmd
@@
 
-# Descriptive Statistics
-
-## Dependent Variable
-
-### Externalizing
-```{r}
-ggplot(data_munged) +
-  geom_bar(aes(x = externalizing_sum, fill = genere), alpha = 0.7) +
-  facet_grid(genere ~ .)
-```
-
-### Internalizing
-```{r}
-ggplot(data_munged) +
-  geom_bar(aes(x = internalizing_sum, fill = genere), alpha = 0.7) +
-  facet_grid(genere ~ .)
-```
-
-# Cluster Analysis
-
-## Mother
-
-```{r}
-plot(cluster_mother_tat, main = "Dendrogramma")
-rect.hclust(cluster_mother_tat, k=4, border="red")
-```
-
-Frequencies
-
-```{r, echo = TRUE}
-table(data_cluster_tat$cluster_mother_tat)
-
-prop.table(table(data_cluster_tat$cluster_mother_tat))
-
-prop.table(table(data_cluster_tat$cluster_mother_tat,
-                 data_cluster_tat$genere),2)
-
-summary(table(data_cluster_tat$cluster_mother_tat,
-              data_cluster_tat$genere))
-```
-
-Plot Scores
-
-```{r}
-plot_scores_mother(data = data_cluster_tat)
-```
-
-#### Mclust check
-
-```{r}
-plot(mclust_mother)
-summary(mclust_mother)
-```
-
-## Father
-
-```{r}
-plot(cluster_father_tat, main = "Dendrogramma")
-rect.hclust(cluster_father_tat, k=4, border="red")
-```
-
-Frequencies
-
-```{r, echo = TRUE}
-table(data_cluster_tat$cluster_father_tat)
-
-prop.table(table(data_cluster_tat$cluster_father_tat))
-
-prop.table(table(data_cluster_tat$cluster_father_tat,
-                 data_cluster_tat$genere),2)
-
-summary(table(data_cluster_tat$cluster_father_tat,
-              data_cluster_tat$genere))
-```
-
-Plot Scores
-
-```{r}
-plot_scores_father(data = data_cluster_tat)
-```
-
-#### Mclust check
-
-```{r}
-plot(mclust_father)
-summary(mclust_father)
-```
-
-# Statistical Approach
-
-In this section we describe the statistical approach.
+In this Reeport we describe the statistical approach.
 First we define the statistical model used to describe the data generative process.
@@
 
-## Model Definition
+# Model Definition
 
-### Psychologial Background
+## Psychologial Background
 
@@
 
-### Zero Inflated Poisson (ZIP) {#model}
+## Zero Inflated Poisson (ZIP) {#model}
 
@@
 
-## Test of Hypotheses with Inequality and Equality Constraints
+# Test of Hypotheses with Inequality and Equality Constraints
 
@@
 
-### Inequality Constraints: A First Approach
+## Inequality Constraints: A First Approach
 
@@
 
-### Inequality and Equality Constraints: A Second Approach {#in-eq-const}
+## Inequality and Equality Constraints: A Second Approach {#in-eq-const}
 
@@
 
-#### @mulderBayesFactorTesting2019 {#mulder}
+### @mulderBayesFactorTesting2019 {#mulder}
 
@@
 
-#### @guApproximatedAdjustedFractional2018
+### @guApproximatedAdjustedFractional2018
 
@@
 
-### Present Study
+## Present Study
 
@@
 
-### Issues
+## Issues
 
@@
 
-## Estimating the Constrained Model
+# Estimating the Constrained Model
 
@@
 
-### STAN Approach
+## STAN Approach
 
@@
 
-#### Issues
+### Issues
 
@@
 
-### Gibbs Sampler Approach
+## Gibbs Sampler Approach
 
-@rodriguez-yamEfficientGibbsSampling implemented a Gibbs sampler for a ZIP model, whereas @ katoBayesianApproachInequality2006 presented a Gibbs sampler to estimate a model with inequality constraints using truncated normal distributions.
+@rodrigues-mottaZeroInflatedPoissonModel2007 implemented a Gibbs sampler for a ZIP model, whereas @ katoBayesianApproachInequality2006 presented a Gibbs sampler to estimate a model with inequality constraints using truncated normal distributions.
 We would like to put together the two methods in order to estimate a ZIP model with inequality constraints on the parameters.
@@
 
-#### Conditional Posterior Distributions
+### Conditional Posterior Distributions
 
@@
 
-#### Conditional Posteriors
+#### Conditional Posteriors {-}
 
@@
 
-Nel lavoro di @rodriguez-yamEfficientGibbsSampling, inoltre, fanno una cosa strana nel senso che definiscono $\lambda = X\beta+\epsilon$ e oltre a mettere le prior sui parametri $\beta$ la mettono anche su $\lambda$.
+Nel lavoro di @rodrigues-mottaZeroInflatedPoissonModel2007, inoltre, fanno una cosa strana nel senso che definiscono $\lambda = X\beta+\epsilon$ e oltre a mettere le prior sui parametri $\beta$ la mettono anche su $\lambda$.
 Non capisco:
@@
 
-#### Including Inequality Constraints
+### Including Inequality Constraints
 
@@
 
-### Issue
+## Issue
 
@@
 
-## brms
-
-```{r}
-summary(fit_int)
-```
-
-```{r}
-brms::conditional_effects(fit_int, ask= FALSE)
-```
-
-### Prior
-
-```{r, echo = TRUE}
-brms::get_prior(brms::bf(
-      internalizing_sum ~ genere + cluster_mother_tat + cluster_father_tat,
-      zi ~ genere + cluster_mother_tat + cluster_father_tat),
-      data = data_cluster_tat,
-      family = brms::zero_inflated_poisson())
-```
-
-# References {-}
+# References

### 2021-06-29 Documents/analisi_d1.Rmd
init repo

---
title: "Analisi dei Cluster - Zandonella Callegher et al"
author: ''
date: "Maggio 2021"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  html_notebook:
    number_sections: no
    toc: yes
    toc_depth: 3
    toc_float: yes
  html_document:
    number_sections: no
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

```{r,warning=FALSE}

rm(list=ls())
options(digits = 3)
```

Librerie 
```{r,warning=FALSE,include=TRUE}
library(car)
library(semPlot)
library(foreign)
library(lavaan)
library(psych)
library(effects)
library(sciplot)
library(psych)
```

```{r,include=FALSE}
# effect size
etas=function(m.lm){
  library(car)
  ris=NULL
  anovam=Anova(m.lm,type="III")
  l.SS=length(anovam$"Sum Sq")
  SStotal=sum(anovam$"Sum Sq"[2:l.SS])
  eta.q=(anovam$"Sum Sq"[2:(l.SS-1)])/SStotal
  peta.q=(anovam$"Sum Sq"[2:(l.SS-1)]) / ( (anovam$"Sum Sq"[2:(l.SS-1)]) + (anovam$"Sum Sq"[l.SS]))
  ris=data.frame(eta.q,peta.q)
  row.names(ris)=row.names(anovam)[2:(l.SS-1)]
  return(ris)
}
```

```{r,warning=FALSE,include=TRUE}
#######################################################################################
#                                                          #
setwd("~/Documents/Mega/Paper/In preparation/Zandonella et al/Analisi_data_d1")

load("/Users/tatiana/Documents/Mega/Paper/In preparation/Zandonella et al/Analisi_data_d1/ddef_datiECR.rda")

```

```{r}
ddef=ddef_datiECR[ddef_datiECR$age_year<12.30,]
ddef<- subset(ddef, ddef$fas !="NA")
nrow(ddef) #847
save(ddef,file=paste('ddef.rda',sep=""))
```

```{r,warning=FALSE}
load("/Users/tatiana/Documents/Mega/Paper/In preparation/Zandonella et al/Analisi_data_d1/ddef.rda")
```

```{r,warning=FALSE}
#######################################################################################
######################### DISTRIBUZIONE SDQ TOTALE
#

#quantile(ddef$ebdtot_somma, prob = c(0.00, 0.30, 0.40, 0.70, 1), na.rm=TRUE)

#cut-off: 
#0-13 normale 
#borderline 14-16 
#problematico 17-40
ddef$SDQgroup <-ifelse(ddef$sdqtot_sum < 14, "1",
                       ifelse((ddef$sdqtot_sum >= 14) & (ddef$sdqtot_sum<=16),"2","3"))

prop.table(table(ddef$SDQgroup))

# pochi problemi!
```

```{r}
#se dovesse servire lavorare su dati primaria
primaria<-ddef[ddef$ordine_scolastico=="PRIMARIA",]
save(primaria,file=paste('primaria.rda',sep=""))
```

#Cluster mamma
```{r,warning=FALSE}
#######################################################################################
#1. ######################## CLUSTER
# 
dcM <- dist(ddef[,c(60:71)], method = "euclidean") # distance matrix
fit <- hclust(dcM, method="ward.D")
plot(fit, main = "Dendrogramma")
# dal dendrogramma sembrano emergere 4 cluster 
rect.hclust(fit, k=4, border="red")
ddef$gruppiattM <- as.factor(cutree(fit, k=4))

save(ddef,file=paste('ddef.rda',sep=""))

#######################################################
table(ddef$gruppiattM)
prop.table(table(ddef$gruppiattM))
prop.table(table(ddef$gruppiattM,ddef$genere),2) 
summary(table(ddef$gruppiattM,ddef$genere))
summary(table(ddef$gruppiattM,ddef$fas))

```

### Profilo grafico cluster
```{r}
fattore=rep(c("Ansia","Evitamento"),rep(dim(ddef)[1],2))
y=c(scale(ddef$Anxm),scale(ddef$Avm))
y1=c(ddef$Anxm,ddef$Avm)
gruppo=rep(ddef$gruppiattM,2)
dprof=data.frame(y,y1,fattore,gruppo)

dprof$nomi.gruppi=factor(dprof$gruppo,labels=c("Gruppo1: Sicuri (n = 231)","Gruppo 2: Ansiosi (n = 286)","Gruppo 3: Ansiosi-Evitanti (n = 100)","Gruppo 4: Evitanti (n = 230)"))

```

```{r}
par(mar=c(6, 5, 4, 2) + 0.1)

bargraph.CI(fattore, y, group = nomi.gruppi, data=dprof,legend=T,ylim=c(-2.4,1.6),x.leg=1.2, y.leg=-1.2,ylab="Punteggi standardizzati",xlab="",cex.lab=.8,cex.leg=.8, col=c("yellow","green","blue","red"))

save(ddef,file=paste('ddef.rda',sep=""))
```

### Valori medi per i 4 gruppi
```{r,warning=FALSE}
tapply(ddef$Anxm,ddef$gruppiattM,mean)
tapply(ddef$Avm,ddef$gruppiattM,mean)

tapply(ddef$Anxm,ddef$gruppiattM,sd)
tapply(ddef$Avm,ddef$gruppiattM,sd)
```

### Inferenza sui 4 gruppi rispetto a attaccamento mamma
```{r,warning=FALSE}
# mamma ansia
mod.anx=lm(Anxm~gruppiattM,ddef)
summary(mod.anx)
Anova(mod.anx) 
etas(mod.anx)

# mamma evitamento
mod.av=lm(Avm~gruppiattM,ddef)
summary(mod.av)
Anova(mod.av) 
etas(mod.av)

```

### Prove su internalizing and externalizing

```{r}
m1.1<-lm(externalizing~gruppiattM,ddef)
Anova(m1.1)
summary(m1.1)

g1<- effect("gruppiattM ", m1.1)
plot(g1,ylab="problemi", xlab="gruppi attaccamento mamma",main="",ci.stile="band",band.colors="red")

# R-squared basso. A livello descrittivo risultati interessanti e corrispondenti alle attese. Gruppo 3 (alta ansia, alto evitamento) maggiormente problematico

m1.2<-lm(externalizing~gruppiattM*genere+fas,ddef)
summary(m1.2)
Anova(m1.2)

g1.2<- effect("gruppiattM:genere ", m1.2)
plot(g1.2,ylab="problemi", xlab="gruppi attaccamento mamma",main="",ci.stile="band",band.colors="red")

#no interazione con genere 
```

```{r}
m2.1<-lm(internalizing~gruppiattM,ddef)
summary(m2.1)
Anova(m2.1)

g2.1<- effect("gruppiattM ", m2.1)
plot(g2.1,ylab="problemi", xlab="gruppi attaccamento mamma",main="",ci.stile="band",band.colors="red")

# R-squared basso. A livello descrittivo risultati interessanti e corrispondenti alle attese. Gruppo 3 (alta ansia, alto evitamento) maggiormente problematico

m2.2<-lm(internalizing~gruppiattM*genere,ddef)
summary(m2.2)
Anova(m2.2)

g2.2<- effect("gruppiattM:genere ", m2.2)
plot(g2.2,ylab="problemi", xlab="gruppi attaccamento mamma",main="",ci.stile="band",band.colors="red")

# no effetto genere ma a livello descrittivo risultati interessanti. vedere in particolare gruppo 3 femmine

```

#Cluster papà
```{r,warning=FALSE}
#######################################################################################
#1. ######################## CLUSTER
# 
dcP <- dist(ddef[,c(99:110)], method = "euclidean") # distance matrix
fit <- hclust(dcP, method="ward.D")
plot(fit, main = "Dendrogramma")
# dal dendrogramma sembrano emergere 4 cluster 
rect.hclust(fit, k=4, border="red")
ddef$gruppiattP <- as.factor(cutree(fit, k=4))

save(ddef,file=paste('ddef.rda',sep=""))

table(ddef$gruppiattP)
prop.table(table(ddef$gruppiattP))
prop.table(table(ddef$gruppiattP,ddef$genere),2) 
summary(table(ddef$gruppiattP,ddef$genere))
summary(table(ddef$gruppiattP,ddef$fas))

```

### Profilo grafico cluster
```{r}
fattore=rep(c("Ansia","Evitamento"),rep(dim(ddef)[1],2))
y=c(scale(ddef$Anxp),scale(ddef$Avp))
y1=c(ddef$Anxp,ddef$Avp)
gruppo=rep(ddef$gruppiattP,2)
dprof=data.frame(y,y1,fattore,gruppo)
```

### Valori medi per i 4 gruppi
```{r,warning=FALSE}
tapply(ddef$Anxp,ddef$gruppiattP,mean)
tapply(ddef$Avp,ddef$gruppiattP,mean)

tapply(ddef$Anxp,ddef$gruppiattP,sd)
tapply(ddef$Avp,ddef$gruppiattP,sd)
```

### Inferenza sui 4 gruppi rispetto a attaccamento papà
```{r,warning=FALSE}
# papà ansia
mod.anx=lm(Anxp~gruppiattP,ddef)
summary(mod.anx)
Anova(mod.anx) # 
etas(mod.anx)

# papà evitamento
mod.av=lm(Avp~gruppiattP,ddef)
summary(mod.av)
Anova(mod.av) 
etas(mod.av)

```

```{r,warning=FALSE}

dprof$nomi.gruppi=factor(dprof$gruppo,labels=c("Gruppo1: Sicuri (n = 206)","Gruppo 2: Ansiosi (n = 230)","Gruppo 3: Evitanti (n = 311 )","Gruppo 4: Ansiosi-Evitanti (n = 100)"))

par(mar=c(6, 5, 4, 2) + 0.1)

bargraph.CI(fattore, y, group = nomi.gruppi, data=dprof,legend=T,ylim=c(-2.4,1.6),x.leg=1.2, y.leg=-1.2,ylab="Punteggi standardizzati",xlab="",cex.lab=.8,cex.leg=.8, col=c("yellow","green","blue","red"))

#N.B: nel gruppo 2 anche se nominati ansiosi i livelli sono comunque bassi              
box()

save(ddef,file=paste('ddef.rda',sep=""))
```

###Prove su internalizing e externalizing
```{r}
m3.1<-lm(externalizing~gruppiattP,ddef)
Anova(m3.1)
summary(m3.1)

g3.1<- effect("gruppiattP ", m3.1)
plot(g3.1,ylab="problemi esternalizzanti", xlab="gruppi attaccamento papà",main="",ci.stile="band",band.colors="red")

# R-squared bassissimo. A livello descrittivo  Gruppo 4 (alta ansia, alto evitamento) maggiormente problematico (come gruppo 3 mamma corrispondente a alta ansia alto evitamento)

m3.2<-lm(externalizing~gruppiattP*genere+fas,ddef)
summary(m3.2)
Anova(m3.2)

g3.2<- effect("gruppiattP:genere ", m3.2)
plot(g3.2,ylab="problemi esternalizzanti", xlab="gruppi attaccamento papà",main="",ci.stile="band",band.colors="red")

#no interazione con genere. In generale maschi più problemi esternalizzanti (risultati coerenti con la letteratura) 
```

```{r}
m4.1<-lm(internalizing~gruppiattP,ddef)
summary(m4.1)
Anova(m4.1)

g4.1<- effect("gruppiattP ", m4.1)
plot(g4.1,ylab="problemi", xlab="gruppi attaccamento papà",main="",ci.stile="band",band.colors="red")

# R-squared bassissimo. A livello descrittivo risultati interessanti e corrispondenti alle attese. Gruppo 4 (alta ansia, alto evitamento) maggiormente problematico

m4.2<-lm(internalizing~gruppiattP*genere,ddef)
summary(m4.2)
Anova(m4.2)

g4.2<- effect("gruppiattP:genere ", m4.2)
plot(g4.2,ylab="problemi", xlab="gruppi attaccamento papà",main="",ci.stile="band",band.colors="red")

# no effetto genere ma a livello descrittivo risultati interessanti.

```

Note label gruppi:

Gruoo1 mamma = Gruppo 1 papà = sicuri

Gruoo2 mamma = Gruppo 2 papà = ansiosi

Gruoo3 mamma = Gruppo 4 papà = ansiosi-evitanti

Gruoo4 mamma = Gruppo 3 papà = evitanti

### 2021-06-29 Analysis/Analysis_Drake.R

@@ -1,0 +1,84 @@
+########################
+####    Analysis    ####
+########################
+
+#----    load env    ----
+env <- devtools::load_all()$env
+
+#----    Plan   -----
+
+# load plan
+plan <- get_analysis_plan()
+
+# Configure the analysis plan
+config <- drake::drake_config(plan,
+                              prework = "devtools::load_all()",
+                              envir = env)
+
+# Plot the analysis plan
+drake::vis_drake_graph(config, font_size = 16, targets_only = FALSE)
+
+#----    Make    ----
+
+# Delate the analysis results
+# drake::clean(destroy = TRUE)
+
+# Run the analysis
+drake::make(prework = "devtools::load_all()",
+            envir = env,
+            plan = plan)
+
+# Plot the analysis plan
+drake::vis_drake_graph(config, font_size = 16, targets_only = FALSE)
+
+#----    load    ----
+
+# data
+drake::loadd(data_munged)
+
+#---- cluster ----
+
+# cluster tat
+drake::loadd(cluster_mother_tat)
+drake::loadd(cluster_father_tat)
+
+plot(cluster_mother_tat, main = "Dendrogramma")
+rect.hclust(cluster_mother_tat, k=4, border="red")
+plot(cluster_father_tat, main = "Dendrogramma")
+rect.hclust(cluster_father_tat, k=4, border="red")
+
+drake::loadd(data_cluster_tat)
+table(data_cluster_tat$cluster_mother_tat)
+table(data_cluster_tat$cluster_father_tat)
+
+plot_scores_mother(data = data_cluster_tat)
+plot_scores_father(data = data_cluster_tat)
+
+# mclust
+drake::loadd(mclust_mother)
+drake::loadd(mclust_father)
+
+plot(mclust_mother)
+summary(mclust_mother)
+
+plot(mclust_father)
+summary(mclust_father)
+
+#---- brms models ----
+
+drake::loadd(fit_int)
+
+summary(fit_int)
+plot(brms::conditional_effects(fit_int), ask = FALSE)
+
+plot(fit_int)
+
+drake::loadd(stan_data)
+
+str(fit_int$fit)
+#-----
+
+
+
+
+#----

### 2021-06-29 Analysis/draft.R

@@ -1,0 +1,115 @@
+load("Data/ddef_datiECR.rda")
+ddef=ddef_datiECR[ddef_datiECR$age_year<12.30,]
+ddef<- subset(ddef, ddef$fas !="NA")
+nrow(ddef) #847
+
+#---- cluster madre ----
+
+dcM <- dist(ddef[,c(60:71)], method = "euclidean") # distance matrix
+fit <- hclust(dcM, method="ward.D")
+plot(fit, main = "Dendrogramma")
+# dal dendrogramma sembrano emergere 4 cluster
+rect.hclust(fit, k=4, border="red")
+ddef$gruppiattM <- as.factor(cutree(fit, k=4))
+table(ddef$gruppiattM)
+
+
+# profilo
+fattore=rep(c("Ansia","Evitamento"),rep(dim(ddef)[1],2))
+y=c(scale(ddef$Anxm),scale(ddef$Avm))
+y1=c(ddef$Anxm,ddef$Avm)
+gruppo=rep(ddef$gruppiattM,2)
+dprof=data.frame(y,y1,fattore,gruppo)
+
+
+dprof$nomi.gruppi=factor(dprof$gruppo,labels=c("Gruppo1: Sicuri (n = 231)","Gruppo 2: Ansiosi (n = 286)","Gruppo 3: Ansiosi-Evitanti (n = 100)","Gruppo 4: Evitanti (n = 230)"))
+par(mar=c(6, 5, 4, 2) + 0.1)
+
+sciplot::bargraph.CI(fattore, y, group = nomi.gruppi, data=dprof,legend=T,ylim=c(-2.4,1.6),x.leg=1.2, y.leg=-1.2,ylab="Punteggi standardizzati",xlab="",cex.lab=.8,cex.leg=.8, col=c("yellow","green","blue","red"))
+
+
+#---- cluster padre ----
+
+dcP <- dist(ddef[,c(99:110)], method = "euclidean") # distance matrix
+fit <- hclust(dcP, method="ward.D")
+plot(fit, main = "Dendrogramma")
+# dal dendrogramma sembrano emergere 4 cluster
+rect.hclust(fit, k=4, border="red")
+ddef$gruppiattP <- as.factor(cutree(fit, k=4))
+
+# Profilo
+fattore=rep(c("Ansia","Evitamento"),rep(dim(ddef)[1],2))
+y=c(scale(ddef$Anxp),scale(ddef$Avp))
+y1=c(ddef$Anxp,ddef$Avp)
[…]

### 2021-06-29 R/Clusters.R

@@ -1,0 +1,76 @@
+#================================#
+#====    Cluster Analysis    ====#
+#================================#
+
+#-----    cluster_tatiana    ----
+
+cluster_tatiana <- function(data, parent = c("mother", "father")){
+  parent <- match.arg(parent)
+
+  if(parent == "mother"){
+    cols_num <- 60:71
+  } else {
+    cols_num <- 99:110
+  }
+  dist_matrix <- dist(data[,cols_num], method = "euclidean")
+  fit_cluster <- hclust(dist_matrix, method="ward.D")
+
+  return(fit_cluster)
+}
+
+#----    get_cluster_var    ----
+
+get_cluster_var <- function(fit_cluster){
+  as.factor(cutree(fit_cluster, k=4))
+}
+
+#-----   plot_scores    ----
+
+plot_scores_mother <- function(data){
+  fattore=rep(c("Ansia","Evitamento"),rep(dim(data)[1],2))
+  y=c(scale(data$Anxm),scale(data$Avm))
+  y1=c(data$Anxm,data$Avm)
+  gruppo=rep(data$cluster_mother_tat,2)
+  dprof=data.frame(y,y1,fattore,gruppo)
+
+
+  dprof$nomi.gruppi=factor(dprof$gruppo,labels=c("Gruppo1: Sicuri (n = 231)","Gruppo 2: Ansiosi (n = 286)","Gruppo 3: Ansiosi-Evitanti (n = 100)","Gruppo 4: Evitanti (n = 230)"))
+  sciplot::bargraph.CI(fattore, y, group = nomi.gruppi, data=dprof,legend=T,ylim=c(-2.4,1.6),x.leg=1.2, y.leg=-1.2,ylab="Punteggi standardizzati",xlab="",cex.lab=.8,cex.leg=.8, col=c("yellow","green","blue","red"))
+}
+
+plot_scores_father <- function(data){
+  fattore=rep(c("Ansia","Evitamento"),rep(dim(data)[1],2))
+  y=c(scale(data$Anxp),scale(data$Avp))
+  y1=c(data$Anxp,data$Avp)
+  gruppo=rep(data$cluster_father_tat,2)
+  dprof=data.frame(y,y1,fattore,gruppo)
+
[…]

### 2021-06-29 R/Models.R

@@ -1,0 +1,40 @@
+#================================#
+#====    Model Definition    ====#
+#================================#
+
+#-----    zip_brms    ----
+
+zip_brms <- function(data){
+
+  fit <- brms::brm(brms::bf(
+      internalizing_sum ~ genere + cluster_mother_tat + cluster_father_tat,
+      zi ~ genere + cluster_mother_tat + cluster_father_tat),
+    data = data, family = brms::zero_inflated_poisson())
+
+  return(fit)
+}
+
+#----    make_stan_data    ----
+
+make_stan_data <- function(data = data_cluster_tat){
+  formula <-  brms::bf(
+    internalizing_sum ~ genere + cluster_mother_tat + cluster_father_tat,
+    zi ~ genere + cluster_mother_tat + cluster_father_tat)
+
+  formula <- brms:::validate_formula(formula, data = data, family = brms::zero_inflated_poisson(),
+                                     autocor = NULL, sparse = NULL, cov_ranef = NULL)
+
+  bterms <- brms:::brmsterms(formula)
+
+
+  data_name <- brms:::substitute_name(data)
+  data <- brms:::validate_data(data, bterms = bterms, data2 = NULL, knots = NULL)
+  attr(data, "data_name") <- data_name
+
+  sdata <- brms:::.make_standata(bterms, data = data, prior = NULL,
+                          data2 = NULL, stanvars = NULL, threads = NULL)
+
+  return(sdata)
+}
+
+#-----

### 2021-06-29 R/Munge_data.R

@@ -1,0 +1,22 @@
+#============================#
+#====    Data Munging    ====#
+#============================#
+
+#-----    munge_data    ----
+
+munge_data <- function(data){
+  data <- data[data$age_year<12.30,]
+  data <- subset(data, data$fas !="NA")
+
+  data <- data %>%
+    mutate_at(c("externalizing_sum", "internalizing_sum"), round, 0)
+
+  return(data)
+}
+
+
+#-----
+
+
+
+

### 2021-06-29 R/Plan.R

@@ -1,0 +1,43 @@
+#############################
+####    Analysis Plan    ####
+#############################
+
+
+#----    get_analysis_plan    ----
+
+#' @title Plan of the Analysis
+#'
+#' @description Plan of the Analysis
+#'
+#' @return a \code{drake_plan} object of class \code{tbl_df} with the plan of
+#'   the analysis
+#'
+
+get_analysis_plan <- function(){
+  drake::drake_plan(
+
+    #----    Munge Data    ----
+    raw_data = readRDS("Data/data_ECR.rds"),
+    data_munged = munge_data(data = raw_data),
+
+
+    #----    Cluster Analysis    ----
+    cluster_mother_tat = cluster_tatiana(data = data_munged, parent = "mother"),
+    cluster_father_tat = cluster_tatiana(data = data_munged, parent = "father"),
+
+    data_cluster_tat = cbind(data_munged,
+                             cluster_mother_tat = get_cluster_var(cluster_mother_tat),
+                             cluster_father_tat = get_cluster_var(cluster_father_tat)),
+
+    # mclust check
+    mclust_mother = mclust_BIC(data = data_cluster_tat, parent = "mother"),
+    mclust_father = mclust_BIC(data = data_cluster_tat, parent = "father"),
+
+
+    #----    brms Models    ----
+    fit_int = zip_brms(data_cluster_tat),
+    stan_data = make_stan_data(data = data_cluster_tat)
+  )
+}
+
+#----

### 2021-06-29 Documents/Report-Project/Attachment_Analysis_Report.Rmd
revision analysis cluster

@@
 # Cluster
-drake::loadd(cluster_mother_tat)
-drake::loadd(cluster_father_tat)
-drake::loadd(data_cluster_tat)
+drake::loadd(cluster_mother_fit)
+drake::loadd(cluster_father_fit)
+drake::loadd(data_cluster)
 drake::loadd(mclust_mother)
@@
 ggplot(data_munged) +
-  geom_bar(aes(x = externalizing_sum, fill = genere), alpha = 0.7) +
-  facet_grid(genere ~ .)
+  geom_bar(aes(x = externalizing_sum, fill = gender), alpha = 0.7) +
+  facet_grid(gender ~ .)
 ```
@@
 ggplot(data_munged) +
-  geom_bar(aes(x = internalizing_sum, fill = genere), alpha = 0.7) +
-  facet_grid(genere ~ .)
+  geom_bar(aes(x = internalizing_sum, fill = gender), alpha = 0.7) +
+  facet_grid(gender ~ .)
 ```
@@
 ```{r}
-plot(cluster_mother_tat, main = "Dendrogramma")
-rect.hclust(cluster_mother_tat, k=4, border="red")
+plot(cluster_mother_fit, main = "Dendrogramma")
+rect.hclust(cluster_mother_fit, k=4, border="red")
 ```
@@
 ```{r, echo = TRUE}
-table(data_cluster_tat$cluster_mother_tat)
+table(data_cluster$cluster_mother)
 
-prop.table(table(data_cluster_tat$cluster_mother_tat))
+prop.table(table(data_cluster$cluster_mother))
 
-prop.table(table(data_cluster_tat$cluster_mother_tat,
-                 data_cluster_tat$genere),2)
+prop.table(table(data_cluster$cluster_mother,
+                 data_cluster$gender),2)
 
-summary(table(data_cluster_tat$cluster_mother_tat,
-              data_cluster_tat$genere))
+summary(table(data_cluster$cluster_mother,
+              data_cluster$gender))
 ```
@@
 ```{r}
-plot_scores_mother(data = data_cluster_tat)
+plot_scores_mother(data = data_cluster)
 ```
@@
 ```{r}
-plot(cluster_father_tat, main = "Dendrogramma")
-rect.hclust(cluster_father_tat, k=4, border="red")
+plot(cluster_father_fit, main = "Dendrogramma")
+rect.hclust(cluster_father_fit, k=4, border="red")
 ```
@@
 ```{r, echo = TRUE}
-table(data_cluster_tat$cluster_father_tat)
+table(data_cluster$cluster_father)
 
-prop.table(table(data_cluster_tat$cluster_father_tat))
+prop.table(table(data_cluster$cluster_father))
 
-prop.table(table(data_cluster_tat$cluster_father_tat,
-                 data_cluster_tat$genere),2)
+prop.table(table(data_cluster$cluster_father,
+                 data_cluster$gender),2)
 
-summary(table(data_cluster_tat$cluster_father_tat,
-              data_cluster_tat$genere))
+summary(table(data_cluster$cluster_father,
+              data_cluster$gender))
 ```
@@
 ```{r}
-plot_scores_father(data = data_cluster_tat)
+plot_scores_father(data = data_cluster)
 ```
@@
 brms::get_prior(brms::bf(
-      internalizing_sum ~ genere + cluster_mother_tat + cluster_father_tat,
-      zi ~ genere + cluster_mother_tat + cluster_father_tat),
-      data = data_cluster_tat,
+      internalizing_sum ~ gender + cluster_mother + cluster_father,
+      zi ~ gender + cluster_mother + cluster_father),
+      data = data_cluster,
       family = brms::zero_inflated_poisson())

### 2021-06-29 Analysis/Analysis_Drake.R

@@ -39,20 +39,20 @@ drake::loadd(data_munged)
 #---- cluster ----
 
 # cluster tat
-drake::loadd(cluster_mother_tat)
-drake::loadd(cluster_father_tat)
+drake::loadd(cluster_mother_fit)
+drake::loadd(cluster_father_fit)
 
-plot(cluster_mother_tat, main = "Dendrogramma")
-rect.hclust(cluster_mother_tat, k=4, border="red")
-plot(cluster_father_tat, main = "Dendrogramma")
-rect.hclust(cluster_father_tat, k=4, border="red")
+plot(cluster_mother_fit, main = "Dendrogramma")
+rect.hclust(cluster_mother_fit, k=4, border="red")
+plot(cluster_father_fit, main = "Dendrogramma")
+rect.hclust(cluster_father_fit, k=4, border="red")
 
-drake::loadd(data_cluster_tat)
-table(data_cluster_tat$cluster_mother_tat)
-table(data_cluster_tat$cluster_father_tat)
+drake::loadd(data_cluster)
+table(data_cluster$cluster_mother)
+table(data_cluster$cluster_father)
 
-plot_scores_mother(data = data_cluster_tat)
-plot_scores_father(data = data_cluster_tat)
+plot_scores_mother(data = data_cluster)
+plot_scores_father(data = data_cluster)
 
 # mclust
 drake::loadd(mclust_mother)
@@ -66,16 +66,16 @@ summary(mclust_father)
 
 #---- brms models ----
 
-drake::loadd(fit_int)
+drake::loadd(fit_int_additive)
 
-summary(fit_int)
-plot(brms::conditional_effects(fit_int), ask = FALSE)
+summary(fit_int_additive)
+plot(brms::conditional_effects(fit_int_additive), ask = FALSE)
 
-plot(fit_int)
+plot(fit_int_additive)
 
 drake::loadd(stan_data)
 
-str(fit_int$fit)
+str(fit_int_additive$fit)
 #-----
 
 

### 2021-06-29 R/Clusters.R

@@ -2,15 +2,15 @@
 #====    Cluster Analysis    ====#
 #================================#
 
-#-----    cluster_tatiana    ----
+#-----    get_cluster_fit    ----
 
-cluster_tatiana <- function(data, parent = c("mother", "father")){
+get_cluster_fit <- function(data, parent = c("mother", "father")){
   parent <- match.arg(parent)
 
   if(parent == "mother"){
-    cols_num <- 60:71
+    cols_num <- grepl("o_ecr[[:digit:]]+m", names(data))  # select type o_ecr..m
   } else {
-    cols_num <- 99:110
+    cols_num <- grepl("o_ecr[[:digit:]]+p", names(data))  # select type o_ecr..p
   }
   dist_matrix <- dist(data[,cols_num], method = "euclidean")
   fit_cluster <- hclust(dist_matrix, method="ward.D")
@@ -18,10 +18,32 @@ cluster_tatiana <- function(data, parent = c("mother", "father")){
   return(fit_cluster)
 }
 
-#----    get_cluster_var    ----
+#----    get_data_cluster    ----
 
-get_cluster_var <- function(fit_cluster){
-  as.factor(cutree(fit_cluster, k=4))
+get_data_cluster <- function(data, cluster_mother_fit, cluster_father_fit){
+
+  # Get cluster levels
+  cluster_mother_lev <- as.factor(cutree(cluster_mother_fit, k=4))
+  cluster_father_lev <- as.factor(cutree(cluster_father_fit, k=4))
+
+  data_cluster <- cbind(data,
+                        cluster_mother = cluster_mother_lev,
+                        cluster_father = cluster_father_lev) %>%
+    mutate(cluster_mother = fct_recode(cluster_mother,
+                                       secure = "1",
+                                       anxious = "2",
+                                       anxious_avoidant = "3",
+                                       avoidant = "4"),
+           cluster_mother = fct_relevel(cluster_mother,
+                                        c("secure", "anxious", "avoidant", "anxious_avoidant")),
+           cluster_father = fct_recode(cluster_father,
[…]

### 2021-06-29 R/Models.R

@@ -4,11 +4,13 @@
 
 #-----    zip_brms    ----
 
-zip_brms <- function(data){
+zip_brms <- function(data, y, formula){
 
-  fit <- brms::brm(brms::bf(
-      internalizing_sum ~ genere + cluster_mother_tat + cluster_father_tat,
-      zi ~ genere + cluster_mother_tat + cluster_father_tat),
+  formula_lambda <- paste0("internalizing_sum ~ ", formula)
+  formula_zi <- paste0("zi ~ ", formula)
+
+  fit <- brms::brm(brms::bf(as.formula(formula_lambda),
+                            as.formula(formula_zi)),
     data = data, family = brms::zero_inflated_poisson())
 
   return(fit)
@@ -16,10 +18,10 @@ zip_brms <- function(data){
 
 #----    make_stan_data    ----
 
-make_stan_data <- function(data = data_cluster_tat){
+make_stan_data <- function(data){
   formula <-  brms::bf(
-    internalizing_sum ~ genere + cluster_mother_tat + cluster_father_tat,
-    zi ~ genere + cluster_mother_tat + cluster_father_tat)
+    internalizing_sum ~ gender + cluster_mother + cluster_father,
+    zi ~ gender + cluster_mother + cluster_father)
 
   formula <- brms:::validate_formula(formula, data = data, family = brms::zero_inflated_poisson(),
                                      autocor = NULL, sparse = NULL, cov_ranef = NULL)

### 2021-06-29 R/Munge_data.R

@@ -5,11 +5,16 @@
 #-----    munge_data    ----
 
 munge_data <- function(data){
-  data <- data[data$age_year<12.30,]
-  data <- subset(data, data$fas !="NA")
+
+  # TODO ask Tatiana
+  # data <- data[data$age_year<12.30,]
+  # data <- subset(data, data$fas !="NA")
 
   data <- data %>%
-    mutate_at(c("externalizing_sum", "internalizing_sum"), round, 0)
+    rename("gender" = "genere") %>%
+    mutate_at(c("externalizing_sum", "internalizing_sum"), round, 0) %>%
+    select(c("ID","externalizing_sum", "internalizing_sum", "gender",
+             starts_with(c("o_ecr", "Av", "Anx"))))
 
   return(data)
 }

### 2021-06-29 R/Plan.R

@@ -22,21 +22,30 @@ get_analysis_plan <- function(){
 
 
     #----    Cluster Analysis    ----
-    cluster_mother_tat = cluster_tatiana(data = data_munged, parent = "mother"),
-    cluster_father_tat = cluster_tatiana(data = data_munged, parent = "father"),
+    # Get cluster fit
+    cluster_mother_fit = get_cluster_fit(data = data_munged, parent = "mother"),
+    cluster_father_fit = get_cluster_fit(data = data_munged, parent = "father"),
 
-    data_cluster_tat = cbind(data_munged,
-                             cluster_mother_tat = get_cluster_var(cluster_mother_tat),
-                             cluster_father_tat = get_cluster_var(cluster_father_tat)),
+    # Get cluster data
+    data_cluster = get_data_cluster(data = data_munged,
+                                    cluster_mother_fit = cluster_mother_fit,
+                                    cluster_father_fit = cluster_father_fit),
 
     # mclust check
-    mclust_mother = mclust_BIC(data = data_cluster_tat, parent = "mother"),
-    mclust_father = mclust_BIC(data = data_cluster_tat, parent = "father"),
+    mclust_mother = mclust_BIC(data = data_munged,
+                               class = data_cluster$cluster_mother,
+                               parent = "mother"),
+    mclust_father = mclust_BIC(data = data_munged,
+                               class = data_cluster$cluster_father,
+                               parent = "father"),
 
+    #----    ZIP analysis    ----
 
     #----    brms Models    ----
-    fit_int = zip_brms(data_cluster_tat),
-    stan_data = make_stan_data(data = data_cluster_tat)
+    fit_int_additive = zip_brms(data = data_cluster,
+                                y = "internalizing_sum",
+                                formula = "gender + cluster_mother + cluster_father"),
+    stan_data = make_stan_data(data = data_cluster)
   )
 }
 

### 2021-07-01 Analysis/Analysis_Drake.R
add zip analysisi, anova approach and brms models

@@ -64,21 +64,69 @@ summary(mclust_mother)
 plot(mclust_father)
 summary(mclust_father)
 
+#---- ZIP analysisi ----
+drake::loadd(fit_int_poisson)
+car::Anova(fit_int_poisson)
+summary(fit_int_poisson)
+
+drake::loadd(test_zero_inflated)
+test_zero_inflated
+
+#---- anova approach ----
+drake::loadd(fit_int_zip)
+car::Anova(fit_int_zip) # https://rcompanion.org/handbook/J_01.html see "Zero-inflated regression example"
+
+summary(fit_int_zip)
+
+rcompanion::nagelkerke(fit_int_zip)
 #---- brms models ----
 
-drake::loadd(fit_int_additive)
+drake::loadd(waic_weights)
+drake::loadd(loo_weights)
 
-summary(fit_int_additive)
-plot(brms::conditional_effects(fit_int_additive), ask = FALSE)
+drake::loadd(brm_int_mother)
 
-plot(fit_int_additive)
+summary(brm_int_mother)
+plot(brm_int_mother)
+plot(brms::conditional_effects(brm_int_mother), ask = FALSE)
+
+brms::pp_check(brm_int_mother, nsamples = 100)
+
+#---- BF encompassing priors ----
+
+drake::loadd(prior_model)
+
+#----
 
 drake::loadd(stan_data)
 
-str(fit_int_additive$fit)
+str(brm_int_additive$fit)
+
 #-----
+drake::loadd(brm_int_zero)
+drake::loadd(brm_int_mother)
+drake::loadd(brm_int_additive)
 
 
+#----
 
+ggplot(data_cluster) +
+  geom_histogram(aes(x = internalizing_sum, fill = cluster_mother),alpha = .7, bins = 20) +
+  facet_grid(cluster_mother ~ .)
+
+#----
+data_plot <- brms::posterior_samples(prior_model, pars = c("b_cluster_motheranxious", "b_cluster_motheravoidant"))
+ggplot(data_plot, aes(x=b_cluster_motheranxious, y=b_cluster_motheravoidant) ) +
+  geom_density_2d()
+
+#----
+
+condMVNorm
+
+condMVNorm::dcmvnorm(c(0,0), mean = c(0,0,0), sigma = diag(3),
+                     dependent.ind=c(1,2), given.ind=c(3), X.given = c(0))
+
[…]

### 2021-07-01 R/Models.R

@@ -11,9 +11,42 @@ zip_brms <- function(data, y, formula){
 
   fit <- brms::brm(brms::bf(as.formula(formula_lambda),
                             as.formula(formula_zi)),
-    data = data, family = brms::zero_inflated_poisson())
+    data = data, family = brms::zero_inflated_poisson(), cores = 4)
 
+  fit <- brms::add_criterion(fit, criterion = c("loo", "waic"))
   return(fit)
+}
+
+#----    get_waic_weights    ----
+
+get_rel_weights <- function(..., ic = c("waic", "loo")){
+  ic <- match.arg(ic)
+
+  names_fit <- as.list(match.call(), )[-1] %>%
+    as.character(.)
+
+  if(ic %in% names_fit) names_fit <- names_fit[which(names_fit != ic)]
+
+  list_fit <- list(...)
+
+  if(ic == "waic"){
+    fit_ics <- lapply(list_fit, FUN = function(x){
+      brms::waic(x)$estimates["waic", 1]
+      })
+  } else {
+    fit_ics <- lapply(list_fit, FUN = function(x){
+      brms::loo(x)$estimates["looic", 1]
+    })
+  }
+
+
+  res <- data.frame(names = names_fit,
+                    ic = unlist(fit_ics)) %>%
+    mutate(diff_ic=max(ic)-ic,         # Compute difference
+           rel_lik=exp(diff_ic/2),       # Compute relative likelihood
+           weights=rel_lik/sum(rel_lik))
+
+  return(res)
 }
 
 #----    make_stan_data    ----

### 2021-07-01 R/Plan.R

@@ -40,12 +40,47 @@ get_analysis_plan <- function(){
                                parent = "father"),
 
     #----    ZIP analysis    ----
+    fit_int_poisson = glm(internalizing_sum ~ cluster_mother * cluster_father,
+                          data = data_cluster, family = "poisson"),
+    test_zero_inflated = performance::check_zeroinflation(fit_int_poisson),
+
+    #----    anova approach ----
+    fit_int_zip = pscl::zeroinfl(internalizing_sum ~ cluster_mother * cluster_father,
+                                 dist = "poisson", data = data_cluster),
 
     #----    brms Models    ----
-    fit_int_additive = zip_brms(data = data_cluster,
+    brm_int_zero = zip_brms(data = data_cluster,
+                            y = "internalizing_sum",
+                            formula = "1"),
+    brm_int_mother = zip_brms(data = data_cluster,
+                              y = "internalizing_sum",
+                              formula = "cluster_mother"),
+    brm_int_additive = zip_brms(data = data_cluster,
                                 y = "internalizing_sum",
-                                formula = "gender + cluster_mother + cluster_father"),
-    stan_data = make_stan_data(data = data_cluster)
+                                formula = "cluster_mother + cluster_father"),
+
+    # brm_int_interaction = zip_brms(data = data_cluster,
+    #                                y = "internalizing_sum",
+    #                                formula = "cluster_mother * cluster_father"),
+
+    # stan_data = make_stan_data(data = data_cluster)
+
+    waic_weights = get_rel_weights(brm_int_zero,
+                                   brm_int_mother,
+                                   brm_int_additive, ic = "waic"),
+    loo_weights = get_rel_weights(brm_int_zero,
+                                  brm_int_mother,
+                                  brm_int_additive, ic = "loo"),
+
+    #----    BF encompassing priors    ----
+
+    prior_spec = brms::set_prior("normal(0,5)", class = c("b"), dpar = c("", "zi")),
+    prior_model = brms::brm(brms::bf(internalizing_sum ~ cluster_mother + cluster_father,
+                                     zi ~ cluster_mother + cluster_father),
+                            data = data_cluster, family = brms::zero_inflated_poisson(),
+                            prior = prior_spec, cores = 4, sample_prior = "only",
+                            iter = 5000, warmup = 0)
+
   )
 }
 

### 2021-07-01 Documents/TODO.Rmd
add todo list

---
title: 'TODO'
output:
  bookdown::html_document2: 
    toc: true
    toc_depth: 3
    toc_float: true
    collapsed: false
    # css: ["css/custom.css"]
linestretch: 1.5
number_sections: true
# bibliography: "../Biblio-attachment.bib"
# csl: apa.csl
link-citations: true 
editor_options: 
  chunk_output_type: console
---

# Bayes Factor Encompassing Priors

- [ ] Reparametrize model according to: 
\begin{align}
&\beta_{eq} = R_{eq}\theta - r_{eq},\\
&\beta_{ineq} = R_{ineq}\theta - r_{ineq}.
\end{align}
Doing this we get informative hypotheses as $H_i: \beta_{eq} = 0,\ \beta_{ineeq}>0$, so prior specification is semplified and with simmetric prior we do  not favoir any constraint. Exception for range constraints of type $a<\theta<b$.

- [X] Marginal densities of a multivariate normal distribution are obtained simply dropping irreleevantt variables ([link math-stackexchange](https://math.stackexchange.com/questions/2528201/find-the-marginal-distributions-pdfs-of-a-multivariate-normal-distribution)

### 2021-07-01 Documents/TODO.Rmd
bayes factor first trial

@@
 
-- [X] Marginal densities of a multivariate normal distribution are obtained simply dropping irreleevantt variables ([link math-stackexchange](https://math.stackexchange.com/questions/2528201/find-the-marginal-distributions-pdfs-of-a-multivariate-normal-distribution)
+- [X] Marginal densities of a multivariate normal distribution are obtained simply dropping irreleevantt variables ([link math-stackexchange](https://math.stackexchange.com/questions/2528201/find-the-marginal-distributions-pdfs-of-a-multivariate-normal-distribution))

### 2021-07-01 Analysis/Analysis_Drake.R

@@ -107,7 +107,7 @@ drake::loadd(brm_int_zero)
 drake::loadd(brm_int_mother)
 drake::loadd(brm_int_additive)
 
-
+brms::conditional_effects(brm_int_additive)
 #----
 
 ggplot(data_cluster) +
@@ -115,16 +115,36 @@ ggplot(data_cluster) +
   facet_grid(cluster_mother ~ .)
 
 #----
-data_plot <- brms::posterior_samples(prior_model, pars = c("b_cluster_motheranxious", "b_cluster_motheravoidant"))
-ggplot(data_plot, aes(x=b_cluster_motheranxious, y=b_cluster_motheravoidant) ) +
-  geom_density_2d()
+
+data_plot <- brms::posterior_samples(brm_int_additive, pars = c("b_cluster_motheranxious", "b_cluster_motheravoidant"))
+
+mu <- apply(data_plot,2, mean)[c(1,3)]
+cov <- cov(data_plot[, c(1,3)])
+
+data_grid <- expand.grid(s_1 = seq(0, .3, length.out=100), s_2 = seq(-.1, .25, length.out=100))
+q_samp <- cbind(data_grid, prob = mvtnorm::dmvnorm(data_grid, mean = mu, sigma = cov))
+
+ggplot(data_plot) +
+  geom_density_2d(aes(x=b_cluster_motheranxious, y=b_cluster_motheravoidant)) +
+  geom_contour(data = q_samp, aes(x=s_1, y=s_2, z=prob), col = "black")
 
 #----
 
 condMVNorm
 
-condMVNorm::dcmvnorm(c(0,0), mean = c(0,0,0), sigma = diag(3),
-                     dependent.ind=c(1,2), given.ind=c(3), X.given = c(0))
+mvtnorm::dmvnorm(x = c(0,0), mean = c(0,0), sigma = diag(2)*10)
+
+condMVNorm::dcmvnorm(c(0), mean = c(0,0), sigma = diag(2)*10,
+                     dependent.ind=c(1), given.ind=c(2), X.given = c(0))
+
+obs <- condMVNorm::rcmvnorm(n = 1e4, mean = c(0,0,0), sigma = diag(3),
+                            dependent.ind=c(1,2), given.ind=c(3), X.given = c(0))
+
+res <- apply(obs, 1, function(x){
+  condMVNorm::dcmvnorm(x, mean = c(0,0,0), sigma = diag(3),
[…]

### 2021-07-01 R/Bayes_Factor.R

@@ -1,0 +1,52 @@
+library(rstan)
+options(mc.cores = 4)
+rstan_options(auto_write = TRUE)
+
+stan_data <- make_stan_data(data_cluster)
+fit_H1 <- stan(file = "Stan/ZIP-model-H1.stan", data = stan_data)
+
+round(summary(fit_H1)$summary[, "mean"],2)
+
+round(brms::posterior_summary(brm_int_additive)[, "Estimate"],2)
+
+post_H1 <- as.matrix(fit_H1, pars = c("db_mother[1]", "db_mother[2]", "db_mother[3]"))
+
+colnames(post_H1)
+
+#---- BF ----
+
+post_mean <- apply(post_H1, 2, mean)
+post_cov <- cov(post_H1)
+
+prior_mean <- c(0, 0, 0)
+prior_cov <- diag(3) * 25
+
+# prior density equality
+prior_den_eq <- mvtnorm::dmvnorm(x = 0,
+                                 mean = prior_mean[2],
+                                 sigma = as.matrix(prior_cov[2,2]))
+dnorm(0,0,5)
+
+# posterior density equality
+post_den_eq <- mvtnorm::dmvnorm(x = 0,
+                                mean = post_mean[2],
+                                sigma = as.matrix(post_cov[2,2]))
+dnorm(0, post_mean[2], sqrt(post_cov[2,2]))
+
+# prior conditional probability
+prior_cond_prob <- condMVNorm::pcmvnorm(
+  lower = rep(0,2), upper = rep(Inf,2),
+  mean = prior_mean, sigma = prior_cov,
+  dependent.ind=c(1, 3), given.ind=c(2), X.given = c(0))
+
+# posterior conditional probability
+post_cond_prob <- condMVNorm::pcmvnorm(
+  lower = rep(0,2), upper = rep(Inf,2),
+  mean = post_mean, sigma = post_cov,
+  dependent.ind=c(1, 3), given.ind=c(2), X.given = c(0))
+
+# Resulting BF
+
+BF_H1 <- (post_den_eq * post_cond_prob) / (prior_den_eq * prior_cond_prob)
+
+#----

### 2021-07-01 R/Models.R

@@ -53,8 +53,8 @@ get_rel_weights <- function(..., ic = c("waic", "loo")){
 
 make_stan_data <- function(data){
   formula <-  brms::bf(
-    internalizing_sum ~ gender + cluster_mother + cluster_father,
-    zi ~ gender + cluster_mother + cluster_father)
+    internalizing_sum ~ cluster_mother + cluster_father,
+    zi ~ cluster_mother + cluster_father)
 
   formula <- brms:::validate_formula(formula, data = data, family = brms::zero_inflated_poisson(),
                                      autocor = NULL, sparse = NULL, cov_ranef = NULL)

### 2021-07-02 Documents/Report-Project/Attachment_Analysis_Report.Rmd
revision analysis internalizing

@@
 # Data
+drake::loadd(raw_data)
 drake::loadd(data_munged)
+drake::loadd(data_cluster)
 
@@
 drake::loadd(cluster_father_fit)
-drake::loadd(data_cluster)
+
 drake::loadd(mclust_mother)
@@
 
+# ZIP anlaysis
+drake::loadd(fit_int_poisson)
+
+# ANOVA
+drake::loadd(fit_int_zip)
+
 # brms models
-drake::loadd(fit_int)
+drake::loadd(brm_int_mother)
+drake::loadd(waic_weights_int)
+drake::loadd(loo_weights_int)
+
+# BF encompassing
+drake::loadd(fit_H1)
 ```
+
+In this report, preliminary results of the analysis are presented considering as dependent variable internalizing problems.
+Note the actual paper will consider externalizing problems, instead.
+(**Spoiler**: with externalizing problems models present more interesting results.
+However, here we used internalizing problems as an example to introduce the analysis method avoiding to influence the subsequent expert elicitation regarding externalizing problems).
+
+# Introduction
+
+## Backgorund
+
+The aim of the analysis is to compare the 4 main theories regarding the role of child-mother  and child-father attachment on children development. In brief:
+
+1. **Monotropy Theory** - only the mother is important
+1. **Hierarchical Theory** -  the mother is more important than the father
+1. **Independent Theory** - mother and father affect different area of children development
+1. **Interaction Theory** - mother and father interact
+
+Here we evaluate as dependent variable:
+
+- **Internalizing Problems** - given by the sum of the SDQ (*Strengths & Difficulties Questionnaires*)
+
+As independent variable we consider:
+
+- **Gender** - children gender
+- **Mother Attachment** - considering clusters obtained from the ECR questionnaire
+- **Father Attachment** - considering clusters obtained from the ECR questionnaire
+
+## Analysis Plan
+
+First, we present descriptive statistics and cluster analysis of mother and father attachment.
+Subsequently we present three different analyses discussing pro and con of each approach.
+In particular we adopted:
+
+1. Tradition ANOVA analysis. (Note that actually is Analysisi of Deviance)
+1. Bayesian Model Comparison
+1. Bayes Factor with Encompassing Priors
+
+In all cases, Zero Inflated Poisson (*ZIP*) models were used to take into account the distribution characteristics of the dependent variable. This issue is discussed below.
 
@@
 
-## Dependent Variable
+The sample size is:
 
-### Externalizing
-```{r}
-ggplot(data_munged) +
-  geom_bar(aes(x = externalizing_sum, fill = gender), alpha = 0.7) +
-  facet_grid(gender ~ .)
+```{r sample-size, echo = TRUE}
+nrow(data_cluster)
 ```
 
-### Internalizing
-```{r}
-ggplot(data_munged) +
-  geom_bar(aes(x = internalizing_sum, fill = gender), alpha = 0.7) +
-  facet_grid(gender ~ .)
+#### Age {-}
+
+Summary statistics of children age (in years).
+
+```{r, echo = TRUE}
+summary(raw_data$age_year)
+sd(raw_data$age_year, na.rm = TRUE)
 ```
 
-# Cluster Analysis
+```{r, plot-age}
+ggplot(raw_data) +
+  geom_histogram(aes(x = age_year), col = "grey40", fill = "#00BFC4") +
+  theme_bw()
+```
 
-## Mother
+Children school grade frequancy
 
 ```{r}
+table(raw_data$classe)
+```
+
+#### Gender {-}
+
+```{r}
+table(data_cluster$gender)
+```
+
+## Cluster Analysis
+
+### Mother
+
+From the cluster analysis, 4 groups were selected.
+
+```{r, plot-cluster-mother}
 plot(cluster_mother_fit, main = "Dendrogramma")
@@
 
-Frequencies
+Frequencies of the clusters are
 
 ```{r, echo = TRUE}
-table(data_cluster$cluster_mother)
+table(data_cluster$mother)
 
-prop.table(table(data_cluster$cluster_mother))
+prop.table(table(data_cluster$mother))
 
-prop.table(table(data_cluster$cluster_mother,
+prop.table(table(data_cluster$mother,
                  data_cluster$gender),2)
 
-summary(table(data_cluster$cluster_mother,
+summary(table(data_cluster$mother,
               data_cluster$gender))
@@
 
-Plot Scores
+Plot of average Anxiety and Avoidance scores in the four clusters
 
-```{r}
+```{r, plot-scores-mother}
 plot_scores_mother(data = data_cluster)
@@
 
-#### Mclust check
+#### Mclust check {-}
 
-```{r}
+```{r, plot-mclust-mother}
 plot(mclust_mother)
@@
 
-## Father
+### Father
 
-```{r}
+From the cluster analysis, 4 groups were selected.
+
+```{r, plot-cluster-father}
 plot(cluster_father_fit, main = "Dendrogramma")
@@
 
-Frequencies
+Frequencies of the clusters are
 
 ```{r, echo = TRUE}
-table(data_cluster$cluster_father)
+table(data_cluster$father)
 
-prop.table(table(data_cluster$cluster_father))
+prop.table(table(data_cluster$father))
 
-prop.table(table(data_cluster$cluster_father,
+prop.table(table(data_cluster$father,
                  data_cluster$gender),2)
 
-summary(table(data_cluster$cluster_father,
+summary(table(data_cluster$father,
               data_cluster$gender))
@@
 
-Plot Scores
+Plot of average Anxiety and Avoidance scores in the four clusters
 
-```{r}
+```{r, plot-scores-father}
 plot_scores_father(data = data_cluster)
@@
 
-#### Mclust check
+#### Mclust check {-}
 
-```{r}
+```{r, plot-mclust-father}
 plot(mclust_father)
@@
 
-# Statistical Approach
+### Mother & Father
 
-In this section we describe the statistical approach.
-First we define the statistical model used to describe the data generative process.
-Subsequently, the approach for testing hypotheses with inequality and equality constraints is discussed.
-Finally, the Gibbs sampler to estimate the model with inequality constraints is presented.
+Overall frequencies of mother and father attachment
+```{r, echo = TRUE}
+table(data_cluster$mother, data_cluster$father)
 
-## Model Definition
+round(prop.table(table(data_cluster$mother, data_cluster$father)),3)
 
-### Psychologial Background
-
-In this analysis, we want to evaluate children psychological problems according to children gender and  children-mother and children-father attachment relationship.
-Note that attachment relationship is considered as a categorical variable.
-
-### Zero Inflated Poisson (ZIP) {#model}
-
-The dependent variable is a positive discrete variable.
-Considering Figure \@ref(fig:plot-int), it is possible to observe the the distribution of the dependent variable is characterized by a zero inflation.
-
-```{r plot-int, fig.cap = "Dependent variable distribution"}
-ggplot(data_munged) +
-  geom_bar(aes(x = internalizing_sum, fill = 1), alpha = 0.7) +
-  labs(x = "Internalizing Problems") +
-  theme_bw() + 
-  theme(legend.position = "none")
+table(data_cluster$mother, data_cluster$father, data_cluster$gender)
 ```
 
-Thus, we decided to model the data considering a Zero Inflated Poisson (ZIP):
+## Dependent Variable
+
+### Internalizing
+
+Distribution of internalizing problems
+```{r, plot-internalizing}
+ggplot(data_cluster) +
+  geom_bar(aes(x = internalizing_sum), col = "gray40", fill = "#00BFC4", alpha = 0.7) +
+  theme_bw()
+```
+
+Internalizing according to gender
+
+```{r, plot-internalizing-gender}
+ggplot(data_cluster) +
+  geom_bar(aes(x = internalizing_sum, fill = gender), col = "gray40", 
+           alpha = 0.7, show.legend = FALSE) +
+  facet_grid(gender ~ .) +
+  theme_bw() 
+```
+
+#### Zero Inflation {-}
+
+Considering the distribution of internalizing scores it seems that there is an inflation of zero. To evaluate that we fit a poisson model and we compare the number of observed zero and expected zero.
+
+```{r, echo = TRUE, eval = FALSE}
+# model formula
+internalizing_sum ~ gender + cluster_mother * cluster_father
+```
+
+```{r, echo = TRUE}
+fit_int_poisson
+```
+
+```{r, echo = TRUE}
+performance::check_zeroinflation(fit_int_poisson)
+```
+
+Results indicate that the model is underfitting zeros. Thus in the analysis we will use a Zero inflated Poisson (*ZIP*) model.
+
+# Statistical Analysis
+
+In all subsequent analysis we considered Zero Inflated Poisson (ZIP) models:
 
@@
 
-Where, $1 - p_i$ indicates the probability of given observation $y_i$ being generated from a Poisson distribution with mean $\lambda_i$. In particular,
+Where, $p_i$ is the probability of an observation $y_i$ being an extra zero (i.e., a zero not comming from the poisson distribution) and $1 - p_i$ indicates the probability of given observation $y_i$ being generated from a Poisson distribution with mean $\lambda_i$.
+In particular,
 
@@
 
-That is, we want to model both $p_i$ and $\lambda_i$ according to the variables previously defined estimating respectively parameters vector $\beta_p$ and $\beta_{\lambda}$.
+That is, we want to model both $p_i$ and $\lambda_i$ according to a set of independent variables.
+Thus we have to estimate parameters vector $\beta_p$ and $\beta_{\lambda}$ respectively.
 Note that these are the only parameters in the model.
 
-This model can be easily estimate using `brms`. However, currently it is not possible to include inequality and equality constraints in the parameters prior definition.
+In particular we considered as predictors:
 
-Note that, the actual distribution of the dependent variable is truncated (limit given by the maximum questionnaire score).
-However, we do not consider this aspect to avoid a further level of complexity in the model.
+```{r, echo = TRUE, eval = FALSE}
+# formula for p
+p ~ gender
 
-## Test of Hypotheses with Inequality and Equality Constraints
+# formula for lambda
+lambda ~ gender + ...
+```
 
-**Bayes Factor** to evaluate different hypotheses with inequality and equality constraints can be obtained following the **Encompassing Prior Approach**.
-That is, an unconstrained model is considered as reference with encompassing priors that are uninformative with respect to the parameters.
-All other models are nested in this model and the priors ore obtained by restricting the parameter space in accordance with the constraints imposed by each model.
+That is, we model the probability ($p_i$) of an observation being zero or coming from a poisson distribution according to `gender`.
+Whereas, we model the poisson mean ($\lambda_i$) according to `gender` and other variables among `cluster_mother` and `cluster_father`.
 
-### Inequality Constraints: A First Approach
+## ANOVA Approach
 
-@katoBayesianApproachInequality2006 presented an approach to evaluate **inequality constraints** based on the principle of encompassing priors.
-Given an unconstrained model $M_u$ and a nested model $M_i$,  the prior and posterior densities of $M_i$ can be rewritten in terms of the prior and posterior densities of $M_u$:
+Classical approach is to fit the most complex model.
+Subsequently, ANOVA or likelihood ratio test are computed to evaluate the significance of the predictors.
+Finally, according to the results, researcher evaluate if hypothesis are supported or not.
 
-$$
-\pi(\theta|M_i) = B_i \times \pi(\theta|M_u),\\
-Pr(\theta|D,\ M_i) = A_i \times Pr(\theta|D,\ M_u).
-$$
+In our case we fit a model considering the interaction between `cluster_mother` and `cluster_father`. That is:
+```{r, echo = TRUE, eval = FALSE}
+# formula for p
+p ~ gender
 
-Where, $1/B_i$ indicates the proportion of the prior distribution of $M_u$ in agreement with $M_i$ and $1/A_i$ is the proportion of the posterior distribution of $M_u$ in agreement with $M_i$.
+# formula for lambda
+lambda ~ gender + mother * father
+```
 
-Assuming equal prior probability of the two models ($\pi(M_u) = \pi(M_i)$), the Bayes Factor is obtained as follow:
+Than we conduct an ANOVA using the `car`. Note that as we are using a GLM we are actually conducting an Analysis of Deviance.
 
-\begin{aligned}
-BF_{iu} =& \frac{Pr(D|M_i)}{Pr(D|M_u)} =\\ \\
-&\frac{L(D|\theta)\pi(\theta|M_i)/Pr(\theta|D,\ M_i)}{L(D|\theta)\pi(\theta|M_u)/Pr(\theta|D,\ M_u)} = \\ \\
-&\frac{\pi(\theta|M_i)Pr(\theta|D,\ M_u)}{\pi(\theta|M_u)Pr(\theta|D,\ M_i)} = \\ \\
-&\frac{[B_i \times \pi(\theta|M_u)] Pr(\theta|D,\ M_u)}{\pi(\theta|M_u)[A_i \times Pr(\theta|D,\ M_u)]} = \frac{B_i}{A_i}
-\end{aligned}
+```{r, echo = TRUE}
+car::Anova(fit_int_zip)
+```
 
-That is, the Bayes Factor is the ratio between $1/A_i$ (i.e.
-the proportion of the posterior distribution of $M_u$ in agreement with $M_i$ that provides information about the *fit* of $M_i$ relative to $M_u$), and $1/B_i$ (i.e., the proportion of the prior distribution of $M_u$ in agreement with $M_i$ that provides information about the *complexity* of $M_i$ relative to $M_u$).
+In this case we get that the interaction is significant. Thus results support the **Interaction Theory**.
 
-Note that Bayes Factor is obtained without computing the marginal likelihoods of the two models, but only considering the proportions of the prior and the posterior in agreement with constraints of each of the models.
+Summary of the model:
+```{r, echo = TRUE}
+summary(fit_int_zip)
+```
 
-#### Pro {-}
+R squared:
 
-- Given the prior and posterior samples of the model, it is straightforward to compute $1/A_i$ and $1/B_i$. The analytical distributions are not required.
-- If Prior distributions of $\beta_p$ and $\beta_{\lambda}$ are vague enough and sample is large, influence of the choice of the encompassing prior on the posterior distributions is negligible, and subsequently also its influence on $1/A_i$ is negligible.
-- For constraints of the form $\beta_i > \beta_j > \beta_k$ with $\beta_{i,j,k} \stackrel{i.i.d.}{\sim} \pi(\beta)$, the prior probability of the constraints is independent of the actual choice of the encompassing prior, and subsequently also $1/B_i$ is not influenced.
+```{r, echo = TRUE}
+rcompanion::nagelkerke(fit_int_zip)
+```
 
-#### Cons {-}
+**TODO** - plot of the effects (below are effects from the normal poisson model)
 
-- It is not possible to evaluate **equality constraints**. In the case of $H_i:\ \beta_i = \beta_j$,  $1/A_i$ and $1/B_i$ are equal to zero.
-- Equality constraints can be expressed as $$|\beta_i - \beta_j|\leq \xi$$ for small value of $\xi$.
-In this case, however, for vague encompassing prior $1/A_i$ is still virtually independent but $1/B_i$ is not.
-The more diffuse the encompassing prior is the smaller the Bayes factor in favor of the unconstrained model (similar to *Lindley’s paradox* where results are influenced by the vagueness of the prior distribution of the parameters involved).
-Sensitivity analysis is required considering both the choice of prior distributions and the value of $\xi$.
+```{r, plot-ANOVA-effects}
+plot(effects::effect(mod = fit_int_poisson, term = "mother * father"))
+```
 
-#### Consideration {-}
+### Consideration
 
-This is a possible approach. However, in our hypotheses there are several equality constraints. Thus, it would be important to properly evaluate them.
+The problem here is to evaluate which are the actual differences of interests. Are we modeling relevant effects or random noise? We are not penalizing for complexity of the model.
 
-### Inequality and Equality Constraints: A Second Approach {#in-eq-const}
+Moreover we are not comparing dirrectly the hypothesis of interest but just doing testing.
 
-@guApproximatedAdjustedFractional2018 and @mulderBayesFactorTesting2019 presented an approach to evaluate **inequality and equality constraints** still based on the principle of encompassing priors.
+## Bayesian Model Comparison Approach
 
-Informative hypotheses using equality and/or inequality constraints can be expressed as
+We compare 4 models. In all models $p_i$ is predicted by gender, whereas predictors of $\lambda_i$ are selected according to the different hypothesis:
 
+1. `brm_int_zero`: $\lambda_i \sim$ `gender`
+1. `brm_int_mother`: $\lambda_i \sim$ `gender + mother`
+1. `brm_int_additive`: $\lambda_i \sim$ `gender + mother + father`
+1. `brm_int_inter`: $\lambda_i \sim$ `gender + mother * father`
+
+Models were estimated using in `brms` using default prior settings.
+
+```{r, echo = TRUE}
+brms::prior_summary(brm_int_mother)
+```
+
+Model comparison approach using waic index:
+
+```{r, echo = TRUE}
+waic_weights_int
+```
+
+and loo index
+
+```{r, echo = TRUE}
+loo_weights_int
+```
+
+The *preferred* model is the one considering only the role of mother attachment. Results support the
+**Monotropy Theory**.
+
+### `brm_int_mother`
+
+Model summary. Note that `brms` indicates $p_i$ with `zi`.
+
+```{r, echo = TRUE}
+summary(brm_int_mother)
+```
+
+Plot effects
+
+```{r, plot-effects-brm_int_mother}
+plot(brms::conditional_effects(brm_int_mother), ask = FALSE)
+```
+
+Posterior Predictive Check
+```{r}
+brms::pp_check(brm_int_mother, nsamples = 25)
+```
+
+**TODO** - not really a good fit, clear sign of over-dispersion. Probably Negative binomial would be better than poisson.
+
+R squarded
+
+```{r, echo = TRUE}
+brms::bayes_R2(brm_int_mother)
+```
+
+### Considerations
+
+Overall fit is pretty bad. However, this approach allow us to define models according to research hypothesis and compare them taking into account model complexity.
+
+Using this approach, however, there is not a lot of formalization. For example we are not explicitying the expected direction of the effects or the expected order.
+
+## Bayes Factor  Encompassin Prior Approach
+
+With this approach we can explicit equality and order constraints between parameters. Thus a given Hypothesis can be expressed as:
 $$
@@
 $$
-where $R_E$ and $R_I$ are the restriction matrices for equality and inequality constraints, respectively, and $r_E$ and $r_I$ contain constants.
 
-Following encompassing prior approach, given an unconstrained model $M_u$ and a nested model $M_i$, the Bayes Factor is computed as
+In order to compare informative hypothesis, we define an unconstrained model considered as reference with encompassing priors that are uninformative with respect to the parameters.
+All other models are nested in this model and the priors ore obtained by restricting the parameter space in accordance with the constraints imposed by each model.
+
+Note that we first need to reparametrize the model as follow:
+\begin{align}
+&\beta_{eq} = R_{eq}\theta - r_{eq},\\
+&\beta_{ineq} = R_{ineq}\theta - r_{ineq}.
+\end{align}
+These allows as to express constraints as
+$$H_i: \beta_{eq} = 0,\ \beta_{ineeq}>0,$$ 
+so prior specification is simplified (they are all centered to zero) and with symmetric priors we do  not favor any constraint.
+
+For example for a constraint of type:
+$$
+0<\theta_1<\theta_2<\theta_3
+$$
+we would define
+$$
+d\theta_2:= \theta_2 - \theta_1\\
+d\theta_3:= \theta_3 - \theta_2
+$$
+So wee can express constraints as
+$$
+\theta_1>0\\
+d\theta_2>0\\
+d\theta_3>0
+$$
+
+Subsequently we can compute the Bayes Factor between an informative hypothesis ($M_i$) and the unconstrain model ($M_u$) as
 
@@
 
-Note that the numerators provide information about the *fit* of $M_i$ relative to $M_u$ and the denominators provide information about the *complexity* of $M_i$ relative to $M_u$.
+### Toy Example
 
-#### Pro {-}
+As an example consider these hypothesis considering mother attachment:
 
-- It allows to evaluate inequality and equality constraints.
+$$\text{Mother-Secure} = \text{Mother-Avoidonat} < \text{Mother-Anxious} < \text{Mother-Anxious-Avoidant}$$
+Note that we do not define any constrain regarding the father (but we will do it in the actual application).
 
-#### Cons {-}
+For simplicity consider as encompassing model the model with only the mother and gender as predictor of $\lambda_i$ (actual application will consider the interaction model).
+Note that according to the used *treatment-contrast coding* we have:
 
-- The encompassing prior and posterior distributions are required in analytic form to compute conditional probabilities and marginal densities.
+\begin{align}
+&intercept = \text{Mother-Secure Female}\\
+&\beta_1 = \text{Gender-Male}\\
+&\beta_2 = \text{Mother-Anxious}\\
+&\beta_3 = \text{Mother-Avoidonat}\\
+&\beta_4 = \text{Mother-Anxious-Avoidant}\\
+\end{align}
 
-#### Consideration {-}
+So we re-parametrize the model as follow
+$$
+d\beta_4 := \beta_4 -\beta_2
+$$
+and the constraints we obtain are
+$$
+\beta_2 > 0\\
+\beta_3 = 0\\
+d\beta_4 > 0 
+$$
+Note that $\beta_1$ do not appear in the constraints so is considered as a nuisance parameter together with the intercepts and parameters referiing to $p_i$.
 
-Obtaining the analytic posterior distribution is often difficult.
-To overcome this issue, @guApproximatedAdjustedFractional2018 and @mulderBayesFactorTesting2019 proposed two different solutions both based on **Normal approximations**.
-Let's consider the two approaches separately.
+Here the actual stan code for parameters and transformed parameter block (note a little bit of messing with indexing):
+```{stan output.var='priors', eval = FALSE, echo = TRUE}
+parameters {
+  // lambda regression parameters
+  real b_gender;
+  vector[3] db_mother; // order constraints mother
+  real Intercept;  // temporary intercept for centered predictors
 
-#### @mulderBayesFactorTesting2019 {#mulder}
+  // zi regression parameters
+  vector[Kc_zi] b_zi;  // population-level effects
+  real Intercept_zi;  // temporary intercept for centered predictors
+}
+transformed parameters {
+  vector[Kc] b;  // population-level effects
 
-Authors used to different solutions for computing the posterior and the prior:
-
-- **Computing Posterior** - a Metropolis-Hastings algorithm is used to obtain draws from the posterior of the unconstrained model.
-Subsequently the posterior was assumed to be approximately normally distributed
-$$
-Pr(\theta|Y) \sim \mathcal{N}(\mu_\theta, \Sigma_\theta)
-$$
-where $\mu_\theta$ and $\Sigma_\theta$ are the posterior mean and covariance matrix estimated from the posterior draws.
-Thus, conditional posterior probability and marginal posterior density are computed based on the normal approximation.
-
-- **Computing Prior** - in their case priors are not normally distributed. To estimate the marginal prior density they considered the fact that for a sufficiently small $\delta$,
-$$
-Pr(|\theta_{E_1} - r_{E_1}| < \frac{\delta}{2}, \ldots, |\theta_{E_i} - r_{E_i}| < \frac{\delta}{2}|M_u) \approx \delta^i \times \pi_u(\theta_E = r_E)
-$$
-Thus, the probability can be estimated considering the proportion of draws satisfying the constraints.
-To compute conditional prior probability, they used a normal approximation because this probability is not sensitive to the exact distributional form as long as they are symmetrical distributed around the value of the constraints, usually zero.
-The mean and covariance matrix were estimated based on the prior draws that satisfied the equality constraints.
-To do that they used the same approximation as before (i.e., $|\theta_{E_i} - r_{E_i}| < \frac{\delta}{2}$).
-
-<!-- Note that their procedure implied a linear transformation of the parameters  to express constraints in a simpler form. -->
-
-#### @guApproximatedAdjustedFractional2018
-
-In this paper, the Approximated Adjusted Fractional Bayes Factors (AAFBF) method is presented.
-To avoid ad hoc or subjective specification of the unconstrained prior, the fractional Bayes factor approach is used.
-That is, proper default prior were defined updating non informative priors according to a a fraction *b* of the data
-$$
-\text{Proper Prior: }\pi_u(\theta|Y_b) \approx Pr(Y_b|\theta) \times \pi_u(\theta).
-$$
-The choice of the fraction $b$ also plays a crucial in the AAFBF and is extensively discussed in the article.
-
-Prior and posterior distributions are assumed to be approximately normally distributed due to the large-sample theory:
-\begin{aligned}
-\text{Prior: }& \pi_u(\theta|Y_b) \sim \mathcal{N}(\hat{\theta}, \hat{\Sigma}_\theta/b),\\ \\
-\text{Posterior: }& \pi_u(\theta|Y) \sim \mathcal{N}(\hat{\theta}, \hat{\Sigma}_\theta).
-\end{aligned}
-Where $\hat{\theta}$ and $\hat{\Sigma}_\theta$ denote the maximum likelihood estimate and covariance matrix of $\theta$, respectively.
-
-Moreover, authors proposed an adjustment of the prior mean for centering the prior distribution of $\theta$ on the boundary of the constrained space.
-This ensure that $Pr(\theta>0)$ and $Pr(\theta<0)$ are equal for symmetric distributions and follow common assumption that small effects are more likely a prior than large effects.
-To facilitate the computation of the adjusted prior mean, the parameters are transformed,
-$$
-\beta = \left[\begin{array}{cc}\beta_E\\ \beta_I\end{array}\right] = \left[\begin{array}{cc}R_E \theta - r_E\\ R_I \theta - r_I\end{array}\right].
-$$
-In this way, informative hypothesis becomes $H_i:\ \beta_E=0, \beta_I>0$ and the prior mean vector is simply zero for the new parameter vector $\beta$.
-This parameter transformation from $\theta$ to $\beta$ simplifies the computation of the AAFBF.
-
-Note authors did not adjusted posterior mean since, according to large-sample theory, the prior has a negligible effect on the posterior for large samples.
-Thus, resulting prior and posterior distributions are:
-\begin{aligned}
-\text{Adjusted Prior: }& \pi_u^*(\beta|Y_b) \sim \mathcal{N}(0, \hat{\Sigma}_\beta/b),\\ \\
-\text{Posterior: }& \pi_u(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_\beta).
-\end{aligned}
-Where $\hat{\beta} = R\hat{\theta}-r$ and $\hat{\Sigma}_\beta = R\hat{\Sigma}_\theta R^T$.
-
-### Present Study
-
-In our case, the unconstrained model is a Zero Inflated Poisson model with parameter vectors $\beta_p$ and $\beta_{\lambda}$ (see Section \@ref(model)):
-
-\begin{aligned}
-y_i \sim& ZIPoisson(p_i, \lambda_i),\\ \\
-p_i =& \text{logit}^{-1}(X_i^T\beta_{p}),\\ \\
-\lambda_i =& \text{exp}(X_i^T\beta_{\lambda}).
-\end{aligned}
-
-We can assume independent priors for each parameter $\beta_i \sim \mathcal{N}(0, \sigma)$, with $\sigma$ a large enough so the priors are vague.
-
-To evaluate informative hypothesis with equality and inequality constraints, we can follow the approach presented in Section \@ref(in-eq-const) considering the method proposed by @mulderBayesFactorTesting2019, see Section \@ref(mulder).
-
-In our case, both the prior and the posterior distributions are normally distributed (TODO: is it true?):
-\begin{aligned}
-\text{Prior: }& \Pr(\beta) \sim \mathcal{N}(0, \Sigma_{\sigma}),\\ \\
-\text{Posterior: }& \Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}).
-\end{aligned}
-Where $\Sigma_{\sigma}$ is a diagonal matrix with all the diagonal elements equal to $\sigma$.
-Whereas, $\mu_\theta$ and $\Sigma_\theta$ are the posterior mean and covariance matrix estimated from the posterior draws.
-Posterior sample can be easily obtained in STAN.
-
-### Issues
-
-1. Ha senso questo approccio?
-1. Come posso marginalizzare i valori delle densità? Vedi le loro formule (p.27 in basso).
-1. Come ottenere le distribuzioni condizionate? Vedi le loro formule negli articoli (p.28).
-1. Dovrei preferire invece  l'Approximated Adjusted Fractional Bayes Factors method?
-1. Nel modello ci saranno anche interazioni tra fattori, tutti i possibili gruppi. Devo pensare bene su come parametrizzare i contrasti.
-1.
-Non sappiamo ancora quali saranno tutti i constraints e confronti ma sono tutti confronti tra gruppi.
-Devo essere sicuro che vengano rispettate le assunzioni delle ipotesi se uso l'Approximated Adjusted Fractional Bayes Factors method.
-Vedi "comparable hypotheses" formula 24 in @guApproximatedAdjustedFractional2018.
-1.
-Potrei fare dell'hard coding codificando ogni gruppo con dummy variables.
-Non avrei "effetti principali" ma mi permette di evitare casini nel definire i confronti.
-(Nella codifica tradizionale i valori medi dei gruppi sarebbero dati da somme di più parametri, gli stessi parametri sarebbero usati per più gruppi e questo potrebbee compicare la definizione dei constraints sui parametri).
-1. Devo stare attento che le prior non favoriscano alcun constraints e questo è problematico con gli equality constraints. (Al massimo faccio un po' di sensitivity sulle prior)
-
-## Estimating the Constrained Model
-
-Hypothesis testing will idicate us the most likely model according to the data. To evaluate the model parameters, howevere, we need to estimate the parameter posteriors.
-
-Parameter posteriors of the unconstrained model can be simply obtained using MCMC sampling implemented in STAN.
-However, obtaining parameter posteriors of models including inequality constraints is not straightforward.
-Here we describe two possible direction: the first one based on STAN and the second one based Gibbs sampling.
-
-### STAN Approach
-
-Considering the thread in the STAN forum *"How to give prior to ordered parameters, and also to simplex?"* ([link](https://discourse.mc-stan.org/t/how-to-give-prior-to-ordered-parameters-and-also-to-simplex/12041)), there is one answer ([link](https://discourse.mc-stan.org/t/how-to-give-prior-to-ordered-parameters-and-also-to-simplex/12041/7?u=claudio.zandonella)) suggesting a possible solution based on uniform priors.
-
-Given the restriction $a<\theta_1<\theta_2<\theta_3<b$, is it possible to redefine parameters as follow
-$$
-d\theta_2:= \theta_2 - \theta_1,\\
-d\theta_3:= \theta_3 - \theta_2.
-$$
-Subsequentely, priors can be defined as
-$$
-\theta_1\sim \text{Unif}(a, b),\\
-d\theta_2\sim \text{Unif}(0, b-\theta_1),\\
-d\theta_3\sim \text{Unif}(0, b-\theta_2).
-$$
-Using Uniform prior is plausible as, selecting a range large enough, they can be considered uninformative and similar to a Normal distribution with very large $\sigma$.
-Note that in the present study, the sample size is large ($n\approx$900) so the posterior is not affected by the choice of vague priors.
-
-#### Issues
-
-Questa soluzione l'ho trovata all'ultimo, devo ancora fare delle prove per capire quanto possa essere realmente valida. Ma comunque la segnalo perchè mi sembra interessante.
-
-Precedentemente cercavo se fosse possibile specificare prior normali con troncature.
-Il problema era che la troncatura dipenderebbe dagli altri parametri e quindi la stima diventerebba altamente instabile e le catene non convergono.
-
-In effetti ridefinire i parametri e utilizzare delle uniformi sembra una buona soluzione.
-Solo non riesco a capire se ci saranno comunque problemi di convergenza delle catene e soprattutto la finale intertpretazione dei parametri.
-
-### Gibbs Sampler Approach
-
-@rodriguez-yamEfficientGibbsSampling implemented a Gibbs sampler for a ZIP model, whereas @ katoBayesianApproachInequality2006 presented a Gibbs sampler to estimate a model with inequality constraints using truncated normal distributions.
-We would like to put together the two methods in order to estimate a ZIP model with inequality constraints on the parameters.
-
-We first consider the Gibbs sampler without constraints. Subsequently we discuss how to introduce the inequality constraints.
-
-#### Conditional Posterior Distributions
-
-In order to define the Gibbs sampler we need the joint posterior distribution from which to obtain the conditional distribution of each parameter.
-Let's define the elements of the posterior distribution.
-
-#### Likelihood {-}
-
-The likelihood of the ZIP model is
-
-$$l(p,\lambda| \beta_p, \beta_{\lambda}, Y) = \prod_{y_i=0}\left[p_i + (1-p_i)e^{-\lambda_i}\right] \prod_{y_i\neq0}\left[ (1-p_i)\frac{\lambda_i^{y_i}e^{-\lambda_i}}{y_i!}\right]$$
-where $p_i$ and $\lambda_i$ are defined according to parameters vector $\beta_p$ and $\beta_{\lambda}$, respectively. In particular,
-$$
-p_i = \text{logit}^{-1}(X_i^T\beta_{p}),\\
-\lambda_i = \text{exp}(X_i^T\beta_{\lambda}).
-$$
-
-#### Prior{-}
-
-We can assume the same independent prior distribution for all parameters of $\beta_p$ and $\beta_{\lambda}$.
-
-$$\pi(\beta_p, \beta_{\lambda}) = \pi(\beta_p) \times \pi(\beta_{\lambda})$$
-For example we can assume
-$$
-\pi(\beta) \sim \mathcal{N}(0, \Sigma).
-$$
-
-#### Posterior{-}
-
-$$Pr(\beta_p, \beta_\lambda| Y) \propto l(p,\lambda| \beta_p, \beta_{\lambda}, Y) \times \pi(\beta_p, \beta_{\lambda_i})$$
-
-#### Conditional Posteriors
-
-Ok onde evitare di scrivere cavolate non mi metto a ottenere le distribuzioni condizionate.
-Ho trovato varie cose in internet, sembra abbastanza diretto ma sinceramente andrei alla cieca perchè gli esempi riguardano casi in cui non si fa la regressione di $\lambda_i$ e $p_i$.
-Quindi dato che si parla di conjugate priors e tante altre cose di cui sono assai ignorante, non riesco a capire se quelle soluzioni sono utilizzabili anche nel nostro caso direttamente.
-
-Nel lavoro di @rodriguez-yamEfficientGibbsSampling, inoltre, fanno una cosa strana nel senso che definiscono $\lambda = X\beta+\epsilon$ e oltre a mettere le prior sui parametri $\beta$ la mettono anche su $\lambda$.
-Non capisco:
-
-- perchè ci mettono il termine di errore $\epsilon$?
-- il fatto di mettere la prior anche su $\lambda$ è un loro modo strano per mettere la prior sul termine $\epsilon$?
-Dato che la distibuzione di $\lambda$ dovrebbe essere data dai $\beta$ e $\epsilon$.
-
-**Insomma la domanda è come ottengo le Conditional Posteriors Distributions da utilizzare nel Gibbs sampler?**
-
-#### Including Inequality Constraints
-
-To include inequality constraints in the model, @katoBayesianApproachInequality2006 sampled each $\beta_j$ from a truncated normal distribution with some lower bound $b$
-and upper bound $c$, set equal to the other parameters according to the constrains.
-In particular, they sampled first a value $i$ from a uniform distribution on the interval (0,1) and then taking $\beta_j = \Phi_{\beta_j}^{-1}[\Phi_{\beta_j}(b) + i(\Phi_{\beta_j}(c)- \Phi_{\beta_j}(b))]$, where $\Phi_{\beta_j}$ denotes the standard normal cumulative probability function of $\beta_j$ evaluated at the argument.
-
-Ook che so geroglifici?
-Immagino sia l'inversa di una distribuzione troncata...
-Comunque mi sembra una soluzione plausibile.
-Poi guardando le formule del loro gibbs sampling è tutto un casino.
-Ma sembra fattibile no?
-
-### Issue
-
-Vorrei poter stimare effettivamente i parametri del modello con i constraints per valutare quali sono gli effetti e non fermarmi al hypothesis testing con il BF.
-Penso che la soluzione del Gibbs sampling sia quella "più giusta" (o meno sbagliata ;) ) perchè quella con STAN non capisco bene se è realmente fattibile o meno.
-
-Il problema resta che comunque non saprei come ricavarmi le distribuzioni condizionate delle posteriro da usare per il Gibbs Sampling.
-
-Vorrei capire se
-
-1. Ha senso questo approccio?
-2. Come poter procedere per creare il Gibbs sampling con inequlaity constraints
-
-## brms
-
-```{r}
-summary(fit_int)
+  b[1] = b_gender;
+  b[2] = db_mother[1];
+  b[3] = db_mother[2];
+  b[4] = b[2] + db_mother[3];
+}
 ```
 
-```{r}
-brms::conditional_effects(fit_int, ask= FALSE)
+Now we can proceed to compute all the elements of the bayes Factor.
+
+#### Prior
+
+We defined used as prior for all the parameters of interest a normal distribution with mean zero and standard deviation 5: $\mathcal{N}(0, 5)$.
+
+Thus, the resulting prior is a multivariate normal distribution with vector mean all equal to zero and covariance matrix a diagonal matrix with values 25.
+
+```{r, echo = TRUE}
+prior_mean <- c(0, 0, 0)
+prior_cov <- diag(3) * 25
 ```
 
-### Prior
+- **Prior Density Equality Constraints**  is computed as
+```{r, echo = TRUE}
+prior_den_eq <- mvtnorm::dmvnorm(x = 0,
+                                 mean = prior_mean[2],
+                                 sigma = as.matrix(prior_cov[2,2]))
+prior_den_eq
+```
+
+- **Prior Conditional Probability of Inequality Constraints**  is computed as
+```{r, echo = TRUE}
+prior_cond_prob <- condMVNorm::pcmvnorm(
+  lower = rep(0,2), upper = rep(Inf,2),
+  mean = prior_mean, sigma = prior_cov,
+  dependent.ind=c(1, 3), given.ind=c(2), X.given = c(0))
+prior_cond_prob
+```
+
+#### Posterior
+
+Posterior for the large sample theory, can be approximated to a multivariate normal distribution. Thus we estimate vector mean and covariance from the posteriro sample.
 
 ```{r, echo = TRUE}
-brms::get_prior(brms::bf(
-      internalizing_sum ~ gender + cluster_mother + cluster_father,
-      zi ~ gender + cluster_mother + cluster_father),
-      data = data_cluster,
-      family = brms::zero_inflated_poisson())
+post_H1 <- as.matrix(fit_H1, pars = c("db_mother[1]", "db_mother[2]", "db_mother[3]"))
+post_mean <- apply(post_H1, 2, mean)
+post_cov <- cov(post_H1)
 ```
 
+To evaluate normal approximation consider the following plot:
+
+```{r, plot-normal-approx}
+
+data_plot <- data.frame(db_mother_1 = post_H1[,1],
+                        db_mother_2 = post_H1[,2])
+mu <- apply(post_H1,2, mean)[c(1,2)]
+cov <- cov(post_H1[, c(1,2)])
+
+data_grid <- expand.grid(s_1 = seq(0, .35, length.out=100), s_2 = seq(-.1, .25, length.out=100))
+q_samp <- cbind(data_grid, prob = mvtnorm::dmvnorm(data_grid, mean = mu, sigma = cov))
+
+ggplot(data_plot) +
+  geom_density_2d(aes(x=db_mother_1, y=db_mother_2)) +
+  geom_contour(data = q_samp, aes(x=s_1, y=s_2, z=prob), col = "black")+
+  theme_bw()
+
+```
+
+- **Posterior Density Equality Constraints**  is computed as
+```{r, echo = TRUE}
+post_den_eq <- mvtnorm::dmvnorm(x = 0,
+                                mean = post_mean[2],
+                                sigma = as.matrix(post_cov[2,2]))
+post_den_eq
+```
+
+- **Posterior Conditional Probability of Inequality Constraints**  is computed as
+```{r, echo = TRUE}
+post_cond_prob <- condMVNorm::pcmvnorm(
+  lower = rep(0,2), upper = rep(Inf,2),
+  mean = post_mean, sigma = post_cov,
+  dependent.ind=c(1, 3), given.ind=c(2), X.given = c(0))
+post_cond_prob
+```
+
+#### Resulting Bayes Factor
+
+Thus to obtain the Bayes Factor
+
+```{r, echo = TRUE}
+BF_H1 <- (post_den_eq * post_cond_prob) / (prior_den_eq * prior_cond_prob)
+BF_H1
+```
+
+The Bayes Factor is in favour of our Hypothesis. Note that this was expected as I selected hypothesis 
+$$\text{Mother-Secure} = \text{Mother-Avoidonat} < \text{Mother-Anxious} < \text{Mother-Anxious-Avoidant}$$
+looking to the model estimates
+```{r}
+brms::conditional_effects(brm_int_mother, effects = "mother")
+```
+
+### Considerations
+
+So the method seems to work properly. I will try other hypothesis.
+
+The limit of this approach is that we compare hypotheses but we do not estimate the actual effect. No posterior of the constrained models are obtained!
+
 # References {-}

### 2021-07-02 Documents/Report-Project/Report-analysis.Rmd
revision analysis internalizing

@@
 
-# Cluster
-drake::loadd(cluster_mother_tat)
-drake::loadd(cluster_father_tat)
-drake::loadd(data_cluster_tat)
-drake::loadd(mclust_mother)
-drake::loadd(mclust_father)
-
-# brms models
-drake::loadd(fit_int)
 ```
@@
 
+# TODO
+
+## Bayes Factor Encompassing Priors
+
+- [ ] Reparametrize model according to: 
+\begin{align}
+&\beta_{eq} = R_{eq}\theta - r_{eq},\\
+&\beta_{ineq} = R_{ineq}\theta - r_{ineq}.
+\end{align}
+Doing this we get informative hypotheses as $H_i: \beta_{eq} = 0,\ \beta_{ineeq}>0$, so prior specification is semplified and with simmetric prior we do  not favoir any constraint.
+Exception for range constraints of type $a<\theta<b$.
+
+- [X] Marginal densities of a multivariate normal distribution are obtained simply dropping irreleevantt variables ([link math-stackexchange](https://math.stackexchange.com/questions/2528201/find-the-marginal-distributions-pdfs-of-a-multivariate-normal-distribution))
 # References

### 2021-07-02 Analysis/Analysis_Drake.R

@@ -21,7 +21,7 @@ drake::vis_drake_graph(config, font_size = 16, targets_only = FALSE)
 #----    Make    ----
 
 # Delate the analysis results
-# drake::clean(destroy = TRUE)
+# drake::clean('brm_ext_mother', destroy = TRUE)
 
 # Run the analysis
 drake::make(prework = "devtools::load_all()",
@@ -81,8 +81,9 @@ summary(fit_int_zip)
 rcompanion::nagelkerke(fit_int_zip)
 #---- brms models ----
 
-drake::loadd(waic_weights)
-drake::loadd(loo_weights)
+# internalizing
+drake::loadd(waic_weights_int)
+drake::loadd(loo_weights_int)
 
 drake::loadd(brm_int_mother)
 
@@ -91,6 +92,18 @@ plot(brm_int_mother)
 plot(brms::conditional_effects(brm_int_mother), ask = FALSE)
 
 brms::pp_check(brm_int_mother, nsamples = 100)
+
+# Externalizing
+drake::loadd(waic_weights_ext)
+drake::loadd(loo_weights_ext)
+
+drake::loadd(brm_ext_mother)
+
+summary(brm_ext_mother)
+plot(brm_ext_mother)
+plot(brms::conditional_effects(brm_ext_mother), ask = FALSE)
+
+brms::pp_check(brm_ext_mother, nsamples = 100)
 
 #---- BF encompassing priors ----
 

### 2021-07-02 Bayes_Factor.R

@@ -2,12 +2,12 @@ library(rstan)
 options(mc.cores = 4)
 rstan_options(auto_write = TRUE)
 
-stan_data <- make_stan_data(data_cluster)
+stan_data <- make_stan_data(data_cluster, formula = list("gender + mother", "gender"))
 fit_H1 <- stan(file = "Stan/ZIP-model-H1.stan", data = stan_data)
 
 round(summary(fit_H1)$summary[, "mean"],2)
 
-round(brms::posterior_summary(brm_int_additive)[, "Estimate"],2)
+round(brms::posterior_summary(brm_int_mother)[, "Estimate"],2)
 
 post_H1 <- as.matrix(fit_H1, pars = c("db_mother[1]", "db_mother[2]", "db_mother[3]"))
 
@@ -50,3 +50,17 @@ post_cond_prob <- condMVNorm::pcmvnorm(
 BF_H1 <- (post_den_eq * post_cond_prob) / (prior_den_eq * prior_cond_prob)
 
 #----
+stan_data <- make_stan_data(data_cluster, formula = list("cluster_mother * cluster_father", "gender"))
+fit_int <- stan(file = "Stan/ZIP-model.stan", data = stan_data)
+
+plot(fit_int)
+traceplot(fit_int, pars = "b_zi")
+#----
+
+fit_int_zip = pscl::zeroinfl(externalizing_sum ~ gender + cluster_mother * cluster_father,
+                             dist = "poisson", data = data_cluster)
+car::Anova(fit_int_zip)
+summary(fit_int_zip)
+rcompanion::nagelkerke(fit_int_zip)
+
+

### 2021-07-02 R/Clusters.R

@@ -26,21 +26,42 @@ get_data_cluster <- function(data, cluster_mother_fit, cluster_father_fit){
   cluster_mother_lev <- as.factor(cutree(cluster_mother_fit, k=4))
   cluster_father_lev <- as.factor(cutree(cluster_father_fit, k=4))
 
+  levels_interaction <- c(
+    'M_Secure_F_Secure',
+    'M_Secure_F_Anxious',
+    'M_Secure_F_Avoidant',
+    'M_Secure_F_Anxious_avoidant',
+    'M_Anxious_F_Secure',
+    'M_Anxious_F_Anxious',
+    'M_Anxious_F_Avoidant',
+    'M_Anxious_F_Anxious_avoidant',
+    'M_Avoidant_F_Secure',
+    'M_Avoidant_F_Anxious',
+    'M_Avoidant_F_Avoidant',
+    'M_Avoidant_F_Anxious_avoidant',
+    'M_Anxious_avoidant_F_Secure',
+    'M_Anxious_avoidant_F_Anxious',
+    'M_Anxious_avoidant_F_Avoidant',
+    'M_Anxious_avoidant_F_Anxious_avoidant'
+    )
+
   data_cluster <- cbind(data,
-                        cluster_mother = cluster_mother_lev,
-                        cluster_father = cluster_father_lev) %>%
-    mutate(cluster_mother = fct_recode(cluster_mother,
-                                       secure = "1",
-                                       anxious = "2",
-                                       anxious_avoidant = "3",
-                                       avoidant = "4"),
-           cluster_mother = fct_relevel(cluster_mother,
-                                        c("secure", "anxious", "avoidant", "anxious_avoidant")),
-           cluster_father = fct_recode(cluster_father,
-                                       secure = "1",
-                                       anxious = "2",
-                                       avoidant = "3",
-                                       anxious_avoidant = "4")) %>%
+                        mother = cluster_mother_lev,
+                        father = cluster_father_lev) %>%
+    mutate(mother = fct_recode(mother,
+                               Secure = "1",
+                               Anxious = "2",
+                               Anxious_avoidant = "3",
+                               Avoidant = "4"),
+           mother = fct_relevel(mother,
[…]

### 2021-07-02 R/Models.R

@@ -6,8 +6,13 @@
 
 zip_brms <- function(data, y, formula){
 
-  formula_lambda <- paste0("internalizing_sum ~ ", formula)
-  formula_zi <- paste0("zi ~ ", formula)
+  if(!is.list(formula)){
+    formula <- list(formula,
+                    formula)
+  }
+
+  formula_lambda <- paste0(y ," ~ ", formula[[1]])
+  formula_zi <- paste0("zi ~ ", formula[[2]])
 
   fit <- brms::brm(brms::bf(as.formula(formula_lambda),
                             as.formula(formula_zi)),
@@ -51,10 +56,16 @@ get_rel_weights <- function(..., ic = c("waic", "loo")){
 
 #----    make_stan_data    ----
 
-make_stan_data <- function(data){
+make_stan_data <- function(data, formula = "mother + father"){
+
+  if(!is.list(formula)){
+    formula <- list(formula,
+                    formula)
+  }
+
   formula <-  brms::bf(
-    internalizing_sum ~ cluster_mother + cluster_father,
-    zi ~ cluster_mother + cluster_father)
+    as.formula(paste0("internalizing_sum ~ ", formula[[1]])),
+    as.formula(paste0("zi ~ ", formula[[2]])))
 
   formula <- brms:::validate_formula(formula, data = data, family = brms::zero_inflated_poisson(),
                                      autocor = NULL, sparse = NULL, cov_ranef = NULL)

### 2021-07-02 R/Munge_data.R

@@ -13,7 +13,7 @@ munge_data <- function(data){
   data <- data %>%
     rename("gender" = "genere") %>%
     mutate_at(c("externalizing_sum", "internalizing_sum"), round, 0) %>%
-    select(c("ID","externalizing_sum", "internalizing_sum", "gender",
+    select(c("ID","externalizing_sum", "internalizing_sum", "gender", "age_year",
              starts_with(c("o_ecr", "Av", "Anx"))))
 
   return(data)

### 2021-07-02 R/Plan.R

@@ -33,53 +33,87 @@ get_analysis_plan <- function(){
 
     # mclust check
     mclust_mother = mclust_BIC(data = data_munged,
-                               class = data_cluster$cluster_mother,
+                               class = data_cluster$mother,
                                parent = "mother"),
     mclust_father = mclust_BIC(data = data_munged,
-                               class = data_cluster$cluster_father,
+                               class = data_cluster$father,
                                parent = "father"),
 
     #----    ZIP analysis    ----
-    fit_int_poisson = glm(internalizing_sum ~ cluster_mother * cluster_father,
+    fit_int_poisson = glm(internalizing_sum ~ gender + mother * father,
                           data = data_cluster, family = "poisson"),
     test_zero_inflated = performance::check_zeroinflation(fit_int_poisson),
 
     #----    anova approach ----
-    fit_int_zip = pscl::zeroinfl(internalizing_sum ~ cluster_mother * cluster_father,
+    fit_int_zip = pscl::zeroinfl(internalizing_sum ~ gender + mother * father| gender,
                                  dist = "poisson", data = data_cluster),
 
-    #----    brms Models    ----
+    #----    brms Models int    ----
     brm_int_zero = zip_brms(data = data_cluster,
                             y = "internalizing_sum",
-                            formula = "1"),
+                            formula = list("gender",
+                                           "gender")),
     brm_int_mother = zip_brms(data = data_cluster,
                               y = "internalizing_sum",
-                              formula = "cluster_mother"),
+                              formula = list("gender + mother",
+                                             "gender")),
     brm_int_additive = zip_brms(data = data_cluster,
                                 y = "internalizing_sum",
-                                formula = "cluster_mother + cluster_father"),
-
-    # brm_int_interaction = zip_brms(data = data_cluster,
-    #                                y = "internalizing_sum",
-    #                                formula = "cluster_mother * cluster_father"),
+                                formula = list("gender + mother + father",
+                                               "gender")),
+    brm_int_inter = zip_brms(data = data_cluster,
+                                y = "internalizing_sum",
+                                formula = list("gender + mother * father",
+                                               "gender")),
 
     # stan_data = make_stan_data(data = data_cluster)
 
-    waic_weights = get_rel_weights(brm_int_zero,
-                                   brm_int_mother,
-                                   brm_int_additive, ic = "waic"),
[…]

### 2021-07-12 Bayes_Factor.R
test not supported bayes factor

@@ -3,7 +3,7 @@ options(mc.cores = 4)
 rstan_options(auto_write = TRUE)
 
 stan_data <- make_stan_data(data_cluster, formula = list("gender + mother", "gender"))
-fit_H1 <- stan(file = "Stan/ZIP-model-H1.stan", data = stan_data)
+fit_H3 <- stan(file = "Stan/ZIP-model-H2.stan", data = stan_data)
 
 round(summary(fit_H1)$summary[, "mean"],2)
 
@@ -62,5 +62,56 @@ fit_int_zip = pscl::zeroinfl(externalizing_sum ~ gender + cluster_mother * clust
 car::Anova(fit_int_zip)
 summary(fit_int_zip)
 rcompanion::nagelkerke(fit_int_zip)
+
+#----- non supported hypothesis -----
+
+# prior density equality
+prior_den_eq <- mvtnorm::dmvnorm(x = c(0),
+                                 mean = prior_mean[c(1)],
+                                 sigma = as.matrix(prior_cov[c(1),c(1)]))
+dnorm(0, 0, 5)
+
+# posterior density equality
+post_den_eq <- mvtnorm::dmvnorm(x = c(0),
+                                mean = post_mean[c(1)],
+                                sigma = as.matrix(post_cov[c(1),c(1)]))
+
+ggplot(data.frame(x = 0:1)) +
+  stat_function(fun = dnorm, args = list(mean = 0, sd =5)) +
+  stat_function(fun = dnorm, args = list(mean = post_mean[c(1)], sd = sqrt(post_cov[c(1),c(1)]))) +
+  xlim(-.1,.1) +
+  ylim(0, .25)
+
+# prior conditional probability
+prior_cond_prob <- condMVNorm::pcmvnorm(
+  lower = rep(-Inf, 2), upper = rep(0,2),
+  mean = prior_mean, sigma = prior_cov,
+  dependent.ind=c(2, 3), given.ind=c(1), X.given = c(0))
+
+# posterior conditional probability
+post_cond_prob <- condMVNorm::pcmvnorm(
+  lower = rep(-Inf, 2), upper = rep(0,2),
+  mean = post_mean, sigma = post_cov,
+  dependent.ind=c(2, 3), given.ind=c(1), X.given = c(0))
+
+
+data_plot <- data.frame(db_mother_2 = post_H1[,2],
[…]

### 2021-07-12 R/Plan.R

@@ -107,6 +107,7 @@ get_analysis_plan <- function(){
     #----    BF encompassing priors    ----
 
     stan_data = make_stan_data(data_cluster, formula = list("gender + mother", "gender")),
+
     fit_H1 = stan(file = "Stan/ZIP-model-H1.stan", data = stan_data),
     # prior_spec = brms::set_prior("normal(0,5)", class = c("b"), dpar = c("", "zi")),
     # prior_model = brms::brm(brms::bf(internalizing_sum ~ cluster_mother + cluster_father,

### 2021-07-22 Documents/Report-Project/Formalize-hypotheses.Rmd
Report formalization hypothesis

---
title: 'Formalizing Hypothsis'
author: 'CZC, TM, PDC & GA'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2: 
    toc: true
    toc_depth: 3
    toc_float: true
    collapsed: false
    css: ["css/custom.css"]
linestretch: 1.5
number_sections: true
bibliography: "../Biblio-attachment.bib"
csl: apa.csl
link-citations: true 
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
library(tidyverse)
library(kableExtra)
```

In this report we present an example of the formalization of informative hypotheses according to the main Attachment theories. First, we present the hypothesis considering the attachment according to cluster. Subsequently, we consider attachment using continuous measures of anxiety and avoidance.

# Cluster Approach

Considering **Mother Attachment** we have the following groups:

1. $M_S$ - Secure
2. $M_{Ax}$ - Anxious
3. $M_{Av}$ - Avoidant
4. $M_F$ - Fearful

Considering **Father Attachment** we have the following groups:

1. $P_S$ - Secure
2. $P_{Ax}$ - Anxious
3. $P_{Av}$ - Avoidant
4. $P_F$ - Fearful

In the analysis, we evaluate **Externalizing Problems** according to gender and the interaction between **Mother** and **Father Attachment**:

$$
Ext \sim Gender + Mother\_Att \times Father\_Att
$$
Considering Mother and Father Attachment, there are 16 different combinations:

1. $M_SP_S$ - Mother Secure e Father Secure
1. $M_SP_{Ax}$ - Mother Secure e Father Anxious
1. $M_SP_{Av}$ - Mother Secure e Father Avoidant
1. $M_SP_F$ - Mother Anxious e Father Fearful
1. $M_{Ax}P_S$ - Mother Anxious e Father Secure
1. $M_{Ax}P_{Ax}$ - Mother Anxious e Father Anxious
1. $M_{Ax}P_{Av}$ - Mother Anxious e Father Avoidant
1. $M_{Ax}P_F$ - Mother Avoidant e Father Fearful
1. $M_{Av}P_S$ - Mother Avoidant e Father Secure
1. $M_{Av}P_{Ax}$ - Mother Avoidant e Father Anxious
1. $M_{Av}P_{Av}$ - Mother Avoidant e Father Avoidant
1. $M_{Av}P_F$ - Mother Secure e Father Fearful
1. $M_FP_S$ - Mother Fearful e Father Secure
1. $M_FP_{Ax}$ - Mother Fearful e Father Anxious
1. $M_FP_{Av}$ - Mother Fearful e Father Avoidant
1. $M_FP_F$ - Mother Fearful e Father Fearful

## Null Theory

This is a reference hypothesis whrer Mother and Father Attachment are expecteed to have no effect.

$$
M_* = 0\\
P_* = 0
$$

```{r}
data_null <- data.frame(Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
                        Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                        Score = 0.05)

ggplot(data_null) +
  geom_bar(aes(x = Attachment, y = Score, fill = Parent), stat = "identity", show.legend = FALSE) +
  ylim(0, 1) +
  facet_grid(Parent ~ .) +
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())
```

#### Combined effect {-}

```{r}
data_null_grid <- expand.grid(Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                                Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")))

data_null_grid$Problems <- c(0.05)

ggplot(data_null_grid) +
  geom_tile(aes(x = Father, y = Mother, fill = Problems), col = "gray10") +
  scale_fill_gradient(low = "white", high = "firebrick", limits = c(0,1),
                      breaks=c(0,1), labels = c("Low", "High")) +
  theme_bw()

```

## Monotorpy Theory

According to the Monotorpy theory, father attachment is expected to have no effect. Considering mother attachment, instead, we expect secure children to have the lowest level of problems. Anxious and avoidant children are expected to have similar levels of problems. Fearful children are xpected to have the highest levels of problems.

$$
M_S < M_{Ax} = M_{Av} < M_F\\
P_* = 0
$$

```{r}
data_monotropy <- data.frame(Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
                        Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                        Score = c(0.05, 0.5, 0.5, 1, rep(0.05, 4)))

ggplot(data_monotropy) +
  geom_bar(aes(x = Attachment, y = Score, fill = Parent), stat = "identity", show.legend = FALSE) +
  ylim(0, 1) +
  facet_grid(Parent ~ .) +
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())
```

#### Combined effect {-}

```{r}
data_monotropy_grid <- expand.grid(Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                                Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")))

data_monotropy_grid$Problems <- rep(c(0.05, 0.5, 0.5, 1), 4)

ggplot(data_monotropy_grid) +
  geom_tile(aes(x = Father, y = Mother, fill = Problems), col = "gray10") +
  scale_fill_gradient(low = "white", high = "firebrick", limits = c(0,1),
                      breaks=c(0,1), labels = c("Low", "High")) +
  theme_bw()

```

## Hierarchical Theory

Considering hierarchical theory, father attachment is expected to influence the outcome in the same way as mother attachment but with a minor role.

<!-- $$ -->
<!-- M_SP_S < M_SP_{Ax} = M_SP_{Av} < M_{Ax}P_S = M_{Av}P_S < M_{Ax}P_{Ax} = M_{Ax}P_{Av} =  M_{Av}P_{Ax} = M_{Av}P_{Av} < M_FP_S <  M_FP_{Ax} =  M_FP_{Av} <  M_FP_F -->
<!-- $$ -->

$$
M_S < M_{Ax} = M_{Av} < M_F\\
P_S < P_{Ax} = P_{Av} < P_F\\
P_* < M_*
$$

```{r}
data_hierarchy <- data.frame(Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
                        Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                        Score = c(0.05, 0.5, 0.5, 1, 0.05, 0.25, 0.25, .5))

ggplot(data_hierarchy) +
  geom_bar(aes(x = Attachment, y = Score, fill = Parent), stat = "identity", show.legend = FALSE) +
  ylim(0, 1) +
  facet_grid(Parent ~ .) +
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())
```

#### Combined effect {-}

```{r}
data_hierarchy_grid <- expand.grid(Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                                Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")))

data_hierarchy_grid$Problems <- rep(c(0.05, 0.5, 0.5, 1), 4) + rep(c(0.05, 0.25, 0.25, .5), each = 4)

ggplot(data_hierarchy_grid) +
  geom_tile(aes(x = Father, y = Mother, fill = Problems), col = "gray10") +
  scale_fill_gradient(low = "white", high = "firebrick", limits = c(0,1.5),
                      breaks=c(0,1.5), labels = c("Low", "High")) +
  theme_bw()

```

## Independent Theory

Considering independent theory, Mother and father attachment are expected to affect children outcomes differently. In this case, we considered Avoidant attachemnt towards the father as a condition of hiegher risk.

<!-- $$ -->
<!-- M_SP_S < M_SP_{Ax} = M_SP_{Av} < M_{Ax}P_S = M_{Av}P_S < M_{Ax}P_{Ax} = M_{Ax}P_{Av} =  M_{Av}P_{Ax} = M_{Av}P_{Av} < M_FP_S <  M_FP_{Ax} =  M_FP_{Av} <  M_FP_F -->
<!-- $$ -->

$$
M_S < M_{Ax} = M_{Av} < M_F\\
P_S < P_{Ax} < P_{Av} = P_F\\
$$

```{r}
data_independent <- data.frame(Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
                        Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                        Score = c(0.05, 0.5, 0.5, 1, 0.05, 0.5, 1, 1))

ggplot(data_independent) +
  geom_bar(aes(x = Attachment, y = Score, fill = Parent), stat = "identity", show.legend = FALSE) +
  ylim(0, 1) +
  facet_grid(Parent ~ .) +
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())
```

#### Combined effect {-}

```{r}
data_independent_grid <- expand.grid(Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                                Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")))

data_independent_grid$Problems <- rep(c(.05, .5, .5, 1), 4) + rep(c(.05, .5, 1, 1), each = 4)

ggplot(data_independent_grid) +
  geom_tile(aes(x = Father, y = Mother, fill = Problems), col = "gray10") +
  scale_fill_gradient(low = "white", high = "firebrick", limits = c(0,2),
                      breaks=c(0,2), labels = c("Low", "High")) +
  theme_bw()

```

## Interaction Theory

Considering interaction theory, mother and father attachment are expected to interact. In this case, we consider Secure attachemnt as a protectivee factor and  fearful attachment as a risk condition.

$$
M_SP_S< \{M_SP_{Ax;Av};\ M_{Ax;Av}P_S\} < \{ M_SP_F;\  M_FP_S\} < M_{Ax;Av}P_{Ax;Av} <  \{M_FP_{Ax;Av};\ M_{Ax;Av}P_F\} <  M_FP_F
$$

```{r}
data_interaction <- expand.grid(Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                                Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")))

data_interaction$Score <- c(.05, .15, .15, .40,
                            .10, .50, .50, .90,
                            .10, .50, .50, .90,
                            .40, .90, .90, 1.0)

ggplot(data_interaction) +
  geom_tile(aes(x = Mother, y = Father, fill = Score), col = "gray10") +
  scale_fill_gradient(low = "white", high = "firebrick", limits = c(0,1),
                      breaks=c(0,1), labels = c("Low", "High")) +
  theme_bw()

```

# Continuos Approach

Attachment is measured considering continuous values on the **Anxiety** and **Avoidance** scale. Thus, considering **Mother attachment** we have:

- `Anxm` - Anxiety
- `Avm` - Avoidance

Whereas, considering **Father Attachment** we have:

- `Anxp` - Anxiety
- `Avp` - Avoidance

Cosidering the model with the **four-way interaction** between all attachment measures:

$$
Externalizing \sim gender + Anxm \times Avm \times Anxp \times Avp
$$

we have the following parameters regarding attachment measures

```{r}
model_formula <- formula(externalizing_sum ~ gender + Anxm * Avm * Anxp * Avp , data = data_cluster)
attr(terms.formula(model_formula), "term.labels")[-1]
```

In particular we have:

```{r}
table_terms <- tibble(Term = attr(terms.formula(model_formula), "term.labels")[-1])
kable(table_terms, col.names =  NULL) %>%
  pack_rows("Main Effect", 1,4) %>%
  pack_rows("Two-way interaction", 5,10) %>%
  pack_rows("Three-way interaction", 11,14) %>%
  pack_rows("Four-way interaction", 15,15) %>%
  kable_paper("hover", full_width = F)

```

## Null Theory

This is a reference hypothesis where Mother and Father Attachment are expected to have no effect. So we set all parameters to *zero*.

$$
Anx* = 0\\
Av* = 0
$$

```{r}
my_seq <- seq(0, 1, length.out = 20)

data_continuous <- expand.grid(Anxm = my_seq,
                               Avm = my_seq,
                               Anxp = my_seq,
                               Avp = my_seq)
```

```{r, out.width="100%", fig.width = 10, fig.height = 4}

data_null <- data_continuous %>%
  select(Anxm, Avm) %>%
  distinct() %>%
  mutate(Problems = 0 * Anxm + 0 *  Avm)

p1 <- ggplot(data_null) +
  geom_tile(aes(x = Anxm, y = Avm, fill = Problems)) +
  scale_fill_gradient(low = "white", high = "firebrick", limits = c(-.2,2),
                      breaks=c(-.2,2), labels = c("Low", "High")) +
  ggtitle("Mother") +
  theme_bw()

data_null <- data_continuous %>%
  select(Anxp, Avp) %>%
  distinct() %>%
  mutate(Problems = 0 * Anxp + 0 *  Avp)

p2 <- ggplot(data_null) +
  geom_tile(aes(x = Anxp, y = Avp, fill = Problems)) +
  scale_fill_gradient(low = "white", high = "firebrick", limits = c(-.2,2),
                      breaks=c(-0.2,2), labels = c("Low", "High")) +
  ggtitle("Father") +
  theme_bw()

gridExtra::grid.arrange(p1, p2, nrow = 1)
```

## Monotorpy Theory

According to the Monotropy theory, father attachment is expected to have no effect so we set all parameters regarding father to zero. Considering mother attachment, instead, we expect `Anxm` and `Avm` to be positive ad with the same value (children with higher levels of anxiety or avoidance are expected to have more problems). Moreover, we also expect the interaction terms `Anxm:Avm` to be positive (children with higher levels of on both anxiety and avoidance are expected to have even more problems).

$$
Anxm = Avm > 0\\
Anxm:Avm > 0\\~
\\
Anxp = 0\\
Avp = 0
$$
```{r, out.width="100%", fig.width = 10, fig.height = 4}
data_monotropy <- data_continuous %>%
  select(Anxm, Avm) %>%
  distinct() %>%
  model.matrix(~ Anxm*Avm, .) %>%
  as.data.frame() %>%
  mutate(Problems =  1 * Anxm + 1 *  Avm + 1 * `Anxm:Avm`)

p1 <- ggplot(data_monotropy) +
  geom_tile(aes(x = Anxm, y = Avm, fill = Problems)) +
  scale_fill_gradient(low = "white", high = "firebrick", 
                      limits = c(0,3), 
                      breaks=c(0,3), labels = c("Low", "High"))+
  geom_contour(aes(x=Anxm, y=Avm, z=Problems), col = "black")+
  ggtitle("Mother") +
  theme_bw()

data_monotropy <- data_continuous %>%
  select(Anxp, Avp) %>%
  distinct() %>%
  mutate(Problems = 0 * Anxp + 0 *  Avp)

p2 <- ggplot(data_monotropy) +
  geom_tile(aes(x = Anxp, y = Avp, fill = Problems)) +
  scale_fill_gradient(low = "white", high = "firebrick", limits = c(-.2,2),
                      breaks=c(-0.2,2), labels = c("Low", "High")) +
  ggtitle("Father")+
  theme_bw()

gridExtra::grid.arrange(p1, p2, nrow = 1)
```

## Hierarchical Theory

Considering hierarchical theory, father attachment is expected to influence the outcome in the same way as mother attachment but with a minor role. 
Thus we expect  `Anxm`, `Avm`, `Anxp`, and `Avm` to be positive (children with higher levels of anxiety or avoidance are expected to have more problems). Moreover, we also expect the interaction terms `Anxm:Avm` and `Anxp:Avp` to be positive (children with higher levels of on both anxiety and avoidance are expected to have even more problems). Hoewer, parameters related to father are somller than th respective one referring to mother.

$$
Anxm = Avm > Anxp = Avp > 0\\
Anxm:Avm > Anxp:Avp > 0\\~
$$

```{r, out.width="100%", fig.width = 10, fig.height = 4}
data_hierarchical <- data_continuous %>%
  select(Anxm, Avm) %>%
  distinct() %>%
  model.matrix(~ Anxm*Avm, .) %>%
  as.data.frame() %>%
  mutate(Problems =  1 * Anxm + 1 *  Avm + 1 * `Anxm:Avm`)

p1 <- ggplot(data_hierarchical) +
  geom_tile(aes(x = Anxm, y = Avm, fill = Problems)) +
  scale_fill_gradient(low = "white", high = "firebrick", 
                      limits = c(0,3), 
                      breaks=c(0,3), labels = c("Low", "High"))+
  geom_contour(aes(x=Anxm, y=Avm, z=Problems), col = "black")+
  ggtitle("Mother") +
  theme_bw()

data_hierarchical <- data_continuous %>%
  select(Anxp, Avp) %>%
  distinct() %>%
  model.matrix(~ Anxp*Avp, .) %>%
  as.data.frame() %>%
  mutate(Problems =  .5 * Anxp + .5 *  Avp + .5 * `Anxp:Avp`)

p2 <- ggplot(data_hierarchical) +
  geom_tile(aes(x = Anxp, y = Avp, fill = Problems)) +
  scale_fill_gradient(low = "white", high = "firebrick", 
                      limits = c(0,3), 
                      breaks=c(0,3), labels = c("Low", "High"))+
  geom_contour(aes(x=Anxp, y=Avp, z=Problems), col = "black")+
  ggtitle("Father") +
  theme_bw()

gridExtra::grid.arrange(p1, p2, nrow = 1)
```

## Independent Theory

Considering independent theory, Mother and father attachment are expected to affect children outcomes differently. In this case, we considered Avoidant attachemnt towards the father as a condition of higher risk. Thus we set:

$$
Anxm = Avm > 0\\
Anxm:Avm > 0 \\~
\\
Anxp > Avp > 0\\
Anxp:Avp > 0\\
$$

```{r, out.width="100%", fig.width = 10, fig.height = 4}
data_independent <- data_continuous %>%
  select(Anxm, Avm) %>%
  distinct() %>%
  model.matrix(~ Anxm*Avm, .) %>%
  as.data.frame() %>%
  mutate(Problems =  1 * Anxm + 1 *  Avm + 1 * `Anxm:Avm`)

p1 <- ggplot(data_independent) +
  geom_tile(aes(x = Anxm, y = Avm, fill = Problems)) +
  scale_fill_gradient(low = "white", high = "firebrick", 
                      limits = c(0,3), 
                      breaks=c(0,3), labels = c("Low", "High"))+
  geom_contour(aes(x=Anxm, y=Avm, z=Problems), col = "black")+
  ggtitle("Mother") +
  theme_bw()

data_independent <- data_continuous %>%
  select(Anxp, Avp) %>%
  distinct() %>%
  model.matrix(~ Anxp*Avp, .) %>%
  as.data.frame() %>%
  mutate(Problems =  .7 * Anxp + 1.8 *  Avp + .5 * `Anxp:Avp`)

p2 <- ggplot(data_independent) +
  geom_tile(aes(x = Anxp, y = Avp, fill = Problems)) +
  scale_fill_gradient(low = "white", high = "firebrick", 
                      limits = c(0,3), 
                      breaks=c(0,3), labels = c("Low", "High"))+
  geom_contour(aes(x=Anxp, y=Avp, z=Problems), col = "black")+
  ggtitle("Father") +
  theme_bw()

gridExtra::grid.arrange(p1, p2, nrow = 1)
```

## Interaction Theory

Considering interaction theory, mother and father attachment are expected to interact. In this case, we consider low levels on both Anxiety and Avoidance with at least one parent (secure attachemnt) as a protective factor and  high levels on both Anxiety and Avoidance with at least one parent (fearful attachemnt) as a risk condition.

<!-- Thus, we set -->
<!-- $$ -->
<!-- Anxm = Avm > 0\\ -->
<!-- Anxm:Avm > 0 \\~ -->
<!-- \\ -->
<!-- Anxp > Avp > 0\\ -->
<!-- Anxp:Avp > 0 -->
<!-- $$ -->

<!-- Then we set, -->
<!-- $$ -->
<!-- Anxm:Anxp = 0\\ -->
<!-- Avm:Anxp = 0\\ -->
<!-- Anxm:Avp = 0\\ -->
<!-- Avm:Avp = 0 -->
<!-- $$ -->
<!-- to say that the combination of high level of anxiety in one parent and high level of avoidance in the other parent do not increase the risk of problems. -->

#### Note{-} 
Sinceramente qui non saprei come gestire i parametri meglio la definizione dei parametri e rapprsntarli graficamnte. Già negli altri modelli i termini di intrazione non sono poi così diretti da interpretare, nel caso delle interazioni fino a quattro viee diventa un bel casino.

## Summary

```{r}
summary <- table_terms %>%
  mutate(Null = "= 0",
         Monotropy = c("= Avm > 0", "= Anxm > 0", rep( "= 0", 2), "> 0", rep( "= 0", 10)),
         Hierarchical = c("= Avm > Avp", "= Anxm > Anxp", "= Avp > 0", "= Anxp > 0", 
                          "> Anxp:Avp",rep( "= 0", 4), "> 0", rep( "= 0", 5)),
         Independent = c("= Avm > 0", "= Anxm > 0", "> 0", "> Anxp", 
                          "> 0",rep( "= 0", 4), "> 0", rep( "= 0", 5)),
         Interaction = c("= Avm > 0", "= Anxm > 0", "> 0", "> Anxp", 
                          "> 0",rep( "?", 4), "> 0", rep( "?", 5)))
kable(summary, col.names =  c(" ", "Null", "Monotropy", "Hierarchical", "Independent", "Interaction")) %>%
  pack_rows("Main Effect", 1,4) %>%
  pack_rows("Two-way interaction", 5,10) %>%
  pack_rows("Three-way interaction", 11,14) %>%
  pack_rows("Four-way interaction", 15,15) %>%
  kable_paper("hover", full_width = F)
```

### 2021-07-29 Documents/Report-Project/Attachment_Analysis_Report.Rmd
Update report with int e ext

@@
 title: 'Attachment Analysis: Report Project'
-author: 'CZC, TM & GA'
+author: 'CZC, TM, PDC & GA'
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
 
-# Data
-drake::loadd(raw_data)
-drake::loadd(data_munged)
-drake::loadd(data_cluster)
+drake_load_all()
 
-# Cluster
-drake::loadd(cluster_mother_fit)
-drake::loadd(cluster_father_fit)
-
-drake::loadd(mclust_mother)
-drake::loadd(mclust_father)
-
-# ZIP anlaysis
-drake::loadd(fit_int_poisson)
-
-# ANOVA
-drake::loadd(fit_int_zip)
-
-# brms models
-drake::loadd(brm_int_mother)
-drake::loadd(waic_weights_int)
-drake::loadd(loo_weights_int)
-
-# BF encompassing
-drake::loadd(fit_H1)
 ```
 
-In this report, preliminary results of the analysis are presented considering as dependent variable internalizing problems.
-Note the actual paper will consider externalizing problems, instead.
-(**Spoiler**: with externalizing problems models present more interesting results.
-However, here we used internalizing problems as an example to introduce the analysis method avoiding to influence the subsequent expert elicitation regarding externalizing problems).
+In this report, results of the analysis evaluating attachment theories are presented.
+In Section TODO, the aim of the analysis is discussed and descriptive statistics are presented together with the cluster analysis used to classify attachment.
+Subsequently, results of the analysis are presented separately for internalizing problems (See Section TODO) and externalizing problems (See Section TODO).
 
@@
 
-## Backgorund
+## Aim of the Analysis
 
@@
 1. **Hierarchical Theory** -  the mother is more important than the father
-1. **Independent Theory** - mother and father affect different area of children development
+1. **Independent Theory** - mother and father affect children development differently
 1. **Interaction Theory** - mother and father interact
 
-Here we evaluate as dependent variable:
+We evaluate as dependent variable:
 
-- **Internalizing Problems** - given by the sum of the SDQ (*Strengths & Difficulties Questionnaires*)
+- **Internalizing Problems** (`internalizing_sum`) - given by the sum of the SDQ (*Strengths & Difficulties Questionnaires*)
+- ****Externalizing Problems** (`externalizing_sum`) - given by the sum of the SDQ (*Strengths & Difficulties Questionnaires*)
 
@@
 
-- **Gender** - children gender
-- **Mother Attachment** - considering clusters obtained from the ECR questionnaire
-- **Father Attachment** - considering clusters obtained from the ECR questionnaire
+- **Gender** (`gender`) - children gender
+- **Mother Attachment** (`mother`) - considering clusters obtained from the ECR questionnaire (See Section TODO)
+- **Father Attachment** (`father`) - considering clusters obtained from the ECR questionnaire (See Section TODO)
 
-## Analysis Plan
+### Statistical Approach
 
@@
 
-1. Tradition ANOVA analysis. (Note that actually is Analysisi of Deviance)
+1. Tradition ANOVA analysis (Note that actually is Analysis of Deviance)
 1. Bayesian Model Comparison
@@
 
-In all cases, Zero Inflated Poisson (*ZIP*) models were used to take into account the distribution characteristics of the dependent variable. This issue is discussed below.
+In all cases, Zero Inflated Negative Binomial (*ZINB*) models were used to take into account the distribution characteristics of the dependent variable. *ZINB* models are defined as:
 
-# Descriptive Statistics
+$$
+y_i \sim ZINegative Binomial(p_i, \mu_i)
+$$
 
-The sample size is:
+Where, $p_i$ is the probability of an observation $y_i$ being an extra zero (i.e., a zero not comming from the poisson distribution) and $1 - p_i$ indicates the probability of given observation $y_i$ being generated from a Negative Binomial distribution with mean $\mu_i$.
+In particular,
+
+$$
+p_i = \text{logit}^{-1}(X_i^T\beta_{p}),\\
+\mu_i = \text{exp}(X_i^T\beta_{\mu}).
+$$
+
+That is, we want to model both $p_i$ and $\mu_i$ according to a set of independent variables. Thus we have to estimate parameters vector $\beta_p$ and $\beta_{\mu}$ respectively.
+
+In particular we considered as predictors:
+
+```{r, echo = TRUE, eval = FALSE}
+# formula for p
+p ~ gender
+
+# formula for mu
+mu ~ gender + ...
+```
+
+That is, we model the probability ($p_i$) of an observation being zero or coming from a Negative Binomial distribution according to `gender`.
+Whereas, we model the Negative Binomial mean ($\mu_i$) according to `gender` and other variables combination between `mother` and `father`.
+
+## Bayes Factor  Encompassing Prior Approach
+
+Here we describe the Bayes Factor  Encompassing Prior Approach.
+
+With this approach we can explicit equality and order constraints between parameters.We need first to define the hypothesis, estimate the encompassing model and than compute the Bayes Factor.
+
+### Informative Hypotesis
+
+A given Hypothesis can be expressed as:
+$$
+H_i:\ R_E\theta = r_E,\  R_I\theta > r_I
+$$
+Where, $R_E$ is a matrix indicating equality constraints and $r_E$ is a vector with the equality values.
+Whereas $R_I$ is a matrix indicating inequality constraints and $r_I$ is a vector with the inequality values.
+For example, consider a model with 3 parameters ($\theta_1,\ \theta_2,\ \theta_3$) and the following constraints $0<\theta_1 < \theta_2 < \theta_3;\ \theta_4 = 2$.
+In this case we would have:
+$$
+R_E = \begin{pmatrix} 0 &  0 & 0 & 1\end{pmatrix}; r_E = \begin{pmatrix} 2\end{pmatrix}\\
+R_I = \begin{pmatrix} 1 &  0 & 0 & 0 \\
+                     -1 &  1 & 0 & 0 \\
+                      0 & -1 & 1 & 0\end{pmatrix}; r_I = \begin{pmatrix}0\\ 0\\ 0\end{pmatrix}\\
+$$
+### Encompassing Model
+
+In order to compare informative hypothesis, we define an unconstrained model considered as reference with encompassing priors that are uninformative with respect to the parameters.
+All other models are nested in this model and the priors ore obtained by restricting the parameter space in accordance with the constraints imposed by each hypothesis.
+
+As an example, consider an encompassing model with prior for all the parameters of interest are defined as normal distribution with mean zero and standard deviation 3: $\theta\sim\mathcal{N}(0, 3)$.
+
+#### Paramter Transformation
+
+To guarantee that the prior specification does not favor any constraints, it is necessary to transform the parameters of the model as follow:
+
+$$
+\begin{aligned}
+&\beta_{E} = R_{E}\theta - r_{E},\\
+&\beta_{I} = R_{I}\theta - r_{I}.
+\end{aligned}
+$$
+
+These allows us to express the constraints as
+
+$$
+H_i: \beta_{E} = 0,\ \beta_{I}>0
+$$
+
+so prior specification is simplified (they are all centered to zero, focal point of interest) and with symmetric priors we do  not favor any constraint.
+
+Considering the constrains of the previous example:
+$$
+0<\theta_1 < \theta_2 < \theta_3;\ \theta_4 = 5
+$$
+we would transform parameters as follow
+
+$$
+\beta_E = R_E\theta-r_E =\begin{pmatrix} 0 &  0 & 0 & 1\end{pmatrix}\theta - (2) = \theta_4 - 5\\
+\beta_I = R_I\theta-r_I =\begin{pmatrix} 1 &  0 & 0 & 0 \\
+                     -1 &  1 & 0 & 0 \\
+                      0 & -1 & 1 & 0\end{pmatrix}\theta - \begin{pmatrix}0\\ 0\\ 0\end{pmatrix} =
+                      \begin{pmatrix}\theta_1\\
+                      \theta_2 - \theta_1\\
+                      \theta_3 - \theta_2\end{pmatrix}
+$$
+So wee can express the constraints as
+
+$$
+\begin{aligned}
+&\beta_1 = \theta_4 - 2 = 0\\
+&\beta_2 = \theta_1 > 0\\
+&\beta_3 = \theta_2 - \theta_1 > 0\\
+&\beta_4 = \theta_3 - \theta_2 > 0
+\end{aligned}
+$$
+
+Note that we are applying a linear transformation to the model parameters, thus the new parameter vector $\beta$ is obtained as $\beta = R\theta-r$ with covariance matrix $\Sigma_{\beta} = R\Sigma_{\theta}R^T$.
+This requires the matrix $R = \left[R_E \\ R_I\right]$ to be full-rank.
+If this is not the case a possible solution is to consider in the transformation the maximum number of linearly independent rows and obtain the remaining constraints as linear compositions.
+
+Moreover, to compare different hypothesis is necessary that they are comparable.
+That is, the intersection of their constrained regions is not empty, allowing a common solution that can be used as prior mean.
+(TODO: describe in more details)
+
+### Computing Bayes Factor
+
+Now we can compute the Bayes Factor between an informative hypothesis ($M_i$) and the unconstrained model ($M_u$) as
+
+$$
+\begin{aligned}
+BF_{iu} = \frac{Pr(\text{Inequality Const} | \text{Equality Const}, \text{Data})}{\pi_u(\text{Inequality Const} | \text{Equality Const})} &\frac{Pr(\text{Equality Const}| \text{Data})}{\pi_u( \text{Equality Const})} = \\ \\  \frac{Pr(R_I\theta > r_I | R_E\theta = r_E, Y)}{\pi_u(R_I\theta > r_I | R_E\theta = r_E)} &\frac{Pr(R_E\theta = r_E| Y)}{\pi_u( R_E\theta = r_E)}.
+\end{aligned}
+$$
+
+Where, the first part is a ratio between conditional posterior and conditional prior **probabilities** that the inequality constraints hold under $M_u$.
+The second part is a ratio between  marginal posterior and marginal prior **densities** of the equality constraints under $M_u$, the well-known *Savage–Dickey density ratio*.
+
+#### Prior
+
+Considering the encompassing model of the previous example with priors $\theta\sim\mathcal{N}(0, 3)$.
+Thus, the resulting prior is a multivariate normal distribution with vector mean all equal to zero and covariance matrix a diagonal matrix with values 9.
+
+```{r, echo = TRUE}
+prior_mean <- c(0, 0, 0, 0)
+prior_cov <- diag(4) * 3^2
+```
+
+First we need to transform the parameter in order to center the prior on the focal points of interest:
+
+```{r, echo = TRUE}
+R <- matrix(c( 0, 0, 0, 1,
+               1, 0, 0, 0,
+              -1, 1, 0, 0,
+               0,-1, 1, 0), ncol = 4, byrow = TRUE) # Hypothesis matrix
+r <- c(2, 0, 0, 0) # constrain values
+
+prior_mean_transf <-  R %*% prior_mean - r
+prior_cov_transf <- R %*% prior_cov %*% t(R)
+```
+
+- **Prior Density Equality Constraints** - is computed considering the parameters with equality constrains (in the example $\beta_1$) using the function `mvtnorm::dmvnorm()`:
+```{r, echo = TRUE}
+prior_den_eq <- mvtnorm::dmvnorm(x = 0,
+                                 mean = prior_mean_transf[1],
+                                 sigma = as.matrix(prior_cov_transf[1,1]))
+```
+
+- **Prior Conditional Probability of Inequality Constraints**  - is computed fixing the parameters with equality constrains (in the example $\beta_1$) and considering the parameters with inequality constraints (in the example $\beta_2, \beta_3, \beta_4$) using the function `condMVNorm::pcmvnorm()`:
+```{r, echo = TRUE}
+prior_cond_prob <- condMVNorm::pcmvnorm(
+  lower = rep(0,3), upper = rep(Inf,3),
+  mean = prior_mean_transf, sigma = prior_cov_transf,
+  dependent.ind= 2:4, given.ind=1, X.given = 0)
+```
+
+#### Posterior
+
+Posterior for the large sample theory, can be approximated to a multivariate normal distribution. Thus we estimate vector mean and covariance from the posterior sample.
+
+```{r, echo = TRUE, eval = FALSE}
+post_H1 <- as.matrix(fit_H1, pars = c("theta[1]", "theta[2]", "theta[3]", "theta[4]"))
+post_mean <- apply(post_H1, 2, mean)
+post_cov <- cov(post_H1)
+```
+
+Again, we transform parameters in order to center constraints on the focal points of interest:
+
+```{r, echo = TRUE, eval = FALSE}
+post_mean_transf <-  R %*% post_mean - r
+post_cov_transf <- R %*% post_cov %*% t(R)
+```
+
+- **Posterior Density Equality Constraints**  is computed considering the parameters with equality constrains (in the example $\beta_1$) using the function `mvtnorm::dmvnorm()`:
+```{r, echo = TRUE,  eval = FALSE}
+post_den_eq <- mvtnorm::dmvnorm(x = 0,
+                                mean = post_mean[2],
+                                sigma = as.matrix(post_cov[2,2]))
+```
+
+- **Posterior Conditional Probability of Inequality Constraints**  is computed fixing the parameters with equality constrains (in the example $\beta_1$) and considering the parameters with inequality constraints (in the example $\beta_2, \beta_3, \beta_4$) using the function `condMVNorm::pcmvnorm()`:
+```{r, echo = TRUE,  eval = FALSE}
+post_cond_prob <- condMVNorm::pcmvnorm(
+  lower = rep(0,2), upper = rep(Inf,2),
+  mean = post_mean, sigma = post_cov,
+  dependent.ind=c(1, 3), given.ind=c(2), X.given = c(0))
+```
+
+Now we have all the coponents to compute the Bayes Factor
+```{r, echo = TRUE,  eval = FALSE}
+(post_den_eq * post_cond_prob) / (prior_den_eq * prior_cond_prob)
+```
+
+## Informative Hypotesis Attachment Theories
+
+Now we consider how to formalize the theoretical perspectives on the role of mother and father attachment.
+
+Considering **Mother Attachment** we have the following groups (See Section TODO):
+
+1. $M_S$ - Secure
+2. $M_{Ax}$ - Anxious
+3. $M_{Av}$ - Avoidant
+4. $M_F$ - Fearful
+
+Considering **Father Attachment** we have the following groups (See Section TODO):
+
+1. $F_S$ - Secure
+2. $F_{Ax}$ - Anxious
+3. $F_{Av}$ - Avoidant
+4. $F_F$ - Fearful
+
+Considering the interaction between Mother and Father Attachment, there are 16 different combinations:
+
+1. $M_SF_S$ - Mother Secure e Father Secure
+1. $M_SF_{Ax}$ - Mother Secure e Father Anxious
+1. $M_SF_{Av}$ - Mother Secure e Father Avoidant
+1. $M_SF_F$ - Mother Anxious e Father Fearful
+1. $M_{Ax}F_S$ - Mother Anxious e Father Secure
+1. $M_{Ax}F_{Ax}$ - Mother Anxious e Father Anxious
+1. $M_{Ax}F_{Av}$ - Mother Anxious e Father Avoidant
+1. $M_{Ax}F_F$ - Mother Avoidant e Father Fearful
+1. $M_{Av}F_S$ - Mother Avoidant e Father Secure
+1. $M_{Av}F_{Ax}$ - Mother Avoidant e Father Anxious
+1. $M_{Av}F_{Av}$ - Mother Avoidant e Father Avoidant
+1. $M_{Av}F_F$ - Mother Secure e Father Fearful
+1. $M_FF_S$ - Mother Fearful e Father Secure
+1. $M_FF_{Ax}$ - Mother Fearful e Father Anxious
+1. $M_FF_{Av}$ - Mother Fearful e Father Avoidant
+1. $M_FF_F$ - Mother Fearful e Father Fearful
+
+We formalize the main theoretical perspectives as follows:
+
+#### Null Theory
+
+This is a reference hypothesis where Mother and Father Attachment are expected to have no effect.
+
+$$
+M_* = 0\\
+F_* = 0
+$$
+
+```{r}
+data_null <- data.frame(Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
+                        Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+                        Score = 0.05)
+
+ggplot(data_null) +
+  geom_bar(aes(x = Attachment, y = Score, fill = Parent), stat = "identity", show.legend = FALSE) +
+  ylim(0, 1) +
+  facet_grid(Parent ~ .) +
+  theme_bw() +
+  theme(axis.title.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        axis.text.y = element_blank())
+```
+
+Combined effect
+
+```{r}
+data_null_grid <- expand.grid(Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+                                Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")))
+
+data_null_grid$Problems <- c(0.05)
+
+ggplot(data_null_grid) +
+  geom_tile(aes(x = Father, y = Mother, fill = Problems), col = "gray10") +
+  scale_fill_gradient(low = "white", high = "firebrick", limits = c(0,1),
+                      breaks=c(0,1), labels = c("Low", "High")) +
+  theme_bw()
+
+```
+
+#### Monotorpy Theory
+
+According to the Monotorpy theory, father attachment is expected to have no effect.
+Considering mother attachment, instead, we expect secure children to have the lowest level of problems.
+Anxious and avoidant children are expected to have similar levels of problems.
+Fearful children are expected to have the highest levels of problems.
+
+$$
+M_S < M_{Ax} = M_{Av} < M_F\\
+F_* = 0
+$$
+
+```{r}
+data_monotropy <- data.frame(Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
+                        Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+                        Score = c(0.05, 0.5, 0.5, 1, rep(0.05, 4)))
+
+ggplot(data_monotropy) +
+  geom_bar(aes(x = Attachment, y = Score, fill = Parent), stat = "identity", show.legend = FALSE) +
+  ylim(0, 1) +
+  facet_grid(Parent ~ .) +
+  theme_bw() +
+  theme(axis.title.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        axis.text.y = element_blank())
+```
+
+Combined effect
+
+```{r}
+data_monotropy_grid <- expand.grid(Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+                                Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")))
+
+data_monotropy_grid$Problems <- rep(c(0.05, 0.5, 0.5, 1), 4)
+
+ggplot(data_monotropy_grid) +
+  geom_tile(aes(x = Father, y = Mother, fill = Problems), col = "gray10") +
+  scale_fill_gradient(low = "white", high = "firebrick", limits = c(0,1),
+                      breaks=c(0,1), labels = c("Low", "High")) +
+  theme_bw()
+
+```
+
+#### Hierarchical Theory
+
+Considering hierarchical theory, father attachment is expected to influence the outcome in the same way as mother attachment but with a minor role.
+
+$$
+M_S < M_{Ax} = M_{Av} < M_F\\
+F_S < F_{Ax} = F_{Av} < F_F\\
+F_* < M_*
+$$
+
+```{r}
+data_hierarchy <- data.frame(Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
+                        Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+                        Score = c(0.05, 0.5, 0.5, 1, 0.05, 0.25, 0.25, .5))
+
+ggplot(data_hierarchy) +
+  geom_bar(aes(x = Attachment, y = Score, fill = Parent), stat = "identity", show.legend = FALSE) +
+  ylim(0, 1) +
+  facet_grid(Parent ~ .) +
+  theme_bw() +
+  theme(axis.title.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        axis.text.y = element_blank())
+```
+
+Combined effect
+
+```{r}
+data_hierarchy_grid <- expand.grid(Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+                                Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")))
+
+data_hierarchy_grid$Problems <- rep(c(0.05, 0.5, 0.5, 1), 4) + rep(c(0.05, 0.25, 0.25, .5), each = 4)
+
+ggplot(data_hierarchy_grid) +
+  geom_tile(aes(x = Father, y = Mother, fill = Problems), col = "gray10") +
+  scale_fill_gradient(low = "white", high = "firebrick", limits = c(0,1.5),
+                      breaks=c(0,1.5), labels = c("Low", "High")) +
+  theme_bw()
+
+```
+
+#### Independent Theory
+
+Considering independent theory, Mother and father attachment are expected to affect children outcomes differently.
+In this case, we considered Avoidant attachemnt towards the father as a condition of hiegher risk.
+
+$$
+M_S < M_{Ax} = M_{Av} < M_F\\
+F_S < F_{Ax} < F_{Av} < F_F\\
+$$
+
+```{r}
+data_independent <- data.frame(Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
+                        Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+                        Score = c(.05, .5, .5, 1, .05, .25, .75, 1))
+
+ggplot(data_independent) +
+  geom_bar(aes(x = Attachment, y = Score, fill = Parent), stat = "identity", show.legend = FALSE) +
+  ylim(0, 1) +
+  facet_grid(Parent ~ .) +
+  theme_bw() +
+  theme(axis.title.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        axis.text.y = element_blank())
+```
+
+Combined effect
+
+```{r}
+data_independent_grid <- expand.grid(Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+                                Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")))
+
+data_independent_grid$Problems <- rep(c(.05, .5, .5, 1), 4) + rep(c(.05, .30, .75, 1), each = 4)
+
+ggplot(data_independent_grid) +
+  geom_tile(aes(x = Father, y = Mother, fill = Problems), col = "gray10") +
+  scale_fill_gradient(low = "white", high = "firebrick", limits = c(0,2),
+                      breaks=c(0,2), labels = c("Low", "High")) +
+  theme_bw()
+
+```
+
+#### Interaction Theory
+
+Considering interaction theory, mother and father attachment are expected to interact. In this case, we consider Secure attachment as a protective factor and  fearful attachment as a risk condition. 
+$$
+M_SF_S< \{M_SF_{Ax;Av} = M_{Ax;Av}F_S\} < M_{Ax;Av}F_{Ax;Av} <  \{M_FF_{Ax;Av} = M_{Ax;Av}F_F\} <  M_FF_F
+$$
+
+With,
+$$
+M_{Ax}F_{Ax} = M_{Ax}F_{Av} = M_{Av}F_{Ax} = M_{Av}F_{Av}
+$$
+
+```{r}
+data_interaction <- expand.grid(Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+                                Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")))
+
+data_interaction$Score <- c(.05, .15, .15, NA,
+                            .10, .50, .50, .90,
+                            .10, .50, .50, .90,
+                            NA, .90, .90, 1.0)
+
+ggplot(data_interaction) +
+  geom_tile(aes(x = Mother, y = Father, fill = Score), col = "gray10") +
+  scale_fill_gradient(low = "white", high = "firebrick", limits = c(0,1),
+                      breaks=c(0,1), labels = c("Low", "High")) +
+  theme_bw()
+
+```
+
+Note that we do not specify the conditions $M_SF_F$ and $M_FF_S$ as their frequency is very low (around 1% of the sample).
+
+## Descriptive Statistics
+
+In the analysis children in the middle childhood were considered. Seven children were excluded from the analysis as they were older (failed in school). The sample size is:
 
@@
 ```{r, echo = TRUE}
-summary(raw_data$age_year)
-sd(raw_data$age_year, na.rm = TRUE)
+summary(data_cluster$age_year)
+sd(data_cluster$age_year, na.rm = TRUE)
 ```
@@
 ```{r, plot-age}
-ggplot(raw_data) +
+ggplot(data_cluster) +
   geom_histogram(aes(x = age_year), col = "grey40", fill = "#00BFC4") +
@@
 
-Children school grade frequancy
+Children school grade frequency
 
 ```{r}
-table(raw_data$classe)
+table_grade(data_raw)
 ```
@@
 
-## Dependent Variable
-
-### Internalizing
+# Internalizing Problems
 
@@
 
-Considering the distribution of internalizing scores it seems that there is an inflation of zero. To evaluate that we fit a poisson model and we compare the number of observed zero and expected zero.
+Considering the distribution of internalizing scores it seems that there is an inflation of zeros.
+To evaluate this, we fit a **negative binomial** model and we compare the number of observed zero and expected zero.
 
@@
 # model formula
-internalizing_sum ~ gender + cluster_mother * cluster_father
+internalizing_sum ~ gender + mother * father
 ```
@@
 ```{r, echo = TRUE}
-fit_int_poisson
+fit_int_nb
 ```
@@
 ```{r, echo = TRUE}
-performance::check_zeroinflation(fit_int_poisson)
+performance::check_zeroinflation(fit_int_nb)
 ```
 
-Results indicate that the model is underfitting zeros. Thus in the analysis we will use a Zero inflated Poisson (*ZIP*) model.
+Results indicate that the model is slightly  under-fitting the number of zeros. We can now try to fit a Zero Inflated Negative Binomial (*ZINB*) model and compare the performance of the two.
 
-# Statistical Analysis
-
-In all subsequent analysis we considered Zero Inflated Poisson (ZIP) models:
-
-$$
-y_i \sim ZIPoisson(p_i, \lambda_i)
-$$
-
-Where, $p_i$ is the probability of an observation $y_i$ being an extra zero (i.e., a zero not comming from the poisson distribution) and $1 - p_i$ indicates the probability of given observation $y_i$ being generated from a Poisson distribution with mean $\lambda_i$.
-In particular,
-
-$$
-p_i = \text{logit}^{-1}(X_i^T\beta_{p}),\\
-\lambda_i = \text{exp}(X_i^T\beta_{\lambda}).
-$$
-
-That is, we want to model both $p_i$ and $\lambda_i$ according to a set of independent variables.
-Thus we have to estimate parameters vector $\beta_p$ and $\beta_{\lambda}$ respectively.
-Note that these are the only parameters in the model.
-
-In particular we considered as predictors:
-
-```{r, echo = TRUE, eval = FALSE}
-# formula for p
-p ~ gender
-
-# formula for lambda
-lambda ~ gender + ...
+```{r, echo = TRUE}
+pscl::vuong(fit_int_nb, fit_int_zinb)
 ```
 
-That is, we model the probability ($p_i$) of an observation being zero or coming from a poisson distribution according to `gender`.
-Whereas, we model the poisson mean ($\lambda_i$) according to `gender` and other variables among `cluster_mother` and `cluster_father`.
+From the result we can see that *ZINB* model performs slightly better but there is not clear indication about which model is better.
+Nevertheless, in the following section we decide to continue to use *ZINB* models.
 
@@
 
-In our case we fit a model considering the interaction between `cluster_mother` and `cluster_father`. That is:
+In our case we fit a model considering the interaction between `mother` and `father`. That is:
 ```{r, echo = TRUE, eval = FALSE}
@@
 
-# formula for lambda
-lambda ~ gender + mother * father
+# formula for mu
+mu ~ gender + mother * father
 ```
@@
 ```{r, echo = TRUE}
-car::Anova(fit_int_zip)
+car::Anova(fit_int_zinb)
 ```
 
-In this case we get that the interaction is significant. Thus results support the **Interaction Theory**.
+In this case we get that there are no significant effects.
 
@@
 ```{r, echo = TRUE}
-summary(fit_int_zip)
+summary(fit_int_zinb)
 ```
@@
 ```{r, echo = TRUE}
-rcompanion::nagelkerke(fit_int_zip)
+rcompanion::nagelkerke(fit_int_zinb)
 ```
 
-**TODO** - plot of the effects (below are effects from the normal poisson model)
+Plot of the effects
 
-```{r, plot-ANOVA-effects}
-plot(effects::effect(mod = fit_int_poisson, term = "mother * father"))
+```{r, plot-ANOVA-effects-ints}
+plot(plot_zinb_int)
 ```
@@
 
-The problem here is to evaluate which are the actual differences of interests. Are we modeling relevant effects or random noise? We are not penalizing for complexity of the model.
-
-Moreover we are not comparing dirrectly the hypothesis of interest but just doing testing.
+The problem here is that we are no comparing and evaluating directly the hypothesis of interest.
+Moreover, p-value do not quantify evidence in favor of one hypothesis.
+To overcome this issue we consider the *Model Comparison Approach*.
 
@@
 
-We compare 4 models. In all models $p_i$ is predicted by gender, whereas predictors of $\lambda_i$ are selected according to the different hypothesis:
+Model comparison approach allows to formalize different models according the research hypothesis and to evaluate which is the most likely model according to the data among those considered.
+We compare 4 models.
+In all models $p_i$ is predicted by gender, whereas predictors of $\mu_i$ are selected according to the different hypothesis:
 
-1. `brm_int_zero`: $\lambda_i \sim$ `gender`
-1. `brm_int_mother`: $\lambda_i \sim$ `gender + mother`
-1. `brm_int_additive`: $\lambda_i \sim$ `gender + mother + father`
-1. `brm_int_inter`: $\lambda_i \sim$ `gender + mother * father`
+1. `brm_int_zero`: $\mu_i \sim$ `gender`
+1. `brm_int_mother`: $\mu_i \sim$ `gender + mother`
+1. `brm_int_additive`: $\mu_i \sim$ `gender + mother + father`
+1. `brm_int_inter`: $\mu_i \sim$ `gender + mother * father`
 
-Models were estimated using in `brms` using default prior settings.
+Note that in these models we included as random intercept the children classroom `(1|ID_class)`, to take into account the individual variability of teachers in evaluating children problems.
+The random intercept was included both as predictor of $p$ and $\mu$.
+
+Models were estimated following the Bayesian approach using `brms` with the default prior settings.
 
@@
 
-Plot effects
+Plot effects on $mu$:
 
-```{r, plot-effects-brm_int_mother}
+```{r, plot-effects-brm_int_mother-mu}
 plot(brms::conditional_effects(brm_int_mother), ask = FALSE)
+```
+
+Plots effects on `zi`:
+
+```{r, plot-effects-brm_int_mother-pi}
+plot(brms::conditional_effects(brm_int_mother, dpar = "zi"), ask = FALSE)
 ```
@@
 
-**TODO** - not really a good fit, clear sign of over-dispersion. Probably Negative binomial would be better than poisson.
+Now the fit of the model is good, the predicted values follow the distribution of the observed values.
 
-R squarded
+R squared:
 
@@
 
+Note that the value is much high due to the inclusion of the random effects.
+
 ### Considerations
 
-Overall fit is pretty bad. However, this approach allow us to define models according to research hypothesis and compare them taking into account model complexity.
+Overall the fit is pretty good. This approach allow us to define models according to research hypothesis and compare them taking into account model complexity.
 
-Using this approach, however, there is not a lot of formalization. For example we are not explicitying the expected direction of the effects or the expected order.
+Using this approach, however, there is not a lot of formalization.
+For example we are not expliciting the expected direction of the effects or the expected order.
+To overcome this limit we consider the Bayes Factor Encompassing Prior Approach.
 
-## Bayes Factor  Encompassin Prior Approach
+## Bayes Factor  Encompassing Prior Approach
 
-With this approach we can explicit equality and order constraints between parameters. Thus a given Hypothesis can be expressed as:
-$$
-H_i:\ R_E\theta = r_E,\  R_I\theta > r_I
-$$
+Now we evaluate the results of the Bayes Factor considering the informative hypothesis regarding attachment specified in Section TODO.
 
-In order to compare informative hypothesis, we define an unconstrained model considered as reference with encompassing priors that are uninformative with respect to the parameters.
-All other models are nested in this model and the priors ore obtained by restricting the parameter space in accordance with the constraints imposed by each model.
+### Encompassing Model
 
-Note that we first need to reparametrize the model as follow:
-\begin{align}
-&\beta_{eq} = R_{eq}\theta - r_{eq},\\
-&\beta_{ineq} = R_{ineq}\theta - r_{ineq}.
-\end{align}
-These allows as to express constraints as
-$$H_i: \beta_{eq} = 0,\ \beta_{ineeq}>0,$$ 
-so prior specification is simplified (they are all centered to zero) and with symmetric priors we do  not favor any constraint.
+As encompassing model we considered the model with the interaction between `mother` and `father` attachment, the additive effect of `gender`  and the random effect of `ID_class`.
+We  used as prior for all the parameters of interest a normal distribution with mean zero and standard deviation 3: $\theta\sim\mathcal{N}(0, 3)$.
 
-For example for a constraint of type:
-$$
-0<\theta_1<\theta_2<\theta_3
-$$
-we would define
-$$
-d\theta_2:= \theta_2 - \theta_1\\
-d\theta_3:= \theta_3 - \theta_2
-$$
-So wee can express constraints as
-$$
-\theta_1>0\\
-d\theta_2>0\\
-d\theta_3>0
-$$
-
-Subsequently we can compute the Bayes Factor between an informative hypothesis ($M_i$) and the unconstrain model ($M_u$) as
-
-\begin{aligned}
-BF_{iu} = \frac{Pr(\text{Inequality Const} | \text{Equality Const}, \text{Data})}{\pi_u(\text{Inequality Const} | \text{Equality Const})} &\frac{Pr(\text{Equality Const}| \text{Data})}{\pi_u( \text{Equality Const})} = \\ \\  \frac{Pr(R_I\theta > r_I | R_E\theta = r_E, Y)}{\pi_u(R_I\theta > r_I | R_E\theta = r_E)} &\frac{Pr(R_E\theta = r_E| Y)}{\pi_u( R_E\theta = r_E)}.
-\end{aligned}
-
-Where, the first part is a ratio between conditional posterior and conditional prior **probabilities** that the inequality constraints hold under $M_u$.
-The second part is a ratio between  marginal posterior and marginal prior **densities** of the equality constraints under $M_u$, the well-known *Savage–Dickey density ratio*.
-
-### Toy Example
-
-As an example consider these hypothesis considering mother attachment:
-
-$$\text{Mother-Secure} = \text{Mother-Avoidonat} < \text{Mother-Anxious} < \text{Mother-Anxious-Avoidant}$$
-Note that we do not define any constrain regarding the father (but we will do it in the actual application).
-
-For simplicity consider as encompassing model the model with only the mother and gender as predictor of $\lambda_i$ (actual application will consider the interaction model).
-Note that according to the used *treatment-contrast coding* we have:
-
-\begin{align}
-&intercept = \text{Mother-Secure Female}\\
-&\beta_1 = \text{Gender-Male}\\
-&\beta_2 = \text{Mother-Anxious}\\
-&\beta_3 = \text{Mother-Avoidonat}\\
-&\beta_4 = \text{Mother-Anxious-Avoidant}\\
-\end{align}
-
-So we re-parametrize the model as follow
-$$
-d\beta_4 := \beta_4 -\beta_2
-$$
-and the constraints we obtain are
-$$
-\beta_2 > 0\\
-\beta_3 = 0\\
-d\beta_4 > 0 
-$$
-Note that $\beta_1$ do not appear in the constraints so is considered as a nuisance parameter together with the intercepts and parameters referiing to $p_i$.
-
-Here the actual stan code for parameters and transformed parameter block (note a little bit of messing with indexing):
-```{stan output.var='priors', eval = FALSE, echo = TRUE}
-parameters {
-  // lambda regression parameters
-  real b_gender;
-  vector[3] db_mother; // order constraints mother
-  real Intercept;  // temporary intercept for centered predictors
-
-  // zi regression parameters
-  vector[Kc_zi] b_zi;  // population-level effects
-  real Intercept_zi;  // temporary intercept for centered predictors
-}
-transformed parameters {
-  vector[Kc] b;  // population-level effects
-
-  b[1] = b_gender;
-  b[2] = db_mother[1];
-  b[3] = db_mother[2];
-  b[4] = b[2] + db_mother[3];
-}
+```{r, echo = TRUE}
+brms::prior_summary(encompassing_model_int)
 ```
 
-Now we can proceed to compute all the elements of the bayes Factor.
+Thus, the resulting prior of the parameter of interest is a multivariate normal distribution with vector mean all equal to zero and covariance matrix a diagonal matrix with values 9.
 
-#### Prior
+### Bayes Factor Results
 
-We defined used as prior for all the parameters of interest a normal distribution with mean zero and standard deviation 5: $\mathcal{N}(0, 5)$.
-
-Thus, the resulting prior is a multivariate normal distribution with vector mean all equal to zero and covariance matrix a diagonal matrix with values 25.
-
+Table with the Bayes Factor (row/column):
 ```{r, echo = TRUE}
-prior_mean <- c(0, 0, 0)
-prior_cov <- diag(3) * 25
+round(table_BF_int, 2)
 ```
 
-- **Prior Density Equality Constraints**  is computed as
-```{r, echo = TRUE}
-prior_den_eq <- mvtnorm::dmvnorm(x = 0,
-                                 mean = prior_mean[2],
-                                 sigma = as.matrix(prior_cov[2,2]))
-prior_den_eq
+Bayes Factor weights
+
+```{r}
+BF_weights_int %>%
+  mutate_if(is.numeric, round, 2)
 ```
 
-- **Prior Conditional Probability of Inequality Constraints**  is computed as
-```{r, echo = TRUE}
-prior_cond_prob <- condMVNorm::pcmvnorm(
-  lower = rep(0,2), upper = rep(Inf,2),
-  mean = prior_mean, sigma = prior_cov,
-  dependent.ind=c(1, 3), given.ind=c(2), X.given = c(0))
-prior_cond_prob
+The hipotesis that is most supported by the data is the Monotropy Theory.
+
+### Prior Sensitivity
+
+The same analysis were conducted considering different prior settings:
+
+- $\mathcal{N}(0, .5)$ - unreasonably tight
+- $\mathcal{N}(0, 1)$ - tight 
+- $\mathcal{N}(0, 3)$ - default
+- $\mathcal{N}(0, 5)$ - wide 
+- $\mathcal{N}(0, 10)$ - unreasonably wide
+
+Results are reported below:
+
+```{r}
+summary_sensitivity_int %>%
+  mutate_if(is.numeric, round, 2) %>%
+  select(names, bf, weights) %>%
+  kable(.) %>%
+  kable_paper("hover", full_width = F) %>%
+  pack_rows("N(0, .5)", 1, 5) %>%
+  pack_rows("N(0, 1)", 6, 10) %>%
+  pack_rows("N(0, 3)", 11, 15) %>%
+  pack_rows("N(0, 5)", 16, 20) %>%
+  pack_rows("N(0, 10)", 21, 25) 
 ```
 
-#### Posterior
-
-Posterior for the large sample theory, can be approximated to a multivariate normal distribution. Thus we estimate vector mean and covariance from the posteriro sample.
-
-```{r, echo = TRUE}
-post_H1 <- as.matrix(fit_H1, pars = c("db_mother[1]", "db_mother[2]", "db_mother[3]"))
-post_mean <- apply(post_H1, 2, mean)
-post_cov <- cov(post_H1)
-```
-
-To evaluate normal approximation consider the following plot:
-
-```{r, plot-normal-approx}
-
-data_plot <- data.frame(db_mother_1 = post_H1[,1],
-                        db_mother_2 = post_H1[,2])
-mu <- apply(post_H1,2, mean)[c(1,2)]
-cov <- cov(post_H1[, c(1,2)])
-
-data_grid <- expand.grid(s_1 = seq(0, .35, length.out=100), s_2 = seq(-.1, .25, length.out=100))
-q_samp <- cbind(data_grid, prob = mvtnorm::dmvnorm(data_grid, mean = mu, sigma = cov))
-
-ggplot(data_plot) +
-  geom_density_2d(aes(x=db_mother_1, y=db_mother_2)) +
-  geom_contour(data = q_samp, aes(x=s_1, y=s_2, z=prob), col = "black")+
-  theme_bw()
-
-```
-
-- **Posterior Density Equality Constraints**  is computed as
-```{r, echo = TRUE}
-post_den_eq <- mvtnorm::dmvnorm(x = 0,
-                                mean = post_mean[2],
-                                sigma = as.matrix(post_cov[2,2]))
-post_den_eq
-```
-
-- **Posterior Conditional Probability of Inequality Constraints**  is computed as
-```{r, echo = TRUE}
-post_cond_prob <- condMVNorm::pcmvnorm(
-  lower = rep(0,2), upper = rep(Inf,2),
-  mean = post_mean, sigma = post_cov,
-  dependent.ind=c(1, 3), given.ind=c(2), X.given = c(0))
-post_cond_prob
-```
-
-#### Resulting Bayes Factor
-
-Thus to obtain the Bayes Factor
-
-```{r, echo = TRUE}
-BF_H1 <- (post_den_eq * post_cond_prob) / (prior_den_eq * prior_cond_prob)
-BF_H1
-```
-
-The Bayes Factor is in favour of our Hypothesis. Note that this was expected as I selected hypothesis 
-$$\text{Mother-Secure} = \text{Mother-Avoidonat} < \text{Mother-Anxious} < \text{Mother-Anxious-Avoidant}$$
-looking to the model estimates
-```{r}
-brms::conditional_effects(brm_int_mother, effects = "mother")
-```
+**TODO** - ragionare un po' su come interpretare il variare dei risultati con le differenti prior
 
@@
 
+# Externalizing Problems
+
+Distribution of externalizing problems
+```{r, plot-externalizing}
+ggplot(data_cluster) +
+  geom_bar(aes(x = externalizing_sum), col = "gray40", fill = "#F8766D", alpha = 0.7) +
+  theme_bw()
+```
+
+Externalizing according to gender
+
+```{r, plot-externalizing-gender}
+ggplot(data_cluster) +
+  geom_bar(aes(x = externalizing_sum, fill = gender), col = "gray40", 
+           alpha = 0.7, show.legend = FALSE) +
+  facet_grid(gender ~ .) +
+  theme_bw() 
+```
+
+#### Zero Inflation {-}
+
+Considering the distribution of externalizing scores it seems that there is an inflation of zeros.
+To evaluate this, we fit a **negative binomial** model and we compare the number of observed zero and expected zero.
+
+```{r, echo = TRUE, eval = FALSE}
+# model formula
+externalizing_sum ~ gender + mother * father
+```
+
+```{r, echo = TRUE}
+fit_ext_nb
+```
+
+```{r, echo = TRUE}
+performance::check_zeroinflation(fit_ext_nb)
+```
+
+Results indicate that the model is slightly under-fitting the number of zeros. We can now try to fit a Zero Inflated Negative Binomial (*ZINB*) model and compare the performance of the two.
+
+```{r, echo = TRUE}
+pscl::vuong(fit_ext_nb, fit_ext_zinb)
+```
+
+From the result we can see that *ZINB* model performs slightly better but there is not clear indication about which model is better.
+Nevertheless, in the following section we decide to continue to use *ZINB* models.
+
+## ANOVA Approach
+
+Classical approach is to fit the most complex model.
+Subsequently, ANOVA or likelihood ratio test are computed to evaluate the significance of the predictors.
+Finally, according to the results, researcher evaluate if hypothesis are supported or not.
+
+In our case we fit a model considering the interaction between `mother` and `father`. That is:
+```{r, echo = TRUE, eval = FALSE}
+# formula for p
+p ~ gender
+
+# formula for mu
+mu ~ gender + mother * father
+```
+
+Than we conduct an ANOVA using the `car`. Note that as we are using a GLM we are actually conducting an Analysis of Deviance.
+
+```{r, echo = TRUE}
+car::Anova(fit_ext_zinb)
+```
+
+In this case we get a significant effects of the gender and the mother.
+
+Summary of the model:
+```{r, echo = TRUE}
+summary(fit_ext_zinb)
+```
+
+R squared:
+
+```{r, echo = TRUE}
+rcompanion::nagelkerke(fit_ext_zinb)
+```
+
+Plot of the effects (TODO consider marginal effect only mother)
+
+```{r, plot-ANOVA-effects-ext}
+plot(plot_zinb_ext)
+```
+
+## Bayesian Model Comparison Approach
+
+We compare the same 4 models as for internalizing problems. In all models $p_i$ is predicted by gender, whereas predictors of $\mu_i$ are selected according to the different hypothesis:
+
+1. `brm_int_zero`: $\mu_i \sim$ `gender`
+1. `brm_int_mother`: $\mu_i \sim$ `gender + mother`
+1. `brm_int_additive`: $\mu_i \sim$ `gender + mother + father`
+1. `brm_int_inter`: $\mu_i \sim$ `gender + mother * father`
+
+Note that in these models we included as random intercept the children classroom `(1|ID_class)`, to take into account the individual variability of teachers in evaluating children problems.
+The random intercept was included both as predictor of $p$ and $\mu$.
+
+Models were estimated following the Bayesian approach using `brms` with the default prior settings.
+
+```{r, echo = TRUE}
+brms::prior_summary(brm_ext_mother)
+```
+
+Model comparison approach using waic index:
+
+```{r, echo = TRUE}
+waic_weights_ext
+```
+
+and loo index
+
+```{r, echo = TRUE}
+loo_weights_ext
+```
+
+The *preferred* model is the one considering only the role of mother attachment. Results support the **Monotropy Theory**.
+
+### `brm_int_mother`
+
+Model summary. Note that `brms` indicates $p_i$ with `zi`.
+
+```{r, echo = TRUE}
+summary(brm_ext_mother)
+```
+
+Plot effects on $mu$:
+
+```{r, plot-effects-brm_ext_mother-mu}
+plot(brms::conditional_effects(brm_ext_mother), ask = FALSE)
+```
+
+Plots effects on `zi`:
+
+```{r, plot-effects-brm_ext_mother-pi}
+plot(brms::conditional_effects(brm_ext_mother, dpar = "zi"), ask = FALSE)
+```
+
+Posterior Predictive Check
+```{r}
+brms::pp_check(brm_ext_mother, nsamples = 25)
+```
+
+Now the fit of the model is good, the predicted values follow the distribution of the observed values.
+
+R squared:
+
+```{r, echo = TRUE}
+brms::bayes_R2(brm_ext_mother)
+```
+
+Note that the value is much high due to the inclusion of the random effects.
+
+## Bayes Factor  Encompassing Prior Approach
+
+Now we evaluate the results of the Bayes Factor considering the informative hypothesis regarding attachment specified in Section TODO.
+
+### Encompassing Model
+
+As encompassing model we considered the model with the interaction between `mother` and `father` attachment, the additive effect of `gender`  and the random effect of `ID_class`.
+We  used as prior for all the parameters of interest a normal distribution with mean zero and standard deviation 3: $\theta\sim\mathcal{N}(0, 3)$.
+
+```{r, echo = TRUE}
+brms::prior_summary(encompassing_model_ext)
+```
+
+Thus, the resulting prior of the parameter of interest is a multivariate normal distribution with vector mean all equal to zero and covariance matrix a diagonal matrix with values 9.
+
+### Bayes Factor Results
+
+Table with the Bayes Factor (row/column):
+```{r, echo = TRUE}
+round(table_BF_ext, 2)
+```
+
+Bayes Factor weights
+
+```{r}
+BF_weights_ext %>%
+  mutate_if(is.numeric, round, 2)
+```
+
+The hipotesis that is most supported by the data is the Monotropy Theory.
+
+### Prior Sensitivity
+
+The same analysis were conducted considering different prior settings:
+
+- $\mathcal{N}(0, .5)$ - unreasonably tight
+- $\mathcal{N}(0, 1)$ - tight 
+- $\mathcal{N}(0, 3)$ - default
+- $\mathcal{N}(0, 5)$ - wide 
+- $\mathcal{N}(0, 10)$ - unreasonably wide
+
+Results are reported below:
+
+```{r}
+summary_sensitivity_ext %>%
+  mutate_if(is.numeric, round, 2) %>%
+  select(names, bf, weights) %>%
+  kable(.) %>%
+  kable_paper("hover", full_width = F) %>%
+  pack_rows("N(0, .5)", 1, 5) %>%
+  pack_rows("N(0, 1)", 6, 10) %>%
+  pack_rows("N(0, 3)", 11, 15) %>%
+  pack_rows("N(0, 5)", 16, 20) %>%
+  pack_rows("N(0, 10)", 21, 25) 
+```
+
+**TODO** - ragionare un po' su come interpretare il variare dei risultati con le differenti prior
+
 # References {-}

### 2021-07-29 Documents/Report-Project/Formalize-hypotheses.Rmd
Update report with int e ext

@@
 M_S < M_{Ax} = M_{Av} < M_F\\
-P_S < P_{Ax} < P_{Av} = P_F\\
+P_S < P_{Ax} < P_{Av} < P_F\\
 $$
@@
                                             levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
-                        Score = c(0.05, 0.5, 0.5, 1, 0.05, 0.5, 1, 1))
+                        Score = c(.05, .5, .5, 1, .05, .25, .75, 1))
 
@@
 
-data_independent_grid$Problems <- rep(c(.05, .5, .5, 1), 4) + rep(c(.05, .5, 1, 1), each = 4)
+data_independent_grid$Problems <- rep(c(.05, .5, .5, 1), 4) + rep(c(.05, .30, .75, 1), each = 4)
 
@@
 $$
-M_SP_S< \{M_SP_{Ax;Av};\ M_{Ax;Av}P_S\} < \{ M_SP_F;\  M_FP_S\} < M_{Ax;Av}P_{Ax;Av} <  \{M_FP_{Ax;Av};\ M_{Ax;Av}P_F\} <  M_FP_F
+M_SP_S< \{M_SP_{Ax;Av} = M_{Ax;Av}P_S\} < M_{Ax;Av}P_{Ax;Av} <  \{M_FP_{Ax;Av} = M_{Ax;Av}P_F\} <  M_FP_F
+$$
+
+With,
+$$
+M_{Ax}P_{Ax} = M_{Ax}P_{Av} = M_{Av}P_{Ax} = M_{Av}P_{Av}
 $$
@@
 
-data_interaction$Score <- c(.05, .15, .15, .40,
+data_interaction$Score <- c(.05, .15, .15, NA,
                             .10, .50, .50, .90,
                             .10, .50, .50, .90,
-                            .40, .90, .90, 1.0)
+                            NA, .90, .90, 1.0)
 

### 2021-07-29 Analysis/Analysis_Drake.R

@@ -169,6 +169,10 @@ drake::loadd(BF_interaction_ext)
 drake::loadd(table_BF_ext)
 drake::loadd(BF_weights_ext)
 
+# sensitivity
+drake::loadd(summary_sensitivity_ext)
+
+
 #===========================#
 
 

### 2021-07-29 R/Utils_report.R

@@ -1,0 +1,93 @@
+#=================================#
+#====    Utilities Report     ====#
+#=================================#
+
+#----    drake_load_all    ----
+
+load_glob_env <- function(...){
+  drake::loadd(..., envir = globalenv())
+}
+
+drake_load_all <- function(){
+  # Data
+  load_glob_env(data_raw)
+  load_glob_env(data_munged)
+  load_glob_env(data_cluster)
+
+  # Cluster
+  load_glob_env(cluster_mother_fit)
+  load_glob_env(cluster_father_fit)
+
+  load_glob_env(mclust_mother)
+  load_glob_env(mclust_father)
+
+  #----    Internalizing    ----
+
+  # ZINB anlaysis
+  load_glob_env(fit_int_nb)
+
+  # ANOVA
+  load_glob_env(fit_int_zinb)
+  load_glob_env(plot_zinb_int)
+
+  # brms models
+  load_glob_env(brm_int_mother)
+  load_glob_env(waic_weights_int)
+  load_glob_env(loo_weights_int)
+
+  # BF encompassing
+  load_glob_env(encompassing_model_int)
+  load_glob_env(table_BF_int)
+  load_glob_env(BF_weights_int)
+  load_glob_env(summary_sensitivity_int)
+
+  #----    Externalizing    ----
+
+  # ZINB anlaysis
+  load_glob_env(fit_ext_nb)
+
+  # ANOVA
+  load_glob_env(fit_ext_zinb)
+  load_glob_env(plot_zinb_ext)
+
+  # brms models
+  load_glob_env(brm_ext_mother)
+  load_glob_env(waic_weights_ext)
+  load_glob_env(loo_weights_ext)
+
+  # BF encompassing
+  load_glob_env(encompassing_model_ext)
+  load_glob_env(table_BF_ext)
+  load_glob_env(BF_weights_ext)
+  load_glob_env(summary_sensitivity_ext)
+
+}
+
+#----    table_grade  ----
+
+table_grade <- function(data_raw){
+  data_raw %>%
+    dplyr::filter(age_year < 12.30) %>%
+    select(classe) %>%
+    table()
+}
+
+#----    normal_approximation    ----
+
+normal_approximation <- function(){
+  data_plot <- data.frame(db_mother_1 = post_H1[,1],
+                          db_mother_2 = post_H1[,2])
[…]

### 2021-08-03 R/Bayes_factor.R
add documentation funcctions

@@ -252,7 +252,7 @@ get_hypothesis_matrix <- function(hypothesis = c("null", "monotropy", "hierarchi
 #'
 #' @param mean vector with the parameters mean
 #' @param sigma covariance matrix of the parameters
-#' @param n_eqinteger indicating thee number of equality constraints
+#' @param n_eq integer indicating the number of equality constraints
 #'
 #' @return a numeric single value
 #'
@@ -280,7 +280,8 @@ compute_density <- function(mean, sigma, n_eq){
 #'
 #' @param mean vector with the parameters mean
 #' @param sigma covariance matrix of the parameters
-#' @param n_eqinteger indicating thee number of equality constraints
+#' @param n_eq integer indicating the number of equality constraints
+#' @param n_ineq integer indicating the number of inequality constraints
 #'
 #' @return a numeric single value
 #'
@@ -303,8 +304,11 @@ compute_cond_prob <- function(mean, sigma, n_eq, n_ineq){
 
 #' Get Prior Info
 #'
-#' @param encompassing_model
-#' @param hyp
+#' Given the encompassing model, get prior mean and covariance matrix
+#'
+#' @param encompassing_model a `brms` fit object of the encompassing model
+#' @param hyp a matrix with the hypothesis constraints returned from
+#'   `get_hypothesis_matrix()` function
 #'
 #' @return list with the prior mean and covariance matrix
 #'
@@ -312,6 +316,7 @@ compute_cond_prob <- function(mean, sigma, n_eq, n_ineq){
 #' drake::loadd(encompassing_model_int)
 #' hyp <- get_hypothesis_matrix(hypothesis = "hierarchical", encompassing_model_int)$hyp
 #' get_prior_info(encompassing_model = encompassing_model_int, hyp = hyp)
+#'
 
 get_prior_info <- function(encompassing_model, hyp){
   prior_sd <- get_prior_sd(encompassing_model)
@@ -327,12 +332,16 @@ get_prior_info <- function(encompassing_model, hyp){
 
 #' Get Posterior Info
 #'
-#' @param encompassing_model
+#' Given the encompassing model, get posterior mean and covariance matrix
+#'
+#' @param encompassing_model a `brms` fit object of the encompassing model
 #'
 #' @return list with the posterior mean and covariance matrix
 #'
+#' @examples
 #' drake::loadd(encompassing_model_int)
[…]

### 2021-08-03 R/Models.R

@@ -101,6 +101,8 @@ get_rel_weights <- function(..., ic = c("waic", "loo")){
 
 #----    make_stan_data    ----
 
+# function no longer used in thee analysis
+
 make_stan_data <- function(data, formula = "mother + father"){
 
   if(!is.list(formula)){

### 2021-08-03 R/Utils_report.R

@@ -2,11 +2,36 @@
 #====    Utilities Report     ====#
 #=================================#
 
-#----    drake_load_all    ----
+#----    load_glob_env    ----
+
+#' Load Drake in Global Environment
+#'
+#' Load drake object in Global Environment
+#'
+#' @param ... parameters passed to `drake::loadd()` function
+#'
+#' @return The cached value of the target
+#'
+#' @examples
+#' load_glob_env(BF_weights_int)
+#' BF_weights_int
+#'
 
 load_glob_env <- function(...){
   drake::loadd(..., envir = globalenv())
 }
+
+#----    drake_load_all    ----
+
+#' Load All Analyisis Objects
+#'
+#' Load all analysis objects
+#'
+#' @return all cached value of the target
+#'
+#' @examples
+#' drake_load_all()
+#'
 
 drake_load_all <- function(){
   # Data
@@ -65,6 +90,19 @@ drake_load_all <- function(){
 
 #----    table_grade  ----
 
+#' Get Table School Grade
+#'
+#' Get table school grade from data_raw selcting subjeects accroding to age
+#'
+#' @param data_raw the row dataset
+#'
+#' @return a contingency table
+#'
+#' @examples
+#' drake::loadd(data_raw)
+#' table_grade(data_raw)
+#'
+
 table_grade <- function(data_raw){
   data_raw %>%
     dplyr::filter(age_year < 12.30) %>%
@@ -74,20 +112,48 @@ table_grade <- function(data_raw){
 
 #----    normal_approximation    ----
 
-normal_approximation <- function(){
-  data_plot <- data.frame(db_mother_1 = post_H1[,1],
-                          db_mother_2 = post_H1[,2])
-  mu <- apply(post_H1,2, mean)[c(1,2)]
-  cov <- cov(post_H1[, c(1,2)])
+# Extra function not used at the moment
 
-  data_grid <- expand.grid(s_1 = seq(0, .35, length.out=100), s_2 = seq(-.1, .25, length.out=100))
+normal_approximation <- function(){
+
+  drake::loadd(encompassing_model_int)
+  par_post <- brms::fixef(encompassing_model_int, summary = FALSE) %>%
+    as.data.frame()
+
+  mu <- apply(par_post[, c("motherAvoidant",
+                           "motherAvoidant:fatherAvoidant")],2, mean)
[…]

### 2021-08-06 Analysis/Analysis_Drake.R
add initial section Bayes Factor

@@ -175,6 +175,7 @@ drake::loadd(summary_sensitivity_ext)
 
 #===========================#
 
+BF_weights_ext$bf / sum(BF_weights_ext$bf)
 
 #----
 

### 2021-08-09 Analysis/Analysis_Drake.R
set seed for analysis

@@ -26,7 +26,8 @@ drake::vis_drake_graph(config, font_size = 16, targets_only = FALSE)
 # Run the analysis
 drake::make(prework = "devtools::load_all()",
             envir = env,
-            plan = plan)
+            plan = plan,
+            seed = 2021)
 
 # Plot the analysis plan
 drake::vis_drake_graph(config, font_size = 16, targets_only = FALSE)

### 2021-08-09 R/Bayes_factor.R

@@ -14,7 +14,7 @@
 #'
 #' @param data dataframe with the cluster groups and other subjects' information
 #'   ("data_cluster")
-#' @param y character indicanting the dependent variable ("internalizin_sum" or
+#' @param y character indicanting the dependent variable ("internalizing_sum" or
 #'   "externalizing_sum")
 #' @param prior_par character indicating the prior or the fixed effect
 #'
@@ -38,7 +38,7 @@ get_encompassing_model <- function(data, y,  prior_par){
                             as.formula(formula_zi)),
                    data = data, family = brms::zero_inflated_negbinomial(),
                    prior = my_prior, chains = 6, iter = 1e4, cores = 6, warmup = 2000,
-                   save_pars = brms::save_pars(all = TRUE))
+                   save_pars = brms::save_pars(all = TRUE), seed = 2021)
 
   return(fit)
 }

### 2021-08-09 R/Models.R

@@ -39,7 +39,8 @@ zinb_brms <- function(data, y, formula){
 
   fit <- brms::brm(brms::bf(as.formula(formula_mu),
                             as.formula(formula_zi)),
-    data = data, family = brms::zero_inflated_negbinomial(), cores = 4)
+    data = data, family = brms::zero_inflated_negbinomial(),
+    cores = 4, seed = 2021)
 
   fit <- brms::add_criterion(fit, criterion = c("loo", "waic"))
   return(fit)

### 2021-08-09 R/Plots.R

@@ -1,52 +1,0 @@
-#=====================#
-#====    Plots    ====#
-#=====================#
-
-#----    get_plot_zinb    ----
-
-#' Plot of the ZINB Model
-#'
-#' Plot of the marginal effects of the Zero inflated Negative Binomial model (ZINB)
-#'
-#' @param model the ZINB modle
-#'
-#' @return a ggplot object
-#'
-#' @examples
-#' drake::loadd(fit_int_zinb)
-#' get_plot_zinb(model = fit_int_zinb)
-#'
-
-get_plot_zinb <- function(model){
-
-  marginal_effects_gender <- emmeans::emmeans(model, specs = ~ gender)
-
-  p_gender <- ggplot(as.data.frame(marginal_effects_gender),
-         aes(x = gender, y = emmean, colour = gender)) +
-    geom_point(show.legend = FALSE) +
-    geom_errorbar(aes(ymin=asymp.LCL, ymax = asymp.UCL, colour = gender),
-                  size = 1, width = .2, show.legend = FALSE) +
-    labs(x = "Gender",
-         y = "Problems") +
-    coord_cartesian(ylim = c(0, 8)) +
-    theme_bw()
-
-  marginal_effects_att <- emmeans::emmeans(model, specs = ~ mother*father)
-
-  p_attachemnt <- ggplot(as.data.frame(marginal_effects_att),
-         aes(x = mother, y = emmean, colour = father, group = father)) +
-    geom_point(show.legend = FALSE) +
-    geom_line(show.legend = FALSE) +
-    geom_errorbar(aes(ymin=asymp.LCL, ymax = asymp.UCL, colour = father),
-                  width = .5, show.legend = FALSE) +
-    facet_grid(.~father) +
-    labs(x = "Mother Attachment",
-         y = "Problems") +
-    coord_cartesian(ylim = c(0, 8)) +
-    theme_bw()
-
-  gridExtra::grid.arrange(p_gender, p_attachemnt, layout_matrix = matrix(c(1,2,2,2,2), nrow = 1))
-}
-
-#----
-

### 2021-08-09 R/Plots_Tables.R

@@ -1,92 +1,55 @@
-#=================================#
-#====    Utilities Report     ====#
-#=================================#
+#=============================#
+#====    Plots & Tables   ====#
+#=============================#
 
-#----    load_glob_env    ----
+#----    get_plot_zinb    ----
 
-#' Load Drake in Global Environment
+#' Plot of the ZINB Model
 #'
-#' Load drake object in Global Environment
+#' Plot of the marginal effects of the Zero inflated Negative Binomial model (ZINB)
 #'
-#' @param ... parameters passed to `drake::loadd()` function
+#' @param model the ZINB modle
 #'
-#' @return The cached value of the target
-#'
-#' @examples
-#' load_glob_env(BF_weights_int)
-#' BF_weights_int
-#'
-
-load_glob_env <- function(...){
-  drake::loadd(..., envir = globalenv())
-}
-
-#----    drake_load_all    ----
-
-#' Load All Analyisis Objects
-#'
-#' Load all analysis objects
-#'
-#' @return all cached value of the target
+#' @return a ggplot object
 #'
 #' @examples
-#' drake_load_all()
+#' drake::loadd(fit_int_zinb)
+#' get_plot_zinb(model = fit_int_zinb)
 #'
 
-drake_load_all <- function(){
-  # Data
-  load_glob_env(data_raw)
-  load_glob_env(data_munged)
-  load_glob_env(data_cluster)
+get_plot_zinb <- function(model){
 
-  # Cluster
-  load_glob_env(cluster_mother_fit)
-  load_glob_env(cluster_father_fit)
+  marginal_effects_gender <- emmeans::emmeans(model, specs = ~ gender)
 
-  load_glob_env(mclust_mother)
-  load_glob_env(mclust_father)
+  p_gender <- ggplot(as.data.frame(marginal_effects_gender),
+         aes(x = gender, y = emmean, colour = gender)) +
+    geom_point(show.legend = FALSE) +
+    geom_errorbar(aes(ymin=asymp.LCL, ymax = asymp.UCL, colour = gender),
+                  size = 1, width = .2, show.legend = FALSE) +
+    labs(x = "Gender",
+         y = "Problems") +
+    coord_cartesian(ylim = c(0, 8)) +
+    theme_bw()
 
-  #----    Internalizing    ----
[…]

### 2021-08-09 Documents/Utils_report.R
add section prior adjust (not finished)

@@ -1,0 +1,92 @@
+#=================================#
+#====    Utilities Report     ====#
+#=================================#
+
+#----    load_glob_env    ----
+
+#' Load Drake in Global Environment
+#'
+#' Load drake object in Global Environment
+#'
+#' @param ... parameters passed to `drake::loadd()` function
+#'
+#' @return The cached value of the target
+#'
+#' @examples
+#' load_glob_env(BF_weights_int)
+#' BF_weights_int
+#'
+
+load_glob_env <- function(...){
+  drake::loadd(..., envir = globalenv())
+}
+
+#----    drake_load_all    ----
+
+#' Load All Analyisis Objects
+#'
+#' Load all analysis objects
+#'
+#' @return all cached value of the target
+#'
+#' @examples
+#' drake_load_all()
+#'
+
+drake_load_all <- function(){
+  # Data
+  load_glob_env(data_raw)
+  load_glob_env(data_munged)
+  load_glob_env(data_cluster)
+
+  # Cluster
+  load_glob_env(cluster_mother_fit)
+  load_glob_env(cluster_father_fit)
+
+  load_glob_env(mclust_mother)
+  load_glob_env(mclust_father)
+
+  #----    Internalizing    ----
+
+  # ZINB anlaysis
+  load_glob_env(fit_int_nb)
+
+  # ANOVA
+  load_glob_env(fit_int_zinb)
+  load_glob_env(plot_zinb_int)
+
+  # brms models
+  load_glob_env(brm_int_mother)
+  load_glob_env(waic_weights_int)
+  load_glob_env(loo_weights_int)
+
+  # BF encompassing
+  load_glob_env(encompassing_model_int)
+  load_glob_env(table_BF_int)
+  load_glob_env(BF_weights_int)
+  load_glob_env(summary_sensitivity_int)
+
+  #----    Externalizing    ----
+
+  # ZINB anlaysis
+  load_glob_env(fit_ext_nb)
+
+  # ANOVA
+  load_glob_env(fit_ext_zinb)
+  load_glob_env(plot_zinb_ext)
+
+  # brms models
+  load_glob_env(brm_ext_mother)
+  load_glob_env(waic_weights_ext)
+  load_glob_env(loo_weights_ext)
+
+  # BF encompassing
+  load_glob_env(encompassing_model_ext)
+  load_glob_env(table_BF_ext)
+  load_glob_env(BF_weights_ext)
+  load_glob_env(summary_sensitivity_ext)
+
+}
+
+
+#=============

### 2021-08-09 R/Plots_Tables.R

@@ -48,6 +48,23 @@ get_plot_zinb <- function(model){
   gridExtra::grid.arrange(p_gender, p_attachemnt, layout_matrix = matrix(c(1,2,2,2,2), nrow = 1))
 }
 
+#----    plot_prior_adj    ----
+
+plot_prior_adj <- function(k = 1){
+
+  ggplot(data.frame(x = c(-3,3))) +
+    geom_area(stat = "function", fun = dnorm, col = "gray40", fill = "#F98400", xlim = c(-3, k), size = 1) +
+    geom_area(stat = "function", fun = dnorm, col = "gray40", fill = "#5BBCD6", xlim = c(k, 3), size = 1) +
+    geom_segment(x = k, xend = k , y = 0, yend = .35, size = 1.5, col = "gray20") +
+    annotate(geom = "text", x = k, y = .37, label = "\\textit{k}") +
+    xlim(-3, 3) +
+    labs(x = "$\\theta_i$") +
+    theme_classic() +
+    theme(axis.text = element_blank(),
+          axis.ticks = element_blank(),
+          axis.title.y = element_blank(),
+          axis.line.y.left = element_blank())
+}
 
 #----
 

### 2021-08-10 R/Bayes_factor.R
fic adj prior center on focal point

@@ -357,11 +357,13 @@ get_posterior_info <- function(encompassing_model){
 
 #' Linear Transformation of the Parameters
 #'
-#' Compute mean and covariance of the linear transformed parameters
+#' Compute mean and covariance of the linear transformed parameters. If prior
+#' the vector mean is set to zero.
 #'
 #' @param param_info result of `get_posterior_info()` or `get_prior_info()`
 #'   function
 #' @param hyp matrix of the linear transformation
+#' @param prior logical value indicating whether is prior.
 #'
 #' @return list with the transformed mean and covariance matrix
 #'
@@ -371,8 +373,13 @@ get_posterior_info <- function(encompassing_model){
 #' hyp <- get_hypothesis_matrix("hierarchical", encompassing_model_int)$hyp[1:15, ]
 #' transform_param(param_info, hyp)
 
-transform_param <- function(param_info, hyp){
-  param_mean <- hyp %*% param_info$mean
+transform_param <- function(param_info, hyp, prior = FALSE){
+
+  if(isTRUE(prior)){
+    param_mean <- matrix(rep(0, length(param_info$mean)), ncol = 1)
+  } else {
+    param_mean <- hyp %*% param_info$mean
+  }
   param_cov <- hyp %*% param_info$cov %*% t(hyp)
 
   return(list(mean = param_mean,
@@ -433,7 +440,7 @@ get_BF <- function(hypothesis = c("null", "monotropy", "hierarchical",
       #----    Monotropy Hypothesis    ----
 
       # Linear transformation of the parameters
-      prior <- transform_param(prior, hyp_matrix$hyp)
+      prior <- transform_param(prior, hyp_matrix$hyp, prior = TRUE)
       posterior <- transform_param(posterior, hyp_matrix$hyp)
 
       # prior density equality
@@ -465,7 +472,7 @@ get_BF <- function(hypothesis = c("null", "monotropy", "hierarchical",
                                                   independent_rows = independent_rows)
 
       # Linear transformation of the parameters
-      prior <- transform_param(prior, hyp_matrix$hyp[1:15, ])
+      prior <- transform_param(prior, hyp_matrix$hyp[1:15, ], prior = TRUE)
       posterior <- transform_param(posterior, hyp_matrix$hyp[1:15, ])
 
       # prior density equality
@@ -502,7 +509,7 @@ get_BF <- function(hypothesis = c("null", "monotropy", "hierarchical",
       #----    Independent Hypothesis    ----
[…]

### 2021-08-10 Documents/Utils_report.R
finish BF computation

@@ -88,5 +88,15 @@ drake_load_all <- function(){
 
 }
 
+#----    get_sigma_example    ----
 
+get_sigma_example <- function(){
+  R <- matrix(c( 0, 0, 1,-1, 0,
+                 0, 0, 0, 1,-1,
+                -1, 1, 0, 0, 0,
+                 0,-1, 1, 0, 0), ncol = 5, byrow = TRUE)
+  sigma_theta <- diag(5)*4
+
+  R%*%sigma_theta%*%t(R)
+}
 #=============

### 2021-08-12 Analysis/Analysis_Drake.R
rename hypothesis

@@ -109,9 +109,9 @@ drake::loadd(encompassing_model_int)
 
 drake::loadd(BF_null_int)
 drake::loadd(BF_monotropy_int)
-drake::loadd(BF_hierarchical_int)
-drake::loadd(BF_independent_int)
-drake::loadd(BF_interaction_int)
+drake::loadd(BF_hierarchy_int)
+drake::loadd(BF_independence_int)
+drake::loadd(BF_integration_int)
 
 drake::loadd(table_BF_int)
 drake::loadd(BF_weights_int)

### 2021-08-12 R/Bayes_factor.R

@@ -100,7 +100,7 @@ get_prior_sd <- function(encompassing_model){
 
 #' Get Model Matrix
 #'
-#' Get the model matrix considering mother and father attachmnt in interaction
+#' Get the model matrix considering mother and father attachment in interaction
 #'
 #' @return a matrix
 #'
@@ -131,7 +131,7 @@ get_model_matrix <- function(){
 #' matrix given by the union of the previous two.
 #'
 #' @param hypothesis a character indicating the hypothesis ("null", "monotropy",
-#'   "hierarchical", "independent", "iteraction")
+#'   "hierarchy", "independence", "integration")
 #' @param encompassing_model a `brms` fit object of the encompassing model
 #'
 #' @return a list with the following matrixes:
@@ -144,8 +144,8 @@ get_model_matrix <- function(){
 #' get_hypothesis_matrix(hypothesis = "null", encompassing_model = encompassing_model_int)
 #'
 
-get_hypothesis_matrix <- function(hypothesis = c("null", "monotropy", "hierarchical",
-                                                 "independent", "interaction"),
+get_hypothesis_matrix <- function(hypothesis = c("null", "monotropy", "hierarchy",
+                                                 "independence", "integration"),
                                   encompassing_model){
   hypothesis <- match.arg(hypothesis)
 
@@ -175,8 +175,8 @@ get_hypothesis_matrix <- function(hypothesis = c("null", "monotropy", "hierarchi
     ineq_matrix <- rbind(mm["M_Anx_F_Sec", ],             # M_Anxious > 0
                          c(0, -1, 1, rep(0, n_pars - 3))) # M_Fearful - M_Avoidant > 0
 
-  } else if(hypothesis == "hierarchical"){
-    #----    Hierarchical Hypothesis    ----
+  } else if(hypothesis == "hierarchy"){
+    #----    Hierarchy Hypothesis    ----
 
     # equality constraints
     eq_matrix <- rbind(mm["M_Anx_F_Sec", ] - mm["M_Av_F_Sec", ], # M_Anxious - M_Avoidant = 0
@@ -192,8 +192,8 @@ get_hypothesis_matrix <- function(hypothesis = c("null", "monotropy", "hierarchi
                          mm["M_Av_F_Sec", ] - mm["M_Sec_F_Av", ],     # M_Avoidant > F_Avoidant
[…]

### 2021-08-12 R/Plan.R

@@ -37,9 +37,9 @@ get_analysis_plan <- function(){
     mclust_father = mclust_BIC(data = data_munged,
                                parent = "father"),
 
-    #=============================#
-    #====    Internalizing    ====#
-    #=============================#
+    #=============================
+    #====    Internalizing    ====
+    #=============================
 
     #----    ZINB analysis    ----
     fit_int_nb = MASS::glm.nb(internalizing_sum ~ gender + mother * father,
@@ -90,16 +90,15 @@ get_analysis_plan <- function(){
     # BF hypothesis
     BF_null_int = get_BF(hypothesis = "null", encompassing_model_int),
     BF_monotropy_int = get_BF(hypothesis = "monotropy", encompassing_model_int),
-    BF_hierarchical_int = get_BF(hypothesis = "hierarchical", encompassing_model_int),
-    BF_independent_int = get_BF(hypothesis = "independent", encompassing_model_int),
-    BF_interaction_int = get_BF(hypothesis = "interaction", encompassing_model_int),
+    BF_hierarchy_int = get_BF(hypothesis = "hierarchy", encompassing_model_int),
+    BF_independence_int = get_BF(hypothesis = "independence", encompassing_model_int),
+    BF_integration_int = get_BF(hypothesis = "integration", encompassing_model_int),
 
-    table_BF_int = get_table_BF(BF_null_int, BF_monotropy_int, BF_hierarchical_int,
-                                BF_independent_int, BF_interaction_int),
+    table_BF_int = get_table_BF(BF_null_int, BF_monotropy_int, BF_hierarchy_int,
+                                BF_independence_int, BF_integration_int),
 
-    BF_weights_int = get_BF_weights(BF_null_int, BF_monotropy_int, BF_hierarchical_int,
-                                    BF_independent_int, BF_interaction_int,
-                                    encompassing_model = encompassing_model_int),
+    BF_weights_int = get_BF_weights(BF_null_int, BF_monotropy_int, BF_hierarchy_int,
+                                    BF_independence_int, BF_integration_int),
 
     # Prior Sensitivity
     encompassing_model_ps_int = drake::target(
@@ -122,9 +121,9 @@ get_analysis_plan <- function(){
                                                       prior_sensitivity_int_05,
                                                       prior_sensitivity_int_10),
 
-    #=============================#
-    #====    Externalizing    ====#
[…]

### 2021-08-12 R/Plots_Tables.R
end part bayes factor start example

@@ -66,7 +66,49 @@ plot_prior_adj <- function(k = 1){
           axis.line.y.left = element_blank())
 }
 
-#----
+#----    plot_bounded_par    ----
+
+plot_bounded_par <- function(){
+
+  ggplot(data.frame(x = c(-3,3))) +
+    geom_area(stat = "function", fun = dnorm, col = "gray40", fill = "#F98400",
+              args = list(sd = .75), size = 1, alpha = .7) +
+    geom_area(stat = "function", fun = dunif, args = list(min = -1), col = "gray40", fill = "#5BBCD6", size = 1, alpha = .7) +
+    geom_segment(x = 0, xend = 0 , y = 0, yend = .55, size = 1.5, col = "gray20") +
+    xlim(-2.2, 2.2) +
+    labs(x = "$\\rho_i$") +
+    theme_classic() +
+    theme(axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          axis.title.y = element_blank(),
+          axis.line.y.left = element_blank())
+}
+
+#----    perc_females    ----
+
+perc_females <- function(perc = TRUE, digits = 2){
+  freq <- table(data_cluster$gender)
+
+  if(isTRUE(perc)){
+    res <- round(freq[1]*100/nrow(data_cluster), digits = digits)
+  } else {
+    res <- freq[1]
+  }
+  return(res)
+}
+
+#----    perc_females    ----
+
+perc_females <- function(perc = TRUE, digits = 2){
+  freq <- table(data_cluster$gender)
+
+  if(isTRUE(perc)){
+    res <- round(freq[1]*100/nrow(data_cluster), digits = digits)
+  } else {
+    res <- freq[1]
+  }
+  return(res)
+}
 
 #----    table_grade  ----
 

### 2021-08-12 R/Plots_Tables.R
present study introduction

@@ -53,8 +53,10 @@ get_plot_zinb <- function(model){
 plot_prior_adj <- function(k = 1){
 
   ggplot(data.frame(x = c(-3,3))) +
-    geom_area(stat = "function", fun = dnorm, col = "gray40", fill = "#F98400", xlim = c(-3, k), size = 1) +
-    geom_area(stat = "function", fun = dnorm, col = "gray40", fill = "#5BBCD6", xlim = c(k, 3), size = 1) +
+    geom_area(stat = "function", fun = dnorm, col = "gray40", fill = "#F98400",
+              xlim = c(-3, k), size = 1, alpha = .8) +
+    geom_area(stat = "function", fun = dnorm, col = "gray40", fill = "#5BBCD6",
+              xlim = c(k, 3), size = 1, alpha = .8) +
     geom_segment(x = k, xend = k , y = 0, yend = .35, size = 1.5, col = "gray20") +
     annotate(geom = "text", x = k, y = .37, label = "\\textit{k}") +
     xlim(-3, 3) +
@@ -97,17 +99,36 @@ perc_females <- function(perc = TRUE, digits = 2){
   return(res)
 }
 
-#----    perc_females    ----
+#----    get_table_cluster    ----
 
-perc_females <- function(perc = TRUE, digits = 2){
-  freq <- table(data_cluster$gender)
+get_table_cluster <- function(perc = TRUE, digits = 2){
 
-  if(isTRUE(perc)){
-    res <- round(freq[1]*100/nrow(data_cluster), digits = digits)
-  } else {
-    res <- freq[1]
-  }
-  return(res)
+  data_cluster %>%
+    select(father, mother) %>%
+    group_by(father, mother) %>%
+    count() %>%
+    pivot_wider(names_from = father, values_from = n) %>%
+    bind_cols(Total = rowSums(.[, 2:5])) %>%
+    ungroup() %>%
+    bind_rows(tibble(mother = "Total",
+                     summarise_at(., vars(Secure:Total), sum))) %>%
+    kable(., booktabs = T, align = c("r", rep("c", 5)),
+          col.names = c("Mother Attachemnt", "Secure", "Anxious", "Avoidant", "Fearful", "Total"),
+          caption = "Attachment styles frequencies ($n_{subj} = 847$)") %>%
+    add_header_above(c(" ", "Father Attachment" = 4, " ")) %>%
+    kable_styling(latex_options = c("hold_position"))
+}
+
[…]

### 2021-08-13 R/Plots_Tables.R
add example encomapssing model definition

@@ -130,6 +130,115 @@ plot_externalizing_dist <- function(){
          y = "Frequency") +
     theme_classic()
 }
+#----    plot_attachment_marginal    ----
+
+plot_attachment_marginal <- function(mother_score = c(0.05, 0.5, 0.5, 1),
+                                     father_score = c( 0.05, 0.25, 0.25, .5),
+                                     lab_y = "Externalizing Problems"){
+  data_plot <- data.frame(
+    Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
+    Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
+                        levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+    Score = c(mother_score, father_score))
+
+  ggplot(data_plot) +
+    geom_bar(aes(x = Attachment, y = Score, fill = Parent),
+             stat = "identity", show.legend = FALSE, alpha = .8, col = "gray20") +
+    ylim(0, 1) +
+    facet_grid(Parent ~ .) +
+    labs(x = "Attachemnt Style",
+         y = lab_y) +
+    theme_classic() +
+    theme(axis.ticks.y = element_blank(),
+          axis.text.y = element_blank(),
+          panel.border = element_rect(fill = "#FF000000"))
+}
+
+#----    plot_attachment_tile    ----
+
+plot_attachment_tile <- function(problems_score,
+                                 lab_legend = "Externalizing Problems"){
+  data_plot <- expand.grid(
+    Mother = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                    levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
+    Father = factor(c("Secure", "Anxious", "Avoidant", "Fearful"),
+                    levels = c("Secure", "Anxious", "Avoidant", "Fearful")))
+
+  data_plot$Problems <- problems_score
+  range_score <- c(0,max(data_plot$Problems, 1))
+
+
+  ggplot(data_plot) +
+    geom_tile(aes(x = Father, y = Mother, fill = Problems), col = "gray10") +
+    scale_fill_gradient(low = "white", high = "firebrick", limits = range_score,
+                        breaks= range_score, labels = c("Low", "High")) +
+    labs(fill = "Problems",
+         y = "Mother Attachment",
+         x = "Father Attachment")+
+    guides(fill = guide_colourbar(barheight = .75, label = FALSE)) +
[…]

### 2021-08-16 R/Bayes_factor.R
add sensitivity analysis

@@ -172,8 +172,8 @@ get_hypothesis_matrix <- function(hypothesis = c("null", "monotropy", "hierarchy
                        diag(n_pars)[4:n_pars, ])                 # All father and interaction terms = 0
 
     # inequality constraints
-    ineq_matrix <- rbind(mm["M_Anx_F_Sec", ],             # M_Anxious > 0
-                         c(0, -1, 1, rep(0, n_pars - 3))) # M_Fearful - M_Avoidant > 0
+    ineq_matrix <- rbind(mm["M_Anx_F_Sec", ],                       # M_Anxious > 0
+                         mm["M_Fear_F_Sec", ] - mm["M_Av_F_Sec", ]) # M_Fearful - M_Avoidant > 0
 
   } else if(hypothesis == "hierarchy"){
     #----    Hierarchy Hypothesis    ----

### 2021-08-16 R/Plots_Tables.R

@@ -240,6 +240,85 @@ perc_rare_condition <- function(perc = TRUE, digits = 1){
   return(res)
 }
 
+#----    get_ggplot_balls    ----
+
+get_ggplot_balls <- function(data, filename = "Documents/Paper/figure/Prova.png"){
+  plot <- data %>%
+    ggplot() +
+    geom_point(aes(x = 0, y = 0, size = weights, fill = weights),
+               shape = 21, stroke = 2, col = "gray20") +
+    scale_size(limits = c(0,1), range = c(15,150),
+               breaks = seq(0,1, length.out =10)) +
+    scale_fill_gradient(limit=c(0,1), high = "#046C9A", low = "white") +
+    theme_classic() +
+    theme(legend.position = "none",
+          axis.line = element_blank(),
+          axis.text = element_blank(),
+          axis.ticks = element_blank(),
+          axis.title = element_blank())
+
+  ggsave(plot = plot, filename = filename, width =4.67, height =4.67)
+}
+
+
+#----    get_table_bf    ----
+
+get_table_bf <- function(bf_result = BF_weights_ext,
+                         path_img = "Documents/Paper/figure/"){
+
+  names_plot <- paste("ball", c("null", "monotropy", "hierarchy",
+                                "independence", "integration"), sep = "_")
+  images <- paste0(path_img, names_plot, ".png")
+
+  for(i in 1:5){
+    get_ggplot_balls(data = bf_result[i,],
+                     filename = images[i])
+  }
+
+  # centerText <- function(text){
+  #   paste0("\\multirow{1}{*}[0pt]{", text, "}")
+  # }
+
+
+
+  bf_result %>%
+    bind_cols(img = "") %>%
+    mutate(hypothesis = c("Null", "Monotropy", "Hierarchy",
+                          "Independence", "Integration"),
+           bf = format(bf, digits = 2),
+           weights = round(weights,2)) %>%
+    select(hypothesis, bf, weights, img) %>%
+    # mutate_at(c("hypothesis", "bf","weights"), centerText) %>%
+    kable(., booktabs = T, align = c("r", rep("c", 3)), escape = FALSE,
+          col.names = c("Hypothesis", "Bayes Factor", "Posterior Probability", " "),
[…]

### 2021-08-18 Documents/Utils_report.R
end first draft

@@ -88,6 +88,17 @@ drake_load_all <- function(){
 
 }
 
+drake_load_paper <- function(){
+  # Data
+  load_glob_env(data_cluster)
+
+  # BF encompassing
+  load_glob_env(encompassing_model_ext)
+  load_glob_env(BF_weights_ext)
+  load_glob_env(summary_sensitivity_ext)
+
+}
+
 #----    get_sigma_example    ----
 
 get_sigma_example <- function(){

### 2021-09-14 Documents/Utils_report.R
Corrige Altoe and fix plot and tables

@@ -86,6 +86,7 @@ drake_load_all <- function(){
   load_glob_env(BF_weights_ext)
   load_glob_env(summary_sensitivity_ext)
 
+  load_glob_env(data_prior_predict)
 }
 
 drake_load_paper <- function(){
@@ -96,6 +97,8 @@ drake_load_paper <- function(){
   load_glob_env(encompassing_model_ext)
   load_glob_env(BF_weights_ext)
   load_glob_env(summary_sensitivity_ext)
+
+  load_glob_env(data_prior_predict)
 
 }
 
@@ -110,4 +113,5 @@ get_sigma_example <- function(){
 
   R%*%sigma_theta%*%t(R)
 }
+
 #=============

### 2021-09-14 R/Models.R

@@ -100,6 +100,18 @@ get_rel_weights <- function(..., ic = c("waic", "loo")){
   return(res)
 }
 
+#----    get_data_prior_predict    ----
+
+get_data_prior_predict <- function(){
+  tibble(prior_sd = c(.5, 1, 3, 5, 10),
+         prior = paste0("$\\mathcal{N}(0, ", prior_sd, ")$")) %>%
+    mutate(q_1 = exp(1 - 1 * prior_sd),
+           q_2 = exp(1 - .5 * prior_sd),
+           q_mean = exp(1 + 0 * prior_sd),
+           q_3 = exp(1 + .5 * prior_sd),
+           q_4 = exp(1 + 1 * prior_sd))
+}
+
 #----    make_stan_data    ----
 
 # function no longer used in thee analysis

### 2021-09-14 R/Plan.R

@@ -20,7 +20,6 @@ get_analysis_plan <- function(){
     data_raw = readRDS("Data/data_ECR.rds"),
     data_munged = munge_data(data = data_raw),
 
-
     #----    Cluster Analysis    ----
     # Get cluster fit
     cluster_mother_fit = get_cluster_fit(data = data_munged, parent = "mother"),
@@ -204,6 +203,7 @@ get_analysis_plan <- function(){
                                                       prior_sensitivity_ext_05,
                                                       prior_sensitivity_ext_10),
 
+    data_prior_predict = get_data_prior_predict(),
   )
 }
 

### 2021-09-14 R/Plots_Tables.R

@@ -112,11 +112,35 @@ get_table_cluster <- function(perc = TRUE, digits = 2){
     ungroup() %>%
     bind_rows(tibble(mother = "Total",
                      summarise_at(., vars(Secure:Total), sum))) %>%
-    kable(., booktabs = T, align = c("r", rep("c", 5)),
+    kable(., format = "latex", booktabs = TRUE, align = c("r", rep("c", 5)),
           col.names = c("Mother Attachemnt", "Secure", "Anxious", "Avoidant", "Fearful", "Total"),
-          caption = "Attachment styles frequencies ($n_{subj} = 847$)") %>%
-    add_header_above(c(" ", "Father Attachment" = 4, " ")) %>%
+          caption = "Attachment styles frequencies ($n_{subj} = 847$).") %>%
+    add_header_above(c(" ", "Father Attachment" = 4, " "), bold = TRUE) %>%
+    row_spec(0, bold = TRUE) %>%
     kable_styling(latex_options = c("hold_position"))
+}
+
+#----    get_table_cluster_ext    ----
+
+get_table_cluster_ext <- function(){
+  data_cluster %>%
+    group_by(father, mother) %>%
+    summarize(mean = my_round(mean(externalizing_sum), 2),
+              median = my_round(median(externalizing_sum), 1),
+              sd =  my_round(sd(externalizing_sum), 2),
+              summary = paste0(mean, " (",
+                               sd, ")")) %>%
+    select(father, mother, summary, median) %>%
+    pivot_wider(names_from = father, values_from = c(summary, median)) %>%
+    select(mother, dplyr::ends_with("Secure"), dplyr::ends_with("Anxious"),
+           dplyr::ends_with("Avoidant"),  dplyr::ends_with("Fearful")) %>%
+    kable(.,format = "latex", booktabs = TRUE, align = c("r", rep("c", 8)),
+          col.names = c("Mother Attachemnt", rep(c("Mean (SD)", "Median"), 4)),
+          caption = "Externalizing problems according to attachment styles ($n_{subj} = 847$).") %>%
+    add_header_above(c(" ", "Secure" = 2, "Anxious" = 2, "Avoidant" = 2, "Fearful" = 2), bold = TRUE) %>%
+    add_header_above(c(" ", "Father Attachment" = 8), bold = TRUE) %>%
[…]

### 2021-09-14 R/Utils.R

@@ -1,0 +1,15 @@
+#=====================#
+#====    Utils    ====#
+#=====================#
+
+#----    my_round    ----
+
+my_round <- function(x, digits = 2){
+  format(round(x, digits), nsmall = digits)
+}
+
+#-------
+
+
+
+

### 2021-09-14 Documents/Bookdown/index.Rmd
add template github pag bookdown

--- 
title: "Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach"
subtitle: "Supplemental Material"
author: "Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: ["../Biblio-attachment.bib"]
csl: "../apa.csl"
link-citations: yes
github-repo: ClaudioZandonella/Attachment
description: "This the Suppleemental Material of the article ..."
cover-image: "images/logo_psicostat.png"
header-includes: 
  - \usepackage{titlepic}
  - \titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
url: 'https\://ClaudioZandonella.github.io/Attachment/'
params:
  format: html
---

```{r, echo = FALSE}
library(kableExtra)
library(ggplot2)

# Chunks settings
knitr::opts_chunk$set(echo = FALSE,
                      # Plot settings
                      # dev = "tikz", dev.args=list(pointsize=12),fig.align='center',
                      # fig.height=3, fig.width=5, fig.pos = "!ht",

                      # Code output width
                      tidy=TRUE, tidy.opts = list(width.cutoff = 80),
                      # comment = NA, prompt = TRUE

                      # Cache options
                      cache = FALSE, autodep=TRUE)

# Console output width
options(width = 80)

# Chunk theme
thm = knitr::knit_theme$get("bclear")
knitr::knit_theme$set(thm)
knitr::opts_chunk$set(background = c(.98, .98, 1))

# Option KableExtra
# options(knitr.kable.NA = '')

## ggplot settings
theme_set(theme_classic()+
            theme(text = element_text(size=12)))

devtools::load_all("../../")
source("../Utils_report.R")

#----    load drake    ----

drake_load_paper()
```

# Prerequisites {-}

trial

### 2021-09-14 Documents/Bookdown/preamble.tex
add template github pag bookdown

\usepackage{booktabs}
\usepackage{amsthm}
\makeatletter
\def\thm@space@setup{%
  \thm@preskip=8pt plus 2pt minus 4pt
  \thm@postskip=\thm@preskip
}
\makeatother

%----    define infoboxes    ----%
\usepackage{tcolorbox}
\usepackage{xcolor}

% colors
\definecolor{background}{HTML}{fcfcfc}
\definecolor{tip-text}{HTML}{e7b002}
\definecolor{tip-line}{HTML}{fdce38}
\definecolor{warning-text}{HTML}{b06336}
\definecolor{warning-line}{HTML}{c97d50}
\definecolor{deffun-text}{HTML}{0b797e}
\definecolor{deffun-line}{HTML}{6CC2C9}
\definecolor{design-text}{HTML}{7c972e}
\definecolor{design-line}{HTML}{a7c84a}
\definecolor{trick-text}{HTML}{8c3031}
\definecolor{trick-line}{HTML}{A3595A}

\newtcolorbox{mybox}[1][black]{
  colback=background,
  coltext=black,
  colframe=#1,
  boxsep=5pt,
  arc=4pt}

% tip
\newenvironment{tip}[1][Title]
  {
  \setlength{\fboxsep}{1em}
  \begin{mybox}[tip-line]
    \raisebox{-.2\height}{\includegraphics[height=.6cm]{images/lightbulb.png}} \large \textcolor{tip-text}{Tip-Box: #1}
    \vspace{1em}
    }
    {
  \end{mybox}
  }

% warning
\newenvironment{warning}[1][Title]
  {
  \setlength{\fboxsep}{1em}
  \begin{mybox}[warning-line]
    \raisebox{-.2\height}{\includegraphics[height=.6cm]{images/gotcha.png}} \large \textcolor{warning-text}{Warning-Box: #1}
    \vspace{1em}
    }
    {
  \end{mybox}
  }

% deffun
\newenvironment{deffun}[1][Title]
  {
  \setlength{\fboxsep}{1em}
  \begin{mybox}[deffun-line]
    \raisebox{-.2\height}{\includegraphics[height=.6cm]{images/gears.png}} \large \textcolor{deffun-text}{Definition-Box: #1}
    \vspace{1em}
    }
    {
  \end{mybox}
  }

% design
\newenvironment{design}[1][Title]
  {
  \setlength{\fboxsep}{1em}
  \begin{mybox}[design-line]
    \raisebox{-.2\height}{\includegraphics[height=.6cm]{images/design.png}} \large \textcolor{design-text}{Design-Box: #1}
    \vspace{1em}
    }
    {
  \end{mybox}
  }

% trick
\newenvironment{trick}[1][Title]
  {
  \setlength{\fboxsep}{1em}
  \begin{mybox}[trick-line]
    \raisebox{-.2\height}{\includegraphics[height=.6cm]{images/hat.png}} \large \textcolor{trick-text}{Trick-Box: #1}
    \vspace{1em}
    }
    {
  \end{mybox}
  }

### 2021-09-14 Documents/Utils_report.R

@@ -114,4 +114,18 @@ get_sigma_example <- function(){
   R%*%sigma_theta%*%t(R)
 }
 
+#----    make_my_book    ----
+
+make_my_book <- function(subdir = "Documents/Bookdown/") {
+
+  origwd <- setwd(file.path(subdir))
+  on.exit(setwd(origwd))
+  bookdown::render_book(input='_bookdown.yml', config_file='_bookdown.yml',
+                        output_format = "bookdown::gitbook",
+                        params = list(format = "html"))
+  bookdown::render_book(input='_bookdown.yml', config_file='_bookdown.yml',
+                        output_format = "bookdown::pdf_book",
+                        params = list(format = "latex"))
+}
+
 #=============

### 2021-09-14 R/Plots_Tables.R

@@ -101,7 +101,7 @@ perc_females <- function(perc = TRUE, digits = 2){
 
 #----    get_table_cluster    ----
 
-get_table_cluster <- function(perc = TRUE, digits = 2){
+get_table_cluster <- function(perc = TRUE, digits = 2, format = "latex"){
 
   data_cluster %>%
     select(father, mother) %>%
@@ -112,7 +112,7 @@ get_table_cluster <- function(perc = TRUE, digits = 2){
     ungroup() %>%
     bind_rows(tibble(mother = "Total",
                      summarise_at(., vars(Secure:Total), sum))) %>%
-    kable(., format = "latex", booktabs = TRUE, align = c("r", rep("c", 5)),
+    kable(., format = format, booktabs = TRUE, align = c("r", rep("c", 5)),
           col.names = c("Mother Attachemnt", "Secure", "Anxious", "Avoidant", "Fearful", "Total"),
           caption = "Attachment styles frequencies ($n_{subj} = 847$).") %>%
     add_header_above(c(" ", "Father Attachment" = 4, " "), bold = TRUE) %>%

### 2021-09-14 docs/attachment-bayes-factor.tex
first version bookdown template

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{book}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach},
  pdfauthor={Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{booktabs}
\usepackage{amsthm}
\makeatletter
\def\thm@space@setup{%
  \thm@preskip=8pt plus 2pt minus 4pt
  \thm@postskip=\thm@preskip
}
\makeatother

%----    define infoboxes    ----%
\usepackage{tcolorbox}
\usepackage{xcolor}

% colors
\definecolor{background}{HTML}{fcfcfc}
\definecolor{tip-text}{HTML}{e7b002}
\definecolor{tip-line}{HTML}{fdce38}
\definecolor{warning-text}{HTML}{b06336}
\definecolor{warning-line}{HTML}{c97d50}
\definecolor{deffun-text}{HTML}{0b797e}
\definecolor{deffun-line}{HTML}{6CC2C9}
\definecolor{design-text}{HTML}{7c972e}
\definecolor{design-line}{HTML}{a7c84a}
\definecolor{trick-text}{HTML}{8c3031}
\definecolor{trick-line}{HTML}{A3595A}

\newtcolorbox{mybox}[1][black]{
  colback=background,
  coltext=black,
  colframe=#1,
  boxsep=5pt,
  arc=4pt}

% tip
\newenvironment{tip}[1][Title]
  {
  \setlength{\fboxsep}{1em}
  \begin{mybox}[tip-line]
    \raisebox{-.2\height}{\includegraphics[height=.6cm]{images/lightbulb.png}} \large \textcolor{tip-text}{Tip-Box: #1}
    \vspace{1em}
    }
    {
  \end{mybox}
  }

% warning
\newenvironment{warning}[1][Title]
  {
  \setlength{\fboxsep}{1em}
  \begin{mybox}[warning-line]
    \raisebox{-.2\height}{\includegraphics[height=.6cm]{images/gotcha.png}} \large \textcolor{warning-text}{Warning-Box: #1}
    \vspace{1em}
    }
    {
  \end{mybox}
  }

% deffun
\newenvironment{deffun}[1][Title]
  {
  \setlength{\fboxsep}{1em}
  \begin{mybox}[deffun-line]
    \raisebox{-.2\height}{\includegraphics[height=.6cm]{images/gears.png}} \large \textcolor{deffun-text}{Definition-Box: #1}
    \vspace{1em}
    }
    {
  \end{mybox}
  }

% design
\newenvironment{design}[1][Title]
  {
  \setlength{\fboxsep}{1em}
  \begin{mybox}[design-line]
    \raisebox{-.2\height}{\includegraphics[height=.6cm]{images/design.png}} \large \textcolor{design-text}{Design-Box: #1}
    \vspace{1em}
    }
    {
  \end{mybox}
  }

% trick
\newenvironment{trick}[1][Title]
  {
  \setlength{\fboxsep}{1em}
  \begin{mybox}[trick-line]
    \raisebox{-.2\height}{\includegraphics[height=.6cm]{images/hat.png}} \large \textcolor{trick-text}{Trick-Box: #1}
    \vspace{1em}
    }
    {
  \end{mybox}
  }

\usepackage{titlepic}
\titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\title{Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supplemental Material}
\author{Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
\date{2021-09-14}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{1}
\tableofcontents
}
\begin{verbatim}
## i Loading Attachment
\end{verbatim}

\hypertarget{prerequisites}{%
\chapter*{Prerequisites}\label{prerequisites}}
\addcontentsline{toc}{chapter}{Prerequisites}

trial

\hypertarget{intro}{%
\chapter{Introduction}\label{intro}}

trial code

\begin{verbatim}
##   ID ID_class externalizing_sum internalizing_sum gender age_year Avm      Avp
## 1 25        2                16                 7      F     8.42 1.0 1.000000
## 2 27        2                 3                 3      F     9.00 2.0 2.166667
## 3 29        2                 5                 5      M     9.00 3.5 2.200000
## 4 30        2                11                11      M     8.92 1.6 2.666667
## 5 31        2                 0                 1      F     9.00 2.0 2.800000
## 6 32        2                 4                12      F     8.92 3.0 2.833333
##        av_m      av_p     Anxm     Anxp     anx_m     anx_p  mother   father
## 1 1.0000000 1.0000000 1.000000 1.000000 0.8333333 1.0000000  Secure   Secure
## 2 1.0000000 1.0000000 1.000000 1.000000 1.0000000 1.0000000 Anxious   Secure
## 3 1.0000000 0.8333333 1.500000 2.400000 1.0000000 0.8333333 Fearful  Anxious
## 4 0.8333333 1.0000000 1.600000 1.666667 0.8333333 1.0000000 Anxious Avoidant
## 5 1.0000000 0.8333333 1.833333 1.333333 1.0000000 1.0000000 Anxious Avoidant
## 6 1.0000000 1.0000000 3.200000 2.833333 0.8333333 1.0000000 Anxious  Fearful
##            interaction
## 1    M_Secure_F_Secure
## 2   M_Anxious_F_Secure
## 3  M_Fearful_F_Anxious
## 4 M_Anxious_F_Avoidant
## 5 M_Anxious_F_Avoidant
## 6  M_Anxious_F_Fearful
\end{verbatim}

plot trial

\includegraphics{attachment-bayes-factor_files/figure-latex/unnamed-chunk-3-1.pdf}

table trial

\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-4}Attachment styles frequencies ($n_{subj} = 847$).}
\centering
\begin{tabular}[t]{rccccc}
\toprule
\multicolumn{1}{c}{\textbf{ }} & \multicolumn{4}{c}{\textbf{Father Attachment}} & \multicolumn{1}{c}{\textbf{ }} \\
\cmidrule(l{3pt}r{3pt}){2-5}
\textbf{Mother Attachemnt} & \textbf{Secure} & \textbf{Anxious} & \textbf{Avoidant} & \textbf{Fearful} & \textbf{Total}\\
\midrule
Secure & 125 & 49 & 49 & 8 & 231\\
Anxious & 51 & 100 & 98 & 37 & 286\\
Avoidant & 25 & 67 & 126 & 12 & 230\\
Fearful & 5 & 14 & 38 & 43 & 100\\
Total & 206 & 230 & 311 & 100 & 847\\
\bottomrule
\end{tabular}
\end{table}

trial citation

\citep{guApproximatedAdjustedFractional2018}

troppe cit \citep{mcelreathStatisticalRethinkingBayesian2020}

  \bibliography{../Biblio-attachment.bib}

\end{document}

### 2021-09-17 Documents/Bookdown/01-case-study.Rmd
add first part bookdwon chpter descriptive stsatistics

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Case Study {#case-study}

In this chapter, first, we describe the sample included in the study. Subsequently, we present the results of the cluster analysis to classify the different attachment patterns.

For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article].

## The Study Sample

To evaluate the different role of father attachment and mother attachment, we consider `r tot_subj()` Italian children from third to sixth school grade. Only middle-childhood children are included in the analysis (`r tot_subj_older()` participants are excluded as older than 12.3 years and `r tot_subj_NA()` participants are excluded are excluded as the age is missing). The total sample size included in the analysis is `r tot_subj_included()` (`r perc_females()` \% Females). Participants frequencies by grade and gender are reported in Table~\@ref(tab:table-gender-grade).

```{r table-gender-grade, cache=TRUE}
table_gender_grade(format = params$format)
```

Participants age mean is `r var_info("age_year")`. The participants age summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-age).

```{r, cache=TRUE}
var_summary("age_year")
```

```{r plot-age, cache=TRUE, fig.cap="Participants age distribution ($n_{subj} = 847$)"}
plot_age_dist()
```

## Attachment Styles

Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale (ECR; [TODO add references]) completed by the children. Four main attachment styles have been recognized in the literature according to thee levels of *anxiety* and *avoidance*:

- **Secure Attachment -** children with low levels of anxiety and avoidance.
- **Anxious Attachment -** children characterized by high levels of anxiety.
- **Avoidant Attachment -** children characterized by high levels of avoidance.
- **Fearful Attachment -** children with high levels of anxiety and avoidance.

To identify children attachment styles towards the mother and towards the father, we conduct two separate cluster analyses. Clusters are obtained using the function `hclust()` (with argument `method="ward.D"`) considering *Euclidean* distances between participants responses to the ECR items.

### Mother Cluster Analysis

Regarding mother attachment, 4 groups are selected from the cluster analysis results (see Figure~\@ref(fig:plot-cluster-mother)).

```{r plot-cluster-mother, cache=TRUE, fig.cap = "Mother attachment cluster dendrogram ($n_{subj} = 847$)."}
plot(cluster_mother_fit, main = NULL,  xlab="ECR Mother")
rect.hclust(cluster_mother_fit, k=4, border="red")
```

In Figure~\@ref(fig:plot-scores-mother), Anxiety (“*Anx*”) and Avoidance (“*Av*”) scores are presented according to mother attachment styles. The frequencies of mother attachment styles according to gender are reported in Table~\ref{tab:table-cluster-mother}.

```{r plot-scores-mother, cache=TRUE, fig.asp=.55, fig.cap="Anxiety (“Anx”) and Avoidance (“Av”) scores according to mother attachment styles. Dashed lines represents overall average values ($n_{subj} = 847$)."}
plot_scores_cluster(parent = "mother")
```

```{r table-cluster-mother, cache=TRUE}
table_parent_clusters(parent = "mother", format = params$format)
```

Compared to the overall average values of anxiety and avoidance, we can observe that:

- *Secure* children have lower levels of anxiety and avoidance 
- *Anxious* children have higher levels of anxiety and about the average levels of avoidance
- *Avoidant* children have lower levels of anxiety and higher levels of avoidance
- *Fearful* children have higher levels of anxiety and avoidance

These results reflect the traditional definition of the four attachment styles. Moreover, attachment styles frequencies are in lines with general results in the literature [TODO: add reference values].

#### Mclust Check {-}

To evaluate if 4 cluster is an appropriate choice, we compare the BIC values of different model-based clustering options. To do that we use the function `mclustBIC()` from the `mclust` R-package [@scruccaMclustClusteringClassification2016]. BIC values of the best three model-based clustering are reported below and overall results are presented in Figure~\@ref(fig:plot-mclust-mother). See `?mclustBIC()` help page for further information.

```{r mother-mclust, cache=TRUE}
parent_mclust(parent = "mother")
```

```{r plot-mclust-mother, fig.cap="BIC values of different model-based clustering options. See '?mclustBIC()' help page for further information."}
plot(mclust_mother)
```

Results indicate the possible presence of a larger number of clusters. However, considering only 4 clusters seems to us the most reasonable choice. This is in line with attachment theory and general results in the literature. The important thing is hat no smaller number of clusters provided better results than the division in 4 clusters.

### Father Cluster Analysis

Regarding father attachment, 4 groups are selected from the cluster analysis results (see Figure~\@ref(fig:plot-cluster-father)).

```{r plot-cluster-father, cache=TRUE, fig.cap = "Father attachment cluster dendrogram ($n_{subj} = 847$)."}
plot(cluster_father_fit, main = NULL,  xlab="ECR Father")
rect.hclust(cluster_father_fit, k=4, border="red")
```

In Figure~\@ref(fig:plot-scores-father), Anxiety (“*Anx*”) and Avoidance (“*Av*”) scores are presented according to father attachment styles. The frequencies of father attachment styles according to gender are reported in Table~\ref{tab:table-cluster-father}.

```{r plot-scores-father, cache=TRUE, fig.asp=.55, fig.cap="Anxiety (“Anx”) and Avoidance (“Av”) scores according to father attachment styles. Dashed lines represents overall average values ($n_{subj} = 847$)."}
plot_scores_cluster(parent = "father")
```

```{r table-cluster-father, cache=TRUE}
table_parent_clusters(parent = "father", format = params$format)
```

Compared to the overall average values of anxiety and avoidance, we can observe that:

- *Secure* children have lower levels of anxiety and avoidance 
- *Anxious* children have lower levels of anxiety and avoidance
- *Avoidant* children have lower levels of anxiety and higher levels of avoidance
- *Fearful* children have higher levels of anxiety and avoidance

These results are no as good as in the mother attachment classification, but they are still reasonable. Moreover, attachment styles frequencies are close to the general results in the literature [TODO: add reference values].

#### Mclust Check {-}

To evaluate if 4 cluster is an appropriate choice, we compare the BIC values of different model-based clustering options as before.  BIC values of the best three model-based clustering are reported below and overall results are presented in Figure~\@ref(fig:plot-mclust-father).

```{r father-mclust, cache=TRUE}
parent_mclust(parent = "father")
```

```{r plot-mclust-father, fig.cap="BIC values of different model-based clustering options. See '?mclustBIC()' help page for further information."}
plot(mclust_father)
```

As for the mother, results indicate the possible presence of a larger number of clusters. However, considering only 4 clusters seems to us the most reasonable choice for the same reasons as before.

### Mother and Father

The frequencies of mother attachment and father attachment styles are reported in Table~\@ref(tab:table-cluster-mother-father).

```{r table-cluster-mother-father, cache=TRUE}
table_mother_father_clusters(format = params$format)
```

We can observe how values on the diagonal (same attachment styles towards both parents) tends to be larger than others.

## Children Outcomes

Children's social-emotional development was measured using the Strength \& Difficulties Questionnaire (SDQ; [TODO add references]) completed by the teachers. Separate scores for externalizing and internalizing problems were obtained as sum of the questionnaire items.

### Externalizing Problems

Participants externalizing problems mean is `r var_info("externalizing_sum")`. The participants externalizing problems summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-externalizing-dist).

```{r, cache=TRUE}
var_summary("externalizing_sum")
```

```{r plot-externalizing-dist, cache=TRUE, fig.cap="Participants externalizing problems distribution ($n_{subj} = 847$)"}
plot_problems_dist("ext")
```

Externalizing problems according to attachment styles are reported in Table~\@ref(tab:table-cluster-ext).

```{r table-cluster-ext, cache=TRUE}
get_table_cluster_prob("ext", format = params$format)
```

### Internalizing Problems

Participants internalizing problems mean is `r var_info("internalizing_sum")`. The participants internalizing problems summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-internalizing-dist).

```{r, cache=TRUE}
var_summary("internalizing_sum")
```

```{r plot-internalizing-dist, cache=TRUE, fig.cap="Participants internalizing problems distribution ($n_{subj} = 847$)"}
plot_problems_dist("int")
```

Internalizing problems according to attachment styles are reported in Table~\ref(tab:table-cluster-ext).

```{r table-cluster-int, cache=TRUE}
get_table_cluster_prob("int", format = params$format)
```

### 2021-09-17 Documents/Bookdown/02-ext.Rmd
add first part bookdwon chpter descriptive stsatistics

# Externalizing Problems {#ext}

blah blaah

[@guApproximatedAdjustedFractional2018]

### 2021-09-17 Documents/Bookdown/index.Rmd
add first part bookdwon chpter descriptive stsatistics

@@
 subtitle: "Supplemental Material"
-author: "Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
+author: "[Claudio Zandonella Callegher](https://claudiozandonella.netlify.app/), Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
 date: "`r Sys.Date()`"
@@
 github-repo: ClaudioZandonella/Attachment
-description: "This the Suppleemental Material of the article ..."
+description: "This the Supplemental Material of the article “Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach”"
 cover-image: "images/logo_psicostat.png"
@@
                       tidy=TRUE, tidy.opts = list(width.cutoff = 80),
-                      # comment = NA, prompt = TRUE
+                      # comment = NA, prompt = TRUE,
+                      collapse = TRUE,
 
@@
 ## ggplot settings
-theme_set(theme_classic()+
+theme_set(theme_bw()+
             theme(text = element_text(size=12)))
@@
 
-drake_load_paper()
+drake_load_bookdown()
 ```
 
-# Prerequisites {-}
+# Introduction {-}
 
-trial
+This is the Supplemental Material of the article “*Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach*” [TODO: add cit].
+The aim of the paper is to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.
+
+## Study Summary {-}
+
+When conducting a study, researchers usually have expectations based on hypotheses or theoretical perspectives they want to evaluate.
+Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called “*informative hypotheses*”.
+However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are unsuitable for testing complex informative hypotheses.
+An alternative approach is to use the Bayes Factor.
+In particular, the Bayes Factor based on the “*encompassing prior approach*” allows researchers to easily evaluate complex informative hypotheses.
+In this paper we provide a clear and detailed introduction to this approach.
+We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor following the encompassing prior approach.
+Subsequently, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development.
+
+## Supplemental Material Structure {-}
+
+In the supplemental material we provide the complete statistical analyses of the case study regarding attachment.
+For more information regarding the Bayes Factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article].
+The supplemental material is structure as follow:
+
+- **Chapter \@ref(case-study) - Case Study.** We describe the sample included in the study and present the results of the cluster analysis to classify the different attachment patterns.
+- **Chapter \@ref(ext) - Externalizing Problems.** The analyses regarding externalizing problems are presented.
+First, we conduct the analysis following the traditional NHST approach.
+Subsequently, we consider Bayesian Model Comparison using the WAIC and LOO as criteria.
+Finally, we consider the Bayes Factor with encompassing prior approach.
+- **Chapter \@ref(int) - Internalizing Problems.** The analyses regarding internalizing problems are presented.
+The analyses follow the same structure as the case of externalizing problems.
+Thus, only differences will be highlighted.
+
+## GitHub {-}
+
+All the materials are available at the GitHub repository https://github.com/ClaudioZandonella/Attachment.
+
+Refer to the `README` file for further information.

### 2021-09-17 Documents/Utils_report.R

@@ -102,6 +102,26 @@ drake_load_paper <- function(){
 
 }
 
+drake_load_bookdown <- function(){
+  # Data
+  load_glob_env(data_raw)
+  load_glob_env(data_cluster)
+
+  # Cluster
+  load_glob_env(cluster_mother_fit)
+  load_glob_env(cluster_father_fit)
+
+  load_glob_env(mclust_mother)
+  load_glob_env(mclust_father)
+
+  # BF encompassing
+  load_glob_env(encompassing_model_ext)
+  load_glob_env(BF_weights_ext)
+  load_glob_env(summary_sensitivity_ext)
+
+  load_glob_env(data_prior_predict)
+}
+
 #----    get_sigma_example    ----
 
 get_sigma_example <- function(){

### 2021-09-17 R/Plots.R

@@ -1,6 +1,6 @@
-#=============================#
-#====    Plots & Tables   ====#
-#=============================#
+#=====================#
+#====    Plots    ====#
+#=====================#
 
 #----    get_plot_zinb    ----
 
@@ -84,63 +84,6 @@ plot_bounded_par <- function(){
           axis.ticks.y = element_blank(),
           axis.title.y = element_blank(),
           axis.line.y.left = element_blank())
-}
-
-#----    perc_females    ----
-
-perc_females <- function(perc = TRUE, digits = 2){
-  freq <- table(data_cluster$gender)
-
-  if(isTRUE(perc)){
-    res <- round(freq[1]*100/nrow(data_cluster), digits = digits)
-  } else {
-    res <- freq[1]
-  }
-  return(res)
-}
-
-#----    get_table_cluster    ----
-
-get_table_cluster <- function(perc = TRUE, digits = 2, format = "latex"){
-
-  data_cluster %>%
-    select(father, mother) %>%
-    group_by(father, mother) %>%
-    count() %>%
-    pivot_wider(names_from = father, values_from = n) %>%
-    bind_cols(Total = rowSums(.[, 2:5])) %>%
-    ungroup() %>%
-    bind_rows(tibble(mother = "Total",
-                     summarise_at(., vars(Secure:Total), sum))) %>%
-    kable(., format = format, booktabs = TRUE, align = c("r", rep("c", 5)),
-          col.names = c("Mother Attachemnt", "Secure", "Anxious", "Avoidant", "Fearful", "Total"),
-          caption = "Attachment styles frequencies ($n_{subj} = 847$).") %>%
-    add_header_above(c(" ", "Father Attachment" = 4, " "), bold = TRUE) %>%
-    row_spec(0, bold = TRUE) %>%
-    kable_styling(latex_options = c("hold_position"))
-}
-
-#----    get_table_cluster_ext    ----
-
-get_table_cluster_ext <- function(){
-  data_cluster %>%
-    group_by(father, mother) %>%
-    summarize(mean = my_round(mean(externalizing_sum), 2),
-              median = my_round(median(externalizing_sum), 1),
-              sd =  my_round(sd(externalizing_sum), 2),
-              summary = paste0(mean, " (",
-                               sd, ")")) %>%
[…]

### 2021-09-17 R/Tables.R

@@ -1,0 +1,295 @@
+#=====================#
+#====    Tables   ====#
+#=====================#
+
+#----    get_table_cluster    ----
+
+get_table_cluster <- function(perc = TRUE, digits = 2, format = "latex"){
+
+  data_cluster %>%
+    select(father, mother) %>%
+    group_by(father, mother) %>%
+    count() %>%
+    pivot_wider(names_from = father, values_from = n) %>%
+    bind_cols(Total = rowSums(.[, 2:5])) %>%
+    ungroup() %>%
+    bind_rows(tibble(mother = "Total",
+                     summarise_at(., vars(Secure:Total), sum))) %>%
+    kable(., format = format, booktabs = TRUE, align = c("r", rep("c", 5)),
+          col.names = c("Mother Attachemnt", "Secure", "Anxious", "Avoidant", "Fearful", "Total"),
+          caption = "Attachment styles frequencies ($n_{subj} = 847$).") %>%
+    add_header_above(c(" ", "Father Attachment" = 4, " "), bold = TRUE) %>%
+    row_spec(0, bold = TRUE) %>%
+    kable_styling(latex_options = c("hold_position"))
+}
+
+#----    get_table_cluster_ext    ----
+
+get_table_cluster_ext <- function(){
+  data_cluster %>%
+    group_by(father, mother) %>%
+    summarize(mean = my_round(mean(externalizing_sum), 2),
+              median = my_round(median(externalizing_sum), 1),
+              sd =  my_round(sd(externalizing_sum), 2),
+              summary = paste0(mean, " (",
+                               sd, ")")) %>%
+    select(father, mother, summary, median) %>%
+    pivot_wider(names_from = father, values_from = c(summary, median)) %>%
+    select(mother, dplyr::ends_with("Secure"), dplyr::ends_with("Anxious"),
+           dplyr::ends_with("Avoidant"),  dplyr::ends_with("Fearful")) %>%
+    kable(.,format = "latex", booktabs = TRUE, align = c("r", rep("c", 8)),
+          col.names = c("Mother Attachemnt", rep(c("Mean (SD)", "Median"), 4)),
+          caption = "Externalizing problems according to attachment styles ($n_{subj} = 847$).") %>%
+    add_header_above(c(" ", "Secure" = 2, "Anxious" = 2, "Avoidant" = 2, "Fearful" = 2), bold = TRUE) %>%
[…]

### 2021-09-17 R/Utils.R

@@ -8,6 +8,17 @@ my_round <- function(x, digits = 2){
   format(round(x, digits), nsmall = digits)
 }
 
+#----    my_perc    ----
+
+my_perc <- function(x, digits = 2){
+  format(round(x*100, digits), nsmall = digits)
+}
+
+#----    my_comment    ----
+
+my_comment <- function(x){
+  cat(paste0("  # ", x, "\n"))
+}
 #-------
 
 

### 2021-09-17 R/Values.R

@@ -1,0 +1,138 @@
+#=====================#
+#====    Values   ====#
+#=====================#
+
+#----    perc_females    ----
+
+perc_females <- function(perc = TRUE, digits = 2){
+  freq <- table(data_cluster$gender)
+
+  if(isTRUE(perc)){
+    res <- round(freq[1]*100/nrow(data_cluster), digits = digits)
+  } else {
+    res <- freq[1]
+  }
+  return(res)
+}
+
+#----    perc_rare_condition    ----
+
+perc_rare_condition <- function(perc = TRUE, digits = 1){
+  test <- with(data_cluster,
+               (mother == "Secure" & father == "Fearful") |
+                 (mother == "Fearful" & father == "Secure"))
+
+  if(isTRUE(perc)){
+    res <- round(mean(test)*100, digits = digits)
+  } else {
+    res <- sum(test)
+  }
+  return(res)
+}
+
+#----    tot_subj    ----
+
+tot_subj <- function(){
+  nrow(data_raw)
+}
+
+#----    tot_subj_older    ----
+
+tot_subj_older <- function(){
+  data_raw %>%
+    dplyr::filter(age_year >= 12.3) %>%
+    count()
+}
+
+#----    tot_subj_NA    ----
+
+tot_subj_NA <- function(){
+  data_raw %>%
+    dplyr::filter(is.na(age_year)) %>%
+    count()
+}
+
+#----    tot_subj_included    ----
+
+tot_subj_included <- function(){
+  nrow(data_cluster)
+}
+
+#----    var_info    ----
+
+var_info <- function(var){
+
+  sd_age <- sd(data_cluster[, var]) %>%
+    my_round()
+  mean_age <- mean(data_cluster[, var]) %>%
+    my_round()
+
+  paste0(mean_age, " (SD = ", sd_age, ")")
+}
+
+#----    var_summary    ----
+
+var_summary <- function(var){
+
+  var_name <- switch(var,
+                     "age_year" = "Age",
+                     "externalizing_sum" = "Externalizing problems")
+  comment <- sprintf("%s summary statistics", var_name)
+  my_comment(comment)
+  summary(data_cluster[,var])
+}
+
+#----    freq_gender    ----
+
+freq_gender <- function(){
+  my_comment("Gender frequencies")
+  table(data_cluster$gender)
+}
+
+#----    freq_grade    ----
+
+freq_grade <- function(){
[…]

### 2021-09-19 Documents/Bookdown/01-case-study.Rmd
fix zero inflatiion and anova analyses

@@
 
-In this chapter, first, we describe the sample included in the study. Subsequently, we present the results of the cluster analysis to classify the different attachment patterns.
+In this chapter, we describe the sample included in the study.
+First we present general information about the sample.
+Subsequently, we present the results of the cluster analysis to classify the different attachment patterns.
+Finally, we consider children's social-emotional problems.
 
@@
 
-### Externalizing Problems
+### Externalizing Problems {-}
 
@@
 
+Overall, externalizing problems are low.
+This is expected as the sample is not a clinical sample.
 Externalizing problems according to attachment styles are reported in Table~\@ref(tab:table-cluster-ext).
@@
 
-### Internalizing Problems
+### Internalizing Problems {-}
 
@@
 
+Overall, internalizing problems are low.
+Again, this is expected as the sample is not a clinical sample.
 Internalizing problems according to attachment styles are reported in Table~\ref(tab:table-cluster-ext).

### 2021-09-19 Documents/Bookdown/02-ext.Rmd
fix zero inflatiion and anova analyses

@@
+---
+output: html_document
+editor_options: 
+  chunk_output_type: console
+---
 # Externalizing Problems {#ext}
 
-blah blaah
+In this chapter, we present the analyses to evaluate the different role of mother attachment and father attachment on children's externalizing problems.
+First, we discuss the appropriate models family to to take into account data characteristics.
+Next we conduct inference following three different approaches: 1) traditional Null Hypothesis Significance Testing (NHST) 2) Model Comparison using the AIC and BIC criteria 3) Bayes Factor with encompassing prior approach.
 
-[@guApproximatedAdjustedFractional2018]
+## Models Family Choiche
+
+Externalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20.
+Thus, we should use appropriate discrete distribution such as the *Poisson* distribution or the *Negative Binomial*.
+In the Poisson distribution mean and variance are defined according to the same parameter $\lambda$.
+On the contrary, Negative Binomial has an extra parameter to adjust the variance allowing more flexibility.
+Considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe that data have high dispersion with a long right tail.
+In this case, Poisson distribution would be a poor choice and we prefer Negative Binomial instead.
+
+Again, considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe an high peak of values at zero.
+Remember that this is not a clinical sample, thus it is expected that children majority has no problems or really few problem.
+We could question ourselves, however, whether a *Zero-Inflated* model may be appropriate
+
+### Zero Inflated Negative Binomial
+
+To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model.
+We consider in the model the role of gender and the interaction between mother attachment and father attachment.
+Moreover, we consider the children's classroom ID as a random effect to account for teachers' different ability to evaluate children's problems.
+Using R formula syntax, we have
+```{r echo = TRUE, eval=FALSE}
+# model formula
+externalizing_sum ~ gender + mother * father + (1|ID_class)
+```
+
+The model is fitted using the function `glmmTMB()` from the `glmmTMB` R-package [@brooksGlmmTMBBalancesSpeed2017].
+Next, we compare the number of observed zero and expected zeros using an adapted version the function `check_zeroinflation()` from the R-package `performance` [@ludeckePerformancePackageAssessment2021] that solves a small bug (see issue https://github.com/easystats/performance/issues/367).
+```{r echo = TRUE, cache=TRUE}
+my_check_zeroinflation(fit_ext_nb)
+```
+
+Results indicate that the model is slightly under-fitting the number of zeros.
+Now, we can try to fit a *Zero Inflated Negative Binomial* (ZINB) model and compare the performance of the two models.
+ZINB models are defined as
+$$
+y_{i} \sim ZINB(p_{i}, \mu_{i}, \phi),
+$$
+where $p_i$ is the probability of an observation $y_{i}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_i$ indicates the probability of a given observation $y_{i}$ being generated form a Negative Binomial distribution with mean $\mu_{i}$ and variance $\sigma_{i}^2 = \mu_{i} + \frac{\mu_{i}^2}{\phi}$.
+Moreover, we have that
+$$
+p_{i} = \text{logit}^{-1}(X_i^T\beta_p),\\
+\mu_{i} = \text{exp}(X_i^T\beta_{\mu}).
+$$
+That is, both $p$ and $\mu$ are modelled separately according to (possibly) different variables.
+In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ the consider also the interaction between mother attachment and father attachment.
+In both cases, we consider the children's classroom ID as a random effect (teachers may differ in they ability to detect children's problem and quantify them).
+Using R formula syntax, we have
+```{r echo = TRUE, eval=FALSE}
+# formula for p
+p ~ gender + (1|ID_class)
+
+# formula for mu
+mu ~ gender + mother * father + (1|ID_class)
+```
+
+The ZINB model is fitted using the function `zeroinfl()` from the `pscl` R-package [@zeileisRegressionModelsCount2008].
+To compare the ZINB model and the Negative Binomial model we conduct an analysis of *Deviance*.
+Note that, in the case of generalized linear models (GLM), the deviance is the corresponding of the residual variance used in the traditional ANOVA in the case of linear models.
+```{r echo=TRUE, cache=TRUE}
+anova(fit_ext_nb, fit_ext_zinb)
+```
+
+Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses we decide to use ZINB models.
+
+## NHST
+
+Following traditional NHST approach, we consider the model previously defind that includes all possible effects of interest.
+That is the gender effect and the interaction between mother attachment and father attachment.
+Subsequently, we can run an analysis of deviance to evaluate the significance of the predictors using the function `Anova()` from the R-package `car` [@foxCompanionAppliedRegression2019].
+```{r, echo =TRUE, cache=TRUE}
+car::Anova(fit_ext_zinb)
+```
+Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are no significant. Model summary is reported below.
+```{r, echo =TRUE, cache=TRUE}
+summary(fit_ext_zinb)
+```
+To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-nhst-effects).
+Not that the marginal predicted values for gender are averaged over mother and father attachment effects.
+Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
+```{r plot-nhst-effects, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment. Values are averaged over the other effects ($n_{subj} = 847$)."}
+get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
+```

### 2021-09-19 Documents/Utils_report.R

@@ -114,12 +114,23 @@ drake_load_bookdown <- function(){
   load_glob_env(mclust_mother)
   load_glob_env(mclust_father)
 
+  #----    Externalizing    ----
+
+  # Zero inflation
+  load_glob_env(fit_ext_nb)
+
+  # ANOVA
+  load_glob_env(fit_ext_zinb)
+  #load_glob_env(plot_zinb_ext)
+
   # BF encompassing
   load_glob_env(encompassing_model_ext)
   load_glob_env(BF_weights_ext)
   load_glob_env(summary_sensitivity_ext)
 
   load_glob_env(data_prior_predict)
+
+  #----    Internalizing    ----
 }
 
 #----    get_sigma_example    ----

### 2021-09-19 R/Models.R

@@ -2,6 +2,45 @@
 #====    Model Definition    ====#
 #================================#
 
+#----    my_check_zeroinflation    ----
+
+# fix bug glmmTMB in performance::check_zeroinflation()
+# https://github.com/easystats/performance/issues/367
+
+my_check_zeroinflation <- function(x, tolerance = 0.05){
+  model_info <- insight::model_info(x)
+  if (!model_info$is_count) {
+    stop("Model must be from Poisson-family.", call. = FALSE)
+  }
+  obs.zero <- sum(insight::get_response(x, verbose = FALSE) ==
+                    0)
+  if (obs.zero == 0) {
+    insight::print_color("Model has no observed zeros in the response variable.\n",
+                         "red")
+    return(NULL)
+  }
+
+  # get theta
+  if(is(x, "glmmTMB")){
+    theta <- stats::sigma(x)
+  } else {
+    theta <- x$theta
+  }
+  mu <- stats::fitted(x)
+  if (model_info$is_negbin && !is.null(theta)) {
+    pred.zero <- round(sum(stats::dnbinom(x = 0, size = theta,
+                                          mu = mu)))
+  }
+  else {
+    pred.zero <- round(sum(stats::dpois(x = 0, lambda = mu)))
+  }
+  structure(class = "check_zi", list(predicted.zeros = pred.zero,
+                                     observed.zeros = obs.zero, ratio = pred.zero/obs.zero,
+                                     tolerance = tolerance))
+
+}
+
+
 #----    zinb_brms    ----
 
 #' Fit ZINB Model

### 2021-09-19 R/Plan.R

@@ -41,15 +41,16 @@ get_analysis_plan <- function(){
     #=============================
 
     #----    ZINB analysis    ----
-    fit_int_nb = MASS::glm.nb(internalizing_sum ~ gender + mother * father,
-                              data = data_cluster),
-    test_zero_inflated_int = performance::check_zeroinflation(fit_int_nb),
+    fit_int_nb = glmmTMB::glmmTMB(internalizing_sum ~ gender + mother * father + (1|ID_class),
+                                  data = data_cluster, family = glmmTMB::nbinom2()),
+    test_zero_inflated_int = my_check_zeroinflation(fit_int_nb),
 
     #----    anova approach ----
-    fit_int_zinb = pscl::zeroinfl(internalizing_sum ~ gender + mother * father | gender,
-                                  data = data_cluster, dist = "negbin"),
+    fit_int_zinb = glmmTMB::glmmTMB(internalizing_sum ~ gender + mother * father + (1|ID_class),
+                                    ziformula = ~ gender + (1|ID_class),
+                                    data = data_cluster, family = glmmTMB::nbinom2()),
 
-    plot_zinb_int = get_plot_zinb(model = fit_int_zinb),
+    plot_zinb_int = get_plot_zinb(model = fit_int_zinb, attachment = "mother"),
 
     #----    brms Models int    ----
     brm_int_zero = zinb_brms(data = data_cluster,
@@ -125,15 +126,16 @@ get_analysis_plan <- function(){
     #=============================
 
     #----    ZINB analysis    ----
-    fit_ext_nb = MASS::glm.nb(externalizing_sum ~ gender + mother * father,
-                              data = data_cluster),
-    test_zero_inflated_ext = performance::check_zeroinflation(fit_ext_nb),
+    fit_ext_nb = glmmTMB::glmmTMB(externalizing_sum ~ gender + mother * father + (1|ID_class),
+                                  data = data_cluster, family = glmmTMB::nbinom2()),
+    test_zero_inflated_ext = my_check_zeroinflation(fit_ext_nb),
 
     #----    anova approach ----
-    fit_ext_zinb = pscl::zeroinfl(externalizing_sum ~ gender + mother * father | gender,
-                                  data = data_cluster, dist = "negbin"),
+    fit_ext_zinb = glmmTMB::glmmTMB(externalizing_sum ~ gender + mother * father + (1|ID_class),
[…]

### 2021-09-19 R/Plots.R

@@ -14,38 +14,65 @@
 #'
 #' @examples
 #' drake::loadd(fit_int_zinb)
-#' get_plot_zinb(model = fit_int_zinb)
+#' get_plot_zinb(model = fit_int_zinb, attachment = "mother")
 #'
 
-get_plot_zinb <- function(model){
+get_plot_zinb <- function(model, attachment = c("interaction", "mother")){
+  attachment <- match.arg(attachment)
 
-  marginal_effects_gender <- emmeans::emmeans(model, specs = ~ gender)
+  marginal_effects_gender <- emmeans::emmeans(model, specs = ~ gender) %>%
+    as.data.frame() %>%
+    mutate_at(vars(emmean, lower.CL, upper.CL), exp)
 
   p_gender <- ggplot(as.data.frame(marginal_effects_gender),
          aes(x = gender, y = emmean, colour = gender)) +
-    geom_point(show.legend = FALSE) +
-    geom_errorbar(aes(ymin=asymp.LCL, ymax = asymp.UCL, colour = gender),
+    geom_point(show.legend = FALSE, size = 3) +
+    geom_errorbar(aes(ymin=lower.CL, ymax = upper.CL, colour = gender),
                   size = 1, width = .2, show.legend = FALSE) +
     labs(x = "Gender",
          y = "Problems") +
-    coord_cartesian(ylim = c(0, 8)) +
+    coord_cartesian(ylim = c(0, 6)) +
     theme_bw()
 
-  marginal_effects_att <- emmeans::emmeans(model, specs = ~ mother*father)
+  if(attachment == "interaction"){
+    marginal_effects_att <- emmeans::emmeans(model, specs = ~ mother*father) %>%
+      as.data.frame() %>%
+      mutate_at(vars(emmean, lower.CL, upper.CL), exp)
 
-  p_attachemnt <- ggplot(as.data.frame(marginal_effects_att),
-         aes(x = mother, y = emmean, colour = father, group = father)) +
-    geom_point(show.legend = FALSE) +
-    geom_line(show.legend = FALSE) +
-    geom_errorbar(aes(ymin=asymp.LCL, ymax = asymp.UCL, colour = father),
-                  width = .5, show.legend = FALSE) +
-    facet_grid(.~father) +
-    labs(x = "Mother Attachment",
-         y = "Problems") +
-    coord_cartesian(ylim = c(0, 8)) +
-    theme_bw()
[…]

### 2021-09-19 Documents/Bookdown/01-case-study.Rmd
Add first part model comparison ext

@@
 
-```{r plot-mclust-mother, fig.cap="BIC values of different model-based clustering options. See '?mclustBIC()' help page for further information."}
+```{r plot-mclust-mother, cache=TRUE, fig.cap="BIC values of different model-based clustering options. See '?mclustBIC()' help page for further information."}
 plot(mclust_mother)
@@
 
-```{r plot-mclust-father, fig.cap="BIC values of different model-based clustering options. See '?mclustBIC()' help page for further information."}
+```{r plot-mclust-father, cache=TRUE, fig.cap="BIC values of different model-based clustering options. See '?mclustBIC()' help page for further information."}
 plot(mclust_father)

### 2021-09-19 Documents/Bookdown/02-ext.Rmd
Add first part model comparison ext

@@
 
-## Models Family Choiche
+## Models Family Choiche {#model-choice}
 
@@
 
-Following traditional NHST approach, we consider the model previously defind that includes all possible effects of interest.
+Following traditional NHST approach, we consider the model previously defined that includes all effects of interest.
 That is the gender effect and the interaction between mother attachment and father attachment.
@@
 Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
-```{r plot-nhst-effects, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment. Values are averaged over the other effects ($n_{subj} = 847$)."}
+```{r plot-nhst-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment.
+Values are averaged over the other effects ($n_{subj} = 847$)."}
 get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
 ```
+
+Post-hoc test are run to evaluate differences between mother attachment styles.
+To do that we use the `contrast()` function from the `emmeans` R-package, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
+This approach is less restrictive than traditional *“Bonferroni”* method, as it determines the adjustment according to a multivariate *t*-distribution with the same covariance structure as the estimates.
+Results are reported below,
+```{r, cache=TRUE, echo = TRUE}
+emmeans::contrast(emmeans::emmeans(fit_ext_zinb, specs = ~ mother ),
+                  "pairwise", adjust = "mvt")
+```
+
+Overall, results indicate that Males have more externalizing problems than Females and, regarding mother attachment, Fearful children have more problems than Secure children.
+
+To evaluate the fit of model to the data, we used $R^2$.
+In the case of generalized mixed-effects models, however, there are several definitions of $R^2$.
+We computed the *Marginal* $R^2$ and the *Conditional* $R^2$ as suggested by @nakagawaCoefficientDeterminationR22017.
+*Marginal* $R^2$ is concerned with the variance explained by fixed factors of the model, and *Conditional* $R^2$ is concerned with the variance explained by both fixed and random factors of the model.
+To do that we use the function `performance::r2()`.
+
+```{r, echo=TRUE, message=FALSE, cache=TRUE}
+performance::r2(fit_ext_zinb)
+```
+
+We can see that the actual variance explained by fixed factors is really small.
+
+#### Conclusions {-}
+
+Considering attachment theoretical perspectives, results indicate only the role of mother attachment.
+Note, however, that traditional NHST does not allow us to evaluate evidence in favour of an hypotheses.
+Moreover, we actually have not tested our hypotheses but only the catch-all null hypothesis that *“nothing is going on”*.
+
+## Model Comparison
+
+Model comparison allows us to compare multiple hypotheses and identify which is the most supported by the data [@mcelreathStatisticalRethinkingBayesian2020].
+First, we need to formalize models according to our hypotheses.
+Subsequently,we can evaluate which is the most supported model among those considered according to the data using the AIC and BIC [@wagenmakersAICModelSelection2004; @akaike1973a; @schwarzEstimatingDimensionModel1978].
+
+### Formalize Models
+
+Following the same reasons as before (see Section~\@ref(model-choice)), we consider Zero Inflated Negative Binomial Mixed-Effects models.
+Again, we consider only the role of gender as fixed effect and children's classroom ID as random effect for $p$.
+Whereas, considering $\mu$, we define four different models to take into account the different theoretical perspectives:
+
+- `fit_ext_zero`: we consider only the effect of gender. This model assumes that attachment plays no role.
+- `fit_ext_mother`: we consider the additive effects of gender and mother attachment. This model supports the idea that only mother attachment is important (**Monotropy Theory**).
+- `fit_ext_additive`: we consider the additive effects of gender,  mother attachment, and father attachment.
+This model supports the idea that both mother attachment and father attachment are important, but not their interaction (**Hierarchy Theory** or **Independence Theory**).
+- `fit_ext_inter`: we consider the additive effects of gender and the interaction between mother attachment and father attachment.
+This model supports the idea that the interaction between mother attachment and father attachment is important (**Integration Theory**).
+
+Moreover, in all models we include children's classroom ID as random effect to take into  account teachers' different ability to evaluate children's problems. Using R formula syntax, we have
+```{r, echo = TRUE, eval=FALSE}
+# formula for p (same for all models)
+p ~ gender + (1|ID_class)
+
+# formula for mu
+
+# fit_ext_zero
+mu ~ gender + (1|ID_class)
+
+# fit_ext_mother
+mu ~ gender + mother + (1|ID_class)
+
+# fit_ext_additive
+mu ~ gender + mother + father + (1|ID_class)
+
+# fit_ext_inter
+mu ~ gender + mother * father + (1|ID_class)
+```
+
+### AIC and BIC Results
+
+After estimating the models, the AIC and BIC values together with their relative weights are computed. Results are reported in Table~\@ref(tab:table-AIC-BIC-weights).
+
+```{r table-AIC-BIC-weights}
+get_table_AIC_BIC(AIC_weights = AIC_weights_ext,
+                  BIC_weights = BIC_weights_ext,
+                  problem = "ext",
+                  format = params$format,
+                  path_img = "images/")
+```
+
+Accordinng to AIC, the most likely model is `fit\_ext\_mother` (92\%) and the second most likely model is `fit\_ext\_additive` (8\%) given the data and the set of models considered.
+According to BIC, instead,  the most likely model is `fit\_ext\_zero` (78\%) and the second most likely model is `fit\_ext\_mother` (22\%) given the data and the set of models considered.
+
+To interpret these results note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
+As pointed by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
+We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.
+
+### Selected Model

### 2021-09-19 Documents/Utils_report.R

@@ -48,12 +48,18 @@ drake_load_all <- function(){
 
   #----    Internalizing    ----
 
-  # ZINB anlaysis
+  # ZINB analysis
   load_glob_env(fit_int_nb)
 
   # ANOVA
   load_glob_env(fit_int_zinb)
   load_glob_env(plot_zinb_int)
+
+  # model comparison
+  load_glob_env(fit_int_zero)
+  load_glob_env(fit_int_mother)
+  load_glob_env(AIC_weights_int)
+  load_glob_env(BIC_weights_int)
 
   # brms models
   load_glob_env(brm_int_mother)
@@ -68,12 +74,18 @@ drake_load_all <- function(){
 
   #----    Externalizing    ----
 
-  # ZINB anlaysis
+  # ZINB anslysis
   load_glob_env(fit_ext_nb)
 
   # ANOVA
   load_glob_env(fit_ext_zinb)
   load_glob_env(plot_zinb_ext)
+
+  # model comparison
+  load_glob_env(fit_ext_zero)
+  load_glob_env(fit_ext_mother)
+  load_glob_env(AIC_weights_ext)
+  load_glob_env(BIC_weights_ext)
 
   # brms models
   load_glob_env(brm_ext_mother)
@@ -121,7 +133,11 @@ drake_load_bookdown <- function(){
 
   # ANOVA
   load_glob_env(fit_ext_zinb)
-  #load_glob_env(plot_zinb_ext)
+
+  # model comparison
+  load_glob_env(fit_ext_mother)
+  load_glob_env(AIC_weights_ext)
+  load_glob_env(BIC_weights_ext)
 
   # BF encompassing
   load_glob_env(encompassing_model_ext)

### 2021-09-19 R/Models.R

@@ -41,6 +41,19 @@ my_check_zeroinflation <- function(x, tolerance = 0.05){
 }
 
 
+#----    zinb_fit    ----
+
+zinb_fit<- function(data, y, formula){
+
+  formula_mu<- paste0(y ," ~ ", formula, " + (1|ID_class)")
+
+  fit <- glmmTMB::glmmTMB(as.formula(formula_mu),
+                          ziformula = ~ gender + (1|ID_class),
+                          data = data, family = glmmTMB::nbinom2())
+
+  return(fit)
+}
+
 #----    zinb_brms    ----
 
 #' Fit ZINB Model
@@ -85,6 +98,26 @@ zinb_brms <- function(data, y, formula){
   return(fit)
 }
 
+#----    get_model_df    ----
+
+get_model_df<- function(fit){
+
+  if(is(fit, "brmsfit")){
+    n_fixed <- nrow(brms::fixef(fit))
+    n_random <- nrow(fit[["ranef"]])
+  } else {
+    fixed <- glmmTMB::fixef(fit)
+    n_fixed <- length(fixed$cond) + length(fixed$zi)
+
+    random <- glmmTMB::ranef(fit)
+    n_random <- length(random$cond) + length(random$zi)
+  }
+
+  res <- n_fixed + n_random
+
+  return(res)
+}
+
 #----    get_rel_weights    ----
 
 #' Get Relative Fit Criterion Weights
@@ -109,7 +142,7 @@ zinb_brms <- function(data, y, formula){
 #'                 brm_int_inter, ic = "loo")
 #'
 
-get_rel_weights <- function(..., ic = c("waic", "loo")){
+get_rel_weights <- function(..., ic = c("waic", "loo", "AIC", "BIC")){
   ic <- match.arg(ic)
 
   names_fit <- as.list(match.call(), )[-1] %>%
@@ -123,14 +156,20 @@ get_rel_weights <- function(..., ic = c("waic", "loo")){
     fit_ics <- lapply(list_fit, FUN = function(x){
       brms::waic(x)$estimates["waic", 1]
       })
-  } else {
+  } else if(ic == "loo"){
     fit_ics <- lapply(list_fit, FUN = function(x){
       brms::loo(x)$estimates["looic", 1]
     })
+  } else if(ic == "AIC"){
+    fit_ics <- lapply(list_fit, FUN = AIC)
+  } else {
+    fit_ics <- lapply(list_fit, FUN = BIC)
   }
 
[…]

### 2021-09-19 R/Plan.R

@@ -52,6 +52,25 @@ get_analysis_plan <- function(){
 
     plot_zinb_int = get_plot_zinb(model = fit_int_zinb, attachment = "mother"),
 
+    #----    Model Comparison int    ----
+    fit_int_zero = zinb_fit(data = data_cluster, y = "internalizing_sum",
+                            formula = "gender"),
+    fit_int_mother = zinb_fit(data = data_cluster, y = "internalizing_sum",
+                              formula = "gender + mother"),
+    fit_int_additive = zinb_fit(data = data_cluster, y = "internalizing_sum",
+                                formula = "gender + mother + father"),
+    fit_int_inter = zinb_fit(data = data_cluster, y = "internalizing_sum",
+                             formula = "gender + mother * father"),
+
+    # AIC BIC Weights
+    AIC_weights_int = get_rel_weights(fit_int_zero,
+                                      fit_int_mother,
+                                      fit_int_additive,
+                                      fit_int_inter, ic = "AIC"),
+    BIC_weights_int = get_rel_weights(fit_int_zero,
+                                      fit_int_mother,
+                                      fit_int_additive,
+                                      fit_int_inter, ic = "BIC"),
     #----    brms Models int    ----
     brm_int_zero = zinb_brms(data = data_cluster,
                             y = "internalizing_sum",
@@ -136,6 +155,26 @@ get_analysis_plan <- function(){
                                     data = data_cluster, family = glmmTMB::nbinom2()),
 
     plot_zinb_ext = get_plot_zinb(model = fit_ext_zinb, attachment = "mother"),
+
+    #----    Model Comparison ext    ----
+    fit_ext_zero = zinb_fit(data = data_cluster, y = "externalizing_sum",
+                             formula = "gender"),
+    fit_ext_mother = zinb_fit(data = data_cluster, y = "externalizing_sum",
+                               formula = "gender + mother"),
+    fit_ext_additive = zinb_fit(data = data_cluster, y = "externalizing_sum",
+                                 formula = "gender + mother + father"),
+    fit_ext_inter = zinb_fit(data = data_cluster, y = "externalizing_sum",
+                              formula = "gender + mother * father"),
+
+    # AIC BIC Weights
+    AIC_weights_ext = get_rel_weights(fit_ext_zero,
+                                       fit_ext_mother,
+                                       fit_ext_additive,
+                                       fit_ext_inter, ic = "AIC"),
+    BIC_weights_ext = get_rel_weights(fit_ext_zero,
[…]

### 2021-09-19 R/Plots.R

@@ -13,8 +13,8 @@
 #' @return a ggplot object
 #'
 #' @examples
-#' drake::loadd(fit_int_zinb)
-#' get_plot_zinb(model = fit_int_zinb, attachment = "mother")
+#' drake::loadd(fit_ext_zinb)
+#' get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
 #'
 
 get_plot_zinb <- function(model, attachment = c("interaction", "mother")){
@@ -22,16 +22,17 @@ get_plot_zinb <- function(model, attachment = c("interaction", "mother")){
 
   marginal_effects_gender <- emmeans::emmeans(model, specs = ~ gender) %>%
     as.data.frame() %>%
-    mutate_at(vars(emmean, lower.CL, upper.CL), exp)
+    mutate_at(vars(emmean, lower.CL, upper.CL), exp) %>%
+    mutate(gender = recode_factor(gender, "F" = "Female", "M" = "Male"))
 
-  p_gender <- ggplot(as.data.frame(marginal_effects_gender),
-         aes(x = gender, y = emmean, colour = gender)) +
+  p_gender <- ggplot(marginal_effects_gender,
+                     aes(x = gender, y = emmean, colour = gender)) +
     geom_point(show.legend = FALSE, size = 3) +
     geom_errorbar(aes(ymin=lower.CL, ymax = upper.CL, colour = gender),
                   size = 1, width = .2, show.legend = FALSE) +
     labs(x = "Gender",
          y = "Problems") +
-    coord_cartesian(ylim = c(0, 6)) +
+    coord_cartesian(ylim = c(0, 7.5)) +
     theme_bw()
 
   if(attachment == "interaction"){
@@ -39,7 +40,7 @@ get_plot_zinb <- function(model, attachment = c("interaction", "mother")){
       as.data.frame() %>%
       mutate_at(vars(emmean, lower.CL, upper.CL), exp)
 
-    p_attachemnt <- ggplot(as.data.frame(marginal_effects_att),
+    p_attachemnt <- ggplot(marginal_effects_att,
                            aes(x = mother, y = emmean, colour = father, group = father)) +
       geom_point(show.legend = FALSE) +
       geom_line(show.legend = FALSE) +
@@ -57,14 +58,14 @@ get_plot_zinb <- function(model, attachment = c("interaction", "mother")){
       as.data.frame() %>%
[…]

### 2021-09-19 R/Tables.R

@@ -273,6 +273,72 @@ get_table_cluster_prob <- function(prob = c("ext", "int"), format = "html"){
                   full_width = FALSE, font_size = font_size)
 }
 
+#----    get_table_AIC_BIC    ----
+
+# drake::loadd(AIC_weights_ext, BIC_weights_ext)
+get_table_AIC_BIC <- function(AIC_weights = AIC_weights_ext,
+                              BIC_weights = BIC_weights_ext,
+                              problem = c("ext", "int"),
+                              format = c("html", "latex"),
+                              path_img = "Documents/Bookdown/images/"){
+
+  problem <- match.arg(problem)
+  format <- match.arg(format)
+
+  names_plot_AIC <- paste("ball_AIC", problem, c("zero", "mother", "additive",
+                                "inter"), sep = "_")
+  names_plot_BIC <- paste("ball_BIC", problem, c("zero", "mother", "additive",
+                                                 "inter"), sep = "_")
+  images_AIC <- paste0(path_img, names_plot_AIC, ".png")
+  images_BIC <- paste0(path_img, names_plot_BIC, ".png")
+
+  for(i in seq_along(images_AIC)){
+    get_ggplot_balls(data = AIC_weights[i,],
+                     filename = images_AIC[i])
+    get_ggplot_balls(data = BIC_weights[i, ],
+                     filename = images_BIC[i])
+  }
+
+  data_table <- AIC_weights %>%
+    left_join(BIC_weights, by = "names", suffix = c("_AIC", "_BIC")) %>%
+    mutate(img_AIC = "",
+           img_BIC = "") %>%
+    mutate_at(vars(starts_with("weights")), round, 2) %>%
+    mutate_at(vars(starts_with("ic")), round, 1) %>%
+    select(names, df_AIC, ic_AIC, weights_AIC, img_AIC,
+           ic_BIC, weights_BIC, img_BIC)
+
+
+  if(format == "latex"){
+    data_table <- data_table %>%
+      mutate(names = gsub("_", "-", names))
+    col_width <- "1cm"
+    image_size <- 100
+  } else {
+    col_width <- "50pt"
+    image_size <- 125
+  }
+
+  problem_title <- if_else(problem == "ext", "externalizing", "internalizing")
+
+  kable(data_table, format = format, booktabs = TRUE, align = c("r", rep("c", 7)), escape = FALSE,
+          col.names = c("Model", "Df", "AIC", "AIC$_{weights}$", " ",
[…]

### 2021-09-20 Documents/Bookdown/01-case-study.Rmd
pre revision hypotheses matrix

@@
 In this chapter, we describe the sample included in the study.
-First we present general information about the sample.
-Subsequently, we present the results of the cluster analysis to classify the different attachment patterns.
+First we describe the aim of the study.
+Subsequently, we present general information about the sample and the results of the cluster analysis to classify the different attachment patterns.
 Finally, we consider children's social-emotional problems.
+
+## Aim of the Study
+
+The aim of the study is to compare the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social emotional development.
+In the literature, four different main theoretical perspectives have been identified [@brethertonFathersAttachmentTheory2010]:
+
+- **Monotropy Theory** - only the mother has an impact on children's development.
+- **Hierarchy Theory** - the mother has a greater impact on children development than the  the father.
+- **Independence Theory** - all attachment figures are equally important but they affect the children's development differently.
+- **Integration Theory** - to understand the impact on children's development it is necessary to consider attachment relationships taken together.
+
+Contrasting results have been reported by studies investigating which is the “correct” theory.
+No study, however, has tried to properly evaluate the different theoretical perspectives by directly comparing the different hypotheses.
 
@@
 
-### Externalizing Problems {-}
+### Externalizing Problems
 
@@
 
-### Internalizing Problems {-}
+### Internalizing Problems
 

### 2021-09-20 Documents/Bookdown/02-ext.Rmd
pre revision hypotheses matrix

@@
 
-We can see that the actual variance explained by fixed factors is really small.
+We can see that the actual variance explained by fixed effects is almost 10\%, not bad for psychology.
 
@@
 First, we need to formalize models according to our hypotheses.
-Subsequently,we can evaluate which is the most supported model among those considered according to the data using the AIC and BIC [@wagenmakersAICModelSelection2004; @akaike1973a; @schwarzEstimatingDimensionModel1978].
+Subsequently, we can evaluate which is the most supported model among those considered according to the data using the AIC and BIC [@wagenmakersAICModelSelection2004; @akaike1973a; @schwarzEstimatingDimensionModel1978].
 
@@
 
-```{r table-AIC-BIC-weights}
+```{r table-AIC-BIC-weights, cache=TRUE}
 get_table_AIC_BIC(AIC_weights = AIC_weights_ext,
@@
 
-Accordinng to AIC, the most likely model is `fit\_ext\_mother` (92\%) and the second most likely model is `fit\_ext\_additive` (8\%) given the data and the set of models considered.
-According to BIC, instead,  the most likely model is `fit\_ext\_zero` (78\%) and the second most likely model is `fit\_ext\_mother` (22\%) given the data and the set of models considered.
+Accordinng to AIC, the most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "AIC")`\%) and the second most likely model is `fit_ext_additive` (`r perc_model_ext("fit_ext_additive", "AIC")`\%) given the data and the set of models considered.
+According to BIC, instead,  the most likely model is `fit_ext_zero` (`r perc_model_ext("fit_ext_zero", "BIC")`\%) and the second most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "BIC")`\%) given the data and the set of models considered.
 
@@
 ### Selected Model
+
+Considering model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
+```{r, echo =TRUE, cache=TRUE}
+car::Anova(fit_ext_mother)
+```
+Results confirm a statistically significant effect of gender and mother attachment. Model summary is reported below.
+```{r, echo =TRUE, cache=TRUE}
+summary(fit_ext_mother)
+```
+To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects).
+Not that the marginal predicted values for gender are averaged over mother attachment.
+Whereas, the marginal predicted values for mother attachment are averaged over gender.
+```{r plot-comparison-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
+get_plot_zinb(model = fit_ext_mother, attachment = "mother")
+```
+
+Post-hoc test are run to evaluate differences between mother attachment styles, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
+Results are reported below,
+```{r, cache=TRUE, echo = TRUE}
+emmeans::contrast(emmeans::emmeans(fit_ext_mother, specs = ~ mother ),
+                  "pairwise", adjust = "mvt")
+```
+
+Overall, results indicate that Males have more externalizing problems than Females.
+Regarding mother attachment, Fearful and Avoidant children have more problems than Secure children.
+Moreover, also the difference between Anxious and Secure children and the difference between Anxious and Fearful children have a low (but not statistically significant) *p*-value.
+
+To evaluate the fit of model to the data, we computed the *Marginal* $R^2$ and the *Conditional* $R^2$.
+
+```{r, echo=TRUE, message=FALSE, cache=TRUE}
+performance::r2(fit_ext_mother)
+```
+
+We can see that the actual variance explained by fixed effects is around 7\%, not bad for psychology.
+
+#### Conclusions {-}
+
+Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the **Monotropy Theory**.
+Note, however, that the compared models contain no information regarding the expected direction of the effects but we only include/exclude predictors.
+
+## Bayes Factor
+
+To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes Factor with encompassing prior approach.
+See the main article for a detailed introduction to this approach [TODO: add link article].
+
+First, we define the encompassing model.
+Subsequently, we obtain the hypotheses matrices according to the informative hypotheses.
+Next, we compute the Bayes Factor and, finally, we describe the selected model.
+
+### Encompassing Model
+
+We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects model to take into account the characteristics of the dependent variable and its distribution (see Section~\@ref(model-choice)).
+Again, we consider only the role of gender as fixed effect and children’s classroom ID as random effect for $p$.
+Whereas, regarding $\mu$, we consider the interaction between mother and father attachment together with gender as fixed effects and children’s classroom ID as random effect.
+In the R formula syntax, we have
+```{r, echo=TRUE, eval=FALSE}
+# formula for p
+p ~ gender + (1|ID_class)
+
+# formula for mu
+mu ~ gender + mother * father + (1|ID_class)
+```
+
+The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).
+To do that we use the `brm()` fucntion from the `brms` R-package [@burknerBrmsPackageBayesian2017; burknerAdvancedBayesianMultilevel2018a], which is based on STAN [@standevelopmentteamRStanInterfaceStan2020].
+
+#### Prior Choiche {-}
+
+Prior choice is important for the parameters involved in the equality and inequality constraints.
+In our case, the parameters of interest (i.e., those related to mother and father attachment interaction) are unbounded.
+Thus, we can simply specify as prior a normal distribution with mean 0 and a given standard deviation.
+Considering the standard deviation, however, we have to choose a value so that the resulting prior is non-informative but without being excessively diffuse.
+
+We can evaluate the consequences of different values choice considering the resulting prior predictions.
+To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest.
+Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1, because $exp(1) \approx 2.7$ that is close to the externalizing problems sample mean  `r ext_mean()`.
+In Table~\@ref(table-prior-predict), summary information about prior predictions for different standard deviation values are reported.
+```{r table-prior-predict}
+get_table_prior_predict(format = params$format)
+```
+
+Considering that externalizing problems are bounded between 0 and 20, a reasonable prior is  $\mathcal{N}(0,3)$.
+as prior predicted values cover all possible values without including excessively large values.
+More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values.
+The influence of prior specification will be subsequently evaluated in a prior sensitivity analysis.
+
+Regarding the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) `brms` default priors are maintained. The resulting prior settings are
+```{r prior-seettings}
+options(width = 300)
+brms::prior_summary(encompassing_model_ext)
+```
+
+#### Hypotheses Matrices {-}
+
+Finally, note that in this case, we do not need to standardize our parameters as they represent mean groups differences (see main article [TODO: add link article]).

### 2021-09-20 Documents/Utils_report.R

@@ -140,6 +140,8 @@ drake_load_bookdown <- function(){
   load_glob_env(BIC_weights_ext)
 
   # BF encompassing
+  load_glob_env(data_prior_predict)
+
   load_glob_env(encompassing_model_ext)
   load_glob_env(BF_weights_ext)
   load_glob_env(summary_sensitivity_ext)

### 2021-09-20 R/Bayes_factor.R

@@ -65,8 +65,8 @@ get_par_names<- function(encompassing_model){
     .[grep("^b_(?!.*(Intercept|zi|gender))", ., perl = TRUE)] %>%
     gsub("^b_", replacement = "", .) %>%  # remove initial "b_"
     gsub("mother", replacement = "M_", .) %>%
-    gsub("father", replacement = "F_", .) %>%
-    gsub(":", replacement = "_", .)
+    gsub("father", replacement = "F_", .)
+    # gsub(":", replacement = "_", .)
 
   return(par_names)
 }

### 2021-09-20 R/Models.R

@@ -43,13 +43,13 @@ my_check_zeroinflation <- function(x, tolerance = 0.05){
 
 #----    zinb_fit    ----
 
-zinb_fit<- function(data, y, formula){
+zinb_fit<- function(data_cluster, y, formula){
 
   formula_mu<- paste0(y ," ~ ", formula, " + (1|ID_class)")
 
   fit <- glmmTMB::glmmTMB(as.formula(formula_mu),
                           ziformula = ~ gender + (1|ID_class),
-                          data = data, family = glmmTMB::nbinom2())
+                          data = data_cluster, family = glmmTMB::nbinom2())
 
   return(fit)
 }

### 2021-09-20 R/Plan.R

@@ -157,13 +157,13 @@ get_analysis_plan <- function(){
     plot_zinb_ext = get_plot_zinb(model = fit_ext_zinb, attachment = "mother"),
 
     #----    Model Comparison ext    ----
-    fit_ext_zero = zinb_fit(data = data_cluster, y = "externalizing_sum",
+    fit_ext_zero = zinb_fit(data_cluster, y = "externalizing_sum",
                              formula = "gender"),
-    fit_ext_mother = zinb_fit(data = data_cluster, y = "externalizing_sum",
+    fit_ext_mother = zinb_fit(data_cluster, y = "externalizing_sum",
                                formula = "gender + mother"),
-    fit_ext_additive = zinb_fit(data = data_cluster, y = "externalizing_sum",
+    fit_ext_additive = zinb_fit(data_cluster, y = "externalizing_sum",
                                  formula = "gender + mother + father"),
-    fit_ext_inter = zinb_fit(data = data_cluster, y = "externalizing_sum",
+    fit_ext_inter = zinb_fit(data_cluster, y = "externalizing_sum",
                               formula = "gender + mother * father"),
 
     # AIC BIC Weights

### 2021-09-20 R/Tables.R

@@ -48,15 +48,21 @@ get_table_cluster_ext <- function(){
 
 #----    get_table_prior_predict    ----
 
-get_table_prior_predict <- function(data = data_prior_predict){
+# drake::loadd(data_prior_predict)
+
+get_table_prior_predict <- function(data = data_prior_predict, format = c("latex", "html")){
+  format <- match.arg(format)
+
   data %>%
     dplyr::select(- prior_sd) %>%
     mutate_if(is.numeric, round, 1) %>%
-    kable(., booktabs = TRUE, align = c("r", rep("c", 5)), escape = FALSE,
-          col.names = c("Prior", "- 1 SD", "- .5 SD", "+ 0 SD", "+ .5 SD", "+ 1 SD"),
+    kable(., format = format, booktabs = TRUE, align = c("r", rep("c", 5)), escape = FALSE,
+          col.names = c("Prior", "$-1$ SD", "$-.5$ SD", "$+0$ SD", "$+ .5$ SD", "$+ 1$ SD"),
           caption = "Prior prediction acording to different prior settings assuming $exp(1)$ as intercept value.") %>%
     add_header_above(c(" " = 1, "Predicted Problems" = 5)) %>%
-    kable_styling(latex_options = c("hold_position"))
+    kable_styling(latex_options = c("hold_position"),
+                  bootstrap_options = c("hover", "striped"),
+                  full_width = FALSE)
 }
 #----    get_table_bf    ----
 
@@ -279,7 +285,7 @@ get_table_cluster_prob <- function(prob = c("ext", "int"), format = "html"){
 get_table_AIC_BIC <- function(AIC_weights = AIC_weights_ext,
                               BIC_weights = BIC_weights_ext,
                               problem = c("ext", "int"),
-                              format = c("html", "latex"),
+                              format = c("latex", "html"),
                               path_img = "Documents/Bookdown/images/"){
 
   problem <- match.arg(problem)

### 2021-09-20 R/Values.R

@@ -125,6 +125,24 @@ parent_mclust <- function(parent = c("mother", "father")){
 }
 
 
+#-
+#----    perc_model_ext    ----
+perc_model_ext <- function(model, ic = c("AIC", "BIC")){
+  ic <- match.arg(ic)
+
+  if(ic == "AIC"){
+    res <- AIC_weights_ext[AIC_weights_ext$names == model, "weights"]
+  } else {
+    res <- BIC_weights_ext[BIC_weights_ext$names == model, "weights"]
+  }
+
+  return(my_perc(res, 0))
+}
+#----    ext_mean    ----
+
+ext_mean <- function(){
+  my_round(mean(data_cluster$externalizing_sum))
+}
 #-----
 
 #-------

### 2021-09-20 Documents/Bookdown/02-ext.Rmd
finish first part BF ext

@@
 
-The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).
-To do that we use the `brm()` fucntion from the `brms` R-package [@burknerBrmsPackageBayesian2017; burknerAdvancedBayesianMultilevel2018a], which is based on STAN [@standevelopmentteamRStanInterfaceStan2020].
-
 #### Prior Choiche {-}
@@
 Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1, because $exp(1) \approx 2.7$ that is close to the externalizing problems sample mean  `r ext_mean()`.
-In Table~\@ref(table-prior-predict), summary information about prior predictions for different standard deviation values are reported.
+In Table~\@ref(tab:table-prior-predict), summary information about prior predictions for different standard deviation values are reported.
 ```{r table-prior-predict}
@@
 
-#### Hypotheses Matrices {-}
+#### Posterior{-}
+The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).
+To do that we use the `brm()` function from the `brms` R-package [@burknerBrmsPackageBayesian2017; @burknerAdvancedBayesianMultilevel2018a], which is based on STAN [@standevelopmentteamRStanInterfaceStan2020].
+Summary of the encompassing model is presented below.
+```{r}
+summary(encompassing_model_ext)
+```
 
-Finally, note that in this case, we do not need to standardize our parameters as they represent mean groups differences (see main article [TODO: add link article]).
+### Hypothesis Matrices
+
+For each informative hypothesis, we obtain an hypothesis matrix that translate equality and inequality constraints according to the encompassing model parametrization.
+Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ([TODO: add link]).
+
+Here we present the obtained hypothesis matrices were on the columns we have the parameters of the encompassing model (excluding the intercept) and each row express an equality constraint or an inequality constraint.
+Matrices row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters).
+For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicate the group condition.
+Equality and inequality constraints ar presented separately.
+
+#### Null Hypothesis {-}
+
+- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
+```{r cache=TRUE}
+get_hypothesis_matrix("null", encompassing_model_ext)$eq
+```
+
+- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero). There are no inequality constraints.
+
+#### Monotropy Hypothesis {-}
+
+- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
+```{r cache=TRUE}
+get_hypothesis_matrix("monotropy", encompassing_model_ext)$eq
+```
+
+- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
+```{r cache=TRUE}
+get_hypothesis_matrix("monotropy", encompassing_model_ext)$ineq
+```
+
+#### Hierarchy Hypothesis {-}
+
+- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
+```{r cache=TRUE}
+get_hypothesis_matrix("hierarchy", encompassing_model_ext)$eq
+```
+
+- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
+```{r cache=TRUE}
+get_hypothesis_matrix("hierarchy", encompassing_model_ext)$ineq
+```
+
+#### Independence Hypothesis {-}
+
+- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
+```{r cache=TRUE}
+get_hypothesis_matrix("independence", encompassing_model_ext)$eq
+```
+
+- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
+```{r cache=TRUE}
+get_hypothesis_matrix("independence", encompassing_model_ext)$ineq
+```
+
+#### Integration Hypothesis {-}
+
+- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
+```{r cache=TRUE}
+get_hypothesis_matrix("integration", encompassing_model_ext)$eq
+```
+
+- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
+```{r cache=TRUE}
+get_hypothesis_matrix("integration", encompassing_model_ext)$ineq
+```
+
+### Centering and Adjusting
+
+So far we have specified the encompassing prior, obtained the model posterior distribution, and defined the hypotheses matrices.
+Now, we need to transform our parameters of interest and center the distribution on the constraints focal points of interest.
+We apply the following transformation
+$$
+\beta = R\theta - r
+$$
+but we can ignore $r$ as in all our constraints it is always a vector of zeros.
+
+Next, we get the adjusted prior and the posterior of the transformed parameters vector  $\beta$ (i.e., the parameters that identify the constraints) for each hypothesis. The adjusted prior is given by
+
+$$
+\pi_{adj}(\beta) \sim \mathcal{N}(0, \Sigma_{\beta}) = \mathcal{N}(0, R\Sigma_{\theta}R^T).
+$$
+Note that we set the mean vector to zero. The posterior is given by the same transformation
+$$
+Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\theta}-r, R\hat{\Sigma}_{\theta}R^T).
+$$
+See the main article for more details [TODO: add link].
+
+This adjustment, however, requires the hypothesis matrix $R$ to be *full-row-rank* (i.e., all constraints are linearly independent).
+However, this is not the case of the hierarchy hypothesis.
+To overcome this issue, we follow the solution presented in the main article.
+First define $R^*$ selecting the maximum number of independent rows.
+In this case 15 contrast are independent
+
+```{r cache=TRUE}
+get_hypothesis_matrix("hierarchy", encompassing_model_ext)$hyp[1:15,]
+```
+
+```{r cache=TRUE}
+R <- get_hypothesis_matrix("hierarchy", encompassing_model_ext)$hyp
+```
+
+The remaining contrasts, instead, are obtained as linear combination of the other constraints. In particular,
+```{r, echo = TRUE, cache = TRUE}
+# Constraint 16: [M_Anx_F_Sec - M_Sec_F_Anx]
+all(R["[M_Anx_F_Sec - M_Sec_F_Anx]",] == R["[M_Anx_F_Sec]", ] - R["[M_Sec_F_Anx]", ])
+
+# Constraint 17: [M_Av_F_Sec - M_Sec_F_Av]
+all(R["[M_Av_F_Sec - M_Sec_F_Av]",] == - R["[M_Anx_F_Sec - M_Av_F_Sec]", ] + R["[M_Sec_F_Anx - M_Sec_F_Av]", ] +  R["[M_Anx_F_Sec - M_Sec_F_Anx]", ])
+
+# Constraint 18: [M_Fear_F_Sec - M_Sec_F_Fear] 
+all(R["[M_Fear_F_Sec - M_Sec_F_Fear]",] == R["[M_Av_F_Sec - M_Sec_F_Av]", ] + R["[M_Fear_F_Sec - M_Av_F_Sec]", ] - R["[M_Sec_F_Fear - M_Sec_F_Av]", ])
+```
+
+Before computing the Bayes Factor, note that we have a set of comparable hypotheses as exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero.
+The solution is the trivial solution of simply consider all parameters equal to zero.
+Finally, we do not need to standardize our parameters as they represent mean groups differences.
+See the main article for detailed explanation [TODO: add link article].
+
+### Results and Sensitivity
+
+To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in details in the main article [TODO: add link article].
+Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).
+
+```{r table-bf-results-ext, cache = TRUE}
+get_table_bf(bf_result = BF_weights_ext,
+             path_img = "images/", problem = "ext",
+             format = params$format)
+```
+
+Remember, however, that prior specification affects the Bayes Factor results.
+Therefore, we also evaluate the results considering different prior settings.
+In particular, we consider as possible priors for the parameters of interest:
+
+- $\mathcal{N}(0,.5)$ - unreasonable tight prior
+- $\mathcal{N}(0,1)$ - tighter prior
+- $\mathcal{N}(0,3)$ - original prior
+- $\mathcal{N}(0,5)$ - more diffuse prior
+- $\mathcal{N}(0,10)$ - unreasonably diffuse prior
+
+The results of the prior sensitivity analysis are reported in Table~\@ref(tab:table-sens-prior-analysis-ext).
+
+```{r table-sens-prior-analysis-ext, cache = TRUE}
+get_table_sens_analysis(summary_sensitivity_ext,
+                        format = params$format,
+                        bookdown = TRUE)
+```
+
+Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data.
+However, we can observe two distinct patterns.
+As the prior gets more diffuse, the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
+Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.
+
+To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
+On the contrary, equality constraints are highly affected by the prior definition (see he main article for more details[TODO: add link article]).
+
+All the defined hypotheses include equality constraints.
+Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
+Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).
+
+### Selected Model

### 2021-09-20 R/Bayes_factor.R

@@ -122,6 +122,92 @@ get_model_matrix <- function(){
   return(mm)
 }
 
+#----    get_hyp_rownames    ----
+
+get_hyp_rownames <- function(hypothesis = c("null", "monotropy", "hierarchy",
+                                            "independence", "integration"),
+                             par_names){
+  hypothesis <- match.arg(hypothesis)
+  n_pars <- length(par_names)
+
+  if(hypothesis == "null"){
+    #----    Null Hypothesis    ----
+
+    # names equality constraints
+    names_eq <- par_names
+
+    # names inequality constraints
+    names_ineq <- NULL
+
+  } else if(hypothesis == "monotropy"){
+    #----    Monotropy Hypothesis    ----
+
+    # names equality constraints
+    names_eq <- c("[M_Anx_F_Sec - M_Av_F_Sec]",
+                  par_names[4:n_pars])
+
+    # inequality constraints
+    names_ineq <- c("[M_Anx_F_Sec]",
+                    "[M_Fear_F_Sec - M_Av_F_Sec]")
+
+  } else if(hypothesis == "hierarchy"){
+    #----    Hierarchy Hypothesis    ----
+
+    # names equality constraints
+    names_eq <- c("[M_Anx_F_Sec - M_Av_F_Sec]",
+                  "[M_Sec_F_Anx - M_Sec_F_Av]",
+                  par_names[7:n_pars])
+
+    # inequality constraints
+    names_ineq <- c("[M_Anx_F_Sec]",
+                    "[M_Fear_F_Sec - M_Av_F_Sec]",
+                    "[M_Sec_F_Anx]",
+                    "[M_Sec_F_Fear - M_Sec_F_Av]",
+                    "[M_Anx_F_Sec - M_Sec_F_Anx]",
+                    "[M_Av_F_Sec - M_Sec_F_Av]",
+                    "[M_Fear_F_Sec - M_Sec_F_Fear]")
+
+  } else if(hypothesis == "independence"){
+    #----    Independence Hypothesis    ----
+    # names equality constraints
+    names_eq <- c("[M_Anx_F_Sec - M_Av_F_Sec]",
+                  par_names[7:n_pars])
+
+    # inequality constraints
+    names_ineq <- c("[M_Anx_F_Sec]",
[…]

### 2021-09-20 R/Plan.R

@@ -245,6 +245,13 @@ get_analysis_plan <- function(){
                                                       prior_sensitivity_ext_10),
 
     data_prior_predict = get_data_prior_predict(),
+
+    # selected model
+    brm_selected_ext = brms::brm(brms::bf(externalizing_sum ~ gender + mother + (1|ID_class),
+                                          zi ~ gender + (1|ID_class)),
+                                 family = brms::zero_inflated_negbinomial(),
+                                 data = data_cluster,
+                                 chains = 6, iter = 6000, cores = 6, warmup = 2000, seed = 2021)
   )
 }
 

### 2021-09-20 R/Tables.R

@@ -67,9 +67,13 @@ get_table_prior_predict <- function(data = data_prior_predict, format = c("latex
 #----    get_table_bf    ----
 
 get_table_bf <- function(bf_result = BF_weights_ext,
-                         path_img = "Documents/Paper/figure/"){
+                         path_img = "Documents/Paper/figure/",
+                         problem = c("ext", "int"),
+                         format = c("latex", "html")){
+  format <- match.arg(format)
+  problem <- match.arg(problem)
 
-  names_plot <- paste("ball", c("null", "monotropy", "hierarchy",
+  names_plot <- paste("ball_BF",problem, c("null", "monotropy", "hierarchy",
                                 "independence", "integration"), sep = "_")
   images <- paste0(path_img, names_plot, ".png")
 
@@ -78,11 +82,13 @@ get_table_bf <- function(bf_result = BF_weights_ext,
                      filename = images[i])
   }
 
-  # centerText <- function(text){
-  #   paste0("\\multirow{1}{*}[0pt]{", text, "}")
-  # }
-
-
+  if(format == "latex"){
+    col_width <- "1cm"
+    image_size <- 100
+  } else {
+    col_width <- "50pt"
+    image_size <- 125
+  }
 
   bf_result %>%
     bind_cols(img = "") %>%
@@ -92,21 +98,28 @@ get_table_bf <- function(bf_result = BF_weights_ext,
            weights = round(weights,2)) %>%
     select(hypothesis, bf, weights, img) %>%
     # mutate_at(c("hypothesis", "bf","weights"), centerText) %>%
-    kable(., booktabs = TRUE, align = c("r", rep("c", 3)), escape = FALSE,
+    kable(., format = format, booktabs = TRUE, align = c("r", rep("c", 3)), escape = FALSE,
           col.names = c("Hypothesis", "Bayes Factor", "Posterior Probability", " "),
           caption = "Bayes Factor encompassing model and hypothesis posteriro probabilities  ($n_{subj} = 847$).") %>%
-    column_spec(4, image = spec_image(images, 100, 100),
-                width = "1cm", latex_valign = "m") %>%
+    column_spec(4, image = spec_image(images, image_size, image_size),
+                extra_css = "vertical-align:middle;padding-bottom: 0px;",
[…]

### 2021-09-21 Documents/Bookdown/02-ext.Rmd
end first draaft ext

@@
 $$
-y_{i} \sim ZINB(p_{i}, \mu_{i}, \phi),
+y_{ij} \sim ZINB(p_{ij}, \mu_{ij}, \phi),
 $$
-where $p_i$ is the probability of an observation $y_{i}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_i$ indicates the probability of a given observation $y_{i}$ being generated form a Negative Binomial distribution with mean $\mu_{i}$ and variance $\sigma_{i}^2 = \mu_{i} + \frac{\mu_{i}^2}{\phi}$.
+where $p_{ij}$ is the probability of an observation $y_{ij}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_{ij}$ indicates the probability of a given observation $y_{ij}$ being generated form a Negative Binomial distribution with mean $\mu_{ij}$ and variance $\sigma_{ij}^2 = \mu_{ij} + \frac{\mu_{ij}^2}{\phi}$.
 Moreover, we have that
 $$
-p_{i} = \text{logit}^{-1}(X_i^T\beta_p),\\
-\mu_{i} = \text{exp}(X_i^T\beta_{\mu}).
+p_{ij} = \text{logit}^{-1}(X_i^T\beta_p+ Z_j^Tu_p),\\
+\mu_{ij} = \text{exp}(X_i^T\beta_{\mu}+ Z_j^Tu_{\mu}).
 $$
@@
 
-Accordinng to AIC, the most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "AIC")`\%) and the second most likely model is `fit_ext_additive` (`r perc_model_ext("fit_ext_additive", "AIC")`\%) given the data and the set of models considered.
+According to AIC, the most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "AIC")`\%) and the second most likely model is `fit_ext_additive` (`r perc_model_ext("fit_ext_additive", "AIC")`\%) given the data and the set of models considered.
 According to BIC, instead,  the most likely model is `fit_ext_zero` (`r perc_model_ext("fit_ext_zero", "BIC")`\%) and the second most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "BIC")`\%) given the data and the set of models considered.
@@
 Regarding the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) `brms` default priors are maintained. The resulting prior settings are
-```{r prior-seettings}
+```{r prior-settings-encompassing-ext}
 options(width = 300)
@@
 For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicate the group condition.
-Equality and inequality constraints ar presented separately.
+This is done because when assuming no interaction or no father attachment effect we set constraints directly on the model parameters, instead when constrains involve group comparisons we need to obtain the resulting conditions.
+Equality and inequality constraints are presented separately.
 
@@
 This adjustment, however, requires the hypothesis matrix $R$ to be *full-row-rank* (i.e., all constraints are linearly independent).
-However, this is not the case of the hierarchy hypothesis.
+However, this is not the case of the Hierarchy Hypothesis.
 To overcome this issue, we follow the solution presented in the main article.
@@
 ### Selected Model
+
+One of the limit of the Bayes Factor with the encompassing prior approach is that we only get the selected hypothesis but we do not obtain the actual estimates of the parameters posterior.
+To overcome this limit we rely on Bayesian inference that allows us to effectively estimate the model parameter posteriors.
+
+This time in the model we consider only the role of gender and mother attachment as fixed effects of $\mu$. In the R formula syntax, we have
+```{r, echo=TRUE, eval=FALSE}
+# formula for p
+p ~ gender + (1|ID_class)
+
+# formula for mu
+mu ~ gender + mother + (1|ID_class)
+```
+Again, we specify a normal distribution with mean 0 and standard deviation of 3, $\mathcal{N}(0,3)$, as prior for the beta parameters (i.e., those related to gender and mother attachment).
+Whereas, for the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) `brms` default priors are maintained.
+The resulting prior settings are
+```{r prior-settings-selcted-ext, cache=TRUE}
+brms::prior_summary(brm_selected_ext)
+```
+
+The model is estimated using 6 independent chains with 6,000 iterations (warm-up 2,000). Model summary is presented below.
+```{r cache=TRUE}
+summary(brm_selected_ext)
+```
+
+Marginal effects are presented in Figure~\@ref(fig:plot-marginal-ext) and differences between mother attachment patterns are reported in Figure~\@ref(fig:plot-diff-ext).
+```{r plot-marginal-ext, cache=TRUE, fig.asp=.5, out.width="95%", message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
+plot_post_pred(post_pred_ext, problem = "Externalizing")
+```
+
+```{r plot-diff-ext, cache=TRUE, fig.asp=.5, message=FALSE, fig.cap="Predicted differences between mother attachment patterns ($n_{subj} = 847$)."}
+plot_post_diff(post_pred_ext, problem = "Externalizing")
+```
+
+Overall, results indicate that Males have more externalizing problems than Females.
+Regarding mother attachment, Fearful, Avoidant, and Anxious children have more problems than Secure children.
+Moreover, Fearful children have more problems than Anxious children.
+
+To evaluate the fit of model to the data, we computed the *Bayesian* $R^2$ and using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-ext).
+
+```{r, echo=TRUE, message=FALSE, cache=TRUE}
+r2_ext
+```
+
+```{r plot-ppcheck-ext, cache=TRUE, fig.cap="Posterior predictive check ($n_{subj} = 847$).", message=FALSE,}
+my_pp_check(brm_selected_ext, problem = "Externalizing")
+```
+
+We can see that the actual variance explained by fixed effects and random effect is around 15\%. Moreover, posterior predictive check indicates a good fit to the data.
+
+#### Conclusions{-}
+
+Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the Monotropy Theory.
+
+## Conclusions Externalizing Problems
+
+Overall, we obtained consistent results from the three different approaches.
+Males have more problems than Females and, regarding attachment, only mother attachment influence children's externalizing problems.
+In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children heave the highest level of problems.
+Taken together, these results support the Monotropy Theory.
+
+Although if the different approaches lead to apparently similar results, the rigorous interpretation of the results is very different.
+
+- Considering the NHST approach, we actually only found that it is unlikely that mother attachment has no effect.
+Thus, we reject the null hypothesis but we can not quantify the evidence in favour of any of our hypotheses.
+- Only model comparison allow us to quantify the relative evidence of our models.
+Model comparison results clearly indicated evidence in favour of an effect of mother attachment but not father attachment.
+However, using information criteria we could not directly evaluate our informative hypotheses regarding the expected effects, but only the presence of any effect.
+- Bayes Factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects.
+Results clearly selected the Monotropy theory as the most likely theory among those considered.
+
+Summarizing, the apparently identical results actually have a completely different meaning and what we learn from the data is very different.
+Hopefully, now it is clear that statistical inference is a complex process that requires careful thinking.
+In particular, to answer to the questions we are actually interested in, we need to apply the appropriate statistical techniques.

### 2021-09-21 Documents/Bookdown/index.Rmd
fix zero inflatiion and anova analyses
end first draaft ext

@@
                       # Plot settings
-                      # dev = "tikz", dev.args=list(pointsize=12),fig.align='center',
+                      fig.align='center',
+                      # dev = "tikz", dev.args=list(pointsize=12),
                       # fig.height=3, fig.width=5, fig.pos = "!ht",
@@
 First, we conduct the analysis following the traditional NHST approach.
-Subsequently, we consider Bayesian Model Comparison using the WAIC and LOO as criteria.
+Subsequently, we consider Model Comparison using the AIC and BIC criteria.
 Finally, we consider the Bayes Factor with encompassing prior approach.

### 2021-09-21 Documents/Utils_report.R

@@ -148,6 +148,9 @@ drake_load_bookdown <- function(){
 
   load_glob_env(data_prior_predict)
 
+  load_glob_env(brm_selected_ext)
+  load_glob_env(post_pred_ext)
+  load_glob_env(r2_ext)
   #----    Internalizing    ----
 }
 

### 2021-09-21 R/Models.R

@@ -98,6 +98,24 @@ zinb_brms <- function(data, y, formula){
   return(fit)
 }
 
+#----    zinb_brms_selected    ----
+
+zinb_brms_selected <- function(data, y, prior_par){
+
+  formula_mu<- paste0(y ," ~ gender + mother + (1|ID_class)")
+
+  my_prior <- brms::set_prior(prior_par, class = "b")
+
+  fit <- brms::brm(brms::bf(as.formula(formula_mu),
+                            zi ~ gender + (1|ID_class)),
+                   family = brms::zero_inflated_negbinomial(),
+                   data = data, prior = my_prior,
+                   chains = 6, iter = 6000, cores = 6, warmup = 2000, seed = 2021)
+
+  return(fit)
+}
+
+
 #----    get_model_df    ----
 
 get_model_df<- function(fit){
@@ -189,6 +207,22 @@ get_data_prior_predict <- function(){
            q_3 = exp(1 + .5 * prior_sd),
            q_4 = exp(1 + 1 * prior_sd))
 }
+
+#----    get_post_pred    ----
+
+get_post_pred <- function(model){
+  levels <- c("Secure", "Anxious", "Avoidant", "Fearful")
+  new_data <- expand_grid(gender = factor(c("F", "M")),
+                          mother = factor(levels, levels = levels))
+
+  post_pred <- brms::posterior_linpred(model, newdata = new_data,
+                                       re_formula = NA, summary = FALSE)
+
+  colnames(post_pred) <- paste(new_data$gender, new_data$mother, sep = "_")
+
+  return(as.data.frame(post_pred))
+}
+
 
 #----    make_stan_data    ----
 

### 2021-09-21 R/Plan.R

@@ -247,11 +247,11 @@ get_analysis_plan <- function(){
     data_prior_predict = get_data_prior_predict(),
 
     # selected model
-    brm_selected_ext = brms::brm(brms::bf(externalizing_sum ~ gender + mother + (1|ID_class),
-                                          zi ~ gender + (1|ID_class)),
-                                 family = brms::zero_inflated_negbinomial(),
-                                 data = data_cluster,
-                                 chains = 6, iter = 6000, cores = 6, warmup = 2000, seed = 2021)
+    brm_selected_ext = zinb_brms_selected(data = data_cluster,
+                                          y = "externalizing_sum",
+                                          prior_par = "normal(0, 3)"),
+    post_pred_ext = get_post_pred(brm_selected_ext),
+    r2_ext = brms::bayes_R2(brm_selected_ext)
   )
 }
 

### 2021-09-21 R/Plots.R

@@ -393,5 +393,121 @@ plot_problems_dist <- function(prob = c("ext", "int")){
     labs(x = label_x,
          y = "Frequency")
 }
+#----    plot_post_pred    ----
+
+# drake::loadd(post_pred_ext)
+plot_post_pred <-  function(post_pred = post_pred_ext, problem = c("Externalizing", "Internalizing")){
+  problem <- match.arg(problem)
+
+  data <- post_pred %>%
+    mutate_all(exp) %>%
+    mutate(Female = (F_Secure + F_Anxious + F_Avoidant + F_Fearful)/4,
+           Male = (M_Secure + M_Anxious + M_Avoidant + M_Fearful)/4,
+           Secure = (F_Secure + M_Secure)/2,
+           Anxious = (F_Anxious + M_Anxious)/2,
+           Avoidant = (F_Avoidant + M_Avoidant)/2,
+           Fearful = (F_Fearful + M_Fearful)/2) %>%
+    select(Female:Fearful)
+
+  p_gender <- data %>%
+    select(Female, Male) %>%
+    pivot_longer(c(Female, Male), names_to = "Gender", values_to = "Problems") %>%
+    ggplot() +
+    ggridges::stat_density_ridges(aes(x = Problems, y = Gender, fill = factor(stat(quantile))),
+                                  geom = "density_ridges_gradient", show.legend = FALSE,
+                                  calc_ecdf = TRUE, quantiles = c(0.025, 0.975), color = "gray30") +
+    ggridges::stat_density_ridges(aes(x = Problems, y = Gender, fill = Gender), show.legend = FALSE,
+                                  quantile_lines = TRUE, quantiles = c(0.025,.5, 0.975), color = "gray30", alpha = 0.7) +
+    scale_fill_manual(values = c("gray10", "#ffffff00", "gray10", "#F8766D", "#00BFC4")) +
+    scale_y_discrete(expand = expansion(add = c(.3, 1.5))) +
+    labs(x = sprintf("%s Problems", problem))
+
+  p_attachemnt <- data %>%
+    select(Secure, Anxious, Avoidant, Fearful) %>%
+    pivot_longer(c(Secure, Anxious, Avoidant, Fearful), names_to = "Mother", values_to = "Problems") %>%
+    mutate(Mother = factor(Mother, levels = c("Secure", "Anxious", "Avoidant", "Fearful"))) %>%
+    ggplot() +
[…]

### 2021-09-21 Documents/Bookdown/02-ext.Rmd
trackdown corrige ext

@@
 The model is fitted using the function `glmmTMB()` from the `glmmTMB` R-package [@brooksGlmmTMBBalancesSpeed2017].
-Next, we compare the number of observed zero and expected zeros using an adapted version the function `check_zeroinflation()` from the R-package `performance` [@ludeckePerformancePackageAssessment2021] that solves a small bug (see issue https://github.com/easystats/performance/issues/367).
+Next, we compare the number of observed zero and expected zeros using an adapted version of the function `check_zeroinflation()` from the R-package `performance` [@ludeckePerformancePackageAssessment2021] that solves a small bug (see issue https://github.com/easystats/performance/issues/367).
 ```{r echo = TRUE, cache=TRUE}
@@
 In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ the consider also the interaction between mother attachment and father attachment.
-In both cases, we consider the children's classroom ID as a random effect (teachers may differ in they ability to detect children's problem and quantify them).
+In both cases, we consider the children's classroom ID as a random effect (teachers may differ in the ability to detect children's problems and quantify them).
 Using R formula syntax, we have
@@
 
-Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses we decide to use ZINB models.
+Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses, we decide to use ZINB models.
 
@@
 
-Following traditional NHST approach, we consider the model previously defined that includes all effects of interest.
+Following the traditional NHST approach, we consider the model previously defined that includes all effects of interest.
 That is the gender effect and the interaction between mother attachment and father attachment.
@@
 ```
-Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are no significant. Model summary is reported below.
+Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are not significant. The model summary is reported below.
 ```{r, echo =TRUE, cache=TRUE}
@@
 
-Post-hoc test are run to evaluate differences between mother attachment styles.
+Post-hoc tests are run to evaluate differences between mother attachment styles.
 To do that we use the `contrast()` function from the `emmeans` R-package, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
-This approach is less restrictive than traditional *“Bonferroni”* method, as it determines the adjustment according to a multivariate *t*-distribution with the same covariance structure as the estimates.
+This approach is less restrictive than the traditional *“Bonferroni”* method, as it determines the adjustment according to a multivariate *t*-distribution with the same covariance structure as the estimates.
 Results are reported below,
@@
 
-To evaluate the fit of model to the data, we used $R^2$.
+To evaluate the fit of the model to the data, we used $R^2$.
 In the case of generalized mixed-effects models, however, there are several definitions of $R^2$.
@@
 Considering attachment theoretical perspectives, results indicate only the role of mother attachment.
-Note, however, that traditional NHST does not allow us to evaluate evidence in favour of an hypotheses.
+Note, however, that traditional NHST does not allow us to evaluate evidence in favour of a hypothesis.
 Moreover, we actually have not tested our hypotheses but only the catch-all null hypothesis that *“nothing is going on”*.
@@
 Following the same reasons as before (see Section~\@ref(model-choice)), we consider Zero Inflated Negative Binomial Mixed-Effects models.
-Again, we consider only the role of gender as fixed effect and children's classroom ID as random effect for $p$.
+Again, we consider only the role of gender as a fixed effect and children's classroom ID as a random effect for $p$.
 Whereas, considering $\mu$, we define four different models to take into account the different theoretical perspectives:
@@
 
-Moreover, in all models we include children's classroom ID as random effect to take into  account teachers' different ability to evaluate children's problems. Using R formula syntax, we have
+Moreover, in all models, we include children's classroom ID as a random effect to take into account teachers' different ability to evaluate children's problems. Using R formula syntax, we have
 ```{r, echo = TRUE, eval=FALSE}
@@
 
-To interpret these results note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
+To interpret these results, note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
 As pointed by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
@@
 ```
-Results confirm a statistically significant effect of gender and mother attachment. Model summary is reported below.
+Results confirm a statistically significant effect of gender and mother attachment. The model summary is reported below.
 ```{r, echo =TRUE, cache=TRUE}
@@
 
-Post-hoc test are run to evaluate differences between mother attachment styles, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
+Post-hoc tests are run to evaluate differences between mother attachment styles, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
 Results are reported below,
@@
 
-To evaluate the fit of model to the data, we computed the *Marginal* $R^2$ and the *Conditional* $R^2$.
+To evaluate the fit of the model to the data, we computed the *Marginal* $R^2$ and the *Conditional* $R^2$.
 
@@
 We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects model to take into account the characteristics of the dependent variable and its distribution (see Section~\@ref(model-choice)).
-Again, we consider only the role of gender as fixed effect and children’s classroom ID as random effect for $p$.
-Whereas, regarding $\mu$, we consider the interaction between mother and father attachment together with gender as fixed effects and children’s classroom ID as random effect.
+Again, we consider only the role of gender as a fixed effect and children’s classroom ID as a random effect for $p$.
+Whereas, regarding $\mu$, we consider the interaction between mother and father attachment together with gender as fixed effects and children’s classroom ID as a random effect.
 In the R formula syntax, we have
@@
 
-Prior choice is important for the parameters involved in the equality and inequality constraints.
+The prior choice is important for the parameters involved in the equality and inequality constraints.
 In our case, the parameters of interest (i.e., those related to mother and father attachment interaction) are unbounded.
@@
 To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest.
-Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1, because $exp(1) \approx 2.7$ that is close to the externalizing problems sample mean  `r ext_mean()`.
-In Table~\@ref(tab:table-prior-predict), summary information about prior predictions for different standard deviation values are reported.
+Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1 because $exp(1) \approx 2.7$ that is close to the externalizing problems sample mean  `r ext_mean()`.
+In Table~\@ref(tab:table-prior-predict), summary information about prior predictions for different standard deviation values is reported.
 ```{r table-prior-predict}
@@
 
-For each informative hypothesis, we obtain an hypothesis matrix that translate equality and inequality constraints according to the encompassing model parametrization.
+For each informative hypothesis, we obtain a hypothesis matrix that translates equality and inequality constraints according to the encompassing model parametrization.
 Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ([TODO: add link]).
@@
 For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicate the group condition.
-This is done because when assuming no interaction or no father attachment effect we set constraints directly on the model parameters, instead when constrains involve group comparisons we need to obtain the resulting conditions.
+This is done because when assuming no interaction or no father attachment effect we set constraints directly on the model parameters, instead, when constraints involve group comparisons, we need to obtain the resulting conditions.
 Equality and inequality constraints are presented separately.
@@
 To overcome this issue, we follow the solution presented in the main article.
-First define $R^*$ selecting the maximum number of independent rows.
-In this case 15 contrast are independent
+First, define $R^*$ selecting the maximum number of independent rows.
+In this case, 15 contrast are independent
 
@@
 
-The remaining contrasts, instead, are obtained as linear combination of the other constraints. In particular,
+The remaining contrasts, instead, are obtained as linear combinations of the other constraints. In particular,
 ```{r, echo = TRUE, cache = TRUE}
@@
 Finally, we do not need to standardize our parameters as they represent mean groups differences.
-See the main article for detailed explanation [TODO: add link article].
+See the main article for a detailed explanation [TODO: add link article].
 
@@
 
-To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in details in the main article [TODO: add link article].
+To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in detail in the main article [TODO: add link article].
 Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).
@@
 To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
-On the contrary, equality constraints are highly affected by the prior definition (see he main article for more details[TODO: add link article]).
+On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details[TODO: add link article]).
 
@@
 
-One of the limit of the Bayes Factor with the encompassing prior approach is that we only get the selected hypothesis but we do not obtain the actual estimates of the parameters posterior.
+One of the limits of the Bayes Factor with the encompassing prior approach is that we only get the selected hypothesis but we do not obtain the actual estimates of the parameters posterior.
 To overcome this limit we rely on Bayesian inference that allows us to effectively estimate the model parameter posteriors.
@@
 
-The model is estimated using 6 independent chains with 6,000 iterations (warm-up 2,000). Model summary is presented below.
+The model is estimated using 6 independent chains with 6,000 iterations (warm-up 2,000). The model summary is presented below.
 ```{r cache=TRUE}
@@
 
-To evaluate the fit of model to the data, we computed the *Bayesian* $R^2$ and using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-ext).
+To evaluate the fit of the model to the data, we computed the *Bayesian* $R^2$ and using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-ext).
 
@@
 Males have more problems than Females and, regarding attachment, only mother attachment influence children's externalizing problems.
-In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children heave the highest level of problems.
+In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems.
 Taken together, these results support the Monotropy Theory.
@@
 
-Summarizing, the apparently identical results actually have a completely different meaning and what we learn from the data is very different.
+To summarize, the apparently identical results actually have a completely different meaning and what we learn from the data is very different.
 Hopefully, now it is clear that statistical inference is a complex process that requires careful thinking.
-In particular, to answer to the questions we are actually interested in, we need to apply the appropriate statistical techniques.
+In particular, to answer the questions we are actually interested in, we need to apply the appropriate statistical techniques.

### 2021-09-21 Documents/Bookdown/01-case-study.Rmd
rearrange structure bookdown

@@
 ---
+# (PART\*) Presentation {-}
+
 # Case Study {#case-study}
 
-In this chapter, we describe the sample included in the study.
-First we describe the aim of the study.
-Subsequently, we present general information about the sample and the results of the cluster analysis to classify the different attachment patterns.
+In this chapter, first, we describe the aim of the study.
+Subsequently,  we describe the sample included in the study.
+We present general information about the sample and the results of the cluster analysis to classify the different attachment patterns.
 Finally, we consider children's social-emotional problems.

### 2021-09-21 Documents/Bookdown/02-ext-model-choice.Rmd
rearrange structure bookdown

--- 2021-09-20 Documents/Bookdown/02-ext.Rmd
@@
----
-output: html_document
-editor_options: 
-  chunk_output_type: console
----
-# Externalizing Problems {#ext}
+# (PART\*) Externalizing Problems {-}
 
-In this chapter, we present the analyses to evaluate the different role of mother attachment and father attachment on children's externalizing problems.
-First, we discuss the appropriate models family to to take into account data characteristics.
-Next we conduct inference following three different approaches: 1) traditional Null Hypothesis Significance Testing (NHST) 2) Model Comparison using the AIC and BIC criteria 3) Bayes Factor with encompassing prior approach.
+# Models Family Choice {#model-choice-ext}
 
-## Models Family Choiche {#model-choice}
+In this chapter, we discuss the appropriate models family to to take into account data characteristics.
+
+## Negative Binomial
 
@@
 
-### Zero Inflated Negative Binomial
+## Zero Inflated Negative Binomial
 
@@
 
-Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses we decide to use ZINB models.
-
-## NHST
-
-Following traditional NHST approach, we consider the model previously defined that includes all effects of interest.
-That is the gender effect and the interaction between mother attachment and father attachment.
-Subsequently, we can run an analysis of deviance to evaluate the significance of the predictors using the function `Anova()` from the R-package `car` [@foxCompanionAppliedRegression2019].
-```{r, echo =TRUE, cache=TRUE}
-car::Anova(fit_ext_zinb)
-```
-Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are no significant. Model summary is reported below.
-```{r, echo =TRUE, cache=TRUE}
-summary(fit_ext_zinb)
-```
-To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-nhst-effects).
-Not that the marginal predicted values for gender are averaged over mother and father attachment effects.
-Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
-```{r plot-nhst-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment.
-Values are averaged over the other effects ($n_{subj} = 847$)."}
-get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
-```
-
-Post-hoc test are run to evaluate differences between mother attachment styles.
-To do that we use the `contrast()` function from the `emmeans` R-package, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
-This approach is less restrictive than traditional *“Bonferroni”* method, as it determines the adjustment according to a multivariate *t*-distribution with the same covariance structure as the estimates.
-Results are reported below,
-```{r, cache=TRUE, echo = TRUE}
-emmeans::contrast(emmeans::emmeans(fit_ext_zinb, specs = ~ mother ),
-                  "pairwise", adjust = "mvt")
-```
-
-Overall, results indicate that Males have more externalizing problems than Females and, regarding mother attachment, Fearful children have more problems than Secure children.
-
-To evaluate the fit of model to the data, we used $R^2$.
-In the case of generalized mixed-effects models, however, there are several definitions of $R^2$.
-We computed the *Marginal* $R^2$ and the *Conditional* $R^2$ as suggested by @nakagawaCoefficientDeterminationR22017.
-*Marginal* $R^2$ is concerned with the variance explained by fixed factors of the model, and *Conditional* $R^2$ is concerned with the variance explained by both fixed and random factors of the model.
-To do that we use the function `performance::r2()`.
-
-```{r, echo=TRUE, message=FALSE, cache=TRUE}
-performance::r2(fit_ext_zinb)
-```
-
-We can see that the actual variance explained by fixed effects is almost 10\%, not bad for psychology.
-
-#### Conclusions {-}
-
-Considering attachment theoretical perspectives, results indicate only the role of mother attachment.
-Note, however, that traditional NHST does not allow us to evaluate evidence in favour of an hypotheses.
-Moreover, we actually have not tested our hypotheses but only the catch-all null hypothesis that *“nothing is going on”*.
-
-## Model Comparison
-
-Model comparison allows us to compare multiple hypotheses and identify which is the most supported by the data [@mcelreathStatisticalRethinkingBayesian2020].
-First, we need to formalize models according to our hypotheses.
-Subsequently, we can evaluate which is the most supported model among those considered according to the data using the AIC and BIC [@wagenmakersAICModelSelection2004; @akaike1973a; @schwarzEstimatingDimensionModel1978].
-
-### Formalize Models
-
-Following the same reasons as before (see Section~\@ref(model-choice)), we consider Zero Inflated Negative Binomial Mixed-Effects models.
-Again, we consider only the role of gender as fixed effect and children's classroom ID as random effect for $p$.
-Whereas, considering $\mu$, we define four different models to take into account the different theoretical perspectives:
-
-- `fit_ext_zero`: we consider only the effect of gender. This model assumes that attachment plays no role.
-- `fit_ext_mother`: we consider the additive effects of gender and mother attachment. This model supports the idea that only mother attachment is important (**Monotropy Theory**).
-- `fit_ext_additive`: we consider the additive effects of gender,  mother attachment, and father attachment.
-This model supports the idea that both mother attachment and father attachment are important, but not their interaction (**Hierarchy Theory** or **Independence Theory**).
-- `fit_ext_inter`: we consider the additive effects of gender and the interaction between mother attachment and father attachment.
-This model supports the idea that the interaction between mother attachment and father attachment is important (**Integration Theory**).
-
-Moreover, in all models we include children's classroom ID as random effect to take into  account teachers' different ability to evaluate children's problems. Using R formula syntax, we have
-```{r, echo = TRUE, eval=FALSE}
-# formula for p (same for all models)
-p ~ gender + (1|ID_class)
-
-# formula for mu
-
-# fit_ext_zero
-mu ~ gender + (1|ID_class)
-
-# fit_ext_mother
-mu ~ gender + mother + (1|ID_class)
-
-# fit_ext_additive
-mu ~ gender + mother + father + (1|ID_class)
-
-# fit_ext_inter
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-### AIC and BIC Results
-
-After estimating the models, the AIC and BIC values together with their relative weights are computed. Results are reported in Table~\@ref(tab:table-AIC-BIC-weights).
-
-```{r table-AIC-BIC-weights, cache=TRUE}
-get_table_AIC_BIC(AIC_weights = AIC_weights_ext,
-                  BIC_weights = BIC_weights_ext,
-                  problem = "ext",
-                  format = params$format,
-                  path_img = "images/")
-```
-
-Accordinng to AIC, the most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "AIC")`\%) and the second most likely model is `fit_ext_additive` (`r perc_model_ext("fit_ext_additive", "AIC")`\%) given the data and the set of models considered.
-According to BIC, instead,  the most likely model is `fit_ext_zero` (`r perc_model_ext("fit_ext_zero", "BIC")`\%) and the second most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "BIC")`\%) given the data and the set of models considered.
-
-To interpret these results note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
-As pointed by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
-We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.
-
-### Selected Model
-
-Considering model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
-```{r, echo =TRUE, cache=TRUE}
-car::Anova(fit_ext_mother)
-```
-Results confirm a statistically significant effect of gender and mother attachment. Model summary is reported below.
-```{r, echo =TRUE, cache=TRUE}
-summary(fit_ext_mother)
-```
-To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects).
-Not that the marginal predicted values for gender are averaged over mother attachment.
-Whereas, the marginal predicted values for mother attachment are averaged over gender.
-```{r plot-comparison-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
-get_plot_zinb(model = fit_ext_mother, attachment = "mother")
-```
-
-Post-hoc test are run to evaluate differences between mother attachment styles, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
-Results are reported below,
-```{r, cache=TRUE, echo = TRUE}
-emmeans::contrast(emmeans::emmeans(fit_ext_mother, specs = ~ mother ),
-                  "pairwise", adjust = "mvt")
-```
-
-Overall, results indicate that Males have more externalizing problems than Females.
-Regarding mother attachment, Fearful and Avoidant children have more problems than Secure children.
-Moreover, also the difference between Anxious and Secure children and the difference between Anxious and Fearful children have a low (but not statistically significant) *p*-value.
-
-To evaluate the fit of model to the data, we computed the *Marginal* $R^2$ and the *Conditional* $R^2$.
-
-```{r, echo=TRUE, message=FALSE, cache=TRUE}
-performance::r2(fit_ext_mother)
-```
-
-We can see that the actual variance explained by fixed effects is around 7\%, not bad for psychology.
-
-#### Conclusions {-}
-
-Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the **Monotropy Theory**.
-Note, however, that the compared models contain no information regarding the expected direction of the effects but we only include/exclude predictors.
-
-## Bayes Factor
-
-To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes Factor with encompassing prior approach.
-See the main article for a detailed introduction to this approach [TODO: add link article].
-
-First, we define the encompassing model.
-Subsequently, we obtain the hypotheses matrices according to the informative hypotheses.
-Next, we compute the Bayes Factor and, finally, we describe the selected model.
-
-### Encompassing Model
-
-We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects model to take into account the characteristics of the dependent variable and its distribution (see Section~\@ref(model-choice)).
-Again, we consider only the role of gender as fixed effect and children’s classroom ID as random effect for $p$.
-Whereas, regarding $\mu$, we consider the interaction between mother and father attachment together with gender as fixed effects and children’s classroom ID as random effect.
-In the R formula syntax, we have
-```{r, echo=TRUE, eval=FALSE}
-# formula for p
-p ~ gender + (1|ID_class)
-
-# formula for mu
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-#### Prior Choiche {-}
-
-Prior choice is important for the parameters involved in the equality and inequality constraints.
-In our case, the parameters of interest (i.e., those related to mother and father attachment interaction) are unbounded.
-Thus, we can simply specify as prior a normal distribution with mean 0 and a given standard deviation.
-Considering the standard deviation, however, we have to choose a value so that the resulting prior is non-informative but without being excessively diffuse.
-
-We can evaluate the consequences of different values choice considering the resulting prior predictions.
-To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest.
-Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1, because $exp(1) \approx 2.7$ that is close to the externalizing problems sample mean  `r ext_mean()`.
-In Table~\@ref(tab:table-prior-predict), summary information about prior predictions for different standard deviation values are reported.
-```{r table-prior-predict}
-get_table_prior_predict(format = params$format)
-```
-
-Considering that externalizing problems are bounded between 0 and 20, a reasonable prior is  $\mathcal{N}(0,3)$.
-as prior predicted values cover all possible values without including excessively large values.
-More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values.
-The influence of prior specification will be subsequently evaluated in a prior sensitivity analysis.
-
-Regarding the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) `brms` default priors are maintained. The resulting prior settings are
-```{r prior-seettings}
-options(width = 300)
-brms::prior_summary(encompassing_model_ext)
-```
-
-#### Posterior{-}
-The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).
-To do that we use the `brm()` function from the `brms` R-package [@burknerBrmsPackageBayesian2017; @burknerAdvancedBayesianMultilevel2018a], which is based on STAN [@standevelopmentteamRStanInterfaceStan2020].
-Summary of the encompassing model is presented below.
-```{r}
-summary(encompassing_model_ext)
-```
-
-### Hypothesis Matrices
-
-For each informative hypothesis, we obtain an hypothesis matrix that translate equality and inequality constraints according to the encompassing model parametrization.
-Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ([TODO: add link]).
-
-Here we present the obtained hypothesis matrices were on the columns we have the parameters of the encompassing model (excluding the intercept) and each row express an equality constraint or an inequality constraint.
-Matrices row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters).
-For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicate the group condition.
-Equality and inequality constraints ar presented separately.
-
-#### Null Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("null", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero). There are no inequality constraints.
-
-#### Monotropy Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("monotropy", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("monotropy", encompassing_model_ext)$ineq
-```
-
-#### Hierarchy Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$ineq
-```
-
-#### Independence Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("independence", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("independence", encompassing_model_ext)$ineq
-```
-
-#### Integration Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("integration", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("integration", encompassing_model_ext)$ineq
-```
-
-### Centering and Adjusting
-
-So far we have specified the encompassing prior, obtained the model posterior distribution, and defined the hypotheses matrices.
-Now, we need to transform our parameters of interest and center the distribution on the constraints focal points of interest.
-We apply the following transformation
-$$
-\beta = R\theta - r
-$$
-but we can ignore $r$ as in all our constraints it is always a vector of zeros.
-
-Next, we get the adjusted prior and the posterior of the transformed parameters vector  $\beta$ (i.e., the parameters that identify the constraints) for each hypothesis. The adjusted prior is given by
-
-$$
-\pi_{adj}(\beta) \sim \mathcal{N}(0, \Sigma_{\beta}) = \mathcal{N}(0, R\Sigma_{\theta}R^T).
-$$
-Note that we set the mean vector to zero. The posterior is given by the same transformation
-$$
-Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\theta}-r, R\hat{\Sigma}_{\theta}R^T).
-$$
-See the main article for more details [TODO: add link].
-
-This adjustment, however, requires the hypothesis matrix $R$ to be *full-row-rank* (i.e., all constraints are linearly independent).
-However, this is not the case of the hierarchy hypothesis.
-To overcome this issue, we follow the solution presented in the main article.
-First define $R^*$ selecting the maximum number of independent rows.
-In this case 15 contrast are independent
-
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$hyp[1:15,]
-```
-
-```{r cache=TRUE}
-R <- get_hypothesis_matrix("hierarchy", encompassing_model_ext)$hyp
-```
-
-The remaining contrasts, instead, are obtained as linear combination of the other constraints. In particular,
-```{r, echo = TRUE, cache = TRUE}
-# Constraint 16: [M_Anx_F_Sec - M_Sec_F_Anx]
-all(R["[M_Anx_F_Sec - M_Sec_F_Anx]",] == R["[M_Anx_F_Sec]", ] - R["[M_Sec_F_Anx]", ])
-
-# Constraint 17: [M_Av_F_Sec - M_Sec_F_Av]
-all(R["[M_Av_F_Sec - M_Sec_F_Av]",] == - R["[M_Anx_F_Sec - M_Av_F_Sec]", ] + R["[M_Sec_F_Anx - M_Sec_F_Av]", ] +  R["[M_Anx_F_Sec - M_Sec_F_Anx]", ])
-
-# Constraint 18: [M_Fear_F_Sec - M_Sec_F_Fear] 
-all(R["[M_Fear_F_Sec - M_Sec_F_Fear]",] == R["[M_Av_F_Sec - M_Sec_F_Av]", ] + R["[M_Fear_F_Sec - M_Av_F_Sec]", ] - R["[M_Sec_F_Fear - M_Sec_F_Av]", ])
-```
-
-Before computing the Bayes Factor, note that we have a set of comparable hypotheses as exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero.
-The solution is the trivial solution of simply consider all parameters equal to zero.
-Finally, we do not need to standardize our parameters as they represent mean groups differences.
-See the main article for detailed explanation [TODO: add link article].
-
-### Results and Sensitivity
-
-To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in details in the main article [TODO: add link article].
-Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).
-
-```{r table-bf-results-ext, cache = TRUE}
-get_table_bf(bf_result = BF_weights_ext,
-             path_img = "images/", problem = "ext",
-             format = params$format)
-```
-
-Remember, however, that prior specification affects the Bayes Factor results.
-Therefore, we also evaluate the results considering different prior settings.
-In particular, we consider as possible priors for the parameters of interest:
-
-- $\mathcal{N}(0,.5)$ - unreasonable tight prior
-- $\mathcal{N}(0,1)$ - tighter prior
-- $\mathcal{N}(0,3)$ - original prior
-- $\mathcal{N}(0,5)$ - more diffuse prior
-- $\mathcal{N}(0,10)$ - unreasonably diffuse prior
-
-The results of the prior sensitivity analysis are reported in Table~\@ref(tab:table-sens-prior-analysis-ext).
-
-```{r table-sens-prior-analysis-ext, cache = TRUE}
-get_table_sens_analysis(summary_sensitivity_ext,
-                        format = params$format,
-                        bookdown = TRUE)
-```
-
-Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data.
-However, we can observe two distinct patterns.
-As the prior gets more diffuse, the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
-Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.
-
-To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
-On the contrary, equality constraints are highly affected by the prior definition (see he main article for more details[TODO: add link article]).
-
-All the defined hypotheses include equality constraints.
-Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
-Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).
-
-### Selected Model
+Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses, we decide to use ZINB models.

### 2021-09-21 Documents/Bookdown/03-ext-nhst.Rmd
rearrange structure bookdown

--- 2021-09-20 Documents/Bookdown/02-ext.Rmd
@@
----
-output: html_document
-editor_options: 
-  chunk_output_type: console
----
-# Externalizing Problems {#ext}
+# NHST {#nhst-ext}
 
-In this chapter, we present the analyses to evaluate the different role of mother attachment and father attachment on children's externalizing problems.
-First, we discuss the appropriate models family to to take into account data characteristics.
-Next we conduct inference following three different approaches: 1) traditional Null Hypothesis Significance Testing (NHST) 2) Model Comparison using the AIC and BIC criteria 3) Bayes Factor with encompassing prior approach.
-
-## Models Family Choiche {#model-choice}
-
-Externalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20.
-Thus, we should use appropriate discrete distribution such as the *Poisson* distribution or the *Negative Binomial*.
-In the Poisson distribution mean and variance are defined according to the same parameter $\lambda$.
-On the contrary, Negative Binomial has an extra parameter to adjust the variance allowing more flexibility.
-Considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe that data have high dispersion with a long right tail.
-In this case, Poisson distribution would be a poor choice and we prefer Negative Binomial instead.
-
-Again, considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe an high peak of values at zero.
-Remember that this is not a clinical sample, thus it is expected that children majority has no problems or really few problem.
-We could question ourselves, however, whether a *Zero-Inflated* model may be appropriate
-
-### Zero Inflated Negative Binomial
-
-To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model.
-We consider in the model the role of gender and the interaction between mother attachment and father attachment.
-Moreover, we consider the children's classroom ID as a random effect to account for teachers' different ability to evaluate children's problems.
-Using R formula syntax, we have
-```{r echo = TRUE, eval=FALSE}
-# model formula
-externalizing_sum ~ gender + mother * father + (1|ID_class)
-```
-
-The model is fitted using the function `glmmTMB()` from the `glmmTMB` R-package [@brooksGlmmTMBBalancesSpeed2017].
-Next, we compare the number of observed zero and expected zeros using an adapted version the function `check_zeroinflation()` from the R-package `performance` [@ludeckePerformancePackageAssessment2021] that solves a small bug (see issue https://github.com/easystats/performance/issues/367).
-```{r echo = TRUE, cache=TRUE}
-my_check_zeroinflation(fit_ext_nb)
-```
-
-Results indicate that the model is slightly under-fitting the number of zeros.
-Now, we can try to fit a *Zero Inflated Negative Binomial* (ZINB) model and compare the performance of the two models.
-ZINB models are defined as
-$$
-y_{i} \sim ZINB(p_{i}, \mu_{i}, \phi),
-$$
-where $p_i$ is the probability of an observation $y_{i}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_i$ indicates the probability of a given observation $y_{i}$ being generated form a Negative Binomial distribution with mean $\mu_{i}$ and variance $\sigma_{i}^2 = \mu_{i} + \frac{\mu_{i}^2}{\phi}$.
-Moreover, we have that
-$$
-p_{i} = \text{logit}^{-1}(X_i^T\beta_p),\\
-\mu_{i} = \text{exp}(X_i^T\beta_{\mu}).
-$$
-That is, both $p$ and $\mu$ are modelled separately according to (possibly) different variables.
-In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ the consider also the interaction between mother attachment and father attachment.
-In both cases, we consider the children's classroom ID as a random effect (teachers may differ in they ability to detect children's problem and quantify them).
-Using R formula syntax, we have
-```{r echo = TRUE, eval=FALSE}
-# formula for p
-p ~ gender + (1|ID_class)
-
-# formula for mu
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-The ZINB model is fitted using the function `zeroinfl()` from the `pscl` R-package [@zeileisRegressionModelsCount2008].
-To compare the ZINB model and the Negative Binomial model we conduct an analysis of *Deviance*.
-Note that, in the case of generalized linear models (GLM), the deviance is the corresponding of the residual variance used in the traditional ANOVA in the case of linear models.
-```{r echo=TRUE, cache=TRUE}
-anova(fit_ext_nb, fit_ext_zinb)
-```
-
-Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses we decide to use ZINB models.
-
-## NHST
-
-Following traditional NHST approach, we consider the model previously defined that includes all effects of interest.
+Following the traditional NHST approach, we consider the model previously defined that includes all effects of interest.
 That is the gender effect and the interaction between mother attachment and father attachment.
@@
 Considering attachment theoretical perspectives, results indicate only the role of mother attachment.
-Note, however, that traditional NHST does not allow us to evaluate evidence in favour of an hypotheses.
+Note, however, that traditional NHST does not allow us to evaluate evidence in favour of a hypothesis.
 Moreover, we actually have not tested our hypotheses but only the catch-all null hypothesis that *“nothing is going on”*.
-
-## Model Comparison
-
-Model comparison allows us to compare multiple hypotheses and identify which is the most supported by the data [@mcelreathStatisticalRethinkingBayesian2020].
-First, we need to formalize models according to our hypotheses.
-Subsequently, we can evaluate which is the most supported model among those considered according to the data using the AIC and BIC [@wagenmakersAICModelSelection2004; @akaike1973a; @schwarzEstimatingDimensionModel1978].
-
-### Formalize Models
-
-Following the same reasons as before (see Section~\@ref(model-choice)), we consider Zero Inflated Negative Binomial Mixed-Effects models.
-Again, we consider only the role of gender as fixed effect and children's classroom ID as random effect for $p$.
-Whereas, considering $\mu$, we define four different models to take into account the different theoretical perspectives:
-
-- `fit_ext_zero`: we consider only the effect of gender. This model assumes that attachment plays no role.
-- `fit_ext_mother`: we consider the additive effects of gender and mother attachment. This model supports the idea that only mother attachment is important (**Monotropy Theory**).
-- `fit_ext_additive`: we consider the additive effects of gender,  mother attachment, and father attachment.
-This model supports the idea that both mother attachment and father attachment are important, but not their interaction (**Hierarchy Theory** or **Independence Theory**).
-- `fit_ext_inter`: we consider the additive effects of gender and the interaction between mother attachment and father attachment.
-This model supports the idea that the interaction between mother attachment and father attachment is important (**Integration Theory**).
-
-Moreover, in all models we include children's classroom ID as random effect to take into  account teachers' different ability to evaluate children's problems. Using R formula syntax, we have
-```{r, echo = TRUE, eval=FALSE}
-# formula for p (same for all models)
-p ~ gender + (1|ID_class)
-
-# formula for mu
-
-# fit_ext_zero
-mu ~ gender + (1|ID_class)
-
-# fit_ext_mother
-mu ~ gender + mother + (1|ID_class)
-
-# fit_ext_additive
-mu ~ gender + mother + father + (1|ID_class)
-
-# fit_ext_inter
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-### AIC and BIC Results
-
-After estimating the models, the AIC and BIC values together with their relative weights are computed. Results are reported in Table~\@ref(tab:table-AIC-BIC-weights).
-
-```{r table-AIC-BIC-weights, cache=TRUE}
-get_table_AIC_BIC(AIC_weights = AIC_weights_ext,
-                  BIC_weights = BIC_weights_ext,
-                  problem = "ext",
-                  format = params$format,
-                  path_img = "images/")
-```
-
-Accordinng to AIC, the most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "AIC")`\%) and the second most likely model is `fit_ext_additive` (`r perc_model_ext("fit_ext_additive", "AIC")`\%) given the data and the set of models considered.
-According to BIC, instead,  the most likely model is `fit_ext_zero` (`r perc_model_ext("fit_ext_zero", "BIC")`\%) and the second most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "BIC")`\%) given the data and the set of models considered.
-
-To interpret these results note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
-As pointed by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
-We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.
-
-### Selected Model
-
-Considering model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
-```{r, echo =TRUE, cache=TRUE}
-car::Anova(fit_ext_mother)
-```
-Results confirm a statistically significant effect of gender and mother attachment. Model summary is reported below.
-```{r, echo =TRUE, cache=TRUE}
-summary(fit_ext_mother)
-```
-To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects).
-Not that the marginal predicted values for gender are averaged over mother attachment.
-Whereas, the marginal predicted values for mother attachment are averaged over gender.
-```{r plot-comparison-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
-get_plot_zinb(model = fit_ext_mother, attachment = "mother")
-```
-
-Post-hoc test are run to evaluate differences between mother attachment styles, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
-Results are reported below,
-```{r, cache=TRUE, echo = TRUE}
-emmeans::contrast(emmeans::emmeans(fit_ext_mother, specs = ~ mother ),
-                  "pairwise", adjust = "mvt")
-```
-
-Overall, results indicate that Males have more externalizing problems than Females.
-Regarding mother attachment, Fearful and Avoidant children have more problems than Secure children.
-Moreover, also the difference between Anxious and Secure children and the difference between Anxious and Fearful children have a low (but not statistically significant) *p*-value.
-
-To evaluate the fit of model to the data, we computed the *Marginal* $R^2$ and the *Conditional* $R^2$.
-
-```{r, echo=TRUE, message=FALSE, cache=TRUE}
-performance::r2(fit_ext_mother)
-```
-
-We can see that the actual variance explained by fixed effects is around 7\%, not bad for psychology.
-
-#### Conclusions {-}
-
-Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the **Monotropy Theory**.
-Note, however, that the compared models contain no information regarding the expected direction of the effects but we only include/exclude predictors.
-
-## Bayes Factor
-
-To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes Factor with encompassing prior approach.
-See the main article for a detailed introduction to this approach [TODO: add link article].
-
-First, we define the encompassing model.
-Subsequently, we obtain the hypotheses matrices according to the informative hypotheses.
-Next, we compute the Bayes Factor and, finally, we describe the selected model.
-
-### Encompassing Model
-
-We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects model to take into account the characteristics of the dependent variable and its distribution (see Section~\@ref(model-choice)).
-Again, we consider only the role of gender as fixed effect and children’s classroom ID as random effect for $p$.
-Whereas, regarding $\mu$, we consider the interaction between mother and father attachment together with gender as fixed effects and children’s classroom ID as random effect.
-In the R formula syntax, we have
-```{r, echo=TRUE, eval=FALSE}
-# formula for p
-p ~ gender + (1|ID_class)
-
-# formula for mu
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-#### Prior Choiche {-}
-
-Prior choice is important for the parameters involved in the equality and inequality constraints.
-In our case, the parameters of interest (i.e., those related to mother and father attachment interaction) are unbounded.
-Thus, we can simply specify as prior a normal distribution with mean 0 and a given standard deviation.
-Considering the standard deviation, however, we have to choose a value so that the resulting prior is non-informative but without being excessively diffuse.
-
-We can evaluate the consequences of different values choice considering the resulting prior predictions.
-To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest.
-Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1, because $exp(1) \approx 2.7$ that is close to the externalizing problems sample mean  `r ext_mean()`.
-In Table~\@ref(tab:table-prior-predict), summary information about prior predictions for different standard deviation values are reported.
-```{r table-prior-predict}
-get_table_prior_predict(format = params$format)
-```
-
-Considering that externalizing problems are bounded between 0 and 20, a reasonable prior is  $\mathcal{N}(0,3)$.
-as prior predicted values cover all possible values without including excessively large values.
-More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values.
-The influence of prior specification will be subsequently evaluated in a prior sensitivity analysis.
-
-Regarding the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) `brms` default priors are maintained. The resulting prior settings are
-```{r prior-seettings}
-options(width = 300)
-brms::prior_summary(encompassing_model_ext)
-```
-
-#### Posterior{-}
-The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).
-To do that we use the `brm()` function from the `brms` R-package [@burknerBrmsPackageBayesian2017; @burknerAdvancedBayesianMultilevel2018a], which is based on STAN [@standevelopmentteamRStanInterfaceStan2020].
-Summary of the encompassing model is presented below.
-```{r}
-summary(encompassing_model_ext)
-```
-
-### Hypothesis Matrices
-
-For each informative hypothesis, we obtain an hypothesis matrix that translate equality and inequality constraints according to the encompassing model parametrization.
-Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ([TODO: add link]).
-
-Here we present the obtained hypothesis matrices were on the columns we have the parameters of the encompassing model (excluding the intercept) and each row express an equality constraint or an inequality constraint.
-Matrices row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters).
-For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicate the group condition.
-Equality and inequality constraints ar presented separately.
-
-#### Null Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("null", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero). There are no inequality constraints.
-
-#### Monotropy Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("monotropy", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("monotropy", encompassing_model_ext)$ineq
-```
-
-#### Hierarchy Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$ineq
-```
-
-#### Independence Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("independence", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("independence", encompassing_model_ext)$ineq
-```
-
-#### Integration Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("integration", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("integration", encompassing_model_ext)$ineq
-```
-
-### Centering and Adjusting
-
-So far we have specified the encompassing prior, obtained the model posterior distribution, and defined the hypotheses matrices.
-Now, we need to transform our parameters of interest and center the distribution on the constraints focal points of interest.
-We apply the following transformation
-$$
-\beta = R\theta - r
-$$
-but we can ignore $r$ as in all our constraints it is always a vector of zeros.
-
-Next, we get the adjusted prior and the posterior of the transformed parameters vector  $\beta$ (i.e., the parameters that identify the constraints) for each hypothesis. The adjusted prior is given by
-
-$$
-\pi_{adj}(\beta) \sim \mathcal{N}(0, \Sigma_{\beta}) = \mathcal{N}(0, R\Sigma_{\theta}R^T).
-$$
-Note that we set the mean vector to zero. The posterior is given by the same transformation
-$$
-Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\theta}-r, R\hat{\Sigma}_{\theta}R^T).
-$$
-See the main article for more details [TODO: add link].
-
-This adjustment, however, requires the hypothesis matrix $R$ to be *full-row-rank* (i.e., all constraints are linearly independent).
-However, this is not the case of the hierarchy hypothesis.
-To overcome this issue, we follow the solution presented in the main article.
-First define $R^*$ selecting the maximum number of independent rows.
-In this case 15 contrast are independent
-
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$hyp[1:15,]
-```
-
-```{r cache=TRUE}
-R <- get_hypothesis_matrix("hierarchy", encompassing_model_ext)$hyp
-```
-
-The remaining contrasts, instead, are obtained as linear combination of the other constraints. In particular,
-```{r, echo = TRUE, cache = TRUE}
-# Constraint 16: [M_Anx_F_Sec - M_Sec_F_Anx]
-all(R["[M_Anx_F_Sec - M_Sec_F_Anx]",] == R["[M_Anx_F_Sec]", ] - R["[M_Sec_F_Anx]", ])
-
-# Constraint 17: [M_Av_F_Sec - M_Sec_F_Av]
-all(R["[M_Av_F_Sec - M_Sec_F_Av]",] == - R["[M_Anx_F_Sec - M_Av_F_Sec]", ] + R["[M_Sec_F_Anx - M_Sec_F_Av]", ] +  R["[M_Anx_F_Sec - M_Sec_F_Anx]", ])
-
-# Constraint 18: [M_Fear_F_Sec - M_Sec_F_Fear] 
-all(R["[M_Fear_F_Sec - M_Sec_F_Fear]",] == R["[M_Av_F_Sec - M_Sec_F_Av]", ] + R["[M_Fear_F_Sec - M_Av_F_Sec]", ] - R["[M_Sec_F_Fear - M_Sec_F_Av]", ])
-```
-
-Before computing the Bayes Factor, note that we have a set of comparable hypotheses as exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero.
-The solution is the trivial solution of simply consider all parameters equal to zero.
-Finally, we do not need to standardize our parameters as they represent mean groups differences.
-See the main article for detailed explanation [TODO: add link article].
-
-### Results and Sensitivity
-
-To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in details in the main article [TODO: add link article].
-Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).
-
-```{r table-bf-results-ext, cache = TRUE}
-get_table_bf(bf_result = BF_weights_ext,
-             path_img = "images/", problem = "ext",
-             format = params$format)
-```
-
-Remember, however, that prior specification affects the Bayes Factor results.
-Therefore, we also evaluate the results considering different prior settings.
-In particular, we consider as possible priors for the parameters of interest:
-
-- $\mathcal{N}(0,.5)$ - unreasonable tight prior
-- $\mathcal{N}(0,1)$ - tighter prior
-- $\mathcal{N}(0,3)$ - original prior
-- $\mathcal{N}(0,5)$ - more diffuse prior
-- $\mathcal{N}(0,10)$ - unreasonably diffuse prior
-
-The results of the prior sensitivity analysis are reported in Table~\@ref(tab:table-sens-prior-analysis-ext).
-
-```{r table-sens-prior-analysis-ext, cache = TRUE}
-get_table_sens_analysis(summary_sensitivity_ext,
-                        format = params$format,
-                        bookdown = TRUE)
-```
-
-Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data.
-However, we can observe two distinct patterns.
-As the prior gets more diffuse, the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
-Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.
-
-To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
-On the contrary, equality constraints are highly affected by the prior definition (see he main article for more details[TODO: add link article]).
-
-All the defined hypotheses include equality constraints.
-Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
-Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).
-
-### Selected Model

### 2021-09-21 Documents/Bookdown/04-ext-model-comparison.Rmd
rearrange structure bookdown

--- 2021-09-20 Documents/Bookdown/02-ext.Rmd
@@
----
-output: html_document
-editor_options: 
-  chunk_output_type: console
----
-# Externalizing Problems {#ext}
-
-In this chapter, we present the analyses to evaluate the different role of mother attachment and father attachment on children's externalizing problems.
-First, we discuss the appropriate models family to to take into account data characteristics.
-Next we conduct inference following three different approaches: 1) traditional Null Hypothesis Significance Testing (NHST) 2) Model Comparison using the AIC and BIC criteria 3) Bayes Factor with encompassing prior approach.
-
-## Models Family Choiche {#model-choice}
-
-Externalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20.
-Thus, we should use appropriate discrete distribution such as the *Poisson* distribution or the *Negative Binomial*.
-In the Poisson distribution mean and variance are defined according to the same parameter $\lambda$.
-On the contrary, Negative Binomial has an extra parameter to adjust the variance allowing more flexibility.
-Considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe that data have high dispersion with a long right tail.
-In this case, Poisson distribution would be a poor choice and we prefer Negative Binomial instead.
-
-Again, considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe an high peak of values at zero.
-Remember that this is not a clinical sample, thus it is expected that children majority has no problems or really few problem.
-We could question ourselves, however, whether a *Zero-Inflated* model may be appropriate
-
-### Zero Inflated Negative Binomial
-
-To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model.
-We consider in the model the role of gender and the interaction between mother attachment and father attachment.
-Moreover, we consider the children's classroom ID as a random effect to account for teachers' different ability to evaluate children's problems.
-Using R formula syntax, we have
-```{r echo = TRUE, eval=FALSE}
-# model formula
-externalizing_sum ~ gender + mother * father + (1|ID_class)
-```
-
-The model is fitted using the function `glmmTMB()` from the `glmmTMB` R-package [@brooksGlmmTMBBalancesSpeed2017].
-Next, we compare the number of observed zero and expected zeros using an adapted version the function `check_zeroinflation()` from the R-package `performance` [@ludeckePerformancePackageAssessment2021] that solves a small bug (see issue https://github.com/easystats/performance/issues/367).
-```{r echo = TRUE, cache=TRUE}
-my_check_zeroinflation(fit_ext_nb)
-```
-
-Results indicate that the model is slightly under-fitting the number of zeros.
-Now, we can try to fit a *Zero Inflated Negative Binomial* (ZINB) model and compare the performance of the two models.
-ZINB models are defined as
-$$
-y_{i} \sim ZINB(p_{i}, \mu_{i}, \phi),
-$$
-where $p_i$ is the probability of an observation $y_{i}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_i$ indicates the probability of a given observation $y_{i}$ being generated form a Negative Binomial distribution with mean $\mu_{i}$ and variance $\sigma_{i}^2 = \mu_{i} + \frac{\mu_{i}^2}{\phi}$.
-Moreover, we have that
-$$
-p_{i} = \text{logit}^{-1}(X_i^T\beta_p),\\
-\mu_{i} = \text{exp}(X_i^T\beta_{\mu}).
-$$
-That is, both $p$ and $\mu$ are modelled separately according to (possibly) different variables.
-In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ the consider also the interaction between mother attachment and father attachment.
-In both cases, we consider the children's classroom ID as a random effect (teachers may differ in they ability to detect children's problem and quantify them).
-Using R formula syntax, we have
-```{r echo = TRUE, eval=FALSE}
-# formula for p
-p ~ gender + (1|ID_class)
-
-# formula for mu
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-The ZINB model is fitted using the function `zeroinfl()` from the `pscl` R-package [@zeileisRegressionModelsCount2008].
-To compare the ZINB model and the Negative Binomial model we conduct an analysis of *Deviance*.
-Note that, in the case of generalized linear models (GLM), the deviance is the corresponding of the residual variance used in the traditional ANOVA in the case of linear models.
-```{r echo=TRUE, cache=TRUE}
-anova(fit_ext_nb, fit_ext_zinb)
-```
-
-Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses we decide to use ZINB models.
-
-## NHST
-
-Following traditional NHST approach, we consider the model previously defined that includes all effects of interest.
-That is the gender effect and the interaction between mother attachment and father attachment.
-Subsequently, we can run an analysis of deviance to evaluate the significance of the predictors using the function `Anova()` from the R-package `car` [@foxCompanionAppliedRegression2019].
-```{r, echo =TRUE, cache=TRUE}
-car::Anova(fit_ext_zinb)
-```
-Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are no significant. Model summary is reported below.
-```{r, echo =TRUE, cache=TRUE}
-summary(fit_ext_zinb)
-```
-To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-nhst-effects).
-Not that the marginal predicted values for gender are averaged over mother and father attachment effects.
-Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
-```{r plot-nhst-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment.
-Values are averaged over the other effects ($n_{subj} = 847$)."}
-get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
-```
-
-Post-hoc test are run to evaluate differences between mother attachment styles.
-To do that we use the `contrast()` function from the `emmeans` R-package, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
-This approach is less restrictive than traditional *“Bonferroni”* method, as it determines the adjustment according to a multivariate *t*-distribution with the same covariance structure as the estimates.
-Results are reported below,
-```{r, cache=TRUE, echo = TRUE}
-emmeans::contrast(emmeans::emmeans(fit_ext_zinb, specs = ~ mother ),
-                  "pairwise", adjust = "mvt")
-```
-
-Overall, results indicate that Males have more externalizing problems than Females and, regarding mother attachment, Fearful children have more problems than Secure children.
-
-To evaluate the fit of model to the data, we used $R^2$.
-In the case of generalized mixed-effects models, however, there are several definitions of $R^2$.
-We computed the *Marginal* $R^2$ and the *Conditional* $R^2$ as suggested by @nakagawaCoefficientDeterminationR22017.
-*Marginal* $R^2$ is concerned with the variance explained by fixed factors of the model, and *Conditional* $R^2$ is concerned with the variance explained by both fixed and random factors of the model.
-To do that we use the function `performance::r2()`.
-
-```{r, echo=TRUE, message=FALSE, cache=TRUE}
-performance::r2(fit_ext_zinb)
-```
-
-We can see that the actual variance explained by fixed effects is almost 10\%, not bad for psychology.
-
-#### Conclusions {-}
-
-Considering attachment theoretical perspectives, results indicate only the role of mother attachment.
-Note, however, that traditional NHST does not allow us to evaluate evidence in favour of an hypotheses.
-Moreover, we actually have not tested our hypotheses but only the catch-all null hypothesis that *“nothing is going on”*.
-
-## Model Comparison
+# Model Comparison {#model-comparison-ext}
 
@@
 
-### Formalize Models
+## Formalize Models
 
-Following the same reasons as before (see Section~\@ref(model-choice)), we consider Zero Inflated Negative Binomial Mixed-Effects models.
-Again, we consider only the role of gender as fixed effect and children's classroom ID as random effect for $p$.
+Following the same reasons as before (see Section~\@ref(model-choice-ext)), we consider Zero Inflated Negative Binomial Mixed-Effects models.
+Again, we consider only the role of gender as a fixed effect and children's classroom ID as a random effect for $p$.
 Whereas, considering $\mu$, we define four different models to take into account the different theoretical perspectives:
@@
 
-### AIC and BIC Results
+## AIC and BIC Results
 
@@
 
-Accordinng to AIC, the most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "AIC")`\%) and the second most likely model is `fit_ext_additive` (`r perc_model_ext("fit_ext_additive", "AIC")`\%) given the data and the set of models considered.
+According to AIC, the most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "AIC")`\%) and the second most likely model is `fit_ext_additive` (`r perc_model_ext("fit_ext_additive", "AIC")`\%) given the data and the set of models considered.
 According to BIC, instead,  the most likely model is `fit_ext_zero` (`r perc_model_ext("fit_ext_zero", "BIC")`\%) and the second most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "BIC")`\%) given the data and the set of models considered.
 
-To interpret these results note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
+To interpret these results, note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
 As pointed by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
@@
 
-### Selected Model
+## Selected Model
 
@@
 Note, however, that the compared models contain no information regarding the expected direction of the effects but we only include/exclude predictors.
-
-## Bayes Factor
-
-To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes Factor with encompassing prior approach.
-See the main article for a detailed introduction to this approach [TODO: add link article].
-
-First, we define the encompassing model.
-Subsequently, we obtain the hypotheses matrices according to the informative hypotheses.
-Next, we compute the Bayes Factor and, finally, we describe the selected model.
-
-### Encompassing Model
-
-We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects model to take into account the characteristics of the dependent variable and its distribution (see Section~\@ref(model-choice)).
-Again, we consider only the role of gender as fixed effect and children’s classroom ID as random effect for $p$.
-Whereas, regarding $\mu$, we consider the interaction between mother and father attachment together with gender as fixed effects and children’s classroom ID as random effect.
-In the R formula syntax, we have
-```{r, echo=TRUE, eval=FALSE}
-# formula for p
-p ~ gender + (1|ID_class)
-
-# formula for mu
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-#### Prior Choiche {-}
-
-Prior choice is important for the parameters involved in the equality and inequality constraints.
-In our case, the parameters of interest (i.e., those related to mother and father attachment interaction) are unbounded.
-Thus, we can simply specify as prior a normal distribution with mean 0 and a given standard deviation.
-Considering the standard deviation, however, we have to choose a value so that the resulting prior is non-informative but without being excessively diffuse.
-
-We can evaluate the consequences of different values choice considering the resulting prior predictions.
-To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest.
-Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1, because $exp(1) \approx 2.7$ that is close to the externalizing problems sample mean  `r ext_mean()`.
-In Table~\@ref(tab:table-prior-predict), summary information about prior predictions for different standard deviation values are reported.
-```{r table-prior-predict}
-get_table_prior_predict(format = params$format)
-```
-
-Considering that externalizing problems are bounded between 0 and 20, a reasonable prior is  $\mathcal{N}(0,3)$.
-as prior predicted values cover all possible values without including excessively large values.
-More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values.
-The influence of prior specification will be subsequently evaluated in a prior sensitivity analysis.
-
-Regarding the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) `brms` default priors are maintained. The resulting prior settings are
-```{r prior-seettings}
-options(width = 300)
-brms::prior_summary(encompassing_model_ext)
-```
-
-#### Posterior{-}
-The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).
-To do that we use the `brm()` function from the `brms` R-package [@burknerBrmsPackageBayesian2017; @burknerAdvancedBayesianMultilevel2018a], which is based on STAN [@standevelopmentteamRStanInterfaceStan2020].
-Summary of the encompassing model is presented below.
-```{r}
-summary(encompassing_model_ext)
-```
-
-### Hypothesis Matrices
-
-For each informative hypothesis, we obtain an hypothesis matrix that translate equality and inequality constraints according to the encompassing model parametrization.
-Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ([TODO: add link]).
-
-Here we present the obtained hypothesis matrices were on the columns we have the parameters of the encompassing model (excluding the intercept) and each row express an equality constraint or an inequality constraint.
-Matrices row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters).
-For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicate the group condition.
-Equality and inequality constraints ar presented separately.
-
-#### Null Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("null", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero). There are no inequality constraints.
-
-#### Monotropy Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("monotropy", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("monotropy", encompassing_model_ext)$ineq
-```
-
-#### Hierarchy Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$ineq
-```
-
-#### Independence Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("independence", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("independence", encompassing_model_ext)$ineq
-```
-
-#### Integration Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("integration", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("integration", encompassing_model_ext)$ineq
-```
-
-### Centering and Adjusting
-
-So far we have specified the encompassing prior, obtained the model posterior distribution, and defined the hypotheses matrices.
-Now, we need to transform our parameters of interest and center the distribution on the constraints focal points of interest.
-We apply the following transformation
-$$
-\beta = R\theta - r
-$$
-but we can ignore $r$ as in all our constraints it is always a vector of zeros.
-
-Next, we get the adjusted prior and the posterior of the transformed parameters vector  $\beta$ (i.e., the parameters that identify the constraints) for each hypothesis. The adjusted prior is given by
-
-$$
-\pi_{adj}(\beta) \sim \mathcal{N}(0, \Sigma_{\beta}) = \mathcal{N}(0, R\Sigma_{\theta}R^T).
-$$
-Note that we set the mean vector to zero. The posterior is given by the same transformation
-$$
-Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\theta}-r, R\hat{\Sigma}_{\theta}R^T).
-$$
-See the main article for more details [TODO: add link].
-
-This adjustment, however, requires the hypothesis matrix $R$ to be *full-row-rank* (i.e., all constraints are linearly independent).
-However, this is not the case of the hierarchy hypothesis.
-To overcome this issue, we follow the solution presented in the main article.
-First define $R^*$ selecting the maximum number of independent rows.
-In this case 15 contrast are independent
-
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$hyp[1:15,]
-```
-
-```{r cache=TRUE}
-R <- get_hypothesis_matrix("hierarchy", encompassing_model_ext)$hyp
-```
-
-The remaining contrasts, instead, are obtained as linear combination of the other constraints. In particular,
-```{r, echo = TRUE, cache = TRUE}
-# Constraint 16: [M_Anx_F_Sec - M_Sec_F_Anx]
-all(R["[M_Anx_F_Sec - M_Sec_F_Anx]",] == R["[M_Anx_F_Sec]", ] - R["[M_Sec_F_Anx]", ])
-
-# Constraint 17: [M_Av_F_Sec - M_Sec_F_Av]
-all(R["[M_Av_F_Sec - M_Sec_F_Av]",] == - R["[M_Anx_F_Sec - M_Av_F_Sec]", ] + R["[M_Sec_F_Anx - M_Sec_F_Av]", ] +  R["[M_Anx_F_Sec - M_Sec_F_Anx]", ])
-
-# Constraint 18: [M_Fear_F_Sec - M_Sec_F_Fear] 
-all(R["[M_Fear_F_Sec - M_Sec_F_Fear]",] == R["[M_Av_F_Sec - M_Sec_F_Av]", ] + R["[M_Fear_F_Sec - M_Av_F_Sec]", ] - R["[M_Sec_F_Fear - M_Sec_F_Av]", ])
-```
-
-Before computing the Bayes Factor, note that we have a set of comparable hypotheses as exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero.
-The solution is the trivial solution of simply consider all parameters equal to zero.
-Finally, we do not need to standardize our parameters as they represent mean groups differences.
-See the main article for detailed explanation [TODO: add link article].
-
-### Results and Sensitivity
-
-To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in details in the main article [TODO: add link article].
-Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).
-
-```{r table-bf-results-ext, cache = TRUE}
-get_table_bf(bf_result = BF_weights_ext,
-             path_img = "images/", problem = "ext",
-             format = params$format)
-```
-
-Remember, however, that prior specification affects the Bayes Factor results.
-Therefore, we also evaluate the results considering different prior settings.
-In particular, we consider as possible priors for the parameters of interest:
-
-- $\mathcal{N}(0,.5)$ - unreasonable tight prior
-- $\mathcal{N}(0,1)$ - tighter prior
-- $\mathcal{N}(0,3)$ - original prior
-- $\mathcal{N}(0,5)$ - more diffuse prior
-- $\mathcal{N}(0,10)$ - unreasonably diffuse prior
-
-The results of the prior sensitivity analysis are reported in Table~\@ref(tab:table-sens-prior-analysis-ext).
-
-```{r table-sens-prior-analysis-ext, cache = TRUE}
-get_table_sens_analysis(summary_sensitivity_ext,
-                        format = params$format,
-                        bookdown = TRUE)
-```
-
-Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data.
-However, we can observe two distinct patterns.
-As the prior gets more diffuse, the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
-Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.
-
-To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
-On the contrary, equality constraints are highly affected by the prior definition (see he main article for more details[TODO: add link article]).
-
-All the defined hypotheses include equality constraints.
-Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
-Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).
-
-### Selected Model

### 2021-09-21 Documents/Bookdown/05-ext-BF.Rmd
rearrange structure bookdown

--- 2021-09-21 Documents/Bookdown/02-ext.Rmd
@@
----
-output: html_document
-editor_options: 
-  chunk_output_type: console
----
-# Externalizing Problems {#ext}
-
-In this chapter, we present the analyses to evaluate the different role of mother attachment and father attachment on children's externalizing problems.
-First, we discuss the appropriate models family to to take into account data characteristics.
-Next we conduct inference following three different approaches: 1) traditional Null Hypothesis Significance Testing (NHST) 2) Model Comparison using the AIC and BIC criteria 3) Bayes Factor with encompassing prior approach.
-
-## Models Family Choiche {#model-choice}
-
-Externalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20.
-Thus, we should use appropriate discrete distribution such as the *Poisson* distribution or the *Negative Binomial*.
-In the Poisson distribution mean and variance are defined according to the same parameter $\lambda$.
-On the contrary, Negative Binomial has an extra parameter to adjust the variance allowing more flexibility.
-Considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe that data have high dispersion with a long right tail.
-In this case, Poisson distribution would be a poor choice and we prefer Negative Binomial instead.
-
-Again, considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe an high peak of values at zero.
-Remember that this is not a clinical sample, thus it is expected that children majority has no problems or really few problem.
-We could question ourselves, however, whether a *Zero-Inflated* model may be appropriate
-
-### Zero Inflated Negative Binomial
-
-To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model.
-We consider in the model the role of gender and the interaction between mother attachment and father attachment.
-Moreover, we consider the children's classroom ID as a random effect to account for teachers' different ability to evaluate children's problems.
-Using R formula syntax, we have
-```{r echo = TRUE, eval=FALSE}
-# model formula
-externalizing_sum ~ gender + mother * father + (1|ID_class)
-```
-
-The model is fitted using the function `glmmTMB()` from the `glmmTMB` R-package [@brooksGlmmTMBBalancesSpeed2017].
-Next, we compare the number of observed zero and expected zeros using an adapted version of the function `check_zeroinflation()` from the R-package `performance` [@ludeckePerformancePackageAssessment2021] that solves a small bug (see issue https://github.com/easystats/performance/issues/367).
-```{r echo = TRUE, cache=TRUE}
-my_check_zeroinflation(fit_ext_nb)
-```
-
-Results indicate that the model is slightly under-fitting the number of zeros.
-Now, we can try to fit a *Zero Inflated Negative Binomial* (ZINB) model and compare the performance of the two models.
-ZINB models are defined as
-$$
-y_{ij} \sim ZINB(p_{ij}, \mu_{ij}, \phi),
-$$
-where $p_{ij}$ is the probability of an observation $y_{ij}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_{ij}$ indicates the probability of a given observation $y_{ij}$ being generated form a Negative Binomial distribution with mean $\mu_{ij}$ and variance $\sigma_{ij}^2 = \mu_{ij} + \frac{\mu_{ij}^2}{\phi}$.
-Moreover, we have that
-$$
-p_{ij} = \text{logit}^{-1}(X_i^T\beta_p+ Z_j^Tu_p),\\
-\mu_{ij} = \text{exp}(X_i^T\beta_{\mu}+ Z_j^Tu_{\mu}).
-$$
-That is, both $p$ and $\mu$ are modelled separately according to (possibly) different variables.
-In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ the consider also the interaction between mother attachment and father attachment.
-In both cases, we consider the children's classroom ID as a random effect (teachers may differ in the ability to detect children's problems and quantify them).
-Using R formula syntax, we have
-```{r echo = TRUE, eval=FALSE}
-# formula for p
-p ~ gender + (1|ID_class)
-
-# formula for mu
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-The ZINB model is fitted using the function `zeroinfl()` from the `pscl` R-package [@zeileisRegressionModelsCount2008].
-To compare the ZINB model and the Negative Binomial model we conduct an analysis of *Deviance*.
-Note that, in the case of generalized linear models (GLM), the deviance is the corresponding of the residual variance used in the traditional ANOVA in the case of linear models.
-```{r echo=TRUE, cache=TRUE}
-anova(fit_ext_nb, fit_ext_zinb)
-```
-
-Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses, we decide to use ZINB models.
-
-## NHST
-
-Following the traditional NHST approach, we consider the model previously defined that includes all effects of interest.
-That is the gender effect and the interaction between mother attachment and father attachment.
-Subsequently, we can run an analysis of deviance to evaluate the significance of the predictors using the function `Anova()` from the R-package `car` [@foxCompanionAppliedRegression2019].
-```{r, echo =TRUE, cache=TRUE}
-car::Anova(fit_ext_zinb)
-```
-Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are not significant. The model summary is reported below.
-```{r, echo =TRUE, cache=TRUE}
-summary(fit_ext_zinb)
-```
-To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-nhst-effects).
-Not that the marginal predicted values for gender are averaged over mother and father attachment effects.
-Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
-```{r plot-nhst-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment.
-Values are averaged over the other effects ($n_{subj} = 847$)."}
-get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
-```
-
-Post-hoc tests are run to evaluate differences between mother attachment styles.
-To do that we use the `contrast()` function from the `emmeans` R-package, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
-This approach is less restrictive than the traditional *“Bonferroni”* method, as it determines the adjustment according to a multivariate *t*-distribution with the same covariance structure as the estimates.
-Results are reported below,
-```{r, cache=TRUE, echo = TRUE}
-emmeans::contrast(emmeans::emmeans(fit_ext_zinb, specs = ~ mother ),
-                  "pairwise", adjust = "mvt")
-```
-
-Overall, results indicate that Males have more externalizing problems than Females and, regarding mother attachment, Fearful children have more problems than Secure children.
-
-To evaluate the fit of the model to the data, we used $R^2$.
-In the case of generalized mixed-effects models, however, there are several definitions of $R^2$.
-We computed the *Marginal* $R^2$ and the *Conditional* $R^2$ as suggested by @nakagawaCoefficientDeterminationR22017.
-*Marginal* $R^2$ is concerned with the variance explained by fixed factors of the model, and *Conditional* $R^2$ is concerned with the variance explained by both fixed and random factors of the model.
-To do that we use the function `performance::r2()`.
-
-```{r, echo=TRUE, message=FALSE, cache=TRUE}
-performance::r2(fit_ext_zinb)
-```
-
-We can see that the actual variance explained by fixed effects is almost 10\%, not bad for psychology.
-
-#### Conclusions {-}
-
-Considering attachment theoretical perspectives, results indicate only the role of mother attachment.
-Note, however, that traditional NHST does not allow us to evaluate evidence in favour of a hypothesis.
-Moreover, we actually have not tested our hypotheses but only the catch-all null hypothesis that *“nothing is going on”*.
-
-## Model Comparison
-
-Model comparison allows us to compare multiple hypotheses and identify which is the most supported by the data [@mcelreathStatisticalRethinkingBayesian2020].
-First, we need to formalize models according to our hypotheses.
-Subsequently, we can evaluate which is the most supported model among those considered according to the data using the AIC and BIC [@wagenmakersAICModelSelection2004; @akaike1973a; @schwarzEstimatingDimensionModel1978].
-
-### Formalize Models
-
-Following the same reasons as before (see Section~\@ref(model-choice)), we consider Zero Inflated Negative Binomial Mixed-Effects models.
-Again, we consider only the role of gender as a fixed effect and children's classroom ID as a random effect for $p$.
-Whereas, considering $\mu$, we define four different models to take into account the different theoretical perspectives:
-
-- `fit_ext_zero`: we consider only the effect of gender. This model assumes that attachment plays no role.
-- `fit_ext_mother`: we consider the additive effects of gender and mother attachment. This model supports the idea that only mother attachment is important (**Monotropy Theory**).
-- `fit_ext_additive`: we consider the additive effects of gender,  mother attachment, and father attachment.
-This model supports the idea that both mother attachment and father attachment are important, but not their interaction (**Hierarchy Theory** or **Independence Theory**).
-- `fit_ext_inter`: we consider the additive effects of gender and the interaction between mother attachment and father attachment.
-This model supports the idea that the interaction between mother attachment and father attachment is important (**Integration Theory**).
-
-Moreover, in all models, we include children's classroom ID as a random effect to take into account teachers' different ability to evaluate children's problems. Using R formula syntax, we have
-```{r, echo = TRUE, eval=FALSE}
-# formula for p (same for all models)
-p ~ gender + (1|ID_class)
-
-# formula for mu
-
-# fit_ext_zero
-mu ~ gender + (1|ID_class)
-
-# fit_ext_mother
-mu ~ gender + mother + (1|ID_class)
-
-# fit_ext_additive
-mu ~ gender + mother + father + (1|ID_class)
-
-# fit_ext_inter
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-### AIC and BIC Results
-
-After estimating the models, the AIC and BIC values together with their relative weights are computed. Results are reported in Table~\@ref(tab:table-AIC-BIC-weights).
-
-```{r table-AIC-BIC-weights, cache=TRUE}
-get_table_AIC_BIC(AIC_weights = AIC_weights_ext,
-                  BIC_weights = BIC_weights_ext,
-                  problem = "ext",
-                  format = params$format,
-                  path_img = "images/")
-```
-
-According to AIC, the most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "AIC")`\%) and the second most likely model is `fit_ext_additive` (`r perc_model_ext("fit_ext_additive", "AIC")`\%) given the data and the set of models considered.
-According to BIC, instead,  the most likely model is `fit_ext_zero` (`r perc_model_ext("fit_ext_zero", "BIC")`\%) and the second most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "BIC")`\%) given the data and the set of models considered.
-
-To interpret these results, note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
-As pointed by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
-We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.
-
-### Selected Model
-
-Considering model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
-```{r, echo =TRUE, cache=TRUE}
-car::Anova(fit_ext_mother)
-```
-Results confirm a statistically significant effect of gender and mother attachment. The model summary is reported below.
-```{r, echo =TRUE, cache=TRUE}
-summary(fit_ext_mother)
-```
-To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects).
-Not that the marginal predicted values for gender are averaged over mother attachment.
-Whereas, the marginal predicted values for mother attachment are averaged over gender.
-```{r plot-comparison-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
-get_plot_zinb(model = fit_ext_mother, attachment = "mother")
-```
-
-Post-hoc tests are run to evaluate differences between mother attachment styles, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
-Results are reported below,
-```{r, cache=TRUE, echo = TRUE}
-emmeans::contrast(emmeans::emmeans(fit_ext_mother, specs = ~ mother ),
-                  "pairwise", adjust = "mvt")
-```
-
-Overall, results indicate that Males have more externalizing problems than Females.
-Regarding mother attachment, Fearful and Avoidant children have more problems than Secure children.
-Moreover, also the difference between Anxious and Secure children and the difference between Anxious and Fearful children have a low (but not statistically significant) *p*-value.
-
-To evaluate the fit of the model to the data, we computed the *Marginal* $R^2$ and the *Conditional* $R^2$.
-
-```{r, echo=TRUE, message=FALSE, cache=TRUE}
-performance::r2(fit_ext_mother)
-```
-
-We can see that the actual variance explained by fixed effects is around 7\%, not bad for psychology.
-
-#### Conclusions {-}
-
-Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the **Monotropy Theory**.
-Note, however, that the compared models contain no information regarding the expected direction of the effects but we only include/exclude predictors.
-
-## Bayes Factor
+# Bayes Factor {#BF-ext}
 
@@
 
-### Encompassing Model
+## Encompassing Model
 
-We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects model to take into account the characteristics of the dependent variable and its distribution (see Section~\@ref(model-choice)).
+We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects model to take into account the characteristics of the dependent variable and its distribution (see Section~\@ref(model-choice-ext)).
 Again, we consider only the role of gender as a fixed effect and children’s classroom ID as a random effect for $p$.
@@
 
-#### Prior Choiche {-}
+### Prior Choiche
 
@@
 
-#### Posterior{-}
+### Posterior
 The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).
@@
 Summary of the encompassing model is presented below.
-```{r}
+```{r, cache=TRUE}
 summary(encompassing_model_ext)
@@
 
-### Hypothesis Matrices
+## Hypothesis Matrices
 
@@
 
-### Centering and Adjusting
+## Centering and Adjusting
 
@@
 
-### Results and Sensitivity
+## Results and Sensitivity
 
@@
 Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the Monotropy Theory.
-
-## Conclusions Externalizing Problems
-
-Overall, we obtained consistent results from the three different approaches.
-Males have more problems than Females and, regarding attachment, only mother attachment influence children's externalizing problems.
-In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems.
-Taken together, these results support the Monotropy Theory.
-
-Although if the different approaches lead to apparently similar results, the rigorous interpretation of the results is very different.
-
-- Considering the NHST approach, we actually only found that it is unlikely that mother attachment has no effect.
-Thus, we reject the null hypothesis but we can not quantify the evidence in favour of any of our hypotheses.
-- Only model comparison allow us to quantify the relative evidence of our models.
-Model comparison results clearly indicated evidence in favour of an effect of mother attachment but not father attachment.
-However, using information criteria we could not directly evaluate our informative hypotheses regarding the expected effects, but only the presence of any effect.
-- Bayes Factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects.
-Results clearly selected the Monotropy theory as the most likely theory among those considered.
-
-To summarize, the apparently identical results actually have a completely different meaning and what we learn from the data is very different.
-Hopefully, now it is clear that statistical inference is a complex process that requires careful thinking.
-In particular, to answer the questions we are actually interested in, we need to apply the appropriate statistical techniques.

### 2021-09-21 Documents/Bookdown/06-ext-conclusion.Rmd
rearrange structure bookdown

--- 2021-09-20 Documents/Bookdown/02-ext.Rmd
@@
 ---
-# Externalizing Problems {#ext}
+# Conclusions Externalizing Problems {#conclusion-ext}
 
-In this chapter, we present the analyses to evaluate the different role of mother attachment and father attachment on children's externalizing problems.
-First, we discuss the appropriate models family to to take into account data characteristics.
-Next we conduct inference following three different approaches: 1) traditional Null Hypothesis Significance Testing (NHST) 2) Model Comparison using the AIC and BIC criteria 3) Bayes Factor with encompassing prior approach.
+Overall, we obtained consistent results from the three different approaches.
+Males have more problems than Females and, regarding attachment, only mother attachment influence children's externalizing problems.
+In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems.
+Taken together, these results support the Monotropy Theory.
 
-## Models Family Choiche {#model-choice}
+Although if the different approaches lead to apparently similar results, the rigorous interpretation of the results is very different.
 
-Externalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20.
-Thus, we should use appropriate discrete distribution such as the *Poisson* distribution or the *Negative Binomial*.
-In the Poisson distribution mean and variance are defined according to the same parameter $\lambda$.
-On the contrary, Negative Binomial has an extra parameter to adjust the variance allowing more flexibility.
-Considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe that data have high dispersion with a long right tail.
-In this case, Poisson distribution would be a poor choice and we prefer Negative Binomial instead.
+- Considering the NHST approach, we actually only found that it is unlikely that mother attachment has no effect.
+Thus, we reject the null hypothesis but we can not quantify the evidence in favour of any of our hypotheses.
+- Only model comparison allow us to quantify the relative evidence of our models.
+Model comparison results clearly indicated evidence in favour of an effect of mother attachment but not father attachment.
+However, using information criteria we could not directly evaluate our informative hypotheses regarding the expected effects, but only the presence of any effect.
+- Bayes Factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects.
+Results clearly selected the Monotropy theory as the most likely theory among those considered.
 
-Again, considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe an high peak of values at zero.
-Remember that this is not a clinical sample, thus it is expected that children majority has no problems or really few problem.
-We could question ourselves, however, whether a *Zero-Inflated* model may be appropriate
-
-### Zero Inflated Negative Binomial
-
-To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model.
-We consider in the model the role of gender and the interaction between mother attachment and father attachment.
-Moreover, we consider the children's classroom ID as a random effect to account for teachers' different ability to evaluate children's problems.
-Using R formula syntax, we have
-```{r echo = TRUE, eval=FALSE}
-# model formula
-externalizing_sum ~ gender + mother * father + (1|ID_class)
-```
-
-The model is fitted using the function `glmmTMB()` from the `glmmTMB` R-package [@brooksGlmmTMBBalancesSpeed2017].
-Next, we compare the number of observed zero and expected zeros using an adapted version the function `check_zeroinflation()` from the R-package `performance` [@ludeckePerformancePackageAssessment2021] that solves a small bug (see issue https://github.com/easystats/performance/issues/367).
-```{r echo = TRUE, cache=TRUE}
-my_check_zeroinflation(fit_ext_nb)
-```
-
-Results indicate that the model is slightly under-fitting the number of zeros.
-Now, we can try to fit a *Zero Inflated Negative Binomial* (ZINB) model and compare the performance of the two models.
-ZINB models are defined as
-$$
-y_{i} \sim ZINB(p_{i}, \mu_{i}, \phi),
-$$
-where $p_i$ is the probability of an observation $y_{i}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_i$ indicates the probability of a given observation $y_{i}$ being generated form a Negative Binomial distribution with mean $\mu_{i}$ and variance $\sigma_{i}^2 = \mu_{i} + \frac{\mu_{i}^2}{\phi}$.
-Moreover, we have that
-$$
-p_{i} = \text{logit}^{-1}(X_i^T\beta_p),\\
-\mu_{i} = \text{exp}(X_i^T\beta_{\mu}).
-$$
-That is, both $p$ and $\mu$ are modelled separately according to (possibly) different variables.
-In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ the consider also the interaction between mother attachment and father attachment.
-In both cases, we consider the children's classroom ID as a random effect (teachers may differ in they ability to detect children's problem and quantify them).
-Using R formula syntax, we have
-```{r echo = TRUE, eval=FALSE}
-# formula for p
-p ~ gender + (1|ID_class)
-
-# formula for mu
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-The ZINB model is fitted using the function `zeroinfl()` from the `pscl` R-package [@zeileisRegressionModelsCount2008].
-To compare the ZINB model and the Negative Binomial model we conduct an analysis of *Deviance*.
-Note that, in the case of generalized linear models (GLM), the deviance is the corresponding of the residual variance used in the traditional ANOVA in the case of linear models.
-```{r echo=TRUE, cache=TRUE}
-anova(fit_ext_nb, fit_ext_zinb)
-```
-
-Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses we decide to use ZINB models.
-
-## NHST
-
-Following traditional NHST approach, we consider the model previously defined that includes all effects of interest.
-That is the gender effect and the interaction between mother attachment and father attachment.
-Subsequently, we can run an analysis of deviance to evaluate the significance of the predictors using the function `Anova()` from the R-package `car` [@foxCompanionAppliedRegression2019].
-```{r, echo =TRUE, cache=TRUE}
-car::Anova(fit_ext_zinb)
-```
-Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are no significant. Model summary is reported below.
-```{r, echo =TRUE, cache=TRUE}
-summary(fit_ext_zinb)
-```
-To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-nhst-effects).
-Not that the marginal predicted values for gender are averaged over mother and father attachment effects.
-Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
-```{r plot-nhst-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment.
-Values are averaged over the other effects ($n_{subj} = 847$)."}
-get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
-```
-
-Post-hoc test are run to evaluate differences between mother attachment styles.
-To do that we use the `contrast()` function from the `emmeans` R-package, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
-This approach is less restrictive than traditional *“Bonferroni”* method, as it determines the adjustment according to a multivariate *t*-distribution with the same covariance structure as the estimates.
-Results are reported below,
-```{r, cache=TRUE, echo = TRUE}
-emmeans::contrast(emmeans::emmeans(fit_ext_zinb, specs = ~ mother ),
-                  "pairwise", adjust = "mvt")
-```
-
-Overall, results indicate that Males have more externalizing problems than Females and, regarding mother attachment, Fearful children have more problems than Secure children.
-
-To evaluate the fit of model to the data, we used $R^2$.
-In the case of generalized mixed-effects models, however, there are several definitions of $R^2$.
-We computed the *Marginal* $R^2$ and the *Conditional* $R^2$ as suggested by @nakagawaCoefficientDeterminationR22017.
-*Marginal* $R^2$ is concerned with the variance explained by fixed factors of the model, and *Conditional* $R^2$ is concerned with the variance explained by both fixed and random factors of the model.
-To do that we use the function `performance::r2()`.
-
-```{r, echo=TRUE, message=FALSE, cache=TRUE}
-performance::r2(fit_ext_zinb)
-```
-
-We can see that the actual variance explained by fixed effects is almost 10\%, not bad for psychology.
-
-#### Conclusions {-}
-
-Considering attachment theoretical perspectives, results indicate only the role of mother attachment.
-Note, however, that traditional NHST does not allow us to evaluate evidence in favour of an hypotheses.
-Moreover, we actually have not tested our hypotheses but only the catch-all null hypothesis that *“nothing is going on”*.
-
-## Model Comparison
-
-Model comparison allows us to compare multiple hypotheses and identify which is the most supported by the data [@mcelreathStatisticalRethinkingBayesian2020].
-First, we need to formalize models according to our hypotheses.
-Subsequently, we can evaluate which is the most supported model among those considered according to the data using the AIC and BIC [@wagenmakersAICModelSelection2004; @akaike1973a; @schwarzEstimatingDimensionModel1978].
-
-### Formalize Models
-
-Following the same reasons as before (see Section~\@ref(model-choice)), we consider Zero Inflated Negative Binomial Mixed-Effects models.
-Again, we consider only the role of gender as fixed effect and children's classroom ID as random effect for $p$.
-Whereas, considering $\mu$, we define four different models to take into account the different theoretical perspectives:
-
-- `fit_ext_zero`: we consider only the effect of gender. This model assumes that attachment plays no role.
-- `fit_ext_mother`: we consider the additive effects of gender and mother attachment. This model supports the idea that only mother attachment is important (**Monotropy Theory**).
-- `fit_ext_additive`: we consider the additive effects of gender,  mother attachment, and father attachment.
-This model supports the idea that both mother attachment and father attachment are important, but not their interaction (**Hierarchy Theory** or **Independence Theory**).
-- `fit_ext_inter`: we consider the additive effects of gender and the interaction between mother attachment and father attachment.
-This model supports the idea that the interaction between mother attachment and father attachment is important (**Integration Theory**).
-
-Moreover, in all models we include children's classroom ID as random effect to take into  account teachers' different ability to evaluate children's problems. Using R formula syntax, we have
-```{r, echo = TRUE, eval=FALSE}
-# formula for p (same for all models)
-p ~ gender + (1|ID_class)
-
-# formula for mu
-
-# fit_ext_zero
-mu ~ gender + (1|ID_class)
-
-# fit_ext_mother
-mu ~ gender + mother + (1|ID_class)
-
-# fit_ext_additive
-mu ~ gender + mother + father + (1|ID_class)
-
-# fit_ext_inter
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-### AIC and BIC Results
-
-After estimating the models, the AIC and BIC values together with their relative weights are computed. Results are reported in Table~\@ref(tab:table-AIC-BIC-weights).
-
-```{r table-AIC-BIC-weights, cache=TRUE}
-get_table_AIC_BIC(AIC_weights = AIC_weights_ext,
-                  BIC_weights = BIC_weights_ext,
-                  problem = "ext",
-                  format = params$format,
-                  path_img = "images/")
-```
-
-Accordinng to AIC, the most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "AIC")`\%) and the second most likely model is `fit_ext_additive` (`r perc_model_ext("fit_ext_additive", "AIC")`\%) given the data and the set of models considered.
-According to BIC, instead,  the most likely model is `fit_ext_zero` (`r perc_model_ext("fit_ext_zero", "BIC")`\%) and the second most likely model is `fit_ext_mother` (`r perc_model_ext("fit_ext_mother", "BIC")`\%) given the data and the set of models considered.
-
-To interpret these results note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
-As pointed by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
-We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.
-
-### Selected Model
-
-Considering model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
-```{r, echo =TRUE, cache=TRUE}
-car::Anova(fit_ext_mother)
-```
-Results confirm a statistically significant effect of gender and mother attachment. Model summary is reported below.
-```{r, echo =TRUE, cache=TRUE}
-summary(fit_ext_mother)
-```
-To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects).
-Not that the marginal predicted values for gender are averaged over mother attachment.
-Whereas, the marginal predicted values for mother attachment are averaged over gender.
-```{r plot-comparison-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
-get_plot_zinb(model = fit_ext_mother, attachment = "mother")
-```
-
-Post-hoc test are run to evaluate differences between mother attachment styles, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution.
-Results are reported below,
-```{r, cache=TRUE, echo = TRUE}
-emmeans::contrast(emmeans::emmeans(fit_ext_mother, specs = ~ mother ),
-                  "pairwise", adjust = "mvt")
-```
-
-Overall, results indicate that Males have more externalizing problems than Females.
-Regarding mother attachment, Fearful and Avoidant children have more problems than Secure children.
-Moreover, also the difference between Anxious and Secure children and the difference between Anxious and Fearful children have a low (but not statistically significant) *p*-value.
-
-To evaluate the fit of model to the data, we computed the *Marginal* $R^2$ and the *Conditional* $R^2$.
-
-```{r, echo=TRUE, message=FALSE, cache=TRUE}
-performance::r2(fit_ext_mother)
-```
-
-We can see that the actual variance explained by fixed effects is around 7\%, not bad for psychology.
-
-#### Conclusions {-}
-
-Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the **Monotropy Theory**.
-Note, however, that the compared models contain no information regarding the expected direction of the effects but we only include/exclude predictors.
-
-## Bayes Factor
-
-To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes Factor with encompassing prior approach.
-See the main article for a detailed introduction to this approach [TODO: add link article].
-
-First, we define the encompassing model.
-Subsequently, we obtain the hypotheses matrices according to the informative hypotheses.
-Next, we compute the Bayes Factor and, finally, we describe the selected model.
-
-### Encompassing Model
-
-We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects model to take into account the characteristics of the dependent variable and its distribution (see Section~\@ref(model-choice)).
-Again, we consider only the role of gender as fixed effect and children’s classroom ID as random effect for $p$.
-Whereas, regarding $\mu$, we consider the interaction between mother and father attachment together with gender as fixed effects and children’s classroom ID as random effect.
-In the R formula syntax, we have
-```{r, echo=TRUE, eval=FALSE}
-# formula for p
-p ~ gender + (1|ID_class)
-
-# formula for mu
-mu ~ gender + mother * father + (1|ID_class)
-```
-
-#### Prior Choiche {-}
-
-Prior choice is important for the parameters involved in the equality and inequality constraints.
-In our case, the parameters of interest (i.e., those related to mother and father attachment interaction) are unbounded.
-Thus, we can simply specify as prior a normal distribution with mean 0 and a given standard deviation.
-Considering the standard deviation, however, we have to choose a value so that the resulting prior is non-informative but without being excessively diffuse.
-
-We can evaluate the consequences of different values choice considering the resulting prior predictions.
-To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest.
-Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1, because $exp(1) \approx 2.7$ that is close to the externalizing problems sample mean  `r ext_mean()`.
-In Table~\@ref(tab:table-prior-predict), summary information about prior predictions for different standard deviation values are reported.
-```{r table-prior-predict}
-get_table_prior_predict(format = params$format)
-```
-
-Considering that externalizing problems are bounded between 0 and 20, a reasonable prior is  $\mathcal{N}(0,3)$.
-as prior predicted values cover all possible values without including excessively large values.
-More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values.
-The influence of prior specification will be subsequently evaluated in a prior sensitivity analysis.
-
-Regarding the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) `brms` default priors are maintained. The resulting prior settings are
-```{r prior-seettings}
-options(width = 300)
-brms::prior_summary(encompassing_model_ext)
-```
-
-#### Posterior{-}
-The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).
-To do that we use the `brm()` function from the `brms` R-package [@burknerBrmsPackageBayesian2017; @burknerAdvancedBayesianMultilevel2018a], which is based on STAN [@standevelopmentteamRStanInterfaceStan2020].
-Summary of the encompassing model is presented below.
-```{r}
-summary(encompassing_model_ext)
-```
-
-### Hypothesis Matrices
-
-For each informative hypothesis, we obtain an hypothesis matrix that translate equality and inequality constraints according to the encompassing model parametrization.
-Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ([TODO: add link]).
-
-Here we present the obtained hypothesis matrices were on the columns we have the parameters of the encompassing model (excluding the intercept) and each row express an equality constraint or an inequality constraint.
-Matrices row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters).
-For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicate the group condition.
-Equality and inequality constraints ar presented separately.
-
-#### Null Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("null", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero). There are no inequality constraints.
-
-#### Monotropy Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("monotropy", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("monotropy", encompassing_model_ext)$ineq
-```
-
-#### Hierarchy Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$ineq
-```
-
-#### Independence Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("independence", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("independence", encompassing_model_ext)$ineq
-```
-
-#### Integration Hypothesis {-}
-
-- **Equality matrix**, $R_{iE} = 0$ (each row is set to zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("integration", encompassing_model_ext)$eq
-```
-
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
-```{r cache=TRUE}
-get_hypothesis_matrix("integration", encompassing_model_ext)$ineq
-```
-
-### Centering and Adjusting
-
-So far we have specified the encompassing prior, obtained the model posterior distribution, and defined the hypotheses matrices.
-Now, we need to transform our parameters of interest and center the distribution on the constraints focal points of interest.
-We apply the following transformation
-$$
-\beta = R\theta - r
-$$
-but we can ignore $r$ as in all our constraints it is always a vector of zeros.
-
-Next, we get the adjusted prior and the posterior of the transformed parameters vector  $\beta$ (i.e., the parameters that identify the constraints) for each hypothesis. The adjusted prior is given by
-
-$$
-\pi_{adj}(\beta) \sim \mathcal{N}(0, \Sigma_{\beta}) = \mathcal{N}(0, R\Sigma_{\theta}R^T).
-$$
-Note that we set the mean vector to zero. The posterior is given by the same transformation
-$$
-Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\theta}-r, R\hat{\Sigma}_{\theta}R^T).
-$$
-See the main article for more details [TODO: add link].
-
-This adjustment, however, requires the hypothesis matrix $R$ to be *full-row-rank* (i.e., all constraints are linearly independent).
-However, this is not the case of the hierarchy hypothesis.
-To overcome this issue, we follow the solution presented in the main article.
-First define $R^*$ selecting the maximum number of independent rows.
-In this case 15 contrast are independent
-
-```{r cache=TRUE}
-get_hypothesis_matrix("hierarchy", encompassing_model_ext)$hyp[1:15,]
-```
-
-```{r cache=TRUE}
-R <- get_hypothesis_matrix("hierarchy", encompassing_model_ext)$hyp
-```
-
-The remaining contrasts, instead, are obtained as linear combination of the other constraints. In particular,
-```{r, echo = TRUE, cache = TRUE}
-# Constraint 16: [M_Anx_F_Sec - M_Sec_F_Anx]
-all(R["[M_Anx_F_Sec - M_Sec_F_Anx]",] == R["[M_Anx_F_Sec]", ] - R["[M_Sec_F_Anx]", ])
-
-# Constraint 17: [M_Av_F_Sec - M_Sec_F_Av]
-all(R["[M_Av_F_Sec - M_Sec_F_Av]",] == - R["[M_Anx_F_Sec - M_Av_F_Sec]", ] + R["[M_Sec_F_Anx - M_Sec_F_Av]", ] +  R["[M_Anx_F_Sec - M_Sec_F_Anx]", ])
-
-# Constraint 18: [M_Fear_F_Sec - M_Sec_F_Fear] 
-all(R["[M_Fear_F_Sec - M_Sec_F_Fear]",] == R["[M_Av_F_Sec - M_Sec_F_Av]", ] + R["[M_Fear_F_Sec - M_Av_F_Sec]", ] - R["[M_Sec_F_Fear - M_Sec_F_Av]", ])
-```
-
-Before computing the Bayes Factor, note that we have a set of comparable hypotheses as exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero.
-The solution is the trivial solution of simply consider all parameters equal to zero.
-Finally, we do not need to standardize our parameters as they represent mean groups differences.
-See the main article for detailed explanation [TODO: add link article].
-
-### Results and Sensitivity
-
-To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in details in the main article [TODO: add link article].
-Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).
-
-```{r table-bf-results-ext, cache = TRUE}
-get_table_bf(bf_result = BF_weights_ext,
-             path_img = "images/", problem = "ext",
-             format = params$format)
-```
-
-Remember, however, that prior specification affects the Bayes Factor results.
-Therefore, we also evaluate the results considering different prior settings.
-In particular, we consider as possible priors for the parameters of interest:
-
-- $\mathcal{N}(0,.5)$ - unreasonable tight prior
-- $\mathcal{N}(0,1)$ - tighter prior
-- $\mathcal{N}(0,3)$ - original prior
-- $\mathcal{N}(0,5)$ - more diffuse prior
-- $\mathcal{N}(0,10)$ - unreasonably diffuse prior
-
-The results of the prior sensitivity analysis are reported in Table~\@ref(tab:table-sens-prior-analysis-ext).
-
-```{r table-sens-prior-analysis-ext, cache = TRUE}
-get_table_sens_analysis(summary_sensitivity_ext,
-                        format = params$format,
-                        bookdown = TRUE)
-```
-
-Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data.
-However, we can observe two distinct patterns.
-As the prior gets more diffuse, the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
-Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.
-
-To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
-On the contrary, equality constraints are highly affected by the prior definition (see he main article for more details[TODO: add link article]).
-
-All the defined hypotheses include equality constraints.
-Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
-Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).
-
-### Selected Model
+To summarize, the apparently identical results actually have a completely different meaning and what we learn from the data is very different.
+Hopefully, now it is clear that statistical inference is a complex process that requires careful thinking.
+In particular, to answer the questions we are actually interested in, we need to apply the appropriate statistical techniques.

### 2021-09-21 Documents/Bookdown/index.Rmd
rearrange structure bookdown

@@
 For more information regarding the Bayes Factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article].
-The supplemental material is structure as follow:
+The supplemental material is structure in three parts:
+
+#### 1) Presentation {-}
+
+In this section, we describe the aim of the study and the sample included in the study.
 
 - **Chapter \@ref(case-study) - Case Study.** We describe the sample included in the study and present the results of the cluster analysis to classify the different attachment patterns.
-- **Chapter \@ref(ext) - Externalizing Problems.** The analyses regarding externalizing problems are presented.
-First, we conduct the analysis following the traditional NHST approach.
-Subsequently, we consider Model Comparison using the AIC and BIC criteria.
-Finally, we consider the Bayes Factor with encompassing prior approach.
+
+#### 2) Exteranlizing Problems {-}
+
+In this section, the analyses to evaluate the different role of mother attachment and father attachment on children's externalizing problems are presented following three different approaches.
+
+- **Chapter \@ref(model-choice-ext) - Models Family Choice.**  We discuss the appropriate models family to to take into account data characteristics.
+- **Chapter \@ref(nhst-ext) - NHST.**  Analysis are conducted following the traditional Null Hypothesis Significance Testing (NHST).
+- **Chapter \@ref(model-comparison-ext) - Model Comparison.**  Analysis are conducted according to the  Model Comparison approach using the AIC and BIC criteria.
+- **Chapter \@ref(BF-ext) - Bayes Factor.**  Analysis are conducted following the Bayes Factor with encompassing prior approach.
+- **Chapter \@ref(conclusion-ext) - Conclusion.**  Results of the three approaches are discussed.
+
+#### 3) Interanlizing Problems {-}
+
 - **Chapter \@ref(int) - Internalizing Problems.** The analyses regarding internalizing problems are presented.

### 2021-09-21 Documents/Bookdown/03-ext-nhst.Rmd
add bookdown int analysis

@@
 ```
-To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-nhst-effects).
+To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-nhst-effects-ext).
 Not that the marginal predicted values for gender are averaged over mother and father attachment effects.
 Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
-```{r plot-nhst-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment.
+```{r plot-nhst-effects-ext, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment.
 Values are averaged over the other effects ($n_{subj} = 847$)."}

### 2021-09-21 Documents/Bookdown/04-ext-model-comparison.Rmd
add bookdown int analysis

@@
 
-After estimating the models, the AIC and BIC values together with their relative weights are computed. Results are reported in Table~\@ref(tab:table-AIC-BIC-weights).
+After estimating the models, the AIC and BIC values together with their relative weights are computed. Results are reported in Table~\@ref(tab:table-AIC-BIC-weights-ext).
 
-```{r table-AIC-BIC-weights, cache=TRUE}
+```{r table-AIC-BIC-weights-ext, cache=TRUE}
 get_table_AIC_BIC(AIC_weights = AIC_weights_ext,
@@
 ```
-To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects).
+To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects-ext).
 Not that the marginal predicted values for gender are averaged over mother attachment.
 Whereas, the marginal predicted values for mother attachment are averaged over gender.
-```{r plot-comparison-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
+```{r plot-comparison-effects-ext, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
 get_plot_zinb(model = fit_ext_mother, attachment = "mother")

### 2021-09-21 Documents/Bookdown/07-int-model-choice.Rmd
add bookdown int analysis

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# (PART\*) Internalizing Problems {-}

# Models Family Choice  {#model-choice-int}

In this chapter, we discuss the appropriate models family to to take into account data characteristics.

Internalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20. Considering data distribution (see Figure~\@ref(fig:plot-internalizing-dist)), we choose a **Negative Binomial** distribution to model the data.

## Zero Inflated Negative Binomial

As in the case of externalizing problems, we evaluate whether a *Zero-Inflated* model may be appropriate. We compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model considering the same predictors as in the case of externalizing problems. Using R formula syntax, we have
```{r echo = TRUE, eval=FALSE}
# model formula
internalizing_sum ~ gender + mother * father + (1|ID_class)
```

Comparing the number of observed zero and expected zeros, we get 
```{r echo = TRUE, cache=TRUE}
my_check_zeroinflation(fit_int_nb)
```
Results indicate that the model is slightly under-fitting the number of zeros. Thus, we can fit a *Zero Inflated Negative Binomial* (ZINB) model and compare the performance of the two models. Using R formula syntax, we have
```{r echo = TRUE, eval=FALSE}
# formula for p
p ~ gender + (1|ID_class)

# formula for mu
mu ~ gender + mother * father + (1|ID_class)
```

Below we report results of the analysis of deviance.
```{r echo=TRUE, cache=TRUE}
anova(fit_int_nb, fit_int_zinb)
```

Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Note, however, that BIC actually prefers the model without zero inflation. Nevertheless, in the following analyses we decide to use ZINB models to be consistent with the externalizing problems analysis.

### 2021-09-21 Documents/Bookdown/08-int-nhst.Rmd
add bookdown int analysis

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# NHST {#nhst-int}

Following the traditional NHST approach, we consider the model previously defined that includes all effects of interest (gender effect and the interaction between mother attachment and father attachment). Results of the analysis of deviance are reported below.
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_int_zinb)
```
Results indicate only a statistically significant effect of mother attachment. On the contrary, the interaction and father attachment are not significant. The model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_int_zinb)
```
To evaluate the effect of mother attachment, the marginal predicted values are presented in Figure~\@ref(fig:plot-nhst-effects-int). Not that the marginal predicted values are averaged over father attachment and gender effect.
```{r plot-nhst-effects-int, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to mother attachment. Values are averaged over the other effects ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_int_zinb, attachment = "mother", gender = FALSE)
```

Post-hoc tests are run to evaluate differences between mother attachment styles, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution. Results are reported below,
```{r, cache=TRUE, echo = TRUE}
emmeans::contrast(emmeans::emmeans(fit_int_zinb, specs = ~ mother ),
                  "pairwise", adjust = "mvt")
```

After adjusting p-values we actually get that there are no statistically significant differences. Without adjusting, difference between Anxious and Secure children and the difference between Fearful and Secure children have a low (but not statistically significant) *p*-value.
```{r, cache=TRUE, echo = TRUE}
emmeans::contrast(emmeans::emmeans(fit_int_zinb, specs = ~ mother ),
                  "pairwise", adjust = NULL)
```

To evaluate the fit of the model to the data, we computed the *Marginal* $R^2$ and the *Conditional* $R^2$.

```{r, echo=TRUE, message=FALSE, cache=TRUE}
performance::r2(fit_int_zinb)
```

We can see that the actual variance explained by fixed effects is less than 5\%, not that much.

#### Conclusions {-}

Results are difficult to interpret because we have a statistically significant effect of mother attachment, but, considering pot-hoc tests, we get no statistically significant difference.
Overall, we could say that, in some way, results indicate a role of mother attachment but this probably is small.

### 2021-09-21 Documents/Bookdown/09-int-model-comparison.Rmd
add bookdown int analysis

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Model Comparison {#model-comparison-int}

## Formalize Models

We consider Zero Inflated Negative Binomial Mixed-Effects models with only the role of gender as a fixed effect and children's classroom ID as a random effect for $p$. Whereas, considering $\mu$, we define the same models as in the analysis of externalizing problems. Using R formula syntax, we have
```{r, echo = TRUE, eval=FALSE}
# formula for p (same for all models)
p ~ gender + (1|ID_class)

# formula for mu

# fit_int_zero
mu ~ gender + (1|ID_class)

# fit_int_mother
mu ~ gender + mother + (1|ID_class)

# fit_int_additive
mu ~ gender + mother + father + (1|ID_class)

# fit_int_inter
mu ~ gender + mother * father + (1|ID_class)
```

## AIC and BIC Results

AIC and BIC values together with their relative weights are computed are reported in Table~\@ref(tab:table-AIC-BIC-weights-int).

```{r table-AIC-BIC-weights-int, cache=TRUE}
get_table_AIC_BIC(AIC_weights = AIC_weights_int,
                  BIC_weights = BIC_weights_int,
                  problem = "int",
                  format = params$format,
                  path_img = "images/")
```

According to AIC, the most likely model is `fit_int_mother` (`r perc_model_int("fit_int_mother", "AIC")`\%) and the second most likely model is `fit_int_additive` (`r perc_model_int("fit_int_additive", "AIC")`\%) given the data and the set of models considered. According to BIC, instead, `fit_int_zero` and `fit_int_mother` models have almost the same probability, `r perc_model_int("fit_int_zero", "BIC")`\% and `r perc_model_int("fit_int_mother", "BIC")`\% respectively.

We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.

## Selected Model

Results of analysis of deviance for  model `fit_int_mother` are reported below.
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_int_mother)
```
Results confirm a statistically significant effect of mother attachment. The model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_int_mother)
```
To evaluate the effect of mother attachment, the marginal predicted values are presented in Figure~\@ref(fig:plot-comparison-effects-int). Not that the marginal predicted values for gender are averaged over mother attachment. Whereas, the marginal predicted values for mother attachment are averaged over gender.
```{r plot-comparison-effects-int, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_int_mother, attachment = "mother", gender = FALSE)
```

Post-hoc tests are run, considering pairwise comparisons and adjusting *p*-values according to multivariate *t*-distribution. Results are reported below,
```{r, cache=TRUE, echo = TRUE}
emmeans::contrast(emmeans::emmeans(fit_int_mother, specs = ~ mother ),
                  "pairwise", adjust = "mvt")
```

Results indicate that Fearful and Anxious children have more problems than Secure children. Moreover, also the difference between Avoidant and Fearful children is significant.

To evaluate the fit of the model to the data, we computed the *Marginal* $R^2$ and the *Conditional* $R^2$.

```{r, echo=TRUE, message=FALSE, cache=TRUE}
performance::r2(fit_int_mother)
```

We can see that the actual variance explained by fixed effects is 3\%, not that much.

#### Conclusions {-}

Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the **Monotropy Theory**. Note, however, that the compared models contain no information regarding the expected direction of the effects but we only include/exclude predictors.

### 2021-09-21 Documents/Bookdown/10-int-BF.Rmd
add bookdown int analysis

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Bayes Factor {#BF-int}

## Encompassing Model

We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects considering only the role of gender as a fixed effect and children’s classroom ID as a random effect for $p$. Whereas, regarding $\mu$, we consider the interaction between mother and father attachment together with gender as fixed effects and children’s classroom ID as a random effect. In the R formula syntax, we have
```{r, echo=TRUE, eval=FALSE}
# formula for p
p ~ gender + (1|ID_class)

# formula for mu
mu ~ gender + mother * father + (1|ID_class)
```

### Prior Choiche

We set the same prior as for the externalizing problems analysis. The resulting prior settings are
```{r prior-settings-encompassing-int}
options(width = 300)
brms::prior_summary(encompassing_model_int)
```

### Posterior

The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000). Summary of the encompassing model is presented below.
```{r, cache=TRUE}
summary(encompassing_model_int)
```

## Hypothesis Matrices

Hypothesis matrices are the same as for the externalizing problems analysis.

## Centering and Adjusting

Centering and adjusting procedures are the same as for the externalizing problems analysis.

## Results and Sensitivity

Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-int).

```{r table-bf-results-int, cache = TRUE}
get_table_bf(bf_result = BF_weights_int,
             path_img = "images/", problem = "int",
             format = params$format)
```

Prior sensitivity analysis is conducted considering the same prior as for the externalizing problems analysis. The results of the prior sensitivity analysis are reported in Table~\@ref(tab:table-sens-prior-analysis-int).

```{r table-sens-prior-analysis-int, cache = TRUE}
get_table_sens_analysis(summary_sensitivity_int,
                        format = params$format,
                        bookdown = TRUE)
```

Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data. However, we can observe the same patterns as for the externalizing problems analysis. More diffuse prior, favour hypothesis with more equality constraints. Whereas, tighter prior penalize hypothesis with more equality constraints.

## Selected Model

In the model we consider only the role of gender and mother attachment as fixed effects of $\mu$. In the R formula syntax, we have
```{r, echo=TRUE, eval=FALSE}
# formula for p
p ~ gender + (1|ID_class)

# formula for mu
mu ~ gender + mother + (1|ID_class)
```
Again, we specify the same prior distributions as before. The resulting prior settings are
```{r prior-settings-selcted-int, cache=TRUE}
brms::prior_summary(brm_selected_int)
```

The model is estimated using 6 independent chains with 6,000 iterations (warm-up 2,000). The model summary is presented below.
```{r cache=TRUE}
summary(brm_selected_int)
```

Marginal effects are presented in Figure~\@ref(fig:plot-marginal-int) and differences between mother attachment patterns are reported in Figure~\@ref(fig:plot-diff-int).
```{r plot-marginal-int, cache=TRUE, fig.asp=.5, out.width="95%", message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
plot_post_pred(post_pred_int, problem = "Internalizing")
```

```{r plot-diff-int, cache=TRUE, fig.asp=.5, message=FALSE, fig.cap="Predicted differences between mother attachment patterns ($n_{subj} = 847$)."}
plot_post_diff(post_pred_int, problem = "Internalizing")
```

Overall, results indicate that Fearful, and Anxious children have more problems than Secure children. Moreover, Fearful children have more problems than Avoidant children. Finally, also the difference between Avoidant and Anxious children is close to the threshold.

To evaluate the fit of the model to the data, we computed the *Bayesian* $R^2$ and using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-int).

```{r, echo=TRUE, message=FALSE, cache=TRUE}
r2_int
```

```{r plot-ppcheck-int, cache=TRUE, fig.cap="Posterior predictive check ($n_{subj} = 847$).", message=FALSE,}
my_pp_check(brm_selected_int, problem = "Internalizing")
```

We can see that the actual variance explained by fixed effects and random effect is around 22\%. Moreover, posterior predictive check indicates a good fit to the data.

#### Conclusions{-}

Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the Monotropy Theory.

### 2021-09-21 Documents/Bookdown/11-int-conclusion.Rmd
add bookdown int analysis

--- 2021-09-21 Documents/Bookdown/06-ext-conclusion.Rmd
@@
 ---
-# Conclusions Externalizing Problems {#conclusion-ext}
+# Conclusions {#conclusion-int}
 
-Overall, we obtained consistent results from the three different approaches.
-Males have more problems than Females and, regarding attachment, only mother attachment influence children's externalizing problems.
+Overall, we obtained consistent results from the three different approaches: only mother attachment influence children's externalizing problems.
 In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems.
+Compared to externalizing problems, however, difference between attachment groups are less pronounced.
 Taken together, these results support the Monotropy Theory.
-
-Although if the different approaches lead to apparently similar results, the rigorous interpretation of the results is very different.
-
-- Considering the NHST approach, we actually only found that it is unlikely that mother attachment has no effect.
-Thus, we reject the null hypothesis but we can not quantify the evidence in favour of any of our hypotheses.
-- Only model comparison allow us to quantify the relative evidence of our models.
-Model comparison results clearly indicated evidence in favour of an effect of mother attachment but not father attachment.
-However, using information criteria we could not directly evaluate our informative hypotheses regarding the expected effects, but only the presence of any effect.
-- Bayes Factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects.
-Results clearly selected the Monotropy theory as the most likely theory among those considered.
-
-To summarize, the apparently identical results actually have a completely different meaning and what we learn from the data is very different.
-Hopefully, now it is clear that statistical inference is a complex process that requires careful thinking.
-In particular, to answer the questions we are actually interested in, we need to apply the appropriate statistical techniques.

### 2021-09-21 Documents/Bookdown/index.Rmd
add bookdown int analysis

@@
 
-In this section, the analyses to evaluate the different role of mother attachment and father attachment on children's externalizing problems are presented following three different approaches.
+In this section, we present the analyses evaluating the different role of mother attachment and father attachment on children's externalizing problems. We follow three different approaches.
 
@@
 
-- **Chapter \@ref(int) - Internalizing Problems.** The analyses regarding internalizing problems are presented.
-The analyses follow the same structure as the case of externalizing problems.
-Thus, only differences will be highlighted.
+In this section, we present the analyses evaluating the different role of mother attachment and father attachment on children's internalizing problems.
+We follow the three different approaches as for the externalizing problems analysis.
+This section is shorter than previous as we focus only on the results without repeating all the descriptions of the methods.
+
+- **Chapter \@ref(model-choice-int) - Models Family Choice.**  We discuss the appropriate models family to to take into account data characteristics.
+- **Chapter \@ref(nhst-int) - NHST.**  Analysis are conducted following the traditional Null Hypothesis Significance Testing (NHST).
+- **Chapter \@ref(model-comparison-int) - Model Comparison.**  Analysis are conducted according to the  Model Comparison approach using the AIC and BIC criteria.
+- **Chapter \@ref(BF-int) - Bayes Factor.**  Analysis are conducted following the Bayes Factor with encompassing prior approach.
+- **Chapter \@ref(conclusion-int) - Conclusion.**  Results of the three approaches are discussed.
 

### 2021-09-21 Documents/Utils_report.R

@@ -146,12 +146,31 @@ drake_load_bookdown <- function(){
   load_glob_env(BF_weights_ext)
   load_glob_env(summary_sensitivity_ext)
 
-  load_glob_env(data_prior_predict)
-
   load_glob_env(brm_selected_ext)
   load_glob_env(post_pred_ext)
   load_glob_env(r2_ext)
+
   #----    Internalizing    ----
+  # Zero inflation
+  load_glob_env(fit_int_nb)
+
+  # ANOVA
+  load_glob_env(fit_int_zinb)
+
+  # model comparison
+  load_glob_env(fit_int_mother)
+  load_glob_env(AIC_weights_int)
+  load_glob_env(BIC_weights_int)
+
+  # BF encompassing
+  load_glob_env(encompassing_model_int)
+  load_glob_env(BF_weights_int)
+  load_glob_env(summary_sensitivity_int)
+
+
+  load_glob_env(brm_selected_int)
+  load_glob_env(post_pred_int)
+  load_glob_env(r2_int)
 }
 
 #----    get_sigma_example    ----

### 2021-09-21 R/Plan.R

@@ -140,6 +140,13 @@ get_analysis_plan <- function(){
                                                       prior_sensitivity_int_05,
                                                       prior_sensitivity_int_10),
 
+    # selected model
+    brm_selected_int = zinb_brms_selected(data = data_cluster,
+                                          y = "internalizing_sum",
+                                          prior_par = "normal(0, 3)"),
+    post_pred_int = get_post_pred(brm_selected_int),
+    r2_int = brms::bayes_R2(brm_selected_int),
+
     #=============================
     #----    Externalizing    ----
     #=============================

### 2021-09-21 R/Plots.R

@@ -17,23 +17,8 @@
 #' get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
 #'
 
-get_plot_zinb <- function(model, attachment = c("interaction", "mother")){
+get_plot_zinb <- function(model, attachment = c("interaction", "mother"), gender = TRUE){
   attachment <- match.arg(attachment)
-
-  marginal_effects_gender <- emmeans::emmeans(model, specs = ~ gender) %>%
-    as.data.frame() %>%
-    mutate_at(vars(emmean, lower.CL, upper.CL), exp) %>%
-    mutate(gender = recode_factor(gender, "F" = "Female", "M" = "Male"))
-
-  p_gender <- ggplot(marginal_effects_gender,
-                     aes(x = gender, y = emmean, colour = gender)) +
-    geom_point(show.legend = FALSE, size = 3) +
-    geom_errorbar(aes(ymin=lower.CL, ymax = upper.CL, colour = gender),
-                  size = 1, width = .2, show.legend = FALSE) +
-    labs(x = "Gender",
-         y = "Problems") +
-    coord_cartesian(ylim = c(0, 7.5)) +
-    theme_bw()
 
   if(attachment == "interaction"){
     marginal_effects_att <- emmeans::emmeans(model, specs = ~ mother*father) %>%
@@ -72,8 +57,28 @@ get_plot_zinb <- function(model, attachment = c("interaction", "mother")){
     layout <- matrix(c(1,1,2,2,2), nrow = 1)
   }
 
+  if(isTRUE(gender)){
+    marginal_effects_gender <- emmeans::emmeans(model, specs = ~ gender) %>%
+      as.data.frame() %>%
+      mutate_at(vars(emmean, lower.CL, upper.CL), exp) %>%
+      mutate(gender = recode_factor(gender, "F" = "Female", "M" = "Male"))
 
-  gridExtra::grid.arrange(p_gender, p_attachemnt, layout_matrix = layout)
+    p_gender <- ggplot(marginal_effects_gender,
+                       aes(x = gender, y = emmean, colour = gender)) +
+      geom_point(show.legend = FALSE, size = 3) +
+      geom_errorbar(aes(ymin=lower.CL, ymax = upper.CL, colour = gender),
+                    size = 1, width = .2, show.legend = FALSE) +
+      labs(x = "Gender",
+           y = "Problems") +
[…]

### 2021-09-21 R/Values.R

@@ -143,6 +143,19 @@ perc_model_ext <- function(model, ic = c("AIC", "BIC")){
 ext_mean <- function(){
   my_round(mean(data_cluster$externalizing_sum))
 }
+
+#----    perc_model_int    ----
+perc_model_int <- function(model, ic = c("AIC", "BIC")){
+  ic <- match.arg(ic)
+
+  if(ic == "AIC"){
+    res <- AIC_weights_int[AIC_weights_int$names == model, "weights"]
+  } else {
+    res <- BIC_weights_int[BIC_weights_int$names == model, "weights"]
+  }
+
+  return(my_perc(res, 0))
+}
 #-----
 
 #-------

### 2021-09-21 docs/attachment-bayes-factor.tex
publish supplmental

@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{longtable,booktabs,array}
@@
 \subtitle{Supplemental Material}
-\author{Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
-\date{2021-09-14}
+\author{\href{https://claudiozandonella.netlify.app/}{Claudio Zandonella Callegher}, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
+\date{2021-09-21}
 
@@
 
-\hypertarget{prerequisites}{%
-\chapter*{Prerequisites}\label{prerequisites}}
-\addcontentsline{toc}{chapter}{Prerequisites}
+\hypertarget{introduction}{%
+\chapter*{Introduction}\label{introduction}}
+\addcontentsline{toc}{chapter}{Introduction}
 
-trial
+This is the Supplemental Material of the article ``\emph{Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach}'' {[}TODO: add cit{]}.
+The aim of the paper is to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.
 
-\hypertarget{intro}{%
-\chapter{Introduction}\label{intro}}
+\hypertarget{study-summary}{%
+\section*{Study Summary}\label{study-summary}}
+\addcontentsline{toc}{section}{Study Summary}
 
-trial code
+When conducting a study, researchers usually have expectations based on hypotheses or theoretical perspectives they want to evaluate.
+Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called ``\emph{informative hypotheses}''.
+However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are unsuitable for testing complex informative hypotheses.
+An alternative approach is to use the Bayes Factor.
+In particular, the Bayes Factor based on the ``\emph{encompassing prior approach}'' allows researchers to easily evaluate complex informative hypotheses.
+In this paper we provide a clear and detailed introduction to this approach.
+We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor following the encompassing prior approach.
+Subsequently, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development.
 
-\begin{verbatim}
-##   ID ID_class externalizing_sum internalizing_sum gender age_year Avm      Avp
-## 1 25        2                16                 7      F     8.42 1.0 1.000000
-## 2 27        2                 3                 3      F     9.00 2.0 2.166667
-## 3 29        2                 5                 5      M     9.00 3.5 2.200000
-## 4 30        2                11                11      M     8.92 1.6 2.666667
-## 5 31        2                 0                 1      F     9.00 2.0 2.800000
-## 6 32        2                 4                12      F     8.92 3.0 2.833333
-##        av_m      av_p     Anxm     Anxp     anx_m     anx_p  mother   father
-## 1 1.0000000 1.0000000 1.000000 1.000000 0.8333333 1.0000000  Secure   Secure
-## 2 1.0000000 1.0000000 1.000000 1.000000 1.0000000 1.0000000 Anxious   Secure
-## 3 1.0000000 0.8333333 1.500000 2.400000 1.0000000 0.8333333 Fearful  Anxious
-## 4 0.8333333 1.0000000 1.600000 1.666667 0.8333333 1.0000000 Anxious Avoidant
-## 5 1.0000000 0.8333333 1.833333 1.333333 1.0000000 1.0000000 Anxious Avoidant
-## 6 1.0000000 1.0000000 3.200000 2.833333 0.8333333 1.0000000 Anxious  Fearful
-##            interaction
-## 1    M_Secure_F_Secure
-## 2   M_Anxious_F_Secure
-## 3  M_Fearful_F_Anxious
-## 4 M_Anxious_F_Avoidant
-## 5 M_Anxious_F_Avoidant
-## 6  M_Anxious_F_Fearful
-\end{verbatim}
+\hypertarget{supplemental-material-structure}{%
+\section*{Supplemental Material Structure}\label{supplemental-material-structure}}
+\addcontentsline{toc}{section}{Supplemental Material Structure}
 
-plot trial
+In the supplemental material we provide the complete statistical analyses of the case study regarding attachment.
+For more information regarding the Bayes Factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article {[}TODO: add link article{]}.
+The supplemental material is structure in three parts:
 
-\includegraphics{attachment-bayes-factor_files/figure-latex/unnamed-chunk-3-1.pdf}
+\hypertarget{presentation}{%
+\subsubsection*{1) Presentation}\label{presentation}}
+\addcontentsline{toc}{subsubsection}{1) Presentation}
 
-table trial
+In this section, we describe the aim of the study and the sample included in the study.
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Chapter \ref{case-study} - Case Study.} We describe the sample included in the study and present the results of the cluster analysis to classify the different attachment patterns.
+\end{itemize}
+
+\hypertarget{exteranlizing-problems}{%
+\subsubsection*{2) Exteranlizing Problems}\label{exteranlizing-problems}}
+\addcontentsline{toc}{subsubsection}{2) Exteranlizing Problems}
+
+In this section, we present the analyses evaluating the different role of mother attachment and father attachment on children's externalizing problems. We follow three different approaches.
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Chapter \ref{model-choice-ext} - Models Family Choice.} We discuss the appropriate models family to to take into account data characteristics.
+\item
+  \textbf{Chapter \ref{nhst-ext} - NHST.} Analysis are conducted following the traditional Null Hypothesis Significance Testing (NHST).
+\item
+  \textbf{Chapter \ref{model-comparison-ext} - Model Comparison.} Analysis are conducted according to the Model Comparison approach using the AIC and BIC criteria.
+\item
+  \textbf{Chapter \ref{BF-ext} - Bayes Factor.} Analysis are conducted following the Bayes Factor with encompassing prior approach.
+\item
+  \textbf{Chapter \ref{conclusion-ext} - Conclusion.} Results of the three approaches are discussed.
+\end{itemize}
+
+\hypertarget{interanlizing-problems}{%
+\subsubsection*{3) Interanlizing Problems}\label{interanlizing-problems}}
+\addcontentsline{toc}{subsubsection}{3) Interanlizing Problems}
+
+In this section, we present the analyses evaluating the different role of mother attachment and father attachment on children's internalizing problems.
+We follow the three different approaches as for the externalizing problems analysis.
+This section is shorter than previous as we focus only on the results without repeating all the descriptions of the methods.
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Chapter \ref{model-choice-int} - Models Family Choice.} We discuss the appropriate models family to to take into account data characteristics.
+\item
+  \textbf{Chapter \ref{nhst-int} - NHST.} Analysis are conducted following the traditional Null Hypothesis Significance Testing (NHST).
+\item
+  \textbf{Chapter \ref{model-comparison-int} - Model Comparison.} Analysis are conducted according to the Model Comparison approach using the AIC and BIC criteria.
+\item
+  \textbf{Chapter \ref{BF-int} - Bayes Factor.} Analysis are conducted following the Bayes Factor with encompassing prior approach.
+\item
+  \textbf{Chapter \ref{conclusion-int} - Conclusion.} Results of the three approaches are discussed.
+\end{itemize}
+
+\hypertarget{github}{%
+\section*{GitHub}\label{github}}
+\addcontentsline{toc}{section}{GitHub}
+
+All the materials are available at the GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
+
+Refer to the \texttt{README} file for further information.
+
+\hypertarget{part-presentation}{%
+\part*{Presentation}\label{part-presentation}}
+\addcontentsline{toc}{part}{Presentation}
+
+\hypertarget{case-study}{%
+\chapter{Case Study}\label{case-study}}
+
+In this chapter, first, we describe the aim of the study.
+Subsequently, we describe the sample included in the study.
+We present general information about the sample and the results of the cluster analysis to classify the different attachment patterns.
+Finally, we consider children's social-emotional problems.
+
+\hypertarget{aim-of-the-study}{%
+\section{Aim of the Study}\label{aim-of-the-study}}
+
+The aim of the study is to compare the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social emotional development.
+In the literature, four different main theoretical perspectives have been identified \citep{brethertonFathersAttachmentTheory2010}:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Monotropy Theory} - only the mother has an impact on children's development.
+\item
+  \textbf{Hierarchy Theory} - the mother has a greater impact on children development than the the father.
+\item
+  \textbf{Independence Theory} - all attachment figures are equally important but they affect the children's development differently.
+\item
+  \textbf{Integration Theory} - to understand the impact on children's development it is necessary to consider attachment relationships taken together.
+\end{itemize}
+
+Contrasting results have been reported by studies investigating which is the ``correct'' theory.
+No study, however, has tried to properly evaluate the different theoretical perspectives by directly comparing the different hypotheses.
+
+For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article {[}TODO: add link article{]}.
+
+\hypertarget{the-study-sample}{%
+\section{The Study Sample}\label{the-study-sample}}
+
+To evaluate the different role of father attachment and mother attachment, we consider 854 Italian children from third to sixth school grade.
+Only middle-childhood children are included in the analysis (5 participants are excluded as older than 12.3 years and 2 participants are excluded are excluded as the age is missing).
+The total sample size included in the analysis is 847 (50.65 \% Females).
+Participants frequencies by grade and gender are reported in Table\textasciitilde\ref{tab:table-gender-grade}.
 
@@
 
-\caption{\label{tab:unnamed-chunk-4}Attachment styles frequencies ($n_{subj} = 847$).}
+\caption{\label{tab:table-gender-grade}Participants frequancies by grade and gender ($n_{subj} = 847$).}
 \centering
-\begin{tabular}[t]{rccccc}
+\begin{tabular}[t]{>{}rccc}
 \toprule
-\multicolumn{1}{c}{\textbf{ }} & \multicolumn{4}{c}{\textbf{Father Attachment}} & \multicolumn{1}{c}{\textbf{ }} \\
-\cmidrule(l{3pt}r{3pt}){2-5}
-\textbf{Mother Attachemnt} & \textbf{Secure} & \textbf{Anxious} & \textbf{Avoidant} & \textbf{Fearful} & \textbf{Total}\\
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{2}{c}{\textbf{Gender}} & \multicolumn{1}{c}{\textbf{ }} \\
+\cmidrule(l{3pt}r{3pt}){2-3}
+\textbf{Grade} & \textbf{Females} & \textbf{Males} & \textbf{Total}\\
 \midrule
-Secure & 125 & 49 & 49 & 8 & 231\\
-Anxious & 51 & 100 & 98 & 37 & 286\\
-Avoidant & 25 & 67 & 126 & 12 & 230\\
-Fearful & 5 & 14 & 38 & 43 & 100\\
-Total & 206 & 230 & 311 & 100 & 847\\
+\textbf{3rd} & 133 & 127 & 260\\
+\textbf{4th} & 81 & 75 & 156\\
+\textbf{5th} & 36 & 32 & 68\\
+\textbf{6th} & 179 & 184 & 363\\
+\textbf{Total} & 429 & 418 & 847\\
 \bottomrule
@@
 
-trial citation
+Participants age mean is 10.28 (SD = 1.34). The participants age summary statistics are reported below and the distribution is presented in Figure\textasciitilde\ref{fig:plot-age}.
 
-\citep{guApproximatedAdjustedFractional2018}
+\begin{verbatim}
+##   # Age summary statistics
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
+##    7.92    9.00   10.25   10.28   11.58   12.25
+\end{verbatim}
 
-troppe cit \citep{mcelreathStatisticalRethinkingBayesian2020}
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-age-1}
+
+}
+
+\caption{Participants age distribution ($n_{subj} = 847$)}\label{fig:plot-age}
+\end{figure}
+
+\hypertarget{attachment-styles}{%
+\section{Attachment Styles}\label{attachment-styles}}
+
+Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale (ECR; {[}TODO add references{]}) completed by the children.
+Four main attachment styles have been recognized in the literature according to thee levels of \emph{anxiety} and \emph{avoidance}:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Secure Attachment -} children with low levels of anxiety and avoidance.
+\item
+  \textbf{Anxious Attachment -} children characterized by high levels of anxiety.
+\item
+  \textbf{Avoidant Attachment -} children characterized by high levels of avoidance.
+\item
+  \textbf{Fearful Attachment -} children with high levels of anxiety and avoidance.
+\end{itemize}
+
+To identify children attachment styles towards the mother and towards the father, we conduct two separate cluster analyses.
+Clusters are obtained using the function \texttt{hclust()} (with argument \texttt{method="ward.D"}) considering \emph{Euclidean} distances between participants responses to the ECR items.
+
+\hypertarget{mother-cluster-analysis}{%
+\subsection{Mother Cluster Analysis}\label{mother-cluster-analysis}}
+
+Regarding mother attachment, 4 groups are selected from the cluster analysis results (see Figure\textasciitilde\ref{fig:plot-cluster-mother}).
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-cluster-mother-1}
+
+}
+
+\caption{Mother attachment cluster dendrogram ($n_{subj} = 847$).}\label{fig:plot-cluster-mother}
+\end{figure}
+
+In Figure\textasciitilde\ref{fig:plot-scores-mother}, Anxiety (``\emph{Anx}'') and Avoidance (``\emph{Av}'') scores are presented according to mother attachment styles.
+The frequencies of mother attachment styles according to gender are reported in Table\textasciitilde{}\ref{tab:table-cluster-mother}.
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-scores-mother-1}
+
+}
+
+\caption{Anxiety (“Anx”) and Avoidance (“Av”) scores according to mother attachment styles. Dashed lines represents overall average values ($n_{subj} = 847$).}\label{fig:plot-scores-mother}
+\end{figure}
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-cluster-mother}Mother attachment styles by gender ($n_{subj} = 847$).}
+\centering
+\begin{tabular}[t]{>{}rcccc}
+\toprule
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{4}{c}{\textbf{Attachment Style}} \\
+\cmidrule(l{3pt}r{3pt}){2-5}
+\textbf{Gender} & \textbf{Secure} & \textbf{Anxious} & \textbf{Avoidant} & \textbf{Fearful}\\
+\midrule
+\textbf{Females} & 132 (16\%) & 131 (15\%) & 111 (13\%) & 55 ( 6\%)\\
+\textbf{Males} & 99 (12\%) & 155 (18\%) & 119 (14\%) & 45 ( 5\%)\\
+\textbf{Total} & 231 (27\%) & 286 (34\%) & 230 (27\%) & 100 (12\%)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Compared to the overall average values of anxiety and avoidance, we can observe that:
+
+\begin{itemize}
+\tightlist
+\item
+  \emph{Secure} children have lower levels of anxiety and avoidance
+\item
+  \emph{Anxious} children have higher levels of anxiety and about the average levels of avoidance
+\item
+  \emph{Avoidant} children have lower levels of anxiety and higher levels of avoidance
+\item
+  \emph{Fearful} children have higher levels of anxiety and avoidance
+\end{itemize}
+
+These results reflect the traditional definition of the four attachment styles.
+Moreover, attachment styles frequencies are in lines with general results in the literature {[}TODO: add reference values{]}.
+
+\hypertarget{mclust-check}{%
+\subsubsection*{Mclust Check}\label{mclust-check}}
+\addcontentsline{toc}{subsubsection}{Mclust Check}
+
+To evaluate if 4 cluster is an appropriate choice, we compare the BIC values of different model-based clustering options.
+To do that we use the function \texttt{mclustBIC()} from the \texttt{mclust} R-package \citep{scruccaMclustClusteringClassification2016}.
+BIC values of the best three model-based clustering are reported below and overall results are presented in Figure\textasciitilde\ref{fig:plot-mclust-mother}.
+See \texttt{?mclustBIC()} help page for further information.
+
+\begin{verbatim}
+##   # Best model-based clustering for mother attachment
+## Best BIC values:
+##              EEV,6       EEV,7      EEV,8
+## BIC      -23978.93 -24842.2437 -25039.952
+## BIC diff      0.00   -863.3168  -1061.025
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-mclust-mother-1}
+
+}
+
+\caption{BIC values of different model-based clustering options. See '?mclustBIC()' help page for further information.}\label{fig:plot-mclust-mother}
+\end{figure}
+
+Results indicate the possible presence of a larger number of clusters.
+However, considering only 4 clusters seems to us the most reasonable choice.
+This is in line with attachment theory and general results in the literature.
+The important thing is hat no smaller number of clusters provided better results than the division in 4 clusters.
+
+\hypertarget{father-cluster-analysis}{%
+\subsection{Father Cluster Analysis}\label{father-cluster-analysis}}
+
+Regarding father attachment, 4 groups are selected from the cluster analysis results (see Figure\textasciitilde\ref{fig:plot-cluster-father}).
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-cluster-father-1}
+
+}
+
+\caption{Father attachment cluster dendrogram ($n_{subj} = 847$).}\label{fig:plot-cluster-father}
+\end{figure}
+
+In Figure\textasciitilde\ref{fig:plot-scores-father}, Anxiety (``\emph{Anx}'') and Avoidance (``\emph{Av}'') scores are presented according to father attachment styles.
+The frequencies of father attachment styles according to gender are reported in Table\textasciitilde{}\ref{tab:table-cluster-father}.
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-scores-father-1}
+
+}
+
+\caption{Anxiety (“Anx”) and Avoidance (“Av”) scores according to father attachment styles. Dashed lines represents overall average values ($n_{subj} = 847$).}\label{fig:plot-scores-father}
+\end{figure}
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-cluster-father}Father attachment styles by gender ($n_{subj} = 847$).}
+\centering
+\begin{tabular}[t]{>{}rcccc}
+\toprule
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{4}{c}{\textbf{Attachment Style}} \\
+\cmidrule(l{3pt}r{3pt}){2-5}
+\textbf{Gender} & \textbf{Secure} & \textbf{Anxious} & \textbf{Avoidant} & \textbf{Fearful}\\
+\midrule
+\textbf{Females} & 99 (12\%) & 104 (12\%) & 163 (19\%) & 63 ( 7\%)\\
+\textbf{Males} & 107 (13\%) & 126 (15\%) & 148 (17\%) & 37 ( 4\%)\\
+\textbf{Total} & 206 (24\%) & 230 (27\%) & 311 (37\%) & 100 (12\%)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Compared to the overall average values of anxiety and avoidance, we can observe that:
+
+\begin{itemize}
+\tightlist
+\item
+  \emph{Secure} children have lower levels of anxiety and avoidance
+\item
+  \emph{Anxious} children have lower levels of anxiety and avoidance
+\item
+  \emph{Avoidant} children have lower levels of anxiety and higher levels of avoidance
+\item
+  \emph{Fearful} children have higher levels of anxiety and avoidance
+\end{itemize}
+
+These results are no as good as in the mother attachment classification, but they are still reasonable.
+Moreover, attachment styles frequencies are close to the general results in the literature {[}TODO: add reference values{]}.
+
+\hypertarget{mclust-check-1}{%
+\subsubsection*{Mclust Check}\label{mclust-check-1}}
+\addcontentsline{toc}{subsubsection}{Mclust Check}
+
+To evaluate if 4 cluster is an appropriate choice, we compare the BIC values of different model-based clustering options as before.
+BIC values of the best three model-based clustering are reported below and overall results are presented in Figure\textasciitilde\ref{fig:plot-mclust-father}.
+
+\begin{verbatim}
+##   # Best model-based clustering for father attachment
+## Best BIC values:
+##              EEV,9       EEV,8      EEV,5
+## BIC      -25351.43 -25790.9130 -25905.197
+## BIC diff      0.00   -439.4807   -553.765
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-mclust-father-1}
+
+}
+
+\caption{BIC values of different model-based clustering options. See '?mclustBIC()' help page for further information.}\label{fig:plot-mclust-father}
+\end{figure}
+
+As for the mother, results indicate the possible presence of a larger number of clusters. However, considering only 4 clusters seems to us the most reasonable choice for the same reasons as before.
+
+\hypertarget{mother-and-father}{%
+\subsection{Mother and Father}\label{mother-and-father}}
+
+The frequencies of mother attachment and father attachment styles are reported in Table\textasciitilde\ref{tab:table-cluster-mother-father}.
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-cluster-mother-father}Mother attachment and father attachemtn styles ($n_{subj} = 847$).}
+\centering
+\begin{tabular}[t]{>{}rcccc}
+\toprule
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{4}{c}{\textbf{Father Attachment}} \\
+\cmidrule(l{3pt}r{3pt}){2-5}
+\textbf{Mother Attachment} & \textbf{Secure} & \textbf{Anxious} & \textbf{Avoidant} & \textbf{Fearful}\\
+\midrule
+\textbf{Secure} & 125 (15\%) & 49 ( 6\%) & 49 ( 6\%) & 8 (1\%)\\
+\textbf{Anxious} & 51 ( 6\%) & 100 (12\%) & 98 (12\%) & 37 (4\%)\\
+\textbf{Avoidant} & 25 ( 3\%) & 67 ( 8\%) & 126 (15\%) & 12 (1\%)\\
+\textbf{Fearful} & 5 ( 1\%) & 14 ( 2\%) & 38 ( 4\%) & 43 (5\%)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+We can observe how values on the diagonal (same attachment styles towards both parents) tends to be larger than others.
+
+\hypertarget{children-outcomes}{%
+\section{Children Outcomes}\label{children-outcomes}}
+
+Children's social-emotional development was measured using the Strength \& Difficulties Questionnaire (SDQ; {[}TODO add references{]}) completed by the teachers.
+Separate scores for externalizing and internalizing problems were obtained as sum of the questionnaire items.
+
+\hypertarget{externalizing-problems}{%
+\subsection{Externalizing Problems}\label{externalizing-problems}}
+
+Participants externalizing problems mean is 3.35 (SD = 3.91).
+The participants externalizing problems summary statistics are reported below and the distribution is presented in Figure\textasciitilde\ref{fig:plot-externalizing-dist}.
+
+\begin{verbatim}
+##   # Externalizing problems summary statistics
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
+##   0.000   0.000   2.000   3.349   6.000  18.000
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-externalizing-dist-1}
+
+}
+
+\caption{Participants externalizing problems distribution ($n_{subj} = 847$)}\label{fig:plot-externalizing-dist}
+\end{figure}
+
+Overall, externalizing problems are low.
+This is expected as the sample is not a clinical sample.
+Externalizing problems according to attachment styles are reported in Table\textasciitilde\ref{tab:table-cluster-ext}.
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-cluster-ext}Externalizing problems according to attachment styles ($n_{subj} = 847$).}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{>{}rcccccccc}
+\toprule
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{8}{c}{\textbf{Father Attachment}} \\
+\cmidrule(l{3pt}r{3pt}){2-9}
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{2}{c}{\textbf{Secure}} & \multicolumn{2}{c}{\textbf{Anxious}} & \multicolumn{2}{c}{\textbf{Avoidant}} & \multicolumn{2}{c}{\textbf{Fearful}} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
+\textbf{Mother Attachemnt} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median}\\
+\midrule
+\textbf{Secure} & 2.63 (3.57) & 1.0 & 3.45 (4.48) & 2.0 & 1.61 (2.13) & 1.0 & 2.88 (3.44) & 2.0\\
+\textbf{Anxious} & 3.69 (4.07) & 2.0 & 3.01 (3.61) & 2.0 & 3.32 (4.12) & 2.0 & 4.05 (3.61) & 3.0\\
+\textbf{Avoidant} & 2.84 (3.34) & 1.0 & 3.31 (3.65) & 2.0 & 3.71 (4.19) & 2.0 & 3.75 (4.81) & 1.0\\
+\textbf{Fearful} & 7.60 (4.04) & 8.0 & 4.64 (3.84) & 4.5 & 4.76 (4.67) & 3.0 & 4.26 (4.07) & 4.0\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+\hypertarget{internalizing-problems}{%
+\subsection{Internalizing Problems}\label{internalizing-problems}}
+
+Participants internalizing problems mean is 2.96 (SD = 3.14).
+The participants internalizing problems summary statistics are reported below and the distribution is presented in Figure\textasciitilde\ref{fig:plot-internalizing-dist}.
+
+\begin{verbatim}
+##   #
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
+##   0.000   0.000   2.000   2.955   4.000  18.000
+\end{verbatim}
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-internalizing-dist-1}
+
+}
+
+\caption{Participants internalizing problems distribution ($n_{subj} = 847$)}\label{fig:plot-internalizing-dist}
+\end{figure}
+
+Overall, internalizing problems are low.
+Again, this is expected as the sample is not a clinical sample.
+Internalizing problems according to attachment styles are reported in Table\textasciitilde{}\ref(tab:table-cluster-ext).
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-cluster-int}Internalizing problems according to attachment styles ($n_{subj} = 847$).}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{>{}rcccccccc}
+\toprule
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{8}{c}{\textbf{Father Attachment}} \\
+\cmidrule(l{3pt}r{3pt}){2-9}
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{2}{c}{\textbf{Secure}} & \multicolumn{2}{c}{\textbf{Anxious}} & \multicolumn{2}{c}{\textbf{Avoidant}} & \multicolumn{2}{c}{\textbf{Fearful}} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
+\textbf{Mother Attachemnt} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median}\\
+\midrule
+\textbf{Secure} & 2.29 (2.64) & 1.0 & 2.63 (2.75) & 2.0 & 2.67 (2.75) & 3.0 & 3.62 (3.46) & 3.0\\
+\textbf{Anxious} & 3.29 (3.48) & 2.0 & 3.15 (3.09) & 2.0 & 3.28 (3.72) & 2.0 & 3.11 (3.81) & 2.0\\
+\textbf{Avoidant} & 1.88 (2.28) & 1.0 & 2.99 (3.22) & 2.0 & 2.65 (2.86) & 2.0 & 4.08 (3.78) & 3.5\\
+\textbf{Fearful} & 4.40 (3.65) & 4.0 & 2.07 (1.69) & 2.0 & 3.68 (3.68) & 3.0 & 4.37 (3.12) & 4.0\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+\hypertarget{part-externalizing-problems}{%
+\part*{Externalizing Problems}\label{part-externalizing-problems}}
+\addcontentsline{toc}{part}{Externalizing Problems}
+
+\hypertarget{model-choice-ext}{%
+\chapter{Models Family Choice}\label{model-choice-ext}}
+
+In this chapter, we discuss the appropriate models family to to take into account data characteristics.
+
+\hypertarget{negative-binomial}{%
+\section{Negative Binomial}\label{negative-binomial}}
+
+Externalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20.
+Thus, we should use appropriate discrete distribution such as the \emph{Poisson} distribution or the \emph{Negative Binomial}.
+In the Poisson distribution mean and variance are defined according to the same parameter \(\lambda\).
+On the contrary, Negative Binomial has an extra parameter to adjust the variance allowing more flexibility.
+Considering data distribution (see Figure\textasciitilde\ref{fig:plot-externalizing-dist}), we can observe that data have high dispersion with a long right tail.
+In this case, Poisson distribution would be a poor choice and we prefer Negative Binomial instead.
+
+Again, considering data distribution (see Figure\textasciitilde\ref{fig:plot-externalizing-dist}), we can observe an high peak of values at zero.
+Remember that this is not a clinical sample, thus it is expected that children majority has no problems or really few problem.
+We could question ourselves, however, whether a \emph{Zero-Inflated} model may be appropriate
+
+\hypertarget{zero-inflated-negative-binomial}{%
+\section{Zero Inflated Negative Binomial}\label{zero-inflated-negative-binomial}}
+
+To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model.
+We consider in the model the role of gender and the interaction between mother attachment and father attachment.
+Moreover, we consider the children's classroom ID as a random effect to account for teachers' different ability to evaluate children's problems.
+Using R formula syntax, we have
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# model formula}
+\NormalTok{externalizing\_sum }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{*}\NormalTok{ father }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+\end{Highlighting}
+\end{Shaded}
+
+The model is fitted using the function \texttt{glmmTMB()} from the \texttt{glmmTMB} R-package \citep{brooksGlmmTMBBalancesSpeed2017}.
+Next, we compare the number of observed zero and expected zeros using an adapted version of the function \texttt{check\_zeroinflation()} from the R-package \texttt{performance} \citep{ludeckePerformancePackageAssessment2021} that solves a small bug (see issue \url{https://github.com/easystats/performance/issues/367}).
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{my\_check\_zeroinflation}\NormalTok{(fit\_ext\_nb)}
+\DocumentationTok{\#\# \# Check for zero{-}inflation}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\#    Observed zeros: 276}
+\DocumentationTok{\#\#   Predicted zeros: 245}
+\DocumentationTok{\#\#             Ratio: 0.89}
+\DocumentationTok{\#\# Model is underfitting zeros (probable zero{-}inflation).}
+\end{Highlighting}
+\end{Shaded}
+
+Results indicate that the model is slightly under-fitting the number of zeros.
+Now, we can try to fit a \emph{Zero Inflated Negative Binomial} (ZINB) model and compare the performance of the two models.
+ZINB models are defined as
+\[
+y_{ij} \sim ZINB(p_{ij}, \mu_{ij}, \phi),
+\]
+where \(p_{ij}\) is the probability of an observation \(y_{ij}\) being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and \(1-p_{ij}\) indicates the probability of a given observation \(y_{ij}\) being generated form a Negative Binomial distribution with mean \(\mu_{ij}\) and variance \(\sigma_{ij}^2 = \mu_{ij} + \frac{\mu_{ij}^2}{\phi}\).
+Moreover, we have that
+\[
+p_{ij} = \text{logit}^{-1}(X_i^T\beta_p+ Z_j^Tu_p),\\
+\mu_{ij} = \text{exp}(X_i^T\beta_{\mu}+ Z_j^Tu_{\mu}).
+\]
+That is, both \(p\) and \(\mu\) are modelled separately according to (possibly) different variables.
+In our case, we consider only the role of gender for \(p\) (i.e., the probability of having externalizing problems depends on gender), whereas for \(\mu\) the consider also the interaction between mother attachment and father attachment.
+In both cases, we consider the children's classroom ID as a random effect (teachers may differ in the ability to detect children's problems and quantify them).
+Using R formula syntax, we have
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# formula for p}
+\NormalTok{p }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# formula for mu}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{*}\NormalTok{ father }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+\end{Highlighting}
+\end{Shaded}
+
+The ZINB model is fitted using the function \texttt{zeroinfl()} from the \texttt{pscl} R-package \citep{zeileisRegressionModelsCount2008}.
+To compare the ZINB model and the Negative Binomial model we conduct an analysis of \emph{Deviance}.
+Note that, in the case of generalized linear models (GLM), the deviance is the corresponding of the residual variance used in the traditional ANOVA in the case of linear models.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{anova}\NormalTok{(fit\_ext\_nb, fit\_ext\_zinb)}
+\DocumentationTok{\#\# Data: data\_cluster}
+\DocumentationTok{\#\# Models:}
+\DocumentationTok{\#\# fit\_ext\_nb: externalizing\_sum \textasciitilde{} gender + mother * father + (1 | ID\_class), zi=\textasciitilde{}0, disp=\textasciitilde{}1}
+\DocumentationTok{\#\# fit\_ext\_zinb: externalizing\_sum \textasciitilde{} gender + mother * father + (1 | ID\_class), zi=\textasciitilde{}gender + (1 | ID\_class), disp=\textasciitilde{}1}
+\DocumentationTok{\#\#              Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(\textgreater{}Chisq)    }
+\DocumentationTok{\#\# fit\_ext\_nb   19 3910.1 4000.2 {-}1936.1   3872.1                             }
+\DocumentationTok{\#\# fit\_ext\_zinb 22 3867.6 3971.9 {-}1911.8   3823.6 48.556      3  1.622e{-}10 ***}
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\end{Highlighting}
+\end{Shaded}
+
+Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses, we decide to use ZINB models.
+
+\hypertarget{nhst-ext}{%
+\chapter{NHST}\label{nhst-ext}}
+
+Following the traditional NHST approach, we consider the model previously defined that includes all effects of interest.
+That is the gender effect and the interaction between mother attachment and father attachment.
+Subsequently, we can run an analysis of deviance to evaluate the significance of the predictors using the function \texttt{Anova()} from the R-package \texttt{car} \citep{foxCompanionAppliedRegression2019}.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{car}\SpecialCharTok{::}\FunctionTok{Anova}\NormalTok{(fit\_ext\_zinb)}
+\DocumentationTok{\#\# Analysis of Deviance Table (Type II Wald chisquare tests)}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Response: externalizing\_sum}
+\DocumentationTok{\#\#                 Chisq Df Pr(\textgreater{}Chisq)    }
+\DocumentationTok{\#\# gender        15.2947  1  9.197e{-}05 ***}
+\DocumentationTok{\#\# mother        15.6195  3   0.001357 ** }
+\DocumentationTok{\#\# father         1.1006  3   0.776938    }
+\DocumentationTok{\#\# mother:father  8.9096  9   0.445657    }
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\end{Highlighting}
+\end{Shaded}
+
+Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are not significant. The model summary is reported below.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{summary}\NormalTok{(fit\_ext\_zinb)}
+\DocumentationTok{\#\#  Family: nbinom2  ( log )}
+\DocumentationTok{\#\# Formula:          externalizing\_sum \textasciitilde{} gender + mother * father + (1 | ID\_class)}
+\DocumentationTok{\#\# Zero inflation:                     \textasciitilde{}gender + (1 | ID\_class)}
+\DocumentationTok{\#\# Data: data\_cluster}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\#      AIC      BIC   logLik deviance df.resid }
+\DocumentationTok{\#\#   3867.6   3971.9  {-}1911.8   3823.6      825 }
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Random effects:}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Conditional model:}
+\DocumentationTok{\#\#  Groups   Name        Variance Std.Dev.}
+\DocumentationTok{\#\#  ID\_class (Intercept) 0.08132  0.2852  }
+\DocumentationTok{\#\# Number of obs: 847, groups:  ID\_class, 50}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Zero{-}inflation model:}
+\DocumentationTok{\#\#  Groups   Name        Variance Std.Dev.}
+\DocumentationTok{\#\#  ID\_class (Intercept) 0.7669   0.8757  }
+\DocumentationTok{\#\# Number of obs: 847, groups:  ID\_class, 50}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Dispersion parameter for nbinom2 family (): 1.86 }
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Conditional model:}
+\DocumentationTok{\#\#                               Estimate Std. Error z value Pr(\textgreater{}|z|)    }
+\DocumentationTok{\#\# (Intercept)                    1.01996    0.12814   7.960 1.72e{-}15 ***}
+\DocumentationTok{\#\# genderM                        0.31556    0.08069   3.911 9.20e{-}05 ***}
+\DocumentationTok{\#\# motherAnxious                  0.30735    0.18664   1.647   0.0996 .  }
+\DocumentationTok{\#\# motherAvoidant                 0.14496    0.25509   0.568   0.5699    }
+\DocumentationTok{\#\# motherFearful                  0.62950    0.39550   1.592   0.1115    }
+\DocumentationTok{\#\# fatherAnxious                  0.21543    0.19156   1.125   0.2607    }
+\DocumentationTok{\#\# fatherAvoidant                {-}0.46555    0.21138  {-}2.202   0.0276 *  }
+\DocumentationTok{\#\# fatherFearful                  0.07138    0.41737   0.171   0.8642    }
+\DocumentationTok{\#\# motherAnxious:fatherAnxious   {-}0.38346    0.26981  {-}1.421   0.1553    }
+\DocumentationTok{\#\# motherAvoidant:fatherAnxious  {-}0.09675    0.33041  {-}0.293   0.7697    }
+\DocumentationTok{\#\# motherFearful:fatherAnxious   {-}0.40811    0.49348  {-}0.827   0.4082    }
+\DocumentationTok{\#\# motherAnxious:fatherAvoidant   0.34281    0.28290   1.212   0.2256    }
+\DocumentationTok{\#\# motherAvoidant:fatherAvoidant  0.63111    0.32765   1.926   0.0541 .  }
+\DocumentationTok{\#\# motherFearful:fatherAvoidant   0.34025    0.46490   0.732   0.4642    }
+\DocumentationTok{\#\# motherAnxious:fatherFearful   {-}0.04630    0.47448  {-}0.098   0.9223    }
+\DocumentationTok{\#\# motherAvoidant:fatherFearful   0.11794    0.56413   0.209   0.8344    }
+\DocumentationTok{\#\# motherFearful:fatherFearful   {-}0.20316    0.58602  {-}0.347   0.7288    }
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Zero{-}inflation model:}
+\DocumentationTok{\#\#             Estimate Std. Error z value Pr(\textgreater{}|z|)    }
+\DocumentationTok{\#\# (Intercept)  {-}1.1239     0.2417   {-}4.65 3.32e{-}06 ***}
+\DocumentationTok{\#\# genderM      {-}0.7145     0.2516   {-}2.84  0.00451 ** }
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\end{Highlighting}
+\end{Shaded}
+
+To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure\textasciitilde\ref{fig:plot-nhst-effects-ext}.
+Not that the marginal predicted values for gender are averaged over mother and father attachment effects.
+Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-nhst-effects-ext-1}
+
+}
+
+\caption{Marginal predicted values according to gender and mother attachment. Values are averaged over the other effects ($n_{subj} = 847$).}\label{fig:plot-nhst-effects-ext}
+\end{figure}
+
+Post-hoc tests are run to evaluate differences between mother attachment styles.
+To do that we use the \texttt{contrast()} function from the \texttt{emmeans} R-package, considering pairwise comparisons and adjusting \emph{p}-values according to multivariate \emph{t}-distribution.
+This approach is less restrictive than the traditional \emph{``Bonferroni''} method, as it determines the adjustment according to a multivariate \emph{t}-distribution with the same covariance structure as the estimates.
+Results are reported below,
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_ext\_zinb, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
+                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
+\DocumentationTok{\#\# }\AlertTok{NOTE}\DocumentationTok{: Results may be misleading due to involvement in interactions}
+\DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1719}
+\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.162 825  {-}1.902  0.2227}
+\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5617 0.178 825  {-}3.149  0.0092}
+\DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0224 0.124 825  {-}0.181  0.9978}
+\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2761 0.146 825  {-}1.885  0.2300}
+\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2537 0.167 825  {-}1.522  0.4180}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Results are averaged over the levels of: gender, father }
+\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
+\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
+\end{Highlighting}
+\end{Shaded}
+
+Overall, results indicate that Males have more externalizing problems than Females and, regarding mother attachment, Fearful children have more problems than Secure children.
+
+To evaluate the fit of the model to the data, we used \(R^2\).
+In the case of generalized mixed-effects models, however, there are several definitions of \(R^2\).
+We computed the \emph{Marginal} \(R^2\) and the \emph{Conditional} \(R^2\) as suggested by \citet{nakagawaCoefficientDeterminationR22017}.
+\emph{Marginal} \(R^2\) is concerned with the variance explained by fixed factors of the model, and \emph{Conditional} \(R^2\) is concerned with the variance explained by both fixed and random factors of the model.
+To do that we use the function \texttt{performance::r2()}.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{performance}\SpecialCharTok{::}\FunctionTok{r2}\NormalTok{(fit\_ext\_zinb)}
+\DocumentationTok{\#\# Warning: mu of 4.2 is too close to zero, estimate of random effect variances may be}
+\DocumentationTok{\#\#   unreliable.}
+\DocumentationTok{\#\# \# R2 for Mixed Models}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\#   Conditional R2: 0.191}
+\DocumentationTok{\#\#      Marginal R2: 0.091}
+\end{Highlighting}
+\end{Shaded}
+
+We can see that the actual variance explained by fixed effects is almost 10\%, not bad for psychology.
+
+\hypertarget{conclusions}{%
+\subsubsection*{Conclusions}\label{conclusions}}
+\addcontentsline{toc}{subsubsection}{Conclusions}
+
+Considering attachment theoretical perspectives, results indicate only the role of mother attachment.
+Note, however, that traditional NHST does not allow us to evaluate evidence in favour of a hypothesis.
+Moreover, we actually have not tested our hypotheses but only the catch-all null hypothesis that \emph{``nothing is going on''}.
+
+\hypertarget{model-comparison-ext}{%
+\chapter{Model Comparison}\label{model-comparison-ext}}
+
+Model comparison allows us to compare multiple hypotheses and identify which is the most supported by the data \citep{mcelreathStatisticalRethinkingBayesian2020}.
+First, we need to formalize models according to our hypotheses.
+Subsequently, we can evaluate which is the most supported model among those considered according to the data using the AIC and BIC \citep{wagenmakersAICModelSelection2004, akaike1973a, schwarzEstimatingDimensionModel1978}.
+
+\hypertarget{formalize-models}{%
+\section{Formalize Models}\label{formalize-models}}
+
+Following the same reasons as before (see Section\textasciitilde\ref{model-choice-ext}), we consider Zero Inflated Negative Binomial Mixed-Effects models.
+Again, we consider only the role of gender as a fixed effect and children's classroom ID as a random effect for \(p\).
+Whereas, considering \(\mu\), we define four different models to take into account the different theoretical perspectives:
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{fit\_ext\_zero}: we consider only the effect of gender. This model assumes that attachment plays no role.
+\item
+  \texttt{fit\_ext\_mother}: we consider the additive effects of gender and mother attachment. This model supports the idea that only mother attachment is important (\textbf{Monotropy Theory}).
+\item
+  \texttt{fit\_ext\_additive}: we consider the additive effects of gender, mother attachment, and father attachment.
+This model supports the idea that both mother attachment and father attachment are important, but not their interaction (\textbf{Hierarchy Theory} or \textbf{Independence Theory}).
+\item
+  \texttt{fit\_ext\_inter}: we consider the additive effects of gender and the interaction between mother attachment and father attachment.
+This model supports the idea that the interaction between mother attachment and father attachment is important (\textbf{Integration Theory}).
+\end{itemize}
+
+Moreover, in all models, we include children's classroom ID as a random effect to take into account teachers' different ability to evaluate children's problems. Using R formula syntax, we have
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# formula for p (same for all models)}
+\NormalTok{p }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# formula for mu}
+
+\CommentTok{\# fit\_ext\_zero}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# fit\_ext\_mother}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# fit\_ext\_additive}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{+}\NormalTok{ father }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# fit\_ext\_inter}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{*}\NormalTok{ father }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{aic-and-bic-results}{%
+\section{AIC and BIC Results}\label{aic-and-bic-results}}
+
+After estimating the models, the AIC and BIC values together with their relative weights are computed. Results are reported in Table\textasciitilde\ref{tab:table-AIC-BIC-weights-ext}.
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-AIC-BIC-weights-ext}Model comparison externalizing problems ($n_{subj} = 847$).}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{rccc>{\centering\arraybackslash}m{1cm}cc>{\centering\arraybackslash}m{1cm}}
+\toprule
+\textbf{Model} & \textbf{Df} & \textbf{AIC} & \textbf{AIC$_{weights}$} & \textbf{ } & \textbf{BIC} & \textbf{BIC$_{weights}$} & \textbf{ }\\
+\midrule
+fit-ext-zero & 6 & 3865.1 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_AIC_ext_zero.png} & 3898.3 & 0.78 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BIC_ext_zero.png}\\
+fit-ext-mother & 9 & 3853.4 & 0.92 & \includegraphics[width=0.33in, height=0.33in]{images/ball_AIC_ext_mother.png} & 3900.8 & 0.22 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BIC_ext_mother.png}\\
+fit-ext-additive & 12 & 3858.4 & 0.08 & \includegraphics[width=0.33in, height=0.33in]{images/ball_AIC_ext_additive.png} & 3920.0 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BIC_ext_additive.png}\\
+fit-ext-inter & 21 & 3867.6 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_AIC_ext_inter.png} & 3971.9 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BIC_ext_inter.png}\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+According to AIC, the most likely model is \texttt{fit\_ext\_mother} (92\%) and the second most likely model is \texttt{fit\_ext\_additive} (8\%) given the data and the set of models considered.
+According to BIC, instead, the most likely model is \texttt{fit\_ext\_zero} (78\%) and the second most likely model is \texttt{fit\_ext\_mother} (22\%) given the data and the set of models considered.
+
+To interpret these results, note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
+As pointed by \citet{kuhaAICBICComparisons2004}, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
+We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.
+
+\hypertarget{selected-model}{%
+\section{Selected Model}\label{selected-model}}
+
+Considering model \texttt{fit\_ext\_mother}, we can run an analysis of deviance to evaluate the significance of the predictors.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{car}\SpecialCharTok{::}\FunctionTok{Anova}\NormalTok{(fit\_ext\_mother)}
+\DocumentationTok{\#\# Analysis of Deviance Table (Type II Wald chisquare tests)}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Response: externalizing\_sum}
+\DocumentationTok{\#\#         Chisq Df Pr(\textgreater{}Chisq)    }
+\DocumentationTok{\#\# gender 17.732  1  2.544e{-}05 ***}
+\DocumentationTok{\#\# mother 17.398  3  0.0005851 ***}
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\end{Highlighting}
+\end{Shaded}
+
+Results confirm a statistically significant effect of gender and mother attachment. The model summary is reported below.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{summary}\NormalTok{(fit\_ext\_mother)}
+\DocumentationTok{\#\#  Family: nbinom2  ( log )}
+\DocumentationTok{\#\# Formula:          externalizing\_sum \textasciitilde{} gender + mother + (1 | ID\_class)}
+\DocumentationTok{\#\# Zero inflation:                     \textasciitilde{}gender + (1 | ID\_class)}
+\DocumentationTok{\#\# Data: data\_cluster}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\#      AIC      BIC   logLik deviance df.resid }
+\DocumentationTok{\#\#   3853.4   3900.8  {-}1916.7   3833.4      837 }
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Random effects:}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Conditional model:}
+\DocumentationTok{\#\#  Groups   Name        Variance Std.Dev.}
+\DocumentationTok{\#\#  ID\_class (Intercept) 0.07747  0.2783  }
+\DocumentationTok{\#\# Number of obs: 847, groups:  ID\_class, 50}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Zero{-}inflation model:}
+\DocumentationTok{\#\#  Groups   Name        Variance Std.Dev.}
+\DocumentationTok{\#\#  ID\_class (Intercept) 0.766    0.8752  }
+\DocumentationTok{\#\# Number of obs: 847, groups:  ID\_class, 50}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Dispersion parameter for nbinom2 family (): 1.81 }
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Conditional model:}
+\DocumentationTok{\#\#                Estimate Std. Error z value Pr(\textgreater{}|z|)    }
+\DocumentationTok{\#\# (Intercept)     0.98649    0.10770   9.160  \textless{} 2e{-}16 ***}
+\DocumentationTok{\#\# genderM         0.33533    0.07964   4.211 2.54e{-}05 ***}
+\DocumentationTok{\#\# motherAnxious   0.24321    0.10338   2.353  0.01864 *  }
+\DocumentationTok{\#\# motherAvoidant  0.30803    0.10910   2.823  0.00475 ** }
+\DocumentationTok{\#\# motherFearful   0.52680    0.13135   4.011 6.05e{-}05 ***}
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Zero{-}inflation model:}
+\DocumentationTok{\#\#             Estimate Std. Error z value Pr(\textgreater{}|z|)    }
+\DocumentationTok{\#\# (Intercept)  {-}1.1211     0.2432  {-}4.609 4.05e{-}06 ***}
+\DocumentationTok{\#\# genderM      {-}0.6990     0.2491  {-}2.807    0.005 ** }
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\end{Highlighting}
+\end{Shaded}
+
+To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure\textasciitilde\ref{fig:plot-comparison-effects-ext}.
+Not that the marginal predicted values for gender are averaged over mother attachment.
+Whereas, the marginal predicted values for mother attachment are averaged over gender.
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-comparison-effects-ext-1}
+
+}
+
+\caption{Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$).}\label{fig:plot-comparison-effects-ext}
+\end{figure}
+
+Post-hoc tests are run to evaluate differences between mother attachment styles, considering pairwise comparisons and adjusting \emph{p}-values according to multivariate \emph{t}-distribution.
+Results are reported below,
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_ext\_mother, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
+                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
+\DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2432 0.1034 837  {-}2.353  0.0858}
+\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0244}
+\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0004}
+\DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0648 0.0981 837  {-}0.661  0.9107}
+\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0902}
+\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2188 0.1276 837  {-}1.714  0.3135}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Results are averaged over the levels of: gender }
+\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
+\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
+\end{Highlighting}
+\end{Shaded}
+
+Overall, results indicate that Males have more externalizing problems than Females.
+Regarding mother attachment, Fearful and Avoidant children have more problems than Secure children.
+Moreover, also the difference between Anxious and Secure children and the difference between Anxious and Fearful children have a low (but not statistically significant) \emph{p}-value.
+
+To evaluate the fit of the model to the data, we computed the \emph{Marginal} \(R^2\) and the \emph{Conditional} \(R^2\).
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{performance}\SpecialCharTok{::}\FunctionTok{r2}\NormalTok{(fit\_ext\_mother)}
+\DocumentationTok{\#\# Warning: mu of 4.2 is too close to zero, estimate of random effect variances may be}
+\DocumentationTok{\#\#   unreliable.}
+\DocumentationTok{\#\# \# R2 for Mixed Models}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\#   Conditional R2: 0.168}
+\DocumentationTok{\#\#      Marginal R2: 0.071}
+\end{Highlighting}
+\end{Shaded}
+
+We can see that the actual variance explained by fixed effects is around 7\%, not bad for psychology.
+
+\hypertarget{conclusions-1}{%
+\subsubsection*{Conclusions}\label{conclusions-1}}
+\addcontentsline{toc}{subsubsection}{Conclusions}
+
+Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the \textbf{Monotropy Theory}.
+Note, however, that the compared models contain no information regarding the expected direction of the effects but we only include/exclude predictors.
+
+\hypertarget{BF-ext}{%
+\chapter{Bayes Factor}\label{BF-ext}}
+
+To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes Factor with encompassing prior approach.
+See the main article for a detailed introduction to this approach {[}TODO: add link article{]}.
+
+First, we define the encompassing model.
+Subsequently, we obtain the hypotheses matrices according to the informative hypotheses.
+Next, we compute the Bayes Factor and, finally, we describe the selected model.
+
+\hypertarget{encompassing-model}{%
+\section{Encompassing Model}\label{encompassing-model}}
+
+We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects model to take into account the characteristics of the dependent variable and its distribution (see Section\textasciitilde\ref{model-choice-ext}).
+Again, we consider only the role of gender as a fixed effect and children's classroom ID as a random effect for \(p\).
+Whereas, regarding \(\mu\), we consider the interaction between mother and father attachment together with gender as fixed effects and children's classroom ID as a random effect.
+In the R formula syntax, we have
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# formula for p}
+\NormalTok{p }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# formula for mu}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{*}\NormalTok{ father }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{prior-choiche}{%
+\subsection{Prior Choiche}\label{prior-choiche}}
+
+The prior choice is important for the parameters involved in the equality and inequality constraints.
+In our case, the parameters of interest (i.e., those related to mother and father attachment interaction) are unbounded.
+Thus, we can simply specify as prior a normal distribution with mean 0 and a given standard deviation.
+Considering the standard deviation, however, we have to choose a value so that the resulting prior is non-informative but without being excessively diffuse.
+
+We can evaluate the consequences of different values choice considering the resulting prior predictions.
+To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest.
+Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1 because \(exp(1) \approx 2.7\) that is close to the externalizing problems sample mean 3.35.
+In Table\textasciitilde\ref{tab:table-prior-predict}, summary information about prior predictions for different standard deviation values is reported.
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-prior-predict}Prior prediction acording to different prior settings assuming $exp(1)$ as intercept value.}
+\centering
+\begin{tabular}[t]{rccccc}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Predicted Problems} \\
+\cmidrule(l{3pt}r{3pt}){2-6}
+Prior & $-1$ SD & $-.5$ SD & $+0$ SD & $+ .5$ SD & $+ 1$ SD\\
+\midrule
+$\mathcal{N}(0, 0.5)$ & 1.6 & 2.1 & 2.7 & 3.5 & 4.5\\
+$\mathcal{N}(0, 1)$ & 1.0 & 1.6 & 2.7 & 4.5 & 7.4\\
+$\mathcal{N}(0, 3)$ & 0.1 & 0.6 & 2.7 & 12.2 & 54.6\\
+$\mathcal{N}(0, 5)$ & 0.0 & 0.2 & 2.7 & 33.1 & 403.4\\
+$\mathcal{N}(0, 10)$ & 0.0 & 0.0 & 2.7 & 403.4 & 59874.1\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Considering that externalizing problems are bounded between 0 and 20, a reasonable prior is \(\mathcal{N}(0,3)\).
+as prior predicted values cover all possible values without including excessively large values.
+More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values.
+The influence of prior specification will be subsequently evaluated in a prior sensitivity analysis.
+
+Regarding the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) \texttt{brms} default priors are maintained. The resulting prior settings are
+
+\begin{verbatim}
+##                   prior     class                          coef    group resp dpar nlpar bound       source
+##            normal(0, 3)         b                                                                      user
+##            normal(0, 3)         b                 fatherAnxious                                (vectorized)
+##            normal(0, 3)         b                fatherAvoidant                                (vectorized)
+##            normal(0, 3)         b                 fatherFearful                                (vectorized)
+##            normal(0, 3)         b                       genderM                                (vectorized)
+##            normal(0, 3)         b                 motherAnxious                                (vectorized)
+##            normal(0, 3)         b   motherAnxious:fatherAnxious                                (vectorized)
+##            normal(0, 3)         b  motherAnxious:fatherAvoidant                                (vectorized)
+##            normal(0, 3)         b   motherAnxious:fatherFearful                                (vectorized)
+##            normal(0, 3)         b                motherAvoidant                                (vectorized)
+##            normal(0, 3)         b  motherAvoidant:fatherAnxious                                (vectorized)
+##            normal(0, 3)         b motherAvoidant:fatherAvoidant                                (vectorized)
+##            normal(0, 3)         b  motherAvoidant:fatherFearful                                (vectorized)
+##            normal(0, 3)         b                 motherFearful                                (vectorized)
+##            normal(0, 3)         b   motherFearful:fatherAnxious                                (vectorized)
+##            normal(0, 3)         b  motherFearful:fatherAvoidant                                (vectorized)
+##            normal(0, 3)         b   motherFearful:fatherFearful                                (vectorized)
+##            normal(0, 3)         b                                               zi             (vectorized)
+##            normal(0, 3)         b                       genderM                 zi             (vectorized)
+##  student_t(3, 0.7, 2.5) Intercept                                                                   default
+##          logistic(0, 1) Intercept                                               zi                  default
+##    student_t(3, 0, 2.5)        sd                                                                   default
+##    student_t(3, 0, 2.5)        sd                                               zi                  default
+##    student_t(3, 0, 2.5)        sd                               ID_class                       (vectorized)
+##    student_t(3, 0, 2.5)        sd                     Intercept ID_class                       (vectorized)
+##    student_t(3, 0, 2.5)        sd                               ID_class        zi             (vectorized)
+##    student_t(3, 0, 2.5)        sd                     Intercept ID_class        zi             (vectorized)
+##       gamma(0.01, 0.01)     shape                                                                   default
+\end{verbatim}
+
+\hypertarget{posterior}{%
+\subsection{Posterior}\label{posterior}}
+
+The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).
+To do that we use the \texttt{brm()} function from the \texttt{brms} R-package \citep{burknerBrmsPackageBayesian2017, burknerAdvancedBayesianMultilevel2018a}, which is based on STAN \citep{standevelopmentteamRStanInterfaceStan2020}.
+Summary of the encompassing model is presented below.
+
+\begin{verbatim}
+##  Family: zero_inflated_negbinomial 
+##   Links: mu = log; shape = identity; zi = logit 
+## Formula: externalizing_sum ~ gender + mother * father + (1 | ID_class) 
+##          zi ~ gender + (1 | ID_class)
+##    Data: data (Number of observations: 847) 
+## Samples: 6 chains, each with iter = 10000; warmup = 2000; thin = 1;
+##          total post-warmup samples = 48000
+## 
+## Group-Level Effects: 
+## ~ID_class (Number of levels: 50) 
+##                  Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## sd(Intercept)        0.30      0.07     0.17     0.45 1.00    14161    20827
+## sd(zi_Intercept)     1.14      0.29     0.68     1.82 1.00    22361    31673
+## 
+## Population-Level Effects: 
+##                               Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## Intercept                         0.98      0.13     0.72     1.24 1.00    35521    38291
+## zi_Intercept                     -1.33      0.33    -2.09    -0.78 1.00    36797    30278
+## genderM                           0.32      0.08     0.16     0.49 1.00    81905    36734
+## motherAnxious                     0.32      0.19    -0.05     0.70 1.00    39619    37732
+## motherAvoidant                    0.17      0.26    -0.33     0.69 1.00    37098    36353
+## motherFearful                     0.69      0.41    -0.07     1.54 1.00    34182    30539
+## fatherAnxious                     0.22      0.20    -0.16     0.60 1.00    40404    38489
+## fatherAvoidant                   -0.45      0.22    -0.87    -0.02 1.00    40412    38016
+## fatherFearful                     0.11      0.42    -0.69     0.96 1.00    35432    34390
+## motherAnxious:fatherAnxious      -0.39      0.28    -0.94     0.15 1.00    36701    36495
+## motherAvoidant:fatherAnxious     -0.12      0.34    -0.80     0.53 1.00    36329    36398
+## motherFearful:fatherAnxious      -0.43      0.51    -1.46     0.55 1.00    35084    32876
+## motherAnxious:fatherAvoidant      0.33      0.29    -0.25     0.89 1.00    36157    37830
+## motherAvoidant:fatherAvoidant     0.61      0.34    -0.06     1.26 1.00    34169    35603
+## motherFearful:fatherAvoidant      0.30      0.48    -0.68     1.20 1.00    32533    31702
+## motherAnxious:fatherFearful      -0.06      0.48    -1.02     0.86 1.00    34008    34560
+## motherAvoidant:fatherFearful      0.09      0.57    -1.04     1.19 1.00    34795    33933
+## motherFearful:fatherFearful      -0.26      0.60    -1.48     0.86 1.00    30725    30729
+## zi_genderM                       -0.78      0.29    -1.38    -0.23 1.00    70555    35796
+## 
+## Family Specific Parameters: 
+##       Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## shape     1.63      0.24     1.22     2.14 1.00    34643    32767
+## 
+## Samples were drawn using sampling(NUTS). For each parameter, Bulk_ESS
+## and Tail_ESS are effective sample size measures, and Rhat is the potential
+## scale reduction factor on split chains (at convergence, Rhat = 1).
+\end{verbatim}
+
+\hypertarget{hypothesis-matrices}{%
+\section{Hypothesis Matrices}\label{hypothesis-matrices}}
+
+For each informative hypothesis, we obtain a hypothesis matrix that translates equality and inequality constraints according to the encompassing model parametrization.
+Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ({[}TODO: add link{]}).
+
+Here we present the obtained hypothesis matrices were on the columns we have the parameters of the encompassing model (excluding the intercept) and each row express an equality constraint or an inequality constraint.
+Matrices row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters).
+For example, \texttt{"M\_Avoidant:F\_Anxious"} indicates the actual interaction term of the model, whereas \texttt{"{[}M\_Avoidant\_F\_Anxious{]}"} indicate the group condition.
+This is done because when assuming no interaction or no father attachment effect we set constraints directly on the model parameters, instead, when constraints involve group comparisons, we need to obtain the resulting conditions.
+Equality and inequality constraints are presented separately.
+
+\hypertarget{null-hypothesis}{%
+\subsubsection*{Null Hypothesis}\label{null-hypothesis}}
+\addcontentsline{toc}{subsubsection}{Null Hypothesis}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Equality matrix}, \(R_{iE} = 0\) (each row is set to zero).
+\end{itemize}
+
+\begin{verbatim}
+##                       M_Anxious M_Avoidant M_Fearful F_Anxious F_Avoidant F_Fearful M_Anxious:F_Anxious M_Avoidant:F_Anxious M_Fearful:F_Anxious M_Anxious:F_Avoidant M_Avoidant:F_Avoidant M_Fearful:F_Avoidant M_Anxious:F_Fearful M_Avoidant:F_Fearful M_Fearful:F_Fearful
+## M_Anxious                     1          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Avoidant                    0          1         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Fearful                     0          0         1         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## F_Anxious                     0          0         0         1          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## F_Avoidant                    0          0         0         0          1         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## F_Fearful                     0          0         0         0          0         1                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Anxious:F_Anxious           0          0         0         0          0         0                   1                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Avoidant:F_Anxious          0          0         0         0          0         0                   0                    1                   0                    0                     0                    0                   0                    0                   0
+## M_Fearful:F_Anxious           0          0         0         0          0         0                   0                    0                   1                    0                     0                    0                   0                    0                   0
+## M_Anxious:F_Avoidant          0          0         0         0          0         0                   0                    0                   0                    1                     0                    0                   0                    0                   0
+## M_Avoidant:F_Avoidant         0          0         0         0          0         0                   0                    0                   0                    0                     1                    0                   0                    0                   0
+## M_Fearful:F_Avoidant          0          0         0         0          0         0                   0                    0                   0                    0                     0                    1                   0                    0                   0
+## M_Anxious:F_Fearful           0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   1                    0                   0
+## M_Avoidant:F_Fearful          0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    1                   0
+## M_Fearful:F_Fearful           0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   1
+\end{verbatim}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Inequality matrix}, \(R_{iI} > 0\) (each row is set to grater than zero). There are no inequality constraints.
+\end{itemize}
+
+\hypertarget{monotropy-hypothesis}{%
+\subsubsection*{Monotropy Hypothesis}\label{monotropy-hypothesis}}
+\addcontentsline{toc}{subsubsection}{Monotropy Hypothesis}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Equality matrix}, \(R_{iE} = 0\) (each row is set to zero).
+\end{itemize}
+
+\begin{verbatim}
+##                            M_Anxious M_Avoidant M_Fearful F_Anxious F_Avoidant F_Fearful M_Anxious:F_Anxious M_Avoidant:F_Anxious M_Fearful:F_Anxious M_Anxious:F_Avoidant M_Avoidant:F_Avoidant M_Fearful:F_Avoidant M_Anxious:F_Fearful M_Avoidant:F_Fearful M_Fearful:F_Fearful
+## [M_Anx_F_Sec - M_Av_F_Sec]         1         -1         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## F_Anxious                          0          0         0         1          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## F_Avoidant                         0          0         0         0          1         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## F_Fearful                          0          0         0         0          0         1                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Anxious:F_Anxious                0          0         0         0          0         0                   1                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Avoidant:F_Anxious               0          0         0         0          0         0                   0                    1                   0                    0                     0                    0                   0                    0                   0
+## M_Fearful:F_Anxious                0          0         0         0          0         0                   0                    0                   1                    0                     0                    0                   0                    0                   0
+## M_Anxious:F_Avoidant               0          0         0         0          0         0                   0                    0                   0                    1                     0                    0                   0                    0                   0
+## M_Avoidant:F_Avoidant              0          0         0         0          0         0                   0                    0                   0                    0                     1                    0                   0                    0                   0
+## M_Fearful:F_Avoidant               0          0         0         0          0         0                   0                    0                   0                    0                     0                    1                   0                    0                   0
+## M_Anxious:F_Fearful                0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   1                    0                   0
+## M_Avoidant:F_Fearful               0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    1                   0
+## M_Fearful:F_Fearful                0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   1
+\end{verbatim}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Inequality matrix}, \(R_{iI} > 0\) (each row is set to grater than zero).
+\end{itemize}
+
+\begin{verbatim}
+##                             M_Anxious M_Avoidant M_Fearful F_Anxious F_Avoidant F_Fearful M_Anxious:F_Anxious M_Avoidant:F_Anxious M_Fearful:F_Anxious M_Anxious:F_Avoidant M_Avoidant:F_Avoidant M_Fearful:F_Avoidant M_Anxious:F_Fearful M_Avoidant:F_Fearful M_Fearful:F_Fearful
+## [M_Anx_F_Sec]                       1          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Fear_F_Sec - M_Av_F_Sec]         0         -1         1         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+\end{verbatim}
+
+\hypertarget{hierarchy-hypothesis}{%
+\subsubsection*{Hierarchy Hypothesis}\label{hierarchy-hypothesis}}
+\addcontentsline{toc}{subsubsection}{Hierarchy Hypothesis}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Equality matrix}, \(R_{iE} = 0\) (each row is set to zero).
+\end{itemize}
+
+\begin{verbatim}
+##                            M_Anxious M_Avoidant M_Fearful F_Anxious F_Avoidant F_Fearful M_Anxious:F_Anxious M_Avoidant:F_Anxious M_Fearful:F_Anxious M_Anxious:F_Avoidant M_Avoidant:F_Avoidant M_Fearful:F_Avoidant M_Anxious:F_Fearful M_Avoidant:F_Fearful M_Fearful:F_Fearful
+## [M_Anx_F_Sec - M_Av_F_Sec]         1         -1         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Sec_F_Anx - M_Sec_F_Av]         0          0         0         1         -1         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Anxious:F_Anxious                0          0         0         0          0         0                   1                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Avoidant:F_Anxious               0          0         0         0          0         0                   0                    1                   0                    0                     0                    0                   0                    0                   0
+## M_Fearful:F_Anxious                0          0         0         0          0         0                   0                    0                   1                    0                     0                    0                   0                    0                   0
+## M_Anxious:F_Avoidant               0          0         0         0          0         0                   0                    0                   0                    1                     0                    0                   0                    0                   0
+## M_Avoidant:F_Avoidant              0          0         0         0          0         0                   0                    0                   0                    0                     1                    0                   0                    0                   0
+## M_Fearful:F_Avoidant               0          0         0         0          0         0                   0                    0                   0                    0                     0                    1                   0                    0                   0
+## M_Anxious:F_Fearful                0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   1                    0                   0
+## M_Avoidant:F_Fearful               0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    1                   0
+## M_Fearful:F_Fearful                0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   1
+\end{verbatim}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Inequality matrix}, \(R_{iI} > 0\) (each row is set to grater than zero).
+\end{itemize}
+
+\begin{verbatim}
+##                               M_Anxious M_Avoidant M_Fearful F_Anxious F_Avoidant F_Fearful M_Anxious:F_Anxious M_Avoidant:F_Anxious M_Fearful:F_Anxious M_Anxious:F_Avoidant M_Avoidant:F_Avoidant M_Fearful:F_Avoidant M_Anxious:F_Fearful M_Avoidant:F_Fearful M_Fearful:F_Fearful
+## [M_Anx_F_Sec]                         1          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Fear_F_Sec - M_Av_F_Sec]           0         -1         1         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Sec_F_Anx]                         0          0         0         1          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Sec_F_Fear - M_Sec_F_Av]           0          0         0         0         -1         1                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Anx_F_Sec - M_Sec_F_Anx]           1          0         0        -1          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Av_F_Sec - M_Sec_F_Av]             0          1         0         0         -1         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Fear_F_Sec - M_Sec_F_Fear]         0          0         1         0          0        -1                   0                    0                   0                    0                     0                    0                   0                    0                   0
+\end{verbatim}
+
+\hypertarget{independence-hypothesis}{%
+\subsubsection*{Independence Hypothesis}\label{independence-hypothesis}}
+\addcontentsline{toc}{subsubsection}{Independence Hypothesis}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Equality matrix}, \(R_{iE} = 0\) (each row is set to zero).
+\end{itemize}
+
+\begin{verbatim}
+##                            M_Anxious M_Avoidant M_Fearful F_Anxious F_Avoidant F_Fearful M_Anxious:F_Anxious M_Avoidant:F_Anxious M_Fearful:F_Anxious M_Anxious:F_Avoidant M_Avoidant:F_Avoidant M_Fearful:F_Avoidant M_Anxious:F_Fearful M_Avoidant:F_Fearful M_Fearful:F_Fearful
+## [M_Anx_F_Sec - M_Av_F_Sec]         1         -1         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Anxious:F_Anxious                0          0         0         0          0         0                   1                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Avoidant:F_Anxious               0          0         0         0          0         0                   0                    1                   0                    0                     0                    0                   0                    0                   0
+## M_Fearful:F_Anxious                0          0         0         0          0         0                   0                    0                   1                    0                     0                    0                   0                    0                   0
+## M_Anxious:F_Avoidant               0          0         0         0          0         0                   0                    0                   0                    1                     0                    0                   0                    0                   0
+## M_Avoidant:F_Avoidant              0          0         0         0          0         0                   0                    0                   0                    0                     1                    0                   0                    0                   0
+## M_Fearful:F_Avoidant               0          0         0         0          0         0                   0                    0                   0                    0                     0                    1                   0                    0                   0
+## M_Anxious:F_Fearful                0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   1                    0                   0
+## M_Avoidant:F_Fearful               0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    1                   0
+## M_Fearful:F_Fearful                0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   1
+\end{verbatim}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Inequality matrix}, \(R_{iI} > 0\) (each row is set to grater than zero).
+\end{itemize}
+
+\begin{verbatim}
+##                             M_Anxious M_Avoidant M_Fearful F_Anxious F_Avoidant F_Fearful M_Anxious:F_Anxious M_Avoidant:F_Anxious M_Fearful:F_Anxious M_Anxious:F_Avoidant M_Avoidant:F_Avoidant M_Fearful:F_Avoidant M_Anxious:F_Fearful M_Avoidant:F_Fearful M_Fearful:F_Fearful
+## [M_Anx_F_Sec]                       1          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Fear_F_Sec - M_Av_F_Sec]         0         -1         1         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Sec_F_Anx]                       0          0         0         1          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Sec_F_Av - M_Sec_F_Anx]          0          0         0        -1          1         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Sec_F_Fear - M_Sec_F_Av]         0          0         0         0         -1         1                   0                    0                   0                    0                     0                    0                   0                    0                   0
+\end{verbatim}
+
+\hypertarget{integration-hypothesis}{%
+\subsubsection*{Integration Hypothesis}\label{integration-hypothesis}}
+\addcontentsline{toc}{subsubsection}{Integration Hypothesis}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Equality matrix}, \(R_{iE} = 0\) (each row is set to zero).
+\end{itemize}
+
+\begin{verbatim}
+##                               M_Anxious M_Avoidant M_Fearful F_Anxious F_Avoidant F_Fearful M_Anxious:F_Anxious M_Avoidant:F_Anxious M_Fearful:F_Anxious M_Anxious:F_Avoidant M_Avoidant:F_Avoidant M_Fearful:F_Avoidant M_Anxious:F_Fearful M_Avoidant:F_Fearful M_Fearful:F_Fearful
+## [M_Anx_F_Sec - M_Av_F_Sec]            1         -1         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Anx_F_Sec - M_Sec_F_Anx]           1          0         0        -1          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Anx_F_Sec - M_Sec_F_Av]            1          0         0         0         -1         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Anx_F_Anx - M_Anx_F_Av]            0          0         0         1         -1         0                   1                    0                   0                   -1                     0                    0                   0                    0                   0
+## [M_Anx_F_Anx - M_Av_F_Anx]            1         -1         0         0          0         0                   1                   -1                   0                    0                     0                    0                   0                    0                   0
+## [M_Anx_F_Anx - M_Av_F_Av]             1         -1         0         1         -1         0                   1                    0                   0                    0                    -1                    0                   0                    0                   0
+## [M_Fear_F_Anx - M_Fear_F_Av]          0          0         0         1         -1         0                   0                    0                   1                    0                     0                   -1                   0                    0                   0
+## [M_Fear_F_Anx - M_Anx_F_Fear]        -1          0         1         1          0        -1                   0                    0                   1                    0                     0                    0                  -1                    0                   0
+## [M_Fear_F_Anx - M_Av_F_Fear]          0         -1         1         1          0        -1                   0                    0                   1                    0                     0                    0                   0                   -1                   0
+\end{verbatim}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Inequality matrix}, \(R_{iI} > 0\) (each row is set to grater than zero).
+\end{itemize}
+
+\begin{verbatim}
+##                                M_Anxious M_Avoidant M_Fearful F_Anxious F_Avoidant F_Fearful M_Anxious:F_Anxious M_Avoidant:F_Anxious M_Fearful:F_Anxious M_Anxious:F_Avoidant M_Avoidant:F_Avoidant M_Fearful:F_Avoidant M_Anxious:F_Fearful M_Avoidant:F_Fearful M_Fearful:F_Fearful
+## [M_Anx_F_Sec]                          1          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Anx_F_Anx - M_Anx_F_Sec]            0          0         0         1          0         0                   1                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Fear_F_Anx - M_Anx_F_Anx]          -1          0         1         0          0         0                  -1                    0                   1                    0                     0                    0                   0                    0                   0
+## [M_Fear_F_Fear - M_Fear_F_Anx]         0          0         0        -1          0         1                   0                    0                  -1                    0                     0                    0                   0                    0                   1
+\end{verbatim}
+
+\hypertarget{centering-and-adjusting}{%
+\section{Centering and Adjusting}\label{centering-and-adjusting}}
+
+So far we have specified the encompassing prior, obtained the model posterior distribution, and defined the hypotheses matrices.
+Now, we need to transform our parameters of interest and center the distribution on the constraints focal points of interest.
+We apply the following transformation
+\[
+\beta = R\theta - r
+\]
+but we can ignore \(r\) as in all our constraints it is always a vector of zeros.
+
+Next, we get the adjusted prior and the posterior of the transformed parameters vector \(\beta\) (i.e., the parameters that identify the constraints) for each hypothesis.
+The adjusted prior is given by
+
+\[
+\pi_{adj}(\beta) \sim \mathcal{N}(0, \Sigma_{\beta}) = \mathcal{N}(0, R\Sigma_{\theta}R^T).
+\]
+Note that we set the mean vector to zero. The posterior is given by the same transformation
+\[
+Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\theta}-r, R\hat{\Sigma}_{\theta}R^T).
+\]
+See the main article for more details {[}TODO: add link{]}.
+
+This adjustment, however, requires the hypothesis matrix \(R\) to be \emph{full-row-rank} (i.e., all constraints are linearly independent).
+However, this is not the case of the Hierarchy Hypothesis.
+To overcome this issue, we follow the solution presented in the main article.
+First, define \(R^*\) selecting the maximum number of independent rows.
+In this case, 15 contrast are independent
+
+\begin{verbatim}
+##                             M_Anxious M_Avoidant M_Fearful F_Anxious F_Avoidant F_Fearful M_Anxious:F_Anxious M_Avoidant:F_Anxious M_Fearful:F_Anxious M_Anxious:F_Avoidant M_Avoidant:F_Avoidant M_Fearful:F_Avoidant M_Anxious:F_Fearful M_Avoidant:F_Fearful M_Fearful:F_Fearful
+## [M_Anx_F_Sec - M_Av_F_Sec]          1         -1         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Sec_F_Anx - M_Sec_F_Av]          0          0         0         1         -1         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Anxious:F_Anxious                 0          0         0         0          0         0                   1                    0                   0                    0                     0                    0                   0                    0                   0
+## M_Avoidant:F_Anxious                0          0         0         0          0         0                   0                    1                   0                    0                     0                    0                   0                    0                   0
+## M_Fearful:F_Anxious                 0          0         0         0          0         0                   0                    0                   1                    0                     0                    0                   0                    0                   0
+## M_Anxious:F_Avoidant                0          0         0         0          0         0                   0                    0                   0                    1                     0                    0                   0                    0                   0
+## M_Avoidant:F_Avoidant               0          0         0         0          0         0                   0                    0                   0                    0                     1                    0                   0                    0                   0
+## M_Fearful:F_Avoidant                0          0         0         0          0         0                   0                    0                   0                    0                     0                    1                   0                    0                   0
+## M_Anxious:F_Fearful                 0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   1                    0                   0
+## M_Avoidant:F_Fearful                0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    1                   0
+## M_Fearful:F_Fearful                 0          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   1
+## [M_Anx_F_Sec]                       1          0         0         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Fear_F_Sec - M_Av_F_Sec]         0         -1         1         0          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Sec_F_Anx]                       0          0         0         1          0         0                   0                    0                   0                    0                     0                    0                   0                    0                   0
+## [M_Sec_F_Fear - M_Sec_F_Av]         0          0         0         0         -1         1                   0                    0                   0                    0                     0                    0                   0                    0                   0
+\end{verbatim}
+
+The remaining contrasts, instead, are obtained as linear combinations of the other constraints. In particular,
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# Constraint 16: [M\_Anx\_F\_Sec {-} M\_Sec\_F\_Anx]}
+\FunctionTok{all}\NormalTok{(R[}\StringTok{"[M\_Anx\_F\_Sec {-} M\_Sec\_F\_Anx]"}\NormalTok{,] }\SpecialCharTok{==}\NormalTok{ R[}\StringTok{"[M\_Anx\_F\_Sec]"}\NormalTok{, ] }\SpecialCharTok{{-}}\NormalTok{ R[}\StringTok{"[M\_Sec\_F\_Anx]"}\NormalTok{, ])}
+\DocumentationTok{\#\# [1] TRUE}
+
+\CommentTok{\# Constraint 17: [M\_Av\_F\_Sec {-} M\_Sec\_F\_Av]}
+\FunctionTok{all}\NormalTok{(R[}\StringTok{"[M\_Av\_F\_Sec {-} M\_Sec\_F\_Av]"}\NormalTok{,] }\SpecialCharTok{==} \SpecialCharTok{{-}}\NormalTok{ R[}\StringTok{"[M\_Anx\_F\_Sec {-} M\_Av\_F\_Sec]"}\NormalTok{, ] }\SpecialCharTok{+}\NormalTok{ R[}\StringTok{"[M\_Sec\_F\_Anx {-} M\_Sec\_F\_Av]"}\NormalTok{, ] }\SpecialCharTok{+}\NormalTok{  R[}\StringTok{"[M\_Anx\_F\_Sec {-} M\_Sec\_F\_Anx]"}\NormalTok{, ])}
+\DocumentationTok{\#\# [1] TRUE}
+
+\CommentTok{\# Constraint 18: [M\_Fear\_F\_Sec {-} M\_Sec\_F\_Fear] }
+\FunctionTok{all}\NormalTok{(R[}\StringTok{"[M\_Fear\_F\_Sec {-} M\_Sec\_F\_Fear]"}\NormalTok{,] }\SpecialCharTok{==}\NormalTok{ R[}\StringTok{"[M\_Av\_F\_Sec {-} M\_Sec\_F\_Av]"}\NormalTok{, ] }\SpecialCharTok{+}\NormalTok{ R[}\StringTok{"[M\_Fear\_F\_Sec {-} M\_Av\_F\_Sec]"}\NormalTok{, ] }\SpecialCharTok{{-}}\NormalTok{ R[}\StringTok{"[M\_Sec\_F\_Fear {-} M\_Sec\_F\_Av]"}\NormalTok{, ])}
+\DocumentationTok{\#\# [1] TRUE}
+\end{Highlighting}
+\end{Shaded}
+
+Before computing the Bayes Factor, note that we have a set of comparable hypotheses as exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero.
+The solution is the trivial solution of simply consider all parameters equal to zero.
+Finally, we do not need to standardize our parameters as they represent mean groups differences.
+See the main article for a detailed explanation {[}TODO: add link article{]}.
+
+\hypertarget{results-and-sensitivity}{%
+\section{Results and Sensitivity}\label{results-and-sensitivity}}
+
+To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in detail in the main article {[}TODO: add link article{]}.
+Bayes Factor and posterior probability of each hypothesis are reported in Table\textasciitilde\ref{tab:table-bf-results-ext}.
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-bf-results-ext}Bayes Factor encompassing model and hypothesis posteriro probabilities  ($n_{subj} = 847$).}
+\centering
+\begin{tabular}[t]{rcc>{\centering\arraybackslash}m{1cm}}
+\toprule
+\textbf{Hypothesis} & \textbf{Bayes Factor} & \textbf{Posterior Probability} & \textbf{ }\\
+\midrule
+Null & 2.9e+11 & 0.01 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_null.png}\\
+Monotropy & 2.6e+13 & 0.98 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_monotropy.png}\\
+Hierarchy & 2.7e+11 & 0.01 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_hierarchy.png}\\
+Independence & 3.9e+09 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_independence.png}\\
+Integration & 3.2e+09 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_integration.png}\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Remember, however, that prior specification affects the Bayes Factor results.
+Therefore, we also evaluate the results considering different prior settings.
+In particular, we consider as possible priors for the parameters of interest:
+
+\begin{itemize}
+\tightlist
+\item
+  \(\mathcal{N}(0,.5)\) - unreasonable tight prior
+\item
+  \(\mathcal{N}(0,1)\) - tighter prior
+\item
+  \(\mathcal{N}(0,3)\) - original prior
+\item
+  \(\mathcal{N}(0,5)\) - more diffuse prior
+\item
+  \(\mathcal{N}(0,10)\) - unreasonably diffuse prior
+\end{itemize}
+
+The results of the prior sensitivity analysis are reported in Table\textasciitilde\ref{tab:table-sens-prior-analysis-ext}.
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-sens-prior-analysis-ext}Bayes Factor encompassing model v and hypothesis posterior probabilities (PP) under different prior settings  ($n_{subj} = 847$).}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{>{}rcccrcccrcc}
+\toprule
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, .5)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 1)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 3)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 5)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 10)$}} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11}
+\textbf{Hypothesis} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP}\\
+\midrule
+\textbf{Null} & 8.2e+01 & 0.00 & 9.4e+04 & 0.00 & 2.9e+11 & 0.01 & 4.7e+14 & 0.03 & 1.5e+19 & 0.11\\
+\textbf{Monotropy} & 1.2e+05 & 0.67 & 6.3e+07 & 0.90 & 2.6e+13 & 0.98 & 1.6e+16 & 0.97 & 1.2e+20 & 0.89\\
+\textbf{Hierarchy} & 4.9e+04 & 0.28 & 6.1e+06 & 0.09 & 2.7e+11 & 0.01 & 6.7e+13 & 0.00 & 1.2e+17 & 0.00\\
+\textbf{Independence} & 4.4e+03 & 0.02 & 2.6e+05 & 0.00 & 3.9e+09 & 0.00 & 5.8e+11 & 0.00 & 5.1e+14 & 0.00\\
+\textbf{Integration} & 4.6e+03 & 0.03 & 3.3e+05 & 0.00 & 3.2e+09 & 0.00 & 3.3e+11 & 0.00 & 1.5e+14 & 0.00\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data.
+However, we can observe two distinct patterns.
+As the prior gets more diffuse, the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
+Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.
+
+To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
+On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details{[}TODO: add link article{]}).
+
+All the defined hypotheses include equality constraints.
+Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
+Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).
+
+\hypertarget{selected-model-1}{%
+\section{Selected Model}\label{selected-model-1}}
+
+One of the limits of the Bayes Factor with the encompassing prior approach is that we only get the selected hypothesis but we do not obtain the actual estimates of the parameters posterior.
+To overcome this limit we rely on Bayesian inference that allows us to effectively estimate the model parameter posteriors.
+
+This time in the model we consider only the role of gender and mother attachment as fixed effects of \(\mu\). In the R formula syntax, we have
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# formula for p}
+\NormalTok{p }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# formula for mu}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+\end{Highlighting}
+\end{Shaded}
+
+Again, we specify a normal distribution with mean 0 and standard deviation of 3, \(\mathcal{N}(0,3)\), as prior for the beta parameters (i.e., those related to gender and mother attachment).
+Whereas, for the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) \texttt{brms} default priors are maintained.
+The resulting prior settings are
+
+\begin{verbatim}
+##                   prior     class           coef    group resp dpar nlpar bound       source
+##            normal(0, 3)         b                                                       user
+##            normal(0, 3)         b        genderM                                (vectorized)
+##            normal(0, 3)         b  motherAnxious                                (vectorized)
+##            normal(0, 3)         b motherAvoidant                                (vectorized)
+##            normal(0, 3)         b  motherFearful                                (vectorized)
+##            normal(0, 3)         b                                zi             (vectorized)
+##            normal(0, 3)         b        genderM                 zi             (vectorized)
+##  student_t(3, 0.7, 2.5) Intercept                                                    default
+##          logistic(0, 1) Intercept                                zi                  default
+##    student_t(3, 0, 2.5)        sd                                                    default
+##    student_t(3, 0, 2.5)        sd                                zi                  default
+##    student_t(3, 0, 2.5)        sd                ID_class                       (vectorized)
+##    student_t(3, 0, 2.5)        sd      Intercept ID_class                       (vectorized)
+##    student_t(3, 0, 2.5)        sd                ID_class        zi             (vectorized)
+##    student_t(3, 0, 2.5)        sd      Intercept ID_class        zi             (vectorized)
+##       gamma(0.01, 0.01)     shape                                                    default
+\end{verbatim}
+
+The model is estimated using 6 independent chains with 6,000 iterations (warm-up 2,000). The model summary is presented below.
+
+\begin{verbatim}
+##  Family: zero_inflated_negbinomial 
+##   Links: mu = log; shape = identity; zi = logit 
+## Formula: externalizing_sum ~ gender + mother + (1 | ID_class) 
+##          zi ~ gender + (1 | ID_class)
+##    Data: data (Number of observations: 847) 
+## Samples: 6 chains, each with iter = 6000; warmup = 2000; thin = 1;
+##          total post-warmup samples = 24000
+## 
+## Group-Level Effects: 
+## ~ID_class (Number of levels: 50) 
+##                  Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## sd(Intercept)        0.29      0.07     0.17     0.43 1.00     7372    10149
+## sd(zi_Intercept)     1.10      0.27     0.65     1.74 1.00     9371    12428
+## 
+## Population-Level Effects: 
+##                Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## Intercept          0.96      0.11     0.74     1.18 1.00    14818    16592
+## zi_Intercept      -1.27      0.31    -1.97    -0.75 1.00    14384    12961
+## genderM            0.34      0.08     0.18     0.50 1.00    30197    18984
+## motherAnxious      0.25      0.10     0.05     0.46 1.00    21564    18963
+## motherAvoidant     0.32      0.11     0.10     0.53 1.00    21623    19168
+## motherFearful      0.54      0.14     0.28     0.81 1.00    22199    18755
+## zi_genderM        -0.74      0.27    -1.30    -0.22 1.00    27915    17381
+## 
+## Family Specific Parameters: 
+##       Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## shape     1.70      0.25     1.27     2.23 1.00    15644    16568
+## 
+## Samples were drawn using sampling(NUTS). For each parameter, Bulk_ESS
+## and Tail_ESS are effective sample size measures, and Rhat is the potential
+## scale reduction factor on split chains (at convergence, Rhat = 1).
+\end{verbatim}
+
+Marginal effects are presented in Figure\textasciitilde\ref{fig:plot-marginal-ext} and differences between mother attachment patterns are reported in Figure\textasciitilde\ref{fig:plot-diff-ext}.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.95\linewidth]{attachment-bayes-factor_files/figure-latex/plot-marginal-ext-1}
+
+}
+
+\caption{Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$).}\label{fig:plot-marginal-ext}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-diff-ext-1}
+
+}
+
+\caption{Predicted differences between mother attachment patterns ($n_{subj} = 847$).}\label{fig:plot-diff-ext}
+\end{figure}
+
+Overall, results indicate that Males have more externalizing problems than Females.
+Regarding mother attachment, Fearful, Avoidant, and Anxious children have more problems than Secure children.
+Moreover, Fearful children have more problems than Anxious children.
+
+To evaluate the fit of the model to the data, we computed the \emph{Bayesian} \(R^2\) and using the function \texttt{brms::bayes\_R2()}, and we present Posterior Predictions in Figure\textasciitilde\ref{fig:plot-ppcheck-ext}.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{r2\_ext}
+\DocumentationTok{\#\#     Estimate  Est.Error       Q2.5     Q97.5}
+\DocumentationTok{\#\# R2 0.1482686 0.02972484 0.09435914 0.2106949}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-ppcheck-ext-1}
+
+}
+
+\caption{Posterior predictive check ($n_{subj} = 847$).}\label{fig:plot-ppcheck-ext}
+\end{figure}
+
+We can see that the actual variance explained by fixed effects and random effect is around 15\%. Moreover, posterior predictive check indicates a good fit to the data.
+
+\hypertarget{conclusions-2}{%
+\subsubsection*{Conclusions}\label{conclusions-2}}
+\addcontentsline{toc}{subsubsection}{Conclusions}
+
+Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the Monotropy Theory.
+
+\hypertarget{conclusion-ext}{%
+\chapter{Conclusions}\label{conclusion-ext}}
+
+Overall, we obtained consistent results from the three different approaches.
+Males have more problems than Females and, regarding attachment, only mother attachment influence children's externalizing problems.
+In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems.
+Taken together, these results support the Monotropy Theory.
+
+Although if the different approaches lead to apparently similar results, the rigorous interpretation of the results is very different.
+
+\begin{itemize}
+\tightlist
+\item
+  Considering the NHST approach, we actually only found that it is unlikely that mother attachment has no effect.
+Thus, we reject the null hypothesis but we can not quantify the evidence in favour of any of our hypotheses.
+\item
+  Only model comparison allow us to quantify the relative evidence of our models.
+Model comparison results clearly indicated evidence in favour of an effect of mother attachment but not father attachment.
+However, using information criteria we could not directly evaluate our informative hypotheses regarding the expected effects, but only the presence of any effect.
+\item
+  Bayes Factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects.
+Results clearly selected the Monotropy theory as the most likely theory among those considered.
+\end{itemize}
+
+To summarize, the apparently identical results actually have a completely different meaning and what we learn from the data is very different.
+Hopefully, now it is clear that statistical inference is a complex process that requires careful thinking.
+In particular, to answer the questions we are actually interested in, we need to apply the appropriate statistical techniques.
+
+\hypertarget{part-internalizing-problems}{%
+\part*{Internalizing Problems}\label{part-internalizing-problems}}
+\addcontentsline{toc}{part}{Internalizing Problems}
+
+\hypertarget{model-choice-int}{%
+\chapter{Models Family Choice}\label{model-choice-int}}
+
+In this chapter, we discuss the appropriate models family to to take into account data characteristics.
+
+Internalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20.
+Considering data distribution (see Figure\textasciitilde\ref{fig:plot-internalizing-dist}), we choose a \textbf{Negative Binomial} distribution to model the data.
+
+\hypertarget{zero-inflated-negative-binomial-1}{%
+\section{Zero Inflated Negative Binomial}\label{zero-inflated-negative-binomial-1}}
+
+As in the case of externalizing problems, we evaluate whether a \emph{Zero-Inflated} model may be appropriate.
+We compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model considering the same predictors as in the case of externalizing problems.
+Using R formula syntax, we have
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# model formula}
+\NormalTok{internalizing\_sum }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{*}\NormalTok{ father }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+\end{Highlighting}
+\end{Shaded}
+
+Comparing the number of observed zero and expected zeros, we get
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{my\_check\_zeroinflation}\NormalTok{(fit\_int\_nb)}
+\DocumentationTok{\#\# \# Check for zero{-}inflation}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\#    Observed zeros: 226}
+\DocumentationTok{\#\#   Predicted zeros: 195}
+\DocumentationTok{\#\#             Ratio: 0.86}
+\DocumentationTok{\#\# Model is underfitting zeros (probable zero{-}inflation).}
+\end{Highlighting}
+\end{Shaded}
+
+Results indicate that the model is slightly under-fitting the number of zeros.
+Thus, we can fit a \emph{Zero Inflated Negative Binomial} (ZINB) model and compare the performance of the two models.
+Using R formula syntax, we have
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# formula for p}
+\NormalTok{p }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# formula for mu}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{*}\NormalTok{ father }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+\end{Highlighting}
+\end{Shaded}
+
+Below we report results of the analysis of deviance.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{anova}\NormalTok{(fit\_int\_nb, fit\_int\_zinb)}
+\DocumentationTok{\#\# Data: data\_cluster}
+\DocumentationTok{\#\# Models:}
+\DocumentationTok{\#\# fit\_int\_nb: internalizing\_sum \textasciitilde{} gender + mother * father + (1 | ID\_class), zi=\textasciitilde{}0, disp=\textasciitilde{}1}
+\DocumentationTok{\#\# fit\_int\_zinb: internalizing\_sum \textasciitilde{} gender + mother * father + (1 | ID\_class), zi=\textasciitilde{}gender + (1 | ID\_class), disp=\textasciitilde{}1}
+\DocumentationTok{\#\#              Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(\textgreater{}Chisq)    }
+\DocumentationTok{\#\# fit\_int\_nb   19 3680.7 3770.8 {-}1821.3   3642.7                             }
+\DocumentationTok{\#\# fit\_int\_zinb 22 3669.0 3773.3 {-}1812.5   3625.0 17.677      3  0.0005127 ***}
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\end{Highlighting}
+\end{Shaded}
+
+Overall, results indicate that the ZINB model performs better than the Negative Binomial model.
+Note, however, that BIC actually prefers the model without zero inflation.
+Nevertheless, in the following analyses we decide to use ZINB models to be consistent with the externalizing problems analysis.
+
+\hypertarget{nhst-int}{%
+\chapter{NHST}\label{nhst-int}}
+
+Following the traditional NHST approach, we consider the model previously defined that includes all effects of interest (gender effect and the interaction between mother attachment and father attachment).
+Results of the analysis of deviance are reported below.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{car}\SpecialCharTok{::}\FunctionTok{Anova}\NormalTok{(fit\_int\_zinb)}
+\DocumentationTok{\#\# Analysis of Deviance Table (Type II Wald chisquare tests)}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Response: internalizing\_sum}
+\DocumentationTok{\#\#                 Chisq Df Pr(\textgreater{}Chisq)   }
+\DocumentationTok{\#\# gender         0.9449  1   0.331015   }
+\DocumentationTok{\#\# mother        12.4302  3   0.006046 **}
+\DocumentationTok{\#\# father         2.6855  3   0.442698   }
+\DocumentationTok{\#\# mother:father  9.6213  9   0.382006   }
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\end{Highlighting}
+\end{Shaded}
+
+Results indicate only a statistically significant effect of mother attachment. On the contrary, the interaction and father attachment are not significant. The model summary is reported below.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{summary}\NormalTok{(fit\_int\_zinb)}
+\DocumentationTok{\#\#  Family: nbinom2  ( log )}
+\DocumentationTok{\#\# Formula:          internalizing\_sum \textasciitilde{} gender + mother * father + (1 | ID\_class)}
+\DocumentationTok{\#\# Zero inflation:                     \textasciitilde{}gender + (1 | ID\_class)}
+\DocumentationTok{\#\# Data: data\_cluster}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\#      AIC      BIC   logLik deviance df.resid }
+\DocumentationTok{\#\#   3669.0   3773.3  {-}1812.5   3625.0      825 }
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Random effects:}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Conditional model:}
+\DocumentationTok{\#\#  Groups   Name        Variance Std.Dev.}
+\DocumentationTok{\#\#  ID\_class (Intercept) 0.1364   0.3693  }
+\DocumentationTok{\#\# Number of obs: 847, groups:  ID\_class, 50}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Zero{-}inflation model:}
+\DocumentationTok{\#\#  Groups   Name        Variance Std.Dev.}
+\DocumentationTok{\#\#  ID\_class (Intercept) 3.225    1.796   }
+\DocumentationTok{\#\# Number of obs: 847, groups:  ID\_class, 50}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Dispersion parameter for nbinom2 family ():  2.6 }
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Conditional model:}
+\DocumentationTok{\#\#                               Estimate Std. Error z value Pr(\textgreater{}|z|)    }
+\DocumentationTok{\#\# (Intercept)                    0.85592    0.12115   7.065 1.61e{-}12 ***}
+\DocumentationTok{\#\# genderM                        0.06854    0.07051   0.972  0.33101    }
+\DocumentationTok{\#\# motherAnxious                  0.47960    0.16672   2.877  0.00402 ** }
+\DocumentationTok{\#\# motherAvoidant                {-}0.08057    0.24671  {-}0.327  0.74398    }
+\DocumentationTok{\#\# motherFearful                  0.66801    0.41101   1.625  0.10410    }
+\DocumentationTok{\#\# fatherAnxious                  0.07410    0.16668   0.445  0.65661    }
+\DocumentationTok{\#\# fatherAvoidant                 0.09901    0.17349   0.571  0.56822    }
+\DocumentationTok{\#\# fatherFearful                  0.38182    0.33578   1.137  0.25550    }
+\DocumentationTok{\#\# motherAnxious:fatherAnxious   {-}0.26373    0.23441  {-}1.125  0.26055    }
+\DocumentationTok{\#\# motherAvoidant:fatherAnxious   0.25023    0.30643   0.817  0.41416    }
+\DocumentationTok{\#\# motherFearful:fatherAnxious   {-}0.80565    0.50634  {-}1.591  0.11158    }
+\DocumentationTok{\#\# motherAnxious:fatherAvoidant  {-}0.25807    0.23926  {-}1.079  0.28076    }
+\DocumentationTok{\#\# motherAvoidant:fatherAvoidant  0.10204    0.30109   0.339  0.73467    }
+\DocumentationTok{\#\# motherFearful:fatherAvoidant  {-}0.25422    0.46295  {-}0.549  0.58292    }
+\DocumentationTok{\#\# motherAnxious:fatherFearful   {-}0.53674    0.39927  {-}1.344  0.17885    }
+\DocumentationTok{\#\# motherAvoidant:fatherFearful   0.23131    0.47623   0.486  0.62718    }
+\DocumentationTok{\#\# motherFearful:fatherFearful   {-}0.41834    0.54125  {-}0.773  0.43958    }
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Zero{-}inflation model:}
+\DocumentationTok{\#\#             Estimate Std. Error z value Pr(\textgreater{}|z|)    }
+\DocumentationTok{\#\# (Intercept)  {-}2.6112     0.6183  {-}4.223 2.41e{-}05 ***}
+\DocumentationTok{\#\# genderM      {-}0.2890     0.3531  {-}0.818    0.413    }
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\end{Highlighting}
+\end{Shaded}
+
+To evaluate the effect of mother attachment, the marginal predicted values are presented in Figure\textasciitilde\ref{fig:plot-nhst-effects-int}.
+Not that the marginal predicted values are averaged over father attachment and gender effect.
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-nhst-effects-int-1}
+
+}
+
+\caption{Marginal predicted values according to mother attachment. Values are averaged over the other effects ($n_{subj} = 847$).}\label{fig:plot-nhst-effects-int}
+\end{figure}
+
+Post-hoc tests are run to evaluate differences between mother attachment styles, considering pairwise comparisons and adjusting \emph{p}-values according to multivariate \emph{t}-distribution.
+Results are reported below,
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_int\_zinb, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
+                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
+\DocumentationTok{\#\# }\AlertTok{NOTE}\DocumentationTok{: Results may be misleading due to involvement in interactions}
+\DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2150 0.117 825  {-}1.836  0.2509}
+\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.0653 0.136 825  {-}0.481  0.9622}
+\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.2985 0.166 825  {-}1.793  0.2708}
+\DocumentationTok{\#\#  Anxious {-} Avoidant   0.1496 0.112 825   1.336  0.5322}
+\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.0835 0.147 825  {-}0.566  0.9403}
+\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2331 0.164 825  {-}1.423  0.4774}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Results are averaged over the levels of: gender, father }
+\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
+\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
+\end{Highlighting}
+\end{Shaded}
+
+After adjusting p-values we actually get that there are no statistically significant differences.
+Without adjusting, difference between Anxious and Secure children and the difference between Fearful and Secure children have a low (but not statistically significant) \emph{p}-value.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_int\_zinb, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
+                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \ConstantTok{NULL}\NormalTok{)}
+\DocumentationTok{\#\# }\AlertTok{NOTE}\DocumentationTok{: Results may be misleading due to involvement in interactions}
+\DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2150 0.117 825  {-}1.836  0.0668}
+\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.0653 0.136 825  {-}0.481  0.6307}
+\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.2985 0.166 825  {-}1.793  0.0734}
+\DocumentationTok{\#\#  Anxious {-} Avoidant   0.1496 0.112 825   1.336  0.1818}
+\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.0835 0.147 825  {-}0.566  0.5713}
+\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2331 0.164 825  {-}1.423  0.1551}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Results are averaged over the levels of: gender, father }
+\DocumentationTok{\#\# Results are given on the log (not the response) scale.}
+\end{Highlighting}
+\end{Shaded}
+
+To evaluate the fit of the model to the data, we computed the \emph{Marginal} \(R^2\) and the \emph{Conditional} \(R^2\).
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{performance}\SpecialCharTok{::}\FunctionTok{r2}\NormalTok{(fit\_int\_zinb)}
+\DocumentationTok{\#\# Warning: mu of 3.2 is too close to zero, estimate of random effect variances may be unreliable.}
+\DocumentationTok{\#\# \# R2 for Mixed Models}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\#   Conditional R2: 0.217}
+\DocumentationTok{\#\#      Marginal R2: 0.047}
+\end{Highlighting}
+\end{Shaded}
+
+We can see that the actual variance explained by fixed effects is less than 5\%, not that much.
+
+\hypertarget{conclusions-3}{%
+\subsubsection*{Conclusions}\label{conclusions-3}}
+\addcontentsline{toc}{subsubsection}{Conclusions}
+
+Results are difficult to interpret because we have a statistically significant effect of mother attachment, but, considering pot-hoc tests, we get no statistically significant difference.
+Overall, we could say that, in some way, results indicate a role of mother attachment but this probably is small.
+
+\hypertarget{model-comparison-int}{%
+\chapter{Model Comparison}\label{model-comparison-int}}
+
+\hypertarget{formalize-models-1}{%
+\section{Formalize Models}\label{formalize-models-1}}
+
+We consider Zero Inflated Negative Binomial Mixed-Effects models with only the role of gender as a fixed effect and children's classroom ID as a random effect for \(p\).
+Whereas, considering \(\mu\), we define the same models as in the analysis of externalizing problems.
+Using R formula syntax, we have
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# formula for p (same for all models)}
+\NormalTok{p }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# formula for mu}
+
+\CommentTok{\# fit\_int\_zero}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# fit\_int\_mother}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# fit\_int\_additive}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{+}\NormalTok{ father }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# fit\_int\_inter}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{*}\NormalTok{ father }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{aic-and-bic-results-1}{%
+\section{AIC and BIC Results}\label{aic-and-bic-results-1}}
+
+AIC and BIC values together with their relative weights are computed are reported in Table\textasciitilde\ref{tab:table-AIC-BIC-weights-int}.
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-AIC-BIC-weights-int}Model comparison internalizing problems ($n_{subj} = 847$).}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{rccc>{\centering\arraybackslash}m{1cm}cc>{\centering\arraybackslash}m{1cm}}
+\toprule
+\textbf{Model} & \textbf{Df} & \textbf{AIC} & \textbf{AIC$_{weights}$} & \textbf{ } & \textbf{BIC} & \textbf{BIC$_{weights}$} & \textbf{ }\\
+\midrule
+fit-int-zero & 6 & 3671.4 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_AIC_int_zero.png} & 3704.6 & 0.52 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BIC_int_zero.png}\\
+fit-int-mother & 9 & 3657.4 & 0.83 & \includegraphics[width=0.33in, height=0.33in]{images/ball_AIC_int_mother.png} & 3704.8 & 0.48 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BIC_int_mother.png}\\
+fit-int-additive & 12 & 3660.6 & 0.16 & \includegraphics[width=0.33in, height=0.33in]{images/ball_AIC_int_additive.png} & 3722.2 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BIC_int_additive.png}\\
+fit-int-inter & 21 & 3669.0 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_AIC_int_inter.png} & 3773.3 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BIC_int_inter.png}\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+According to AIC, the most likely model is \texttt{fit\_int\_mother} (83\%) and the second most likely model is \texttt{fit\_int\_additive} (16\%) given the data and the set of models considered.
+According to BIC, instead, \texttt{fit\_int\_zero} and \texttt{fit\_int\_mother} models have almost the same probability, 52\% and 48\% respectively.
+
+We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.
+
+\hypertarget{selected-model-2}{%
+\section{Selected Model}\label{selected-model-2}}
+
+Results of analysis of deviance for model \texttt{fit\_int\_mother} are reported below.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{car}\SpecialCharTok{::}\FunctionTok{Anova}\NormalTok{(fit\_int\_mother)}
+\DocumentationTok{\#\# Analysis of Deviance Table (Type II Wald chisquare tests)}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Response: internalizing\_sum}
+\DocumentationTok{\#\#         Chisq Df Pr(\textgreater{}Chisq)    }
+\DocumentationTok{\#\# gender  0.754  1  0.3852261    }
+\DocumentationTok{\#\# mother 19.894  3  0.0001786 ***}
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\end{Highlighting}
+\end{Shaded}
+
+Results confirm a statistically significant effect of mother attachment. The model summary is reported below.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{summary}\NormalTok{(fit\_int\_mother)}
+\DocumentationTok{\#\#  Family: nbinom2  ( log )}
+\DocumentationTok{\#\# Formula:          internalizing\_sum \textasciitilde{} gender + mother + (1 | ID\_class)}
+\DocumentationTok{\#\# Zero inflation:                     \textasciitilde{}gender + (1 | ID\_class)}
+\DocumentationTok{\#\# Data: data\_cluster}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\#      AIC      BIC   logLik deviance df.resid }
+\DocumentationTok{\#\#   3657.4   3704.8  {-}1818.7   3637.4      837 }
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Random effects:}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Conditional model:}
+\DocumentationTok{\#\#  Groups   Name        Variance Std.Dev.}
+\DocumentationTok{\#\#  ID\_class (Intercept) 0.1423   0.3772  }
+\DocumentationTok{\#\# Number of obs: 847, groups:  ID\_class, 50}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Zero{-}inflation model:}
+\DocumentationTok{\#\#  Groups   Name        Variance Std.Dev.}
+\DocumentationTok{\#\#  ID\_class (Intercept) 2.966    1.722   }
+\DocumentationTok{\#\# Number of obs: 847, groups:  ID\_class, 50}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Dispersion parameter for nbinom2 family (): 2.56 }
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Conditional model:}
+\DocumentationTok{\#\#                Estimate Std. Error z value Pr(\textgreater{}|z|)    }
+\DocumentationTok{\#\# (Intercept)     0.91263    0.10407   8.770  \textless{} 2e{-}16 ***}
+\DocumentationTok{\#\# genderM         0.06096    0.07021   0.868  0.38523    }
+\DocumentationTok{\#\# motherAnxious   0.28519    0.08921   3.197  0.00139 ** }
+\DocumentationTok{\#\# motherAvoidant  0.11979    0.09462   1.266  0.20550    }
+\DocumentationTok{\#\# motherFearful   0.46860    0.11682   4.011 6.04e{-}05 ***}
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Zero{-}inflation model:}
+\DocumentationTok{\#\#             Estimate Std. Error z value Pr(\textgreater{}|z|)    }
+\DocumentationTok{\#\# (Intercept)  {-}2.5021     0.5425  {-}4.612 3.99e{-}06 ***}
+\DocumentationTok{\#\# genderM      {-}0.2774     0.3493  {-}0.794    0.427    }
+\DocumentationTok{\#\# {-}{-}{-}}
+\DocumentationTok{\#\# Signif.
+codes:  0 \textquotesingle{}***\textquotesingle{} 0.001 \textquotesingle{}**\textquotesingle{} 0.01 \textquotesingle{}*\textquotesingle{} 0.05 \textquotesingle{}.\textquotesingle{} 0.1 \textquotesingle{} \textquotesingle{} 1}
+\end{Highlighting}
+\end{Shaded}
+
+To evaluate the effect of mother attachment, the marginal predicted values are presented in Figure\textasciitilde\ref{fig:plot-comparison-effects-int}.
+Not that the marginal predicted values for gender are averaged over mother attachment.
+Whereas, the marginal predicted values for mother attachment are averaged over gender.
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-comparison-effects-int-1}
+
+}
+
+\caption{Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$).}\label{fig:plot-comparison-effects-int}
+\end{figure}
+
+Post-hoc tests are run, considering pairwise comparisons and adjusting \emph{p}-values according to multivariate \emph{t}-distribution. Results are reported below,
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_int\_mother, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
+                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
+\DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
+\DocumentationTok{\#\#  Secure {-} Anxious     {-}0.285 0.0892 837  {-}3.197  0.0077}
+\DocumentationTok{\#\#  Secure {-} Avoidant    {-}0.120 0.0946 837  {-}1.266  0.5809}
+\DocumentationTok{\#\#  Secure {-} Fearful     {-}0.469 0.1168 837  {-}4.011  0.0004}
+\DocumentationTok{\#\#  Anxious {-} Avoidant    0.165 0.0869 837   1.903  0.2243}
+\DocumentationTok{\#\#  Anxious {-} Fearful    {-}0.183 0.1096 837  {-}1.673  0.3347}
+\DocumentationTok{\#\#  Avoidant {-} Fearful   {-}0.349 0.1167 837  {-}2.989  0.0146}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\# Results are averaged over the levels of: gender }
+\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
+\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
+\end{Highlighting}
+\end{Shaded}
+
+Results indicate that Fearful and Anxious children have more problems than Secure children. Moreover, also the difference between Avoidant and Fearful children is significant.
+
+To evaluate the fit of the model to the data, we computed the \emph{Marginal} \(R^2\) and the \emph{Conditional} \(R^2\).
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{performance}\SpecialCharTok{::}\FunctionTok{r2}\NormalTok{(fit\_int\_mother)}
+\DocumentationTok{\#\# Warning: mu of 3.2 is too close to zero, estimate of random effect variances may be unreliable.}
+\DocumentationTok{\#\# \# R2 for Mixed Models}
+\DocumentationTok{\#\# }
+\DocumentationTok{\#\#   Conditional R2: 0.209}
+\DocumentationTok{\#\#      Marginal R2: 0.031}
+\end{Highlighting}
+\end{Shaded}
+
+We can see that the actual variance explained by fixed effects is 3\%, not that much.
+
+\hypertarget{conclusions-4}{%
+\subsubsection*{Conclusions}\label{conclusions-4}}
+\addcontentsline{toc}{subsubsection}{Conclusions}
+
+Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the \textbf{Monotropy Theory}.
+Note, however, that the compared models contain no information regarding the expected direction of the effects but we only include/exclude predictors.
+
+\hypertarget{BF-int}{%
+\chapter{Bayes Factor}\label{BF-int}}
+
+\hypertarget{encompassing-model-1}{%
+\section{Encompassing Model}\label{encompassing-model-1}}
+
+We define a Zero-Inflated Negative Binomial (ZINB) mixed-effects considering only the role of gender as a fixed effect and children's classroom ID as a random effect for \(p\).
+Whereas, regarding \(\mu\), we consider the interaction between mother and father attachment together with gender as fixed effects and children's classroom ID as a random effect.
+In the R formula syntax, we have
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# formula for p}
+\NormalTok{p }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# formula for mu}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{*}\NormalTok{ father }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{prior-choiche-1}{%
+\subsection{Prior Choiche}\label{prior-choiche-1}}
+
+We set the same prior as for the externalizing problems analysis. The resulting prior settings are
+
+\begin{verbatim}
+##                   prior     class                          coef    group resp dpar nlpar bound       source
+##            normal(0, 3)         b                                                                      user
+##            normal(0, 3)         b                 fatherAnxious                                (vectorized)
+##            normal(0, 3)         b                fatherAvoidant                                (vectorized)
+##            normal(0, 3)         b                 fatherFearful                                (vectorized)
+##            normal(0, 3)         b                       genderM                                (vectorized)
+##            normal(0, 3)         b                 motherAnxious                                (vectorized)
+##            normal(0, 3)         b   motherAnxious:fatherAnxious                                (vectorized)
+##            normal(0, 3)         b  motherAnxious:fatherAvoidant                                (vectorized)
+##            normal(0, 3)         b   motherAnxious:fatherFearful                                (vectorized)
+##            normal(0, 3)         b                motherAvoidant                                (vectorized)
+##            normal(0, 3)         b  motherAvoidant:fatherAnxious                                (vectorized)
+##            normal(0, 3)         b motherAvoidant:fatherAvoidant                                (vectorized)
+##            normal(0, 3)         b  motherAvoidant:fatherFearful                                (vectorized)
+##            normal(0, 3)         b                 motherFearful                                (vectorized)
+##            normal(0, 3)         b   motherFearful:fatherAnxious                                (vectorized)
+##            normal(0, 3)         b  motherFearful:fatherAvoidant                                (vectorized)
+##            normal(0, 3)         b   motherFearful:fatherFearful                                (vectorized)
+##            normal(0, 3)         b                                               zi             (vectorized)
+##            normal(0, 3)         b                       genderM                 zi             (vectorized)
+##  student_t(3, 0.7, 2.5) Intercept                                                                   default
+##          logistic(0, 1) Intercept                                               zi                  default
+##    student_t(3, 0, 2.5)        sd                                                                   default
+##    student_t(3, 0, 2.5)        sd                                               zi                  default
+##    student_t(3, 0, 2.5)        sd                               ID_class                       (vectorized)
+##    student_t(3, 0, 2.5)        sd                     Intercept ID_class                       (vectorized)
+##    student_t(3, 0, 2.5)        sd                               ID_class        zi             (vectorized)
+##    student_t(3, 0, 2.5)        sd                     Intercept ID_class        zi             (vectorized)
+##       gamma(0.01, 0.01)     shape                                                                   default
+\end{verbatim}
+
+\hypertarget{posterior-1}{%
+\subsection{Posterior}\label{posterior-1}}
+
+The encompassing model is estimated using 6 independent chains with 10,000 iterations (warm-up 2,000). Summary of the encompassing model is presented below.
+
+\begin{verbatim}
+##  Family: zero_inflated_negbinomial 
+##   Links: mu = log; shape = identity; zi = logit 
+## Formula: internalizing_sum ~ gender + mother * father + (1 | ID_class) 
+##          zi ~ gender + (1 | ID_class)
+##    Data: data (Number of observations: 847) 
+## Samples: 6 chains, each with iter = 10000; warmup = 2000; thin = 1;
+##          total post-warmup samples = 48000
+## 
+## Group-Level Effects: 
+## ~ID_class (Number of levels: 50) 
+##                  Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## sd(Intercept)        0.44      0.08     0.29     0.62 1.00     9467    20478
+## sd(zi_Intercept)     2.24      0.56     1.37     3.52 1.00    22914    28211
+## 
+## Population-Level Effects: 
+##                               Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## Intercept                         0.83      0.13     0.57     1.07 1.00    21805    30756
+## zi_Intercept                     -2.94      0.70    -4.58    -1.84 1.00    23476    24791
+## genderM                           0.08      0.07    -0.06     0.22 1.00    69575    38126
+## motherAnxious                     0.46      0.17     0.13     0.79 1.00    33349    37383
+## motherAvoidant                   -0.08      0.25    -0.56     0.41 1.00    28640    33103
+## motherFearful                     0.63      0.40    -0.14     1.45 1.00    28081    31710
+## fatherAnxious                     0.07      0.17    -0.27     0.40 1.00    36862    37511
+## fatherAvoidant                    0.08      0.18    -0.26     0.43 1.00    36867    35693
+## fatherFearful                     0.36      0.34    -0.28     1.04 1.00    30611    33358
+## motherAnxious:fatherAnxious      -0.24      0.24    -0.70     0.22 1.00    31718    36313
+## motherAvoidant:fatherAnxious      0.24      0.31    -0.38     0.85 1.00    28308    33805
+## motherFearful:fatherAnxious      -0.75      0.50    -1.75     0.22 1.00    30436    34570
+## motherAnxious:fatherAvoidant     -0.23      0.24    -0.70     0.24 1.00    32215    36746
+## motherAvoidant:fatherAvoidant     0.11      0.30    -0.49     0.71 1.00    27005    33164
+## motherFearful:fatherAvoidant     -0.19      0.45    -1.09     0.69 1.00    27741    32785
+## motherAnxious:fatherFearful      -0.47      0.40    -1.25     0.31 1.00    27639    33504
+## motherAvoidant:fatherFearful      0.28      0.48    -0.67     1.21 1.00    26850    35151
+## motherFearful:fatherFearful      -0.35      0.53    -1.41     0.68 1.00    24657    31248
+## zi_genderM                       -0.30      0.40    -1.10     0.48 1.00    49145    34266
+## 
+## Family Specific Parameters: 
+##       Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## shape     2.46      0.32     1.90     3.17 1.00    38857    36697
+## 
+## Samples were drawn using sampling(NUTS). For each parameter, Bulk_ESS
+## and Tail_ESS are effective sample size measures, and Rhat is the potential
+## scale reduction factor on split chains (at convergence, Rhat = 1).
+\end{verbatim}
+
+\hypertarget{hypothesis-matrices-1}{%
+\section{Hypothesis Matrices}\label{hypothesis-matrices-1}}
+
+Hypothesis matrices are the same as for the externalizing problems analysis.
+
+\hypertarget{centering-and-adjusting-1}{%
+\section{Centering and Adjusting}\label{centering-and-adjusting-1}}
+
+Centering and adjusting procedures are the same as for the externalizing problems analysis.
+
+\hypertarget{results-and-sensitivity-1}{%
+\section{Results and Sensitivity}\label{results-and-sensitivity-1}}
+
+Bayes Factor and posterior probability of each hypothesis are reported in Table\textasciitilde\ref{tab:table-bf-results-int}.
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-bf-results-int}Bayes Factor encompassing model and hypothesis posteriro probabilities  ($n_{subj} = 847$).}
+\centering
+\begin{tabular}[t]{rcc>{\centering\arraybackslash}m{1cm}}
+\toprule
+\textbf{Hypothesis} & \textbf{Bayes Factor} & \textbf{Posterior Probability} & \textbf{ }\\
+\midrule
+Null & 3.5e+11 & 0.03 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_null.png}\\
+Monotropy & 9.2e+12 & 0.92 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_monotropy.png}\\
+Hierarchy & 4.7e+11 & 0.05 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_hierarchy.png}\\
+Independence & 1.1e+10 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_independence.png}\\
+Integration & 1.7e+10 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_integration.png}\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Prior sensitivity analysis is conducted considering the same prior as for the externalizing problems analysis.
+The results of the prior sensitivity analysis are reported in Table\textasciitilde\ref{tab:table-sens-prior-analysis-int}.
+
+\begin{table}[!h]
+
+\caption{\label{tab:table-sens-prior-analysis-int}Bayes Factor encompassing model v and hypothesis posterior probabilities (PP) under different prior settings  ($n_{subj} = 847$).}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{>{}rcccrcccrcc}
+\toprule
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, .5)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 1)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 3)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 5)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 10)$}} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11}
+\textbf{Hypothesis} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP}\\
+\midrule
+\textbf{Null} & 3.8e+01 & 0.00 & 8.9e+04 & 0.00 & 3.5e+11 & 0.03 & 5.5e+14 & 0.09 & 1.8e+19 & 0.27\\
+\textbf{Monotropy} & 2.3e+04 & 0.29 & 1.8e+07 & 0.63 & 9.2e+12 & 0.92 & 5.4e+15 & 0.89 & 4.9e+19 & 0.72\\
+\textbf{Hierarchy} & 4.0e+04 & 0.51 & 8.8e+06 & 0.30 & 4.7e+11 & 0.05 & 1.0e+14 & 0.02 & 2.2e+17 & 0.00\\
+\textbf{Independence} & 5.7e+03 & 0.07 & 6.4e+05 & 0.02 & 1.1e+10 & 0.00 & 1.5e+12 & 0.00 & 1.6e+15 & 0.00\\
+\textbf{Integration} & 9.8e+03 & 0.13 & 1.4e+06 & 0.05 & 1.7e+10 & 0.00 & 1.5e+12 & 0.00 & 8.4e+14 & 0.00\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data.
+However, we can observe the same patterns as for the externalizing problems analysis.
+More diffuse prior, favour hypothesis with more equality constraints.
+Whereas, tighter prior penalize hypothesis with more equality constraints.
+
+\hypertarget{selected-model-3}{%
+\section{Selected Model}\label{selected-model-3}}
+
+In the model we consider only the role of gender and mother attachment as fixed effects of \(\mu\). In the R formula syntax, we have
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# formula for p}
+\NormalTok{p }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+
+\CommentTok{\# formula for mu}
+\NormalTok{mu }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gender }\SpecialCharTok{+}\NormalTok{ mother }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{|}\NormalTok{ID\_class)}
+\end{Highlighting}
+\end{Shaded}
+
+Again, we specify the same prior distributions as before. The resulting prior settings are
+
+\begin{verbatim}
+##                   prior     class           coef    group resp dpar nlpar bound       source
+##            normal(0, 3)         b                                                       user
+##            normal(0, 3)         b        genderM                                (vectorized)
+##            normal(0, 3)         b  motherAnxious                                (vectorized)
+##            normal(0, 3)         b motherAvoidant                                (vectorized)
+##            normal(0, 3)         b  motherFearful                                (vectorized)
+##            normal(0, 3)         b                                zi             (vectorized)
+##            normal(0, 3)         b        genderM                 zi             (vectorized)
+##  student_t(3, 0.7, 2.5) Intercept                                                    default
+##          logistic(0, 1) Intercept                                zi                  default
+##    student_t(3, 0, 2.5)        sd                                                    default
+##    student_t(3, 0, 2.5)        sd                                zi                  default
+##    student_t(3, 0, 2.5)        sd                ID_class                       (vectorized)
+##    student_t(3, 0, 2.5)        sd      Intercept ID_class                       (vectorized)
+##    student_t(3, 0, 2.5)        sd                ID_class        zi             (vectorized)
+##    student_t(3, 0, 2.5)        sd      Intercept ID_class        zi             (vectorized)
+##       gamma(0.01, 0.01)     shape                                                    default
+\end{verbatim}
+
+The model is estimated using 6 independent chains with 6,000 iterations (warm-up 2,000). The model summary is presented below.
+
+\begin{verbatim}
+##  Family: zero_inflated_negbinomial 
+##   Links: mu = log; shape = identity; zi = logit 
+## Formula: internalizing_sum ~ gender + mother + (1 | ID_class) 
+##          zi ~ gender + (1 | ID_class)
+##    Data: data (Number of observations: 847) 
+## Samples: 6 chains, each with iter = 6000; warmup = 2000; thin = 1;
+##          total post-warmup samples = 24000
+## 
+## Group-Level Effects: 
+## ~ID_class (Number of levels: 50) 
+##                  Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## sd(Intercept)        0.43      0.08     0.29     0.61 1.00     5203    10756
+## sd(zi_Intercept)     2.18      0.53     1.35     3.43 1.00    11849    14075
+## 
+## Population-Level Effects: 
+##                Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## Intercept          0.88      0.11     0.66     1.10 1.00     9744    13174
+## zi_Intercept      -2.82      0.65    -4.33    -1.78 1.00    11781    12633
+## genderM            0.07      0.07    -0.07     0.21 1.00    36050    19093
+## motherAnxious      0.29      0.09     0.11     0.46 1.00    26032    19760
+## motherAvoidant     0.12      0.10    -0.07     0.31 1.00    29724    20101
+## motherFearful      0.48      0.12     0.25     0.71 1.00    26736    20112
+## zi_genderM        -0.29      0.39    -1.06     0.46 1.00    28148    18297
+## 
+## Family Specific Parameters: 
+##       Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
+## shape     2.53      0.33     1.95     3.25 1.00    21936    18166
+## 
+## Samples were drawn using sampling(NUTS). For each parameter, Bulk_ESS
+## and Tail_ESS are effective sample size measures, and Rhat is the potential
+## scale reduction factor on split chains (at convergence, Rhat = 1).
+\end{verbatim}
+
+Marginal effects are presented in Figure\textasciitilde\ref{fig:plot-marginal-int} and differences between mother attachment patterns are reported in Figure\textasciitilde\ref{fig:plot-diff-int}.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.95\linewidth]{attachment-bayes-factor_files/figure-latex/plot-marginal-int-1}
+
+}
+
+\caption{Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$).}\label{fig:plot-marginal-int}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-diff-int-1}
+
+}
+
+\caption{Predicted differences between mother attachment patterns ($n_{subj} = 847$).}\label{fig:plot-diff-int}
+\end{figure}
+
+Overall, results indicate that Fearful, and Anxious children have more problems than Secure children.
+Moreover, Fearful children have more problems than Avoidant children.
+Finally, also the difference between Avoidant and Anxious children is close to the threshold.
+
+To evaluate the fit of the model to the data, we computed the \emph{Bayesian} \(R^2\) and using the function \texttt{brms::bayes\_R2()}, and we present Posterior Predictions in Figure\textasciitilde\ref{fig:plot-ppcheck-int}.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{r2\_int}
+\DocumentationTok{\#\#     Estimate  Est.Error      Q2.5    Q97.5}
+\DocumentationTok{\#\# R2 0.2224337 0.02977471 0.1651088 0.281678}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}
+
+{\centering \includegraphics{attachment-bayes-factor_files/figure-latex/plot-ppcheck-int-1}
+
+}
+
+\caption{Posterior predictive check ($n_{subj} = 847$).}\label{fig:plot-ppcheck-int}
+\end{figure}
+
+We can see that the actual variance explained by fixed effects and random effect is around 22\%. Moreover, posterior predictive check indicates a good fit to the data.
+
+\hypertarget{conclusions-5}{%
+\subsubsection*{Conclusions}\label{conclusions-5}}
+\addcontentsline{toc}{subsubsection}{Conclusions}
+
+Considering attachment theoretical perspectives, results indicate only the role of mother attachment so we can support the Monotropy Theory.
+
+\hypertarget{conclusion-int}{%
+\chapter{Conclusions}\label{conclusion-int}}
+
+Overall, we obtained consistent results from the three different approaches: only mother attachment influence children's externalizing problems.
+In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems.
+Compared to externalizing problems, however, difference between attachment groups are less pronounced.
+Taken together, these results support the Monotropy Theory.
 

### 2021-10-04 Documents/Paper/paper.Rnw
corrige trackdown first round
update heeader info with correct orcid number

%%
%% This is file `./samples/longsample.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% apa7.dtx  (with options: `longsample')
%% ----------------------------------------------------------------------
%%
%% apa7 - A LaTeX class for formatting documents in compliance with the
%% American Psychological Association's Publication Manual, 7th edition
%%
%% Copyright (C) 2019 by Daniel A. Weiss <daniel.weiss.led at gmail.com>
%%
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%%
%% http://www.latex-project.org/lppl.txt
%%
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%%
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%%
%% ----------------------------------------------------------------------
%%
\documentclass[man, floatsintext]{apa7}

\usepackage{lipsum}

\usepackage[american]{babel}

% KabelExtra packages
\usepackage{booktabs} %
\usepackage{longtable} %
\usepackage{array} %
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float} %
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\usepackage{amsmath}
\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{../Biblio-attachment.bib}

%----    LaTeX Settings    ----%
% \usepackage{setspace} % linee spacing
\newcommand{\codespacing}{\linespread{1}}
\newcommand{\doublespacing}{\linespread{1.655}}

\setcounter{secnumdepth}{3} % Show section number
%----

\title{Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach}
\shorttitle{The Bayes Factor Encompassing Prior Approach}

\author{Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, Gianmarco Altoè}
\affiliation{UNIPD}

\leftheader{loook}

\abstract{When conducting a study, researchers usually have expectations based on hypotheses or theoretical perspectives they want to evaluate. Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called “\textit{informative hypotheses}”. However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are unsuitable for testing complex informative hypotheses. An alternative approach is to use the Bayes Factor. In particular, the Bayes Factor based on the “\textit{encompassing prior approach}” allows researchers to easily evaluate complex informative hypotheses. In this paper we provide a clear and detailed introduction to this approach. We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor following the encompassing prior approach. Subsequently, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social-emotional development.}

\keywords{keyword-1, keyword-2}

\authornote{
   \addORCIDlink{Claudio Zandonella Callegher}{0000-0001-7721-6318}

  Correspondence concerning this article should be addressed to Claudio Zandonella Callegher, Department of Developmental Psychology and Socialisation, University of Padua, Via Venezia, 8 - 35131 Padova, Italy.  E-mail: claudiozandonella@gmail.com}

<<settings, echo=FALSE, message=FALSE>>=
library(kableExtra)
library(ggplot2)

# Chunks settings
knitr::opts_chunk$set(echo = FALSE,
                      # Plot settings
                      dev = "tikz", dev.args=list(pointsize=12),fig.align='center',
                      fig.height=3, fig.width=5, fig.pos = "!ht",

                      # Code output width
                      tidy=TRUE, tidy.opts = list(width.cutoff = 80),
                      # comment = NA, prompt = TRUE

                      # Cache options
                      cache = FALSE, autodep=TRUE)

# Console output width
options(width = 80)

# Chunk theme
thm=knit_theme$get("bclear")
knitr::knit_theme$set(thm)
knitr::opts_chunk$set(background = c(.98, .98, 1))

# Option KableExtra
# options(knitr.kable.NA = '')

## ggplot settings
theme_set(theme_classic()+
            theme(text = element_text(size=12)))

devtools::load_all("../../")
source("../Utils_report.R")

#----    load drake    ----

drake_load_paper()
@

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

When conducting a study, researchers usually have expectations based on hypotheses or theoretical perspectives they want to evaluate according to the observed data. In fact, the evaluation of research and theoretical hypotheses is one of the principal goals of empirical research.

In psychology, the dominant statistical approach to evaluate research hypotheses is the Null Hypothesis Significance Testing (NHST). In the literature, however, the utility and validity of NHST are largely debated \parencite{wassersteinMovingWorld052019}. This approach presents indeed several limitations. First, the NHST places a narrow focus on statistical testing rather than on the formalization of hypotheses. This has usually led researchers to evaluate data against the catch-all null-hypothesis that nothing is going on rather than testing their specific expectation [and the alternative hypothesis is rarely formalized]. Second, the p-value does not quantify the evidence in favour of one hypothesis, thus, it is not possible to \textit{“accept”} a hypothesis but only to \textit{“reject”} it. This is inconvenient as, in case of not significant results, the researchers are left in a state of indecision. Third, NHST does not allow testing multiple hypotheses at the same time. Using the NHST the null hypothesis is tested only against a single alternative. Fourth, NHST is unsuitable for testing broad classes of hypotheses with equality and inequality constraints \parencite{mulderSimpleBayesianTesting2019}. Expectations can be evaluated using one-side tests, however, when more groups or more variables are involved, it is not possible to evaluate complex parameter constraints that reflect researchers' expectations \parencite{vandeschootIntroductionBayesianModel2011}.

Model comparison is a different approach that allows researchers to compare multiple hypotheses and identify which is the most supported by the data \parencite{mcelreathStatisticalRethinkingBayesian2020}. Hypotheses are first formalized as statistical models according to researchers expectations or theoretical perspectives. Subsequently, it is possible to evaluate which is the most supported model among those considered according to the data. To do that a popular approach is to use information criteria such as the AIC or BIC criteria that estimate models ability to predict new data \parencite{wagenmakersAICModelSelection2004,akaike1973a, schwarzEstimatingDimensionModel1978}. Model comparison has several advantages and, in particular, it allows to directly compute the relative plausibility of each model given the data and the set of models considered. Model comparison using the information criteria, however, is not appropriate to evaluate hypotheses that include complex parameter constraints reflecting researchers' expectations. In fact, information criteria evaluate models complexity according to the number of parameters, but they do not take into account possible order constraints on the parameters.

An alternative criterium to evaluate research hypotheses in a model comparison is the Bayes Factor. In the last 25 years, there has been an increasing interest in the Bayes Factor and its use has been proposed as the solution to the critical issues of the NHST \parencite{heckReviewApplicationsBayes2020, mulderEditorsIntroductionSpecial2016}. Although it has its own limitations and it does not solve the fundamental issues of the misuse of statistical techniques \parencite{schadWorkflowTechniquesRobust2021, gelmanBayesianDataAnalysis2013}, the Bayes Factor offers some clear advantages. In particular, the Bayes Factor allows us to compare hypotheses obtaining a relative index of evidence, like the information criteria, but it also allows us to easily compare complex research hypotheses. In fact, so-called \textit{“informative hypotheses”} (i.e., hypotheses containing information about the ordering of the model parameters) can be formalized according to researchers' expectations or theoretical perspectives using equality and inequality constraints \parencite{vandeschootIntroductionBayesianModel2011}. Subsequently, these hypotheses can be compared against each other using the Bayes Factor.

The evaluation of informative hypotheses is of particular interest to the researchers as it allows them to directly assess specific complex expectations and theoretical perspectives. In the literature, a particular approach allowing to easily compute the Bayes Factor with complex informative hypotheses has received increasing attention: \textit{“the Bayes Factor with encompassing prior”}. \textcite{vandeschootIntroductionBayesianModel2011} presented a general introduction to informative hypotheses testing using the Bayes Factor with the encompassing prior approach, whereas \textcite{hoijtinkInformativeHypothesesTheory2012} offered a more detailed description of the development of this method. Other studies, instead, considered the application of this approach with specific statistical models; for example: mixed effect models \parencite{katoBayesianApproachInequality2006}, evaluation of correlation coefficients \parencite{mulderBayesFactorsTesting2016} and multinomial models \parencite{heckMultinomialModelsLinear2019}. In addition, \textcite{guBayesianEvaluationInequality2014} proposed a general approximate procedure to evaluate inequality constraints in a wide range of statistical models.

All studies mentioned above, however, considered only informative hypotheses with inequality constraints. Evaluating in the same hypothesis equality and inequality constraints, instead, it was no possible and equality constraints had to be approximate to “\textit{about equality constraints}” (i.e., a equality constraints of type $\theta_i = \theta_j$ is approximated to $|\theta_i - \theta_j| < \xi$ for a value of $\xi$ small enough).

Only recently, \textcite{guApproximatedAdjustedFractional2018} introduced an approximate procedure to evaluate both equality and inequality constraints using the Bayes Factor with the encompassing prior approach in a wide range of statistical models (i.e., generalized linear mixed models and structural equation models). Subsequently, this approach was extended by \textcite{mulderBayesFactorTesting2019} to generalized multivariate probit models and, finally, \textcite{mulderSimpleBayesianTesting2019} proposed an accurate procedure (i.e., not based on an approximation) that allows testing informative hypotheses with equality and inequality constraints in linear regression models.

The development and implementation of this approach are of particular interest because, although with its limits, it allows researchers to directly evaluate their expectations and hypotheses. The available literature, however, is rather technical. The complexity of these articles makes it difficult for researchers not familiar with this approach to clearly understand all the steps involved. On the other hand, articles offering a general introduction to the Bayes Factor do not provide enough details to allow readers to autonomously apply this method to their problems, but they usually rely on ad-hoc solutions implemented in some statistical software.

The aim of this paper, therefore, is to offer a clear and detailed description of the Bayes Factor with the encompassing prior approach to allow other researchers to apply this approach in their studies. In particular, we refer to the approximated method proposed by \textcite{guApproximatedAdjustedFractional2018} as it applies to a wider range of conditions than the more accurate approach proposed by \textcite{mulderSimpleBayesianTesting2019}. The paper is organized as follows. First, the method is introduced providing a detailed description of all steps and elements involved in the formalization of informative hypotheses and Bayes Factor computation. Subsequently, an application of the method to real data is presented to offer the opportunity to discuss the typical issues encountered in real complex scenarios.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Bayes Factor for Informative Hypothesis Testing}

The evaluation of informative hypotheses with equality and/or inequality constraints involves several steps and elements. In this section, first, we describe how to formulate informative hypotheses. Subsequently, we introduce the Bayes Factor considering the encompassing prior approach based on the approximated method proposed by \textcite{guApproximatedAdjustedFractional2018}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Formulation of Informative Hypothesis}\label{sec:informative-hypothesis}

Informative hypotheses can be defined according to researchers' expectation, evidence from the literature or theoretical perspectives and they are formed by equality and/or inequality constraints on certain model parameters. These constraints are obtained as a linear combination of certain parameters and eventual constant values. For example, it is possible to state that two parameters are equal ($\theta_i = \theta_j$), one parameter is greater than another ($\theta_i > \theta_j$), or express other complex conditions as the difference between two parameter is less than a given value ($\theta_i - \theta_j < .5$; $2\times\theta_i - \theta_j < .1 \times \sigma$).

Thus, an informative hypothesis $H_i$ with equality and inequality constraints can be expressed in the form
\begin{equation}
H_i:\ \ R_E\bm{\theta} = r_E \ ~ \ \& \ ~ \ R_I\bm{\theta} > r_I,
\end{equation}
where $R_E$ is a matrix expressing the equality constraints and $r_E$ is a vector containing the constant values of the equality constraints. Whereas, $R_I$ is a matrix expressing the inequality constraints and $r_E$ is a vector containing the constant values of the inequality constraints. Finally, $\bm{\theta}$ is a vector with the model parameters involved in the constraints.

As an example, consider a study evaluating the efficacy of a new psychological treatment that is supposed to improve a given cognitive ability. In the study, a control group receiving no treatment and another group receiving the traditional treatment were included as a comparison. Moreover, imagine that the new psychological treatment was administered in three different modalities to different groups: individually, in-group, and online. Researchers expect no differences between the three modalities but they hypothesize that the new treatment will perform better than the traditional one and this, in turn, will be better than the no-treatment control condition. We can express this hypothesis as
\begin{equation}
H_i:\ \ \theta_{control}< \theta_{traditional} < \theta_{individual} = \theta_{group} = \theta_{online},
\end{equation}
were $\theta_{control}$ is the parameter estimating the average score of the no-treatment control group, $\theta_{traditional}$ is the parameter estimating the average score of the group receiving the traditional treatment, and $\theta_{individual}$, $\theta_{group}$, and $\theta_{online}$ are the parameters estimating the average scores of the groups receiving the new treatment individually, in group, and on-line, respectively. The corresponding formulation of the hypothesis using the matrix notation introduced before is
\begin{equation}
\begin{aligned}
H_i: &\\
& R_E\bm{\theta} =
\begin{bmatrix}
0 & 0 & 1 & -1 & 0\\
0 & 0 & 0 & 1 & -1
\end{bmatrix}        \begin{bmatrix} \theta_{control} \\ \theta_{traditional} \\ \theta_{individual} \\ \theta_{group} \\ \theta_{online}\end{bmatrix} = \begin{bmatrix} 0 \\ 0\end{bmatrix} = r_E,\\~\\
& R_I\bm{\theta} =
\begin{bmatrix}
-1 & 1 & 0 & 0 & 0\\
0 & -1 & 1 & 0 & 0
\end{bmatrix}        \begin{bmatrix} \theta_{control} \\ \theta_{traditional} \\ \theta_{individual} \\ \theta_{group} \\ \theta_{online}\end{bmatrix} > \begin{bmatrix} 0 \\ 0\end{bmatrix} = r_I.
\end{aligned}
\end{equation}
Note how each row of $R_E$ and $R_I$ matrices expresses an equality or an inequality constraint, respectively. For example, in the first row of $R_E$ we have $\theta_{individual} - \theta_{group} = 0$ (i.e., $\theta_{individual} = \theta_{group}$) and in the first row of $R_I$ we have $\theta_{traditional} - \theta_{control} > 0$ (i.e., $\theta_{traditional} > \theta_{control}$).

Now that we have understood how to define an informative hypothesis with equality and inequality constraints introducing an appropriate notation, let's see how to evaluate an informative hypothesis using the Bayes Factor with the encompassing prior approach.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Bayes Factor}

The Bayes Factor of hypothesis $H_1$ against a competing hypothesis $H_2$ is defined as the ratio between the marginal likelihoods of the two hypotheses:
\begin{equation}
BF_{12} = \frac{Pr(Y|H_1)}{Pr(Y|H_2)} = \frac{\int l(Y|\theta_1, H_1) \pi(\theta_1| H_1)\,d\theta_1}{\int l(Y|\theta_2, H_2) \pi(\theta_2| H_2)\,d\theta_2},
\end{equation}
where $Y$ indicates the data, $\theta_i$ is the vector of parameters under the hypothesis $H_i$, $l(Y|\theta_i, , H_i)$ is the likelihood function under the hypothesis $H_i$, and $\pi(\theta_i| H_i)$ is the prior of the parameters under the hypothesis $H_i$. The marginal likelihood $Pr(Y|H_i)$ can be interpreted as a measure of the plausibility of the data under $H_i$.

Therefore, the Bayes Factor $BF_{12}$ quantifies the relative support of the data for the two competing hypotheses (and not the ratio between the probability of the two hypotheses). For values close to 1, the Bayes Factor indicates that $H_1$ and $H_2$ have similar support from the data. Larger values indicate evidence in favour of $H_1$, whereas values close to 0 indicate evidence in favour of $H_2$. The ratio between the posterior probabilities of the two hypotheses can be computed as
\begin{equation}
\frac{Pr(H_1|Y)}{Pr(H_2|Y)} = \overbrace{\frac{Pr(Y|H_1)}{Pr(Y|H_2)}}^{BF_{12}} \times \frac{Pr(H_1)}{Pr(H_2)},
\end{equation}
where $Pr(H_i)$ is the prior probability of $H_i$ and $Pr(H_i|Y)$ is the posterior probability of $H_i$. For a detailed description of the Bayes Factor considering also its interpretation and application in different contexts see \textcite{wagenmakersBayesianHypothesisTesting2010, mulderEditorsIntroductionSpecial2016, heckReviewApplicationsBayes2020}.

Note that to compute the marginal likelihood $Pr(Y|H_i)$ of a hypothesis $H_i$ it is necessary to integrate the product between the likelihood and the prior. These integrals, however, are usually difficult to compute [in particular when hypotheses include order constraints]. In the case of hypotheses with equality and inequality constraints, however, it is possible to simplify the computation of the Bayes Factor using the encompassing prior approach.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Encompassing Prior Approach}

The basic idea of the encompassing prior approach is to consider an informative hypothesis as a subset of the parameter space of an unconstrained model. Thus, to evaluate the plausibility of a hypothesis we can consider the proportion of parameter space of the unconstrained model that satisfies the constraints. More specifically, given an informative hypothesis $H_i$ and an unconstrained model $H_u$ (or \textit{encompassing model}) that does not contain any constraints on the parameters, if the prior under $H_i$ is defined as a truncation of the proper prior under $H_u$ (\textit{encompassing prior}) according to the constraints, then the Bayes Factor between $H_i$ and $H_u$ can be written as
\begin{equation}\label{eq:BF-encompassing}
\begin{aligned}
BF_{iu} &= \frac{Pr(\text{Inequality Const|Equality Const, Data, } H_u)}{\pi(\text{Inequality Const|Equality Const, } H_u)} \times \frac{Pr(\text{Equality Const|Data, } H_u)}{\pi(\text{Equality Const}|H_u)} \\ ~\\
&= \frac{Pr(R_I\theta > r_I | R_E\theta =r_E, Y, H_u)}{\pi(R_I\theta > r_I | R_E\theta =r_E, H_u)} \times \frac{Pr(R_E\theta =r_E| Y, H_u)}{\pi(R_E\theta =r_E| H_u)}.
\end{aligned}
\end{equation}

The first term is the ratio between the conditional posterior probability and the conditional prior probability that the inequality constraints hold under the unconstrained model $H_u$ given the equality constraints. The second term is the ratio between marginal posterior density and the marginal prior density of the equality constraints under $H_u$ \parencite[the well-known Savage–Dickey density ratio; ][]{dickeyWeightedLikelihoodRatio1971, wetzelsEncompassingPriorGeneralization2010}. In particular, the four elements can be interpreted as:
\begin{itemize}
  \item{The \textbf{conditional posterior probability} $Pr(R_I\theta > r_I | R_E\theta =r_E, Y, H_u)$ is a measure of the fit of the inequality constraints of $H_i$ under $H_u$.}
  \item{The \textbf{conditional prior probability} $\pi(R_I\theta > r_I | R_E\theta =r_E, H_u)$ is a measure of the complexity of the inequality constraints of $H_i$ under $H_u$.}
  \item{The \textbf{marginal posterior density} $Pr(R_E\theta =r_E| Y, H_u)$ is a measure of the fit of the equality constraints of $H_i$ under $H_u$.}
  \item{The \textbf{marginal prior density} $\pi(R_E\theta =r_E| H_u)$ is a measure of the complexity of the equality constraints of $H_i$ under $H_u$.}
\end{itemize}
Summarizing at the denominators we have measures of the \textbf{complexity} of the inequality and equality constraints of the informative hypothesis $H_i$; at the numerators, instead, we have measures of the \textbf{fit} of the data to the inequality and equality constraints of the informative hypothesis $H_i$. Thus, if the hypothesis $H_i$, although applying constraints to the parametric space (less complexity), is still able to provide a good description of the data, the Bayes Factor will favour $H_i$. On the contrary, if the support of the data is poor, the Bayes Factor will favour the unconstrained model $H_u$.

The proof of the formulation of the Bayes Factor with the encompassing prior approach and the evaluation of its consistency (i.e., the probability of selecting the correct hypothesis goes to 1 for the sample size going to infinity) is provided in \textcite{guApproximatedAdjustedFractional2018, mulderBayesFactorTesting2019}. Note that slightly different notation is used here to enhance comprehension and underline that at the numerators we have values computed from the posterior of $H_u$, whereas at the denominators we have values computed from the prior of $H_u$.

To compute the Bayes Factor with the encompassing prior approach, only the prior and the posterior of the unconstrained model are required. To obtain them, first, we need to define the encompassing prior of the unconstrained model.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Definition of the Encompassing Prior}

Prior specification is an important element as the resulting Bayes Factor value is affected by the prior choice. This aspect is particularly relevant in the case of equality constraints \parencite{lindleyStatisticalParadox1957, bartlettCommentLindleyStatistical1957}, whereas inequality constraints are not affected as long as the prior is symmetric and centred to the focal point of interest (this aspect will be further discussed in Section~\ref{sec:adj-prior}).

To avoid arbitrary prior specification, different methods have been proposed in the literature. For example: Jeffreys-Zellner-Siow (JZS) objective priors do not require subjective specification \parencite{jeffreysTheoryProbability1961,zellnerPosteriorOddsRatios1980, bayarriExtendingConventionalPriors2007}; partial Bayes Factor \parencite{desantisMethodsDefaultRobust1999} defines the prior according to part of the data, whereas the remaining part is used to compute the Bayes Factor; intrinsic Bayes Factor \parencite{bergerIntrinsicBayesFactor1996} and fractional Bayes Factor \parencite{ohaganFractionalBayesFactors1995} are a variation of the partial Bayes Factor where priors are defined according to the average of all possible minimal subsets of the data or to a given small fraction of the data, respectively.

Both, \textcite{guApproximatedAdjustedFractional2018, mulderSimpleBayesianTesting2019} based their approach on the fractional Bayes Factor. Starting from a non-informative prior, a minimal fraction of the data is used to obtain a posterior that is subsequently used as proper prior, we refer to it as \textit{fractional prior} (have you ever heard Lindley's \citeyear{lindleyBayesianStatisticsReview1972} famous quote \textit{“Today’s posterior is tomorrow’s prior”}?). The remaining part of the data is used to compute the Bayes Factor. The two approaches, however, have an important difference. \textcite{guApproximatedAdjustedFractional2018} approximated the obtained fractional prior (as well as the posterior, see Section~\ref{sec:posterior-encompassing}) to a (multivariate) normal distribution. In fact, due to large-sample theory \parencite{gelmanBayesianDataAnalysis2013}, parameter posterior distribution can be approximated to a (multivariate) normal distribution. On the contrary, \textcite{mulderSimpleBayesianTesting2019} provided an analytic solution in the case of linear regression models, obtaining an accurate quantification of the distribution.

All methods discussed above suggest objective procedures to avoid arbitrary prior specification. Nevertheless, using subjective (reasonable) priors according to previous information or experts' indications is still a possible approach. Keep in mind, however, that prior specification (even if obtained through an \textit{objective procedure}) affects the Bayes Factor results. Thus, it is fundamental to conduct a prior sensitivity analysis to evaluate the influence of prior specification on the results \parencite{schadWorkflowTechniquesRobust2021, duBayesFactorOnesample2019}.

Going back to our psychological treatment example, we could use independent normal distributions to specify the prior of each parameter of interest (i.e. $\theta_{control}$, $\theta_{traditional}$, $\theta_{individual}$, $\theta_{group}$, and $\theta_{online}$) obtaining as resulting prior a multivariate normal distribution with mean vector $\mu_{\theta}$ and covariance matrix $\Sigma_{\theta}$. In this way, we can still follow the approach proposed by \textcite{guApproximatedAdjustedFractional2018}, based on normal approximation, that will simplify the computation of the Bayes Factor. For example, suppose that, according to experts' indications, a reasonable prior choice for all parameters of interest is a normal distribution with mean zero and standard deviation 2:  $\mathcal{N}(0,2)$. The resulting prior is a multivariate normal distribution with mean vector $\mu_{\theta}$ and covariance matrix $\Sigma_{\theta}$:
\begin{equation}
\begin{gathered}
\pi(\bm{\theta})\sim \mathcal{N}(\mu_{\theta}, \Sigma_{\theta})\\~\\
\text{where  }\ \bm{\theta} = \begin{bmatrix}
0 \\ 0 \\ 0 \\ 0 \\ 0
\end{bmatrix} \ \ \text{and  } \ \
\Sigma_{\theta} = \begin{bmatrix}
4 & 0 & 0 & 0 & 0\\
0 & 4 & 0 & 0 & 0\\
0 & 0 & 4 & 0 & 0\\
0 & 0 & 0 & 4 & 0\\
0 & 0 & 0 & 0 & 4
\end{bmatrix}.
\end{gathered}
\end{equation}

At this point, several authors underline the importance of centring the prior distribution on the constraints points of interest. Let's further discuss this issue in the next section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adjusting Prior Mean}\label{sec:adj-prior}

When evaluating informative hypotheses with equality and inequality constraints using the Bayes Factor, the priors have to be centred on the focal points of interests  \parencite{zellnerPosteriorOddsRatios1980, jeffreysTheoryProbability1961, mulderPriorAdjustedDefault2014}. In the case of equality constraints, centring the prior allows one to consider values close to the point of interest more likely a priori than distant values. This should be in line with researchers' expectations, otherwise one could question why testing that value.

In the case of inequality constraints, instead, this adjustment is done to guarantee that no constraint is favoured a priori. Consider the example represented in Figure~\ref{fig:plot-prior-adj} where the hypothesis $\theta_i > k$ is evaluated against $\theta_i < k$. Remember that, when computing the Bayes Factor, the prior probability that the constraint holds is used as a measure of the complexity of the hypothesis. Thus, if the prior is not centred on the focal point of interest (i.e., $k$), the less complex hypothesis (i.e., $\theta_i > k$ ) will be erroneously preferred a priori over the other (i.e., $\theta_i < k$ ). Only by centring the prior on the focal point, the hypotheses will be equally likely a priori.

<<plot-prior-adj, cache=TRUE, fig.cap="Example of non centered prior considering the constraints $\\theta_i > k$ vs. $\\theta_i < k$.">>=
plot_prior_adj()
@

Centering the prior to the focal point, however, can be difficult in the case of complex hypotheses where constraints are defined as a linear combination of several parameters. To overcome this issue, \textcite{guApproximatedAdjustedFractional2018} proposed the following transformation of the parameters of interest:
\begin{equation} \label{eq:param-transf}
\begin{aligned}
\bm{\beta} = &R\bm{\theta}-r\\~\\
\text{with  } \bm{\beta} = \begin{bmatrix}\beta_E\\\beta_I\end{bmatrix},\ R =& \begin{bmatrix}R_E\\R_I\end{bmatrix} \text{  and  } r = \begin{bmatrix}r_E\\r_I\end{bmatrix},
\end{aligned}
\end{equation}
where $\bm{\theta}$ is the vector of original parameters, $R$ is the matrix expressing equality and inequality constraints, and $r$ is the vector with the constants of the equality and inequality constraints. Doing this, the informative hypothesis under evaluation becomes:
\begin{equation}
H_i:\ \ \beta_E = 0 \ ~ \ \& \ ~ \ \beta_I > 0.
\end{equation}

This parameter transformation has the advantage of simplifying the hypothesis expression without changing the original expectations. In fact, for example, evaluating $\theta_i > \theta_j$ is equivalent to evaluating $\beta_i = \theta_i - \theta_j > 0$. Thus, given the original prior $\pi(\bm{\theta})\sim\mathcal{N}(\mu_{\theta}, \Sigma_{\theta})$, the prior of the new parameter vector $\bm{\beta}$ is given by
\begin{equation}\label{eq:normal-transf}
\pi(\bm{\beta}) \sim \mathcal{N}(\mu_{\beta}, \Sigma_{\beta}) = \mathcal{N}(R\bm{\theta}-r, R\Sigma_{\theta}R^T).
\end{equation}

Note that this operation is nothing more than applying a linear transformation to the original multivariate normal distribution.\footnote{Given a multivariate normal distribution $Y\sim\mathcal{N}(\mu, \Sigma)$, the result of a linear transformation $AY + b$ is still a multivariate normal distribution with vector mean $\mu_{t}=AY+b$ and covariance matrix $\Sigma_{t} = A\Sigma A^T$.} In order to do that, however, the matrix $R$ must be \textit{full-row-rank} (i.e., all rows are linearly independent). If this is not the case, the obtained matrix $\Sigma_{\beta}$ will not be a proper covariance matrix. In Section~\ref{sec:rank-hypo}, we will discuss a solution to overcome this limit.

Now, to center the prior of $\bm{\beta}$ to the focal points, we can simply set the mean vector to zero. Thus, the adjusted prior of $\bm{\beta}$ is
\begin{equation}
\pi_{adj}(\bm{\beta}) \sim \mathcal{N}(\bm{0}, \Sigma_{\beta}) = \mathcal{N}(\bm{0}, R\Sigma_{\theta}R^T).
\end{equation}

Considering the psychological treatment example, the obtained adjusted prior is $\mathcal{N}(\bm{0}, \Sigma_{\beta})$ where:
\begin{equation}
\bm{0} =
\begin{bmatrix}
0 \\ 0 \\ 0 \\ 0
\end{bmatrix} \ ~ \ \text{  and  }\ ~ \
\Sigma_{\beta} = R\Sigma_{\theta}R^T = \begin{bmatrix}
8 & -4 & 0 & 4 \\
-4 & 8 & 0 & 0 \\
0 & 0 & 8 & -4 \\
4 & 0 & -4 & 8
\end{bmatrix}.
\end{equation}

So far we have defined the prior for the parameter vector $\bm{\theta}$ of the encompassing model. Moreover, we have obtained the adjusted prior for the new transformed parameter vector $\bm{\beta}$ that will allow us to properly evaluate the equality and inequality constraints. At this point, we need to compute the posterior of the encompassing model parameters.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Posterior Encompassing Model}\label{sec:posterior-encompassing}

Posterior distribution of the encompassing model parameters can be obtained through numerical approximation using Markov Chain Monte Carlo (MCMC) sampling algorithms, such as Metropolis–Hastings algorithm \parencite{hastingsMonteCarloSampling1970} or Gibbs sampling \parencite{gemanStochasticRelaxationGibbs1984}. Bayesian statistical inference methods are implemented in all major statistical software. In R statistical software \parencite{rcoreteamLanguageEnvironmentStatistical2021}, for example, the popular \texttt{brms} package \parencite{burknerBrmsPackageBayesian2017, burknerAdvancedBayesianMultilevel2018a}, which is based on STAN \parencite{standevelopmentteamRStanInterfaceStan2020}, allows to easily conduct Bayesian inference.

Following \textcite{guApproximatedAdjustedFractional2018} approach, once we obtain the model posterior, we can approximate it to a (multivariate) normal distribution. Thus, the resulting posterior distribution is
\begin{equation}
Pr(\bm{\theta}|Y) \sim \mathcal{N}(\hat{\bm{\theta}}, \hat{\Sigma}_{\theta})
\end{equation}
where posterior mean $\hat{\bm{\theta}}$ and posterior covariance $\hat{\Sigma}_{\theta}$ can be computed directly from the posterior draws. Next, we can obtain the posterior with respect to the vector parameters $\bm{\beta}$ applying the same transformation used for the prior distribution,
\begin{equation}
Pr(\bm{\beta}|Y) \sim \mathcal{N}(\hat{\bm{\beta}}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\bm{\theta}}-r, R\hat{\Sigma}_{\theta}R^T).
\end{equation}

At this point, we have both the prior and the posterior distributions of the parameters of interests of the encompassing model. Before proceeding, however, let's underline some important aspects.

When defining the prior, we adjusted the prior mean by centring it over the constraint focal points. This change would slightly influence the resulting posterior as well. However, as underlined by \textcite{guApproximatedAdjustedFractional2018}, small prior changes will result in negligible changes on the posterior for large samples due to large-sample theory. For this reason, the authors do not adjust the posterior in their approach, but only the prior. Therefore, when computing the posterior we can simply consider the prior $\pi(\bm{\theta})\sim \mathcal{N}(\mu_{\theta}, \Sigma_{\theta})$ defined at the beginning, without worrying about adjusting it.

In addition, note that, in \textcite{guApproximatedAdjustedFractional2018} original approach, the posterior mean $\hat{\bm{\theta}}$ and the posterior covariance $\hat{\Sigma_{\theta}}$ are not obtained from the posterior draws but they are computed directly from the sample data using the maximum likelihood estimate and the inverse of the Fisher information matrix, respectively. This has the advantage of being faster (posterior draws are not required) but it may be not possible for some complex models.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Computing the Bayes Factor}\label{sec:compute-bf}

In the previous section we obtained the adjusted prior and the posterior of the vector of transformed parameters $\bm{\beta}$, respectively
\begin{equation}
\pi_{adj}(\bm{\beta}) \sim \mathcal{N}(0, \Sigma_{\beta}) \ \ \text{and} \ \
Pr(\bm{\beta}|Y) \sim \mathcal{N}(\hat{\bm{\beta}}, \hat{\Sigma}_{\beta}).
\end{equation}

Given the parameter transformation from $\bm{\theta}$ to $\bm{\beta}$, we can rewrite the Formula~\ref{eq:BF-encompassing} of the Bayes Factor between $H_i$ and $H_u$ as follow,
\begin{equation}
BF_{iu} = \frac{Pr(\beta_I > 0 | \beta_E = 0, Y, H_u)}{\pi_{adj}(\beta_I > 0 | \beta_E =0, H_u)} \times \frac{Pr(\beta_E =0| Y, H_u)}{\pi_{adj}(\beta_E =0| H_u)},
\end{equation}
where $\beta_I$ and $\beta_E$ are defined in Formula~\ref{eq:param-transf} and represent the inequality and equality constraints, respectively.

Now, thanks to (multivariate) normal distribution approximation, we can easily compute the required conditional probabilities and marginal densities required to calculate the Bayes Factor.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Marginal Density}

The marginal distribution of a subset of variables of a multivariate normal distribution is obtained simply discarding the variables to marginalize out. For example, given the adjusted prior of the psychological treatment example, $\pi_{adj}(\bm{\beta}) \sim \mathcal{N}(\bm{0}, \Sigma_{\beta})$ where
\begin{equation}
\bm{0} =
\begin{bmatrix}
0 \\ 0 \\ 0 \\ 0
\end{bmatrix} \ ~ \ \text{  and  }\ ~ \
\Sigma_{\beta} = \begin{bmatrix}
8 & -4 & 0 & 4 \\
-4 & 8 & 0 & 0 \\
0 & 0 & 8 & -4 \\
4 & 0 & -4 & 8
\end{bmatrix},
\end{equation}
the marginal distribution of the equality constraints $\bm{\beta}_E$ is
\begin{equation}
\begin{gathered}
\pi_{adj}(\bm{\beta}_E) \sim \mathcal{N}(\mu_{\beta_E}, \Sigma_{\beta_E}),\\~\\
\text{where  }\ \mu_{\beta_E} = \begin{bmatrix}
0 \\ 0
\end{bmatrix} \ \ \text{and  } \ \
\Sigma_{\beta_E} = \begin{bmatrix}
8 & -4 \\
-4 & 8
\end{bmatrix}.
\end{gathered}
\end{equation}

At this point computing the density at $\beta_E = 0$ is elementary. In R, this can be done using the  \texttt{dmvnorm()} function from the \texttt{mvtnorm} package \parencite{genzMvtnormMultivariateNormal2021}. To compute the \textbf{marginal prior density} $\pi_{adj}(\beta_E =0| H_u)$ of the psychological treatment example, we can use the following code:
\codespacing
<<marginal-density, echo = TRUE, cache=TRUE>>=
# Prior info
mu_prior <- c(0, 0, 0, 0)
Sigma_prior <- matrix(c( 8,-4, 0, 4,
                        -4, 8, 0, 0,
                         0, 0, 8,-4,
                         4, 0,-4, 8), ncol = 4, byrow = TRUE)

# Marginal prior density at beta_1 = 0 and beta_2 = 0
mvtnorm::dmvnorm(x = c(0, 0),
                 mean = mu_prior[1:2],
                 sigma = Sigma_prior[1:2, 1:2])

@
\doublespacing

Analogously, it is possible to compute the \textbf{marginal posterior density} $\pi_{adj}(\beta_E =0| Y, H_u)$ considering this time the estimated posterior mean vector $\bm{\hat{\beta}}$ and the estimated  posterior covariance matrix $\hat{\Sigma}_{\beta}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Conditional Probability}

To compute the conditional probability of the inequality constraints given the equality constraints in a multivariate normal distribution, we can use the \texttt{pcmvnorm()} function from the \texttt{condMVNorm} R-package \parencite{varadhanCondMVNormConditionalMultivariate2020}. Considering the psychological treatment example, to calculate the \textbf{conditional prior probability} $\pi_{adj}(\beta_I > 0 | \beta_E =0, H_u)$ we can run the following code:
\codespacing
<<conditional-prob, echo = TRUE, cache=TRUE>>=
# Conditional prior probability that beta_3 > 0 and beta_4 > 0
# given beta_1 = 0 and beta_2 = 0
condMVNorm::pcmvnorm(
    lower = c(0, 0), upper = c(Inf, Inf), # inequality constraints
    mean = mu_prior, sigma = Sigma_prior,
    dependent.ind = 3:4,                  # inequality variables
    given.ind = 1:2, X.given = c(0, 0))   # equality variables and constraints

@
\doublespacing

Analogously, it is possible to compute the \textbf{conditional posterior probability} $\pi_{adj}(\beta_I > 0 | \beta_E =0, Y, H_u)$ considering this time the estimated posterior mean vector $\bm{\hat{\beta}}$ and the estimated posterior covariance matrix $\hat{\Sigma}_{\beta}$.

At this point, we have all the elements required and we can easily compute the Bayes Factor $BF_{iu}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Advanced Elements}

In the previous sections, we have described in detail all the steps and elements required to evaluate informative hypotheses using the Bayes Factor with the encompassing prior approach following the approximated method proposed by \textcite{guApproximatedAdjustedFractional2018}. As already highlighted, however, compared to \textcite{guApproximatedAdjustedFractional2018} original approach, we took a slightly different path in the prior definition and posterior approximation. Instead of using the fractional prior method, we defined subjective (reasonable) priors and we relied on posterior draws instead of maximum likelihood estimates to approximate the posterior. These choices were done to follow the usual Bayesian workflow in data analysis \parencite{gelmanBayesianWorkflow2020, schadPrincipledBayesianWorkflow2021}.

Before moving to an applied example, however, we consider some more advanced aspects that are important to take into account when applying this method. In particular, we discuss issues related to parameters standardization, range constraints, hypothesis matrix rank, comparable hypotheses, and bounded parameter space.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Parameters Standardization}\label{sec:param-standard}

When evaluating informative hypotheses, it may be necessary to standardize the parameters of interest. As described by \textcite{guApproximatedAdjustedFractional2018}, parameters have to be standardized when comparing regression coefficients of continuous variables that are measured on different scales. In these cases, in fact, evaluating if $\theta_i>\theta_j$ is affected by the scale of the two variables. Standardizing the parameters allows us to correctly compare the two parameters. On the contrary, standardizing the parameters is not necessary if they are compared to constants (i.e., $\theta > 3$) or if they represent group means, such as the case of categorical variables.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Range Constraints}

It is possible to express range constraints such as $0<\theta_i<1$ in which the parameter is constrained between two values. These constraints can be expressed as the combination of two constraints. For example, the previous hypothesis is equivalent to $\beta_1 = \theta_i>0$ and $\beta_2 = 1 - \theta_i > 0$. However, adjusting the prior mean in the case of range constraints would require to centre the prior on the middle of the range space \parencite{mulderBIEMSFortran902012}. Thus, in the previous example we would set $\mu_{\beta_1} = \mu_{\beta_2} = .5$. For a detailed description of prior specification in the case of range constraints, consider Appendix A in \textcite{guApproximatedAdjustedFractional2018}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Hypothesis Matrix Rank}\label{sec:rank-hypo}

In Equation~\ref{eq:normal-transf}, we presented how to obtain the distribution of the transformed parameters $\bm{\beta}$ from the distribution of the original parameters $\bm{\theta}$. This is simply a linear transformation, but, to obtain a proper covariance matrix $\Sigma_{\beta} = R\Sigma_{\theta}R^T$, the hypothesis matrix $R$ has to be \textit{full-row-rank} (i.e., all rows are linearly independent).

To overcome this limit, we can use the same solution adopted by \textcite{mulderBayesFactorsTesting2016, mulderSimpleBayesianTesting2019}. A matrix $R^*$ is defined selecting the maximum number of linearly independent rows of $R$ and it is used to compute the covariance matrix $\Sigma_{\beta} = R^*\Sigma_{\theta}R^{*T}$. This allows us to obtain the distribution of the parameters $\bm{\beta^*}$ that are linearly independent. The remaining constraints can be expressed as linear combinations of the parameters $\bm{\beta^*}$. Finally, to evaluate the probability that all constraints holds we can draw a large sample from the distribution of $\bm{\beta^*}$ and compute the proportion of draws satisfying all the constraints.

Let's see an example to clarify this procedure. Suppose we have the following hypothesis: $H_i: 0 = \theta_1 < \{\theta_2, \theta_3\} < \theta_4$. Thus, the corresponding hypothesis matrix is
\begin{equation}
\begin{aligned}
R &= \begin{bmatrix}
 1 & 0 & 0 & 0\\
-1 & 1 & 0 & 0\\
-1 & 0 & 1 & 0\\
 0 &-1 & 0 & 1\\
 0 & 0 &-1 & 1\\
\end{bmatrix} \ ~ \ \text{  with  }
\end{aligned}
\qquad
\begin{aligned}
\beta_1 &= \theta_1\\
\beta_2 &= \theta_2 - \theta_1\\
\beta_3 &= \theta_3 - \theta_1\\
\beta_4 &= \theta_4 - \theta_2\\
\beta_5 &= \theta_4 - \theta_3\\
\end{aligned}
\end{equation}

Note that only the first four rows ($\beta_1,\beta_2,\beta_3,\beta_4$) are linearly independent. The fifth row, instead, can be obtained as a linear combination: $\beta_5 = \beta_4 - \beta_3 + \beta_2$. At this point, we can define $R^*$ as the first four rows of $R$ and use it to obtain the distribution of $\bm{\beta^*}$ given the original distribution of $\bm{\theta}$. To compute the probability of the inequality constraints, we need to draw a large sample from the multivariate normal distribution conditional to the equality constraints. To do that we can use the \texttt{rcmvnorm()} function from the R-package \texttt{condMVNorm}.
\codespacing
<<example-rank, echo = TRUE, cache=TRUE>>=
# theta distribution
theta_mu <- c(0,0,0,0)
theta_sigma <- diag(4)*2

# Hypothesis matrix
R <- matrix(c(1, 0, 0, 0,
             -1, 1, 0, 0,
             -1, 0, 1, 0,
              0,-1, 0, 1,
              0, 0,-1, 1), ncol = 4, byrow = TRUE)
r <- c(0, 0, 0, 0, 0)

# beta distribution
beta_mu <- R[1:4,] %*% theta_mu - r[1:4]
beta_sigma <- R[1:4, ] %*% theta_sigma %*% t(R[1:4, ])

# Obtain draws
set.seed(2021)
obs <- condMVNorm::rcmvnorm(
  1e4, mean = beta_mu, sigma = beta_sigma,
  dependent.ind = 2:4,        # inequality variables
  given.ind = 1, X.given = 0) # equality variable and constraint

# Define linearly dependent constraints
colnames(obs) <- c("beta_2", "beta_3", "beta_4")
obs <- cbind(obs,
             "beta_5" = obs[, "beta_4"] - obs[, "beta_3"] + obs[, "beta_2"])

# Evaluate on each draw if all constraints hold
test <- rowSums(obs > 0) == 4

# Proportion
mean(test)
@
\doublespacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Comparable Hypotheses}

To compute the Bayes Factor between different informative hypotheses, we can simply consider the ratio of the Bayes Factor of each hypothesis against the encompassing model:
\begin{equation}
BF_{ij} = \frac{BF_{iu}}{BF_{ju}}
\end{equation}
In order to do that, however, it is necessary for the informative hypotheses considered to be comparable \parencite{guApproximatedAdjustedFractional2018}. That is, the intersection of the constrained region of each hypothesis must be non-empty. Thus, a set of informative hypotheses $\{H_1,\ldots, H_i\}$ is comparable if exist at least one solution to
\begin{equation}
\begin{bmatrix}
R_{1E}\\
R_{1I}
\end{bmatrix} \theta = \begin{bmatrix}
r_{1E}\\
r_{1I}
\end{bmatrix}, \ldots,\begin{bmatrix}
R_{iE}\\
R_{iI}
\end{bmatrix} \theta = \begin{bmatrix}
r_{iE}\\
r_{iI}
\end{bmatrix}.
\end{equation}

This will allow us to select a common solution of $\bm{\theta}$  that can be used as the adjusted prior mean of the encompassing model. Note that to solve these equations, also inequality constraints are considered as equality constraints.

For example, $H_1: \theta_1 > \theta_2$ and $H_2: 0 = \theta_1 < \theta_2$ are comparable hypotheses because exists a common solution ($\theta_1 = \theta_2 = 0$). On the country, $H_3: \theta_1 < \theta_2 +3 $ and $H_4: \theta_1 = \theta_2$ are not comparable hypotheses because there is no a common solution to $\theta_1 = \theta_2 +3 $ and $\theta_1 = \theta_2$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Bounded Parameter Space}

The described approach using (multivariate) normal approximation can be straightforward applied when parameters of interest are unbounded. In the case of bounded parameters (i.e., variances, correlations, or probabilities), however, appropriate prior distributions are required to take into account the parameters bounded nature.

Note that, if only inequality constraints are considered, the prior distribution is only used to measure the complexity of the inequality constrained hypotheses. In this case, the prior probability that an inequality constraint holds will be insensitive to the exact distributional form, as long as the distribution is symmetrical and centred on the focal point. For example, the probability that a correlation coefficient $\rho_i$ is greater than zero is the same if we consider a  uniform distribution between -1 and 1 (taking into account parameter bounded nature) or if we consider a normal distribution centred on zero (without taking into account parameter bounded nature; see Figure~\ref{fig:plot-bounded-par}).

<<plot-bounded-par, cache=TRUE, fig.cap="The probability that $\\rho_i>0$ is the same under the uniform prior and the normal prior.">>=
plot_bounded_par()
@

Thus, as suggested by \textcite{guBayesianEvaluationInequality2014}, as long as the complexity of the constrained hypotheses is the same regardless of a (multivariate) normal distribution or an appropriate bonded prior distribution being used, it is still possible to follow the described approach. This is true for hypotheses that belong to an equivalent set \parencite[for a rigorous definition of equivalent set see][]{guBayesianEvaluationInequality2014, hoijtinkInformativeHypothesesTheory2012}.

In the case of equality and inequality constraints, however, normal approximation is possible, based on the same rationale as before, only to compute the conditional prior probability. Instead, to estimate the marginal prior density, alternative solutions have to be adopted using appropriate prior distribution to take into account the bounded nature of the parameters. See \textcite{mulderBayesFactorTesting2019} for an example of hypotheses evaluating correlation coefficients in generalized multivariate probit models.

Note that these issues are relevant only when considering the prior distribution. In the case of the posterior distribution, instead, we can safely approximate it to a (multivariate) normal distribution thanks to the large-sample theory. Moreover, prior specification is relevant only for the parameters of interest (i.e., the parameters involved in the constraints) as nuisance parameters are integrated out in the Bayes Factor. Thus, the results will be insensitive to the actual choice of the prior for the nuisance parameters as long as it is vague enough.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{A Case Study: Hypotheses Testing in the Attachment Theory}

In this section, we propose a real case study evaluating different informative hypotheses within the attachment theory. This will allow us to face the common issues found in real research applications. First, we provide the required background information regarding the attachment theory and the study aims and characteristics. Subsequently, all the steps involved in the evaluation of informative hypotheses using the Bayes Factor with the encompassing prior approach are described. Finally, the results are briefly discussed considering the prior sensitivity analysis and limits of this approach.

All analyses were conducted using the R statistical software \parencite[v\Sexpr{paste(version$major,version$minor, sep = ".")};][]{rcoreteamLanguageEnvironmentStatistical2021}. All materials, data, and analysis code are available at \url{https://github.com/ClaudioZandonella/Attachment}. The Supplemental Material with further details is also available online at \url{https://claudiozandonella.github.io/Attachment/}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Background Information}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Attachment Theory}

Attachment theory originates from the pioneering work of \textcite{bowlbyAttachmentLoss1969} and Ainsworth (\citeyear{ainsworthAttachmentExplorationSeparation1970}). They postulates that children in stressful situations actively seek proximity of the caregiver through some attachment behaviors (e.g., crying; moving towards the caregiver) in order to fulfil the evolutionary goal of protection from dangers. The main tenet of attachment theory is that the relationships with the caregivers that children develop in the early stages of their life (i.e., \textit{attachment bond}) will affect children’s social-emotional future development \parencite{cassidyHandbookAttachmentTheory2016}. Besides behavior, people construct mental representations, or working models, of the self and significant others based on their interpersonal experiences. Four main attachment styles have been recognized in the literature according to different internal representations:
\begin{itemize}
  \item{\textbf{Secure Attachment}} - children who are securely attached display optimal emotional regulation and they consider the caregiver as a secure base.
  \item{\textbf{Anxious Attachment}} - anxious children manifest high levels of anxiety in stressful situations and their relationships with the caregivers is ambivalent displaying anger or helplessness.
  \item{\textbf{Avoidant Attachment}} - avoidant children mask distress in stressful situations displaying little emotions and their relationships with the caregivers is characterized by little involvement.
  \item{\textbf{Fearful Attachment}} - fearful children lack adequate emotional regulation in stressful situations with the risk of displaying non organized behaviors.
\end{itemize}

The attachment theory is one of the main and most supported theories in psychology \parencite{cassidyHandbookAttachmentTheory2016}. In the literature, however, there is still an open debate on the relative role of mother and father attachment on children's social-emotional development. Four different main theoretical perspectives have been identified \parencite{brethertonFathersAttachmentTheory2010}:
\begin{itemize}
  \item{\textbf{Monotropy Theory}} - only the principal attachment figure (usually the mother) has an impact on children's development.
  \item{\textbf{Hierarchy Theory}} - the principal attachment figure (usually the mother) has a greater impact on children development than the subsidiary attachment figure (usually the father).
  \item{\textbf{Independence Theory}} - all attachment figures are equally important but they affect the children's development differently.
  \item{\textbf{Integration Theory}} - to understand the impact on children's development it is necessary to consider all attachment relationships taken together.
\end{itemize}
Contrasting results have been reported by studies investigating which is the “\textit{correct}” theory. No study, however, has tried to properly evaluate the different theoretical perspectives by directly comparing the different hypotheses. [TODO add some references]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Present Study}

The present study aims to directly compare the four different theoretical perspectives regarding the role of father and mother attachment, using the Bayes Factor with the encompassing prior approach.

In the analysis, $n =\Sexpr{nrow(data_cluster)}$ Italian children (\Sexpr{perc_females()}\% Females) between 8 and 12 years old (\textit{middle childhood}, third to sixth school grade) were included. Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child version \parencite[ECR-RC;][]{Brenning2014ThePQ, marciBriefExperiencesClose2019} completed by the children. Subsequently, two separate cluster analyses (i.e., one for mother scores, one for father scores) were performed. Both analyses supported the existence of the four attachment profiles (see above). The results of the classification are reported in Table~\ref{tab:table-cluster}.

\codespacing
<<table-cluster, cache=TRUE>>=
get_table_cluster()
@
\doublespacing

Children's social-emotional development was measured using the Strength \& Difficulties Questionnaire \parencite[SDQ;][]{goodmanWhenUseBroader2010} completed by the teachers. Separate scores for externalizing and internalizing problems were obtained as sum of the questionnaire items. In the analysis, however, only externalizing problems  are considered as teachers are expected to be better at reporting externalizing problems than internalizing problems [TODO spiegare meglio il perchè? aggiungere ref?]. The distribution of externalizing problems ($\text{Mean} = \Sexpr{my_round(mean(data_cluster$externalizing_sum), 2)};\ \text{SD} =  \Sexpr{my_round(sd(data_cluster$externalizing_sum), 2)};\ \text{Median} = \Sexpr{my_round(median(data_cluster$externalizing_sum), 1)}$) is presented in Figure~\ref{fig:plot-externalizing-dist}.
<<plot-externalizing-dist, cache=TRUE, fig.cap="Distribution of externalizing problems ($n_{subj} = 847$).">>=
plot_externalizing_dist()
@

Externalizing problems according to attachment styles are reported in Table~\ref{tab:table-cluster-ext}. More information about the sample, descriptive statistics, cluster analysis, and analysis of internalizing problems can be found in the Supplemental Material available online \url{https://claudiozandonella.github.io/Attachment/}.

\codespacing
<<table-cluster-ext, cache=TRUE>>=
get_table_cluster_ext()
@
\doublespacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evaluating Hypotheses with Bayes Factor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Formalization of Informative Hypotheses}

Each theoretical perspective was formalized into a different informative hypothesis taking into account its own theoretical tenets, main evidence in the literature, and authors' clinical experience in the field.

The following notation is used to formalize the hypothesis. $M$ and $F$ are used to indicate the attachment towards the mother and the father, respectively. The specific attachment style is specified in the subscript where $S$ indicates secure attachment, $Ax$ anxious attachment, $Av$ avoidant attachment, and $F$ fearful attachment. For example, $F_{Av}$ represents children with avoidant attachment towards the father.

Note that when we do not expect interaction between mother and father attachment, we can consider the role of the two parents separately. Whereas, if an interaction is expected, it is necessary to take into account the unique combination of mother and father attachment. Thus, for example, we use $M_SF_{Ax}$ to indicate children with secure attachment towards the mother and anxious attachment towards the father. Moreover, $*$ subscript is used to indicate any attachment style and a set of subscripts is used to indicate “\textit{one among}”. For example, $M_SF_{Ax;Av}$ represents children with secure attachment towards the mother and anxious or avoidant attachment towards the father.

To correctly interpret the following Figures, note that the order is important, whereas the actual values are only indicative.

\paragraph{Null Hypothesis} This is a reference hypothesis where mother attachment and father attachment are expected to have no effect and only gender differences are taken into account (see Section~\ref{sec:def-encompassing-model} for the actual model definition). The hypothesis is represented in Figure~\ref{fig:plot-null-hypothesis}:
\begin{equation}
\begin{gathered}
M_* = 0,\\
F_* = 0.
\end{gathered}
\end{equation}

<<plot-null-hypothesis,fig.width=7, fig.high = 4, out.width="100%", cache=TRUE, fig.cap="\\textbf{Null Hypothesis.} Expected externalizing problems according to mother and father attachment.">>=
plot_hypothesis(hypothesis = "null")
@

\paragraph{Monotropy Hypothesis} Father attachment is expected to have no effect, whereas considering mother attachment we expect the following order: secure children with the lowest level of problems, anxious and avoidant children with similar levels of problems, fearful children with the highest levels of problems. The hypothesis is represented in Figure~\ref{fig:plot-monotropy-hypothesis}:
\begin{equation}
\begin{gathered}
M_S < M_{Ax} = M_{Av} < M_F,\\
F_* = 0.
\end{gathered}
\end{equation}

<<plot-monotropy-hypothesis,fig.width=7, fig.high = 4, out.width="100%", cache=TRUE, fig.cap="\\textbf{Monotropy Hypothesis.} Expected externalizing problems according to mother and father attachment.">>=
plot_hypothesis(hypothesis = "monotropy")
@

\paragraph{Hierarchy Hypothesis} Father attachment is expected to follow the same pattern as the mother attachment, but its influence is expected to be smaller. The hypothesis is represented in Figure~\ref{fig:plot-hierarchy-hypothesis}:
\begin{equation}
\begin{gathered}
M_S < M_{Ax} = M_{Av} < M_F,\\
F_S < F_{Ax} = F_{Av} < F_F,\\
F_{Ax}< M_{Ax};\ ~ \ F_{Av}< M_{Av};\ ~ \ F_F< M_F.
\end{gathered}
\end{equation}

<<plot-hierarchy-hypothesis,fig.width=7, fig.high = 4, out.width="100%", cache=TRUE, fig.cap="\\textbf{Hierarchy Hypothesis.} Expected externalizing problems according to mother and father attachment.">>=
plot_hypothesis(hypothesis = "hierarchy")
@

\paragraph{Independence Hypothesis} Mother and father attachment are expected to affect children outcomes differently. In this case, we considered avoidant attachment towards the father as a condition of higher risk. The hypothesis is represented in Figure~\ref{fig:plot-independence-hypothesis}:
\begin{equation}
\begin{gathered}
M_S < M_{Ax} = M_{Av} < M_F,\\
F_S < F_{Ax} < F_{Av} < F_F.\\
\end{gathered}
\end{equation}

<<plot-independence-hypothesis,fig.width=7, fig.high = 4, out.width="100%", cache=TRUE, fig.cap="\\textbf{Independence Hypothesis.} Expected externalizing problems according to mother and father attachment.">>=
plot_hypothesis(hypothesis = "independence")
@

\paragraph{Integration Hypothesis}  Mother and father attachment are expected to interact. In this case, we consider secure attachment as a protective factor and fearful attachment as a risk condition. We do not specify the conditions $M_SF_F$ and $M_FF_S$ as their frequency is very low (\Sexpr{perc_rare_condition()}\% of the sample). The hypothesis is represented in Figure~\ref{fig:plot-integration-hypothesis}:
\begin{equation}
\begin{gathered}
M_SF_S< \{M_SF_{Ax;Av} = M_{Ax;Av}F_S\} < M_{Ax;Av}F_{Ax;Av} <  \{M_FF_{Ax;Av} = M_{Ax;Av}F_F\} <  M_FF_F,\\
\text{with}\\
M_{Ax}F_{Ax} = M_{Ax}F_{Av} = M_{Av}F_{Ax} = M_{Av}F_{Av}.
\end{gathered}
\end{equation}

<<plot-integration-hypothesis,fig.width=4, fig.high = 3, cache=TRUE, fig.cap="\\textbf{Integration Hypothesis.} Expected externalizing problems according to mother and father attachment.">>=
plot_hypothesis(hypothesis = "integration")
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Definition of the Encompassing Model} \label{sec:def-encompassing-model}

A Zero-Inflated Negative Binomial (ZINB) mixed effect model is defined to take into account the characteristics of the dependent variable and its distribution (see Figure~\ref{fig:plot-externalizing-dist} and see Supplemental Material for more details regarding the analysis of zero inflation \url{https://claudiozandonella.github.io/Attachment/}):
\begin{equation}
y_{ij} \sim ZINB(p_{ij}, \mu_{ij}, \phi),
\end{equation}
where $p_{ij}$ is the probability of an observation $y_{ij}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_{ij}$ indicates the probability of a given observation $y_{ij}$ being generated form a Negative Binomial distribution with mean $\mu_{ij}$ and variance $\sigma_{ij}^2 = \mu_{ij} + \frac{\mu_{ij}^2}{\phi}$. Moreover, we define
\begin{equation}
\begin{gathered}
p_{ij} = \text{logit}^{-1}(X_i^T\beta_p+ Z_j^Tu_p),\\
\mu_{ij} = \text{exp}(X_i^T\beta_{\mu}+ Z_j^Tu_{\mu}).
\end{gathered}
\end{equation}

That is, both $\bm{p}$ and $\bm{\mu}$ are modelled separately according to fixed and random effects.
In particular, we consider the children's classroom ID as a random effect in both cases to account for teachers' different ability to evaluate children's problems. While, regarding fixed effects, only the role of gender is considered for $\bm{p}$, whereas for $\bm{\mu}$ the interaction between mother and father attachment are included together with gender. In the R formula syntax, we have
\codespacing
<<formula-syntax, eval = FALSE, echo=TRUE>>=
# Regression on p
p ~ gender + (1|ID_class)

# Regression on mu
mu ~ gender + mother * father + (1|ID_class)
@
\doublespacing

The parameters of interest (i.e., those related to mother and father attachment interaction) and the parameter related to gender differences are unbounded. Thus, we can simply specify a normal distribution with mean 0 and standard deviation of 3, $\mathcal{N}(0,3)$, as reasonable prior. This prior is intended to be non-informative but without being excessively diffuse\footnote{Considering 1 as intercept (note that $exp(1)$ is approximately the sample mean value), values included within one standard deviation, $exp(1 \pm 1\times SD)$, range between 0 and 55. Although externalizing problems are bounded between 0 and 20, prior predicted values are still reasonable as they cover all possible values without including excessively large values. More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values (see Supplemental Material for further details \url{https://claudiozandonella.github.io/Attachment/})}. The influence of prior specification is subsequently evaluated in a prior sensitivity analysis. Regarding the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) \texttt{brms} default priors are maintained (see Supplemental Material for further details \url{https://claudiozandonella.github.io/Attachment/}). The encompassing model was estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).

Finally, note that in this case, we do not need to standardize our parameters as they represent mean groups differences (see Section~\ref{sec:param-standard}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Hypothesis Matrices}

Before computing the hypothesis matrix for each informative hypothesis, it is important to consider the contrasts coding and the resulting parametrization of the encompassing model. For mother and father attachment, default treatment contrasts are used \parencite{schadHowCapitalizePriori2019} considering secure attachment as the reference category. Therefore, model intercept represents children with secure attachment towards both parents ($M_SF_S$) and we have parameters indicating the main effects of mother and father attachment and other parameters for the interaction effect.

Now, given the informative hypotheses and the parametrization of the encompassing model, we can obtain the respective hypotheses matrices. To do that, first, we need the model matrix with all the conditions of interest. Note that we have to consider only conditions relevant to the constraints (i.e., those related to mother and father attachment) ignoring other nuisance conditions (i.e., gender and classroom ID).

Subsequently, we can derive the required equality and inequality constraints. In particular, with hypotheses that do not expect interaction between mother and father attachment (i.e., monotropy, hierarchy, and independence hypotheses), all interaction terms are set equal to zero and main effects are obtain considered the reference level of the other parent (i.e., $M_{Ax}F_S$ is the main effect of anxious attachment towards the mother).  As an example, consider the following code:
\codespacing
<<echo = TRUE, cache=TRUE, eval = FALSE>>=
# Define relevant conditions
attachment <- c("S", "Ax", "Av", "F")
new_data <- expand.grid(
  mother = factor(attachment, levels = attachment),
  father = factor(attachment, levels = attachment)
)

# Get model matrix
mm <- model.matrix(~ mother * father, data = new_data)[,-1] # remove intercept
rownames(mm) <- paste0("M_",new_data$mother, "_F_", new_data$father)

# Get constraints main effect
# M_Ax = M_Av  --->  M_Ax_F_S - M_Av_F_S = 0
# F_F > F_Av   --->  M_S_F_F - M_S_F_Av > 0
rbind(mm["M_Ax_F_S", ] - mm["M_Av_F_S", ],
      mm["M_S_F_F", ] - mm["M_S_F_Av", ])

# Get constraints interaction
# M_F_F_Ax = M_Ax_F_F  --->  M_F_F_Ax - M_Ax_F_F = 0
# M_Ax_F_Av > M_S_F_Ax  --->  M_Ax_F_Av - M_S_F_Ax > 0
rbind(mm["M_F_F_Ax", ] - mm["M_Ax_F_F", ],
      mm["M_Ax_F_Av", ] - mm["M_S_F_Ax", ])
@
\doublespacing
In this way, we can easily specify all the constraints obtaining the respective hypothesis matrix ($R$) and the vector with the constraints constant values ($r$) for each hypothesis. In all our hypotheses, however, no constraints include constant values. Thus, $r$ is always a vector of zeros and it can be ignored. Moreover, also the intercept is ignored because there are no constraints that include $M_SF_S$ alone (e.g., $M_SF_S>k$) but is always compared with other groups (e.g., $M_SF_S< M_{Ax}F_S$). Thus, the inclusion of the intercept is redundant and we can ignore it.

Full hypothesis matrix specification for each hypothesis is available in the Supplemental Material \url{https://claudiozandonella.github.io/Attachment/}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Computing the Bayes Factor}

So far we defined the hypotheses matrices, specified the encompassing prior, and obtained the model posterior distribution. To compute the Bayes Factor, we now need the adjusted prior and the posterior of the transformed parameters vector $\bm{\beta}$ (i.e., the parameters that identify the constraints) for each hypothesis.

\begin{itemize}
\item{\textbf{Adjusted Prior $\bm{\beta}$.}} As reported in Section~\ref{sec:adj-prior}, adjusted prior is required to properly evaluate the constraints. Applying the Equation~\ref{eq:normal-transf}, we obtain the prior for the transformed parameter and then we set the mean vector to zero.
\item{\textbf{Posterior $\bm{\beta}$.}} The same transformation used for the prior can be applied, this time considering the estimated posterior mean $\hat{\bm{\theta}}$ and the estimated posterior covariance $\hat{\Sigma}_{\theta}$, to obtain the posterior distribution of the transformed parameters vector $\bm{\beta}$.
\end{itemize}

As discussed in Section~\ref{sec:rank-hypo}, Equation~\ref{eq:normal-transf} requires the hypothesis matrix $R$ to be \textit{full-row-rank} (i.e., all constraints are linearly independent). However, this is not the case of the hierarchy hypothesis. Thus, we followed the solution presented in Section~\ref{sec:rank-hypo}. Detailed information is available in the Supplemental Material \url{https://claudiozandonella.github.io/Attachment/}.

Now, we have all the elements required to compute the Bayes Factor for each hypothesis as described in Section~\ref{sec:compute-bf}. Moreover, assuming that each hypothesis is equally likely a priori, we can calculate the posterior probability of each hypothesis as \parencite{hoijtinkInformativeHypothesesTheory2012, guBayesianEvaluationInequality2014},
\begin{equation}
\text{Posterior Probability} H_i = \frac{BF_{iu}}{\sum_iBF_{iu}}.
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results and Prior Sensitivity Analysis}

Bayes Factor and posterior probability of each hypothesis are reported in Table~\ref{tab:table-bf-results}. Results clearly indicate that, among the considered hypotheses, the Monotropy Hypothesis is the most supported by the data.

\codespacing
<<table-bf-results, cache=TRUE>>=
get_table_bf(bf_result = BF_weights_ext,
             path_img = "figure/")
@
\doublespacing

Remember, however, that prior specification affects the Bayes Factor results. It is recommended, therefore, to evaluate also the results obtained using different prior settings. In particular, we considered as possible priors for the parameters of interest:
\begin{itemize}
  \item{$\mathcal{N}(0,.5)$} - unreasonable tight prior
  \item{$\mathcal{N}(0,1)$} - tighter prior
  \item{$\mathcal{N}(0,3)$} - original prior
  \item{$\mathcal{N}(0,5)$} - more diffuse prior
  \item{$\mathcal{N}(0,10)$} - unreasonably diffuse prior
\end{itemize}

The results of the prior sensitivity analysis are reported in Table~\ref{tab:table-sens-prior-analysis}.
\codespacing
<<table-sens-prior-analysis, cache=TRUE>>=
get_table_sens_analysis(summary_sensitivity = summary_sensitivity_ext)
@
\doublespacing
Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data. However, we can observe two distinct patterns. As the prior gets more diffuse, the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases. Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.

To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point. On the contrary, equality constraints are highly affected by the prior definition. As the prior gets more diffuse, the density value at zero decreases as well and, even for posterior distributions centred far from zero, the densities ratio at zero will favour the posterior. Thus, as the prior gets more diffuse, the Bayes Factor will favour more and more the hypotheses with equality constraints, whereas for tighter prior the Bayes Factor will strongly penalize hypotheses with equality constraints if these are not correct (see Figure~\ref{fig:plot-sensitivity-prior}).

All the defined hypotheses include equality constraints. Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases. Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).

<<plot-sensitivity-prior, cache=TRUE, fig.cap="Evaluating densities at 0 for different prior settings and a selection of parameters posteriors.">>=
get_plot_sensitivity()
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Limits}

When interpreting the results, it is important to take into account the limits of the Bayes Factor. First of all, the selected hypothesis is relative to the data and the set of hypotheses considered. That means that we should not interpret the selected hypothesis as the only “\textit{correct}” one. Maybe we did not consider some important aspects and new hypotheses may reveal themselves to be actually much better than the previous ones. For example, regarding the attachment results, taking into account the interaction between children's gender and attachment may be fundamental (do you expect that attachment towards the father plays a different role between girls and boys?). This limit, however, becomes an advantage as it forces the researchers to focus on the definition of the hypotheses: to obtain good answers first we need to ask the right questions.

Moreover, considering a unique single winning hypothesis may be limiting as different hypotheses could help to explain different aspects of the process under investigation. For example, mother and father attachment may play a different role at different ages. Thus, the selected hypothesis may vary according to children's age or other conditions. This should warn against interpreting the result in terms of winning/losing focusing uniquely on the selected hypothesis and discarding other hypotheses from further investigations.

Another important limit we observed is the sensitivity of the results to the prior specification. \textcite{gelmanBayesianDataAnalysis2013} do not recommend the use of the Bayes Factor given its sensitivity to model definition arbitrary choices. Evaluating the results under different conditions and transparently discussing the reasons behind arbitrary choices would help to interpret results more consciously \parencite{schadWorkflowTechniquesRobust2021}.

Finally, another limit related to the use of the Bayes Factor with the encompassing prior approach is that we do not obtain the actual estimates of the parameters posterior. The only information we get is the selected hypothesis, but we have no other information regarding the actual parameters values. Therefore, for example, we are not able to assess the actual effect sizes. To overcome this limit we can rely on Bayesian inference that allows us to effectively estimate the model parameter posteriors. Consider, for example, \textcite{katoBayesianApproachInequality2006} where a Gibbs sampler is defined taking into account parameter constraints.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

In this paper, we presented a detailed description and an applied example of the Bayes Factor with the encompassing prior approach. As discussed in the introduction, this approach has several advantages over traditional Null Hypothesis Significance Testing (NHST): it is possible to evaluate complex hypotheses with equality and inequality constraints; multiple hypotheses can be tested simultaneously; Bayes Factor and Posterior Probabilities allow to quantify the relative evidence form the data in favour of the hypotheses.

This approach is of particular interest to the researchers, because informative hypotheses allow them to formalize expectation with great flexibility. In this paper we considered only the presence/absence of an effect (i.e., $\theta = 0$) or the expected effects order (i.e., $\theta_i > \theta_j$). However, in case of clear indications about the actual effects, researchers can specify the expected range of values for the effects of interest (i.e., $a<\theta_i<b$). This allows even a greater level of precision in the formalization of informative hypotheses.

As underlined by \textcite[p.229]{guApproximatedAdjustedFractional2018}, “this class of informative hypotheses covers a much broader range of scientific expectations than the class of standard null hypotheses. In addition, by testing competing informative hypotheses directly against each other a researcher obtains a direct answer as to which scientific theory is most supported by the data”.

The available literature, however, is often technical and difficult to follow for non-experts in this approach. This paper filled this gap by providing a detailed description of all steps and elements involved in the computation of the Bayes Factor with the encompassing prior approach. This will enhance researchers' awareness regarding all pros and cons of this method, avoiding applying statistical techniques as black boxes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\printbibliography
\end{document}

%%
%% Copyright (C) 2019 by Daniel A. Weiss <daniel.weiss.led at gmail.com>
%%
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%%
%% http://www.latex-project.org/lppl.txt
%%
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%%
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%%
%% This work is "maintained" (as per LPPL maintenance status) by
%% Daniel A. Weiss.
%%
%% This work consists of the file  apa7.dtx
%% and the derived files           apa7.ins,
%%                                 apa7.cls,
%%                                 apa7.pdf,
%%                                 README,
%%                                 APA7american.txt,
%%                                 APA7british.txt,
%%                                 APA7dutch.txt,
%%                                 APA7english.txt,
%%                                 APA7german.txt,
%%                                 APA7ngerman.txt,
%%                                 APA7greek.txt,
%%                                 APA7czech.txt,
%%                                 APA7turkish.txt,
%%                                 APA7endfloat.cfg,
%%                                 Figure1.pdf,
%%                                 shortsample.tex,
%%                                 longsample.tex, and
%%                                 bibliography.bib.
%%
%%
%% End of file `./samples/longsample.tex'.

<<biber>>=
system(paste("biber", sub("\\.Rnw$", "", current_input())))
@

### 2021-10-05 README.Rmd
add readme and tidy repo

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

# Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach

In this repository we collect all the materials of the study “*Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach*”. The aim of the paper is to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example regarding attachment theory.

The pre-print version of the article is available at [TODO: add link]. The Supplemental Material with all the analyses is available at https://claudiozandonella.github.io/Attachment/.

## Project Structure

The project structure is based on the traditional R-package project structure, but the repository is not meant to be installed as a package (see Section [Reproducibility](#reproducibility) on how to run the analyses). R-package project structure, however, allows us to get advantage of some functionalities:

- `DESCRIPTION` file is used to track project metadata and manage project dependencies (note that we also used `renv` for package dependencies, see Section below)
- `devtools::load_all()` allows to easily load all functions defined to run the analysis (note that we followed the *functional programming paradigm*, see Section below)

Moreover, the analysis workflow is managed using `drake` (see Section below) and include other (*non-standard*) folders to organize the scripts for the analysis and for the produced outputs (i.e., paper and supplemental material).

The actual repository folder structure is:

- `Analysis/` - includes the file `Analysis_Drake.R` used to run the analysis workflow using `drake`
- `Data/` - includes the data used in the analyses
- `Documents/` - includes all the scripts and utility files for the creation of the outputs. In particular,
  - `Bookdown/` - the Supplemental Material available online
  - `Paper/` - the pre-print version of the article
- `R/` - includes all the `.R` scripts with the functions used in the analyses
- `docs/` - includes `bookdown` outputs used to build the GitHub Pages site
- `renv/` - utility folder used by `renv`

## Reproducibility {#reproducibility}

To guarantee the reproducibility of the results, the R-package`drake` is used to manage the analysis workflow and to enhance the readability and transparency of the analysis. To know more about `drake` consider the [official Git-hub page](https://github.com/ropensci/drake) or the [user manual](https://books.ropensci.org/drake/). Summarizing, using `drake` the user defines the plan of the analysis where each step in the analysis is defined trough functions. Functions can be appropriately defined to obtain desired targets (i.e., R-output with results of interests) and they are declared in another script. Subsequently, `drake` manages the whole analysis recognizing the dependency structure of the different targets. When any change is made to the code `drake` evaluates the analysis and updates the results. Following the *functional programming paradigm* (i.e., defining functions for each step of the analysis), it allows us to avoid "*coping and paste*" in the code, it makes debugging easier, and it facilitates the reading of the code.

Moreover, the R-package `renv` is used to manage the dependencies of the R-packages used in the analysis. The `renv` package allows to create an isolated, portable, and reproducible environment where the analyses are run. To know more about `renv` consider the [official documentation](https://rstudio.github.io/renv/articles/renv.html). However, `renv` is limited as it can not handle different R versions.

To overcome this issue, we also provide a `Dockerfile` to build a Docker image with R version 4.1.0. To know more about Docker see [official documentation](https://www.docker.com/) or 
[rOpenSci Labs tutorial](https://jsta.github.io/r-docker-tutorial/).

### Run the Analysis

To reproduce the analysis:

1. Download the the repository on your local machine
    ```{bash, eval = FALSE}
    git clone https://github.com/ClaudioZandonella/Attachment
    ```
1. Open the R project by double-clicking the file `Attachment.Rproj` you can find in the project main directory. A new R-studio session will open.
1. Run `renv::restore()` to install project's dependencies (have a coffee, it takes some time).
1. Now the required package will be loaded. Restart the R session (`command`/`ctrl` + `shift` + `f10`) so `devtools::load_all()` is automatically run (according to `.Rprofile`) to load all functions used in the analysis defined in the `R/` folder.

    > Note that also `source("Documents/Utils_report.R")` is automatically run to load report utilities functions (functions to load analysis results and to compile the bookdown).

1. Open `Analysis/Analysis_Drake.R` and run each line (one by one) to run the analysis using drake. First, the analysis environment is setted together with the analysis plan (available at `R/Plan.R`). Next the analysis targets are computed (have a coffee, it takes a long time). Finally, the analysis results are loaded and briefly presented.

    > Note that you can access the analysis targets with using the functions `drake::loadd(<name_target>)`, or load all the results with `drakee_load_all()`.

    > It could happen that some times the session session stay idle when fitting `brms` models without throwing errors. In this case, it is necessary to force restarting the R session and rerun the analysis. An error warning message will appear `Error: drake's cache is locked`. Just follow the instructions provided by drake to force unlock of the cache  `drake::drake_cache("...")$unlock()`.

1. To compile the pre-print version of the article (possible after the analysis), open `Documents/Paper/Paper.Rnw` and compile the file using `knitr` and `pdfLaTeX` (see [project options](https://support.rstudio.com/hc/en-us/articles/200532247-Weaving-Rnw-Files-in-the-RStudio-IDE)). Note that, as usual for LaTeX files, the first run will fail. Run again to obtain the actual output. 
1. To compile the Supplemental Material, run `make_my_book()`. The resulting output is saved in the `docs/` folder.

#### Docker

To run the analysis in a Docker container, build the image according to the `Dockerfile` present in the project main directory, using
```{bash, eval = FALSE}
docker build -t attachment .
```

> It is important too build the image before to run the analysis

Next, you can run the container using
```{bash, eval = FALSE}
docker run --rm -p 8787:8787 -e PASSWORD="<your-PW>" attachment
```

Now, open the folder `Attachment/` and run the analysis following the instructions above from step 2.

### 2021-10-05 Bayes_Factor.R

@@ -1,117 +1,0 @@
-library(rstan)
-options(mc.cores = 4)
-rstan_options(auto_write = TRUE)
-
-stan_data <- make_stan_data(data_cluster, formula = list("gender + mother", "gender"))
-fit_H3 <- stan(file = "Stan/ZIP-model-H2.stan", data = stan_data)
-
-round(summary(fit_H1)$summary[, "mean"],2)
-
-round(brms::posterior_summary(brm_int_mother)[, "Estimate"],2)
-
-post_H1 <- as.matrix(fit_H1, pars = c("db_mother[1]", "db_mother[2]", "db_mother[3]"))
-
-colnames(post_H1)
-
-#---- BF ----
-
-post_mean <- apply(post_H1, 2, mean)
-post_cov <- cov(post_H1)
-
-prior_mean <- c(0, 0, 0)
-prior_cov <- diag(3) * 25
-
-# prior density equality
-prior_den_eq <- mvtnorm::dmvnorm(x = 0,
-                                 mean = prior_mean[2],
-                                 sigma = as.matrix(prior_cov[2,2]))
-dnorm(0,0,5)
-
-# posterior density equality
-post_den_eq <- mvtnorm::dmvnorm(x = 0,
-                                mean = post_mean[2],
-                                sigma = as.matrix(post_cov[2,2]))
-dnorm(0, post_mean[2], sqrt(post_cov[2,2]))
-
-# prior conditional probability
-prior_cond_prob <- condMVNorm::pcmvnorm(
-  lower = rep(0,2), upper = rep(Inf,2),
-  mean = prior_mean, sigma = prior_cov,
-  dependent.ind=c(1, 3), given.ind=c(2), X.given = c(0))
-
-# posterior conditional probability
-post_cond_prob <- condMVNorm::pcmvnorm(
-  lower = rep(0,2), upper = rep(Inf,2),
-  mean = post_mean, sigma = post_cov,
-  dependent.ind=c(1, 3), given.ind=c(2), X.given = c(0))
-
-# Resulting BF
-
-BF_H1 <- (post_den_eq * post_cond_prob) / (prior_den_eq * prior_cond_prob)
-
-#----
-stan_data <- make_stan_data(data_cluster, formula = list("cluster_mother * cluster_father", "gender"))
-fit_int <- stan(file = "Stan/ZIP-model.stan", data = stan_data)
-
-plot(fit_int)
[…]

### 2021-10-05 README.Rmd
corrige read me

@@
 
-    > Note that you can access the analysis targets with using the functions `drake::loadd(<name_target>)`, or load all the results with `drakee_load_all()`.
+    > Note that you can access the analysis targets with using the functions `drake::loadd(<name_target>)`, or load all the results with `drake_load_all()`.
 

### 2021-11-10 Documents/Paper/paper.Rnw
version before trackdown download

@@
 
-\title{Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach}
-\shorttitle{The Bayes Factor Encompassing Prior Approach}
-
-\author{Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, Gianmarco Altoè}
-\affiliation{UNIPD}
+\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints: The Bayes Factor via the Encompassing Prior Approach}
+\shorttitle{The Bayes Factor via the Encompassing Prior Approach}
+
+\author{Claudio Zandonella Callegher$^1$, Tatiana Marci$^1$, Pietro De Carli$^2$, Gianmarco Altoè$^1$}
+\affiliation{$^1$UNIPD\\$^2$UNIMI}
 
@@
 In particular, the Bayes Factor based on the “\textit{encompassing prior approach}” allows researchers to easily evaluate complex informative hypotheses.
-In this paper we provide a clear and detailed introduction to this approach.
+In this paper, we provide a clear and detailed introduction to this approach.
 We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor following the encompassing prior approach.
-Subsequently, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social-emotional development.}
-
-\keywords{keyword-1, keyword-2}
+Subsequently, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social-emotional development.
+\vspace{2em}
+\begin{center}
+\textbf{Translational Abstract}
+\end{center}
+\vspace{.5em}
+\noindent The evaluation of hypotheses is one of the main goals of empirical research.
+In fact, when conducting a study, researchers usually want to evaluate the plausibility of specific hypotheses according to the collected data.
+These hypotheses can be formalized in accordance with researchers' expectations or theoretical perspectives into the so-called “\textit{informative hypotheses}”.
+However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are not suitable for evaluating the plausibility of complex informative hypotheses.
+The Bayes Factor via the “\textit{encompassing prior approach}”, instead, allows researchers to easily evaluate the plausibility of complex informative hypotheses.
+In this paper, we provide a clear and detailed introduction to this approach.
+We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor.
+Moreover, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social-emotional development.
+This approach is of particular interest in applied research as it allows researchers to formalize hypotheses with great flexibility and to directly evaluate which hypothesis is the most supported by the data.
+}
+
+\keywords{Bayes Factor, Encompassing Prior, Informative Hypothesis, Equality and Inequality Constraints, Attahcement Theory}
 
@@
 
-This approach is of particular interest to the researchers, because informative hypotheses allow them to formalize expectation with great flexibility.
+This approach is of particular interest to the researchers, because informative hypotheses allow them to formalize their expectations with great flexibility.
 In this paper we considered only the presence/absence of an effect (i.e., $\theta = 0$) or the expected effects order (i.e., $\theta_i > \theta_j$).

### 2021-11-10 R/Plan.R

@@ -135,7 +135,7 @@ get_analysis_plan <- function(){
 
     plot_zinb_ext = get_plot_zinb(model = fit_ext_zinb, attachment = "mother"),
 
-    #----    Model Comparison extt    ----
+    #----    Model Comparison ext    ----
     fit_ext_zero = zinb_fit(data = data_cluster, y = "externalizing_sum",
                             formula = "gender"),
     fit_ext_mother = zinb_fit(data = data_cluster, y = "externalizing_sum",

### 2021-11-10 Documents/Paper/paper.Rnw
update revision

@@
 
-\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints: The Bayes Factor via the Encompassing Prior Approach}
+\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A tutorial using the Bayes Factor via the Encompassing Prior Approach}
 \shorttitle{The Bayes Factor via the Encompassing Prior Approach}
@@
 In particular, the Bayes Factor based on the “\textit{encompassing prior approach}” allows researchers to easily evaluate complex informative hypotheses.
-In this paper, we provide a clear and detailed introduction to this approach.
-We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor following the encompassing prior approach.
-Subsequently, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social-emotional development.
+This paper provides a detailed introduction to the Bayes Factor with encompassing prior.
+First, all steps and elements involved in the formalization of  informative hypotheses and computation of the Bayes Factor are described.
+Next, we apply this method to a real case scenario considering the attachment theory.
+Precisely, we analyzed the relative role of maternal and paternal attachment on children's social-emotional development by comparing the different theoretical perspectives debated in the literature.
+
 \vspace{2em}
@@
 \vspace{.5em}
+
 \noindent The evaluation of hypotheses is one of the main goals of empirical research.
@@
 The Bayes Factor via the “\textit{encompassing prior approach}”, instead, allows researchers to easily evaluate the plausibility of complex informative hypotheses.
-In this paper, we provide a clear and detailed introduction to this approach.
-We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor.
-Moreover, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social-emotional development.
+This paper provides a detailed introduction to the Bayes Factor with encompassing prior.
+First, all steps and elements involved in the formalization of  informative hypotheses and computation of the Bayes Factor are described.
+Next, we apply this method to a real case scenario considering the attachment theory.
+Precisely, we analyzed the relative role of maternal and paternal attachment on children's social-emotional development by comparing the different theoretical perspectives debated in the literature.
 This approach is of particular interest in applied research as it allows researchers to formalize hypotheses with great flexibility and to directly evaluate which hypothesis is the most supported by the data.
@@
 
-\keywords{Bayes Factor, Encompassing Prior, Informative Hypothesis, Equality and Inequality Constraints, Attahcement Theory}
+\keywords{Bayes Factor, Encompassing Prior, Informative Hypothesis, Equality and Inequality Constraints, Attachment Theory}
 
 \authornote{
-   \addORCIDlink{Claudio Zandonella Callegher}{0000-0001-7721-6318}
+\vspace{-1cm}
+\begin{flushleft}\footnotesize
+\addORCIDlink{Claudio Zandonella Callegher}{0000-0001-7721-6318}\\
+\addORCIDlink{Tatiana Marci}{0000-0002-2813-0312}\\
+\addORCIDlink{Pietro De Carli}{0000-0001-6538-2175}\\
+\addORCIDlink{Gianmarco Altoè}{0000-0003-1154-9528}
+
+Data used for the illustrative application are part of a larger project on the socioemotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]).
+All materials and data are available at [TODO].
 
 Correspondence concerning this article should be addressed to Claudio Zandonella Callegher, Department of Developmental Psychology and Socialisation, University of Padua, Via Venezia, 8 - 35131 Padova, Italy.
-E-mail: claudiozandonella@gmail.com}
+E-mail: claudiozandonella@gmail.com
+\end{flushleft}
+}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
@@
 
-In psychology, the dominant statistical approach to evaluate research hypotheses is the Null Hypothesis Significance Testing (NHST).
+The dominant statistical approach to evaluate research hypotheses in psychology is the Null Hypothesis Significance Testing (NHST).
 In the literature, however, the utility and validity of NHST are largely debated \parencite{wassersteinMovingWorld052019}.
@@
 Second, the p-value does not quantify the evidence in favour of one hypothesis, thus, it is not possible to \textit{“accept”} a hypothesis but only to \textit{“reject”} it.
-This is inconvenient as, in case of not significant results, the researchers are left in a state of indecision.
+This has some drawbacks since, in case of not significant results, the researchers are left in a state of indecision.
 Third, NHST does not allow testing multiple hypotheses at the same time.
@@
 Fourth, NHST is unsuitable for testing broad classes of hypotheses with equality and inequality constraints \parencite{mulderSimpleBayesianTesting2019}.
-Expectations can be evaluated using one-side tests, however, when more groups or more variables are involved, it is not possible to evaluate complex parameter constraints that reflect researchers' expectations \parencite{vandeschootIntroductionBayesianModel2011}.
+Expectations can be evaluated using one-side tests; however, when more groups or more variables are involved, it is not possible to evaluate complex parameter constraints that reflect researchers' expectations \parencite{vandeschootIntroductionBayesianModel2011}.
 
@@
 Model comparison has several advantages and, in particular, it allows to directly compute the relative plausibility of each model given the data and the set of models considered.
-Model comparison using the information criteria, however, is not appropriate to evaluate hypotheses that include complex parameter constraints reflecting researchers' expectations.
+However, model comparison using information criteria is not appropriate to evaluate hypotheses that include complex parameter constraints reflecting researchers' expectations.
 In fact, information criteria evaluate models complexity according to the number of parameters, but they do not take into account possible order constraints on the parameters.
@@
 An alternative criterium to evaluate research hypotheses in a model comparison is the Bayes Factor.
-In the last 25 years, there has been an increasing interest in the Bayes Factor and its use has been proposed as the solution to the critical issues of the NHST \parencite{heckReviewApplicationsBayes2020, mulderEditorsIntroductionSpecial2016}.
+During the last 25 years, there has been an increasing interest in the Bayes Factor and its use has been proposed as the solution to the critical issues of the NHST \parencite{heckReviewApplicationsBayes2020, mulderEditorsIntroductionSpecial2016}.
 Although it has its own limitations and it does not solve the fundamental issues of the misuse of statistical techniques \parencite{schadWorkflowTechniquesRobust2021, gelmanBayesianDataAnalysis2013}, the Bayes Factor offers some clear advantages.
@@
 
-The evaluation of informative hypotheses is of particular interest to the researchers as it allows them to directly assess specific complex expectations and theoretical perspectives.
+The evaluation of informative hypotheses is of particular interest to the researchers as it allows them to assess specific complex expectations and theoretical perspectives directly.
 In the literature, a particular approach allowing to easily compute the Bayes Factor with complex informative hypotheses has received increasing attention: \textit{“the Bayes Factor with encompassing prior”}.
@@
 
-All studies mentioned above, however, considered only informative hypotheses with inequality constraints.
-Evaluating in the same hypothesis equality and inequality constraints, instead, it was no possible and equality constraints had to be approximate to “\textit{about equality constraints}” (i.e., a equality constraints of type $\theta_i = \theta_j$ is approximated to $|\theta_i - \theta_j| < \xi$ for a value of $\xi$ small enough).
+However, all studies mentioned above considered only informative hypotheses with inequality constraints.
+Evaluating in the same hypothesis equality and inequality constraints, instead, it was not possible and equality constraints had to be approximated to “\textit{about equality constraints}” (i.e., a equality constraints of type $\theta_i = \theta_j$ is approximated to $|\theta_i - \theta_j| < \xi$ for a value of $\xi$ small enough).
 
@@
 The complexity of these articles makes it difficult for researchers not familiar with this approach to clearly understand all the steps involved.
-On the other hand, articles offering a general introduction to the Bayes Factor do not provide enough details to allow readers to autonomously apply this method to their problems, but they usually rely on ad-hoc solutions implemented in some statistical software.
+On the other hand, articles offering a general introduction to the Bayes Factor do not provide enough details to allow readers to autonomously apply this method to their problems, but they usually rely on ad-hoc solutions implemented in some statistical software \parencite[for example consider][]{hoijtinkTutorialTestingHypotheses2019a}.
 
@@
 Prior specification is an important element as the resulting Bayes Factor value is affected by the prior choice.
-This aspect is particularly relevant in the case of equality constraints \parencite{lindleyStatisticalParadox1957, bartlettCommentLindleyStatistical1957}, whereas inequality constraints are not affected as long as the prior is symmetric and centred to the focal point of interest (this aspect will be further discussed in Section~\ref{sec:adj-prior}).
+This is particularly relevant in the case of equality constraints \parencite{lindleyStatisticalParadox1957, bartlettCommentLindleyStatistical1957}, whereas inequality constraints are not affected as long as the prior is symmetric and centred to the focal point of interest (this feature will be further discussed in Section~\ref{sec:adj-prior}).
 
@@
 Both, \textcite{guApproximatedAdjustedFractional2018, mulderSimpleBayesianTesting2019} based their approach on the fractional Bayes Factor.
-Starting from a non-informative prior, a minimal fraction of the data is used to obtain a posterior that is subsequently used as proper prior, we refer to it as \textit{fractional prior} (have you ever heard Lindley's \citeyear{lindleyBayesianStatisticsReview1972} famous quote \textit{“Today’s posterior is tomorrow’s prior”}?).
+Starting from a non-informative prior, a minimal fraction of the data is used to obtain a posterior that is subsequently used as proper prior, we refer to it as \textit{fractional prior} (consider  Lindley's \citeyear{lindleyBayesianStatisticsReview1972} famous quote \textit{“Today’s posterior is tomorrow’s prior”}).
 The remaining part of the data is used to compute the Bayes Factor.
@@
 Nevertheless, using subjective (reasonable) priors according to previous information or experts' indications is still a possible approach.
-Keep in mind, however, that prior specification (even if obtained through an \textit{objective procedure}) affects the Bayes Factor results.
+However, prior specification (even if obtained through an \textit{objective procedure}) affects the Bayes Factor results.
 Thus, it is fundamental to conduct a prior sensitivity analysis to evaluate the influence of prior specification on the results \parencite{schadWorkflowTechniquesRobust2021, duBayesFactorOnesample2019}.
@@
 
-At this point, several authors underline the importance of centring the prior distribution on the constraints points of interest. Let's further discuss this issue in the next section.
+At this point, several authors emphasize the importance of centering the prior distribution on the constraints points of interest. Let's further discuss this issue in the next section.
 
@@
 
-At this point, we have both the prior and the posterior distributions of the parameters of interests of the encompassing model. Before proceeding, however, let's underline some important aspects.
+At this point, we have both prior and posterior distributions of the parameters of interests of the encompassing model. Before proceeding, however, let's underline some important aspects.
 
@@
 
-Analogously, it is possible to compute the \textbf{marginal posterior density} $\pi_{adj}(\beta_E =0| Y, H_u)$ considering this time the estimated posterior mean vector $\bm{\hat{\beta}}$ and the estimated  posterior covariance matrix $\hat{\Sigma}_{\beta}$.
+Similarly, it is possible to compute the \textbf{marginal posterior density} $\pi_{adj}(\beta_E =0| Y, H_u)$ considering this time the estimated posterior mean vector $\bm{\hat{\beta}}$ and the estimated  posterior covariance matrix $\hat{\Sigma}_{\beta}$.
 
@@
 
-To compute the Bayes Factor between different informative hypotheses, we can simply consider the ratio of the Bayes Factor of each hypothesis against the encompassing model:
+To compute the Bayes Factor between two different informative hypotheses, we can simply consider the ratio of the Bayes Factor of each hypothesis against the encompassing model:
 \begin{equation}
@@
 The described approach using (multivariate) normal approximation can be straightforward applied when parameters of interest are unbounded.
-In the case of bounded parameters (i.e., variances, correlations, or probabilities), however, appropriate prior distributions are required to take into account the parameters bounded nature.
+However, in the case of bounded parameters (i.e., variances, correlations, or probabilities), appropriate prior distributions are required to take into account the parameters bounded nature.
 
@@
 
-Note that these issues are relevant only when considering the prior distribution.
+These issues are relevant only when considering the prior distribution.
 In the case of the posterior distribution, instead, we can safely approximate it to a (multivariate) normal distribution thanks to the large-sample theory.
@@
 
-\section{A Case Study: Hypotheses Testing in the Attachment Theory}
-
-In this section, we propose a real case study evaluating different informative hypotheses within the attachment theory.
+\section{A Case Study: Hypotheses Testing in Attachment Theory}
+
+In this section, we propose a real case study evaluating different informative hypotheses within attachment theory.
 This will allow us to face the common issues found in real research applications.
-First, we provide the required background information regarding the attachment theory and the study aims and characteristics.
+First, we provide the required background information regarding attachment theory and the study aims and characteristics.
 Subsequently, all the steps involved in the evaluation of informative hypotheses using the Bayes Factor with the encompassing prior approach are described.
@@
 Attachment theory originates from the pioneering work of \textcite{bowlbyAttachmentLoss1969} and Ainsworth (\citeyear{ainsworthAttachmentExplorationSeparation1970}).
-They postulates that children in stressful situations actively seek proximity of the caregiver through some attachment behaviors (e.g., crying; moving towards the caregiver) in order to fulfil the evolutionary goal of protection from dangers.
+They postulate that children in stressful situations actively seek proximity of the caregiver through some attachment behaviors (e.g., crying; moving towards the caregiver) in order to fulfil the evolutionary goal of protection from dangers.
 The main tenet of attachment theory is that the relationships with the caregivers that children develop in the early stages of their life (i.e., \textit{attachment bond}) will affect children’s social-emotional future development \parencite{cassidyHandbookAttachmentTheory2016}.
 Besides behavior, people construct mental representations, or working models, of the self and significant others based on their interpersonal experiences.
-Four main attachment styles have been recognized in the literature according to different internal representations:
+Describing individual differences in self reported attachment mental representations, empirical research suggested a model based on two dimensional traits \parencite{mikulincerAttachmentAdulthoodStructure2007}: attachment avoidance (characterized by discomfort with closeness, excessive self-reliance, and difficulty in relying on others for obtaining security) and attachment anxiety (characterized by low self-worth and fear of abandonment and rejection).
+This perspective, initially developed with adult participants, has been extended to the study of self reported attachment representations also during childhood, even to middle childhood \parencite{kernsAttachmentMiddleChildhood2005, marciBriefExperiencesClose2019} .
+The two dimensions of attachment mental representations can be combined to provide four different attachment styles:
+
 \begin{itemize}
@@
 
-The attachment theory is one of the main and most supported theories in psychology \parencite{cassidyHandbookAttachmentTheory2016}.
+Attachment theory is one of the main and most supported theories in psychology \parencite{cassidyHandbookAttachmentTheory2016}.
 In the literature, however, there is still an open debate on the relative role of mother and father attachment on children's social-emotional development.
@@
 No study, however, has tried to properly evaluate the different theoretical perspectives by directly comparing the different hypotheses.
-[TODO add some references]
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Present Study}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{The Present Study}
 
@@
 Separate scores for externalizing and internalizing problems were obtained as sum of the questionnaire items.
-In the analysis, however, only externalizing problems  are considered as teachers are expected to be better at reporting externalizing problems than internalizing problems [TODO spiegare meglio il perchè?
-aggiungere ref?].
-The distribution of externalizing problems ($\text{Mean} = \Sexpr{my_round(mean(data_cluster$externalizing_sum), 2)};\ \text{SD} =  \Sexpr{my_round(sd(data_cluster$externalizing_sum), 2)};\ \text{Median} = \Sexpr{my_round(median(data_cluster$externalizing_sum), 1)}$) is presented in Figure~\ref{fig:plot-externalizing-dist}.
+For the pourpose of this work, we considered only externalizing problems  The distribution of externalizing problems ($\text{Mean} = \Sexpr{my_round(mean(data_cluster$externalizing_sum), 2)};\ \text{SD} =  \Sexpr{my_round(sd(data_cluster$externalizing_sum), 2)};\ \text{Median} = \Sexpr{my_round(median(data_cluster$externalizing_sum), 1)}$) is presented in Figure~\ref{fig:plot-externalizing-dist}.
 <<plot-externalizing-dist, cache=TRUE, fig.cap="Distribution of externalizing problems ($n_{subj} = 847$).">>=
@@
 More information about the sample, descriptive statistics, cluster analysis, and analysis of internalizing problems can be found in the Supplemental Material available online \url{https://claudiozandonella.github.io/Attachment/}.
+All materials and data are available at [TODO].
 
@@
 Maybe we did not consider some important aspects and new hypotheses may reveal themselves to be actually much better than the previous ones.
-For example, regarding the attachment results, taking into account the interaction between children's gender and attachment may be fundamental (do you expect that attachment towards the father plays a different role between girls and boys?).
+For example, regarding the attachment results, taking into account the interaction between children's gender and attachment may be fundamental (is it possible that attachment towards the father plays a different role between girls and boys?).
 This limit, however, becomes an advantage as it forces the researchers to focus on the definition of the hypotheses: to obtain good answers first we need to ask the right questions.
@@
 
-As underlined by \textcite[p.229]{guApproximatedAdjustedFractional2018}, “this class of informative hypotheses covers a much broader range of scientific expectations than the class of standard null hypotheses.
+As emphasized by \textcite[p.229]{guApproximatedAdjustedFractional2018}, “this class of informative hypotheses covers a much broader range of scientific expectations than the class of standard null hypotheses.
 In addition, by testing competing informative hypotheses directly against each other a researcher obtains a direct answer as to which scientific theory is most supported by the data”.

### 2021-11-10 R/Plots.R

@@ -151,7 +151,7 @@ plot_attachment_marginal <- function(mother_score = c(0.05, 0.5, 0.5, 1),
              stat = "identity", show.legend = FALSE, alpha = .8, col = "gray20") +
     ylim(0, 1) +
     facet_grid(Parent ~ .) +
-    labs(x = "Attachemnt Style",
+    labs(x = "Attachment Style",
          y = lab_y) +
     theme_classic() +
     theme(axis.ticks.y = element_blank(),

### 2021-11-10 R/Tables.R

@@ -18,7 +18,7 @@ get_table_cluster <- function(perc = TRUE, digits = 2, format = "latex"){
     bind_rows(tibble(mother = "Total",
                      summarise_at(., vars(Secure:Total), sum))) %>%
     kable(., format = format, booktabs = TRUE, align = c("r", rep("c", 5)),
-          col.names = c("Mother Attachemnt", "Secure", "Anxious", "Avoidant", "Fearful", "Total"),
+          col.names = c("Mother Attachment", "Secure", "Anxious", "Avoidant", "Fearful", "Total"),
           caption = "Attachment styles frequencies ($n_{subj} = 847$).") %>%
     add_header_above(c(" ", "Father Attachment" = 4, " "), bold = TRUE) %>%
     row_spec(0, bold = TRUE) %>%
@@ -42,7 +42,7 @@ get_table_cluster_ext <- function(){
     select(mother, dplyr::ends_with("Secure"), dplyr::ends_with("Anxious"),
            dplyr::ends_with("Avoidant"),  dplyr::ends_with("Fearful")) %>%
     kable(.,format = "latex", booktabs = TRUE, align = c("r", rep("c", 8)),
-          col.names = c("Mother Attachemnt", rep(c("Mean (SD)", "Median"), 4)),
+          col.names = c("Mother Attachment", rep(c("Mean (SD)", "Median"), 4)),
           caption = "Externalizing problems according to attachment styles ($n_{subj} = 847$).") %>%
     add_header_above(c(" ", "Secure" = 2, "Anxious" = 2, "Avoidant" = 2, "Fearful" = 2), bold = TRUE) %>%
     add_header_above(c(" ", "Father Attachment" = 8), bold = TRUE) %>%
@@ -106,7 +106,7 @@ get_table_bf <- function(bf_result = BF_weights_ext,
     # mutate_at(c("hypothesis", "bf","weights"), centerText) %>%
     kable(., format = format, booktabs = TRUE, align = c("r", rep("c", 3)), escape = FALSE,
           col.names = c("Hypothesis", "Bayes Factor", "Posterior Probability", " "),
-          caption = "Bayes Factor encompassing model and hypothesis posteriro probabilities  ($n_{subj} = 847$).") %>%
+          caption = "Bayes Factor encompassing model and hypothesis posterior probabilities  ($n_{subj} = 847$).") %>%
     column_spec(4, image = spec_image(images, image_size, image_size),
[…]

### 2021-11-27 Documents/Paper/paper.Rnw
corrige eng

@@
 
-\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A tutorial using the Bayes Factor via the Encompassing Prior Approach}
+\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach}
 \shorttitle{The Bayes Factor via the Encompassing Prior Approach}
@@
 \abstract{When conducting a study, researchers usually have expectations based on hypotheses or theoretical perspectives they want to evaluate.
-Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called “\textit{informative hypotheses}”.
+Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called informative hypotheses.
 However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are unsuitable for testing complex informative hypotheses.
-An alternative approach is to use the Bayes Factor.
-In particular, the Bayes Factor based on the “\textit{encompassing prior approach}” allows researchers to easily evaluate complex informative hypotheses.
-This paper provides a detailed introduction to the Bayes Factor with encompassing prior.
-First, all steps and elements involved in the formalization of  informative hypotheses and computation of the Bayes Factor are described.
-Next, we apply this method to a real case scenario considering the attachment theory.
-Precisely, we analyzed the relative role of maternal and paternal attachment on children's social-emotional development by comparing the different theoretical perspectives debated in the literature.
+An alternative approach is to use the Bayes factor.
+In particular, the Bayes factor based on the encompassing prior approach allows researchers to easily evaluate complex informative hypotheses in a wide range of statistical models (e.g., generalized linear).
+This paper provides a detailed introduction to the Bayes factor with encompassing prior.
+First, all steps and elements involved in the formalization of  informative hypotheses and the computation of the Bayes factor with encompassing prior are described.
+Next, we apply this method to a real case scenario, considering the attachment theory.
+Specifically, we analyzed the relative influence of maternal and paternal attachment on children's social-emotional development by comparing the various theoretical perspectives debated in the literature.
 
@@
 
-\noindent The evaluation of hypotheses is one of the main goals of empirical research.
+The evaluation of hypotheses is one of the main goals of empirical research.
 In fact, when conducting a study, researchers usually want to evaluate the plausibility of specific hypotheses according to the collected data.
-These hypotheses can be formalized in accordance with researchers' expectations or theoretical perspectives into the so-called “\textit{informative hypotheses}”.
+These hypotheses can be formalized in accordance with researchers' expectations or theoretical perspectives into the so-called informative hypotheses.
 However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are not suitable for evaluating the plausibility of complex informative hypotheses.
-The Bayes Factor via the “\textit{encompassing prior approach}”, instead, allows researchers to easily evaluate the plausibility of complex informative hypotheses.
-This paper provides a detailed introduction to the Bayes Factor with encompassing prior.
-First, all steps and elements involved in the formalization of  informative hypotheses and computation of the Bayes Factor are described.
-Next, we apply this method to a real case scenario considering the attachment theory.
-Precisely, we analyzed the relative role of maternal and paternal attachment on children's social-emotional development by comparing the different theoretical perspectives debated in the literature.
-This approach is of particular interest in applied research as it allows researchers to formalize hypotheses with great flexibility and to directly evaluate which hypothesis is the most supported by the data.
+Alternatively, the Bayes factor via the encompassing prior approach allows researchers to easily evaluate the plausibility of complex informative hypotheses in a wide range of statistical models.
+This paper provides a detailed introduction to the Bayes factor with encompassing prior.
+First, we describe all steps and elements involved in the formalization of  informative hypotheses and the computation of the Bayes factor.
+Next, we apply this method to a real case scenario, considering the attachment theory.
+Specifically, we analyzed the relative influence of maternal and paternal attachment on children's social-emotional development by comparing the various theoretical perspectives debated in the literature.
+This approach is of particular interest in applied research, as it allows researchers to formalize hypotheses with great flexibility and to directly evaluate which hypothesis is the most supported by the data.
 }
@@
 The dominant statistical approach to evaluate research hypotheses in psychology is the Null Hypothesis Significance Testing (NHST).
-In the literature, however, the utility and validity of NHST are largely debated \parencite{wassersteinMovingWorld052019}.
-This approach presents indeed several limitations.
-First, the NHST places a narrow focus on statistical testing rather than on the formalization of hypotheses.
-This has usually led researchers to evaluate data against the catch-all null-hypothesis that nothing is going on rather than testing their specific expectation [and the alternative hypothesis is rarely formalized].
-Second, the p-value does not quantify the evidence in favour of one hypothesis, thus, it is not possible to \textit{“accept”} a hypothesis but only to \textit{“reject”} it.
-This has some drawbacks since, in case of not significant results, the researchers are left in a state of indecision.
-Third, NHST does not allow testing multiple hypotheses at the same time.
-Using the NHST the null hypothesis is tested only against a single alternative.
-Fourth, NHST is unsuitable for testing broad classes of hypotheses with equality and inequality constraints \parencite{mulderSimpleBayesianTesting2019}.
-Expectations can be evaluated using one-side tests; however, when more groups or more variables are involved, it is not possible to evaluate complex parameter constraints that reflect researchers' expectations \parencite{vandeschootIntroductionBayesianModel2011}.
-
-Model comparison is a different approach that allows researchers to compare multiple hypotheses and identify which is the most supported by the data \parencite{mcelreathStatisticalRethinkingBayesian2020}.
-Hypotheses are first formalized as statistical models according to researchers expectations or theoretical perspectives.
-Subsequently, it is possible to evaluate which is the most supported model among those considered according to the data.
-To do that a popular approach is to use information criteria such as the AIC or BIC criteria that estimate models ability to predict new data \parencite{wagenmakersAICModelSelection2004,akaike1973a, schwarzEstimatingDimensionModel1978}.
-Model comparison has several advantages and, in particular, it allows to directly compute the relative plausibility of each model given the data and the set of models considered.
+In the literature, however, the NHST's utility and validity are largely debated \parencite{wassersteinMovingWorld052019}.
+This approach presents several limitations.
+First, the NHST places a narrow focus on statistical testing rather than on the formalization of hypotheses, leading researchers to evaluate data against the catch-all null hypothesis that nothing is going on rather than testing their specific expectation (and the alternative hypothesis is rarely formalized).
+Second, the \textit{p}-value does not quantify the evidence in favor of one hypothesis; therefore, it is not possible to \textit{“accept”} a hypothesis but only to \textit{“reject”} it.
+This situation has some drawbacks because nonsignificant results leave researchers in a state of indecision.
+Third, the NHST does not allow researchers to test multiple hypotheses at the same time.
+With the NHST, the null hypothesis is tested only against a single alternative.
+Fourth, the NHST is unsuitable for testing broad classes of hypotheses with equality and inequality constraints \parencite{mulderSimpleBayesianTesting2019}.
+Researchers can evaluate expectations using one-side tests; however, when more groups or more variables are involved, it is not possible to evaluate complex parameter constraints that reflect researchers' expectations \parencite{vandeschootIntroductionBayesianModel2011}.
+
+Model comparison is a different approach that allows researchers to compare multiple hypotheses and identify the most supported by the data \parencite{mcelreathStatisticalRethinkingBayesian2020}.
+Researchers first formalize hypotheses as statistical models according to their expectations or theoretical perspectives.
+Therefore, it is possible to determine which is the most supported model among those considered according to the data.
+To do so, a popular approach is to use information criteria, such as the AIC or BIC criteria, that estimate a model's ability to predict new data \parencite{wagenmakersAICModelSelection2004,akaike1973a, schwarzEstimatingDimensionModel1978}.
+Model comparison has several advantages; in particular, it allows researchers to directly compute each model's relative plausibility given the data and the set of models considered.
 However, model comparison using information criteria is not appropriate to evaluate hypotheses that include complex parameter constraints reflecting researchers' expectations.
-In fact, information criteria evaluate models complexity according to the number of parameters, but they do not take into account possible order constraints on the parameters.
-
-An alternative criterium to evaluate research hypotheses in a model comparison is the Bayes Factor.
-During the last 25 years, there has been an increasing interest in the Bayes Factor and its use has been proposed as the solution to the critical issues of the NHST \parencite{heckReviewApplicationsBayes2020, mulderEditorsIntroductionSpecial2016}.
-Although it has its own limitations and it does not solve the fundamental issues of the misuse of statistical techniques \parencite{schadWorkflowTechniquesRobust2021, gelmanBayesianDataAnalysis2013}, the Bayes Factor offers some clear advantages.
-In particular, the Bayes Factor allows us to compare hypotheses obtaining a relative index of evidence, like the information criteria, but it also allows us to easily compare complex research hypotheses.
-In fact, so-called \textit{“informative hypotheses”} (i.e., hypotheses containing information about the ordering of the model parameters) can be formalized according to researchers' expectations or theoretical perspectives using equality and inequality constraints \parencite{vandeschootIntroductionBayesianModel2011}.
-Subsequently, these hypotheses can be compared against each other using the Bayes Factor.
-
-The evaluation of informative hypotheses is of particular interest to the researchers as it allows them to assess specific complex expectations and theoretical perspectives directly.
-In the literature, a particular approach allowing to easily compute the Bayes Factor with complex informative hypotheses has received increasing attention: \textit{“the Bayes Factor with encompassing prior”}.
-\textcite{vandeschootIntroductionBayesianModel2011} presented a general introduction to informative hypotheses testing using the Bayes Factor with the encompassing prior approach, whereas \textcite{hoijtinkInformativeHypothesesTheory2012} offered a more detailed description of the development of this method.
-Other studies, instead, considered the application of this approach with specific statistical models; for example: mixed effect models \parencite{katoBayesianApproachInequality2006}, evaluation of correlation coefficients \parencite{mulderBayesFactorsTesting2016} and multinomial models \parencite{heckMultinomialModelsLinear2019}.
+In fact, information criteria evaluate models' complexity according to the number of parameters, but they do not take into account possible order constraints on the parameters.
+
+An alternative criterium to evaluate research hypotheses in a model comparison is the Bayes factor.
+During the last 25 years, interest in the Bayes factor has increased, and its use has been proposed as the solution to the NHST's critical issues \parencite{heckReviewApplicationsBayes2020, mulderEditorsIntroductionSpecial2016}.
+Although it has its own limitations and it does not solve the fundamental issues of the misuse of statistical techniques \parencite{schadWorkflowTechniquesRobust2021, gelmanBayesianDataAnalysis2013}, the Bayes factor offers some clear advantages.
+In particular, it allows us to compare hypotheses obtaining a relative index of evidence, like the information criteria, but it also allows us to easily compare complex research hypotheses.
+In fact, researchers can formalize so-called \textit{“informative hypotheses”}, hypotheses containing information about the ordering of the model parameters,  according to their expectations or theoretical perspectives, using equality and inequality constraints \parencite{vandeschootIntroductionBayesianModel2011}.
+Researchers can then compare these hypotheses against each other, using the Bayes factor.
+
+The evaluation of informative hypotheses is of particular interest to researchers, as it allows them to assess specific complex expectations and theoretical perspectives directly.
+In the literature, a particular approach allowing researchers to easily compute the Bayes factor with complex informative hypotheses has received increasing attention: \textit{“the Bayes factor with encompassing prior”}.
+\textcite{vandeschootIntroductionBayesianModel2011} presented a general introduction to informative hypothesis testing using the Bayes factor with the encompassing prior approach whereas \textcite{hoijtinkInformativeHypothesesTheory2012} offered a more detailed description of this method's development.
+In other studies, however, researchers considered the application of this approach with specific statistical models, such as mixed-effect models \parencite{katoBayesianApproachInequality2006}, evaluation of correlation coefficients \parencite{mulderBayesFactorsTesting2016}, and multinomial models \parencite{heckMultinomialModelsLinear2019}.
 In addition, \textcite{guBayesianEvaluationInequality2014} proposed a general approximate procedure to evaluate inequality constraints in a wide range of statistical models.
 
-However, all studies mentioned above considered only informative hypotheses with inequality constraints.
-Evaluating in the same hypothesis equality and inequality constraints, instead, it was not possible and equality constraints had to be approximated to “\textit{about equality constraints}” (i.e., a equality constraints of type $\theta_i = \theta_j$ is approximated to $|\theta_i - \theta_j| < \xi$ for a value of $\xi$ small enough).
-
-Only recently, \textcite{guApproximatedAdjustedFractional2018} introduced an approximate procedure to evaluate both equality and inequality constraints using the Bayes Factor with the encompassing prior approach in a wide range of statistical models (i.e., generalized linear mixed models and structural equation models).
-Subsequently, this approach was extended by \textcite{mulderBayesFactorTesting2019} to generalized multivariate probit models and, finally, \textcite{mulderSimpleBayesianTesting2019} proposed an accurate procedure (i.e., not based on an approximation) that allows testing informative hypotheses with equality and inequality constraints in linear regression models.
-
-The development and implementation of this approach are of particular interest because, although with its limits, it allows researchers to directly evaluate their expectations and hypotheses.
+However, in all the studies mentioned above, researchers considered only informative hypotheses with inequality constraints.
+To evaluate equality and inequality constraints in the same hypothesis, researchers had to approximate equality constraints to “\textit{about equality constraints}” (i.e., a equality constraints of type $\theta_i = \theta_j$ is approximated to $|\theta_i - \theta_j| < \xi$ for a value of $\xi$ small enough).
+
+Only recently, \textcite{guApproximatedAdjustedFractional2018} introduced an approximate procedure to evaluate equality and inequality constraints, using the Bayes factor with the encompassing prior approach in a wide range of statistical models (i.e., generalized linear mixed models and structural equation models).
+Subsequently, \textcite{mulderBayesFactorTesting2019} extended this approach to generalized multivariate probit models, and, finally, \textcite{mulderSimpleBayesianTesting2019} proposed an accurate procedure (i.e., not based on an approximation) that allows for testing of informative hypotheses with equality and inequality constraints in linear regression models.
+
+The development and implementation of this approach are of particular interest because although it has limits, it allows researchers to directly evaluate their expectations and hypotheses.
 The available literature, however, is rather technical.
-The complexity of these articles makes it difficult for researchers not familiar with this approach to clearly understand all the steps involved.
-On the other hand, articles offering a general introduction to the Bayes Factor do not provide enough details to allow readers to autonomously apply this method to their problems, but they usually rely on ad-hoc solutions implemented in some statistical software \parencite[for example consider][]{hoijtinkTutorialTestingHypotheses2019a}.
-
-The aim of this paper, therefore, is to offer a clear and detailed description of the Bayes Factor with the encompassing prior approach to allow other researchers to apply this approach in their studies.
-In particular, we refer to the approximated method proposed by \textcite{guApproximatedAdjustedFractional2018} as it applies to a wider range of conditions than the more accurate approach proposed by \textcite{mulderSimpleBayesianTesting2019}.
+These articles' complexity makes it difficult for researchers not familiar with this approach to clearly understand all the steps involved.
+On the other hand, articles offering a general introduction to the Bayes factor do not provide enough details to allow readers to autonomously apply this method to their problems; instead, they usually rely on ad hoc solutions implemented in some statistical software.
+For example, \textcite{hoijtinkTutorialTestingHypotheses2019a} offered an excellent introduction to the Bayes factor for the evaluation of informative hypotheses using the R package \texttt{bain}.
+However, it is limited to the context of analysis-of-variance models, and it is not possible to extend its use to other cases.
+
+The aim of this paper, therefore, is to offer a clear and detailed description of the Bayes factor with the encompassing prior approach to allow other researchers to apply this approach in their studies.
+In particular, we refer to the approximated method \textcite{guApproximatedAdjustedFractional2018} proposed, as it applies to a wider range of conditions than the more accurate approach \textcite{mulderSimpleBayesianTesting2019} introduced.
+In particular, researchers can use the proposed method in the case of generalized linear mixed models and structural equation models, two very general families of statistical models.
+Moreover, by providing an exhaustive description of all of this approach's steps, researchers do not have to rely on already available solutions; instead, they can implement this approach according to their specific needs.
 The paper is organized as follows.
-First, the method is introduced providing a detailed description of all steps and elements involved in the formalization of informative hypotheses and Bayes Factor computation.
-Subsequently, an application of the method to real data is presented to offer the opportunity to discuss the typical issues encountered in real complex scenarios.
+First, we introduce the method, providing a detailed description of all steps and elements involved in the formalization of informative hypotheses and Bayes factor computation.
+We then present an application of the method to real data to discuss the typical issues encountered in real complex scenarios.
 
@@
 In this section, first, we describe how to formulate informative hypotheses.
-Subsequently, we introduce the Bayes Factor considering the encompassing prior approach based on the approximated method proposed by \textcite{guApproximatedAdjustedFractional2018}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Formulation of Informative Hypothesis}\label{sec:informative-hypothesis}
-
-Informative hypotheses can be defined according to researchers' expectation, evidence from the literature or theoretical perspectives and they are formed by equality and/or inequality constraints on certain model parameters.
+We then introduce the Bayes factor, considering the encompassing prior approach based on the approximated method \textcite{guApproximatedAdjustedFractional2018} proposed.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Formulation of Informative Hypotheses}\label{sec:informative-hypotheses}
+
+Researchers can define informative hypotheses according to their expectation, evidence from the literature, or theoretical perspectives, and they form them with equality and/or inequality constraints on certain model parameters.
 These constraints are obtained as a linear combination of certain parameters and eventual constant values.
-For example, it is possible to state that two parameters are equal ($\theta_i = \theta_j$), one parameter is greater than another ($\theta_i > \theta_j$), or express other complex conditions as the difference between two parameter is less than a given value ($\theta_i - \theta_j < .5$; $2\times\theta_i - \theta_j < .1 \times \sigma$).
-
-Thus, an informative hypothesis $H_i$ with equality and inequality constraints can be expressed in the form
+For example, it is possible to state that two parameters are equal ($\theta_i = \theta_j$) or that one parameter is greater than another ($\theta_i > \theta_j$) or to express other complex conditions, such as the difference between two parameter is less than a given value ($\theta_i - \theta_j < .5$; $2\times\theta_i - \theta_j < .1 \times \sigma$).
+
+Therefore, an informative hypothesis, $H_i$, with equality and inequality constraints can be expressed in the form
 \begin{equation}
@@
 \end{equation}
-where $R_E$ is a matrix expressing the equality constraints and $r_E$ is a vector containing the constant values of the equality constraints.
-Whereas, $R_I$ is a matrix expressing the inequality constraints and $r_E$ is a vector containing the constant values of the inequality constraints.
+where $R_E$ is a matrix expressing the equality constraints and $r_E$ is a vector containing the equality constraints' constant values.
+$R_I$ is a matrix expressing the inequality constraints, and $r_E$ is a vector containing the inequality constraints' constant values.
 Finally, $\bm{\theta}$ is a vector with the model parameters involved in the constraints.
@@
 Moreover, imagine that the new psychological treatment was administered in three different modalities to different groups: individually, in-group, and online.
-Researchers expect no differences between the three modalities but they hypothesize that the new treatment will perform better than the traditional one and this, in turn, will be better than the no-treatment control condition.
+Researchers expect no differences between the three modalities, but they hypothesize that the new treatment will perform better than the traditional one, and this result, in turn, will be better than the no-treatment control condition.
 We can express this hypothesis as
@@
 \end{equation}
-were $\theta_{control}$ is the parameter estimating the average score of the no-treatment control group, $\theta_{traditional}$ is the parameter estimating the average score of the group receiving the traditional treatment, and $\theta_{individual}$, $\theta_{group}$, and $\theta_{online}$ are the parameters estimating the average scores of the groups receiving the new treatment individually, in group, and on-line, respectively.
-The corresponding formulation of the hypothesis using the matrix notation introduced before is
+were $\theta_{control}$ is the parameter estimating the average score of the no-treatment control group, $\theta_{traditional}$ is the parameter estimating the average score of the group receiving the traditional treatment, and $\theta_{individual}$, $\theta_{group}$, and $\theta_{online}$ are the parameters estimating the average scores of the groups receiving the new treatment individually, in-group, and online, respectively.
+The corresponding formulation of the hypothesis using the matrix notation previously introduced is
 \begin{equation}
@@
 Note how each row of $R_E$ and $R_I$ matrices expresses an equality or an inequality constraint, respectively.
-For example, in the first row of $R_E$ we have $\theta_{individual} - \theta_{group} = 0$ (i.e., $\theta_{individual} = \theta_{group}$) and in the first row of $R_I$ we have $\theta_{traditional} - \theta_{control} > 0$ (i.e., $\theta_{traditional} > \theta_{control}$).
-
-Now that we have understood how to define an informative hypothesis with equality and inequality constraints introducing an appropriate notation, let's see how to evaluate an informative hypothesis using the Bayes Factor with the encompassing prior approach.
+For example, in the first row of $R_E$, we have $\theta_{individual} - \theta_{group} = 0$ (i.e., $\theta_{individual} = \theta_{group}$) and in the first row of $R_I$ we have $\theta_{traditional} - \theta_{control} > 0$ (i.e., $\theta_{traditional} > \theta_{control}$).
+
+Now that we have explained how to define an informative hypothesis with equality and inequality constraints introducing an appropriate notation, let's see how to evaluate an informative hypothesis using the Bayes factor with the encompassing prior approach.
 
@@
 
-The Bayes Factor of hypothesis $H_1$ against a competing hypothesis $H_2$ is defined as the ratio between the marginal likelihoods of the two hypotheses:
+The Bayes factor of hypothesis $H_1$ against a competing hypothesis, $H_2$, is defined as the ratio between the marginal likelihoods of the two hypotheses:
 \begin{equation}
@@
 where $Y$ indicates the data, $\theta_i$ is the vector of parameters under the hypothesis $H_i$, $l(Y|\theta_i, , H_i)$ is the likelihood function under the hypothesis $H_i$, and $\pi(\theta_i| H_i)$ is the prior of the parameters under the hypothesis $H_i$.
-The marginal likelihood $Pr(Y|H_i)$ can be interpreted as a measure of the plausibility of the data under $H_i$.
-
-Therefore, the Bayes Factor $BF_{12}$ quantifies the relative support of the data for the two competing hypotheses (and not the ratio between the probability of the two hypotheses).
-For values close to 1, the Bayes Factor indicates that $H_1$ and $H_2$ have similar support from the data.
-Larger values indicate evidence in favour of $H_1$, whereas values close to 0 indicate evidence in favour of $H_2$.
-The ratio between the posterior probabilities of the two hypotheses can be computed as
+The marginal likelihood $Pr(Y|H_i)$ can be interpreted as a measure of the data's plausibility under $H_i$.
+
+Therefore, the Bayes factor, $BF_{12}$, quantifies the relative support of the data for the two competing hypotheses (and not the ratio between the probability of the two hypotheses).
+For values close to 1, the Bayes factor indicates that $H_1$ and $H_2$ have similar support from the data.
+Larger values indicate evidence in favor of $H_1$ whereas values close to 0 indicate evidence in favor of $H_2$.
+The ratio between these two hypotheses' posterior probabilities can be computed as
 \begin{equation}
@@
 where $Pr(H_i)$ is the prior probability of $H_i$ and $Pr(H_i|Y)$ is the posterior probability of $H_i$.
-For a detailed description of the Bayes Factor considering also its interpretation and application in different contexts see \textcite{wagenmakersBayesianHypothesisTesting2010, mulderEditorsIntroductionSpecial2016, heckReviewApplicationsBayes2020}.
-
-Note that to compute the marginal likelihood $Pr(Y|H_i)$ of a hypothesis $H_i$ it is necessary to integrate the product between the likelihood and the prior.
-These integrals, however, are usually difficult to compute [in particular when hypotheses include order constraints].
-In the case of hypotheses with equality and inequality constraints, however, it is possible to simplify the computation of the Bayes Factor using the encompassing prior approach.
+For a detailed description of the Bayes factor, considering also its interpretation and application in various contexts see \textcite{wagenmakersBayesianHypothesisTesting2010, mulderEditorsIntroductionSpecial2016, heckReviewApplicationsBayes2020}.
+
+Note that to compute the marginal likelihood $Pr(Y|H_i)$ of a hypothesis, $H_i$, it is necessary to integrate the product between the likelihood and the prior.
+These integrals, however, are usually difficult to compute (in particular when hypotheses include order constraints).
+In the case of hypotheses with equality and inequality constraints, however, it is possible to simplify the computation of the Bayes factor using the encompassing prior approach.
 
@@
 
-The basic idea of the encompassing prior approach is to consider an informative hypothesis as a subset of the parameter space of an unconstrained model.
-Thus, to evaluate the plausibility of a hypothesis we can consider the proportion of parameter space of the unconstrained model that satisfies the constraints.
-More specifically, given an informative hypothesis $H_i$ and an unconstrained model $H_u$ (or \textit{encompassing model}) that does not contain any constraints on the parameters, if the prior under $H_i$ is defined as a truncation of the proper prior under $H_u$ (\textit{encompassing prior}) according to the constraints, then the Bayes Factor between $H_i$ and $H_u$ can be written as
+The basic idea of the encompassing prior approach is to consider an informative hypothesis as a subset of an unconstrained model's parameter space.
+Therefore, to evaluate a hypothesis's plausibility, we can consider the proportion of parameter space of the unconstrained model that satisfies the constraints.
+More specifically, given an informative hypothesis, $H_i$, and an unconstrained model, $H_u$, (or \textit{encompassing model}) that does not contain any constraints on the parameters, if the prior under $H_i$ is defined as a truncation of the proper prior under $H_u$ (\textit{encompassing prior}) according to the constraints, then the Bayes factor between $H_i$ and $H_u$ can be written as
 \begin{equation}\label{eq:BF-encompassing}
@@
 
-The first term is the ratio between the conditional posterior probability and the conditional prior probability that the inequality constraints hold under the unconstrained model $H_u$ given the equality constraints.
+The first term is the ratio between the conditional posterior probability and the conditional prior probability that the inequality constraints hold under the unconstrained model, $H_u$, given the equality constraints.
 The second term is the ratio between marginal posterior density and the marginal prior density of the equality constraints under $H_u$ \parencite[the well-known Savage–Dickey density ratio; ][]{dickeyWeightedLikelihoodRatio1971, wetzelsEncompassingPriorGeneralization2010}.
@@
 \begin{itemize}
-  \item{The \textbf{conditional posterior probability} $Pr(R_I\theta > r_I | R_E\theta =r_E, Y, H_u)$ is a measure of the fit of the inequality constraints of $H_i$ under $H_u$.}
-  \item{The \textbf{conditional prior probability} $\pi(R_I\theta > r_I | R_E\theta =r_E, H_u)$ is a measure of the complexity of the inequality constraints of $H_i$ under $H_u$.}
-  \item{The \textbf{marginal posterior density} $Pr(R_E\theta =r_E| Y, H_u)$ is a measure of the fit of the equality constraints of $H_i$ under $H_u$.}
-  \item{The \textbf{marginal prior density} $\pi(R_E\theta =r_E| H_u)$ is a measure of the complexity of the equality constraints of $H_i$ under $H_u$.}
+  \item{The \textbf{conditional posterior probability}, $Pr(R_I\theta > r_I | R_E\theta =r_E, Y, H_u)$, is a measure of the fit of the inequality constraints of $H_i$ under $H_u$.}
+  \item{The \textbf{conditional prior probability}, $\pi(R_I\theta > r_I | R_E\theta =r_E, H_u)$, is a measure of the complexity of the inequality constraints of $H_i$ under $H_u$.}
+  \item{The \textbf{marginal posterior density}, $Pr(R_E\theta =r_E| Y, H_u)$, is a measure of the fit of the equality constraints of $H_i$ under $H_u$.}
+  \item{The \textbf{marginal prior density}, $\pi(R_E\theta =r_E| H_u)$, is a measure of the complexity of the equality constraints of $H_i$ under $H_u$.}
 \end{itemize}
-Summarizing at the denominators we have measures of the \textbf{complexity} of the inequality and equality constraints of the informative hypothesis $H_i$; at the numerators, instead, we have measures of the \textbf{fit} of the data to the inequality and equality constraints of the informative hypothesis $H_i$.
-Thus, if the hypothesis $H_i$, although applying constraints to the parametric space (less complexity), is still able to provide a good description of the data, the Bayes Factor will favour $H_i$.
-On the contrary, if the support of the data is poor, the Bayes Factor will favour the unconstrained model $H_u$.
-
-The proof of the formulation of the Bayes Factor with the encompassing prior approach and the evaluation of its consistency (i.e., the probability of selecting the correct hypothesis goes to 1 for the sample size going to infinity) is provided in \textcite{guApproximatedAdjustedFractional2018, mulderBayesFactorTesting2019}.
-Note that slightly different notation is used here to enhance comprehension and underline that at the numerators we have values computed from the posterior of $H_u$, whereas at the denominators we have values computed from the prior of $H_u$.
-
-To compute the Bayes Factor with the encompassing prior approach, only the prior and the posterior of the unconstrained model are required.
+Summarizing at the denominators, we have measures of the \textbf{complexity} of the inequality and equality constraints of the informative hypothesis $H_i$; at the numerators, instead, we have measures of the \textbf{fit} of the data to the inequality and equality constraints of the informative hypothesis $H_i$.
+Therefore, if the hypothesis $H_i$, although applying constraints to the parametric space (less complexity), can still provide an accurate description of the data, the Bayes factor will favor $H_i$.
+On the contrary, if the support of the data is poor, the Bayes factor will favor the unconstrained model, $H_u$.
+
+The proof of the formulation of the Bayes factor with the encompassing prior approach and the evaluation of its consistency (i.e., the probability of selecting the correct hypothesis goes to 1 for the sample size going to infinity) is provided in \textcite{guApproximatedAdjustedFractional2018, mulderBayesFactorTesting2019}.
+Note that slightly different notation is used here to enhance comprehension and emphasize that at the numerators, we have values computed from the posterior of $H_u$ whereas at the denominators, we have values computed from the prior of $H_u$.
+
+To compute the Bayes factor with the encompassing prior approach, only the prior and the posterior of the unconstrained model are required.
 To obtain them, first, we need to define the encompassing prior of the unconstrained model.
@@
 
-Prior specification is an important element as the resulting Bayes Factor value is affected by the prior choice.
-This is particularly relevant in the case of equality constraints \parencite{lindleyStatisticalParadox1957, bartlettCommentLindleyStatistical1957}, whereas inequality constraints are not affected as long as the prior is symmetric and centred to the focal point of interest (this feature will be further discussed in Section~\ref{sec:adj-prior}).
-
-To avoid arbitrary prior specification, different methods have been proposed in the literature.
-For example: Jeffreys-Zellner-Siow (JZS) objective priors do not require subjective specification \parencite{jeffreysTheoryProbability1961,zellnerPosteriorOddsRatios1980, bayarriExtendingConventionalPriors2007}; partial Bayes Factor \parencite{desantisMethodsDefaultRobust1999} defines the prior according to part of the data, whereas the remaining part is used to compute the Bayes Factor; intrinsic Bayes Factor \parencite{bergerIntrinsicBayesFactor1996} and fractional Bayes Factor \parencite{ohaganFractionalBayesFactors1995} are a variation of the partial Bayes Factor where priors are defined according to the average of all possible minimal subsets of the data or to a given small fraction of the data, respectively.
-
-Both, \textcite{guApproximatedAdjustedFractional2018, mulderSimpleBayesianTesting2019} based their approach on the fractional Bayes Factor.
-Starting from a non-informative prior, a minimal fraction of the data is used to obtain a posterior that is subsequently used as proper prior, we refer to it as \textit{fractional prior} (consider  Lindley's \citeyear{lindleyBayesianStatisticsReview1972} famous quote \textit{“Today’s posterior is tomorrow’s prior”}).
-The remaining part of the data is used to compute the Bayes Factor.
-The two approaches, however, have an important difference.
+Prior specification is an important element as the resulting Bayes factor value is affected by the prior choice.
+This is particularly relevant in the case of equality constraints \parencite{lindleyStatisticalParadox1957, bartlettCommentLindleyStatistical1957}, whereas inequality constraints are not affected as long as the prior is symmetric and centered on the focal point of interest.
+We will discuss this feature further in Section~\ref{sec:adj-prior}.
+
+To avoid arbitrary prior specification, researchers have proposed various methods.
+For example: Jeffreys-Zellner-Siow objective priors do not require subjective specification \parencite{jeffreysTheoryProbability1961,zellnerPosteriorOddsRatios1980, bayarriExtendingConventionalPriors2007}; partial Bayes factor \parencite{desantisMethodsDefaultRobust1999} defines the prior according to part of the data whereas the remaining part is used to compute the Bayes factor; intrinsic Bayes factor \parencite{bergerIntrinsicBayesFactor1996} and fractional Bayes factor \parencite{ohaganFractionalBayesFactors1995} are variations on the partial Bayes factor where priors are defined according to the average of all possible minimal subsets of the data or to a given small fraction of the data, respectively.
+
+\textcite{guApproximatedAdjustedFractional2018, mulderSimpleBayesianTesting2019} based their approaches on the fractional Bayes factor.
+Starting from a noninformative prior, a minimal fraction of the data is used to obtain a posterior that is subsequently used as proper prior, which we refer to as \textit{fractional prior} Consider  Lindley's (\citeyear{lindleyBayesianStatisticsReview1972}) famous quote, \textit{“Today’s posterior is tomorrow’s prior”}.
+The remaining part of the data is used to compute the Bayes factor.
+These two approaches, however, have an important difference.
 \textcite{guApproximatedAdjustedFractional2018} approximated the obtained fractional prior (as well as the posterior, see Section~\ref{sec:posterior-encompassing}) to a (multivariate) normal distribution.
-In fact, due to large-sample theory \parencite{gelmanBayesianDataAnalysis2013}, parameter posterior distribution can be approximated to a (multivariate) normal distribution.
+In fact, according to large-sample theory \parencite{gelmanBayesianDataAnalysis2013}, parameter posterior distribution can be approximated to a (multivariate) normal distribution.
 On the contrary, \textcite{mulderSimpleBayesianTesting2019} provided an analytic solution in the case of linear regression models, obtaining an accurate quantification of the distribution.
@@
 Nevertheless, using subjective (reasonable) priors according to previous information or experts' indications is still a possible approach.
-However, prior specification (even if obtained through an \textit{objective procedure}) affects the Bayes Factor results.
-Thus, it is fundamental to conduct a prior sensitivity analysis to evaluate the influence of prior specification on the results \parencite{schadWorkflowTechniquesRobust2021, duBayesFactorOnesample2019}.
+However, prior specification (even if obtained through an \textit{objective procedure}) affects the Bayes factor results.
+Therefore, it is necessary to conduct a prior sensitivity analysis to evaluate the influence of prior specification on the results \parencite{schadWorkflowTechniquesRobust2021, duBayesFactorOnesample2019}.
 
 Going back to our psychological treatment example, we could use independent normal distributions to specify the prior of each parameter of interest (i.e.
-$\theta_{control}$, $\theta_{traditional}$, $\theta_{individual}$, $\theta_{group}$, and $\theta_{online}$) obtaining as resulting prior a multivariate normal distribution with mean vector $\mu_{\theta}$ and covariance matrix $\Sigma_{\theta}$.
-In this way, we can still follow the approach proposed by \textcite{guApproximatedAdjustedFractional2018}, based on normal approximation, that will simplify the computation of the Bayes Factor.
-For example, suppose that, according to experts' indications, a reasonable prior choice for all parameters of interest is a normal distribution with mean zero and standard deviation 2:  $\mathcal{N}(0,2)$.
+$\theta_{control}$, $\theta_{traditional}$, $\theta_{individual}$, $\theta_{group}$, and $\theta_{online}$), obtaining as resulting prior a multivariate normal distribution with mean vector $\mu_{\theta}$ and covariance matrix $\Sigma_{\theta}$.
+In this way, we can still follow the approach \textcite{guApproximatedAdjustedFractional2018} proposed based on normal approximation, which will simplify the computation of the Bayes factor.
+For example, suppose that, according to experts' indications, a reasonable prior choice for all parameters of interest is a normal distribution with a mean of 0 and standard deviation of 2:  $\mathcal{N}(0,2)$.
 The resulting prior is a multivariate normal distribution with mean vector $\mu_{\theta}$ and covariance matrix $\Sigma_{\theta}$:
@@
 
-At this point, several authors emphasize the importance of centering the prior distribution on the constraints points of interest. Let's further discuss this issue in the next section.
+At this point, several authors emphasize the importance of centering the prior distribution on the constraints' points of interest. Let's further discuss this issue in the next section.
 
@@
 
-When evaluating informative hypotheses with equality and inequality constraints using the Bayes Factor, the priors have to be centred on the focal points of interests  \parencite{zellnerPosteriorOddsRatios1980, jeffreysTheoryProbability1961, mulderPriorAdjustedDefault2014}.
-In the case of equality constraints, centring the prior allows one to consider values close to the point of interest more likely a priori than distant values.
-This should be in line with researchers' expectations, otherwise one could question why testing that value.
-
-In the case of inequality constraints, instead, this adjustment is done to guarantee that no constraint is favoured a priori.
-Consider the example represented in Figure~\ref{fig:plot-prior-adj} where the hypothesis $\theta_i > k$ is evaluated against $\theta_i < k$.
-Remember that, when computing the Bayes Factor, the prior probability that the constraint holds is used as a measure of the complexity of the hypothesis.
-Thus, if the prior is not centred on the focal point of interest (i.e., $k$), the less complex hypothesis (i.e., $\theta_i > k$ ) will be erroneously preferred a priori over the other (i.e., $\theta_i < k$ ).
-Only by centring the prior on the focal point, the hypotheses will be equally likely a priori.
+When researchers evaluates informative hypotheses with equality and inequality constraints using the Bayes factor, they must center the priors on the focal points of interest  \parencite{zellnerPosteriorOddsRatios1980, jeffreysTheoryProbability1961, mulderPriorAdjustedDefault2014}.
+In the case of equality constraints, centering the prior allows one to consider values close to the point of interest more likely a priori than distant values.
+This adjustment should be in line with researchers' expectations; otherwise, one could question why he or she is testing that value.
+
+In the case of inequality constraints, instead, this adjustment is done to guarantee that no constraint is favored a priori.
+Consider the example represented in Figure~\ref{fig:plot-prior-adj}, where the hypothesis $\theta_i > k$ is evaluated against $\theta_i < k$.
+Remember that, when computing the Bayes factor, the prior probability that the constraint holds is used as a measure of the hypothesis's complexity.
+Therefore, if the prior is not centered on the focal point of interest (i.e., $k$), the less complex hypothesis (i.e., $\theta_i > k$ ) will be erroneously preferred a priori over the other (i.e., $\theta_i < k$ ).
+The hypotheses will be equally likely a priori only when the prior is centered on the focal point.
 
@@
 
-Centering the prior to the focal point, however, can be difficult in the case of complex hypotheses where constraints are defined as a linear combination of several parameters.
+Centering the prior to the focal point, however, can be difficult in the case of complex hypotheses in which constraints are defined as a linear combination of several parameters.
 To overcome this issue, \textcite{guApproximatedAdjustedFractional2018} proposed the following transformation of the parameters of interest:
@@
 where $\bm{\theta}$ is the vector of original parameters, $R$ is the matrix expressing equality and inequality constraints, and $r$ is the vector with the constants of the equality and inequality constraints.
-Doing this, the informative hypothesis under evaluation becomes:
+The informative hypothesis under evaluation then becomes:
 \begin{equation}
@@
 In fact, for example, evaluating $\theta_i > \theta_j$ is equivalent to evaluating $\beta_i = \theta_i - \theta_j > 0$.
-Thus, given the original prior $\pi(\bm{\theta})\sim\mathcal{N}(\mu_{\theta}, \Sigma_{\theta})$, the prior of the new parameter vector $\bm{\beta}$ is given by
+Therefore, given the original prior $\pi(\bm{\theta})\sim\mathcal{N}(\mu_{\theta}, \Sigma_{\theta})$, the prior of the new parameter vector $\bm{\beta}$ is given by
 \begin{equation}\label{eq:normal-transf}
@@
 
-Note that this operation is nothing more than applying a linear transformation to the original multivariate normal distribution.\footnote{Given a multivariate normal distribution $Y\sim\mathcal{N}(\mu, \Sigma)$, the result of a linear transformation $AY + b$ is still a multivariate normal distribution with vector mean $\mu_{t}=AY+b$ and covariance matrix $\Sigma_{t} = A\Sigma A^T$.} In order to do that, however, the matrix $R$ must be \textit{full-row-rank} (i.e., all rows are linearly independent).
+Note that this operation is nothing more than applying a linear transformation to the original multivariate normal distribution.\footnote{Given a multivariate normal distribution $Y\sim\mathcal{N}(\mu, \Sigma)$, the result of a linear transformation $AY + b$ is still a multivariate normal distribution with vector mean $\mu_{t}=AY+b$ and covariance matrix $\Sigma_{t} = A\Sigma A^T$.} To do that, however, the matrix $R$ must be \textit{full-row-rank} (i.e., all rows are linearly independent).
 If this is not the case, the obtained matrix $\Sigma_{\beta}$ will not be a proper covariance matrix.
@@
 
-Now, to center the prior of $\bm{\beta}$ to the focal points, we can simply set the mean vector to zero. Thus, the adjusted prior of $\bm{\beta}$ is
+Now, to center the prior of $\bm{\beta}$ to the focal points, we can simply set the mean vector to 0. Therefore, the adjusted prior of $\bm{\beta}$ is
 \begin{equation}
@@
 
-Considering the psychological treatment example, the obtained adjusted prior is $\mathcal{N}(\bm{0}, \Sigma_{\beta})$ where:
+Considering the psychological treatment example, the obtained adjusted prior is $\mathcal{N}(\bm{0}, \Sigma_{\beta})$, where:
 \begin{equation}
@@
 
-So far we have defined the prior for the parameter vector $\bm{\theta}$ of the encompassing model.
-Moreover, we have obtained the adjusted prior for the new transformed parameter vector $\bm{\beta}$ that will allow us to properly evaluate the equality and inequality constraints.
+So far, we have defined the prior for the parameter vector $\bm{\theta}$ of the encompassing model.
+Moreover, we have obtained the adjusted prior for the new transformed parameter vector $\bm{\beta}$, allowing us to properly evaluate the equality and inequality constraints.
 At this point, we need to compute the posterior of the encompassing model parameters.
@@
 
-Posterior distribution of the encompassing model parameters can be obtained through numerical approximation using Markov Chain Monte Carlo (MCMC) sampling algorithms, such as Metropolis–Hastings algorithm \parencite{hastingsMonteCarloSampling1970} or Gibbs sampling \parencite{gemanStochasticRelaxationGibbs1984}.
+Posterior distribution of the encompassing model parameters can be obtained through numerical approximation using Markov Chain Monte Carlo (MCMC) sampling algorithms, such as the Metropolis–Hastings algorithm \parencite{hastingsMonteCarloSampling1970} or Gibbs sampling \parencite{gemanStochasticRelaxationGibbs1984}.
 Bayesian statistical inference methods are implemented in all major statistical software.
-In R statistical software \parencite{rcoreteamLanguageEnvironmentStatistical2021}, for example, the popular \texttt{brms} package \parencite{burknerBrmsPackageBayesian2017, burknerAdvancedBayesianMultilevel2018a}, which is based on STAN \parencite{standevelopmentteamRStanInterfaceStan2020}, allows to easily conduct Bayesian inference.
-
-Following \textcite{guApproximatedAdjustedFractional2018} approach, once we obtain the model posterior, we can approximate it to a (multivariate) normal distribution.
-Thus, the resulting posterior distribution is
-\begin{equation}
-Pr(\bm{\theta}|Y) \sim \mathcal{N}(\hat{\bm{\theta}}, \hat{\Sigma}_{\theta})
+In R statistical software \parencite{rcoreteamLanguageEnvironmentStatistical2021}, for example, the popular \texttt{brms} package \parencite{burknerBrmsPackageBayesian2017, burknerAdvancedBayesianMultilevel2018a}, which is based on STAN \parencite{standevelopmentteamRStanInterfaceStan2020}, allows researchers to easily conduct Bayesian inference.
+
+Following the approach established by \textcite{guApproximatedAdjustedFractional2018}, once we obtain the model posterior, we can approximate it to a (multivariate) normal distribution.
+Therefore, the resulting posterior distribution is
+\begin{equation}
+Pr(\bm{\theta}|Y) \sim \mathcal{N}(\hat{\bm{\theta}}, \hat{\Sigma}_{\theta}),
 \end{equation}
 where posterior mean $\hat{\bm{\theta}}$ and posterior covariance $\hat{\Sigma}_{\theta}$ can be computed directly from the posterior draws.
-Next, we can obtain the posterior with respect to the vector parameters $\bm{\beta}$ applying the same transformation used for the prior distribution,
+Next, we can obtain the posterior with respect to the vector parameters $\bm{\beta}$ applying the same transformation used for the prior distribution:
 \begin{equation}
@@
 
-At this point, we have both prior and posterior distributions of the parameters of interests of the encompassing model. Before proceeding, however, let's underline some important aspects.
-
-When defining the prior, we adjusted the prior mean by centring it over the constraint focal points.
-This change would slightly influence the resulting posterior as well.
-However, as underlined by \textcite{guApproximatedAdjustedFractional2018}, small prior changes will result in negligible changes on the posterior for large samples due to large-sample theory.
-For this reason, the authors do not adjust the posterior in their approach, but only the prior.
-Therefore, when computing the posterior we can simply consider the prior $\pi(\bm{\theta})\sim \mathcal{N}(\mu_{\theta}, \Sigma_{\theta})$ defined at the beginning, without worrying about adjusting it.
-
-In addition, note that, in \textcite{guApproximatedAdjustedFractional2018} original approach, the posterior mean $\hat{\bm{\theta}}$ and the posterior covariance $\hat{\Sigma_{\theta}}$ are not obtained from the posterior draws but they are computed directly from the sample data using the maximum likelihood estimate and the inverse of the Fisher information matrix, respectively.
-This has the advantage of being faster (posterior draws are not required) but it may be not possible for some complex models.
+At this point, we have both prior and posterior distributions of the parameters of interests of the encompassing model. Before proceeding, however, let's emphasize some important aspects.
+
+When defining the prior, we adjusted the prior mean by centering it over the constraint's focal points.
+This change would slightly influence the resulting posterior, as well.
+However, as \textcite{guApproximatedAdjustedFractional2018} pointed out, small prior changes will result in negligible changes in the posterior for large samples, according to large-sample theory.
+Therefore, the authors do not adjust the posterior in their approach but only the prior.
+Therefore, when computing the posterior, we can simply consider the prior $\pi(\bm{\theta})\sim \mathcal{N}(\mu_{\theta}, \Sigma_{\theta})$ defined at the beginning without worrying about adjusting it.
+
+In addition, note that in the original approach \textcite{guApproximatedAdjustedFractional2018} proposed, the posterior mean $\hat{\bm{\theta}}$ and the posterior covariance $\hat{\Sigma_{\theta}}$ are not obtained from the posterior draws but are computed directly from the sample data using the maximum likelihood estimate and the inverse of the Fisher information matrix, respectively.
+This method has the advantage of being faster (posterior draws are not required), but it may be not possible for some complex models.
 
@@
 
-In the previous section we obtained the adjusted prior and the posterior of the vector of transformed parameters $\bm{\beta}$, respectively
+In the previous section, we obtained the adjusted prior and the posterior of the vector of transformed parameters $\bm{\beta}$, respectively
 \begin{equation}
@@
 
-Given the parameter transformation from $\bm{\theta}$ to $\bm{\beta}$, we can rewrite the Formula~\ref{eq:BF-encompassing} of the Bayes Factor between $H_i$ and $H_u$ as follow,
+Given the parameter transformation from $\bm{\theta}$ to $\bm{\beta}$, we can rewrite Formula~\ref{eq:BF-encompassing} of the Bayes factor between $H_i$ and $H_u$ as follows:
 \begin{equation}
@@
 
-Now, thanks to (multivariate) normal distribution approximation, we can easily compute the required conditional probabilities and marginal densities required to calculate the Bayes Factor.
+Now, thanks to (multivariate) normal distribution approximation, we can easily compute the required conditional probabilities and marginal densities required to calculate the Bayes factor.
 
@@
 
-The marginal distribution of a subset of variables of a multivariate normal distribution is obtained simply discarding the variables to marginalize out.
-For example, given the adjusted prior of the psychological treatment example, $\pi_{adj}(\bm{\beta}) \sim \mathcal{N}(\bm{0}, \Sigma_{\beta})$ where
+The marginal distribution of a subset of variables of a multivariate normal distribution is obtained by simply discarding the variables to marginalize out.
+For example, given the adjusted prior of the psychological treatment example, $\pi_{adj}(\bm{\beta}) \sim \mathcal{N}(\bm{0}, \Sigma_{\beta})$, where
 \begin{equation}
@@
 
-At this point computing the density at $\beta_E = 0$ is elementary.
+At this point, computing the density at $\beta_E = 0$ is elementary.
 In R, this can be done using the  \texttt{dmvnorm()} function from the \texttt{mvtnorm} package \parencite{genzMvtnormMultivariateNormal2021}.
-To compute the \textbf{marginal prior density} $\pi_{adj}(\beta_E =0| H_u)$ of the psychological treatment example, we can use the following code:
+To compute the \textbf{marginal prior density}, $\pi_{adj}(\beta_E =0| H_u)$, of the psychological treatment example, we can use the following code:
 \codespacing
@@
 
-Similarly, it is possible to compute the \textbf{marginal posterior density} $\pi_{adj}(\beta_E =0| Y, H_u)$ considering this time the estimated posterior mean vector $\bm{\hat{\beta}}$ and the estimated  posterior covariance matrix $\hat{\Sigma}_{\beta}$.
+Similarly, it is possible to compute the \textbf{marginal posterior density}, $\pi_{adj}(\beta_E =0| Y, H_u)$, considering this time the estimated posterior mean vector, $\bm{\hat{\beta}}$, and the estimated  posterior covariance matrix, $\hat{\Sigma}_{\beta}$.
 
@@
 To compute the conditional probability of the inequality constraints given the equality constraints in a multivariate normal distribution, we can use the \texttt{pcmvnorm()} function from the \texttt{condMVNorm} R-package \parencite{varadhanCondMVNormConditionalMultivariate2020}.
-Considering the psychological treatment example, to calculate the \textbf{conditional prior probability} $\pi_{adj}(\beta_I > 0 | \beta_E =0, H_u)$ we can run the following code:
+Considering the psychological treatment example, to calculate the \textbf{conditional prior probability}, $\pi_{adj}(\beta_I > 0 | \beta_E =0, H_u)$, we can run the following code:
 \codespacing
@@
 
-Analogously, it is possible to compute the \textbf{conditional posterior probability} $\pi_{adj}(\beta_I > 0 | \beta_E =0, Y, H_u)$ considering this time the estimated posterior mean vector $\bm{\hat{\beta}}$ and the estimated posterior covariance matrix $\hat{\Sigma}_{\beta}$.
-
-At this point, we have all the elements required and we can easily compute the Bayes Factor $BF_{iu}$.
+Analogously, it is possible to compute the \textbf{conditional posterior probability}, $\pi_{adj}(\beta_I > 0 | \beta_E =0, Y, H_u)$, considering this time the estimated posterior mean vector, $\bm{\hat{\beta}}$, and the estimated posterior covariance matrix, $\hat{\Sigma}_{\beta}$.
+
+At this point, we have all the elements required, and we can easily compute the Bayes factor, $BF_{iu}$.
 
@@
 
-In the previous sections, we have described in detail all the steps and elements required to evaluate informative hypotheses using the Bayes Factor with the encompassing prior approach following the approximated method proposed by \textcite{guApproximatedAdjustedFractional2018}.
-As already highlighted, however, compared to \textcite{guApproximatedAdjustedFractional2018} original approach, we took a slightly different path in the prior definition and posterior approximation.
-Instead of using the fractional prior method, we defined subjective (reasonable) priors and we relied on posterior draws instead of maximum likelihood estimates to approximate the posterior.
-These choices were done to follow the usual Bayesian workflow in data analysis \parencite{gelmanBayesianWorkflow2020, schadPrincipledBayesianWorkflow2021}.
+In the previous sections, we have described in detail all the steps and elements required to evaluate informative hypotheses using the Bayes factor with the encompassing prior approach, following the approximated method \textcite{guApproximatedAdjustedFractional2018} proposed.
+As already highlighted, however, compared to the original approach \textcite{guApproximatedAdjustedFractional2018} proposed, we took a slightly different path in the prior definition and posterior approximation.
+Instead of using the fractional prior method, we defined subjective (reasonable) priors, and we relied on posterior draws instead of maximum likelihood estimates to approximate the posterior.
+We made these choices to follow the usual Bayesian workflow in data analysis \parencite{gelmanBayesianWorkflow2020, schadPrincipledBayesianWorkflow2021}.
 
 Before moving to an applied example, however, we consider some more advanced aspects that are important to take into account when applying this method.
-In particular, we discuss issues related to parameters standardization, range constraints, hypothesis matrix rank, comparable hypotheses, and bounded parameter space.
+In particular, we discuss issues related to parameters' standardization, range constraints, hypothesis matrix rank, comparable hypotheses, and bounded parameter space.
 
@@
 When evaluating informative hypotheses, it may be necessary to standardize the parameters of interest.
-As described by \textcite{guApproximatedAdjustedFractional2018}, parameters have to be standardized when comparing regression coefficients of continuous variables that are measured on different scales.
-In these cases, in fact, evaluating if $\theta_i>\theta_j$ is affected by the scale of the two variables.
+As \textcite{guApproximatedAdjustedFractional2018} showed, parameters have to be standardized when comparing regression coefficients of continuous variables that are measured on different scales - in these cases, in fact, determining whether $\theta_i>\theta_j$ is affected by the scale of the two variables.
 Standardizing the parameters allows us to correctly compare the two parameters.
-On the contrary, standardizing the parameters is not necessary if they are compared to constants (i.e., $\theta > 3$) or if they represent group means, such as the case of categorical variables.
+On the contrary, standardizing the parameters is not necessary if they are compared to constants (i.e., $\theta > 3$) or if they represent group means, such as in the case of categorical variables.
 
@@
 
-It is possible to express range constraints such as $0<\theta_i<1$ in which the parameter is constrained between two values.
+It is possible to express range constraints, such as $0<\theta_i<1$, in which the parameter is constrained between two values.
 These constraints can be expressed as the combination of two constraints.
 For example, the previous hypothesis is equivalent to $\beta_1 = \theta_i>0$ and $\beta_2 = 1 - \theta_i > 0$.
-However, adjusting the prior mean in the case of range constraints would require to centre the prior on the middle of the range space \parencite{mulderBIEMSFortran902012}.
-Thus, in the previous example we would set $\mu_{\beta_1} = \mu_{\beta_2} = .5$.
-For a detailed description of prior specification in the case of range constraints, consider Appendix A in \textcite{guApproximatedAdjustedFractional2018}.
+However, adjusting the prior mean in the case of range constraints would require us to center the prior on the middle of the range space \parencite{mulderBIEMSFortran902012}.
+Therefore, in the previous example, we would set $\mu_{\beta_1} = \mu_{\beta_2} = .5$.
+For a detailed description of prior specification in the case of range constraints, see Appendix A in \textcite{guApproximatedAdjustedFractional2018}.
 
@@
 In Equation~\ref{eq:normal-transf}, we presented how to obtain the distribution of the transformed parameters $\bm{\beta}$ from the distribution of the original parameters $\bm{\theta}$.
-This is simply a linear transformation, but, to obtain a proper covariance matrix $\Sigma_{\beta} = R\Sigma_{\theta}R^T$, the hypothesis matrix $R$ has to be \textit{full-row-rank} (i.e., all rows are linearly independent).
-
-To overcome this limit, we can use the same solution adopted by \textcite{mulderBayesFactorsTesting2016, mulderSimpleBayesianTesting2019}.
-A matrix $R^*$ is defined selecting the maximum number of linearly independent rows of $R$ and it is used to compute the covariance matrix $\Sigma_{\beta} = R^*\Sigma_{\theta}R^{*T}$.
+This is simply a linear transformation, but to obtain a proper covariance matrix $\Sigma_{\beta} = R\Sigma_{\theta}R^T$, the hypothesis matrix $R$ has to be \textit{full-row-rank} (i.e., all rows linearly independent).
+
+To overcome this limitation, we can use the same solution adopted by \textcite{mulderBayesFactorsTesting2016, mulderSimpleBayesianTesting2019}.
+A matrix $R^*$ is defined by selecting the maximum number of linearly independent rows of $R$ and used to compute the covariance matrix $\Sigma_{\beta} = R^*\Sigma_{\theta}R^{*T}$.
 This allows us to obtain the distribution of the parameters $\bm{\beta^*}$ that are linearly independent.
 The remaining constraints can be expressed as linear combinations of the parameters $\bm{\beta^*}$.
-Finally, to evaluate the probability that all constraints holds we can draw a large sample from the distribution of $\bm{\beta^*}$ and compute the proportion of draws satisfying all the constraints.
-
-Let's see an example to clarify this procedure. Suppose we have the following hypothesis: $H_i: 0 = \theta_1 < \{\theta_2, \theta_3\} < \theta_4$. Thus, the corresponding hypothesis matrix is
+Finally, to evaluate the probability that all constraints hold, we can draw a large sample from the distribution of $\bm{\beta^*}$ and compute the proportion of draws satisfying all the constraints.
+
+The following is an example to clarify this procedure. Suppose the following hypothesis: $H_i: 0 = \theta_1 < \{\theta_2, \theta_3\} < \theta_4$. Thus, the corresponding hypothesis matrix is
 \begin{equation}
@@
 Note that only the first four rows ($\beta_1,\beta_2,\beta_3,\beta_4$) are linearly independent.
-The fifth row, instead, can be obtained as a linear combination: $\beta_5 = \beta_4 - \beta_3 + \beta_2$.
+The fifth row can be obtained as a linear combination: $\beta_5 = \beta_4 - \beta_3 + \beta_2$.
 At this point, we can define $R^*$ as the first four rows of $R$ and use it to obtain the distribution of $\bm{\beta^*}$ given the original distribution of $\bm{\theta}$.
 To compute the probability of the inequality constraints, we need to draw a large sample from the multivariate normal distribution conditional to the equality constraints.
-To do that we can use the \texttt{rcmvnorm()} function from the R-package \texttt{condMVNorm}.
+To do that, we can use the \texttt{rcmvnorm()} function from the R-package \texttt{condMVNorm}.
 \codespacing
@@
 
-To compute the Bayes Factor between two different informative hypotheses, we can simply consider the ratio of the Bayes Factor of each hypothesis against the encompassing model:
+To compute the Bayes factor between two different informative hypotheses, we can simply consider the ratio of the Bayes factor of each hypothesis against the encompassing model:
 \begin{equation}
@@
 \end{equation}
-In order to do that, however, it is necessary for the informative hypotheses considered to be comparable \parencite{guApproximatedAdjustedFractional2018}.
-That is, the intersection of the constrained region of each hypothesis must be non-empty.
+To do that, however, it is necessary for the informative hypotheses considered to be comparable \parencite{guApproximatedAdjustedFractional2018}.
+That is, the intersection of the constrained region of each hypothesis must be nonempty.
 Thus, a set of informative hypotheses $\{H_1,\ldots, H_i\}$ is comparable if exist at least one solution to
@@
 This will allow us to select a common solution of $\bm{\theta}$  that can be used as the adjusted prior mean of the encompassing model.
-Note that to solve these equations, also inequality constraints are considered as equality constraints.
-
-For example, $H_1: \theta_1 > \theta_2$ and $H_2: 0 = \theta_1 < \theta_2$ are comparable hypotheses because exists a common solution ($\theta_1 = \theta_2 = 0$).
-On the country, $H_3: \theta_1 < \theta_2 +3 $ and $H_4: \theta_1 = \theta_2$ are not comparable hypotheses because there is no a common solution to $\theta_1 = \theta_2 +3 $ and $\theta_1 = \theta_2$.
+Note that to solve these equations, inequality constraints are also considered equality constraints.
+
+For example, $H_1: \theta_1 > \theta_2$ and $H_2: 0 = \theta_1 < \theta_2$ are comparable hypotheses because a common solution exists ($\theta_1 = \theta_2 = 0$).
+On the contrary, $H_3: \theta_1 < \theta_2 +3 $ and $H_4: \theta_1 = \theta_2$ are not comparable hypotheses because there is no common solution to $\theta_1 = \theta_2 +3 $ and $\theta_1 = \theta_2$.
 
@@
 
-The described approach using (multivariate) normal approximation can be straightforward applied when parameters of interest are unbounded.
-However, in the case of bounded parameters (i.e., variances, correlations, or probabilities), appropriate prior distributions are required to take into account the parameters bounded nature.
-
-Note that, if only inequality constraints are considered, the prior distribution is only used to measure the complexity of the inequality constrained hypotheses.
-In this case, the prior probability that an inequality constraint holds will be insensitive to the exact distributional form, as long as the distribution is symmetrical and centred on the focal point.
-For example, the probability that a correlation coefficient $\rho_i$ is greater than zero is the same if we consider a  uniform distribution between -1 and 1 (taking into account parameter bounded nature) or if we consider a normal distribution centred on zero (without taking into account parameter bounded nature; see Figure~\ref{fig:plot-bounded-par}).
+The described approach using (multivariate-) normal approximation can be straightforwardly applied when parameters of interest are unbounded.
+However, in the case of bounded parameters (i.e., variances, correlations, or probabilities), appropriate prior distributions are required to take into account the parameters' bounded nature.
+
+Note that if only inequality constraints are considered, the prior distribution is only used to measure the complexity of the inequality-constrained hypotheses.
+In this case, the prior probability that an inequality constraint holds will be insensitive to the exact distributional form, as long as the distribution is symmetrical and centered on the focal point.
+For example, the probability that a correlation coefficient $\rho_i$ is greater than zero is the same if we consider a  uniform distribution between -1 and 1 (taking into account parameter's bounded nature) or if we consider a normal distribution centered on zero (without taking into account parameter's bounded nature; see Figure~\ref{fig:plot-bounded-par}).
 
@@
 
-Thus, as suggested by \textcite{guBayesianEvaluationInequality2014}, as long as the complexity of the constrained hypotheses is the same regardless of a (multivariate) normal distribution or an appropriate bonded prior distribution being used, it is still possible to follow the described approach.
-This is true for hypotheses that belong to an equivalent set \parencite[for a rigorous definition of equivalent set see][]{guBayesianEvaluationInequality2014, hoijtinkInformativeHypothesesTheory2012}.
-
-In the case of equality and inequality constraints, however, normal approximation is possible, based on the same rationale as before, only to compute the conditional prior probability.
-Instead, to estimate the marginal prior density, alternative solutions have to be adopted using appropriate prior distribution to take into account the bounded nature of the parameters.
+Thus, as suggested by \textcite{guBayesianEvaluationInequality2014}, as long as the complexity of the constrained hypotheses is the same regardless of using (multivariate-) normal distribution or an appropriate bonded prior distribution, it is still possible to follow the described approach.
+This is true for hypotheses that belong to an equivalent set \parencite[for a rigorous definition of equivalent sets, see][]{guBayesianEvaluationInequality2014, hoijtinkInformativeHypothesesTheory2012}.
+
+In the case of equality and inequality constraints, however, normal approximation is possible.
+This is done based on the same rationale as before and is only used to compute the conditional prior probability.
+To estimate the marginal prior density, alternative solutions have to be adopted using appropriate prior distribution to take the bounded nature of the parameters into account.
 See \textcite{mulderBayesFactorTesting2019} for an example of hypotheses evaluating correlation coefficients in generalized multivariate probit models.
@@
 These issues are relevant only when considering the prior distribution.
-In the case of the posterior distribution, instead, we can safely approximate it to a (multivariate) normal distribution thanks to the large-sample theory.
-Moreover, prior specification is relevant only for the parameters of interest (i.e., the parameters involved in the constraints) as nuisance parameters are integrated out in the Bayes Factor.
+In the case of the posterior distribution, instead, we can safely approximate it to a (multivariate) normal distribution thanks to large-sample theory.
+Moreover, prior specification is relevant only for the parameters of interest (i.e., the parameters involved in the constraints), as nuisance parameters are integrated out in the Bayes factor.
 Thus, the results will be insensitive to the actual choice of the prior for the nuisance parameters as long as it is vague enough.
@@
 First, we provide the required background information regarding attachment theory and the study aims and characteristics.
-Subsequently, all the steps involved in the evaluation of informative hypotheses using the Bayes Factor with the encompassing prior approach are described.
-Finally, the results are briefly discussed considering the prior sensitivity analysis and limits of this approach.
-
-All analyses were conducted using the R statistical software \parencite[v\Sexpr{paste(version$major,version$minor, sep = ".")};][]{rcoreteamLanguageEnvironmentStatistical2021}.
+Subsequently, we describe all the steps involved in the evaluation of informative hypotheses using the Bayes factor with the encompassing prior approach.
+Finally, we briefly discuss the obtained results, considering the prior sensitivity analysis and limitations of this approach.
+
+All analyses were conducted using R statistical software \parencite[v\Sexpr{paste(version$major,version$minor, sep = ".")};][]{rcoreteamLanguageEnvironmentStatistical2021}.
 All materials, data, and analysis code are available at \url{https://github.com/ClaudioZandonella/Attachment}.
-The Supplemental Material with further details is also available online at \url{https://claudiozandonella.github.io/Attachment/}.
+Supplemental Material with further details is also available online at \url{https://claudiozandonella.github.io/Attachment/}.
 
@@
 Attachment theory originates from the pioneering work of \textcite{bowlbyAttachmentLoss1969} and Ainsworth (\citeyear{ainsworthAttachmentExplorationSeparation1970}).
-They postulate that children in stressful situations actively seek proximity of the caregiver through some attachment behaviors (e.g., crying; moving towards the caregiver) in order to fulfil the evolutionary goal of protection from dangers.
-The main tenet of attachment theory is that the relationships with the caregivers that children develop in the early stages of their life (i.e., \textit{attachment bond}) will affect children’s social-emotional future development \parencite{cassidyHandbookAttachmentTheory2016}.
-Besides behavior, people construct mental representations, or working models, of the self and significant others based on their interpersonal experiences.
-Describing individual differences in self reported attachment mental representations, empirical research suggested a model based on two dimensional traits \parencite{mikulincerAttachmentAdulthoodStructure2007}: attachment avoidance (characterized by discomfort with closeness, excessive self-reliance, and difficulty in relying on others for obtaining security) and attachment anxiety (characterized by low self-worth and fear of abandonment and rejection).
-This perspective, initially developed with adult participants, has been extended to the study of self reported attachment representations also during childhood, even to middle childhood \parencite{kernsAttachmentMiddleChildhood2005, marciBriefExperiencesClose2019} .
+They postulated that children in stressful situations actively seek proximity of the caregiver through attachment behaviors (e.g., crying; moving toward the caregiver) in order to fulfil the evolutionary goal of protection from dangers.
+The main tenet of attachment theory is that the relationships with the caregivers that children develop in the early stages of their lives (i.e., \textit{attachment bonds}) will affect children’s social-emotional future development \parencite{cassidyHandbookAttachmentTheory2016}.
+Besides behavior, people construct mental representations, or working models, of the self and significant others based on interpersonal experiences.
+Describing individual differences in self-reported attachment mental representations, empirical research suggested a model based on two dimensional traits \parencite{mikulincerAttachmentAdulthoodStructure2007}: attachment avoidance (characterized by discomfort with closeness, excessive self-reliance, and difficulty in relying on others for obtaining security) and attachment anxiety (characterized by low self-worth and fear of abandonment and rejection).
+This perspective, initially developed with adult participants, has been extended to the study of self-reported attachment representations during childhood as well as during middle childhood \parencite{kernsAttachmentMiddleChildhood2005, marciBriefExperiencesClose2019}.
 The two dimensions of attachment mental representations can be combined to provide four different attachment styles:
@@
 \begin{itemize}
-  \item{\textbf{Secure Attachment}} - children who are securely attached display optimal emotional regulation and they consider the caregiver as a secure base.
-  \item{\textbf{Anxious Attachment}} - anxious children manifest high levels of anxiety in stressful situations and their relationships with the caregivers is ambivalent displaying anger or helplessness.
-  \item{\textbf{Avoidant Attachment}} - avoidant children mask distress in stressful situations displaying little emotions and their relationships with the caregivers is characterized by little involvement.
-  \item{\textbf{Fearful Attachment}} - fearful children lack adequate emotional regulation in stressful situations with the risk of displaying non organized behaviors.
+  \item{\textbf{Secure Attachment}}: Children who are securely attached display optimal emotional regulation and consider their caregiver a secure base.
+  \item{\textbf{Anxious Attachment}}: Anxious children manifest high levels of anxiety in stressful situations; their relationships with caregivers are ambivalent, displaying anger or helplessness.
+  \item{\textbf{Avoidant Attachment}}: Avoidant children mask distress in stressful situations, displaying few emotions; their relationships with caregivers are characterized by little involvement.
+  \item{\textbf{Fearful Attachment}}: Fearful children lack adequate emotional regulation in stressful situations, with the risk of displaying disorganized behaviors.
 \end{itemize}
 
-Attachment theory is one of the main and most supported theories in psychology \parencite{cassidyHandbookAttachmentTheory2016}.
-In the literature, however, there is still an open debate on the relative role of mother and father attachment on children's social-emotional development.
+Attachment theory is one of the most supported theories in psychology \parencite{cassidyHandbookAttachmentTheory2016}.
+In the literature, however, there is still an open debate on the relative influence of mother and father attachment on children's social-emotional development.
 Four different main theoretical perspectives have been identified \parencite{brethertonFathersAttachmentTheory2010}:
 \begin{itemize}
-  \item{\textbf{Monotropy Theory}} - only the principal attachment figure (usually the mother) has an impact on children's development.
-  \item{\textbf{Hierarchy Theory}} - the principal attachment figure (usually the mother) has a greater impact on children development than the subsidiary attachment figure (usually the father).
-  \item{\textbf{Independence Theory}} - all attachment figures are equally important but they affect the children's development differently.
-  \item{\textbf{Integration Theory}} - to understand the impact on children's development it is necessary to consider all attachment relationships taken together.
+  \item{\textbf{Monotropy Theory}}: Only the principal attachment figure (usually the mother) has an impact on children's development.
+  \item{\textbf{Hierarchy Theory}}: The principal attachment figure (usually the mother) has a greater impact on children's development than the subsidiary attachment figure (usually the father).
+  \item{\textbf{Independence Theory}}: All attachment figures are equally important, but they affect the children's development differently.
+  \item{\textbf{Integration Theory}}: To understand their impact on children's development, it is necessary to consider all attachment relationships together.
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{The Present Study}
-
-The present study aims to directly compare the four different theoretical perspectives regarding the role of father and mother attachment, using the Bayes Factor with the encompassing prior approach.
-
-In the analysis, $n =\Sexpr{nrow(data_cluster)}$ Italian children (\Sexpr{perc_females()}\% Females) between 8 and 12 years old (\textit{middle childhood}, third to sixth school grade) were included.
-Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child version \parencite[ECR-RC;][]{Brenning2014ThePQ, marciBriefExperiencesClose2019} completed by the children.
-Subsequently, two separate cluster analyses (i.e., one for mother scores, one for father scores) were performed.
+\subsubsection{Present Study}
+
+We aimed to directly compare the four different theoretical perspectives regarding the influence of father and mother attachment using the Bayes factor with the encompassing prior approach.
+
+Out of our initial population, $\Sexpr{nrow(data_cluster)}$ Italian children (\Sexpr{perc_females()}\% females) between 8 and 12 years old (\textit{middle childhood}, third to sixth grade) were included in the final analysis.
+Attachment toward the mother and the father were measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version \parencite[ECR-RC;][]{Brenning2014ThePQ, marciBriefExperiencesClose2019} completed by the children.
+Subsequently, we performed two separate cluster analyses for mother and father scores.
 Both analyses supported the existence of the four attachment profiles (see above).
@@
 
-Children's social-emotional development was measured using the Strength \& Difficulties Questionnaire \parencite[SDQ;][]{goodmanWhenUseBroader2010} completed by the teachers.
-Separate scores for externalizing and internalizing problems were obtained as sum of the questionnaire items.
-For the pourpose of this work, we considered only externalizing problems  The distribution of externalizing problems ($\text{Mean} = \Sexpr{my_round(mean(data_cluster$externalizing_sum), 2)};\ \text{SD} =  \Sexpr{my_round(sd(data_cluster$externalizing_sum), 2)};\ \text{Median} = \Sexpr{my_round(median(data_cluster$externalizing_sum), 1)}$) is presented in Figure~\ref{fig:plot-externalizing-dist}.
+We measured children's social-emotional development using the Strengths and Difficulties Questionnaire \parencite[SDQ;][]{goodmanWhenUseBroader2010} completed by teachers.
+Separate scores for externalizing and internalizing problems were obtained as sums of the questionnaire items.
+For the pourpose of this work, we considered only externalizing problems.
+The distribution of externalizing problems ($M = \Sexpr{my_round(mean(data_cluster$externalizing_sum), 2)};\ SD =  \Sexpr{my_round(sd(data_cluster$externalizing_sum), 2)};\ \text{Median} = \Sexpr{my_round(median(data_cluster$externalizing_sum), 1)}$) is presented in Figure~\ref{fig:plot-externalizing-dist}.
 <<plot-externalizing-dist, cache=TRUE, fig.cap="Distribution of externalizing problems ($n_{subj} = 847$).">>=
@@
 
-Externalizing problems according to attachment styles are reported in Table~\ref{tab:table-cluster-ext}.
+Externalizing problems according to attachment style are reported in Table~\ref{tab:table-cluster-ext}.
 More information about the sample, descriptive statistics, cluster analysis, and analysis of internalizing problems can be found in the Supplemental Material available online \url{https://claudiozandonella.github.io/Attachment/}.
@@
 
-Each theoretical perspective was formalized into a different informative hypothesis taking into account its own theoretical tenets, main evidence in the literature, and authors' clinical experience in the field.
-
-The following notation is used to formalize the hypothesis.
-$M$ and $F$ are used to indicate the attachment towards the mother and the father, respectively.
-The specific attachment style is specified in the subscript where $S$ indicates secure attachment, $Ax$ anxious attachment, $Av$ avoidant attachment, and $F$ fearful attachment.
-For example, $F_{Av}$ represents children with avoidant attachment towards the father.
-
-Note that when we do not expect interaction between mother and father attachment, we can consider the role of the two parents separately.
+Each theoretical perspective was formalized into a different informative hypothesis taking into account its own theoretical tenets, main evidence in the literature, and our clinical experience in the field.
+
+We used the following notation to formalize the hypotheses.
+$M$ and $F$ are used to indicate attachment toward the mother and the father, respectively.
+Specific attachment styles are specified using subscript: $S$ indicates secure attachment, $Ax$ anxious attachment, $Av$ avoidant attachment, and $F$ fearful attachment.
+For example, $F_{Av}$ represents children with avoidant attachment toward their fathers.
+
+Note that when we do not expect interaction between mother and father attachment, we can consider the roles of the two parents separately.
 Whereas, if an interaction is expected, it is necessary to take into account the unique combination of mother and father attachment.
-Thus, for example, we use $M_SF_{Ax}$ to indicate children with secure attachment towards the mother and anxious attachment towards the father.
+Thus, for example, we use $M_SF_{Ax}$ to indicate children with secure attachment toward their mothers and anxious attachment toward their fathers.
 Moreover, $*$ subscript is used to indicate any attachment style and a set of subscripts is used to indicate “\textit{one among}”.
-For example, $M_SF_{Ax;Av}$ represents children with secure attachment towards the mother and anxious or avoidant attachment towards the father.
+For example, $M_SF_{Ax;Av}$ represents children with secure attachment toward their mothers and anxious or avoidant attachment toward their fathers.
 
@@
 
-\paragraph{Null Hypothesis} This is a reference hypothesis where mother attachment and father attachment are expected to have no effect and only gender differences are taken into account (see Section~\ref{sec:def-encompassing-model} for the actual model definition).
+\paragraph{Null Hypothesis} This is a reference hypothesis in which mother attachment and father attachment are expected to have no effect and only gender differences are taken into account (see Section~\ref{sec:def-encompassing-model} for the actual model definition).
 The hypothesis is represented in Figure~\ref{fig:plot-null-hypothesis}:
@@
 
-\paragraph{Monotropy Hypothesis} Father attachment is expected to have no effect, whereas considering mother attachment we expect the following order: secure children with the lowest level of problems, anxious and avoidant children with similar levels of problems, fearful children with the highest levels of problems.
-The hypothesis is represented in Figure~\ref{fig:plot-monotropy-hypothesis}:
+\paragraph{Monotropy Hypothesis} Father attachment is expected to have no effect, whereas considering mother attachment, we expect the following order: secure children should have the lowest level of problems, anxious and avoidant children should exhibit similar levels of problems, and fearful children should exhibit the highest levels of problems.
+This hypothesis is represented in Figure~\ref{fig:plot-monotropy-hypothesis}:
 \begin{equation}
@@
 
-\paragraph{Hierarchy Hypothesis} Father attachment is expected to follow the same pattern as the mother attachment, but its influence is expected to be smaller.
-The hypothesis is represented in Figure~\ref{fig:plot-hierarchy-hypothesis}:
+\paragraph{Hierarchy Hypothesis} Father attachment is expected to follow the same pattern as mother attachment, but with lesser influence.
+This hypothesis is represented in Figure~\ref{fig:plot-hierarchy-hypothesis}:
 \begin{equation}
@@
 
-\paragraph{Independence Hypothesis} Mother and father attachment are expected to affect children outcomes differently.
-In this case, we considered avoidant attachment towards the father as a condition of higher risk.
-The hypothesis is represented in Figure~\ref{fig:plot-independence-hypothesis}:
+\paragraph{Independence Hypothesis} Mother and father attachment are expected to affect children's outcomes differently.
+In this case, we consider avoidant attachment toward the father as a condition of greater risk.
+This hypothesis is represented in Figure~\ref{fig:plot-independence-hypothesis}:
 \begin{equation}
@@
 In this case, we consider secure attachment as a protective factor and fearful attachment as a risk condition.
-We do not specify the conditions $M_SF_F$ and $M_FF_S$ as their frequency is very low (\Sexpr{perc_rare_condition()}\% of the sample).
+We do not specify the conditions $M_SF_F$ and $M_FF_S$, as their frequency is very low (\Sexpr{perc_rare_condition()}\% of the sample).
 The hypothesis is represented in Figure~\ref{fig:plot-integration-hypothesis}:
@@
 
-A Zero-Inflated Negative Binomial (ZINB) mixed effect model is defined to take into account the characteristics of the dependent variable and its distribution (see Figure~\ref{fig:plot-externalizing-dist} and see Supplemental Material for more details regarding the analysis of zero inflation \url{https://claudiozandonella.github.io/Attachment/}):
+We define a zero-inflated negative binomial (ZINB) mixed-effect model to take into account the characteristics of the dependent variable and its distribution (see Figure~\ref{fig:plot-externalizing-dist} and see Supplemental Material for more details regarding the zero-inflation analysis \url{https://claudiozandonella.github.io/Attachment/}):
 \begin{equation}
@@
 \end{equation}
-where $p_{ij}$ is the probability of an observation $y_{ij}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_{ij}$ indicates the probability of a given observation $y_{ij}$ being generated form a Negative Binomial distribution with mean $\mu_{ij}$ and variance $\sigma_{ij}^2 = \mu_{ij} + \frac{\mu_{ij}^2}{\phi}$.
+where $p_{ij}$ is the probability of an observation $y_{ij}$ being an extra zero (i.e., a zero not coming from the negative binomial distribution) and $1-p_{ij}$ indicates the probability of a given observation $y_{ij}$ being generated form a negative binomial distribution with mean $\mu_{ij}$ and variance $\sigma_{ij}^2 = \mu_{ij} + \frac{\mu_{ij}^2}{\phi}$.
 Moreover, we define
@@
 
-That is, both $\bm{p}$ and $\bm{\mu}$ are modelled separately according to fixed and random effects.
-In particular, we consider the children's classroom ID as a random effect in both cases to account for teachers' different ability to evaluate children's problems.
-While, regarding fixed effects, only the role of gender is considered for $\bm{p}$, whereas for $\bm{\mu}$ the interaction between mother and father attachment are included together with gender.
-In the R formula syntax, we have
+That is, both $\bm{p}$ and $\bm{\mu}$ are modeled separately according to fixed and random effects.
+In particular, we consider the children's classroom IDs as a random effect in both cases to account for teachers' different ability to evaluate children's problems.
+Regarding fixed effects, only the role of gender is considered for $\bm{p}$; for $\bm{\mu}$, the interaction between mother and father attachment are included together with gender.
+In R formula syntax, we have
 \codespacing
@@
 The parameters of interest (i.e., those related to mother and father attachment interaction) and the parameter related to gender differences are unbounded.
-Thus, we can simply specify a normal distribution with mean 0 and standard deviation of 3, $\mathcal{N}(0,3)$, as reasonable prior.
-This prior is intended to be non-informative but without being excessively diffuse\footnote{Considering 1 as intercept (note that $exp(1)$ is approximately the sample mean value), values included within one standard deviation, $exp(1 \pm 1\times SD)$, range between 0 and 55.
-Although externalizing problems are bounded between 0 and 20, prior predicted values are still reasonable as they cover all possible values without including excessively large values.
-More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values (see Supplemental Material for further details \url{https://claudiozandonella.github.io/Attachment/})}.
-The influence of prior specification is subsequently evaluated in a prior sensitivity analysis.
-Regarding the other nuisance parameters (i.e., intercepts, random effects and shapes parameters) \texttt{brms} default priors are maintained (see Supplemental Material for further details \url{https://claudiozandonella.github.io/Attachment/}).
-The encompassing model was estimated using 6 independent chains with 10,000 iterations (warm-up 2,000).
-
-Finally, note that in this case, we do not need to standardize our parameters as they represent mean groups differences (see Section~\ref{sec:param-standard}).
+Thus, we can simply specify a normal distribution with a mean of 0 and standard deviation of 3, $\mathcal{N}(0,3)$, as reasonable prior.
+This prior is intended to be noninformative but without being excessively diffuse.\footnote{Considering 1 as intercept (note that $exp(1)$ is approximately the sample mean value), values included within 1 standard deviation, $exp(1 \pm 1\times SD)$, range between 0 and 55.
+Although externalizing problems are bounded between 0 and 20, prior predicted values are still reasonable, as they cover all possible values without including excessively large values.
+More diffuse priors would result in values with a higher order of magnitude, and tighter priors would exclude plausible values (see Supplemental Material for further details \url{https://claudiozandonella.github.io/Attachment/})} We subsequently evaluated the influence of prior specification in a prior sensitivity analysis.
+Regarding the other nuisance parameters (i.e., intercepts, random effects, and shape parameters) \texttt{brms}' default priors are maintained (see Supplemental Material for further details \url{https://claudiozandonella.github.io/Attachment/}).
+The encompassing model was estimated using six independent chains with 10,000 iterations (warm-up 2,000).
+
+Finally, note that in this case, we do not need to standardize our parameters, as they represent mean group differences (see Section~\ref{sec:param-standard}).
 
@@
 
-Before computing the hypothesis matrix for each informative hypothesis, it is important to consider the contrasts coding and the resulting parametrization of the encompassing model.
-For mother and father attachment, default treatment contrasts are used \parencite{schadHowCapitalizePriori2019} considering secure attachment as the reference category.
-Therefore, model intercept represents children with secure attachment towards both parents ($M_SF_S$) and we have parameters indicating the main effects of mother and father attachment and other parameters for the interaction effect.
-
-Now, given the informative hypotheses and the parametrization of the encompassing model, we can obtain the respective hypotheses matrices.
-To do that, first, we need the model matrix with all the conditions of interest.
-Note that we have to consider only conditions relevant to the constraints (i.e., those related to mother and father attachment) ignoring other nuisance conditions (i.e., gender and classroom ID).
+Before computing the hypothesis matrix for each informative hypothesis, it is important to consider the contrasts' coding and the resulting parametrization of the encompassing model.
+We used default treatments contrasts for mother and father attachment \parencite{schadHowCapitalizePriori2019}, considering secure attachment as the reference category.
+Therefore, model intercept represents children with secure attachment toward both parents ($M_SF_S$) and we have parameters indicating the main effects of mother and father attachment and other parameters for the interaction effect.
+
+Given the informative hypotheses and the parametrization of the encompassing model, we can obtain the respective hypotheses' matrices.
+To do that, we first need the model matrix with all the conditions of interest.
+Note that we only have to consider  conditions relevant to the constraints (i.e., those related to mother and father attachment), ignoring other nuisance conditions (i.e., gender and classroom ID).
 
 Subsequently, we can derive the required equality and inequality constraints.
-In particular, with hypotheses that do not expect interaction between mother and father attachment (i.e., monotropy, hierarchy, and independence hypotheses), all interaction terms are set equal to zero and main effects are obtain considered the reference level of the other parent (i.e., $M_{Ax}F_S$ is the main effect of anxious attachment towards the mother).
+In particular, with hypotheses that do not expect interaction between mother and father attachment (i.e., monotropy, hierarchy, and independence hypotheses), all interaction terms are set equal to zero, and main effects are obtain considering the reference level of the other parent (i.e., $M_{Ax}F_S$ is the main effect of anxious attachment toward the mother).
 As an example, consider the following code:
@@
 \doublespacing
-In this way, we can easily specify all the constraints obtaining the respective hypothesis matrix ($R$) and the vector with the constraints constant values ($r$) for each hypothesis.
+In this way, we can easily specify all the constraints obtaining the respective hypothesis matrix ($R$) and the vector with the constraints' constant values ($r$) for each hypothesis.
 In all our hypotheses, however, no constraints include constant values.
 Thus, $r$ is always a vector of zeros and it can be ignored.
-Moreover, also the intercept is ignored because there are no constraints that include $M_SF_S$ alone (e.g., $M_SF_S>k$) but is always compared with other groups (e.g., $M_SF_S< M_{Ax}F_S$).
+Moreover, we can also ignore the intercept because no constraints include $M_SF_S$ alone (e.g., $M_SF_S>k$); but it is always compared with other groups (e.g., $M_SF_S< M_{Ax}F_S$).
 Thus, the inclusion of the intercept is redundant and we can ignore it.
@@
 
-So far we defined the hypotheses matrices, specified the encompassing prior, and obtained the model posterior distribution.
-To compute the Bayes Factor, we now need the adjusted prior and the posterior of the transformed parameters vector $\bm{\beta}$ (i.e., the parameters that identify the constraints) for each hypothesis.
+So far, we defined the hypotheses' matrices, specified the encompassing prior, and obtained the model's posterior distribution.
+To compute the Bayes factor, we now need the adjusted prior and the posterior of the transformed parameters vector $\bm{\beta}$ (i.e., the parameters that identify the constraints) for each hypothesis.
 
 \begin{itemize}
-\item{\textbf{Adjusted Prior $\bm{\beta}$.}} As reported in Section~\ref{sec:adj-prior}, adjusted prior is required to properly evaluate the constraints.
-Applying the Equation~\ref{eq:normal-transf}, we obtain the prior for the transformed parameter and then we set the mean vector to zero.
+\item{\textbf{Adjusted Prior $\bm{\beta}$.}} As reported in Section~\ref{sec:adj-prior}, the adjusted prior is required to properly evaluate the constraints.
+Applying Equation~\ref{eq:normal-transf}, we obtain the prior for the transformed parameter and then set the mean vector to zero.
 \item{\textbf{Posterior $\bm{\beta}$.}} The same transformation used for the prior can be applied, this time considering the estimated posterior mean $\hat{\bm{\theta}}$ and the estimated posterior covariance $\hat{\Sigma}_{\theta}$, to obtain the posterior distribution of the transformed parameters vector $\bm{\beta}$.
@@
 
-As discussed in Section~\ref{sec:rank-hypo}, Equation~\ref{eq:normal-transf} requires the hypothesis matrix $R$ to be \textit{full-row-rank} (i.e., all constraints are linearly independent).
-However, this is not the case of the hierarchy hypothesis.
+As discussed in Section~\ref{sec:rank-hypo}, Equation~\ref{eq:normal-transf} requires hypothesis matrix $R$ to be \textit{full-row-rank} (i.e., all constraints must be linearly independent).
+However, this is not the case for the hierarchy hypothesis.
 Thus, we followed the solution presented in Section~\ref{sec:rank-hypo}.
@@
 
-Now, we have all the elements required to compute the Bayes Factor for each hypothesis as described in Section~\ref{sec:compute-bf}.
-Moreover, assuming that each hypothesis is equally likely a priori, we can calculate the posterior probability of each hypothesis as \parencite{hoijtinkInformativeHypothesesTheory2012, guBayesianEvaluationInequality2014},
+Now, we have all the elements required to compute the Bayes factor for each hypothesis as described in Section~\ref{sec:compute-bf}.
+Moreover, assuming that each hypothesis is equally likely a priori, we can calculate the posterior probability of each hypothesis as \parencite{hoijtinkInformativeHypothesesTheory2012, guBayesianEvaluationInequality2014}:
 \begin{equation}
@@
 
-Bayes Factor and posterior probability of each hypothesis are reported in Table~\ref{tab:table-bf-results}.
-Results clearly indicate that, among the considered hypotheses, the Monotropy Hypothesis is the most supported by the data.
+Bayes factor and posterior probability of each hypothesis are reported in Table~\ref{tab:table-bf-results}.
+Results clearly indicate that among the considered hypotheses, the Monotropy Hypothesis is the most supported by the data.
 
@@
 
-Remember, however, that prior specification affects the Bayes Factor results.
-It is recommended, therefore, to evaluate also the results obtained using different prior settings.
-In particular, we considered as possible priors for the parameters of interest:
+Remember, however, that prior specification affects the Bayes factor results.
+It is therefore recommended, to evaluate the results we would obtain using different prior settings as well.
+In particular, we consider as possible priors for the parameters of interest:
 \begin{itemize}
-  \item{$\mathcal{N}(0,.5)$} - unreasonable tight prior
-  \item{$\mathcal{N}(0,1)$} - tighter prior
-  \item{$\mathcal{N}(0,3)$} - original prior
-  \item{$\mathcal{N}(0,5)$} - more diffuse prior
-  \item{$\mathcal{N}(0,10)$} - unreasonably diffuse prior
+  \item{$\mathcal{N}(0,.5)$}: Unreasonable tight prior
+  \item{$\mathcal{N}(0,1)$}: Tighter prior
+  \item{$\mathcal{N}(0,3)$}: Original prior
+  \item{$\mathcal{N}(0,5)$}: More diffuse prior
+  \item{$\mathcal{N}(0,10)$}: Unreasonably diffuse prior
 \end{itemize}
@@
 However, we can observe two distinct patterns.
-As the prior gets more diffuse, the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
-Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.
-
-To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
+As the prior becomes more diffuse, the order of magnitude of the Bayes factor comparing each hypothesis with the encompassing model increases.
+Moreover, the probability of the Null Hypothesis increases with more diffuse priors, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.
+
+To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centered on the constraint focal point.
 On the contrary, equality constraints are highly affected by the prior definition.
-As the prior gets more diffuse, the density value at zero decreases as well and, even for posterior distributions centred far from zero, the densities ratio at zero will favour the posterior.
-Thus, as the prior gets more diffuse, the Bayes Factor will favour more and more the hypotheses with equality constraints, whereas for tighter prior the Bayes Factor will strongly penalize hypotheses with equality constraints if these are not correct (see Figure~\ref{fig:plot-sensitivity-prior}).
+As the prior gets more diffuse, the density value at zero decreases as well and, even for posterior distributions centered far from zero, the densities ratio at zero will favor the posterior.
+Thus, as the prior becomes more diffuse, the Bayes factor will increasingly favor the hypotheses with equality constraints.
+For tighter priors, the Bayes factor will strongly penalize hypotheses with equality constraints if these are not correct (see Figure~\ref{fig:plot-sensitivity-prior}).
 
 All the defined hypotheses include equality constraints.
-Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
-Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).
+Thus, for more diffuse priors we observe that the order of magnitude of the Bayes factor comparing each hypothesis with the encompassing model increases.
+Moreover, the hypothesis with the highest number of equality constraints (e.g., Null Hypothesis) will be favored over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Limits}
-
-When interpreting the results, it is important to take into account the limits of the Bayes Factor.
+\subsubsection{Limitations}
+
+When interpreting the results, it is important to take into account the limitations of the Bayes factor.
 First of all, the selected hypothesis is relative to the data and the set of hypotheses considered.
 That means that we should not interpret the selected hypothesis as the only “\textit{correct}” one.
-Maybe we did not consider some important aspects and new hypotheses may reveal themselves to be actually much better than the previous ones.
-For example, regarding the attachment results, taking into account the interaction between children's gender and attachment may be fundamental (is it possible that attachment towards the father plays a different role between girls and boys?).
-This limit, however, becomes an advantage as it forces the researchers to focus on the definition of the hypotheses: to obtain good answers first we need to ask the right questions.
-
-Moreover, considering a unique single winning hypothesis may be limiting as different hypotheses could help to explain different aspects of the process under investigation.
-For example, mother and father attachment may play a different role at different ages.
+Perhaps we did not consider some important aspects, and new hypotheses may reveal themselves to be actually much better than the previous ones.
+For example, regarding the attachment results, taking into account the interaction between children's gender and attachment may be fundamental (is it possible that attachment toward the father plays a different role between girls and boys?).
+This limitation, however, becomes an advantage as it forces the researchers to focus on the definition of the hypotheses: to obtain good answers, first we need to ask the right questions.
+
+Moreover, considering a unique single winning hypothesis may be limiting, as different hypotheses could help explain different aspects of the process under investigation.
+For example, mother and father attachment may play different roles at different ages.
 Thus, the selected hypothesis may vary according to children's age or other conditions.
-This should warn against interpreting the result in terms of winning/losing focusing uniquely on the selected hypothesis and discarding other hypotheses from further investigations.
-
-Another important limit we observed is the sensitivity of the results to the prior specification.
-\textcite{gelmanBayesianDataAnalysis2013} do not recommend the use of the Bayes Factor given its sensitivity to model definition arbitrary choices.
+This should warn against interpreting the results in terms of winning or losing, focusing uniquely on the selected hypothesis and discarding other hypotheses from further investigations.
+
+Another important limitation we observed is the sensitivity of the results to the prior specification.
+\textcite{gelmanBayesianDataAnalysis2013} do not recommend using the Bayes factor, given its sensitivity to model definition arbitrary choices.
 Evaluating the results under different conditions and transparently discussing the reasons behind arbitrary choices would help to interpret results more consciously \parencite{schadWorkflowTechniquesRobust2021}.
 
-Finally, another limit related to the use of the Bayes Factor with the encompassing prior approach is that we do not obtain the actual estimates of the parameters posterior.
-The only information we get is the selected hypothesis, but we have no other information regarding the actual parameters values.
-Therefore, for example, we are not able to assess the actual effect sizes.
-To overcome this limit we can rely on Bayesian inference that allows us to effectively estimate the model parameter posteriors.
-Consider, for example, \textcite{katoBayesianApproachInequality2006} where a Gibbs sampler is defined taking into account parameter constraints.
+Finally, another limitation related to the use of the Bayes factor with the encompassing prior approach is that we do not obtain the actual estimates of the parameters posterior.
+The only information we get is the selected hypothesis, but we have no other information regarding the actual parameters' values.
+Therefore, for example, we cannot assess the actual effect sizes.
+To overcome this limitation, we have to obtain via Bayesian inference the actual posterior of the model parameters given the prior, formalized according to parameters' constraints, and the observed data \parencite[for an introduction to Bayesian estimation][]{kruschkeBayesianNewStatistics2018}.
+However, posterior estimation under inequality constraints requires the use of appropriate advanced computational algorithms \parencite[see][]{ghosalBayesianInferenceGeneralized2022, katoBayesianApproachInequality2006}.
 
@@
 
-In this paper, we presented a detailed description and an applied example of the Bayes Factor with the encompassing prior approach.
-As discussed in the introduction, this approach has several advantages over traditional Null Hypothesis Significance Testing (NHST): it is possible to evaluate complex hypotheses with equality and inequality constraints; multiple hypotheses can be tested simultaneously; Bayes Factor and Posterior Probabilities allow to quantify the relative evidence form the data in favour of the hypotheses.
+In this paper, we presented a detailed description and an applied example of the Bayes factor with the encompassing prior approach.
+As discussed in the introduction, this approach has several advantages over traditional NHST: it is possible to evaluate complex hypotheses with equality and inequality constraints, multiple hypotheses can be tested simultaneously, and Bayes factor and posterior probabilities allow quantifying the relative evidence from the data in favor of the hypotheses.
 
 This approach is of particular interest to the researchers, because informative hypotheses allow them to formalize their expectations with great flexibility.
-In this paper we considered only the presence/absence of an effect (i.e., $\theta = 0$) or the expected effects order (i.e., $\theta_i > \theta_j$).
+In this paper, we considered only the presence/absence of an effect (i.e., $\theta = 0$) or the expected effects order (i.e., $\theta_i > \theta_j$).
 However, in case of clear indications about the actual effects, researchers can specify the expected range of values for the effects of interest (i.e., $a<\theta_i<b$).
@@
 
-As emphasized by \textcite[p.229]{guApproximatedAdjustedFractional2018}, “this class of informative hypotheses covers a much broader range of scientific expectations than the class of standard null hypotheses.
+As emphasized by \textcite[p.229]{guApproximatedAdjustedFractional2018}, “This class of informative hypotheses covers a much broader range of scientific expectations than the class of standard null hypotheses.
 In addition, by testing competing informative hypotheses directly against each other a researcher obtains a direct answer as to which scientific theory is most supported by the data”.
@@
 The available literature, however, is often technical and difficult to follow for non-experts in this approach.
-This paper filled this gap by providing a detailed description of all steps and elements involved in the computation of the Bayes Factor with the encompassing prior approach.
-This will enhance researchers' awareness regarding all pros and cons of this method, avoiding applying statistical techniques as black boxes.
+This paper filled this gap by providing a detailed description of all steps and elements involved in the computation of the Bayes factor with the encompassing prior approach.
+This will enhance researchers' awareness regarding all pros and cons of this method, helping them avoid applying statistical techniques as black boxes.
 

### 2021-11-28 Documents/Bookdown/01-case-study.Rmd
update supplemental material

@@
 
-The aim of the study is to compare the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social emotional development.
+The study aims to compare the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social-emotional development.
 In the literature, four different main theoretical perspectives have been identified [@brethertonFathersAttachmentTheory2010]:
@@
 - **Monotropy Theory** - only the mother has an impact on children's development.
-- **Hierarchy Theory** - the mother has a greater impact on children development than the  the father.
+- **Hierarchy Theory** - the mother has a greater impact on children's development than the father.
 - **Independence Theory** - all attachment figures are equally important but they affect the children's development differently.
@@
 
-For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article].
+For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article [TODO: add link article].
 
@@
 
-To evaluate the different role of father attachment and mother attachment, we consider `r tot_subj()` Italian children from third to sixth school grade.
-Only middle-childhood children are included in the analysis (`r tot_subj_older()` participants are excluded as older than 12.3 years and `r tot_subj_NA()` participants are excluded are excluded as the age is missing).
+To evaluate the different roles of father attachment and mother attachment, we consider `r tot_subj()` Italian children from third to sixth school grade.
+Only middle-childhood children are included in the analysis (`r tot_subj_older()` participants are excluded as older than 12.3 years and `r tot_subj_NA()` participants are excluded as the age is missing).
 The total sample size included in the analysis is `r tot_subj_included()` (`r perc_females()` \% Females).
-Participants frequencies by grade and gender are reported in Table~\@ref(tab:table-gender-grade).
+Participants' frequencies by grade and gender are reported in Table~\@ref(tab:table-gender-grade).
 
@@
 
-Participants age mean is `r var_info("age_year")`. The participants age summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-age).
+Participants' age mean is `r var_info("age_year")`. The participants’ age summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-age).
 
@@
 
-Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale (ECR; [TODO add references]) completed by the children.
+Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version [ECR-RC, @Brenning2014ThePQ; marciBriefExperiencesClose2019] completed by the children.
 Four main attachment styles have been recognized in the literature according to thee levels of *anxiety* and *avoidance*:
@@
 
-To identify children attachment styles towards the mother and towards the father, we conduct two separate cluster analyses.
+To identify children's attachment styles towards the mother and towards the father, we conduct two separate cluster analyses.
 Clusters are obtained using the function `hclust()` (with argument `method="ward.D"`) considering *Euclidean* distances between participants responses to the ECR items.
@@
 These results reflect the traditional definition of the four attachment styles.
-Moreover, attachment styles frequencies are in lines with general results in the literature [TODO: add reference values].
 
@@
 
-To evaluate if 4 cluster is an appropriate choice, we compare the BIC values of different model-based clustering options.
+To evaluate if 4 clusters is an appropriate choice, we compare the BIC values of different model-based clustering options.
 To do that we use the function `mclustBIC()` from the `mclust` R-package [@scruccaMclustClusteringClassification2016].
-BIC values of the best three model-based clustering are reported below and overall results are presented in Figure~\@ref(fig:plot-mclust-mother).
+BIC values of the best three model-based clusterings are reported below and overall results are presented in Figure~\@ref(fig:plot-mclust-mother).
 See `?mclustBIC()` help page for further information.
@@
 This is in line with attachment theory and general results in the literature.
-The important thing is hat no smaller number of clusters provided better results than the division in 4 clusters.
+The important thing is that no smaller number of clusters provided better results than the division in 4 clusters.
 
@@
 
-These results are no as good as in the mother attachment classification, but they are still reasonable.
-Moreover, attachment styles frequencies are close to the general results in the literature [TODO: add reference values].
+These results are not as good as in the mother attachment classification, but they are still reasonable.
 
@@
 
-To evaluate if 4 cluster is an appropriate choice, we compare the BIC values of different model-based clustering options as before.
-BIC values of the best three model-based clustering are reported below and overall results are presented in Figure~\@ref(fig:plot-mclust-father).
+To evaluate if 4 clusters is an appropriate choice, we compare the BIC values of different model-based clustering options as before.
+BIC values of the best three model-based clusterings are reported below and overall results are presented in Figure~\@ref(fig:plot-mclust-father).
 
@@
 
-We can observe how values on the diagonal (same attachment styles towards both parents) tends to be larger than others.
+We can observe how values on the diagonal (same attachment styles towards both parents) tend to be larger than others.
 
@@
 
-Children's social-emotional development was measured using the Strength \& Difficulties Questionnaire (SDQ; [TODO add references]) completed by the teachers.
-Separate scores for externalizing and internalizing problems were obtained as sum of the questionnaire items.
+Children's social-emotional development was measured using the Strength and Difficulties Questionnaire [SDQ, @goodmanWhenUseBroader2010] completed by the teachers.
+Separate scores for externalizing and internalizing problems were obtained as the sum of the questionnaire items.
 
@@
 Participants externalizing problems mean is `r var_info("externalizing_sum")`.
-The participants externalizing problems summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-externalizing-dist).
+The participants' externalizing problems summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-externalizing-dist).
 
@@
 
-Overall, externalizing problems are low.
-This is expected as the sample is not a clinical sample.
-Externalizing problems according to attachment styles are reported in Table~\@ref(tab:table-cluster-ext).
+Overall, externalizing problems are low. This is expected as the sample is not clinical. Externalizing problems according to attachment styles are reported in Table~\@ref(tab:table-cluster-ext).
 
@@
 
-Overall, internalizing problems are low.
-Again, this is expected as the sample is not a clinical sample.
-Internalizing problems according to attachment styles are reported in Table~\ref(tab:table-cluster-ext).
+Overall, internalizing problems are low. Again, this is expected as the sample is not clinical. Internalizing problems according to attachment styles are reported in Table~\ref(tab:table-cluster-ext).
 

### 2021-11-28 Documents/Bookdown/02-ext-model-choice.Rmd
update supplemental material

@@
 
-In this chapter, we discuss the appropriate models family to to take into account data characteristics.
+In this chapter, we discuss the appropriate models’ family to take into account data characteristics.
 
@@
 Considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe that data have high dispersion with a long right tail.
-In this case, Poisson distribution would be a poor choice and we prefer Negative Binomial instead.
+In this case, the Poisson distribution would be a poor choice and we prefer Negative Binomial instead.
 
-Again, considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe an high peak of values at zero.
-Remember that this is not a clinical sample, thus it is expected that children majority has no problems or really few problem.
+Again, considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe a high peak of values at zero.
+Remember that this is not a clinical sample, thus it is expected that the majority of children have no problems or really few problems.
 We could question ourselves, however, whether a *Zero-Inflated* model may be appropriate
@@
 
-To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model.
+To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed-effects model.
 We consider in the model the role of gender and the interaction between mother attachment and father attachment.
@@
 That is, both $p$ and $\mu$ are modelled separately according to (possibly) different variables.
-In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ the consider also the interaction between mother attachment and father attachment.
+In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ we also consider the interaction between mother attachment and father attachment.
 In both cases, we consider the children's classroom ID as a random effect (teachers may differ in the ability to detect children's problems and quantify them).
@@
 
-The ZINB model is fitted using the function `zeroinfl()` from the `pscl` R-package [@zeileisRegressionModelsCount2008].
+The ZINB model is fitted using the function `glmmTMB()`.
 To compare the ZINB model and the Negative Binomial model we conduct an analysis of *Deviance*.

### 2021-11-28 Documents/Bookdown/04-ext-model-comparison.Rmd
update supplemental material

@@
 To interpret these results, note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
-As pointed by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
+As pointed out by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
 We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.
@@
 
-Considering model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
+Considering the model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
 ```{r, echo =TRUE, cache=TRUE}

### 2021-11-28 Documents/Bookdown/05-ext-BF.Rmd
update supplemental material

@@
 
-To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes Factor with encompassing prior approach.
+To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes factor with the encompassing prior approach.
 See the main article for a detailed introduction to this approach [TODO: add link article].
@@
 Subsequently, we obtain the hypotheses matrices according to the informative hypotheses.
-Next, we compute the Bayes Factor and, finally, we describe the selected model.
+Next, we compute the Bayes factor and, finally, we describe the selected model.
 
@@
 
-### Prior Choiche
+### Prior Choice
 
@@
 
-We can evaluate the consequences of different values choice considering the resulting prior predictions.
+We can evaluate the consequences of different values’ choice considering the resulting prior predictions.
 To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest.
@@
 Considering that externalizing problems are bounded between 0 and 20, a reasonable prior is  $\mathcal{N}(0,3)$.
-as prior predicted values cover all possible values without including excessively large values.
+With these settings, prior predicted values cover all possible values without including excessively large values.
 More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values.
@@
 
-Here we present the obtained hypothesis matrices were on the columns we have the parameters of the encompassing model (excluding the intercept) and each row express an equality constraint or an inequality constraint.
-Matrices row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters).
-For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicate the group condition.
+Here we present the obtained hypothesis matrices where on the columns we have the parameters of the encompassing model (excluding the intercept) and each row expresses an equality constraint or an inequality constraint.
+Matrices’ row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters).
+For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicates the group condition.
 This is done because when assuming no interaction or no father attachment effect we set constraints directly on the model parameters, instead, when constraints involve group comparisons, we need to obtain the resulting conditions.
@@
 
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero). There are no inequality constraints.
+- **Inequality matrix**, $R_{iI} > 0$ (each row is set greater than zero). There are no inequality constraints.
 
@@
 
-- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
+- **Inequality matrix**, $R_{iI} > 0$ (each row is set greater than zero).
 ```{r cache=TRUE}
@@
 This adjustment, however, requires the hypothesis matrix $R$ to be *full-row-rank* (i.e., all constraints are linearly independent).
-However, this is not the case of the Hierarchy Hypothesis.
+However, this is not the case with the Hierarchy Hypothesis.
 To overcome this issue, we follow the solution presented in the main article.
@@
 
-Before computing the Bayes Factor, note that we have a set of comparable hypotheses as exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero.
-The solution is the trivial solution of simply consider all parameters equal to zero.
-Finally, we do not need to standardize our parameters as they represent mean groups differences.
+Before computing the Bayes factor, note that we have a set of comparable hypotheses as it exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero.
+The solution is the trivial solution of simply considering all parameters equal to zero.
+Finally, we do not need to standardize our parameters as they represent mean groups’ differences.
 See the main article for a detailed explanation [TODO: add link article].
@@
 
-To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in detail in the main article [TODO: add link article].
-Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).
+To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article [TODO: add link article].
+Bayes factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).
 
@@
 
-Remember, however, that prior specification affects the Bayes Factor results.
+Remember, however, that prior specification affects the Bayes factor results.
 Therefore, we also evaluate the results considering different prior settings.
@@
 However, we can observe two distinct patterns.
-As the prior gets more diffuse, the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
+As the prior gets more diffuse, the order of magnitude of the Bayes factor comparing each hypothesis with the encompassing model increases.
 Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.
@@
 To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
-On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details[TODO: add link article]).
+On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details [TODO: add link article]).
 
 All the defined hypotheses include equality constraints.
-Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
+Thus, for more diffuse prior we observe that the order of magnitude of the Bayes factor comparing each hypothesis with the encompassing model increases.
 Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).
@@
 
-One of the limits of the Bayes Factor with the encompassing prior approach is that we only get the selected hypothesis but we do not obtain the actual estimates of the parameters posterior.
+One of the limits of the Bayes factor with the encompassing prior approach is that we only get the selected hypothesis but we do not obtain the actual estimates of the parameters posterior.
 To overcome this limit we rely on Bayesian inference that allows us to effectively estimate the model parameter posteriors.
@@
 
-To evaluate the fit of the model to the data, we computed the *Bayesian* $R^2$ and using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-ext).
+To evaluate the fit of the model to the data, we computed the *Bayesian* $R^2$, using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-ext).
 
@@
 
-We can see that the actual variance explained by fixed effects and random effect is around 15\%. Moreover, posterior predictive check indicates a good fit to the data.
+We can see that the actual variance explained by fixed effects and random effects is around 15\%. Moreover, the posterior predictive check indicates a good fit to the data.
 

### 2021-11-28 Documents/Bookdown/06-ext-conclusion.Rmd
add bookdown int analysis
update supplemental material

@@
 ---
-# Conclusions Externalizing Problems {#conclusion-ext}
+# Conclusions {#conclusion-ext}
 
 Overall, we obtained consistent results from the three different approaches.
-Males have more problems than Females and, regarding attachment, only mother attachment influence children's externalizing problems.
+Males have more problems than Females and, regarding attachment, only mother attachment influences children's externalizing problems.
 In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems.
@@
 Thus, we reject the null hypothesis but we can not quantify the evidence in favour of any of our hypotheses.
-- Only model comparison allow us to quantify the relative evidence of our models.
+- Only model comparison allows us to quantify the relative evidence of our models.
 Model comparison results clearly indicated evidence in favour of an effect of mother attachment but not father attachment.
 However, using information criteria we could not directly evaluate our informative hypotheses regarding the expected effects, but only the presence of any effect.
-- Bayes Factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects.
+- Bayes factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects.
 Results clearly selected the Monotropy theory as the most likely theory among those considered.

### 2021-11-28 Documents/Bookdown/07-int-model-choice.Rmd
update supplemental material

@@
 As in the case of externalizing problems, we evaluate whether a *Zero-Inflated* model may be appropriate.
-We compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model considering the same predictors as in the case of externalizing problems.
+We compare the number of observed zeros and expected zeros in a Negative Binomial mixed-effects model considering the same predictors as in the case of externalizing problems.
 Using R formula syntax, we have
@@
 Note, however, that BIC actually prefers the model without zero inflation.
-Nevertheless, in the following analyses we decide to use ZINB models to be consistent with the externalizing problems analysis.
+Nevertheless, in the following analyses, we decide to use ZINB models to be consistent with the analysis of the externalizing problems.

### 2021-11-28 Documents/Bookdown/08-int-nhst.Rmd
update supplemental material

@@
 To evaluate the effect of mother attachment, the marginal predicted values are presented in Figure~\@ref(fig:plot-nhst-effects-int).
-Not that the marginal predicted values are averaged over father attachment and gender effect.
+Note that the marginal predicted values are averaged over father attachment and gender effect.
 ```{r plot-nhst-effects-int, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to mother attachment. Values are averaged over the other effects ($n_{subj} = 847$)."}
@@
 After adjusting p-values we actually get that there are no statistically significant differences.
-Without adjusting, difference between Anxious and Secure children and the difference between Fearful and Secure children have a low (but not statistically significant) *p*-value.
+Without adjusting, the difference between Anxious and Secure children and the difference between Fearful and Secure children have a low (but not statistically significant) *p*-value.
 ```{r, cache=TRUE, echo = TRUE}

### 2021-11-28 Documents/Bookdown/10-int-BF.Rmd
update supplemental material

@@
 
-Hypothesis matrices are the same as for the externalizing problems analysis.
+Hypothesis matrices are the same as in the analysis of the externalizing problems.
 
@@
 
-Centering and adjusting procedures are the same as for the externalizing problems analysis.
+Centering and adjusting procedures are the same as in the analysis of the externalizing problems.
 
@@
 
-Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-int).
+Bayes factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-int).
 
@@
 
-Prior sensitivity analysis is conducted considering the same prior as for the externalizing problems analysis.
+Prior sensitivity analysis is conducted considering the same prior as in the analysis of the externalizing problems.
 The results of the prior sensitivity analysis are reported in Table~\@ref(tab:table-sens-prior-analysis-int).
@@
 Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data.
-However, we can observe the same patterns as for the externalizing problems analysis.
+However, we can observe the same patterns as in the analysis of the externalizing problems.
 More diffuse prior, favour hypothesis with more equality constraints.
-Whereas, tighter prior penalize hypothesis with more equality constraints.
+Whereas, tighter prior penalizes hypotheses with more equality constraints.
 
@@
 
-In the model we consider only the role of gender and mother attachment as fixed effects of $\mu$. In the R formula syntax, we have
+In the model, we consider only the role of gender and mother attachment as fixed effects of $\mu$. In the R formula syntax, we have
 ```{r, echo=TRUE, eval=FALSE}
@@
 
-To evaluate the fit of the model to the data, we computed the *Bayesian* $R^2$ and using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-int).
+To evaluate the fit of the model to the data, we computed the *Bayesian* $R^2$ using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-int).
 
@@
 
-We can see that the actual variance explained by fixed effects and random effect is around 22\%. Moreover, posterior predictive check indicates a good fit to the data.
+We can see that the actual variance explained by fixed effects and random effects is around 22\%. Moreover, the posterior predictive check indicates a good fit to the data.
 

### 2021-11-28 Documents/Bookdown/11-int-conclusion.Rmd
update supplemental material

@@
 
-Overall, we obtained consistent results from the three different approaches: only mother attachment influence children's externalizing problems.
+Overall, we obtained consistent results from the three different approaches: only mother attachment influences children's externalizing problems.
 In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems.
-Compared to externalizing problems, however, difference between attachment groups are less pronounced.
+Compared to externalizing problems, however, differences between attachment groups are less pronounced.
 Taken together, these results support the Monotropy Theory.

### 2021-11-28 Documents/Bookdown/index.Rmd
update supplemental material

--- 2021-09-21 Documents/Bookdown/index.Rmd
@@
 github-repo: ClaudioZandonella/Attachment
-description: "This the Supplemental Material of the article “Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach”"
+description: "This the Supplemental Material of the article “Evaluating informative hypotheses with equality and inequality constraint: A tutorial using the Bayes factor via the encompassing prior approach”"
 cover-image: "images/logo_psicostat.png"
@@
 
-This is the Supplemental Material of the article “*Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach*” [TODO: add cit].
-The aim of the paper is to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.
+This is the Supplemental Material of the article “*Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach*” [TODO: add cit].
+The paper aims to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.
 
@@
 When conducting a study, researchers usually have expectations based on hypotheses or theoretical perspectives they want to evaluate.
-Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called “*informative hypotheses*”.
+Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called informative hypotheses.
 However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are unsuitable for testing complex informative hypotheses.
-An alternative approach is to use the Bayes Factor.
-In particular, the Bayes Factor based on the “*encompassing prior approach*” allows researchers to easily evaluate complex informative hypotheses.
-In this paper we provide a clear and detailed introduction to this approach.
-We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor following the encompassing prior approach.
-Subsequently, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development.
+An alternative approach is to use the Bayes factor.
+In particular, the Bayes factor based on the encompassing prior approach allows researchers to easily evaluate complex informative hypotheses in a wide range of statistical models (e.g., generalized linear).
+This paper provides a detailed introduction to the Bayes factor with encompassing prior.
+First, all steps and elements involved in the formalization of informative hypotheses and the computation of the Bayes factor with encompassing prior are described.
+Next, we apply this method to a real case scenario, considering the attachment theory.
+Specifically, we analyzed the relative influence of maternal and paternal attachment on children's social-emotional development by comparing the various theoretical perspectives debated in the literature.
 
@@
 
-In the supplemental material we provide the complete statistical analyses of the case study regarding attachment.
-For more information regarding the Bayes Factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article].
-The supplemental material is structure as follow:
+In the supplemental material, we provide the complete statistical analyses of the case study regarding attachment.
+For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article].
+The supplemental material is structured into three parts:
+
+#### 1) Presentation {-}
+
+In this section, we describe the aim of the study and the sample included in the study.
 
 - **Chapter \@ref(case-study) - Case Study.** We describe the sample included in the study and present the results of the cluster analysis to classify the different attachment patterns.
-- **Chapter \@ref(ext) - Externalizing Problems.** The analyses regarding externalizing problems are presented.
-First, we conduct the analysis following the traditional NHST approach.
-Subsequently, we consider Model Comparison using the AIC and BIC criteria.
-Finally, we consider the Bayes Factor with encompassing prior approach.
-- **Chapter \@ref(int) - Internalizing Problems.** The analyses regarding internalizing problems are presented.
-The analyses follow the same structure as the case of externalizing problems.
-Thus, only differences will be highlighted.
+
+#### 2) Externalizing Problems {-}
+
+In this section, we present the analyses evaluating the different roles of mother attachment and father attachment on children's externalizing problems. We follow three different approaches.
+
+- **Chapter \@ref(model-choice-ext) - Models Family Choice.**  We discuss the appropriate models’ family to take into account data characteristics.
+- **Chapter \@ref(nhst-ext) - NHST.**  Analysis is conducted following the traditional Null Hypothesis Significance Testing (NHST).
+- **Chapter \@ref(model-comparison-ext) - Model Comparison.**  Analysis is conducted according to the  Model Comparison approach using the AIC and BIC criteria.
+- **Chapter \@ref(BF-ext) - Bayes Factor.**  Analysis is conducted following the Bayes Factor with the encompassing prior approach.
+- **Chapter \@ref(conclusion-ext) - Conclusions.**  Results of the three approaches are discussed.
+
+#### 3) Internalizing Problems {-}
+
+In this section, we present the analyses evaluating the different roles of mother attachment and father attachment on children's internalizing problems.
+We follow the three different approaches like in the analysis of the externalizing problems.
+This section is shorter than the previous one as we focus only on the results without repeating all the descriptions of the methods.
+
+- **Chapter \@ref(model-choice-int) - Models Family Choice.**  We discuss the appropriate models’ family to take into account data characteristics.
+- **Chapter \@ref(nhst-int) - NHST.**  Analysis is conducted following the traditional Null Hypothesis Significance Testing (NHST).
+- **Chapter \@ref(model-comparison-int) - Model Comparison.**  Analysis is conducted according to the  Model Comparison approach using the AIC and BIC criteria.
+- **Chapter \@ref(BF-int) - Bayes Factor.**  Analysis is conducted following the Bayes Factor with the encompassing prior approach.
+- **Chapter \@ref(conclusion-int) - Conclusions.**  Results of the three approaches are discussed.
 

### 2021-11-28 docs/attachment-bayes-factor.tex
update supplemental material

@@
 \author{\href{https://claudiozandonella.netlify.app/}{Claudio Zandonella Callegher}, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
-\date{2021-09-21}
+\date{2021-11-28}
 
@@
 
-This is the Supplemental Material of the article ``\emph{Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach}'' {[}TODO: add cit{]}.
-The aim of the paper is to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.
+This is the Supplemental Material of the article ``\emph{Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach}'' {[}TODO: add cit{]}.
+The paper aims to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.
 
@@
 When conducting a study, researchers usually have expectations based on hypotheses or theoretical perspectives they want to evaluate.
-Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called ``\emph{informative hypotheses}''.
+Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called informative hypotheses.
 However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are unsuitable for testing complex informative hypotheses.
-An alternative approach is to use the Bayes Factor.
-In particular, the Bayes Factor based on the ``\emph{encompassing prior approach}'' allows researchers to easily evaluate complex informative hypotheses.
-In this paper we provide a clear and detailed introduction to this approach.
-We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor following the encompassing prior approach.
-Subsequently, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development.
+An alternative approach is to use the Bayes factor.
+In particular, the Bayes factor based on the encompassing prior approach allows researchers to easily evaluate complex informative hypotheses in a wide range of statistical models (e.g., generalized linear).
+This paper provides a detailed introduction to the Bayes factor with encompassing prior.
+First, all steps and elements involved in the formalization of informative hypotheses and the computation of the Bayes factor with encompassing prior are described.
+Next, we apply this method to a real case scenario, considering the attachment theory.
+Specifically, we analyzed the relative influence of maternal and paternal attachment on children's social-emotional development by comparing the various theoretical perspectives debated in the literature.
 
@@
 
-In the supplemental material we provide the complete statistical analyses of the case study regarding attachment.
-For more information regarding the Bayes Factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article {[}TODO: add link article{]}.
-The supplemental material is structure in three parts:
+In the supplemental material, we provide the complete statistical analyses of the case study regarding attachment.
+For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article {[}TODO: add link article{]}.
+The supplemental material is structured into three parts:
 
@@
 
-\hypertarget{exteranlizing-problems}{%
-\subsubsection*{2) Exteranlizing Problems}\label{exteranlizing-problems}}
-\addcontentsline{toc}{subsubsection}{2) Exteranlizing Problems}
-
-In this section, we present the analyses evaluating the different role of mother attachment and father attachment on children's externalizing problems. We follow three different approaches.
+\hypertarget{externalizing-problems}{%
+\subsubsection*{2) Externalizing Problems}\label{externalizing-problems}}
+\addcontentsline{toc}{subsubsection}{2) Externalizing Problems}
+
+In this section, we present the analyses evaluating the different roles of mother attachment and father attachment on children's externalizing problems. We follow three different approaches.
 
@@
 \item
-  \textbf{Chapter \ref{model-choice-ext} - Models Family Choice.} We discuss the appropriate models family to to take into account data characteristics.
-\item
-  \textbf{Chapter \ref{nhst-ext} - NHST.} Analysis are conducted following the traditional Null Hypothesis Significance Testing (NHST).
-\item
-  \textbf{Chapter \ref{model-comparison-ext} - Model Comparison.} Analysis are conducted according to the Model Comparison approach using the AIC and BIC criteria.
-\item
-  \textbf{Chapter \ref{BF-ext} - Bayes Factor.} Analysis are conducted following the Bayes Factor with encompassing prior approach.
-\item
-  \textbf{Chapter \ref{conclusion-ext} - Conclusion.} Results of the three approaches are discussed.
+  \textbf{Chapter \ref{model-choice-ext} - Models Family Choice.} We discuss the appropriate models' family to take into account data characteristics.
+\item
+  \textbf{Chapter \ref{nhst-ext} - NHST.} Analysis is conducted following the traditional Null Hypothesis Significance Testing (NHST).
+\item
+  \textbf{Chapter \ref{model-comparison-ext} - Model Comparison.} Analysis is conducted according to the Model Comparison approach using the AIC and BIC criteria.
+\item
+  \textbf{Chapter \ref{BF-ext} - Bayes Factor.} Analysis is conducted following the Bayes Factor with the encompassing prior approach.
+\item
+  \textbf{Chapter \ref{conclusion-ext} - Conclusions.} Results of the three approaches are discussed.
 \end{itemize}
 
-\hypertarget{interanlizing-problems}{%
-\subsubsection*{3) Interanlizing Problems}\label{interanlizing-problems}}
-\addcontentsline{toc}{subsubsection}{3) Interanlizing Problems}
-
-In this section, we present the analyses evaluating the different role of mother attachment and father attachment on children's internalizing problems.
-We follow the three different approaches as for the externalizing problems analysis.
-This section is shorter than previous as we focus only on the results without repeating all the descriptions of the methods.
+\hypertarget{internalizing-problems}{%
+\subsubsection*{3) Internalizing Problems}\label{internalizing-problems}}
+\addcontentsline{toc}{subsubsection}{3) Internalizing Problems}
+
+In this section, we present the analyses evaluating the different roles of mother attachment and father attachment on children's internalizing problems.
+We follow the three different approaches like in the analysis of the externalizing problems.
+This section is shorter than the previous one as we focus only on the results without repeating all the descriptions of the methods.
 
@@
 \item
-  \textbf{Chapter \ref{model-choice-int} - Models Family Choice.} We discuss the appropriate models family to to take into account data characteristics.
-\item
-  \textbf{Chapter \ref{nhst-int} - NHST.} Analysis are conducted following the traditional Null Hypothesis Significance Testing (NHST).
-\item
-  \textbf{Chapter \ref{model-comparison-int} - Model Comparison.} Analysis are conducted according to the Model Comparison approach using the AIC and BIC criteria.
-\item
-  \textbf{Chapter \ref{BF-int} - Bayes Factor.} Analysis are conducted following the Bayes Factor with encompassing prior approach.
-\item
-  \textbf{Chapter \ref{conclusion-int} - Conclusion.} Results of the three approaches are discussed.
+  \textbf{Chapter \ref{model-choice-int} - Models Family Choice.} We discuss the appropriate models' family to take into account data characteristics.
+\item
+  \textbf{Chapter \ref{nhst-int} - NHST.} Analysis is conducted following the traditional Null Hypothesis Significance Testing (NHST).
+\item
+  \textbf{Chapter \ref{model-comparison-int} - Model Comparison.} Analysis is conducted according to the Model Comparison approach using the AIC and BIC criteria.
+\item
+  \textbf{Chapter \ref{BF-int} - Bayes Factor.} Analysis is conducted following the Bayes Factor with the encompassing prior approach.
+\item
+  \textbf{Chapter \ref{conclusion-int} - Conclusions.} Results of the three approaches are discussed.
 \end{itemize}
@@
 
-The aim of the study is to compare the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social emotional development.
+The study aims to compare the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social-emotional development.
 In the literature, four different main theoretical perspectives have been identified \citep{brethertonFathersAttachmentTheory2010}:
@@
 \item
-  \textbf{Hierarchy Theory} - the mother has a greater impact on children development than the the father.
+  \textbf{Hierarchy Theory} - the mother has a greater impact on children's development than the father.
 \item
@@
 
-For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article {[}TODO: add link article{]}.
+For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article {[}TODO: add link article{]}.
 
@@
 
-To evaluate the different role of father attachment and mother attachment, we consider 854 Italian children from third to sixth school grade.
-Only middle-childhood children are included in the analysis (5 participants are excluded as older than 12.3 years and 2 participants are excluded are excluded as the age is missing).
+To evaluate the different roles of father attachment and mother attachment, we consider 854 Italian children from third to sixth school grade.
+Only middle-childhood children are included in the analysis (5 participants are excluded as older than 12.3 years and 2 participants are excluded as the age is missing).
 The total sample size included in the analysis is 847 (50.65 \% Females).
-Participants frequencies by grade and gender are reported in Table\textasciitilde\ref{tab:table-gender-grade}.
+Participants' frequencies by grade and gender are reported in Table\textasciitilde\ref{tab:table-gender-grade}.
 
@@
 
-Participants age mean is 10.28 (SD = 1.34). The participants age summary statistics are reported below and the distribution is presented in Figure\textasciitilde\ref{fig:plot-age}.
+Participants' age mean is 10.28 (SD = 1.34). The participants' age summary statistics are reported below and the distribution is presented in Figure\textasciitilde\ref{fig:plot-age}.
 
@@
 
-Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale (ECR; {[}TODO add references{]}) completed by the children.
+Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version {[}ECR-RC, \citet{Brenning2014ThePQ}; marciBriefExperiencesClose2019{]} completed by the children.
 Four main attachment styles have been recognized in the literature according to thee levels of \emph{anxiety} and \emph{avoidance}:
@@
 
-To identify children attachment styles towards the mother and towards the father, we conduct two separate cluster analyses.
+To identify children's attachment styles towards the mother and towards the father, we conduct two separate cluster analyses.
 Clusters are obtained using the function \texttt{hclust()} (with argument \texttt{method="ward.D"}) considering \emph{Euclidean} distances between participants responses to the ECR items.
@@
 These results reflect the traditional definition of the four attachment styles.
-Moreover, attachment styles frequencies are in lines with general results in the literature {[}TODO: add reference values{]}.
 
@@
 
-To evaluate if 4 cluster is an appropriate choice, we compare the BIC values of different model-based clustering options.
+To evaluate if 4 clusters is an appropriate choice, we compare the BIC values of different model-based clustering options.
 To do that we use the function \texttt{mclustBIC()} from the \texttt{mclust} R-package \citep{scruccaMclustClusteringClassification2016}.
-BIC values of the best three model-based clustering are reported below and overall results are presented in Figure\textasciitilde\ref{fig:plot-mclust-mother}.
+BIC values of the best three model-based clusterings are reported below and overall results are presented in Figure\textasciitilde\ref{fig:plot-mclust-mother}.
 See \texttt{?mclustBIC()} help page for further information.
@@
 
-These results are no as good as in the mother attachment classification, but they are still reasonable.
-Moreover, attachment styles frequencies are close to the general results in the literature {[}TODO: add reference values{]}.
+These results are not as good as in the mother attachment classification, but they are still reasonable.
 
@@
 
-To evaluate if 4 cluster is an appropriate choice, we compare the BIC values of different model-based clustering options as before.
-BIC values of the best three model-based clustering are reported below and overall results are presented in Figure\textasciitilde\ref{fig:plot-mclust-father}.
+To evaluate if 4 clusters is an appropriate choice, we compare the BIC values of different model-based clustering options as before.
+BIC values of the best three model-based clusterings are reported below and overall results are presented in Figure\textasciitilde\ref{fig:plot-mclust-father}.
 
@@
 
-Children's social-emotional development was measured using the Strength \& Difficulties Questionnaire (SDQ; {[}TODO add references{]}) completed by the teachers.
-Separate scores for externalizing and internalizing problems were obtained as sum of the questionnaire items.
-
-\hypertarget{externalizing-problems}{%
-\subsection{Externalizing Problems}\label{externalizing-problems}}
+Children's social-emotional development was measured using the Strength and Difficulties Questionnaire \citep[SDQ,][]{goodmanWhenUseBroader2010} completed by the teachers.
+Separate scores for externalizing and internalizing problems were obtained as the sum of the questionnaire items.
+
+\hypertarget{externalizing-problems-1}{%
+\subsection{Externalizing Problems}\label{externalizing-problems-1}}
 
 Participants externalizing problems mean is 3.35 (SD = 3.91).
-The participants externalizing problems summary statistics are reported below and the distribution is presented in Figure\textasciitilde\ref{fig:plot-externalizing-dist}.
+The participants' externalizing problems summary statistics are reported below and the distribution is presented in Figure\textasciitilde\ref{fig:plot-externalizing-dist}.
 
@@
 Overall, externalizing problems are low.
-This is expected as the sample is not a clinical sample.
+This is expected as the sample is not clinical.
 Externalizing problems according to attachment styles are reported in Table\textasciitilde\ref{tab:table-cluster-ext}.
@@
 \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
-\textbf{Mother Attachemnt} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median}\\
+\textbf{Mother Attachment} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median} & \textbf{Mean (SD)} & \textbf{Median}\\
 \midrule
@@
 
-\hypertarget{internalizing-problems}{%
-\subsection{Internalizing Problems}\label{internalizing-problems}}
+\hypertarget{internalizing-problems-1}{%
+\subsection{Internalizing Problems}\label{internalizing-problems-1}}
 
@@
 \begin{verbatim}
-##   #
+##   # Internalizing problems summary statistics
 ##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
@@
 Overall, internalizing problems are low.
-Again, this is expected as the sample is not a clinical sample.
+Again, this is expected as the sample is not clinical.
 Internalizing problems according to attachment styles are reported in Table\textasciitilde{}\ref(tab:table-cluster-ext).
@@
 
-In this chapter, we discuss the appropriate models family to to take into account data characteristics.
+In this chapter, we discuss the appropriate models' family to take into account data characteristics.
 
@@
 Considering data distribution (see Figure\textasciitilde\ref{fig:plot-externalizing-dist}), we can observe that data have high dispersion with a long right tail.
-In this case, Poisson distribution would be a poor choice and we prefer Negative Binomial instead.
-
-Again, considering data distribution (see Figure\textasciitilde\ref{fig:plot-externalizing-dist}), we can observe an high peak of values at zero.
-Remember that this is not a clinical sample, thus it is expected that children majority has no problems or really few problem.
+In this case, the Poisson distribution would be a poor choice and we prefer Negative Binomial instead.
+
+Again, considering data distribution (see Figure\textasciitilde\ref{fig:plot-externalizing-dist}), we can observe a high peak of values at zero.
+Remember that this is not a clinical sample, thus it is expected that the majority of children have no problems or really few problems.
 We could question ourselves, however, whether a \emph{Zero-Inflated} model may be appropriate
@@
 That is, both \(p\) and \(\mu\) are modelled separately according to (possibly) different variables.
-In our case, we consider only the role of gender for \(p\) (i.e., the probability of having externalizing problems depends on gender), whereas for \(\mu\) the consider also the interaction between mother attachment and father attachment.
+In our case, we consider only the role of gender for \(p\) (i.e., the probability of having externalizing problems depends on gender), whereas for \(\mu\) we also consider the interaction between mother attachment and father attachment.
 In both cases, we consider the children's classroom ID as a random effect (teachers may differ in the ability to detect children's problems and quantify them).
@@
 
-The ZINB model is fitted using the function \texttt{zeroinfl()} from the \texttt{pscl} R-package \citep{zeileisRegressionModelsCount2008}.
+The ZINB model is fitted using the function \texttt{glmmTMB()}.
 To compare the ZINB model and the Negative Binomial model we conduct an analysis of \emph{Deviance}.
@@
 \DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
-\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1719}
-\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.162 825  {-}1.902  0.2227}
-\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5617 0.178 825  {-}3.149  0.0092}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1720}
+\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.162 825  {-}1.902  0.2228}
+\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5617 0.178 825  {-}3.149  0.0089}
 \DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0224 0.124 825  {-}0.181  0.9978}
@@
 To interpret these results, note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.
-As pointed by \citet{kuhaAICBICComparisons2004}, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
+As pointed out by \citet{kuhaAICBICComparisons2004}, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion.
 We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.
@@
 
-Considering model \texttt{fit\_ext\_mother}, we can run an analysis of deviance to evaluate the significance of the predictors.
+Considering the model \texttt{fit\_ext\_mother}, we can run an analysis of deviance to evaluate the significance of the predictors.
 
@@
 \DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
-\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2432 0.1034 837  {-}2.353  0.0858}
-\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0244}
-\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0004}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2432 0.1034 837  {-}2.353  0.0859}
+\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0247}
+\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0003}
 \DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0648 0.0981 837  {-}0.661  0.9107}
-\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0902}
+\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0898}
 \DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2188 0.1276 837  {-}1.714  0.3135}
@@
 
-To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes Factor with encompassing prior approach.
+To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes factor with the encompassing prior approach.
 See the main article for a detailed introduction to this approach {[}TODO: add link article{]}.
@@
 
-\hypertarget{prior-choiche}{%
-\subsection{Prior Choiche}\label{prior-choiche}}
+\hypertarget{prior-choice}{%
+\subsection{Prior Choice}\label{prior-choice}}
 
@@
 
-We can evaluate the consequences of different values choice considering the resulting prior predictions.
+We can evaluate the consequences of different values' choice considering the resulting prior predictions.
 To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest.
@@
 Considering that externalizing problems are bounded between 0 and 20, a reasonable prior is \(\mathcal{N}(0,3)\).
-as prior predicted values cover all possible values without including excessively large values.
+With these settings, prior predicted values cover all possible values without including excessively large values.
 More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values.
@@
 
-Here we present the obtained hypothesis matrices were on the columns we have the parameters of the encompassing model (excluding the intercept) and each row express an equality constraint or an inequality constraint.
-Matrices row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters).
-For example, \texttt{"M\_Avoidant:F\_Anxious"} indicates the actual interaction term of the model, whereas \texttt{"{[}M\_Avoidant\_F\_Anxious{]}"} indicate the group condition.
+Here we present the obtained hypothesis matrices where on the columns we have the parameters of the encompassing model (excluding the intercept) and each row expresses an equality constraint or an inequality constraint.
+Matrices' row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters).
+For example, \texttt{"M\_Avoidant:F\_Anxious"} indicates the actual interaction term of the model, whereas \texttt{"{[}M\_Avoidant\_F\_Anxious{]}"} indicates the group condition.
 This is done because when assuming no interaction or no father attachment effect we set constraints directly on the model parameters, instead, when constraints involve group comparisons, we need to obtain the resulting conditions.
@@
 \item
-  \textbf{Inequality matrix}, \(R_{iI} > 0\) (each row is set to grater than zero). There are no inequality constraints.
+  \textbf{Inequality matrix}, \(R_{iI} > 0\) (each row is set greater than zero). There are no inequality constraints.
 \end{itemize}
@@
 \item
-  \textbf{Inequality matrix}, \(R_{iI} > 0\) (each row is set to grater than zero).
+  \textbf{Inequality matrix}, \(R_{iI} > 0\) (each row is set greater than zero).
 \end{itemize}
@@
 This adjustment, however, requires the hypothesis matrix \(R\) to be \emph{full-row-rank} (i.e., all constraints are linearly independent).
-However, this is not the case of the Hierarchy Hypothesis.
+However, this is not the case with the Hierarchy Hypothesis.
 To overcome this issue, we follow the solution presented in the main article.
@@
 
-Before computing the Bayes Factor, note that we have a set of comparable hypotheses as exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero.
-The solution is the trivial solution of simply consider all parameters equal to zero.
-Finally, we do not need to standardize our parameters as they represent mean groups differences.
+Before computing the Bayes factor, note that we have a set of comparable hypotheses as it exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero.
+The solution is the trivial solution of simply considering all parameters equal to zero.
+Finally, we do not need to standardize our parameters as they represent mean groups' differences.
 See the main article for a detailed explanation {[}TODO: add link article{]}.
@@
 
-To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in detail in the main article {[}TODO: add link article{]}.
-Bayes Factor and posterior probability of each hypothesis are reported in Table\textasciitilde\ref{tab:table-bf-results-ext}.
+To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article {[}TODO: add link article{]}.
+Bayes factor and posterior probability of each hypothesis are reported in Table\textasciitilde\ref{tab:table-bf-results-ext}.
 
@@
 
-\caption{\label{tab:table-bf-results-ext}Bayes Factor encompassing model and hypothesis posteriro probabilities  ($n_{subj} = 847$).}
+\caption{\label{tab:table-bf-results-ext}Bayes factor encompassing model and hypothesis posterior probabilities  ($n_{subj} = 847$).}
 \centering
@@
 
-\caption{\label{tab:table-sens-prior-analysis-ext}Bayes Factor encompassing model v and hypothesis posterior probabilities (PP) under different prior settings  ($n_{subj} = 847$).}
+\caption{\label{tab:table-sens-prior-analysis-ext}Bayes factor encompassing model and hypothesis posterior probabilities (PP) under different prior settings  ($n_{subj} = 847$).}
 \centering
@@
 To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
-On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details{[}TODO: add link article{]}).
+On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details {[}TODO: add link article{]}).
 
 All the defined hypotheses include equality constraints.
-Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases.
+Thus, for more diffuse prior we observe that the order of magnitude of the Bayes factor comparing each hypothesis with the encompassing model increases.
 Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).
@@
 
-To evaluate the fit of the model to the data, we computed the \emph{Bayesian} \(R^2\) and using the function \texttt{brms::bayes\_R2()}, and we present Posterior Predictions in Figure\textasciitilde\ref{fig:plot-ppcheck-ext}.
+To evaluate the fit of the model to the data, we computed the \emph{Bayesian} \(R^2\), using the function \texttt{brms::bayes\_R2()}, and we present Posterior Predictions in Figure\textasciitilde\ref{fig:plot-ppcheck-ext}.
 
@@
 Overall, we obtained consistent results from the three different approaches.
-Males have more problems than Females and, regarding attachment, only mother attachment influence children's externalizing problems.
+Males have more problems than Females and, regarding attachment, only mother attachment influences children's externalizing problems.
 In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems.
@@
 \item
-  Only model comparison allow us to quantify the relative evidence of our models.
+  Only model comparison allows us to quantify the relative evidence of our models.
 Model comparison results clearly indicated evidence in favour of an effect of mother attachment but not father attachment.
@@
 \item
-  Bayes Factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects.
+  Bayes factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects.
 Results clearly selected the Monotropy theory as the most likely theory among those considered.
@@
 As in the case of externalizing problems, we evaluate whether a \emph{Zero-Inflated} model may be appropriate.
-We compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model considering the same predictors as in the case of externalizing problems.
+We compare the number of observed zeros and expected zeros in a Negative Binomial mixed-effects model considering the same predictors as in the case of externalizing problems.
 Using R formula syntax, we have
@@
 Note, however, that BIC actually prefers the model without zero inflation.
-Nevertheless, in the following analyses we decide to use ZINB models to be consistent with the externalizing problems analysis.
+Nevertheless, in the following analyses, we decide to use ZINB models to be consistent with the analysis of the externalizing problems.
 
@@
 To evaluate the effect of mother attachment, the marginal predicted values are presented in Figure\textasciitilde\ref{fig:plot-nhst-effects-int}.
-Not that the marginal predicted values are averaged over father attachment and gender effect.
+Note that the marginal predicted values are averaged over father attachment and gender effect.
 
@@
 \DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
-\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2150 0.117 825  {-}1.836  0.2509}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2150 0.117 825  {-}1.836  0.2508}
 \DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.0653 0.136 825  {-}0.481  0.9622}
-\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.2985 0.166 825  {-}1.793  0.2708}
-\DocumentationTok{\#\#  Anxious {-} Avoidant   0.1496 0.112 825   1.336  0.5322}
+\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.2985 0.166 825  {-}1.793  0.2707}
+\DocumentationTok{\#\#  Anxious {-} Avoidant   0.1496 0.112 825   1.336  0.5321}
 \DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.0835 0.147 825  {-}0.566  0.9403}
@@
 After adjusting p-values we actually get that there are no statistically significant differences.
-Without adjusting, difference between Anxious and Secure children and the difference between Fearful and Secure children have a low (but not statistically significant) \emph{p}-value.
+Without adjusting, the difference between Anxious and Secure children and the difference between Fearful and Secure children have a low (but not statistically significant) \emph{p}-value.
 
@@
 
-AIC and BIC values together with their relative weights are computed are reported in Table\textasciitilde\ref{tab:table-AIC-BIC-weights-int}.
+AIC and BIC values together with their relative weights are computed and reported in Table\textasciitilde\ref{tab:table-AIC-BIC-weights-int}.
 
@@
 \DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
-\DocumentationTok{\#\#  Secure {-} Anxious     {-}0.285 0.0892 837  {-}3.197  0.0077}
+\DocumentationTok{\#\#  Secure {-} Anxious     {-}0.285 0.0892 837  {-}3.197  0.0075}
 \DocumentationTok{\#\#  Secure {-} Avoidant    {-}0.120 0.0946 837  {-}1.266  0.5809}
-\DocumentationTok{\#\#  Secure {-} Fearful     {-}0.469 0.1168 837  {-}4.011  0.0004}
+\DocumentationTok{\#\#  Secure {-} Fearful     {-}0.469 0.1168 837  {-}4.011  0.0003}
 \DocumentationTok{\#\#  Anxious {-} Avoidant    0.165 0.0869 837   1.903  0.2243}
 \DocumentationTok{\#\#  Anxious {-} Fearful    {-}0.183 0.1096 837  {-}1.673  0.3347}
-\DocumentationTok{\#\#  Avoidant {-} Fearful   {-}0.349 0.1167 837  {-}2.989  0.0146}
+\DocumentationTok{\#\#  Avoidant {-} Fearful   {-}0.349 0.1167 837  {-}2.989  0.0148}
 \DocumentationTok{\#\# }
@@
 
-\hypertarget{prior-choiche-1}{%
-\subsection{Prior Choiche}\label{prior-choiche-1}}
+\hypertarget{prior-choice-1}{%
+\subsection{Prior Choice}\label{prior-choice-1}}
 
@@
 
-Bayes Factor and posterior probability of each hypothesis are reported in Table\textasciitilde\ref{tab:table-bf-results-int}.
+Bayes factor and posterior probability of each hypothesis are reported in Table\textasciitilde\ref{tab:table-bf-results-int}.
 
@@
 
-\caption{\label{tab:table-bf-results-int}Bayes Factor encompassing model and hypothesis posteriro probabilities  ($n_{subj} = 847$).}
+\caption{\label{tab:table-bf-results-int}Bayes factor encompassing model and hypothesis posterior probabilities  ($n_{subj} = 847$).}
 \centering
@@
 
-Prior sensitivity analysis is conducted considering the same prior as for the externalizing problems analysis.
+Prior sensitivity analysis is conducted considering the same prior as in the analysis of the externalizing problems.
 The results of the prior sensitivity analysis are reported in Table\textasciitilde\ref{tab:table-sens-prior-analysis-int}.
@@
 
-\caption{\label{tab:table-sens-prior-analysis-int}Bayes Factor encompassing model v and hypothesis posterior probabilities (PP) under different prior settings  ($n_{subj} = 847$).}
+\caption{\label{tab:table-sens-prior-analysis-int}Bayes factor encompassing model and hypothesis posterior probabilities (PP) under different prior settings  ($n_{subj} = 847$).}
 \centering
@@
 
-In the model we consider only the role of gender and mother attachment as fixed effects of \(\mu\). In the R formula syntax, we have
+In the model, we consider only the role of gender and mother attachment as fixed effects of \(\mu\). In the R formula syntax, we have
 
@@
 
-To evaluate the fit of the model to the data, we computed the \emph{Bayesian} \(R^2\) and using the function \texttt{brms::bayes\_R2()}, and we present Posterior Predictions in Figure\textasciitilde\ref{fig:plot-ppcheck-int}.
+To evaluate the fit of the model to the data, we computed the \emph{Bayesian} \(R^2\) using the function \texttt{brms::bayes\_R2()}, and we present Posterior Predictions in Figure\textasciitilde\ref{fig:plot-ppcheck-int}.
 

### 2021-11-28 README.Rmd
update read me

@@
 
-# Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach
+# Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach
 
-In this repository we collect all the materials of the study “*Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach*”.
-The aim of the paper is to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example regarding attachment theory.
+In this repository we collect all the materials of the study “*Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach*”.
+The paper aims to provide a clear and detailed description of the Bayes factor with the encompassing prior approach considering an applied example regarding attachment theory.
 
@@
 To know more about `drake` consider the [official Git-hub page](https://github.com/ropensci/drake) or the [user manual](https://books.ropensci.org/drake/).
-Summarizing, using `drake` the user defines the plan of the analysis where each step in the analysis is defined trough functions.
+Summarizing, using `drake` the user defines the plan of the analysis where each step in the analysis is defined through functions.
 Functions can be appropriately defined to obtain desired targets (i.e., R-output with results of interests) and they are declared in another script.
@@
 When any change is made to the code `drake` evaluates the analysis and updates the results.
-Following the *functional programming paradigm* (i.e., defining functions for each step of the analysis), it allows us to avoid "*coping and paste*" in the code, it makes debugging easier, and it facilitates the reading of the code.
+Following the *functional programming paradigm* (i.e., defining functions for each step of the analysis) allows us to avoid "*coping and paste*" in the code, it makes debugging easier, and it facilitates the reading of the code.
 
 Moreover, the R-package `renv` is used to manage the dependencies of the R-packages used in the analysis.
-The `renv` package allows to create an isolated, portable, and reproducible environment where the analyses are run.
+The `renv` package allows the creation of an isolated, portable, and reproducible environment where the analyses are run.
 To know more about `renv` consider the [official documentation](https://rstudio.github.io/renv/articles/renv.html).
@@
 
-1. Download the the repository on your local machine
+1. Download the repository on your local machine
     ```{bash, eval = FALSE}
@@
 1. Open the R project by double-clicking the file `Attachment.Rproj` you can find in the project main directory. A new R-studio session will open.
-1. Run `renv::restore()` to install project's dependencies (have a coffee, it takes some time).
+1. Run `renv::restore()` to install the project's dependencies (have a coffee, it takes some time).
 1.
@@
 
-    > Note that also `source("Documents/Utils_report.R")` is automatically run to load report utilities functions (functions to load analysis results and to compile the bookdown).
+    > Note that also `source("Documents/Utils_report.R")` is automatically run to load report utility functions (functions to load analysis results and to compile the bookdown).
 
@@
 Open `Analysis/Analysis_Drake.R` and run each line (one by one) to run the analysis using drake.
-First, the analysis environment is setted together with the analysis plan (available at `R/Plan.R`).
-Next the analysis targets are computed (have a coffee, it takes a long time).
+First, the analysis environment is set together with the analysis plan (available at `R/Plan.R`).
+Next, the analysis targets are computed (have a coffee, it takes a long time).
 Finally, the analysis results are loaded and briefly presented.
 
-    > Note that you can access the analysis targets with using the functions `drake::loadd(<name_target>)`, or load all the results with `drake_load_all()`.
+    > Note that you can access the analysis targets using the functions `drake::loadd(<name_target>)`, or load all the results with `drake_load_all()`.
 
-    > It could happen that some times the session session stay idle when fitting `brms` models without throwing errors.
+    > It could happen that sometimes the session stays idle when fitting `brms` models without throwing errors.
 In this case, it is necessary to force restarting the R session and rerun the analysis.
-An error warning message will appear `Error: drake's cache is locked`.
+An error warning message will appear: `Error: drake's cache is locked`.
 Just follow the instructions provided by drake to force unlock of the cache  `drake::drake_cache("...")$unlock()`.
@@
 
-To run the analysis in a Docker container, build the image according to the `Dockerfile` present in the project main directory, using
+To run the analysis in a Docker container, first, download the repository on your local machine. Next, build the image according to the `Dockerfile` present in the project main directory, using
 ```{bash, eval = FALSE}
@@
 
-> It is important too build the image before to run the analysis
+> It is important to build the image before running the analysis
 

### 2021-11-28 R/Tables.R
corrige tables

@@ -106,7 +106,7 @@ get_table_bf <- function(bf_result = BF_weights_ext,
     # mutate_at(c("hypothesis", "bf","weights"), centerText) %>%
     kable(., format = format, booktabs = TRUE, align = c("r", rep("c", 3)), escape = FALSE,
           col.names = c("Hypothesis", "Bayes Factor", "Posterior Probability", " "),
-          caption = "Bayes Factor encompassing model and hypothesis posterior probabilities  ($n_{subj} = 847$).") %>%
+          caption = "Bayes factor encompassing model and hypothesis posterior probabilities  ($n_{subj} = 847$).") %>%
     column_spec(4, image = spec_image(images, image_size, image_size),
                 extra_css = "vertical-align:middle;padding-bottom: 0px;",
                 width = col_width, latex_valign = "m") %>%
@@ -138,7 +138,7 @@ get_table_sens_analysis <- function(summary_sensitivity, format = c("latex", "ht
                      "Independence", "Integration")) %>%
     kable(., format = format, booktabs = T, align = c("r", rep("c", 3)), escape = FALSE,
           col.names = c("Hypothesis", rep(c("BF", "PP"), 5)),
-          caption = "Bayes Factor encompassing model v and hypothesis posterior probabilities (PP) under different prior settings  ($n_{subj} = 847$).")
+          caption = "Bayes factor encompassing model and hypothesis posterior probabilities (PP) under different prior settings  ($n_{subj} = 847$).")
 
   if(format == "html"){
     table <- table %>%

### 2021-11-28 Documents/Paper/paper.Rnw
add affiliation paper

@@
 \author{Claudio Zandonella Callegher$^1$, Tatiana Marci$^1$, Pietro De Carli$^2$, Gianmarco Altoè$^1$}
-\affiliation{$^1$UNIPD\\$^2$UNIMI}
+\affiliation{$^1$Department of Developmental Psychology and Socialization, University of Padova\\
+$^2$UNIMI TODO }
 
@@
 All analyses were conducted using R statistical software \parencite[v\Sexpr{paste(version$major,version$minor, sep = ".")};][]{rcoreteamLanguageEnvironmentStatistical2021}.
-All materials, data, and analysis code are available at \url{https://github.com/ClaudioZandonella/Attachment}.
+All materials, data, and analysis code are available at \url{https://github.com/ClaudioZandonella/Attachment} [TDO add doi].
 Supplemental Material with further details is also available online at \url{https://claudiozandonella.github.io/Attachment/}.

### 2021-11-28 Documents/Bookdown/index.Rmd
fix title supplemental

@@
 --- 
-title: "Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach"
+title: "Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach"
 subtitle: "Supplemental Material"

### 2021-11-28 docs/attachment-bayes-factor.tex
fix title supplemental

@@
 \hypersetup{
-  pdftitle={Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach},
+  pdftitle={Evaluating Informative Hypotheses with Equality and Inequality Constraints:~A Tutorial Using the Bayes Factor via the Encompassing Prior Approach},
   pdfauthor={Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè},
@@
 
-\title{Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach}
+\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints:~A Tutorial Using the Bayes Factor via the Encompassing Prior Approach}
 \usepackage{etoolbox}

### 2021-11-28 Documents/Paper/paper.Rnw
add doi

@@
 
-Data used for the illustrative application are part of a larger project on the socioemotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]).
-All materials and data are available at [TODO].
+Data used for the illustrative application are part of a larger project on the social-emotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]).
+All materials and data are available at \url{10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
 
@@
 More information about the sample, descriptive statistics, cluster analysis, and analysis of internalizing problems can be found in the Supplemental Material available online \url{https://claudiozandonella.github.io/Attachment/}.
-All materials and data are available at [TODO].
+All materials and data are available at \url{10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
 

### 2021-11-28 Documents/Paper/paper.Rnw
fix doi

@@
 Data used for the illustrative application are part of a larger project on the social-emotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]).
-All materials and data are available at \url{10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
+All materials and data are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
 
@@
                       # Code output width
-                      tidy=TRUE, tidy.opts = list(width.cutoff = 80),
+                      # tidy=TRUE, tidy.opts = list(width.cutoff = 80),
                       # comment = NA, prompt = TRUE
@@
 
-All analyses were conducted using R statistical software \parencite[v\Sexpr{paste(version$major,version$minor, sep = ".")};][]{rcoreteamLanguageEnvironmentStatistical2021}.
-All materials, data, and analysis code are available at \url{https://github.com/ClaudioZandonella/Attachment} [TDO add doi].
+All analyses were conducted using R statistical software \parencite[Version \Sexpr{paste(version$major,version$minor, sep = ".")};][]{rcoreteamLanguageEnvironmentStatistical2021}.
+All materials, data, and analysis code are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
 Supplemental Material with further details is also available online at \url{https://claudiozandonella.github.io/Attachment/}.
@@
 More information about the sample, descriptive statistics, cluster analysis, and analysis of internalizing problems can be found in the Supplemental Material available online \url{https://claudiozandonella.github.io/Attachment/}.
-All materials and data are available at \url{10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
+All materials and data are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
 

### 2022-09-25 R/Plots.R
update analysis

@@ -480,7 +480,7 @@ plot_post_diff <-  function(post_pred = post_pred_ext, problem = c("Externalizin
 my_pp_check <- function(brm_fit = brm_selected_ext,  problem = c("Externalizing", "Internalizing")){
   problem <- match.arg(problem)
 
-  plot <- brms::pp_check(brm_fit, nsamples = 30)
+  plot <- brms::pp_check(brm_fit, ndraws = 30)
 
   plot +
     theme_bw() +

### 2022-09-25 Documents/Bookdown/01-case-study.Rmd
update bookdown

@@
 
-Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version [ECR-RC, @Brenning2014ThePQ; marciBriefExperiencesClose2019] completed by the children.
+Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version [ECR-RC, @Brenning2014ThePQ; @marciBriefExperiencesClose2019] completed by the children.
 Four main attachment styles have been recognized in the literature according to thee levels of *anxiety* and *avoidance*:
@@
 In Figure~\@ref(fig:plot-scores-mother), Anxiety (“*Anx*”) and Avoidance (“*Av*”) scores are presented according to mother attachment styles.
-The frequencies of mother attachment styles according to gender are reported in Table~\ref{tab:table-cluster-mother}.
+The frequencies of mother attachment styles according to gender are reported in Table~\@ref(tab:table-cluster-mother).
 
@@
 In Figure~\@ref(fig:plot-scores-father), Anxiety (“*Anx*”) and Avoidance (“*Av*”) scores are presented according to father attachment styles.
-The frequencies of father attachment styles according to gender are reported in Table~\ref{tab:table-cluster-father}.
+The frequencies of father attachment styles according to gender are reported in Table~\@ref(tab:table-cluster-father).
 
@@
 
-Overall, internalizing problems are low. Again, this is expected as the sample is not clinical. Internalizing problems according to attachment styles are reported in Table~\ref(tab:table-cluster-ext).
+Overall, internalizing problems are low.
+Again, this is expected as the sample is not clinical.
+Internalizing problems according to attachment styles are reported in Table~\@ref(tab:table-cluster-int).
 

### 2022-09-25 Documents/Bookdown/index.Rmd
update bookdown

--- 2021-11-28 Documents/Bookdown/index.Rmd
@@
 --- 
-title: "Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach"
+title: "Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach"
 subtitle: "Supplemental Material"
@@
 devtools::load_all("../../")
-source("../Utils_report.R")
 
-#----    load drake    ----
+#----    load targets    ----
 
-drake_load_bookdown()
+tar_load_bookdown(store = "../../Analysis/_targets/")
 ```

### 2022-09-25 docs/attachment-bayes-factor.tex
update bookdown

--- 2021-11-28 docs/attachment-bayes-factor.tex
@@
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach},
-  pdfauthor={Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{color}
@@
 \titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
@@
 \bibliographystyle{plainnat}
-
-\title{Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach}
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach},
+  pdfauthor={Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+
+\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach}
 \usepackage{etoolbox}
@@
 \author{\href{https://claudiozandonella.netlify.app/}{Claudio Zandonella Callegher}, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
-\date{2021-11-28}
+\date{2022-09-25}
 
@@
 ## i Loading Attachment
+\end{verbatim}
+
+\begin{verbatim}
+## Tartgets loaded!
 \end{verbatim}
@@
 
-Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version {[}ECR-RC, \citet{Brenning2014ThePQ}; marciBriefExperiencesClose2019{]} completed by the children.
+Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version \citep[ECR-RC,][]{Brenning2014ThePQ, marciBriefExperiencesClose2019} completed by the children.
 Four main attachment styles have been recognized in the literature according to thee levels of \emph{anxiety} and \emph{avoidance}:
@@
 In Figure\textasciitilde\ref{fig:plot-scores-mother}, Anxiety (``\emph{Anx}'') and Avoidance (``\emph{Av}'') scores are presented according to mother attachment styles.
-The frequencies of mother attachment styles according to gender are reported in Table\textasciitilde{}\ref{tab:table-cluster-mother}.
+The frequencies of mother attachment styles according to gender are reported in Table\textasciitilde\ref{tab:table-cluster-mother}.
 
@@
 ## Best BIC values:
-##              EEV,6       EEV,7      EEV,8
-## BIC      -23978.93 -24842.2437 -25039.952
-## BIC diff      0.00   -863.3168  -1061.025
+##              EEV,6       EEV,7       EEV,9
+## BIC      -23978.93 -24842.2954 -24969.9125
+## BIC diff      0.00   -863.3681   -990.9852
 \end{verbatim}
@@
 In Figure\textasciitilde\ref{fig:plot-scores-father}, Anxiety (``\emph{Anx}'') and Avoidance (``\emph{Av}'') scores are presented according to father attachment styles.
-The frequencies of father attachment styles according to gender are reported in Table\textasciitilde{}\ref{tab:table-cluster-father}.
+The frequencies of father attachment styles according to gender are reported in Table\textasciitilde\ref{tab:table-cluster-father}.
 
@@
 ## Best BIC values:
-##              EEV,9       EEV,8      EEV,5
-## BIC      -25351.43 -25790.9130 -25905.197
-## BIC diff      0.00   -439.4807   -553.765
+##              EEV,9       EEV,5       EEV,8
+## BIC      -25351.48 -25905.1973 -25979.1378
+## BIC diff      0.00   -553.7208   -627.6613
 \end{verbatim}
@@
 Again, this is expected as the sample is not clinical.
-Internalizing problems according to attachment styles are reported in Table\textasciitilde{}\ref(tab:table-cluster-ext).
+Internalizing problems according to attachment styles are reported in Table\textasciitilde\ref{tab:table-cluster-int}.
 
@@
 \DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
-\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1720}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1719}
 \DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.162 825  {-}1.902  0.2228}
@@
 \DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2761 0.146 825  {-}1.885  0.2300}
-\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2537 0.167 825  {-}1.522  0.4180}
+\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2537 0.167 825  {-}1.522  0.4179}
 \DocumentationTok{\#\# }
@@
 \NormalTok{performance}\SpecialCharTok{::}\FunctionTok{r2}\NormalTok{(fit\_ext\_zinb)}
-\DocumentationTok{\#\# Warning: mu of 4.2 is too close to zero, estimate of random effect variances may be}
-\DocumentationTok{\#\#   unreliable.}
+\DocumentationTok{\#\# Warning: mu of 4.2 is too close to zero, estimate of random effect variances may}
+\DocumentationTok{\#\#   be unreliable.}
 \DocumentationTok{\#\# \# R2 for Mixed Models}
@@
 \DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2432 0.1034 837  {-}2.353  0.0859}
-\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0247}
-\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0003}
+\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0243}
+\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0004}
 \DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0648 0.0981 837  {-}0.661  0.9107}
-\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0898}
+\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0903}
 \DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2188 0.1276 837  {-}1.714  0.3135}
@@
 \NormalTok{performance}\SpecialCharTok{::}\FunctionTok{r2}\NormalTok{(fit\_ext\_mother)}
-\DocumentationTok{\#\# Warning: mu of 4.2 is too close to zero, estimate of random effect variances may be}
-\DocumentationTok{\#\#   unreliable.}
+\DocumentationTok{\#\# Warning: mu of 4.2 is too close to zero, estimate of random effect variances may}
+\DocumentationTok{\#\#   be unreliable.}
 \DocumentationTok{\#\# \# R2 for Mixed Models}
@@
 \begin{verbatim}
-##                   prior     class                          coef    group resp dpar nlpar bound       source
+##                   prior     class                          coef    group resp dpar nlpar lb ub       source
 ##            normal(0, 3)         b                                                                      user
@@
 ##            normal(0, 3)         b   motherFearful:fatherFearful                                (vectorized)
-##            normal(0, 3)         b                                               zi             (vectorized)
-##            normal(0, 3)         b                       genderM                 zi             (vectorized)
+##                  (flat)         b                                               zi                  default
+##                  (flat)         b                       genderM                 zi             (vectorized)
 ##  student_t(3, 0.7, 2.5) Intercept                                                                   default
 ##          logistic(0, 1) Intercept                                               zi                  default
-##    student_t(3, 0, 2.5)        sd                                                                   default
-##    student_t(3, 0, 2.5)        sd                                               zi                  default
-##    student_t(3, 0, 2.5)        sd                               ID_class                       (vectorized)
-##    student_t(3, 0, 2.5)        sd                     Intercept ID_class                       (vectorized)
-##    student_t(3, 0, 2.5)        sd                               ID_class        zi             (vectorized)
-##    student_t(3, 0, 2.5)        sd                     Intercept ID_class        zi             (vectorized)
-##       gamma(0.01, 0.01)     shape                                                                   default
+##    student_t(3, 0, 2.5)        sd                                                         0         default
+##    student_t(3, 0, 2.5)        sd                                               zi        0         default
+##    student_t(3, 0, 2.5)        sd                               ID_class                  0    (vectorized)
+##    student_t(3, 0, 2.5)        sd                     Intercept ID_class                  0    (vectorized)
+##    student_t(3, 0, 2.5)        sd                               ID_class        zi        0    (vectorized)
+##    student_t(3, 0, 2.5)        sd                     Intercept ID_class        zi        0    (vectorized)
+##       gamma(0.01, 0.01)     shape                                                         0         default
 \end{verbatim}
@@
 ##    Data: data (Number of observations: 847) 
-## Samples: 6 chains, each with iter = 10000; warmup = 2000; thin = 1;
-##          total post-warmup samples = 48000
+##   Draws: 6 chains, each with iter = 10000; warmup = 2000; thin = 1;
+##          total post-warmup draws = 48000
 ## 
@@
 ##                  Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## sd(Intercept)        0.30      0.07     0.17     0.45 1.00    14161    20827
-## sd(zi_Intercept)     1.14      0.29     0.68     1.82 1.00    22361    31673
+## sd(Intercept)        0.30      0.07     0.17     0.45 1.00    14452    20584
+## sd(zi_Intercept)     1.14      0.29     0.68     1.82 1.00    21599    30432
 ## 
@@
 ##                               Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## Intercept                         0.98      0.13     0.72     1.24 1.00    35521    38291
-## zi_Intercept                     -1.33      0.33    -2.09    -0.78 1.00    36797    30278
-## genderM                           0.32      0.08     0.16     0.49 1.00    81905    36734
-## motherAnxious                     0.32      0.19    -0.05     0.70 1.00    39619    37732
-## motherAvoidant                    0.17      0.26    -0.33     0.69 1.00    37098    36353
-## motherFearful                     0.69      0.41    -0.07     1.54 1.00    34182    30539
-## fatherAnxious                     0.22      0.20    -0.16     0.60 1.00    40404    38489
-## fatherAvoidant                   -0.45      0.22    -0.87    -0.02 1.00    40412    38016
-## fatherFearful                     0.11      0.42    -0.69     0.96 1.00    35432    34390
-## motherAnxious:fatherAnxious      -0.39      0.28    -0.94     0.15 1.00    36701    36495
-## motherAvoidant:fatherAnxious     -0.12      0.34    -0.80     0.53 1.00    36329    36398
-## motherFearful:fatherAnxious      -0.43      0.51    -1.46     0.55 1.00    35084    32876
-## motherAnxious:fatherAvoidant      0.33      0.29    -0.25     0.89 1.00    36157    37830
-## motherAvoidant:fatherAvoidant     0.61      0.34    -0.06     1.26 1.00    34169    35603
-## motherFearful:fatherAvoidant      0.30      0.48    -0.68     1.20 1.00    32533    31702
-## motherAnxious:fatherFearful      -0.06      0.48    -1.02     0.86 1.00    34008    34560
-## motherAvoidant:fatherFearful      0.09      0.57    -1.04     1.19 1.00    34795    33933
-## motherFearful:fatherFearful      -0.26      0.60    -1.48     0.86 1.00    30725    30729
-## zi_genderM                       -0.78      0.29    -1.38    -0.23 1.00    70555    35796
+## Intercept                         0.98      0.13     0.72     1.24 1.00    36946    39083
+## zi_Intercept                     -1.33      0.33    -2.08    -0.79 1.00    37409    31478
+## genderM                           0.32      0.08     0.16     0.49 1.00    83483    38460
+## motherAnxious                     0.32      0.19    -0.06     0.69 1.00    40607    39458
+## motherAvoidant                    0.17      0.26    -0.33     0.69 1.00    39406    36276
+## motherFearful                     0.69      0.41    -0.07     1.53 1.00    35752    33258
+## fatherAnxious                     0.22      0.19    -0.16     0.60 1.00    41153    37645
+## fatherAvoidant                   -0.45      0.21    -0.87    -0.03 1.00    43962    38015
+## fatherFearful                     0.11      0.42    -0.68     0.97 1.00    33620    33965
+## motherAnxious:fatherAnxious      -0.39      0.28    -0.93     0.15 1.00    37290    38104
+## motherAvoidant:fatherAnxious     -0.12      0.34    -0.79     0.53 1.00    37877    36168
+## motherFearful:fatherAnxious      -0.43      0.51    -1.45     0.55 1.00    36742    34591
+## motherAnxious:fatherAvoidant      0.33      0.29    -0.24     0.89 1.00    38934    38185
+## motherAvoidant:fatherAvoidant     0.60      0.33    -0.05     1.25 1.00    37462    34839
+## motherFearful:fatherAvoidant      0.30      0.48    -0.67     1.20 1.00    34490    33126
+## motherAnxious:fatherFearful      -0.06      0.48    -1.03     0.87 1.00    33089    34838
+## motherAvoidant:fatherFearful      0.09      0.57    -1.04     1.19 1.00    35141    36840
+## motherFearful:fatherFearful      -0.27      0.59    -1.46     0.86 1.00    29919    31952
+## zi_genderM                       -0.78      0.29    -1.38    -0.24 1.00    68477    37227
 ## 
@@
 ##       Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## shape     1.63      0.24     1.22     2.14 1.00    34643    32767
+## shape     1.64      0.24     1.22     2.14 1.00    34980    35143
 ## 
-## Samples were drawn using sampling(NUTS). For each parameter, Bulk_ESS
+## Draws were sampled using sampling(NUTS). For each parameter, Bulk_ESS
 ## and Tail_ESS are effective sample size measures, and Rhat is the potential
@@
 \midrule
-Null & 2.9e+11 & 0.01 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_null.png}\\
-Monotropy & 2.6e+13 & 0.98 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_monotropy.png}\\
-Hierarchy & 2.7e+11 & 0.01 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_hierarchy.png}\\
-Independence & 3.9e+09 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_independence.png}\\
-Integration & 3.2e+09 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_integration.png}\\
+Null & 2.4e+11 & 0.01 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_null.png}\\
+Monotropy & 2.5e+13 & 0.98 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_monotropy.png}\\
+Hierarchy & 2.9e+11 & 0.01 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_hierarchy.png}\\
+Independence & 4.0e+09 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_independence.png}\\
+Integration & 3.3e+09 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_integration.png}\\
 \bottomrule
@@
 \midrule
-\textbf{Null} & 8.2e+01 & 0.00 & 9.4e+04 & 0.00 & 2.9e+11 & 0.01 & 4.7e+14 & 0.03 & 1.5e+19 & 0.11\\
-\textbf{Monotropy} & 1.2e+05 & 0.67 & 6.3e+07 & 0.90 & 2.6e+13 & 0.98 & 1.6e+16 & 0.97 & 1.2e+20 & 0.89\\
-\textbf{Hierarchy} & 4.9e+04 & 0.28 & 6.1e+06 & 0.09 & 2.7e+11 & 0.01 & 6.7e+13 & 0.00 & 1.2e+17 & 0.00\\
-\textbf{Independence} & 4.4e+03 & 0.02 & 2.6e+05 & 0.00 & 3.9e+09 & 0.00 & 5.8e+11 & 0.00 & 5.1e+14 & 0.00\\
-\textbf{Integration} & 4.6e+03 & 0.03 & 3.3e+05 & 0.00 & 3.2e+09 & 0.00 & 3.3e+11 & 0.00 & 1.5e+14 & 0.00\\
+\textbf{Null} & 8.9e+01 & 0.00 & 9.0e+04 & 0.00 & 2.4e+11 & 0.01 & 5.2e+14 & 0.03 & 1.4e+19 & 0.09\\
+\textbf{Monotropy} & 1.1e+05 & 0.67 & 6.6e+07 & 0.90 & 2.5e+13 & 0.98 & 1.7e+16 & 0.97 & 1.3e+20 & 0.90\\
+\textbf{Hierarchy} & 4.5e+04 & 0.28 & 6.5e+06 & 0.09 & 2.9e+11 & 0.01 & 6.8e+13 & 0.00 & 1.3e+17 & 0.00\\
+\textbf{Independence} & 4.0e+03 & 0.02 & 2.8e+05 & 0.00 & 4.0e+09 & 0.00 & 5.8e+11 & 0.00 & 5.6e+14 & 0.00\\
+\textbf{Integration} & 4.1e+03 & 0.03 & 3.5e+05 & 0.00 & 3.3e+09 & 0.00 & 3.3e+11 & 0.00 & 1.6e+14 & 0.00\\
 \bottomrule
@@
 \begin{verbatim}
-##                   prior     class           coef    group resp dpar nlpar bound       source
+##                   prior     class           coef    group resp dpar nlpar lb ub       source
 ##            normal(0, 3)         b                                                       user
@@
 ##            normal(0, 3)         b  motherFearful                                (vectorized)
-##            normal(0, 3)         b                                zi             (vectorized)
-##            normal(0, 3)         b        genderM                 zi             (vectorized)
+##                  (flat)         b                                zi                  default
+##                  (flat)         b        genderM                 zi             (vectorized)
 ##  student_t(3, 0.7, 2.5) Intercept                                                    default
 ##          logistic(0, 1) Intercept                                zi                  default
-##    student_t(3, 0, 2.5)        sd                                                    default
-##    student_t(3, 0, 2.5)        sd                                zi                  default
-##    student_t(3, 0, 2.5)        sd                ID_class                       (vectorized)
-##    student_t(3, 0, 2.5)        sd      Intercept ID_class                       (vectorized)
-##    student_t(3, 0, 2.5)        sd                ID_class        zi             (vectorized)
-##    student_t(3, 0, 2.5)        sd      Intercept ID_class        zi             (vectorized)
-##       gamma(0.01, 0.01)     shape                                                    default
+##    student_t(3, 0, 2.5)        sd                                          0         default
+##    student_t(3, 0, 2.5)        sd                                zi        0         default
+##    student_t(3, 0, 2.5)        sd                ID_class                  0    (vectorized)
+##    student_t(3, 0, 2.5)        sd      Intercept ID_class                  0    (vectorized)
+##    student_t(3, 0, 2.5)        sd                ID_class        zi        0    (vectorized)
+##    student_t(3, 0, 2.5)        sd      Intercept ID_class        zi        0    (vectorized)
+##       gamma(0.01, 0.01)     shape                                          0         default
 \end{verbatim}
@@
 ##    Data: data (Number of observations: 847) 
-## Samples: 6 chains, each with iter = 6000; warmup = 2000; thin = 1;
-##          total post-warmup samples = 24000
+##   Draws: 6 chains, each with iter = 6000; warmup = 2000; thin = 1;
+##          total post-warmup draws = 24000
 ## 
@@
 ##                  Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## sd(Intercept)        0.29      0.07     0.17     0.43 1.00     7372    10149
-## sd(zi_Intercept)     1.10      0.27     0.65     1.74 1.00     9371    12428
+## sd(Intercept)        0.29      0.07     0.17     0.43 1.00     7364     9731
+## sd(zi_Intercept)     1.10      0.27     0.66     1.72 1.00     9796    13166
 ## 
@@
 ##                Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## Intercept          0.96      0.11     0.74     1.18 1.00    14818    16592
-## zi_Intercept      -1.27      0.31    -1.97    -0.75 1.00    14384    12961
-## genderM            0.34      0.08     0.18     0.50 1.00    30197    18984
-## motherAnxious      0.25      0.10     0.05     0.46 1.00    21564    18963
-## motherAvoidant     0.32      0.11     0.10     0.53 1.00    21623    19168
-## motherFearful      0.54      0.14     0.28     0.81 1.00    22199    18755
-## zi_genderM        -0.74      0.27    -1.30    -0.22 1.00    27915    17381
+## Intercept          0.96      0.11     0.74     1.17 1.00    13837    15737
+## zi_Intercept      -1.27      0.31    -1.95    -0.74 1.00    14172    13282
+## genderM            0.34      0.08     0.18     0.50 1.00    31044    18453
+## motherAnxious      0.25      0.10     0.05     0.46 1.00    21756    19681
+## motherAvoidant     0.32      0.11     0.10     0.53 1.00    22846    19205
+## motherFearful      0.54      0.13     0.29     0.81 1.00    22427    19423
+## zi_genderM        -0.74      0.27    -1.29    -0.22 1.00    28744    17354
 ## 
@@
 ##       Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## shape     1.70      0.25     1.27     2.23 1.00    15644    16568
+## shape     1.71      0.25     1.27     2.24 1.00    15020    16007
 ## 
-## Samples were drawn using sampling(NUTS). For each parameter, Bulk_ESS
+## Draws were sampled using sampling(NUTS). For each parameter, Bulk_ESS
 ## and Tail_ESS are effective sample size measures, and Rhat is the potential
@@
 \DocumentationTok{\#\#     Estimate  Est.Error       Q2.5     Q97.5}
-\DocumentationTok{\#\# R2 0.1482686 0.02972484 0.09435914 0.2106949}
-\end{Highlighting}
-\end{Shaded}
+\DocumentationTok{\#\# R2 0.1484309 0.02931432 0.09501877 0.2107168}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Warning: Argument 'nsamples' is deprecated. Please use argument 'ndraws' instead.
+\end{verbatim}
 
@@
 \DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
-\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2150 0.117 825  {-}1.836  0.2508}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2150 0.117 825  {-}1.836  0.2510}
 \DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.0653 0.136 825  {-}0.481  0.9622}
-\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.2985 0.166 825  {-}1.793  0.2707}
+\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.2985 0.166 825  {-}1.793  0.2708}
 \DocumentationTok{\#\#  Anxious {-} Avoidant   0.1496 0.112 825   1.336  0.5321}
@@
 \DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
-\DocumentationTok{\#\#  Secure {-} Anxious     {-}0.285 0.0892 837  {-}3.197  0.0075}
+\DocumentationTok{\#\#  Secure {-} Anxious     {-}0.285 0.0892 837  {-}3.197  0.0079}
 \DocumentationTok{\#\#  Secure {-} Avoidant    {-}0.120 0.0946 837  {-}1.266  0.5809}
@@
 \DocumentationTok{\#\#  Anxious {-} Avoidant    0.165 0.0869 837   1.903  0.2243}
-\DocumentationTok{\#\#  Anxious {-} Fearful    {-}0.183 0.1096 837  {-}1.673  0.3347}
-\DocumentationTok{\#\#  Avoidant {-} Fearful   {-}0.349 0.1167 837  {-}2.989  0.0148}
+\DocumentationTok{\#\#  Anxious {-} Fearful    {-}0.183 0.1096 837  {-}1.673  0.3346}
+\DocumentationTok{\#\#  Avoidant {-} Fearful   {-}0.349 0.1167 837  {-}2.989  0.0149}
 \DocumentationTok{\#\# }
@@
 ##                  Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## sd(Intercept)        0.44      0.08     0.29     0.62 1.00     9467    20478
-## sd(zi_Intercept)     2.24      0.56     1.37     3.52 1.00    22914    28211
+## sd(Intercept)        0.44      0.08     0.29     0.62 1.00     9576    21295
+## sd(zi_Intercept)     2.24      0.55     1.38     3.53 1.00    23180    29061
 ## 
@@
 ##                               Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## Intercept                         0.83      0.13     0.57     1.07 1.00    21805    30756
-## zi_Intercept                     -2.94      0.70    -4.58    -1.84 1.00    23476    24791
-## genderM                           0.08      0.07    -0.06     0.22 1.00    69575    38126
-## motherAnxious                     0.46      0.17     0.13     0.79 1.00    33349    37383
-## motherAvoidant                   -0.08      0.25    -0.56     0.41 1.00    28640    33103
-## motherFearful                     0.63      0.40    -0.14     1.45 1.00    28081    31710
-## fatherAnxious                     0.07      0.17    -0.27     0.40 1.00    36862    37511
-## fatherAvoidant                    0.08      0.18    -0.26     0.43 1.00    36867    35693
-## fatherFearful                     0.36      0.34    -0.28     1.04 1.00    30611    33358
-## motherAnxious:fatherAnxious      -0.24      0.24    -0.70     0.22 1.00    31718    36313
-## motherAvoidant:fatherAnxious      0.24      0.31    -0.38     0.85 1.00    28308    33805
-## motherFearful:fatherAnxious      -0.75      0.50    -1.75     0.22 1.00    30436    34570
-## motherAnxious:fatherAvoidant     -0.23      0.24    -0.70     0.24 1.00    32215    36746
-## motherAvoidant:fatherAvoidant     0.11      0.30    -0.49     0.71 1.00    27005    33164
-## motherFearful:fatherAvoidant     -0.19      0.45    -1.09     0.69 1.00    27741    32785
-## motherAnxious:fatherFearful      -0.47      0.40    -1.25     0.31 1.00    27639    33504
-## motherAvoidant:fatherFearful      0.28      0.48    -0.67     1.21 1.00    26850    35151
-## motherFearful:fatherFearful      -0.35      0.53    -1.41     0.68 1.00    24657    31248
-## zi_genderM                       -0.30      0.40    -1.10     0.48 1.00    49145    34266
+## Intercept                         0.83      0.13     0.57     1.08 1.00    20193    31209
+## zi_Intercept                     -2.93      0.69    -4.54    -1.84 1.00    23885    24649
+## genderM                           0.07      0.07    -0.07     0.22 1.00    69024    39479
+## motherAnxious                     0.46      0.17     0.14     0.78 1.00    28713    34928
+## motherAvoidant                   -0.08      0.25    -0.56     0.41 1.00    27088    33529
+## motherFearful                     0.63      0.40    -0.13     1.44 1.00    25396    29183
+## fatherAnxious                     0.07      0.17    -0.26     0.40 1.00    32754    37880
+## fatherAvoidant                    0.08      0.18    -0.26     0.43 1.00    33099    33066
+## fatherFearful                     0.36      0.34    -0.29     1.04 1.00    27438    31863
+## motherAnxious:fatherAnxious      -0.24      0.23    -0.70     0.22 1.00    27476    35909
+## motherAvoidant:fatherAnxious      0.24      0.31    -0.37     0.84 1.00    26127    33090
+## motherFearful:fatherAnxious      -0.75      0.50    -1.75     0.22 1.00    27653    33582
+## motherAnxious:fatherAvoidant     -0.23      0.24    -0.70     0.23 1.00    28023    34471
+## motherAvoidant:fatherAvoidant     0.11      0.30    -0.48     0.70 1.00    24526    32104
+## motherFearful:fatherAvoidant     -0.18      0.45    -1.10     0.68 1.00    25043    31079
+## motherAnxious:fatherFearful      -0.46      0.40    -1.25     0.31 1.00    26068    32120
+## motherAvoidant:fatherFearful      0.29      0.48    -0.66     1.22 1.00    26407    35222
+## motherFearful:fatherFearful      -0.35      0.53    -1.41     0.67 1.00    22713    30152
+## zi_genderM                       -0.31      0.41    -1.12     0.49 1.00    49631    32918
 ## 
@@
 ##       Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## shape     2.46      0.32     1.90     3.17 1.00    38857    36697
+## shape     2.47      0.32     1.90     3.17 1.00    36269    34308
 ## 
-## Samples were drawn using sampling(NUTS). For each parameter, Bulk_ESS
+## Draws were sampled using sampling(NUTS). For each parameter, Bulk_ESS
 ## and Tail_ESS are effective sample size measures, and Rhat is the potential
@@
 \midrule
-Null & 3.5e+11 & 0.03 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_null.png}\\
-Monotropy & 9.2e+12 & 0.92 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_monotropy.png}\\
-Hierarchy & 4.7e+11 & 0.05 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_hierarchy.png}\\
+Null & 3.4e+11 & 0.04 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_null.png}\\
+Monotropy & 8.8e+12 & 0.91 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_monotropy.png}\\
+Hierarchy & 4.8e+11 & 0.05 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_hierarchy.png}\\
 Independence & 1.1e+10 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_independence.png}\\
-Integration & 1.7e+10 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_integration.png}\\
+Integration & 1.8e+10 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_int_integration.png}\\
 \bottomrule
@@
 \midrule
-\textbf{Null} & 3.8e+01 & 0.00 & 8.9e+04 & 0.00 & 3.5e+11 & 0.03 & 5.5e+14 & 0.09 & 1.8e+19 & 0.27\\
-\textbf{Monotropy} & 2.3e+04 & 0.29 & 1.8e+07 & 0.63 & 9.2e+12 & 0.92 & 5.4e+15 & 0.89 & 4.9e+19 & 0.72\\
-\textbf{Hierarchy} & 4.0e+04 & 0.51 & 8.8e+06 & 0.30 & 4.7e+11 & 0.05 & 1.0e+14 & 0.02 & 2.2e+17 & 0.00\\
-\textbf{Independence} & 5.7e+03 & 0.07 & 6.4e+05 & 0.02 & 1.1e+10 & 0.00 & 1.5e+12 & 0.00 & 1.6e+15 & 0.00\\
-\textbf{Integration} & 9.8e+03 & 0.13 & 1.4e+06 & 0.05 & 1.7e+10 & 0.00 & 1.5e+12 & 0.00 & 8.4e+14 & 0.00\\
+\textbf{Null} & 4.4e+01 & 0.00 & 8.4e+04 & 0.00 & 3.4e+11 & 0.04 & 6.8e+14 & 0.09 & 1.9e+19 & 0.27\\
+\textbf{Monotropy} & 2.2e+04 & 0.28 & 1.9e+07 & 0.64 & 8.8e+12 & 0.91 & 6.5e+15 & 0.89 & 5.0e+19 & 0.72\\
+\textbf{Hierarchy} & 4.0e+04 & 0.52 & 9.0e+06 & 0.29 & 4.8e+11 & 0.05 & 1.2e+14 & 0.02 & 2.2e+17 & 0.00\\
+\textbf{Independence} & 5.8e+03 & 0.07 & 6.4e+05 & 0.02 & 1.1e+10 & 0.00 & 1.6e+12 & 0.00 & 1.6e+15 & 0.00\\
+\textbf{Integration} & 1.0e+04 & 0.13 & 1.5e+06 & 0.05 & 1.8e+10 & 0.00 & 1.6e+12 & 0.00 & 8.2e+14 & 0.00\\
 \bottomrule
@@
 ##                  Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## sd(Intercept)        0.43      0.08     0.29     0.61 1.00     5203    10756
-## sd(zi_Intercept)     2.18      0.53     1.35     3.43 1.00    11849    14075
+## sd(Intercept)        0.43      0.08     0.29     0.61 1.00     4981    11555
+## sd(zi_Intercept)     2.17      0.53     1.34     3.40 1.00    12787    16150
 ## 
@@
 ##                Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## Intercept          0.88      0.11     0.66     1.10 1.00     9744    13174
-## zi_Intercept      -2.82      0.65    -4.33    -1.78 1.00    11781    12633
-## genderM            0.07      0.07    -0.07     0.21 1.00    36050    19093
-## motherAnxious      0.29      0.09     0.11     0.46 1.00    26032    19760
-## motherAvoidant     0.12      0.10    -0.07     0.31 1.00    29724    20101
-## motherFearful      0.48      0.12     0.25     0.71 1.00    26736    20112
-## zi_genderM        -0.29      0.39    -1.06     0.46 1.00    28148    18297
+## Intercept          0.89      0.11     0.66     1.10 1.00    10532    14506
+## zi_Intercept      -2.81      0.65    -4.31    -1.79 1.00    14230    13767
+## genderM            0.07      0.07    -0.07     0.21 1.00    38142    19994
+## motherAnxious      0.29      0.09     0.11     0.46 1.00    27686    19778
+## motherAvoidant     0.12      0.10    -0.07     0.31 1.00    30305    18855
+## motherFearful      0.48      0.12     0.25     0.71 1.00    28322    20529
+## zi_genderM        -0.29      0.39    -1.07     0.48 1.00    27658    17214
 ## 
@@
 ##       Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
-## shape     2.53      0.33     1.95     3.25 1.00    21936    18166
+## shape     2.53      0.33     1.95     3.26 1.00    21194    18858
 ## 
-## Samples were drawn using sampling(NUTS). For each parameter, Bulk_ESS
+## Draws were sampled using sampling(NUTS). For each parameter, Bulk_ESS
 ## and Tail_ESS are effective sample size measures, and Rhat is the potential
@@
 \DocumentationTok{\#\#     Estimate  Est.Error      Q2.5     Q97.5}
-\DocumentationTok{\#\# R2 0.2224337 0.02977471 0.1651088 0.281678}
-\end{Highlighting}
-\end{Shaded}
+\DocumentationTok{\#\# R2 0.2224078 0.02975503 0.1660707 0.2825445}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Warning: Argument 'nsamples' is deprecated. Please use argument 'ndraws' instead.
+\end{verbatim}
 

### 2022-09-25 Documents/Paper/paper.Rnw
add affiliation
update paper

@@
 \author{Claudio Zandonella Callegher$^1$, Tatiana Marci$^1$, Pietro De Carli$^2$, Gianmarco Altoè$^1$}
-\affiliation{$^1$Department of Developmental Psychology and Socialization, University of Padova\\
-$^2$UNIMI TODO }
+\affiliation{$^1$Department of Developmental Psychology and Socialization - University of Padova\\
+$^2$Department of Psychology - University of Milano-Bicocca}
 
@@
 
-<<settings, echo=FALSE, message=FALSE>>=
+<<settings, echo=FALSE, message=FALSE, include=FALSE>>=
 library(kableExtra)
@@
 
-# Chunk theme
-thm=knit_theme$get("bclear")
+# # Chunk theme
+thm=knitr::knit_theme$get("bclear")
 knitr::knit_theme$set(thm)
-knitr::opts_chunk$set(background = c(.98, .98, 1))
+knitr::opts_chunk$set(background = "#FAFAFF")
 
@@
 devtools::load_all("../../")
-source("../Utils_report.R")
 
@@
 
-drake_load_paper()
+tar_load_paper(store = "../../Analysis/_targets/")
 @

### 2022-09-25 Documents/Paper/paper.Rnw
fix paper cit

@@
 On the other hand, articles offering a general introduction to the Bayes factor do not provide enough details to allow readers to autonomously apply this method to their problems; instead, they usually rely on ad hoc solutions implemented in some statistical software.
-For example, \textcite{hoijtinkTutorialTestingHypotheses2019a} offered an excellent introduction to the Bayes factor for the evaluation of informative hypotheses using the R package \texttt{bain}.
+For example, \textcite{hoijtinkTutorialTestingHypotheses2019} offered an excellent introduction to the Bayes factor for the evaluation of informative hypotheses using the R package \texttt{bain}.
 However, it is limited to the context of analysis-of-variance models, and it is not possible to extend its use to other cases.

### 2022-09-25 README.Rmd
coorrige read me
fix paper cit

@@
 
-# Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach
+# Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach
 
@@
 
-Moreover, the analysis workflow is managed using `drake` (see Section below) and include other (*non-standard*) folders to organize the scripts for the analysis and for the produced outputs (i.e., paper and supplemental material).
+Moreover, the analysis workflow is managed using `targets` (see Section below) and include other (*non-standard*) folders to organize the scripts for the analysis and for the produced outputs (i.e., paper and supplemental material).
 
@@
 
-- `Analysis/` - includes the file `Analysis_Drake.R` used to run the analysis workflow using `drake`
+- `Analysis/`that includes the files
+    - `Targets-workflow.R` the workflow of the analysis 
+    - `Targets-analysis.R` script to run the analysis with `targets`
 - `Data/` - includes the data used in the analyses
@@
 - `R/` - includes all the `.R` scripts with the functions used in the analyses
+  - `Targets-utils.R` functions used to load results of the analysis
 - `docs/` - includes `bookdown` outputs used to build the GitHub Pages site
@@
 
-To guarantee the reproducibility of the results, the R-package`drake` is used to manage the analysis workflow and to enhance the readability and transparency of the analysis.
-To know more about `drake` consider the [official Git-hub page](https://github.com/ropensci/drake) or the [user manual](https://books.ropensci.org/drake/).
-Summarizing, using `drake` the user defines the plan of the analysis where each step in the analysis is defined through functions.
-Functions can be appropriately defined to obtain desired targets (i.e., R-output with results of interests) and they are declared in another script.
-Subsequently, `drake` manages the whole analysis recognizing the dependency structure of the different targets.
-When any change is made to the code `drake` evaluates the analysis and updates the results.
-Following the *functional programming paradigm* (i.e., defining functions for each step of the analysis) allows us to avoid "*coping and paste*" in the code, it makes debugging easier, and it facilitates the reading of the code.
+To guarantee the reproducibility of the results, the R-package`targets` is used to manage the analysis workflow and to enhance the readability and transparency of the analysis.
+To know more about `targets` consider the [official Git-hub page](https://github.com/ropensci/targets) or the [user manual](https://books.ropensci.org/targets/).
+Summarizing, using `targets` the user defines the plan of the analysis where each step in the analysis is defined through functions.
+Functions can be appropriately defined to obtain desired targets (i.e., R-output with results of interests) and they are declared in the file `Targets-workflow.R`.
+Subsequently, `targets` manages the whole analysis recognizing the dependency structure of the different targets.
+When any change is made to the code `targets` evaluates the analysis and updates the results.
+Following the *functional programming paradigm* (i.e., defining functions for each step of the analysis) allows us to avoid "*coping and paste*" in the code, makes debugging easier, and facilitates the reading of the code.
 
 Moreover, the R-package `renv` is used to manage the dependencies of the R-packages used in the analysis.
-The `renv` package allows the creation of an isolated, portable, and reproducible environment where the analyses are run.
+The `renv` package allows to create an isolated, portable, and reproducible environment where the analyses are run.
 To know more about `renv` consider the [official documentation](https://rstudio.github.io/renv/articles/renv.html).
@@
 1.
-Now the required package will be loaded.
-Restart the R session (`command`/`ctrl` + `shift` + `f10`) so `devtools::load_all()` is automatically run (according to `.Rprofile`) to load all functions used in the analysis defined in the `R/` folder.
+Now the required packages are installed.
+Restart the R session (`command`/`ctrl` + `shift` + `f10`) so `devtools::load_all()` is automatically run to load all functions used in the analysis defined in the `R/` folder and required packages are loaded (according to `.Rprofile`).
 
-    > Note that also `source("Documents/Utils_report.R")` is automatically run to load report utility functions (functions to load analysis results and to compile the bookdown).
+    > Note that also `source("Analysis/Utils_targets.R")` is automatically run to load `targets` utilities functions (functions to load analysis results).
+You can also use the shortcut ` Ctrl/Cmd + Shift + L` to run `devtools::load_all()`
 
 1.
-Open `Analysis/Analysis_Drake.R` and run each line (one by one) to run the analysis using drake.
-First, the analysis environment is set together with the analysis plan (available at `R/Plan.R`).
-Next, the analysis targets are computed (have a coffee, it takes a long time).
+Open `Analysis/Analysis_targets.R` and run each line (one by one) to run the analysis using `targets`.
+First, the analysis plan  is checked (available at `Analysis/Targets-workflow.R`).
+Next, the analysis targets are computed.
 Finally, the analysis results are loaded and briefly presented.
 
-    > Note that you can access the analysis targets using the functions `drake::loadd(<name_target>)`, or load all the results with `drake_load_all()`.
-
-    > It could happen that sometimes the session stays idle when fitting `brms` models without throwing errors.
-In this case, it is necessary to force restarting the R session and rerun the analysis.
-An error warning message will appear: `Error: drake's cache is locked`.
-Just follow the instructions provided by drake to force unlock of the cache  `drake::drake_cache("...")$unlock()`.
+    > Note that you can access the analysis targets using the functions `targets::tar_load(<name_target>)`, or load all the results with `tar_load_all()`.
 
@@
 Run again to obtain the actual output.
+
 1. To compile the Supplemental Material, run `make_my_book()`. The resulting output is saved in the `docs/` folder.

### 2022-10-09 Documents/Paper/paper.Rnw
revision foor resubmission

@@
 This paper provides a detailed introduction to the Bayes factor with encompassing prior.
-First, all steps and elements involved in the formalization of  informative hypotheses and the computation of the Bayes factor with encompassing prior are described.
-Next, we apply this method to a real case scenario, considering the attachment theory.
+First, all steps and elements involved in the formalization of  informative hypotheses and the computation of the Bayes factor using the encompassing prior approach are described.
+Next, we apply this method to a real-case scenario, considering the attachment theory.
 Specifically, we analyzed the relative influence of maternal and paternal attachment on children's social-emotional development by comparing the various theoretical perspectives debated in the literature.
 
-\vspace{2em}
-\begin{center}
-\textbf{Translational Abstract}
-\end{center}
-\vspace{.5em}
-
-The evaluation of hypotheses is one of the main goals of empirical research.
+% \vspace{2em}
+% \begin{center}
+% \textbf{Translational Abstract}
+% \end{center}
+% \vspace{.5em}
+%
+% The evaluation of hypotheses is one of the main goals of empirical research.
 In fact, when conducting a study, researchers usually want to evaluate the plausibility of specific hypotheses according to the collected data.
@@
 
-Model comparison is a different approach that allows researchers to compare multiple hypotheses and identify the most supported by the data \parencite{mcelreathStatisticalRethinkingBayesian2020}.
+Model comparison is a different approach that allows researchers to compare multiple hypotheses and identify the one most supported by the data \parencite{mcelreathStatisticalRethinkingBayesian2020}.
 Researchers first formalize hypotheses as statistical models according to their expectations or theoretical perspectives.
@@
 Model comparison has several advantages; in particular, it allows researchers to directly compute each model's relative plausibility given the data and the set of models considered.
-However, model comparison using information criteria is not appropriate to evaluate hypotheses that include complex parameter constraints reflecting researchers' expectations.
-In fact, information criteria evaluate models' complexity according to the number of parameters, but they do not take into account possible order constraints on the parameters.
+However, model comparison using traditional information criteria (i.e., AIC and BIC) is not appropriate to evaluate hypotheses that include complex parameter constraints reflecting researchers' expectations.
+In fact, traditional information criteria penalize models' complexity according to the number of parameters, but they do not take into account possible order constraints on the parameters.
+Modifications of the AIC have been proposed to account for parameters order restrictions, leading to the order-restricted information criterion \parencite[ORIC;][]{anrakuInformationCriterionParameters1999} and its recent generalization into the so-called generalized order-restricted information criterion approximation \parencite[GORICA;][]{altinisikEvaluationInequalityConstrained2021, kuiperAkaiketypeInformationCriterion2011, kuiperGeneralizationOrderrestrictedInformation2012}.
+The GORICA allows to evaluate (in)equality constrained hypotheses under a very broad range of statistical models \parencite{altinisikEvaluationInequalityConstrained2021, kuiperAICtypeTheoryBasedModel2022}, including generalized linear models (GLMs), generalized linear mixed models (GLMMs), and structural equation models (SEMs).
+Consider also \textcite{mulderBICExtensionsOrderconstrained2022} for an extension of the BIC for evaluating order-constrained models.
 
@@
 In particular, it allows us to compare hypotheses obtaining a relative index of evidence, like the information criteria, but it also allows us to easily compare complex research hypotheses.
-In fact, researchers can formalize so-called \textit{“informative hypotheses”}, hypotheses containing information about the ordering of the model parameters,  according to their expectations or theoretical perspectives, using equality and inequality constraints \parencite{vandeschootIntroductionBayesianModel2011}.
+In fact, researchers can formalize the so-called \textit{“informative hypotheses”}, hypotheses containing information about the ordering of the model parameters,  according to their expectations or theoretical perspectives, using equality and inequality constraints \parencite{vandeschootIntroductionBayesianModel2011}.
 Researchers can then compare these hypotheses against each other, using the Bayes factor.
@@
 In the literature, a particular approach allowing researchers to easily compute the Bayes factor with complex informative hypotheses has received increasing attention: \textit{“the Bayes factor with encompassing prior”}.
-\textcite{vandeschootIntroductionBayesianModel2011} presented a general introduction to informative hypothesis testing using the Bayes factor with the encompassing prior approach whereas \textcite{hoijtinkInformativeHypothesesTheory2012} offered a more detailed description of this method's development.
-In other studies, however, researchers considered the application of this approach with specific statistical models, such as mixed-effect models \parencite{katoBayesianApproachInequality2006}, evaluation of correlation coefficients \parencite{mulderBayesFactorsTesting2016}, and multinomial models \parencite{heckMultinomialModelsLinear2019}.
+\textcite{vandeschootIntroductionBayesianModel2011} presented a general introduction to informative hypothesis testing using the Bayes factor with the encompassing prior approach whereas \textcite{hoijtinkInformativeHypothesesTheory2012, klugkistBayesianModelSelection2005, klugkistBayesFactorInequality2007} offered a more detailed description of this method.
+In other studies, researchers considered the application of this approach with specific statistical models, such as analysis of variance models \parencite{klugkistInequalityConstrainedAnalysis2005a}, mixed-effect models \parencite{katoBayesianApproachInequality2006}, evaluation of correlation coefficients \parencite{mulderBayesFactorsTesting2016}, and multinomial models \parencite{heckMultinomialModelsLinear2019}.
 In addition, \textcite{guBayesianEvaluationInequality2014} proposed a general approximate procedure to evaluate inequality constraints in a wide range of statistical models.
@@
 
-Only recently, \textcite{guApproximatedAdjustedFractional2018} introduced an approximate procedure to evaluate equality and inequality constraints, using the Bayes factor with the encompassing prior approach in a wide range of statistical models (i.e., generalized linear mixed models and structural equation models).
+Only recently, \textcite{guApproximatedAdjustedFractional2018} introduced an approximate procedure to evaluate equality and inequality constraints, using the Bayes factor with the encompassing prior approach in a wide range of statistical models (i.e., GLMs, GLMMs, and SEMs).
 Subsequently, \textcite{mulderBayesFactorTesting2019} extended this approach to generalized multivariate probit models, and, finally, \textcite{mulderSimpleBayesianTesting2019} proposed an accurate procedure (i.e., not based on an approximation) that allows for testing of informative hypotheses with equality and inequality constraints in linear regression models.
 
-The development and implementation of this approach are of particular interest because although it has limits, it allows researchers to directly evaluate their expectations and hypotheses.
+The development and implementation of these methods are of particular interest because although they have some limits, they allow researchers to directly evaluate their expectations and hypotheses.
 The available literature, however, is rather technical.
-These articles' complexity makes it difficult for researchers not familiar with this approach to clearly understand all the steps involved.
+The complexity of these articles makes it difficult for researchers not familiar with this approach to clearly understand all the steps involved.
 On the other hand, articles offering a general introduction to the Bayes factor do not provide enough details to allow readers to autonomously apply this method to their problems; instead, they usually rely on ad hoc solutions implemented in some statistical software.
-For example, \textcite{hoijtinkTutorialTestingHypotheses2019} offered an excellent introduction to the Bayes factor for the evaluation of informative hypotheses using the R package \texttt{bain}.
-However, it is limited to the context of analysis-of-variance models, and it is not possible to extend its use to other cases.
-
-The aim of this paper, therefore, is to offer a clear and detailed description of the Bayes factor with the encompassing prior approach to allow other researchers to apply this approach in their studies.
+For example, \textcite{hoijtinkTutorialTestingHypotheses2019} offered an excellent introduction to the Bayes factor for the testing hypotheses discussing all the main aspects.
+However, the description of the evaluation of competing informative hypotheses is limited and no specific details are provided regarding the adopted encompassing prior approach.
+Moreover, using ad-hoc solutions that automate the analysis, such as the functions available in the R packages \texttt{bain} \parencite{guBainBayesFactors2021} and \texttt{BFpack} \parencite{mulderBFpackFlexibleBayes2021}, prevent the users from fully understanding all the steps and limits entailed in this approach.
+
+The aim of this paper, therefore, is to offer a clear and detailed description of the Bayes factor with the encompassing prior approach to allow other researchers to consciously apply this approach in their studies.
 In particular, we refer to the approximated method \textcite{guApproximatedAdjustedFractional2018} proposed, as it applies to a wider range of conditions than the more accurate approach \textcite{mulderSimpleBayesianTesting2019} introduced.
 In particular, researchers can use the proposed method in the case of generalized linear mixed models and structural equation models, two very general families of statistical models.
-Moreover, by providing an exhaustive description of all of this approach's steps, researchers do not have to rely on already available solutions; instead, they can implement this approach according to their specific needs.
+Moreover, by providing an exhaustive description of all of the steps of this approach, researchers do not have to rely on already available solutions; instead, they can implement this approach according to their specific needs, aware of its strengths and limits.
 The paper is organized as follows.
@@
 In this section, first, we describe how to formulate informative hypotheses.
-We then introduce the Bayes factor, considering the encompassing prior approach based on the approximated method \textcite{guApproximatedAdjustedFractional2018} proposed.
+We then introduce the Bayes factor, considering the encompassing prior approach based on the approximated method proposed by \textcite{guApproximatedAdjustedFractional2018}.
 
@@
 The first term is the ratio between the conditional posterior probability and the conditional prior probability that the inequality constraints hold under the unconstrained model, $H_u$, given the equality constraints.
-The second term is the ratio between marginal posterior density and the marginal prior density of the equality constraints under $H_u$ \parencite[the well-known Savage–Dickey density ratio; ][]{dickeyWeightedLikelihoodRatio1971, wetzelsEncompassingPriorGeneralization2010}.
+The second term is the ratio between marginal posterior density and the marginal prior density of the equality constraints under $H_u$ \parencite[the well-known Savage–Dickey density ratio; Equation (6) can be seen as an extension of the Savage-Dickey method, where the density ratio of the equality constraints is multiplied by the probability ratio of the posterior and prior.][]{dickeyWeightedLikelihoodRatio1971, wetzelsEncompassingPriorGeneralization2010}.
 In particular, the four elements can be interpreted as:
@@
 \end{itemize}
+
 Summarizing at the denominators, we have measures of the \textbf{complexity} of the inequality and equality constraints of the informative hypothesis $H_i$; at the numerators, instead, we have measures of the \textbf{fit} of the data to the inequality and equality constraints of the informative hypothesis $H_i$.
+Where the \textit{fit} of an hypothesis indicates its ability to provide a good description of data at hand and the \textit{complexity} of an hypothesis refers to its level of specificity and parsimony (i.e., simpler hypothesis are specific and specific and parsimonious).
 Therefore, if the hypothesis $H_i$, although applying constraints to the parametric space (less complexity), can still provide an accurate description of the data, the Bayes factor will favor $H_i$.
@@
 \end{equation}
+
+Note that, prior specification is relevant only for the parameters of interest (i.e., the parameters involved in the constraints).
+Nuisance parameters (i.e., the parameters not involved in the constraints) are integrated out in the Bayes factor.
+Thus, the results will be insensitive to the actual choice of the prior for the nuisance parameters as long as it is vague enough.
 
@@
 For example, $F_{Av}$ represents children with avoidant attachment toward their fathers.
+Moreover, $*$ subscript is used to indicate any attachment style and a set of subscripts is used to indicate “\textit{one among}”.
+For example, $F_{*}$ indicates children with any type of attachment toward their fathers and $F_{Ax;Av}$ represents children with anxious or avoidant attachment toward their fathers.
 
@@
 Thus, for example, we use $M_SF_{Ax}$ to indicate children with secure attachment toward their mothers and anxious attachment toward their fathers.
-Moreover, $*$ subscript is used to indicate any attachment style and a set of subscripts is used to indicate “\textit{one among}”.
-For example, $M_SF_{Ax;Av}$ represents children with secure attachment toward their mothers and anxious or avoidant attachment toward their fathers.
 
@@
 
-To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centered on the constraint focal point.
-On the contrary, equality constraints are highly affected by the prior definition.
+To interpret these patterns, remember that the bayes factor is insensitive to the prior distribution specification for the parameters with order constraints as long as the distribution is symmetric and centered on the constraint focal point.
+On the contrary, in the case of equality constraints, the bayes factor is highly affected by the prior definition.
 As the prior gets more diffuse, the density value at zero decreases as well and, even for posterior distributions centered far from zero, the densities ratio at zero will favor the posterior.

### 2022-10-15 R/Bayes_factor.R
remove all drake calls

@@ -21,7 +21,7 @@
 #' @return An object of class "brmsfit" with added WAIC and LOO values
 #'
 #' @examples
-#' drake::loadd(data_cluster)
+#' targets::tar_load(data_cluster)
 #' get_encompassing_model(data = data_cluster,
 #'                        y = "internalizing_sum",
 #'                        prior_par = "normal(0, 3)")
@@ -55,7 +55,7 @@ get_encompassing_model <- function(data, y,  prior_par){
 #' @return character sting
 #'
 #' @examples
-#' drake::loadd(encompassing_model_int)
+#' targets::tar_load(encompassing_model_int)
 #' get_par_names(encompassing_model = encompassing_model_int)
 #'
 
@@ -83,7 +83,7 @@ get_par_names<- function(encompassing_model){
 #' @return numeric value
 #'
 #' @examples
-#' drake::loadd(encompassing_model_int)
+#' targets::tar_load(encompassing_model_int)
 #' get_prior_sd(encompassing_model = encompassing_model_int)
 #'
 
@@ -141,7 +141,7 @@ get_model_matrix <- function(){
 #'   M_Av_F_Sec]").
 #'
 #' @examples
-#' drake::loadd(encompassing_model_int)
+#' targets::tar_load(encompassing_model_int)
 #' par_names <- get_par_names(encompassing_model = encompassing_model_int)
 #' get_hyp_rownames(hypothesis = "monotropy", par_names = par_names)
 #'
@@ -248,7 +248,7 @@ get_hyp_rownames <- function(hypothesis = c("null", "monotropy", "hierarchy",
 #'   - `hyp` - the resulting matrix
 #'
 #' @examples
-#' drake::loadd(encompassing_model_int)
+#' targets::tar_load(encompassing_model_int)
 #' get_hypothesis_matrix(hypothesis = "null", encompassing_model = encompassing_model_int)
 #'
 
@@ -426,7 +426,7 @@ compute_cond_prob <- function(mean, sigma, n_eq, n_ineq){
 #' @return list with the prior mean and covariance matrix
 #'
 #' @examples
-#' drake::loadd(encompassing_model_int)
+#' targets::tar_load(encompassing_model_int)
 #' hyp <- get_hypothesis_matrix(hypothesis = "hierarchy", encompassing_model_int)$hyp
 #' get_prior_info(encompassing_model = encompassing_model_int, hyp = hyp)
 #'
[…]

### 2022-10-15 R/Clusters.R

@@ -17,7 +17,7 @@
 #' @return an "hclust" class object with the resulting clusters
 #'
 #' @examples
-#' drake::loadd(data_munged)
+#' targets::tar_load(data_munged)
 #' data <- data_munged
 #' kk <- get_cluster_fit(data, parent = "mother")#'
 
@@ -58,9 +58,9 @@ get_cluster_fit <- function(data, parent = c("mother", "father")){
 #'   items are removed.
 #'
 #' @examples
-#' drake::loadd(data_munged)
-#' drake::loadd(cluster_mother_fit)
-#' drake::loadd(cluster_father_fit)
+#' targets::tar_load(data_munged)
+#' targets::tar_load(cluster_mother_fit)
+#' targets::tar_load(cluster_father_fit)
 #'
 #' get_data_cluster(data = data_munged, cluster_mother_fit, cluster_father_fit)
 #'
@@ -124,7 +124,7 @@ get_data_cluster <- function(data, cluster_mother_fit, cluster_father_fit){
 #' @return an object of class "mclustBIC"
 #'
 #' @examples
-#' drake::loadd(data_munged)
+#' targets::tar_load(data_munged)
 #' mclust_BIC(data = data_munged, parent = "mother")
 #' mclust_BIC(data = data_munged, parent = "father")
 #'

### 2022-10-15 R/Models.R

@@ -17,7 +17,7 @@
 #' @return object of class check_zi
 #'
 #' @examples
-#' drake::loadd(fit_int_nb)
+#' targets::tar_load(fit_int_nb)
 #' my_check_zeroinflation(fit_int_nb)
 #'
 
@@ -72,7 +72,7 @@ my_check_zeroinflation <- function(x, tolerance = 0.05){
 #' @return a glmmTMB fit object
 #'
 #' @examples
-#' drake::loadd(data_cluster)
+#' targets::tar_load(data_cluster)
 #' zinb_fit(data = data_cluster, y = "internalizing_sum",
 #'          formula = "gender + mother + father")
 #'
@@ -107,7 +107,7 @@ zinb_fit<- function(data_cluster, y, formula){
 #' @return a brms fit object
 #'
 #' @examples
-#' drake::loadd(data_cluster)
+#' targets::tar_load(data_cluster)
 #' zinb_brms_selected(data = data_cluster, y = "internalizing_sum",
 #'                    prior_par = "normal(0, 3)")
 #'
@@ -139,7 +139,7 @@ zinb_brms_selected <- function(data, y, prior_par){
 #' @return an integer value
 #'
 #' @examples
-#' drake::loadd(fit_int_inter)
+#' targets::tar_load(fit_int_inter)
 #' get_model_df(fit = fit_int_inter)
 #'
 
@@ -177,7 +177,7 @@ get_model_df<- function(fit){
 #'   - `weights` - fit criteria weights
 #'
 #' @examples
-#' drake::loadd(c(fit_int_zero, fit_int_mother,
+#' targets::tar_load(c(fit_int_zero, fit_int_mother,
 #'        fit_int_additive, fit_int_inter))
 #' get_rel_weights(fit_int_zero,
 #'                 fit_int_mother,
@@ -258,7 +258,7 @@ get_data_prior_predict <- function(){
 #'   `gender` and `mother`on different columns.
 #'
 #' @examples
-#' drake::loadd(brm_selected_int)
+#' targets::tar_load(brm_selected_int)
 #' model <- brm_selected_int
 #' get_post_pred(model = model)
 #'

### 2022-10-15 R/Munge_data.R

@@ -17,7 +17,7 @@
 #' @return data used in the analysis
 #'
 #' @examples
-#' drake::loadd(data_raw)
+#' targets::tar_load(data_raw)
 #' data <- data_raw
 #' munge_data(data)
 #'

### 2022-10-15 R/Plots.R

@@ -17,7 +17,7 @@
 #' @return a ggplot object
 #'
 #' @examples
-#' drake::loadd(fit_ext_zinb)
+#' targets::tar_load(fit_ext_zinb)
 #' get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
 #'
 
@@ -378,7 +378,7 @@ plot_problems_dist <- function(prob = c("ext", "int")){
 }
 #----    plot_post_pred    ----
 
-# drake::loadd(post_pred_ext)
+# targets::tar_load(post_pred_ext)
 plot_post_pred <-  function(post_pred = post_pred_ext, problem = c("Externalizing", "Internalizing")){
   problem <- match.arg(problem)
 
@@ -425,7 +425,7 @@ plot_post_pred <-  function(post_pred = post_pred_ext, problem = c("Externalizin
 }
 #----    plot_post_diff    ----
 
-# drake::loadd(post_pred_ext)
+# targets::tar_load(post_pred_ext)
 plot_post_diff <-  function(post_pred = post_pred_ext, problem = c("Externalizing", "Internalizing")){
   problem <- match.arg(problem)
 
@@ -475,7 +475,7 @@ plot_post_diff <-  function(post_pred = post_pred_ext, problem = c("Externalizin
 
 #----    my_pp_check    ----
 
-# drake::loadd(brm_selected_ext)
+# targets::tar_load(brm_selected_ext)
 
 my_pp_check <- function(brm_fit = brm_selected_ext,  problem = c("Externalizing", "Internalizing")){
   problem <- match.arg(problem)

### 2022-10-15 R/Tables.R

@@ -4,7 +4,7 @@
 
 #----    get_table_cluster    ----
 
-# drake::loadd(data_cluster)
+# targets::tar_load(data_cluster)
 
 get_table_cluster <- function(perc = TRUE, digits = 2, format = "latex"){
 
@@ -27,7 +27,7 @@ get_table_cluster <- function(perc = TRUE, digits = 2, format = "latex"){
 
 #----    get_table_cluster_ext    ----
 
-# drake::loadd(data_cluster)
+# targets::tar_load(data_cluster)
 
 get_table_cluster_ext <- function(){
   data_cluster %>%
@@ -52,7 +52,7 @@ get_table_cluster_ext <- function(){
 
 #----    get_table_prior_predict    ----
 
-# drake::loadd(data_prior_predict)
+# targets::tar_load(data_prior_predict)
 
 get_table_prior_predict <- function(data = data_prior_predict, format = c("latex", "html")){
   format <- match.arg(format)
@@ -70,7 +70,7 @@ get_table_prior_predict <- function(data = data_prior_predict, format = c("latex
 }
 #----    get_table_bf    ----
 
-# drake::loadd(BF_weights_ext)
+# targets::tar_load(BF_weights_ext)
 
 get_table_bf <- function(bf_result = BF_weights_ext,
                          path_img = "Documents/Paper/figure/",
@@ -120,7 +120,7 @@ get_table_bf <- function(bf_result = BF_weights_ext,
 
 #----    get_table_sens_analysis    ----
 
-# drake::loadd(summary_sensitivity_int)
+# targets::tar_load(summary_sensitivity_int)
 # summary_sensitivity <- summary_sensitivity_int
 
 get_table_sens_analysis <- function(summary_sensitivity, format = c("latex", "html"),
@@ -179,7 +179,7 @@ get_table_sens_analysis <- function(summary_sensitivity, format = c("latex", "ht
 
 #----    table_gender_grade    ----
 
-# drake::loadd(data_raw)
+# targets::tar_load(data_raw)
 
 table_gender_grade <- function(format = "latex"){
   data_raw %>%
@@ -307,7 +307,7 @@ get_table_cluster_prob <- function(prob = c("ext", "int"), format = "html"){
 
 #----    get_table_AIC_BIC    ----
 
-# drake::loadd(AIC_weights_ext, BIC_weights_ext)
+# targets::tar_load(AIC_weights_ext, BIC_weights_ext)
 
[…]

### 2022-10-15 R/Values.R

@@ -4,7 +4,7 @@
 
 #----    perc_females    ----
 
-# drake::loadd(data_cluster)
+# targets::tar_load(data_cluster)
 
 perc_females <- function(perc = TRUE, digits = 2){
   freq <- table(data_cluster$gender)
@@ -19,7 +19,7 @@ perc_females <- function(perc = TRUE, digits = 2){
 
 #----    perc_rare_condition    ----
 
-# drake::loadd(data_cluster)
+# targets::tar_load(data_cluster)
 
 perc_rare_condition <- function(perc = TRUE, digits = 1){
   test <- with(data_cluster,
@@ -36,7 +36,7 @@ perc_rare_condition <- function(perc = TRUE, digits = 1){
 
 #----    tot_subj    ----
 
-# drake::loadd(data_raw)
+# targets::tar_load(data_raw)
 
 tot_subj <- function(){
   nrow(data_raw)
@@ -44,7 +44,7 @@ tot_subj <- function(){
 
 #----    tot_subj_older    ----
 
-# drake::loadd(data_raw)
+# targets::tar_load(data_raw)
 
 tot_subj_older <- function(){
   data_raw %>%
@@ -54,7 +54,7 @@ tot_subj_older <- function(){
 
 #----    tot_subj_NA    ----
 
-# drake::loadd(data_raw)
+# targets::tar_load(data_raw)
 
 tot_subj_NA <- function(){
   data_raw %>%
@@ -64,7 +64,7 @@ tot_subj_NA <- function(){
 
 #----    tot_subj_included    ----
 
-# drake::loadd(data_raw)
+# targets::tar_load(data_raw)
 
 tot_subj_included <- function(){
   nrow(data_cluster)
@@ -72,7 +72,7 @@ tot_subj_included <- function(){
 
 #----    var_info    ----
 
-# drake::loadd(data_cluster)
+# targets::tar_load(data_cluster)
 
 var_info <- function(var){
 
@@ -86,7 +86,7 @@ var_info <- function(var){
 
 #----    var_summary    ----
 
-# drake::loadd(data_cluster)
+# targets::tar_load(data_cluster)
 
 var_summary <- function(var){
 
@@ -102,7 +102,7 @@ var_summary <- function(var){
 
 #----    parent_mclust    ----
 
-# drake::loadd(mclust_mother, mclust_father)
+# targets::tar_load(mclust_mother, mclust_father)
 
[…]

### 2022-10-15 Documents/Paper/paper.Rnw
add paper preprint

@@
 
-Data used for the illustrative application are part of a larger project on the social-emotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]).
 All materials and data are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
+Online supplemental material available via GitHub Pages at \url{https://claudiozandonella.github.io/Attachment/}.
 
@@
 
-#----    load drake    ----
+#----    load targets    ----
 
@@
 All materials, data, and analysis code are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
-Supplemental Material with further details is also available online at \url{https://claudiozandonella.github.io/Attachment/}.
+Supplemental Material with further details is also available online via GitHub Pages at \url{https://claudiozandonella.github.io/Attachment/}.
+
+Note that data used for the illustrative application are part of a larger project on the social-emotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\clearpage
+\section*{Author Contributions}
+
+Conceptualization: C. Zandonella Callegher, T. Marci, P. De Carli, and G. Altoè;
+Methodology: C. Zandonella Callegher, T. Marci, P. De Carli, and G. Altoè;
+Software: C. Zandonella Callegher and G. Altoè;
+Formal Analysis: C. Zandonella Callegher and G. Altoè;
+Investigation: T. Marci and  P. De Carli;
+Data Curation: T. Marci and C. Zandonella Callegher;
+Writing – Original Draft: C. Zandonella Callegher;
+Writing – Review \& Editing: T. Marci, P. De Carli, and G. Altoè;
+Visualization: C. Zandonella Callegher;
+Supervision: G. Altoè;
+Project Administration: G. Altoè;
+
+\section*{Conflicts of Interest}
+
+The authors declare that there were no conflicts of interest with respect to the authorship or the publication of this article.
+
+\section*{Supplemental Material}
+
+All materials and data are available at \url{https://doi.org/10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
+Online supplemental material available via GitHub Pages at \url{https://claudiozandonella.github.io/Attachment/}.
+
+Note that data used for the illustrative application are part of a larger project on the social-emotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]).
+
+% \section*{Prior versions}
+%
+% Preprint version of the submitted manuscript is available at [TODO].
 

### 2022-10-15 Documents/Bookdown/01-case-study.Rmd
add review supplemental materials with link to preprint

@@
 
-For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article [TODO: add link article].
+For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article available at https://psyarxiv.com/6kc5u.
 

### 2022-10-15 Documents/Bookdown/05-ext-BF.Rmd
add review supplemental materials with link to preprint

@@
 To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes factor with the encompassing prior approach.
-See the main article for a detailed introduction to this approach [TODO: add link article].
+See the main article for a detailed introduction to this approach (https://psyarxiv.com/6kc5u).
 
@@
 For each informative hypothesis, we obtain a hypothesis matrix that translates equality and inequality constraints according to the encompassing model parametrization.
-Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ([TODO: add link]).
+Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper (https://psyarxiv.com/6kc5u).
 
@@
 $$
-See the main article for more details [TODO: add link].
+For more details, see the main article available at https://psyarxiv.com/6kc5u.
 
@@
 Finally, we do not need to standardize our parameters as they represent mean groups’ differences.
-See the main article for a detailed explanation [TODO: add link article].
+For a detailed explanation, see the main article available at https://psyarxiv.com/6kc5u.
 
@@
 
-To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article [TODO: add link article].
+To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article (https://psyarxiv.com/6kc5u).
 Bayes factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).
@@
 To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
-On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details [TODO: add link article]).
+On the contrary, equality constraints are highly affected by the prior definition (for more details, see the main article available at https://psyarxiv.com/6kc5u).
 

### 2022-10-15 Documents/Bookdown/index.Rmd
add review supplemental materials with link to preprint

@@
 
-This is the Supplemental Material of the article “*Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach*” [TODO: add cit].
+This is the Supplemental Material of the article “*Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach*” available at https://psyarxiv.com/6kc5u.
 The paper aims to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.
@@
 In the supplemental material, we provide the complete statistical analyses of the case study regarding attachment.
-For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article].
+For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article available at https://psyarxiv.com/6kc5u.
 The supplemental material is structured into three parts:

### 2022-10-15 docs/attachment-bayes-factor.tex
add review supplemental materials with link to preprint

@@
 
+%----    layout    ----%
+
+% change margins
+\usepackage[outer = 105pt, inner = 85pt]{geometry}
+\usepackage{afterpage}
+\voffset 5pt
+\headsep 29pt
+\footskip 35pt
+\textheight 590pt
+\usepackage{layout}% http://ctan.org/pkg/layouts
+
+% caption
+\usepackage[labelfont=bf]{caption}
+
 %----    define infoboxes    ----%
@@
 \author{\href{https://claudiozandonella.netlify.app/}{Claudio Zandonella Callegher}, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
-\date{2022-09-25}
+\date{2022-10-15}
 
@@
 
-This is the Supplemental Material of the article ``\emph{Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach}'' {[}TODO: add cit{]}.
+This is the Supplemental Material of the article ``\emph{Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach}'' available at \url{https://psyarxiv.com/6kc5u}.
 The paper aims to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.
@@
 In the supplemental material, we provide the complete statistical analyses of the case study regarding attachment.
-For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article {[}TODO: add link article{]}.
+For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article available at \url{https://psyarxiv.com/6kc5u}.
 The supplemental material is structured into three parts:
@@
 
-For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article {[}TODO: add link article{]}.
+For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article available at \url{https://psyarxiv.com/6kc5u}.
 
@@
 \DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
-\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1719}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1720}
 \DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.162 825  {-}1.902  0.2228}
@@
 \DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0224 0.124 825  {-}0.181  0.9978}
-\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2761 0.146 825  {-}1.885  0.2300}
-\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2537 0.167 825  {-}1.522  0.4179}
+\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2761 0.146 825  {-}1.885  0.2299}
+\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2537 0.167 825  {-}1.522  0.4180}
 \DocumentationTok{\#\# }
@@
 \DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
-\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2432 0.1034 837  {-}2.353  0.0859}
-\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0243}
-\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0004}
+\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2432 0.1034 837  {-}2.353  0.0858}
+\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0248}
+\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0003}
 \DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0648 0.0981 837  {-}0.661  0.9107}
-\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0903}
+\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0900}
 \DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2188 0.1276 837  {-}1.714  0.3135}
@@
 To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes factor with the encompassing prior approach.
-See the main article for a detailed introduction to this approach {[}TODO: add link article{]}.
+See the main article for a detailed introduction to this approach (\url{https://psyarxiv.com/6kc5u}).
 
@@
 For each informative hypothesis, we obtain a hypothesis matrix that translates equality and inequality constraints according to the encompassing model parametrization.
-Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ({[}TODO: add link{]}).
+Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper (\url{https://psyarxiv.com/6kc5u}).
 
@@
 \]
-See the main article for more details {[}TODO: add link{]}.
+For more details, see the main article available at \url{https://psyarxiv.com/6kc5u}.
 
@@
 Finally, we do not need to standardize our parameters as they represent mean groups' differences.
-See the main article for a detailed explanation {[}TODO: add link article{]}.
+For a detailed explanation, see the main article available at \url{https://psyarxiv.com/6kc5u}.
 
@@
 
-To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article {[}TODO: add link article{]}.
+To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article (\url{https://psyarxiv.com/6kc5u}).
 Bayes factor and posterior probability of each hypothesis are reported in Table\textasciitilde\ref{tab:table-bf-results-ext}.
@@
 To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point.
-On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details {[}TODO: add link article{]}).
+On the contrary, equality constraints are highly affected by the prior definition (for more details, see the main article available at \url{https://psyarxiv.com/6kc5u}).
 
@@
 
-\begin{verbatim}
-## Warning: Argument 'nsamples' is deprecated. Please use argument 'ndraws' instead.
-\end{verbatim}
-
 \begin{figure}
@@
 \DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
-\DocumentationTok{\#\#  Secure {-} Anxious     {-}0.285 0.0892 837  {-}3.197  0.0079}
+\DocumentationTok{\#\#  Secure {-} Anxious     {-}0.285 0.0892 837  {-}3.197  0.0075}
 \DocumentationTok{\#\#  Secure {-} Avoidant    {-}0.120 0.0946 837  {-}1.266  0.5809}
-\DocumentationTok{\#\#  Secure {-} Fearful     {-}0.469 0.1168 837  {-}4.011  0.0003}
+\DocumentationTok{\#\#  Secure {-} Fearful     {-}0.469 0.1168 837  {-}4.011  0.0004}
 \DocumentationTok{\#\#  Anxious {-} Avoidant    0.165 0.0869 837   1.903  0.2243}
 \DocumentationTok{\#\#  Anxious {-} Fearful    {-}0.183 0.1096 837  {-}1.673  0.3346}
-\DocumentationTok{\#\#  Avoidant {-} Fearful   {-}0.349 0.1167 837  {-}2.989  0.0149}
+\DocumentationTok{\#\#  Avoidant {-} Fearful   {-}0.349 0.1167 837  {-}2.989  0.0152}
 \DocumentationTok{\#\# }
